### 2020-09-27 3_review-responses/V2_review_responses/Reviewer #1 Response.txt
First data commit: V2-1, before second review

Reviewer #1 Response

------------
1. Comment #3 from Reviewer #3
It is not a deal breaker. However, I am with Reviewer #3 that the hypotheses of this study bring much value to the body of our knowledge. In the sense that this study took an exploratory approach (i.e., data mining), hypothesis testing may not be ideal to achieve the research goal.

Comment #3 from Reviewer #3
"#3 - Literature review
*  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.

*  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist"
------------

------------
2. Comment #4 from Reviewer #3 & Comment #4 from Reviewer #5
I don't think there is nothing that the authors can do about it. I recommend the authors acknowledge it as a study limitation.

Comment #4 from Reviewer #3
"#4 - Method
*  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period. The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts

*  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc"

Comment #4 from Reviewer #5
"In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted? Are the same hotels extracted from both Ctrip and Tripadvisor? How many hotels are there? I believe different types of hotels would have generated different satisfaction level and perspectives. Please provide more details about these hotels."
------------

We added an extra layer to our research to overcome this limitation, although we admit that it's not fully encompassing the category or hotel type. We divided our datasets into price ranges. It is

------------
3. Comment #6 from Reviewer #5
Among the four issues, it is the most critical one. Adjectives themselves cannot identify their associated attribute. I don't think "inspecting random samples" provides sufficient explanation. I recommend the authors run systematic analysis to examine the association between adjectives and nouns.

Comment #6 from Reviewer #5
"Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment". Can the authors explain further how this can be avoided in your data analysis?"
------------

------------
4. Comment #7 from Reviewer #5
I am still confused with internal and external attributes. While the "location" of the hotels is an external attribute, "big" rooms, bathtubs, and bath facilities are internal attributes. Both the location of the hotel and the size of rooms and facilities cannot be changed once the construction of the hotel is completed. The authors may want to recategorise/rename them (e.g., tangibles/intangibles; soft/hard).
Look forward to it.

Comment #7 from Reviewer #5
"For the managerial and environmental keywords, what criteria were used for classifying these keywords? "
------------

### 2020-09-27 0_author-contribution/itt-emotion-authorcontribution.tex
First data commit: V2-1, before second review

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

% For the ORCID icon
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
\begin{tikzpicture}[yscale=-1,transform shape]
\pic{orcidlogo};
\end{tikzpicture}
}{|}}}}

\usepackage{lineno, hyperref}
% \usepackage[hyperfootnotes=false]{hyperref}
\usepackage{array, pbox}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{graphicx}

% To use chinese characters
\usepackage{CJKutf8}

% To add an appendix page
\usepackage[page, title]{appendix}

% Stick footnotes to bottom of the page
\usepackage[bottom]{footmisc}

% To insert commas into large numbers automatically
\usepackage{siunitx}

% To add hypothesis theorem
\usepackage{ntheorem}
\theoremseparator{:}
\newtheorem{hyp}{Hypothesis}

% To add subhypothesis theorems
\makeatletter
\newcounter{subhyp} 
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
} 
\makeatother

% To add the envelope symbol in Corresponding Author using % \Letter
\usepackage{marvosym}

% to add superscripts to mark the institute of authors
% patch \maketitle:
\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}

% For table formatting
\usepackage{multirow}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}

% For landscape tables
\usepackage{lscape}

\modulolinenumbers[5]

\journalname{Information Technology \& Tourism}

\bibliographystyle{spbasic}

\begin{document}

\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}

\titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}

\author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
        Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
        Hirofumi Nonaka                                                 \protect\affmark[1] \and
        Toru Hiraoka                                                    \protect\affmark[2]
}

\authorrunning{E. Alemán Carreón et al.}

\institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
            \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
            % Corresponding Author %  \\
            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
        \and
            \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{mendoza.espana@gmail.com}
        \and
            \hspace*{1em} Hirofumi Nonaka \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
        \and
            \hspace*{1em} Toru Hiraoka \at
            % University of Nagasaki, Nagasaki, Japan \\
            \hspace*{1em} \email{hiraoka@sun.ac.jp}
        \and
            \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
        \and
            \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\section*{Author Contribution}

H. Nonaka and T. Hiraoka conceived of the presented idea. H. Nonaka and E. Alemán Carreón developed the theory. All members participated in planning the experiments. E. Alemán Carreón and H. Mendoza España performed data collection, the experiments, and computations. E. Alemán Carreón wrote the manuscript with support from H. Nonaka and H. Mendoza España. E. Alemán Carreón and H. Nonaka participated in the discussion of results. T. Hiraoka supervised the project.

\end{document}

### 2020-09-27 0_coverletter/V1_submission/itt-emotion-coverletter.tex
First data commit: V2-1, before second review

\documentclass{letter}
\makeatletter
  \def\@texttop{}
\makeatother

\signature{Elisa Claire Alemán Carreón}
\address{
\textbf{Corresponding Author:}\\
Elisa Claire Alemán Carreón \\
Nagaoka University of Technology, Nagaoka, Japan \\
P.C. 940-2033, Ribbon Nagaoka B104, \\
1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
E-mail: elisa.claire.aleman.carreon@gmail.com
}

\addtolength{\headheight}{-11em}
\addtolength{\textheight}{10em}
\addtolength{\textwidth}{8em}
\addtolength{\oddsidemargin}{-6em}

\begin{document}

\begin{letter}{
Information Technology \& Tourism Editorial Board \\
Editor-in-Chief:  Zheng Xiang\\
Virginia Tech, USA}

\opening{Dear Zheng Xiang and ITT Editorial Board:}

We wish to submit an original research paper titled "Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning" for consideration by Information Technology \& Tourism.

We confirm that this work is original and has not been published elsewhere, nor is it currently under consideration for publication elsewhere.

In this paper, we report on our findings on the quantitative analysis of differences in hotel preferences between Chinese and English-speaking tourists in Japan using their online reviews. We found that Chinese customers are satisfied with big and clean spaces, but are unsatisfied with the level of Chinese friendliness, in that Chinese translations might be lacking. On the other hand Western customers are satisfied mostly with staff friendliness, but are unsatisfied with dirty rooms and the smell of cigarette. Both customer groups value the location of the hotel as a secondary factor for satisfaction, and both have concerns about the pricing of the hotels (value for money). We also tested a hypothesis that their satisfaction and dissatisfaction would stem from both managerial and environmental attributes of the hotel, and found that the most important factors are all managerial in nature, and as such, could be improved in the future.

We believe that this manuscript is appropriate for publication by Information Technology \& Tourism because we used text mining and machine learning techniques, as well as a similarity measure RBO used in the information field, to quantitatively measure the satisfaction of customer groups that are important for the tourism industry in Japan.

We have no conflicts of interest to disclose. Please address all correspondence concerning this manuscript to me at the e-mail provided above.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2020-09-27 0_coverletter/V2_first revision/itt-emotion-coverletter.tex
First data commit: V2-1, before second review

\documentclass{letter}
\makeatletter
  \def\@texttop{}
\makeatother

\signature{Elisa Claire Alemán Carreón}
\address{
\textbf{Corresponding Author:}\\
Elisa Claire Alemán Carreón \\
Nagaoka University of Technology, Nagaoka, Japan \\
P.C. 940-2033, Ribbon Nagaoka B104, \\
1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
E-mail: elisa.claire.aleman.carreon@gmail.com
}

\addtolength{\headheight}{-11em}
\addtolength{\textheight}{10em}
\addtolength{\textwidth}{8em}
\addtolength{\oddsidemargin}{-6em}

\begin{document}

\begin{letter}{
Information Technology \& Tourism Editorial Board \\
Editor-in-Chief:  Zheng Xiang\\
Virginia Tech, USA}

\opening{Dear Zheng Xiang and ITT Editorial Board:}

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the revised title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal, the extensive reviews and are grateful for the extension to our deadline that gave us an opportunity to work on this manuscript better under the current COVID-19 pandemic circumstances. This revision required preparing an environment for doing work from home, as well as new experiments done with a data set that is more fair and balanced as pointed out by reviewers. Finally, thanks to our reviewers, our paper is now done under a new focus and research rationale: The Japanese hospitality \textit{Omotenashi} and how different cultures interact with it in terms of satisfaction factors. We found that while Western customers are satisfied with mostly managerial factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with environmental factors (such as location and transport),  and that they do not prioritize hospitality in their satisfaction while staying at Japanese hotels. We discuss theories on the reason behind this in our revised paper.

We believe our new results and discussion are very interesting, and hope we continue to be in your consideration.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2020-09-27 0_manuscript/V1_Submit version/itt-emotion-manuscript_V1.tex
First data commit: V2-1, before second review

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

% For the ORCID icon
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
\begin{tikzpicture}[yscale=-1,transform shape]
\pic{orcidlogo};
\end{tikzpicture}
}{|}}}}

\usepackage{lineno, hyperref}
% \usepackage[hyperfootnotes=false]{hyperref}
\usepackage{array, pbox}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{graphicx}

% To use chinese characters
\usepackage{CJKutf8}

% To add an appendix page
\usepackage[page, title]{appendix}

% Stick footnotes to bottom of the page
\usepackage[bottom]{footmisc}

% To insert commas into large numbers automatically
\usepackage{siunitx}

% To add hypothesis theorem
\usepackage{ntheorem}
\theoremseparator{:}
\newtheorem{hyp}{Hypothesis}

% To add the envelope symbol in Corresponding Author using % \Letter
\usepackage{marvosym}

% to add superscripts to mark the institute of authors
% patch \maketitle:
\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}

% For table formatting
\usepackage{multirow}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}

\modulolinenumbers[5]

\journalname{Information Technology \& Tourism}

\bibliographystyle{spbasic}

\begin{document}

\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}

\titlerunning{Analyzing differences in satisfaction and dissatisfaction between Chinese and ...}

\author{REDACTED
}

\authorrunning{REDACTED}

\institute{REDACTED
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

Up until recently, most studies in tourist behavior have been biased for the Western world. With the increase of Chinese outbound tourists to other countries, academic interest for this group has risen. Increasing variation amongst clients means that managing hotels in a way that caters to their different tastes becomes more important. Despite this, cross-cultural studies of differences between Asian and Western cultures are scarce and predate the current boom in the Chinese economy. This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels. Taking advantage of Web 2.0, we can apply Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples of online reviews without interfering with the decision process of customers. This means that we can measure how important are certain attributes of the hotel to customers, and whether those are managerial or environmental for the hotel. In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which is used for top-weighted ranked lists with different elements and lengths. We found that Chinese customers prefer big and clean spaces, and that Western customers are satisfied with friendly staff members. We also found that Chinese tourists are unsatisfied with lack of a Chinese friendly environment, and that Western customers are unsatisfied with dirty rooms, or the smell of cigarette.

% \medskip
% \noindent\it{Highlights}
% \begin{itemize}
%     \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
%     \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
%     \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
%     \item Both customer groups have concerns about the pricing of hotels (value for money).
%     \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
% \end{itemize}

\keywords{Sentiment Analysis\and Hotels and Lodging\and Machine Learning\and Chinese\and English\and Preferences}

\end{abstract}

\linenumbers

\section{Introduction}\label{intro}

In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China. Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}. With these and other multicultural tourists populations, the tourist market is more and more diverse. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied. Hotel management therefore needs to cater to these different needs and expectations to increase their customers' satisfaction, maintain a good reputation, and, therefore, generate positive word-of-mouth.

However, recent studies on social sciences, which includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations. This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels. It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining, machine learning, and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines. This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Chinese and Western English-speaking tourists populations. With this data, we can both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past. For this purpose, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel, and perform a statistical extraction of the topics that the customers of each population are most concerned about.

\section{Research objective}\label{research_objective}

The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure. Furthermore, we will measure if both customer groups have differences in priorities for the factors that are common to both groups. In addition, we also measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes (internal to the hotel), as well as environmental attributes (external to the hotel).

Furthermore, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose; this means that cultural and language differences often cannot be observed in a single study.

The difference in preferences that our study uncovers can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence them to write more satisfied online reviews that will in turn increase sales and attract new customers.

\section{Theoretical background and hypothesis development}\label{theory_hypothesis}

\subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}

Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} state that satisfaction and dissatisfaction are therefore influenced by each customer's background. This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the services that a hotel can provide for them, the experiences they want to have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay. These contrasting expectations, in turn, will determine the contrasting factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
Therefore we propose our first and second hypothesis:

\begin{hyp}
\label{hyp:1}
Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
\end{hyp}

\begin{hyp}
\label{hyp:2}
The common satisfaction and dissatisfaction factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
\end{hyp}

Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. This leads to correlation analyses (either multivariate or single variable ones) where one factor can lead to satisfaction, while it is implied that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that solely correlate to satisfaction, as well as exploring factors which are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}. While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.

Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e. hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}, without focusing on factors that are uncontrollable by the hotel staff, such as surroundings, location, language immersion of the country as a whole, or of touristic destinations, as well as integration of the hotel with tours available nearby, among other factors that can play a part in the customers choice behavior and satisfaction. 
This leads to our third hypothesis:

\begin{hyp}
\label{hyp:3}
Satisfaction and dissatisfaction stems from both internal (managerial) and external (environmental) attributes of the hotel.
\end{hyp}

\subsection{Chinese and Western tourist behavior}\label{theory_zh_en}

% Asians vs Western behavior
In the past, tourist behavior analyzed from western samples and surveys was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This results in several studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce. A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; as well as \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.

One thing to note with the above cross-culture analyses is that they were performed before the year 2000. The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists, and, as such, in their satisfactions and dissatisfactions when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e. airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves.

% Universal behavior
Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries aren't representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis. \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants. As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries. The general satisfaction score was noticed to be different in those countries, but a deeper cross-cultural analysis of the satisfaction factors wasn't performed. As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.

% Western behavior 
Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data. \cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services. \cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.

% Chinese behavior
Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. Different researchers have found that Chinese tourist populations have several specific attributes. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities. With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists. And as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.

% Studies are not universal.
Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire). This means that the factors will be selected through statistical methods alone. This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.

\subsection{Data mining, knowledge discovery and sentiment analysis}\label{theory_data}

% Explain data mining and discovery of theory inside the data
In the current world, data is presented to us in larger and larger quantities. Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago, but they are now common for market and managerial studies, independent university students and any scientist that can connect to the Internet. Such quantities of data are available to study now more than ever, but it would be impossible for researchers to parse all of this data by themselves. As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation, and only then it can be established as knowledge. With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge. This process is called Knowledge Discovery in Databases.

% Text mining 
Now, there are of course many sources of numerical data to be mined, but perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form. With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed. Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer. Since then, text mining techniques have improved over the years. This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.

% Sentiment Analysis
More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.

% Data exploration
Because the methodology for finding patterns in the data is automatic and statistical in nature, it is both reliable, in that the algorithm will find a pattern by its nature, and unpredictable, in that because it has no intervention from the researchers in making questionnaires it can have different results from anything that the researchers could expect. This is why, much like actual mining, data mining is mostly exploratory in nature. One can never be sure that something can be found, but we can make predictions and estimates about where to find knowledge, and what kind of knowledge can be uncovered.

In this study, we can predict that several things might occur. Our data could show satisfaction and dissatisfaction factors that are universal and it could also find strictly cultural preferences, but we expect that both of these options will present themselves. We can also assert that, if the previous literature is correct in their findings, we could arrive at very similar results, albeit using a database several orders of magnitude larger. We can also expect that, because of the lack of questionnaire design and freedom of users to record their pleasures and grievances, it is possible that we will discover patterns that were previously unnoticed by researchers.

\section{Methodology}\label{method}

We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}}, as well as the travel site \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}} and determined the most commonly used words that would contribute the most to positive and negative opinions in a review using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. After classifying the sentences in the extracted reviews as emotionally positive or negative with an optimized SVM, we also observed the weight values of each keyword in the machine, and the frequency of the terms in all of the reviews to extract the most utilized words in either kind of reviews. We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}.

\begin{figure}[bp]
\centering
\includegraphics[width=\textwidth]{emotion-method-overview.png}
\caption{Overview of the methodology.}
\label{fig:method-overview}
\end{figure}

\subsection{Data collection}\label{datacollection}

In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5938} review pages of hotels in Japan were collected. From these pages, we extracted a total of \num[group-separator={,}]{44177} reviews, which were comprised of \num[group-separator={,}]{572218} separate sentences.

In the TripAdvisor data collection, we collected data from \num[group-separator={,}]{21154} different hotels. In total, we collected \num[group-separator={,}]{295931} reviews in English, which we then separated into \num[group-separator={,}]{2697086} sentences using the \textit{gensim} python library.

\subsection{Text processing}\label{textprocessing}

To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

\subsection{Sentiment analysis}\label{sentimentanalysis}

The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier. The selected SVM's keywords would then clearly represent the user preferences leading to positive and negative emotions. Examples of tagged sentences are shown in Table \ref{tab:training_examples}, and SVM performance results are displayed in section \ref{apx:entropy_results}.

Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus. A word that is included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero.

We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative. The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. After classification, our data contained \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.

\subsection{SVM weight analysis}\label{svmweightsanalysis}

During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly. These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those close to the separating hyperplane. Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process. Below we show the formula for the weight vector (\ref{eq:svm_weight}).

\begin{equation}\label{eq:svm_weight}
w = \sum_{i=1}^N \alpha_i y_i x_i
\end{equation}

\subsection{Rank-biased Overlap}\label{rbo}

In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\). However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity. \cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match. Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method. Webber's RBO produces 3 measurements: a minimum RBO, a residual RBO (from which one can know the maximum RBO), and an extrapolated RBO (where the list is assumed to continue in the same pattern of similarity towards infinity). The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}), Where \(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists (or it could be thought as \(1-p\) being the probability to stop looking at the next item in the list), and \(X\) being the overlap between the lists. The complete process is described at length by \cite{webber2010similarity}.

\begin{equation}\label{eq:rbo_ext}
RBO_{EXT}(S,T,p,k) = \frac{X_k}{k} \cdot p^k + \frac{1-p}{p} \sum_{d=1}^k{\frac{X_d}{d} \cdot p^d}
\end{equation}

\section{Data Analysis}\label{dataanalysis}

% WITHOUT PERCENTAGE
\subsection{Frequent keywords and their SVC weight values}\label{svmresults}

To understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the Support Vector Classifier (SVC). Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value. The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign. We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).

We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English-speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.

There were many more keywords than shown in most cases, however, and some showed to be high in weight but low in frequency. This could mean they were useful for classification (the emotional reaction is more extreme) but aren't as important a preference for users (there aren't many cases in that the keyword was applicable). In the appendix, Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context. In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.

% Chinese_frequencies_svm_weight_positive_translations_matched.csv

\begin{table}[hbp] \centering
\caption{Top 10 frequent positive Chinese keywords in satisfaction sentences.}
\label{tab:pos_keys_zh}
\begin{tabular}{|c|l|c|c|c|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
% 1
\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
    & big 
        & 15470 & 0.624 \\ \hline
% 2
\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
    & clean 
        & 12166 & 0.638 \\ \hline
% 3
\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
    & breakfast 
        & 10575 & 0.495 \\ \hline
% 4
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
    & recommendation 
        & 8752 & 0.495 \\ \hline
% 5
\begin{CJK}{UTF8}{gbsn} 环境 \end{CJK} 
    & \begin{tabular}[c]{@{}l@{}}
    environment
    \end{tabular} 
        & 8694 & 0.248 \\ \hline
% 6
\begin{CJK}{UTF8}{gbsn} 周边 \end{CJK} 
    & periphery 
        & 8456 & 0.495 \\ \hline
% 7
\begin{CJK}{UTF8}{gbsn} 近 \end{CJK} 
    & close
        & 8372 & 0.028 \\ \hline
% 8
\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK} 
    & transportation
        & 8264 & 0.586 \\ \hline
% 9
\begin{CJK}{UTF8}{gbsn} 附近 \end{CJK} 
    & nearby
        & 6619 & 0.495 \\ \hline
% 10
\begin{CJK}{UTF8}{gbsn} 地铁 \end{CJK} 
    & subway
        & 5386 & 0.180 \\ \hline
\end{tabular}
\end{table}

% Chinese_frequencies_svm_weight_negative_translations_matched.csv

\begin{table}[hbp] \centering
\caption{Frequent negative Chinese keywords in dissatisfaction sentences.}
\label{tab:neg_keys_zh}
\begin{tabular}{|c|l|c|c|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
% 1
\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
    & price 
        & 7636 & -1.505 \\ \hline
% 2
\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
    & geography 
        & 2238 & -0.812 \\ \hline
% 3
\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
    & Chinese language 
        & 1410 & -0.714 \\ \hline
% 4
\begin{CJK}{UTF8}{gbsn} 陈旧 \end{CJK} 
    & old-fashioned 
        & 698 & -0.000 \\ \hline
% 5
\begin{CJK}{UTF8}{gbsn} 距离 \end{CJK} 
    & distance 
        & 349 & 0 \\ \hline
% 6
\begin{CJK}{UTF8}{gbsn} 老 \end{CJK} 
    & old 
        & 311 & 0 \\ \hline
% 7
\begin{CJK}{UTF8}{gbsn} 华人 \end{CJK} 
    & Chinese person 
        & 16 & -0.238 \\ \hline
\end{tabular}
\end{table}

% Hugo_1_SVM_Combined_p1.5_n4.25_c2_Frequency_counts_posinega_subject-only.csv

\begin{table}[hbp]
\centering
\caption{Top 10 positive English keywords in satisfaction sentences.}
\label{tab:pos_keys_en}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
% 1
staff & 138677 & 0.537 \\ \hline
% 2
clean & 105971 & 1.886 \\ \hline
% 3
location & 103151 & 0.842 \\ \hline
% 4
helpful & 63558 & 1.999 \\ \hline
% 5
comfortable & 62793 & 1.724 \\ \hline
% 6
friendly & 57307 & 1.199 \\ \hline
% 7
recommend & 51433 & 1.158 \\ \hline
% 8
train & 45148 & -0.000 \\ \hline
% 9
free & 42084 & 0.734 \\ \hline
% 10
subway & 38354 & 1.951 \\ \hline
\end{tabular}
\end{table}

% Hugo_1_SVM_Combined_p1.5_n4.25_c2_Frequency_counts_posinega_subject-only.csv

\begin{table}[hbp]
\centering
\caption{High negative weight English keywords in dissatisfaction sentences.}
\label{tab:neg_keys_en}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
% 1
pricey & 3809 & -1.614 \\ \hline
% 2
carpet & 3683 & -0.507 \\ \hline
% 3
slow & 3177 & -1.281 \\ \hline
% 4
dirty & 2943 & -1.275 \\ \hline
% 5
uncomfortable & 2942 & -2.423 \\ \hline
% 6
stain & 2787 & -1.886 \\ \hline
% 7
cigarette & 2468 & -0.435 \\ \hline
% 8
curtain & 2032 & -0.224 \\ \hline
% 9
paper & 2029 & -0.503 \\ \hline
% 10
renovation & 1898 & -0.548 \\ \hline
\end{tabular}
\end{table}

\subsection{Rank-biased Overlap}\label{rboresults}

In order to calculate the similarity between the ranked lists shown in Tables \ref{tab:pos_keys_zh} and \ref{tab:pos_keys_en}, and the lists in Tables \ref{tab:neg_keys_zh} and \ref{tab:neg_keys_en}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points. Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis. For example, in the English keyword lists, the word is ``pricey" while in the Chinese keywords it is translated as ``price", and as such, it was changed to ``pricey" to match the English keywords. This was purely to overlap the most words possible, so it could have been very well modified the other way around with the same effect. The results of these calculations are shown in Table \ref{tab:rbo}. In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5. Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[hbp]
\centering
\caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
\label{tab:rbo}
\begin{tabular}{|l|c|r|}
\hline
\multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
\multirow{2}{*}{None}   & Satisfaction      & 0.265 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.299 \\ \hline
\multirow{2}{*}{Top 20} & Satisfaction      & 0.265 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.293 \\ \hline
\multirow{2}{*}{Top 10} & Satisfaction      & 0.266 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.285 \\ \hline
\multirow{2}{*}{Top 5}  & Satisfaction      & 0.221 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.321 \\ \hline
\end{tabular}
\end{table}

\section{Results}\label{results}

\subsection{Comparison of Chinese and English-speaking tourists' preferences}

The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)). This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well. This confirms our hypothesis \ref{hyp:1}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.

From observation, however, we can assert that both Chinese and English-speaking tourists in Japan have different priorities, but consider the location of the hotel and the availability of transport nearby, such as subway or trains, as a secondary but still important point in their satisfaction of a hotel. The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, while the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes. English-speaking tourists on the other hand value staff friendliness over room quality when considering their satisfaction.

The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that ``clean", ``recommend", ``subway" and ``price" are common factors to both customer groups. Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank. Furthermore, when arranging both lists by eliminating all uncommon elements, the lists become identical with an RBO of 1.0 for both satisfaction and dissatisfaction lists. This means hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), where the similar aspects in both customer groups were hypothesized to be different in their priority.

We also can observe some keywords that aren't considered by their counterparts. For example, Chinese tourists are very satisfied with breakfast inclusion, while English-speaking customers are satisfied with free amenities. On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.

As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature. We can see these results in Table \ref{tab:hyp3}. The interpretation of these keywords is shown in the Appendix in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[hbp]
\caption{Managerial and Environmental nature of the most frequent keywords}
\label{tab:hyp3}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|r|r|r|}
\hline
\textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
\multirow{2}{*}{Satisfaction} & Chinese speakers & 30\% & 60\% & 10\% \\ \cline{2-5} 
 & English speakers & 60\% & 30\% & 10\% \\ \hline
\multirow{2}{*}{Dissatisfaction} & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
 & English speakers & 100\% & 0\% & 0\% \\ \hline
\end{tabular}%
}
\end{table}

For our purposes, hypothesis \ref{hyp:3} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel. This is confirmed for all but one list. The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial in nature. However, this is only regarding the top 10 items in the list, and lower in the list there are some environmental factors.

\section{Discussion}\label{discussion}

The results indicate that our main hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct. Below we explore what those differences were, what is the possible cause for them, and what they imply for the industry, as well as discussing similarities between the two groups. We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stems from both internal (managerial) and external (environmental) attributes of the hotel.

\subsection{Chinese tourists - A big, clean space, and Chinese friendly}\label{disc:zh}

We found that Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels. From further inspection, we also find that while this is mostly relating to the rooms, there are many references to the public bathing facilities in the hotel. In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with special qualities. On the other hand, there are natural hot springs, called \textit{onsen}, which can be either bathing in the natural source of the water, or using the hot-spring water in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. This can be a cultural shock for many tourists, but still, this is an important attraction for many.

From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most important satisfaction factor for Chinese customers. This means that Chinese tourists have an expectation of spaciousness and cleanliness when coming to Japan, be it by reputation, previous experiences, or cultural backgrounds. Whichever is the case, it appears that Chinese tourists are satisfied, which means their expectations regarding the rooms are being met. We can compare this result with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}. This other few factors found in previous literature could be linked to the keyword ``environment" as well.

One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel. This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive. While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking. In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.

Moreover, Chinese tourists have expectations about the treatment towards the Chinese visitors that aren't being met. Be it Chinese language pamphlets, Chinese texts on instructions for the hotel room and it's appliances and features (T.V. channels, Wi-Fi setup, etc), or just the treatment towards Chinese people, it seems that their expectations are not being met. This is natural, since traveling in a strange land without knowledge of the language can be a daunting experience. \cite{ryan2001} also found that communication difficulties was one of the main reasons Chinese customers would give for not visiting again.

\subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}

From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services. The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the 4th and 6th place. Japan is famous for their customer service all over the world. Staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say ``Please, allow me to guide you", and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well. This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively. After all, Japanese staff treats all customers in this respectful manner, but for some customers, this could very well be the best they have been treated until that moment. We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists. On another note, we can also observe that the word ``free" is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.

However, we can see from the rest of the keywords that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness. Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards. The most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains. \cite{kozak2002} also found that hygiene and cleanliness were important satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts. Aside from cleanliness, we can also observe the word ``renovation" is written lower in the list, as well as the word ``paper". After observation of the samples, it is often used with the expression ``paper-thin walls", which could mean the customers can hear their neighbors easily. Regarding the word ``renovation", some cities in Japan (e.g. Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities. Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences. Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.

\subsection{Price, the common enemy}\label{disc:price}

For both customer groups, the main reason for dissatisfaction is price, which can be interpreted as a concern about value for money. A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall. The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan. In general, Japan is an expensive place to visit, which could have an impact in this placement in the ranking.

\subsection{Location, location, location}\label{disc:location}

The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists. While it wasn't the first priority for either of them, we can assert that the location of the hotel is a secondary but still important point in their satisfaction of a hotel. However, since this is an external factor to the management of the hotel, it is not often considered in literature. Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was nearby to at least two other subjects: subway or train, and convenience stores.

Japan is a country with a particular public transport system. The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for an outside observer. Buses are also available, although less used than the rail systems in the big cities. These three are particularly affordable in price. Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis. Taxis in Japan are a luxury compared to other countries. Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price. This means that for tourists, subway availability and a good map or plan to travel the city are of utmost necessity.

Japanese convenience stores, on the other hand, are also famous worldwide for their convenience. From drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs and so on, Japanese convenience stores are a haven for the traveler in need. If some trouble occurred, or a traveler forgot to pack a certain item, it is almost sure that they can find it here.

Therefore, considering both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to choose carefully their location from the moment that they are constructed. While not a top priority, this is a universal factor for both customer groups and it can be an instant way to generate positive reviews.

\subsection{Tobacco, what's that smell?}\label{disc:tobacco}

A main concern for Western tourists was the smell of tobacco in their room. Upon manual inspection of a sample of reviews with this keyword, we found that it was often the case that the room was advertised as non-smoking, and yet the smell permeated the room and curtains. Another common complaint was that there wasn't any non-smoking facilities available at all, to begin with. This can completely ruin some customers' stay, and give a bad impression for review writers, which can lower the number of future customers.

However, in comparison, Chinese customers seem to not be bothered by this at all. We consulted studies involving the use of tobacco in different countries. Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.

Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years. While smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya), it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas. However, there are many places where ``smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others. Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele. If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell. After all, even if it doesn't bother some customers, the lack of smell would not bother any existing customers.

\subsection{Managerial vs. Environmental satisfaction}\label{disc:hyp3}

As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction. For example, staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}. However, external or environmental attributes, such as location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, weather, and so on, are not usually analyzed in satisfaction studies. Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the amount of importance that those environmental or managerial attributes can have.

From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 60\% of keywords used by Chinese tourists are of an environmental nature (namely ``environment", ``periphery", ``close", ``transportation", ``nearby", and ``subway"), while the remaining 30\% is managerial in nature (and an undefined 10\%). However, these managerial words are all concentrated at the top of the list (``big", ``clean", ``breakfast"). In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean", ``helpful", and ``free" to name a few. English-speaking customers also have managerial attributes at the very top of their list. This means that if one considers the satisfaction of both Chinese and Western tourists, a hotel has the ability to improve in ways that will attract more customers in the future. If it was the other way around and the satisfaction was to be related more with environmental attributes, hotels would have to compete solely on their location. Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management. Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly. However, if hotels want to attract more and more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.

\section{Limitations}\label{limitations}

This paper is not without its limitations. We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones. Following that, we performed observations of sentences with those words, in an attempt to understand the context that these words were being used in. However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database. Another limitation is that a big portion of the Asian tourists coming to Japan are Taiwanese and Korean, of which we couldn't do an analysis because of team members not knowing those languages. Aside from that, because of the anonymous nature of the data, further typology analysis couldn't be made (for example, Chinese men and women of different ages, or their Westerner counterparts).

\section{Conclusion and Future Work}\label{conclusion}

In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via an SVC. We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof). We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points. These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.

We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups (``clean", ``recommend", ``subway" and ``price"), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0. This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.

Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel (that it can be changed via managerial decisions without relocating) or environmental attributes of the hotel (things like location, closeness to shops or public transport). We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:3}. We also found that most of the Western customer satisfaction (60\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel, while environmental attributes only make for a smaller portion of the factors (30\% of the top 10 satisfaction keywords). In the case of Chinese customer satisfaction, the top of the list was managerial in nature (30\% of the top 10 words) and a bigger portion, although lower in ranking, was environmental in nature (60\%). For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial in nature, while the other 28.6\% were environmental in nature.

Our results and discussion can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists, and we can observe their stark differences, as well as their common attributes. In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work. Another point of interest for the future of this study is to use word clusters with similar meanings instead of single words.

\begin{acknowledgements}

REDACTED

\end{acknowledgements}

% \section*{References}

\bibliography{bibfile-emotion}

\clearpage

\appendixpage
\appendix

\section{Sentiment analysis training data examples}\label{apx:sentences_ex}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table}[hbp]
\centering
\caption{Examples of positive and negative sentences used for training SVM}
\label{tab:training_examples}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|l|}
\hline
\textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good. \\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it. \\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3} 
 & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
\multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3} 
 & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
 &  & A bit pricey though \\ \hline
\end{tabular}%
}
\end{table}

\section{Entropy keyword extraction experiment results}\label{apx:entropy_results}

As explained in section \ref{sentimentanalysis}, we performed experiments with different entropy values to extract keywords from the vocabulary. Then we chose the best performing classification machine based on those keywords as shown in the Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. We also performed experiments to choose the best value of the parameter C used in the SVC. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives, but depending on the data it can increase false negatives. Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[hbp]
\centering
\caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
\label{tab:svm_f1_zh}
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
\begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
\end{tabular}
\end{table}

\begin{table}[hbp] \centering
\caption{Best performing SVC 10-fold cross-validation English text classifiers.}
\label{tab:svm_f1_en}
\begin{tabular}{|l|l|l|l|l|}
\hline
Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
\begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
\end{tabular}
\end{table}

\section{Keywords with high SVM weights regardless of frequency}\label{apx:keywords_weights}

There were many more keywords than shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}. Some showed to be high in weight but low in frequency. This could mean they were useful for classification but aren't as important a preference for users. Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context. In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.

\begin{table}[hbp] \centering
\caption{Chinese keywords with high SVM weights regardless of frequency.}
\label{tab:key_weights_zh}
\begin{tabular}{|>{\centering\arraybackslash}m{3em}|m{10em}|>{\centering\arraybackslash}m{7em}|>{\centering\arraybackslash}m{5em}|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Entropy List} & \textbf{SVC Weight} \\ \hline
\begin{CJK}{UTF8}{gbsn} 地方 \end{CJK} 
    & region, local 
        & Positive 
        & 1.343 \\ \hline
\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
    & clean 
        & Positive 
        & 0.638 \\ \hline
\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
    & big, wide 
        & Positive 
        & 0.624 \\ \hline
\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK} 
    & traffic, transportation 
        & Positive 
        & 0.586 \\ \hline
\begin{CJK}{UTF8}{gbsn} 热情 \end{CJK} 
    & cordial, kindness 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 周边 \end{CJK} 
    & periphery 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 景色 \end{CJK} 
    & scenery 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
    & recommendation 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 日本 \end{CJK} 
    & Japan 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
    & breakfast 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 附近 \end{CJK} 
    & nearby 
        & Positive 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
    & Chinese text 
        & Negative 
        & -0.714 \\ \hline
\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
    & geography 
        & Negative 
        & -0.812 \\ \hline
\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
    & price 
        & Negative 
        & -1.505 \\ \hline
\end{tabular}
\end{table}

\begin{table}[hbp]
\centering
\caption{English keywords with high SVM weights regardless of frequency.}
\label{tab:key_weights_en}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Entropy\\ List\end{tabular}}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} \\ \hline
bathhouse & Positive & 2.000 \\ \hline
museum & Positive & 2.000 \\ \hline
meeting & Positive & 1.997 \\ \hline
subway & Positive & 1.951 \\ \hline
cozy & Positive & 2.000 \\ \hline
convenience & Positive & 1.888 \\ \hline
clean & Positive & 1.886 \\ \hline
comfortable & Positive & 1.724 \\ \hline
dirty & Negative & -1.275 \\ \hline
policy & Negative & -1.463 \\ \hline
prepay & Negative & -1.517 \\ \hline
pricey & Negative & -1.614 \\ \hline
sticky & Negative & -2.000 \\ \hline
\end{tabular}
\end{table}

\section{Managerial and Environmental keywords}\label{apx:man_env}

As explained on \ref{disc:hyp3}, we identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}. The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table}[hbp]
\centering
\caption{Hotel attribute types for the top 10 satisfaction keywords}
\label{tab:man_env_pos}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|r|r|}
\cline{1-2} \cline{4-5}
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5} 
managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
managerial & clean &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
managerial & breakfast &  & location & environmental \\ \cline{1-2} \cline{4-5} 
unidentified & recommendation &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
environmental & environment &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
environmental & periphery &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
environmental & close &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
environmental & transportation &  & train & environmental \\ \cline{1-2} \cline{4-5} 
environmental & nearby &  & free & managerial \\ \cline{1-2} \cline{4-5} 
environmental & subway &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
\end{tabular}%
}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[hbp]
\centering
\caption{Hotel attribute types for the top 10 dissatisfaction keywords}
\label{tab:man_env_neg}
\resizebox{\textwidth}{!}{%
\begin{tabular}{lll|r|r|}
\cline{1-2} \cline{4-5}
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & dirty & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & stain & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
 &  &  & curtain & managerial \\ \cline{4-5} 
 &  &  & paper & managerial \\ \cline{4-5} 
 &  &  & renovation & managerial \\ \cline{4-5} 
\end{tabular}%
}
\end{table}

\end{document}

### 2020-09-27 0_manuscript/V2-1_First revision/itt-emotion-manuscript_V2-1.tex
First data commit: V2-1, before second review

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof

% For the ORCID icon
\usepackage{scalerel}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{orcidlogocol}{HTML}{A6CE39}
\tikzset{
  orcidlogo/.pic={
    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
  }
}

\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
\begin{tikzpicture}[yscale=-1,transform shape]
\pic{orcidlogo};
\end{tikzpicture}
}{|}}}}

\usepackage{lineno, hyperref}
% \usepackage[hyperfootnotes=false]{hyperref}
\usepackage{array, pbox}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{graphicx}

% To use chinese characters
\usepackage{CJKutf8}

% To add an appendix page
\usepackage[page, title]{appendix}

% Stick footnotes to bottom of the page
\usepackage[bottom]{footmisc}

% To insert commas into large numbers automatically
\usepackage{siunitx}

% To add hypothesis theorem
\usepackage{ntheorem}
\theoremseparator{:}
\newtheorem{hyp}{Hypothesis}

% To add subhypothesis theorems
\makeatletter
\newcounter{subhyp} 
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
} 
\makeatother

% To add the envelope symbol in Corresponding Author using % \Letter
\usepackage{marvosym}

% to add superscripts to mark the institute of authors
% patch \maketitle:
\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}

% For table formatting
\usepackage{multirow}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}

% For landscape tables
\usepackage{lscape}

\modulolinenumbers[5]

\journalname{Information Technology \& Tourism}

\bibliographystyle{spbasic}

\begin{document}

\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}

\titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}

\author{REDACTED
}

\authorrunning{REDACTED}

\institute{REDACTED
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then measured the similarity value for the frequency in ranked keyword lists using the Rank-biased Overlap measure. It is used for top-weighted ranked lists with different elements and lengths. We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

\keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}

\end{abstract}

\linenumbers

\section{Introduction}\label{intro}

Japan has been known historically for its hospitality being the highest grade. The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}. With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite{al2015characteristics}. Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures hold different expectations \cite{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context? Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.

In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China. Western countries, counting English-speaking countries and the whole of Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing. From that, the number of researchers interested in this phenomenon has been increasing as well. \cite[][]{sun2017}. With these and other multicultural tourist populations, the tourist market is more and more diverse. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied. Hotel management, therefore, needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.  The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.

With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}. Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more. Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study. The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines. This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.

In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}} and Western English-speaking tourists populations posting in \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}}. With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past. In order to do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel. We then perform a statistical extraction of the topics that concerns the customers of each population the most.

\section{Research objective}\label{research_objective}

This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to determine a quantitative measure of similarity between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure, both in general and only considering their common factors. More importantly, we also intend to measure how managerial and environmental attributes influence much satisfaction and dissatisfaction of both customer groups. We define managerial attributes as those internal and modifiable to the hotel. In contrast, environmental attributes are external and unmodifiable, short of moving the hotel building in its entirety.

Our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose. The short scope of those studies means that cultural and language differences often cannot be observed in a single study.

Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between cultures. These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction. Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.

\section{Theoretical background and hypothesis development}\label{theory_hypothesis}

\subsection{Japanese hospitality: \textit{Omotenashi}}\label{theory_omotenashi}

The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite{Kuboyama2020}.

It stands to reason that this high level of hospitality would be a positive aspect that would be at the top of satisfaction for any customer. However, in Japan, every business has this high level of hospitality, in differing levels of success. A simple convenience shop around the corner could be more hospitable if hotel management falls behind. Businesses have to strive to be the most hospitable, and hotels are not allowed to lag in this competition. Because of this, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer. Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.

Therefore we pose two hypotheses for our study:

\begin{subhyp}
\begin{hyp}
\label{hyp:omotenashi_zh}
Chinese tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
\end{hyp}

\begin{hyp}
\label{hyp:omotenashi_en}
Western tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
\end{hyp}

However, Japanese hospitality comes from Japanese culture. Different cultures interacting with it could have a different reaction. While some might be impressed by it, some might consider other factors more important to their stay in a hotel. This point leads us to a derivative of the above hypothesis:

\begin{hyp}
\label{hyp:omotenashi_both}
Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service.
\end{hyp}
\end{subhyp}

\subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}

Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Western and Chinese customers can then have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. These different expectations, in turn, will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.

Therefore we propose:

\begin{subhyp}
\begin{hyp}
\label{hyp:diff_all}
Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
\end{hyp}

Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another. Therefore, it could be that some factors do not appear in the other reviews at all. For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language. So we must measure their differences or similarities at their common ground as well. For this, we prepare the following hypothesis:

\begin{hyp}
\label{hyp:diff_com}
The common factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
\end{hyp}
\end{subhyp}

Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. The use of the Likert scale leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}. This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction. However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.

Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}. However, little focus is put on factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

This leads to the next hypothesis:

\begin{hyp}
\label{hyp:man_env}
Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
\end{hyp}

The resulting proportions of managerial attributes to environmental attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.

\subsection{Chinese and Western tourist behavior}\label{theory_zh_en}

% Asians vs. Western behavior
In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}. This increase resulted in several studies focusing on only the behavior of this subset of tourists. To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce. One example is \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money. Another is  \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another example is \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

One thing to note with the above cross-culture analyses is that they were performed before the year 2000. The current Chinese economy boom is making an increase in the influx of tourists. However, that boom could have created a difference in the expectations of tourists. In turn, that boom could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves.

More recent studies have surfaced as well. A cross-country study \cite{FRANCESCO201924} using posts from U.S.A. citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes. According to their results, it appears that U.S.A. customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes. Another couple of studies \cite{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S. tourists using text mining techniques and more massive datasets, although in a restaurant context.

These last three articles focus on U.S.A. culture, while our study focuses on Western culture. Another difference with our study is that of the context of the study. The first study \cite{FRANCESCO201924} has the context of tourists from 3 countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A. and Chinese tourists eating in 3 countries in Europe, and the third analyzing reviews of restaurants in Bejing. Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall? Our study measures this at a large scale across different hotels in Japan.

% Universal behavior
Other studies, perhaps recognizing that samples being comprised of people from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis. \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants. As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries. The general satisfaction score was noticed to be different in those countries. However, a more in-depth cross-cultural analysis of the satisfaction factors wasn't performed. As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.

% Western behavior 
Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data. \cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services. \cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.

% Chinese behavior
Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. Different researchers have found that Chinese tourist populations have several specific attributes. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities. \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists. Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall. However, the younger generations seem to do so less than their older counterparts.

% Studies are not universal.
Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations; the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. Since our study uses data mining, the definition of each factor is left for hotel customers to decide en masse via their reviews. This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire. Our method allows us to find factors that we would not have contemplated. It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves. This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives an advantage to our study compared to others with smaller samples. Besides, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.

% Reviewer comparison table
Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite{bauer1993changing}, tourist motivation \cite{kim2000}, and closer to our study, satisfaction levels \cite{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924, JIA2020104071, HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its leading rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered as excellent. The number of samples in other text-mining studies is also smaller to ours in comparison. Apart from that, every study has a different text mining method.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage{lscape}
\begin{landscape}
\begin{table}[p]
\centering
\caption{Comparison between cross-culture or cross-country previous studies and our study}
\label{tab:lit-rev}
\resizebox{\linewidth}{!}{%
\begin{tabular}{l|l|l|l|l|l|l|l|}
\cline{2-8}
 & \textbf{Bauer et.al (1993)} & \textbf{\begin{tabular}[c]{@{}l@{}}Choi and\\ Chu (2000)\end{tabular}} & \textbf{Kim and Lee (2000)} & \textbf{Huang (2017)} & \textbf{\begin{tabular}[c]{@{}l@{}}Francesco and\\ Roberta (2019)\end{tabular}} & \textbf{Jia (2020)} & \textbf{Our study} \\ \hline
\multicolumn{1}{|l|}{\textbf{Comparison subjects}} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} & \begin{tabular}[c]{@{}l@{}}Anglo-Americans\\ vs \\ Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ English-speakers\end{tabular} & \begin{tabular}[c]{@{}l@{}}USA\\ vs\\ China\\ vs\\ Italy\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ US tourists\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
\multicolumn{1}{|l|}{\textbf{Study topic}} & Changes in demand & Satisfaction Levels & Tourist Motivation & \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} & \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} & \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and \\ Dissatisfaction\end{tabular}} \\ \hline
\multicolumn{1}{|l|}{\textbf{Geographical focus}} & Asia Pacific region & Hong Kong & Global & Beijing & Multi-national & Multi-national & \textbf{Japan} \\ \hline
\multicolumn{1}{|l|}{\textbf{Industry}} & Hotels & Hotels & Tourism & \begin{tabular}[c]{@{}l@{}}Restaurant \\ (Beijing Roast Duck)\end{tabular} & Hotels & Restaurants & Hotels \\ \hline
\multicolumn{1}{|l|}{\textbf{Study subjects}} & Hotel managers & Hotel customers & \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
\multicolumn{1}{|l|}{\textbf{Sample method}} & surveys & surveys & survey & text mining & text mining & text mining & text mining \\ \hline
\multicolumn{1}{|l|}{\textbf{Number of samples}} & 185 surveys & 540 surveys & \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}9000 reviews \\ (3000 per country)\end{tabular} & \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}91,172 reviews\\ (49,561 Chinese)\\ (41,611 English)\end{tabular}} \\ \hline
\multicolumn{1}{|l|}{\textbf{Study method}} & statistics & VARIMAX & MANOVA & \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} & Text Link Analysis & \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}SVM and \\ Rank-biased overlap\end{tabular}} \\ \hline
\multicolumn{1}{|l|}{\textbf{Subject nationality}} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Fiji, \\ Hong Kong, \\ Indonesia, \\ Malaysia, \\ Singapore, \\ Taiwan, Guam, \\ Tahiti, Thailand\\ \\ Westerners: \\ Australia, \\ New Zealand\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Taiwan, \\ Japan,\\ South Korea, \\ South-East Asia\\ \\ Westerners: \\ North America,\\ Europe, Australia, \\ New Zealand\end{tabular} & USA, Japan & \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., USA, Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} & USA, China, Italy & USA, China & \begin{tabular}[c]{@{}l@{}}Chinese-speakers: \\ China\\ \\ English speakers:\\ (U.K., USA, \\ Australia,  \\ New Zealand, \\ Canada,  Ireland)\end{tabular} \\ \hline
\end{tabular}%
}
\end{table}
\end{landscape}

\subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}

% Explain the discovery of theory inside the data
In the current world, data is presented to us in larger and larger quantities. Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago. However, they are now standard for market and managerial studies, independent university students, and any scientist that can connect to the Internet. Such quantities of data are available to study now more than ever. Nevertheless, it would be impossible for researchers to parse all of this data by themselves. As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation. Only then can it be established as knowledge. With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize. These patterns can, later on, be evaluated to generate knowledge. This process is called Knowledge Discovery in Databases.

% Text mining 
Now, there are, of course, many sources of numerical data to be explored.  However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form. Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed. Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}. Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it. Since then, text mining techniques have improved over the years. This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.

% Sentiment Analysis
More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This method is called sentiment analysis or opinion mining. A precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion. This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.

% Machine Learning
The algorithm used for sentiment analysis in our study is called a Support Vector Machine. It is a form of supervised machine learning used for binary classification. This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically. Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task. Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template. Machine learning can also be unsupervised, where without any pre-labeled data. In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its conclusions on its own. Our study calls for a supervised machine since text analysis can be intricate. Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels. Consequently, we teach the machine through previously labeled text samples.

Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand. Machine learning methods focus on the prediction of new data based on known properties and patterns of the given data. Data mining, on the other hand, is discovering new information and new properties of the data. Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction, and using these to label the rest of the data. We are not exploring new patterns in the sentiment data. However, we are using sentiment predictions for knowledge discovery in our database. Thus our study is a data mining experiment based on machine learning.

% Data exploration
Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable. Reliable in that the algorithm will find a pattern by its nature. Unpredictable in that because it has no intervention from the researchers in making questionnaires, it can have different results from anything that the researchers could expect. These qualities determine why, much like actual mining, data mining is mostly exploratory. One can never be sure that one will find a specific something. However, we can make predictions and estimates about where to find knowledge, and what kind of knowledge we can uncover. The exploration of large opinion datasets with these methods is essential. The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion. In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.

In this study, we can predict that several things might occur. Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors. However, we expect that both of these options will present themselves. We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings. However, we are using a database of several orders of magnitude larger. We can also expect that, because of the lack of questionnaire design and users' freedom to record their pleasures and grievances, we may discover patterns that researchers previously noticed.

\section{Methodology}\label{method}

We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that would contribute the most to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized SVM. We then observed the weight values of each keyword in the machine. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}. Finally, we used this ranking in frequency to perform a Rank-biased overlap test and make observations for the hypothesis testing.

\begin{figure}[bp]
\centering
\includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
\caption{Overview of the methodology to quantitatively rank satisfaction factors.}
\label{fig:method-overview}
\end{figure}

\subsection{Data collection}\label{datacollection}

In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected. From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China. Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks. The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.

In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels. In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English. Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library. For the language detection in both cases we used the \textit{langdetect} python library.

However, we needed to make the data and comparisons we draw from each of these datasets fair. For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580} and that the overlapping date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.

\subsection{Text processing}\label{textprocessing}

To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}. In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. The English language is full of variations and conjugations of words depending on the context and tense. Thus, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

\subsection{Sentiment analysis}\label{sentimentanalysis}

The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite{powers2011}. The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions. We also performed experiments to choose the best value of the parameter C used in the SVM. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives. However, depending on the data, it can increase false negatives. Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives. SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. Examples of tagged sentences are shown in Table \ref{tab:training_examples}.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[hbp]
\centering
\caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
\label{tab:svm_f1_zh}
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
\begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
\end{tabular}
\end{table}

\begin{table}[h] \centering
\caption{Best performing SVC 10-fold cross-validation English text classifiers.}
\label{tab:svm_f1_en}
\begin{tabular}{|l|l|l|l|l|}
\hline
Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
\begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
\end{tabular}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table}[hbp]
\centering
\caption{Examples of positive and negative sentences used for training SVM}
\label{tab:training_examples}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|l|}
\hline
\textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good. \\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it. \\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3} 
 & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
\multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
 &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3} 
 & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
 &  & A bit pricey though \\ \hline
\end{tabular}%
}
\end{table}

Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus. A word that is included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero.

An SVM is trained to classify data based on previously labeled data, generalizing features of the data by defining a separating (p-1)-dimensional hyperplane in a p-dimensional space in which each dimension is a feature of the data. The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes the error of classification.

In our study, we used the linear kernel of the SVM classification process, defined by the formula (\ref{eq:svm1}) below. Each training sentence is a point of data, a row in the vector \(x\). Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence. The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector. The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the angle of the hyperplane. The bias coefficient \(b\) determines its position, as explained in section \ref{svmweightsanalysis}.

\begin{equation}\label{eq:svm1}
f(x) = w^\top x + b
\end{equation}

We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative. The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. After classification, our data contained \num[group-separator={,}]{91239} positive Chinese sentences, \num[group-separator={,}]{13837} negative Chinese sentences, \num[group-separator={,}]{167224} positive English sentences and \num[group-separator={,}]{184798} negative English sentences.

\subsection{SVM weight analysis}\label{svmweightsanalysis}

During the SVM learning algorithm, each data point that is classified incorrectly causes a change in the weight vector to classify new data correctly. These changes to the weight vector are greater for features close to the separating hyperplane. These features have stronger changes because they needed to be taken into account to classify with a minimal error. Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class in the classification process. Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\). Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications. This equation shows the last value of \(\alpha\) after the end of the cycle.

\begin{equation}\label{eq:svm_weight}
w = \sum_{i=1}^N \alpha_i y_i x_i
\end{equation}

\subsection{Rank-biased Overlap}\label{rbo}

In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\). However, the lists are not necessarily of the same length or necessarily have the same contents. They are also top-weighted (where the first rank is the most important to know, and are less and less important as the ranks continue). Therefore, we propose that it is necessary to use another measure of similarity. \cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement. It takes all of these factors into consideration when calculating a value from 0 to 1, where zero means completely different lists, and one means the two lists are an exact match. Because our Chinese keywords (their translations, at least) do not match our English keywords one to one, it is necessary to use this method. Webber's RBO produces three measurements: a minimum RBO, a residual RBO, and an extrapolated RBO.
The residual RBO allows us to know the maximum RBO. In contrast, the extrapolated RBO is calculated by assuming the list would continue in the same pattern of similarity towards infinity. The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}). \(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists, and \(X\) is the overlap between the lists. The evaluation depth \(p\) can also be understood as \(1-p\) being the probability to stop looking at the next item in the list. The complete process is described at length by \cite{webber2010similarity}.

\begin{equation}\label{eq:rbo_ext}
RBO_{EXT}(S,T,p,k) = \frac{X_k}{k} \cdot p^k + \frac{1-p}{p} \sum_{d=1}^k{\frac{X_d}{d} \cdot p^d}
\end{equation}

\section{Data Analysis}\label{dataanalysis}

\subsection{Frequent keywords and their SVC weight values}\label{svmresults}

To understand the satisfaction and dissatisfaction factors of Chinese tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use, and their weight in the Support Vector Classifier (SVC). Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value. The frequency of the keywords in the database shows the level of priority it has for customers. The weight value allows us to observe the sentiment it relates to by its positive or negative sign. We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment. A positive weight means positive sentiment, and a negative weight signifies negative sentiment).

We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study. The keywords are the quantitative rank of the needs of Chinese and English speaking customers. This is shown in the Tables \ref{tab:pos_keys} for positive keywords and \ref{tab:neg_keys} for negative ones (however, the negative Chinese keyword list does not have more than seven keywords available).

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table}[h]
\centering
\caption{Top 10 positive keywords in positive sentences}
\label{tab:pos_keys}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|l|c|c|l|l|c|c|}
\cline{1-4} \cline{6-8}
\multicolumn{4}{|c|}{\textbf{Positive Chinese Keywords}}                                             &                                & \multicolumn{3}{c|}{\textbf{Positive English Keywords}}                       \\ \cline{1-4} \cline{6-8} 
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 大 \end{CJK}             & big                                       & 10155              & 0.623               &                                & staff                              & 13583              & 0.537               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK}            & clean                                     & 6918               & 0.638               &                                & location                           & 10127              & 0.842               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK}            & transportation                            & 6765               & 0.586               &                                & clean                              & 7636               & 1.886               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 日本 \end{CJK}            & Japan                                     & 5889               & 0.495               &                                & helpful                            & 5271               & 1.999               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK}            & breakfast                                 & 5726               & 0.495               &                                & friendly                           & 5060               & 1.199               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 近 \end{CJK}             & close                                     & 5348               & 0.028               &                                & comfortable                        & 4948               & 1.724               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 地铁 \end{CJK}            & subway                                    & 4491               & 0.18                &                                & shopping                           & 4884               & 1.308               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 购物 \end{CJK}            & shopping                                  & 4206               & 0                   &                                & train                              & 4778               & 0                   \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 下次 \end{CJK}            & next time                                 & 3596               & 0.247               &                                & subway                             & 4405               & 1.951               \\ \cline{1-4} \cline{6-8} 
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK}            & recommend                                 & 3574               & 0.495               &                                & recommend                          & 3812               & 1.158               \\ \cline{1-4} \cline{6-8} 
\end{tabular}%
}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[h]
\centering
\caption{Top 10 negative keywords in negative sentences}
\label{tab:neg_keys}
\resizebox{\textwidth}{!}{%
\begin{tabular}{clccl|l|c|c|}
\cline{1-4} \cline{6-8}
\multicolumn{4}{|c|}{\textbf{Negative Chinese Keywords}}                                                                                                             & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{3}{c|}{\textbf{Negative English Keywords}}                       \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{Translation}} & \multicolumn{1}{c|}{\textbf{Frequency}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} }            & \multicolumn{1}{l|}{price}                & \multicolumn{1}{c|}{1908}               & \multicolumn{1}{c|}{-2}                  &                                & dated                              & 426                & 0                   \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} }            & \multicolumn{1}{l|}{Chinese language}     & \multicolumn{1}{c|}{744}                & \multicolumn{1}{c|}{-0.714}              &                                & working                            & 350                & -0.557              \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} }            & \multicolumn{1}{l|}{geography}            & \multicolumn{1}{c|}{710}                & \multicolumn{1}{c|}{-0.812}              &                                & pricey                             & 327                & -1.614              \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 距离 \end{CJK} }            & \multicolumn{1}{l|}{distance}             & \multicolumn{1}{c|}{440}                & \multicolumn{1}{c|}{0}                   &                                & slow                               & 306                & -1.281              \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 陈旧 \end{CJK} }            & \multicolumn{1}{l|}{old-fashioned}        & \multicolumn{1}{c|}{338}                & \multicolumn{1}{c|}{0}                   &                                & carpet                             & 224                & -0.507              \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 老   \end{CJK} }             & \multicolumn{1}{l|}{old}                  & \multicolumn{1}{c|}{323}                & \multicolumn{1}{c|}{0}                   &                                & cigarette                          & 220                & -0.435              \\ \cline{1-4} \cline{6-8} 
\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 华人 \end{CJK} }            & \multicolumn{1}{l|}{Chinese person}       & \multicolumn{1}{c|}{16}                 & \multicolumn{1}{c|}{-0.5}                &                                & uncomfortable                      & 207                & -2.423              \\ \cline{1-4} \cline{6-8} 
                                                                         &                                           &                                         &                                          &                                & paper                              & 185                & -0.503              \\ \cline{6-8} 
                                                                         &                                           &                                         &                                          &                                & smallest                           & 168                & -1.035              \\ \cline{6-8} 
                                                                         &                                           &                                         &                                          &                                & dirty                              & 163                & -1.275              \\ \cline{6-8} 
\end{tabular}%
}
\end{table}

\subsection{Rank-biased Overlap}\label{rboresults}

In order to calculate the similarity between the ranked lists shown in Table \ref{tab:pos_keys}, and the lists in Table \ref{tab:neg_keys}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points. Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis. For example, in the English keyword lists, the word is ``pricey," while in the Chinese keywords it is translated as ``price," so we changed it to ``pricey" to match the English keywords. We did this change purely to overlap the most words possible, and so it could have been modified the other way around with the same effect. The results of these calculations are shown in Table \ref{tab:rbo}. In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5. The RBO measure can work regardless of the length of each list, so there was not a problem in its calculation.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[h]
\centering
\caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
\label{tab:rbo}
\begin{tabular}{|l|c|r|}
\hline
\multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
\multirow{2}{*}{None}   & Satisfaction      & 0.217 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.137 \\ \hline
\multirow{2}{*}{Top 20} & Satisfaction      & 0.216 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.132 \\ \hline
\multirow{2}{*}{Top 10} & Satisfaction      & 0.257 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.128 \\ \hline
\multirow{2}{*}{Top 5}  & Satisfaction      & 0.176 \\ \cline{2-3} 
                        & Dissatisfaction   & 0.176 \\ \hline
\end{tabular}
\end{table}

\section{Results}\label{results}

\subsection{Experiment results and testing the hypotheses}

From the observation of the top-ranking subjects for Chinese tourists, we can assert that keywords relating to service and staff friendliness are not on the top 10 satisfaction factors. Besides, there are complaints about a Chinese friendly environment. This makes our hypothesis \ref{hyp:omotenashi_zh} rejected. On the other hand, the word ``staff'' tops the list of satisfaction factors in English-written reviews, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''. This confirms our hypothesis \ref{hyp:omotenashi_en}. Since we found that these two populations are different in their satisfaction with Japanese hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.

The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.176 to 0.257 in satisfaction lists, and from 0.128 to 0.176 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)). This means that, while there is some similarity, the satisfaction and dissatisfaction factors are fundamentally different if we consider them as top-weighted; that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well. This confirms our hypothesis \ref{hyp:diff_all}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.

Both Chinese and English-speaking tourists in Japan have different priorities. However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel. The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness. In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes. English-speaking tourists, on the other hand, value staff friendliness over room quality when considering their satisfaction.

The lists for Chinese and English-speaking tourists are quite different. However, if we compare the lists, we find that ``clean", ``recommend," ``subway," ``shopping,"  and ``price" are shared factors to both customer groups. Their place in the ranked list is the same for most of them, and only ``shopping" and ``subway" are exchanged in priority. Furthermore, when arranging both lists by eliminating all unique elements, the lists become almost identical with an RBO of 0.906 for the top 20 and top 10 satisfaction keywords and 1.0 for the dissatisfaction lists. The lists become dissimilar when there is no cutoff point. However, it's still an RBO of 0.575 for the satisfaction list and 1.0 for the dissatisfaction list. This means hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), where we hypothesized shared aspects in both customer groups to be different in their priority.

We also can observe some keywords that are not considered by their counterparts. For example, mainland Chinese tourists are very satisfied with breakfast inclusion. At the same time, English-speaking customers are satisfied with the staff and service. On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.

We can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are managerial attributes internal to the hotel, that is, or environmental attributes external to it. We manually labeled the top keywords of each language into either managerial or environmental by considering how the word would be used when writing a review. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial. If the word is describing factors that are unchangeable by the staff or management, we consider them environmental. The interpretation of these keywords is shown in the Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[normalem]{ulem}
% \useunder{\uline}{\ul}{}
\begin{table}[h]
\centering
\caption{Hotel attribute types for the top 10 satisfaction keywords}
\label{tab:man_env_pos}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|r|r|}
\cline{1-2} \cline{4-5}
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5} 
managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
managerial & clean &  & location & environmental \\ \cline{1-2} \cline{4-5} 
environmental & transportation &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
unidentified & Japan &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
managerial & breakfast &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
environmental & close &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
environmental & subway &  & shopping & environmental \\ \cline{1-2} \cline{4-5} 
environmental & shopping &  & train & environmental \\ \cline{1-2} \cline{4-5} 
unidentified & next time &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
unidentified & recommend &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
\end{tabular}%
}
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table}[h]
\centering
\caption{Hotel attribute types for the top 10 dissatisfaction keywords}
\label{tab:man_env_neg}
\resizebox{\textwidth}{!}{%
\begin{tabular}{lll|r|r|}
\cline{1-2} \cline{4-5}
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & dated & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & working & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
 &  &  & paper & managerial \\ \cline{4-5} 
 &  &  & smallest & managerial \\ \cline{4-5} 
 &  &  & dirty & managerial \\ \cline{4-5} 
\end{tabular}%
}
\end{table}

For our purposes, hypothesis \ref{hyp:man_env} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel. This is confirmed for all but one list. The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial. However, this is only regarding the top 10 items on the list. Lower on the list, we can observe some environmental factors. We can see the summarized results in Table \ref{tab:hyp_man_env}.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[h]
\caption{Managerial and Environmental nature of the 10 most frequent keywords}
\label{tab:hyp_man_env}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|c|c|r|r|r|}
\hline
\textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
\multirow{2}{*}{Satisfaction} 
    & Chinese speakers & 30\% & 40\% & 30\% \\ \cline{2-5} 
    & English speakers & 50\% & 40\% & 10\% \\ \hline
\multirow{2}{*}{Dissatisfaction} 
    & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
    & English speakers & 100\% & 0\% & 0\% \\ \hline
\end{tabular}%
}
\end{table}

\subsection{Chinese tourists - A big and clean space}\label{disc:zh}

We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels. From inspecting random samples, we also find that this is mostly relating to the rooms. There are also many references to the public bathing facilities in the hotel. In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called \textit{onsen}. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.

From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most critical satisfaction factor for Chinese customers. However, the word ``big" is widespread in the language and could be used in different contexts to point out positive and negative aspects. Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word ``big" in Chinese. A team of Chinese speaking lab members then pointed out the usage of the word. Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities.

One key component we found in Chinese customer satisfaction factors is the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, like “food” or “eating,” and in a lower ranking. In contrast, the word “breakfast” refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. A recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast.

\subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}

From the satisfaction factors of English-speaking tourists, we can see that at least three words relate to staff friendliness and services. The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the fourth and fifth place. Japanese high standards in hospitality very likely influenced this result.

Aside from cleanliness, we can also observe the word ``working" is written higher on the list, as well as the word ``paper." We observed the samples, and it is often used with the expression ``paper-thin walls", which could mean the customers can easily hear their neighbors. Regarding the word ``working,'' we also took a sample of the texts to see its context. It seems to be related mostly to construction work near or at the facilities. Some cities in Japan (e.g., Osaka) are currently undergoing a large number of renovations, which are also extending to the hotel facilities. Customers staying in places in renovation or near a construction site can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences. Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.

An interesting detail of the keyword ranking is that the word ``comfortable" is high on the list of satisfaction factors and ``uncomfortable" high on the dissatisfaction factors. It seems that in general, western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.

\subsection{Tobacco, what's that smell?}\label{disc:tobacco}

A concern for Western tourists was the smell of tobacco in their room. Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains. Another common complaint was that there were no non-smoking facilities available at all. The smell of smoke can completely ruin some customers' stay and give a bad impression to review writers, which can lower the number of future customers.

However, in comparison, Chinese customers seem not to be bothered by this at all. We consulted studies involving the use of tobacco in different countries. Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.

Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years. Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya). However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas. However, there are many places where ``smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others. Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele. If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell. After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all kinds of customers.

\subsection{Location, location, location}\label{disc:location}

The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists. While it was not the priority for either of them, we can assert that the hotel's location is a secondary but still important point in the hotel's satisfaction. However, since this is an external factor to the management of the hotel, it is not often considered in the literature. Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.

Japan is a country with a peculiar public transport system. The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor. Buses are also available, although less used than the rail systems in the big cities. These three are unusually affordable in price. Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis. Taxis in Japan are a luxury compared to other countries. Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price. This means that for tourists, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity.

Japanese convenience stores, on the other hand, are also famous worldwide. Japanese convenience stores are a haven for the traveler in need. It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, and so on. If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.

Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed. While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.

\section{Discussion}\label{discussion}

The results indicate that our hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct. Furthermore, they indicate that, in the context of Japanese hospitality, only Western customers show satisfaction from staff and service amongst their top detected factors. Below we explore the possible interactions with \textit{Omotenashi}, what the differences between Chinese and Western tourists were, what is the possible cause for them, and what they imply for the industry. We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.

\subsection{Western and Chinese tourists in the \textit{Omotenashi} environment}\label{disc:omotenashi}

To this day, scholars continue to correct our historical bias towards the west. In this time, studies have determined that different cultural backgrounds lead to different expectations, which in turn influence the satisfaction of tourists. Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations. However, Japan presents a particular environment. The spirit of hospitality and service, \textit{Omotenashi}, excels, and is considered the highest standard across the world. Can such an environment affect different cultures equally? Or is it only attractive to certain cultures? Our study brings light to these questions.

Our results indicate that Western tourists are the most satisfied with friendly and helpful staff in Japan. As explained earlier in this paper, Japan is famous for its customer service all over the world. Respectful language and bowing are not exclusive to high priced hotels or businesses and can even be found in convenience stores. The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences. While it could be a culture shock to some, it is mostly seen positively. After all, the Japanese staff respectfully treats all customers. However, for some customers, this could be the best way they have been treated until that moment. We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in the satisfaction of Western tourists.

However, we can see from the rest of the western keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness. Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards. The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench, and general dirtiness. \cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists. However, in the previous literature, this was linked merely to satisfaction. In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction. Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.

According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction. When presented with Japanese hospitality, this expectation is met and overcome. However, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality. We could theorize that despite being presented with high standard hospitality, it is ignored. It could be that their culture does not hold the expectation initially. That is, when an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.

On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction. It is necessary to note the difference between these two phenomenons. The ``nice surprise'' fulfills a need unexpectedly, while perhaps the hospitality grade in Japan is not fulfilling a high enough need for the Chinese population, resulting in less satisfaction. For greater satisfaction, the existence of a need being met is necessary.

However, another possibility presents itself when we observe the Chinese tourists' dissatisfaction factors. Chinese tourists may have expectations about the treatment towards the Chinese visitors that are not being met, even in this high standard hospitality environment. Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite{heinrich2012making, coulmas2002japan}. While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging. Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V. channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples. It is natural to be dissatisfied, since traveling in a strange land without knowing the language can be a daunting experience. \cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again. It seems like this is a problem that is not singular to Japan.

Our initial question was whether the environment of high-grade hospitality would affect both cultures equally. This study brought us closer to the answer. On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners. In that case, it appears that the difference stems from a psychological place. Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction. On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.

It is unclear from our results which of these could be the case. One thing is clear for hotel managers, however. Competing in \textit{Omotenashi} does include language services, especially in the international tourism industry. Better multilingual support can only improve that already high standard in Japan. Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment. Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.

\subsection{Managerial vs. Environmental satisfaction}\label{disc:man_env}

As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction. Examples of managerial attributes include staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}. However, external or environmental attributes, such as the location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies. Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the importance of those environmental or managerial attributes.

From Table \ref{tab:hyp_man_env} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 40\% of keywords used by Chinese tourists are of an environmental nature (namely ``transportation", ``close", ``subway", and ``shopping"), while a lower 30\% is managerial in nature (and an undefined 30\%). However, two of these managerial words are all concentrated at the top of the list (``big", ``clean"). Chinese tourists could expect spaciousness and cleanliness when coming to Japan. That expectation could be caused by reputation, previous experiences, or cultural backgrounds. Some scholars argue that different cultures have different room size perceptions \cite{Saulton2017}. Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures. We argue that one country is not representative of others' cultures, so there can be differences between South Korea and China in room size perception. However, an interesting point appears. It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners. The dissatisfaction list for Western tourists could indicate that they perceive the rooms or bathtubs as small compared to Chinese tourists that praise them. We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}. These other few factors found in previous literature could be linked to the keyword ``environment" as well.

In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean," ``helpful," and ``friendly," to name a few. English-speaking customers also have managerial attributes at the very top of their list, except for the environmental nature of the location of the hotel. If one considers both Chinese and Western tourists' satisfaction, a hotel can improve in ways that will attract more customers in the future. If it was the other way around, and the satisfaction was related more with environmental attributes overall, hotels would have to compete solely on their location.

For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money. A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall. The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan. In general, Japan is an expensive place to visit, which could impact this placement in the ranking. Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1  meters cost around 3,000 to 6,000 yen per night. Bigger business hotel rooms are expensive, ranging from 5,000 to 12,000 yen per night. For comparison, hotels in the USA with a similar quality can be half the price.

Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management. Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly. However, if hotels want to attract more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.

Now, a point of interest in this study is the difference in how managerial and environmental factors concern Chinese and Western tourists. We can see that for Chinese customers, while the top positive keyword is managerial, the size of a room is hardly modifiable once the hotel's construction is complete. The second keyword follows as a managerial factor as well. Except, this time, hotel management can readily improve the cleanliness of their hotel. The rest of the positive keywords, however, are either undefined or environmental. Once the location and construction of the hotel are set, not much can be done to satisfy a Chinese tourist further. On the other hand, one can turn the dissatisfaction factors into satisfaction by focusing on those for improvement. As mentioned before, Chinese language availability is another managerial attribute that can be improved with investment in staff and training.

Western tourists, on the other hand, are all around both satisfied and dissatisfied with mostly managerial factors, with a 50\% of the top 10 satisfaction factors and a 100\% of the top 10 dissatisfaction factors coming from managerial attributes. The room for improvement for Western tourists is more extensive than their Chinese counterparts, and as such, present a bigger investment opportunity. As mentioned earlier in this paper, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite{choi2000}. With bigger returns on managerial improvements, it seems like investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell. Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.

The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging. Attracting a large number of Chinese customers can be a viable strategy for hotels. However, as mentioned before, they tend to focus more on environmental attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.

The basic premise of this study is that different cultures lead to different expectations and satisfaction factors. This premise also plays a role in the differentiation between the preference of managerial or environmental attributes. Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment. Chinese historical backgrounds of Confucianism, Taoism and Buddhism permeate the thought processes of Chinese populations. However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite{gao2017chinese}. However, one could argue that there is a Chinese cultural attribute that emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated. According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite{kim2000}. A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.

\subsection{Implications for hotel managers}\label{disc:implications}

Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations. Chinese tourists are not experiencing the best that \textit{Omotenashi} has to offer. Either they do not get much satisfaction from hospitality or feel that basic language and communication needs are not being met. On the other hand, Western tourists are elated with Japanese hospitality. The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers. Japan is recently seeing an increase in Chinese students as well as Western students of universities. Hiring students as part-time workers could increase the language services of a hotel.

To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free. It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers. Western tourists were also observed to have high standards in comfort, which can be improved upon managerially for better reviews. Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists. However, not all hotels can invest in all of these factors simultaneously. Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free.

Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well. As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists. Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed. A suggestion could be to purchase land and start the construction after plans to make new subway lines are made.

It is left to the managers to consider their business model for the next strategy. One option could be attracting more Chinese customers in number with their observed low budgeting. Another could be attracting more high budget Western customers is on par with their business model. For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase.

\section{Limitations and Future Work}\label{limitations}

This paper is not without its limitations. We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones. Following that, we attempted to understand the context that these words were being used in by taking samples and observing them manually. However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database. Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean. We could not analyze these populations because our team members do not know those languages. Aside from that, because of the nature of the data collected, further typology analysis could not be made (for example, Chinese men and women of different ages or their Westerner counterparts).

In future work, we plan to investigate further into this topic. We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work. Another point of interest in the future of this study is to use word clusters with similar meanings instead of single words.

\section{Conclusion}\label{conclusion}

In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels. We extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations. We used these keywords for sentiment classification via an SVC. We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences to find the differences between Chinese and Western tourists.

In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}. However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction. As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected. Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed. From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}. One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers. The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way. We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.

We obtained values ranging from 0.176 to 0.257 in satisfaction lists and from 0.128 to 0.176 in dissatisfaction lists at different cutoff points. These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}. We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers. We found that from the four words that were common amongst both groups (``clean", ``recommend," ``subway," and ``price"). When these shared terms were isolated, both lists were almost identical at the cutoff point of 20 words. This resulted in an RBO ranging from 0.906 to 1.0. This means our hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.

Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel. Managerial attributes are those that they can be changed via managerial decisions without relocating. On the other hand, environmental attributes are things like location, closeness to shops, or public transport. We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:man_env}. We also found that most of the Western customer satisfaction (50\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel.

In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords). In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%). For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental. We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies. One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number. They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast. Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free. With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels. While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns. The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased. In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.

\begin{acknowledgements}

REDACTED

\end{acknowledgements}

% \section*{References}

\bibliography{bibfile-emotion}

\end{document}

### 2020-09-27 0_titlepage/itt-emotion-titlepage.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_author-contribution/itt-emotion-authorcontribution.tex
@@
 
-\section*{Author Contribution}
+\begin{acknowledgements}
 
-H.
-Nonaka and T.
-Hiraoka conceived of the presented idea.
-H.
-Nonaka and E.
-Alemán Carreón developed the theory.
-All members participated in planning the experiments.
-E.
-Alemán Carreón and H.
-Mendoza España performed data collection, the experiments, and computations.
-E.
-Alemán Carreón wrote the manuscript with support from H.
-Nonaka and H.
-Mendoza España.
-E.
-Alemán Carreón and H.
-Nonaka participated in the discussion of results.
-T.
-Hiraoka supervised the project.
+During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the interpretation of the data.
+We would like to show gratitude to Mr.
+Liangyuan Zhou, Ms.
+Min Fan, and Ms.
+Eerdengqiqige for this.
+
+We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+\medskip
+
+Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+\medskip
+
+Conflict of interest: none
+
+\end{acknowledgements}
 

### 2020-09-27 2_revisions/V0_Before submission/V0_0_After rejection TMP try 1/tmp-emotion_V0_0.tex
First data commit: V2-1, before second review

\documentclass[review]{elsarticle}

\usepackage{lineno, hyperref}
% \usepackage[hyperfootnotes=false]{hyperref}
\usepackage{array, pbox}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{CJKutf8}
\usepackage[page, title]{appendix}
% \usepackage{tablefootnote}
\usepackage{threeparttable}
\usepackage{etoolbox}
\appto\TPTnoteSettings{\footnotesize}
\usepackage[bottom]{footmisc}
\usepackage{siunitx}

%to have numbered 4th level sections 1.1.1.1
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

% to remove period in 4th level sections 1.1.1.1
\makeatletter
\def\els@aparagraph[#1]#2{\elsparagraph[#1]{#2}}
\def\els@bparagraph#1{\elsparagraph*{#1}}
\makeatother
% to enter a newline after 4th level sections
\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\smallskip}

\modulolinenumbers[5]

\journal{Tourism Management Perspectives}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
% \bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Quantitative ranking of satisfaction and dissatisfaction factors based on text mining of online reviews from Chinese and English speaking tourists visiting Japan}

%% or include affiliations in footnotes:
\author[gidai]{Elisa Claire Alemán Carreón
\corref{mycorrespondingauthor}}
\ead{s153400@stn.nagaokaut.ac.jp}
% \orcid{0000-0002-6437-0866}

\author[gidai]{Hirofumi Nonaka}
\ead{nonaka@kjs.nagaokaut.ac.jp}

\author[nagasaki]{Toru Hiraoka}
\ead{hiraoka@sun.ac.jp}

\address[gidai]{Nagaoka University of Technology, Nagaoka, Japan}
\address[nagasaki]{University of Nagasaki, Nagasaki, Japan}

\cortext[mycorrespondingauthor]{
Corresponding author%: \\
% Elisa Claire Alemán Carreón \\
% Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
% Cell Phone: 080-9869-4756 \\
}

\begin{abstract}
Recently, there has been a boom in international tourism in Japan, where particularly Chinese tourists are increasing rapidly, among other international tourists. Because of its effect on the Japanese economy, there is a need for the use of newer research tools that are cost and time effective and use online reviews, which increasingly affect sales and the influx of customers. Using machine learning, we determined keywords representing satisfaction and dissatisfaction factors from Chinese and English online reviews of Japanese hotels in the portal sites \textit{Ctrip} and \textit{TripAdvisor}. We identified that Chinese customers react positively to included breakfasts and big rooms, and are unsatisfied with the pricing of the hotel. We also found English speaking customers dislike pricey hotels and have a high dislike for dirty rooms, stains, and cigarette smell, and that they mainly focus positively on staff, cleanliness, and transportation availability.

\medskip
\noindent\it{Highlights}
\begin{itemize}
    \item Chinese customers tend to prefer included breakfasts, and rooms that are big and clean.
    \item Across all hotel prices, unsatisfied Chinese customers focus on the pricing of the hotel.
    \item English speaking customers are satisfied with the staff, cleanliness, and transportation availability.
    \item English speaking customers dislike pricey hotels and have a high dislike for dirty rooms and cigarette smell.
\end{itemize}

\end{abstract}

\begin{keyword}
Entropy\sep Sentiment Analysis\sep Hotels and Lodging\sep Support Vector Machine\sep Chinese\sep Satisfaction and Dissatisfaction
\end{keyword}

\end{frontmatter}

\section{Introduction}\label{intro}

The population of Chinese tourists has recently increased significantly worldwide over the years. This increase has led to a significant impact on several industries over the world, most directly the hotel industry, as their customer bases changed. In addition to this impact on business, there is a current increase in academic research across the world about Chinese tourist populations \cite[][]{sun2017}. Particularly in Japan, however, international tourism has been increasingly exerting a stronger influence in the economy \cite[][]{Jones2009}. There were notable increases in the Chinese tourist population in Japan of 107.3\% from 2014 to 2015, and a total number of tourists of \num[group-separator={,}]{6372948} in 2016 \cite[][]{jnto2017}. This increase in international tourism creates a need for cross-language, cost and time effective market research tools. In the hospitality industry, where language barriers are a constant problem, there are difficulties and costs when attempting to understand the needs of their customer base.

Until recent years, most of these market studies are performed based on the results of surveys or interviews. Currently, however, there are data mining and text mining techniques which potentially have the advantage over surveys and interviews. During recent years, several studies have successfully proved the validity and potential of using text and data mining analysis in the business management field. A study classified different kinds of Social Media posts and customer response from several U.S. pizza selling companies \cite[][]{he2013}. Another study ranked products by using online reviews and sentiment analysis \cite[][]{liu2017149}, while another used them to predict product sales \cite[][]{fan201790}. Other uses for text mining techniques include patent document analysis, as was done in a study on patent scoring \cite[][]{nonaka2014}, and another on the extraction of technological terminology in patents \cite[][]{nonaka2012}. It has also been used in the tourism and hospitality field to predict hotel demand by using web traffic data \cite[][]{yang2014} or to make recommender systems \cite[][]{loh2003}. Data mining and text mining techniques can not only cheaply and quickly gather tens of thousands if not more samples, but the source of this extensive amount of information also can be thought to be unaltered by human intervention in any part of the data extraction process.

An important benefit of using data and text mining in the hospitality field is that because of the current behavior of the customers in the information age, where the searching, choosing and booking process involves reading online reviews, and where customers write online reviews depending on their satisfaction or dissatisfaction. Previous studies have found that there is a correlation between prominent reviews and sales figures \cite[][]{basuroy2003, ye2009}. There are also studies showing the direct impact of online hotel reviews on consumer consideration, that is, the decision process of many customers is affected either positively or negatively because of the reviews, with a stronger impact for lesser known hotels \cite[][]{vermeulen2009}. Online reviews give researchers access to large databases of unfiltered customers opinions without the need to ask directly via surveys or interviews, and they also provide availability of data from tourists writing in many languages. It is because of the important impact the hotel reviews have on consumers, and because of the highly polarized emotional content these reviews hold that we have decided to use this data for analysis.

Many researchers have focused on studying the level of satisfaction of customers for predefined factors \cite[e.g.][]{balbi2018, kim2017362, truong2009, wu2009, shanka2004, kozak2002}, while others focus on motivation, choice or behavior \cite[e.g.][]{romao2014, dongyang2015}. However, most of the studies rely on making inferences about the larger population based on predefined factors, instead of extracting the factors directly from the data without human intervention. Not only that but when examining international tourism, they are limited by language barriers. In our study, we aim to use the benefits of online reviews to mathematically extract the answer to these questions in a manner that doesn't rely on understanding the language to expand it further to a larger corpus. In addition, while most studies with text mining techniques and sentiment analysis techniques focus on either relevant topics or the sentiment value of reviews, this study merges both techniques to find the relevant topics and their ties to each emotional response.

In our study, we extracted satisfaction and dissatisfaction keywords and analyzed the needs of Chinese and English speaking customers of Japanese Hotels. We chose this combination of population and destination because we aim to apply machine learning techniques to overcome language barriers on a large scale. The extracted keywords are the key to researching which topics and in what order of priority the Chinese tourist and English speaking tourist populations consider when they write their reviews. This is, of course, valuable information for making business management decisions from the point of view of the hotel industry companies. Knowing which topics are not only largely discussed, but those that are most related to customer satisfaction and dissatisfaction, a company can improve customer service or facilities to increase profit. Using the methodology detailed in this study, such knowledge can become available to other researchers and companies by applying it in different environments.

\section{Research objective}\label{research_objective}

The objective of this study is to determine the factors influencing the satisfaction or dissatisfaction of Chinese customers as well as studying English speaking customers of Japanese Hotels because of the language barrier that can be studied and the economic weight that these customers represent. These satisfaction and dissatisfaction factors can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence newer customers to write more satisfied online reviews that will in turn increase sales and attract new customers.

We propose to avoid language barrier limitations by using a process that is based on probability distributions and automatic algorithms, and that is not dependent on language-specific methodologies that limit its application in other environments. To do this, we propose to use a supervised machine learning methodology to be trained on the emotional classification of a sample online review texts and use it not only to classify other texts further but to analyze the weight towards classification that certain keywords hold in that trained machine. Furthermore, we also analyze the relevance of these keywords in different hotel price brackets to observe potential differences.

\section{Related work}\label{relatedwork}

In the hospitality field, satisfaction, motivation, and behavior have been studied for a long time using surveys \cite[e.g.][]{truong2009, wu2009, shanka2004, kozak2002, romao2014, dongyang2015, chan201518}. More recently, studies have used big data in the hospitality industry \cite[e.g.][]{yang2014, loh2003}, as well as data mining tools to analyze hotel reviews \cite[e.g.][]{alsmadi2018, browning2013, xiang2010}. However, most of these studies focus on either the sentiment classification without analyzing the relevant words tied to those sentiments, or they study the most relevant words without taking the emotions they largely represent into account. Other studies focus on review helpfulness \cite[][]{ren2019}; while others focus on summarization of reviews into smaller text \cite[e.g.][]{hu2017436, amplayo201754}. There has not been yet a study that focuses on the conceptual words that are tied with the satisfaction or dissatisfaction of the userbase. For example, one study used a tool called “Word Cloud” to extract frequently used words inside the reviews which were considered important topics of concern to consumers \cite[][]{hargreaves2015}. However, the sentiment analysis is done at a hotel level, instead of a word level, so it is difficult to determine which topics are perceived positively or negatively. Another study used a heuristic frequency analysis to determine guest experience topics \cite[][]{xiang2015}. However, this study doesn't deterministically show which topics are directly tied with satisfaction and dissatisfaction or the ranking order in which they do.

On the other hand, \cite{zhang2011} performed a market analysis based on the sentiment analysis of product reviews using a Chinese sentiment dictionary called HowNet. The problem with using HowNet as a sentiment dictionary is that the words are classified based on ontology \cite[][]{huang2008}, where emotional words are usually those that describe emotions, such as “angry”, “anger”, “happiness”, “content”. While these words represent the emotions themselves, in an online review, it is unlikely that the general population writes their emotions explicitly; instead, it is more likely that words that do not describe the emotion but are intrinsically emotionally fueled are used. For example, one would not write “I am happy with the size of the room and the service”; instead what would be natural is “The room had lots of space for our luggage and the staff was friendly”. HowNet is not able to determine that “space” is tied to positive emotions and that “staff” is being praised by the use of “friendly” in the sentence. These non-emotional words are directly representing the emotion of satisfaction or dissatisfaction in the online review. Now, in turn, this study methodology focuses on the influence of each word and their rank of importance in relation to the satisfaction or dissatisfaction expressed by the user, clearly defining not only their emotion but also the specific needs of Chinese customers in a concrete way.

There have been previous attempts at understanding the factors leading to satisfaction and dissatisfaction with text and data mining techniques as well. One study used a text-link analysis to understand which pairs of words were used more in positive or negative reviews \cite[][]{berezina2016}. However, the conclusions of this study are limited to their sample of manually classified 20 reviews, so it is difficult to extrapolate it to a larger population of reviews. Another study manually extracted factors that could lead to satisfaction or dissatisfaction from a sample and then continued to study the statistical differences between them in that sample \cite[][]{zhou2014}. However, this is limited to their manually defined factors and that there are no further analyses to a larger number of online reviews because of language barriers. Another study used heuristic language-specific parsing algorithms to determine the frequency of words in a previously classified corpus \cite[][]{xu2016}. The problem with this last method is that it is depending on the specific corpus of reviews classified as negative or positive from the moment they're input into the site into different input forms from \textit{Booking.com} and that it is strictly only applicable to English texts. Our methodology not only applies the findings of the sampling to the full corpus, but it does in a way that overcomes the difficulties of language barriers and sentiment classification.

\section{Methodology}\label{method}

We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}}, as well as the travel site \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}} and determined the most commonly used words that would contribute the most to satisfaction and dissatisfaction opinions in a review using an entropy-based mathematical extraction method. These keywords extracted using entropy related to satisfaction or dissatisfaction not only allow us to perform a Support Vector Machine based emotional classification of the reviews but conceptual words in these lists bring insight into which concrete topics are the Chinese tourists concerned with. After classifying the sentences in the extracted reviews as signaling satisfaction and dissatisfaction with an optimized SVM, we have analyzed the weight value assigned to them by the SVM applying the methodology in previous research. We also observed the frequency of the terms in all of the reviews to extract the most utilized words in either kind of reviews. We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}. Furthermore, we have also performed analyses for different price brackets to observe the change in demand for different kinds of hotels varying in luxury in the Chinese reviews.

\begin{figure}[bp]
\centering
\includegraphics[width=\textwidth]{method-overview.png}
\caption{Overview of the methodology.}
\label{fig:method-overview}
\end{figure}

\subsection{Data collection}\label{datacollection}

In this study we used the HTML parsing python library \textit{BeautifulSoup}\footnote{\label{bs4}Beautiful Soup: \href {https://www.crummy.com/software/BeautifulSoup/}{\path{https://www.crummy.com/software/BeautifulSoup/}}}, and the local database management tool \textit{SQLite}\footnote{\label{sqlite}SQLite: A local database management system with an SQL structure: \href {https://www.sqlite.org/}{\path{https://www.sqlite.org/}}} using the python library \textit{sqlite3} to automatize data managing processes.

\subsection{Data processing}\label{dataprocessing}

\subsubsection{Text processing}\label{textprocessing}

Different from the English language, Chinese texts lack a separation between different words, and as such, when collecting these texts, they are all a single string of characters. To be able to perform a statistical analysis of each word, the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University} was implemented for this task using the python \textit{nltk} library. During the segmentation of all the words in our corpus, irregularities occurred where the reviews were written in other languages or where unusual punctuation marks were used. We designated a list of characters that could be recognized as noise, such as punctuation marks, then cleared all the text in the corpus of these characters.

In the case of texts in English, however, only using spaces is not enough to correctly collect concepts. Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word. For this purpose, we used the \textit{gensim} library with the English texts.

\subsubsection{Sentiment analysis}\label{sentimentanalysis}

\myparagraph{Entropy based keyword extraction}\label{entropy}

In order to determine the words that clearly represent the user’s satisfaction or dissatisfaction, we calculated the entropy value of each word in relation to each class. Shannon’s Entropy, in the field of Information Theory, is defined to be the expected value of the information content in a signal \cite[][]{shannon1948} or it can be thought of as the grade of impossibility of predicting an outcome. It is shown in formulas \ref{eq:H} and \ref{eq:lim_H}. Using this value we can observe the probability distribution of each word inside the corpus. A word that is included in many documents, it will have a high entropy value for that set of documents, since it becomes uncertain to predict in which document it will appear. Opposite to this, a word appearing in only one document will have an entropy value of zero, since it is completely predictable. We show this concept in Figure \ref{fig:entropygraphs}.

\begin{equation}\label{eq:H}
H = - \sum_{i=1}^M [P \log_2 P]
\end{equation}

\begin{equation}\label{eq:lim_H}
\lim_{P\to0+} P \log_2 P = 0
\end{equation}

\begin{figure}[bp]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\linewidth]{entropyzero.png}
        \caption{Entropy close to zero.}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\linewidth]{entropyhigh.png}
        \caption{High entropy}
    \end{subfigure}
\caption{Probabilities of a word j being contained in a document i.}
\label{fig:entropygraphs}
\end{figure}

To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, tagged each sentence of a total of 159 as the classes satisfied or dissatisfied depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class. In the case of English reviews, we sampled 665 reviews and with the collaboration of English speaking students manually tagged them by sentence, resulting in 2357 tagged sentences. Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels. This is shown in formula \ref{eq:entropy_pos}. Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts. This is shown in formula \ref{eq:entropy_neg}.

\begin{equation}\label{eq:entropy_pos}
H_{P} > \alpha H_{N} % \rightarrow satisfaction \: keyword
\end{equation}

\begin{equation}\label{eq:entropy_neg}
H_{N} > \alpha' H_{P} % \rightarrow dissatisfaction \: keyword
\end{equation}

\myparagraph{Support Vector Machine classification}\label{svm}

Support Vector Machines are supervised machine learning models usually applied to classification or regression problems \cite[][]{cortes1995}. We use it to classify the rest of our corpus into emotional classes in this study. An SVM is trained to classify data based on previously labeled data, generalizing features of the data by defining a separating (p-1)-dimensional hyperplane in a p-dimensional space in which each dimension is a feature of the data. The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimize the error of classification. We show a two dimensional example in Figure \ref{fig:svm2d}.

\begin{figure}[bp]
\centering
\includegraphics[width=20em]{SVM_2d_example.png}
\caption{Two dimensional example of an SVM classification problem.}
\label{fig:svm2d}
\end{figure}

In this study, we used the SVM classification process described in \cite[][]{Aleman2018ICAROB} with a number of keyword lists, defined by our entropy calculations with different comparison coefficients, as the possible features; trained the SVMs and tested for each one using a K-fold Cross-Validation method \cite[][]{kohavi1995}. In each test we calculated the Precision, Recall and \(F_1\)-measure \cite[][]{powers2011} for our predictions.

\myparagraph{Model evaluation metrics}
\label{model_evaluation}

In order to measure the effectiveness of the training process and data, we performed what is called K-fold cross-validation. This means that after randomly shuffling and splitting the training data into k equal parts, k-1 of those parts are used for training, while the remaining one part is used in validation. Using the trained models, a prediction is made, and it is decided if such a prediction is correct or not, and counted and grouped as a True Positive, True Negative, False Positive or False Negative prediction. This is explained in Table \ref{tab:preds}.

\begin{table}[bp] \centering
\caption{Prediction outcomes.}\label{tab:preds}
\begin{tabular}{c|c|c|}
\cline{2-3}
\textbf{} & \textbf{Prediction is Correct} & \textbf{Prediction is Incorrect} \\ \hline
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Prediction\\  is Positive\end{tabular}}} & True Positive & False Positive \\ \hline
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Prediction \\ is Negative\end{tabular}}} & True Negative & False Negative \\ \hline
\end{tabular}
\end{table}

Measures of accuracy are determined from these prediction outcomes. This process is then repeated \(k\) times and the measures taken are averaged. In this study, we used the \(F_{1}\) score, which measure is a harmonic mean between precision and recall. Precision, described in formula (\ref{eq:precision}), lets us observe the rate of correct positive predictions from all the positive predictions, while Recall, detailed in formula (\ref{eq:recall}), observes the rate of correct positive predictions from the total of actual positive data. The \(F_{1}\) score in formula (\ref{eq:f1}) then can only be high when both of these measures are high simultaneously and will lower substantially if they are not consistent. We use this score as it allows us to avoid overlooking data while maintaining accurate predictions. The overall accuracy (\ref{eq:accuracy}), which doesn't account for overlooking of data, is also observed for reference but isn't used as the main evaluation of the model.

\begin{equation}\label{eq:precision}
Precision = \frac{True \: Positives}{True \: Positives + False \: Positives}
\end{equation}

\begin{equation}\label{eq:recall}
Recall = \frac{True \: Positives}{True \: Positives + False \: Negatives}
\end{equation}

\begin{equation}\label{eq:f1}
F_{1} = 2  \frac{Precision * Recall}{Precision + Recall}
\end{equation}

\begin{equation}\label{eq:accuracy}
Accuracy = \frac{True \: Positives + True \: Negatives}{Number \: Of \: Predictions}
\end{equation}

\subsubsection{Data analysis}\label{dataanalysis}

\myparagraph{SVM weight analysis}\label{svmweightsanalysis}

During the SVC learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly. These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those contained in the support vectors, close to the separating hyperplane. Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process. Because the weight vector gives value to the words that comprise the support vectors, the words with higher weights are thought to be closer to the dividing hyperplane, while still clearly and decisively belonging to one of the categories the hyperplane divides the high-dimensional space in. While other less ambiguously used words could be excluded from this weight assigning process, the words that are assigned weight values are thought to be words that while discussed in both emotional states, they are more strongly discussed in one of these emotional states. If anything, these are highly volatile words relating to the experience of the customers in the hotel, which are important to consider as a hotel business to improve customer satisfaction. Below we show the formula for the weight vector (\ref{eq:svm_weight}).

\begin{equation}\label{eq:svm_weight}
w = \sum_{i=1}^N \alpha_i y_i x_i
\end{equation}

\myparagraph{Keyword frequency analysis}\label{keywordfrequencyanalysis}

Because the machine learning model used in this study is constructed from training data obtained by a relatively small sample of our data, after training the model and classifying the rest of the data, we studied the frequencies of each entropy based keyword in our complete data set. Words signifying a subject or topic that are relatively highly used will have more meaning when analyzing the emotional response of the user-base of Chinese tourists in Japan.

\section{Results}\label{results}

\subsection{Data set}\label{dataset}

In the data collection stage, a total of \num[group-separator={,}]{1541424} HTML files were crawled, from which 5,938 were unique review pages of hotels in Japan. From these pages, we extracted a total of \num[group-separator={,}]{44912} reviews, which were comprised of 286,109 separate sentences. In our corpus, there were \num[group-separator={,}]{23443} different words used, from which \num[group-separator={,}]{2802} were noise characters.

\subsection{Sentiment analysis results}\label{sentimentresults}

After having the training data tagged by a group of 5 Chinese student collaborators, we experimented with different comparison coefficients for the entropy values calculated from the satisfaction and dissatisfaction emotional classes. The mutually independent coefficients \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. The result was 40 lists, 20 for each emotional class. We repeated the process for the reviews in English that our colleagues tagged.

In the beginning, we experimented with different kernels for the SVM, as well as some Ensemble Learning methods, like the Boosting, Voting and Stacking. We ultimately decided to use the linear kernel for the benefits of the weight vector obtainability. We also experimented with different parameters for the SVC, finding that the best performing value for C, a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives, but depending on the data it can increase false negatives. Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives. We found the ideal value for this parameter was C=0.5 in our final classifier for Chinese text, and 2 in the English text one.

We trained a different Support Vector Classifier with each of the lists, and we chose the best performing lists for each emotional class, resulting in a satisfaction emotion classifier (satisfied or not) and a dissatisfaction emotion classifier (dissatisfied or not), based on the results of a 5-fold cross-validation process in the Chinese reviews, and a 10-fold cross-validation process in the English reviews case, in which we calculated their accuracy and F-measure means and standard deviations. The number of \(k\)-folds was decided from the sample size. Since the sample for the Chinese texts was smaller, the number of validation data would be reduced if a higher value for \(k\) was used. After observing the misclassification behavior for the satisfaction emotion classifier, which mostly misclassified sentences with negative words, we decided to combine both keyword lists into a single large list to train the satisfaction emotion classifier. With this Combined list, the accuracy was of \(0.92 \pm 0.03\) and \(F_1 = 0.95 \pm 0.01\), both excellent results for classification. Table \ref{tab:svm_f1_zh} shows the lists that had the best performance results in the case of Chinese text and Table \ref{tab:svm_f1_en} shows the best performance results in English texts.

\begin{table}[bp] \centering
\caption{Results of the best 5-fold cross-validation Chinese text classification performance tests.}\label{tab:svm_f1_zh}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}Accuracy \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Accuracy\\  \(\sigma\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.87 & 0.02 & 0.91 & 0.01 \\ \hline
\begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.85 & 0.05 & 0.67 & 0.11 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.92} & \textbf{0.03} & \textbf{0.95} & \textbf{0.01} \\ \hline
\end{tabular}%
}
\end{table}

\begin{table}[bp] \centering
\caption{Results of the best 10-fold cross-validation English text classification performance tests.}\label{tab:svm_f1_en}
\resizebox{\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}Accuracy \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Accuracy\\  \(\sigma\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.79 & 0.02 & 0.82 & 0.02 \\ \hline
\begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.70 & 0.04 & 0.80 & 0.03 \\ \hline
\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.81} & \textbf{0.02} & \textbf{0.83} & \textbf{0.02} \\ \hline
\end{tabular}%
}
\end{table}

Using both sets of keywords in the same SVC (named ‘Combined’) to classify the testing data, we obtained higher performance results overall. We then used these classifiers in the rest of the respective data to label positive emotion sentences. The sentences not belonging to the positive emotion class were considered to belong in the negative emotion class since the classification of the emotion of each sentence was binary in our training samples original classification.

\subsection{Keywords and their SVM weight values}\label{svmresults}

In Table \ref{tab:key_weights_zh} we show some of our keywords that signify subjects or topics, and as such, help us understand the needs of the users. We show keywords that have a relatively high weight value for both positive and negative extremes, and their translations in the relevant context. In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values.

\begin{table}[bp] \centering
\caption{High weight values for Chinese keywords signifying subjects or topics.}
\label{tab:key_weights_zh}
\begin{tabular}{|>{\centering\arraybackslash}m{3em}|m{10em}|>{\centering\arraybackslash}m{7em}|>{\centering\arraybackslash}m{5em}|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Entropy List} & \textbf{SVC Weight} \\ \hline
\begin{CJK}{UTF8}{gbsn} 地方 \end{CJK} 
    & region, local 
        & Satisfaction 
        & 1.343 \\ \hline
\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
    & clean 
        & Satisfaction 
        & 0.638 \\ \hline
\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
    & big, wide 
        & Satisfaction 
        & 0.624 \\ \hline
\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK} 
    & traffic, transportation 
        & Satisfaction 
        & 0.586 \\ \hline
\begin{CJK}{UTF8}{gbsn} 热情 \end{CJK} 
    & cordial, kindness 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 周边 \end{CJK} 
    & periphery 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 景色 \end{CJK} 
    & scenery 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
    & recommendation 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 日本 \end{CJK} 
    & Japan 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
    & breakfast 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 附近 \end{CJK} 
    & nearby 
        & Satisfaction 
        & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
    & Chinese text 
        & Dissatisfaction 
        & -0.714 \\ \hline
\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
    & geography 
        & Dissatisfaction 
        & -0.812 \\ \hline
\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
    & price 
        & Dissatisfaction 
        & -1.505 \\ \hline
\end{tabular}
\end{table}

\begin{table}[bp]
\centering
\caption{High weight values for English keywords signifying subjects or topics.}
\label{tab:key_weights_en}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Entropy\\ List\end{tabular}}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} \\ \hline
bathhouse & Satisfaction & 2.000 \\ \hline
museum & Satisfaction & 2.000 \\ \hline
meeting & Satisfaction & 1.997 \\ \hline
subway & Satisfaction & 1.951 \\ \hline
cozy & Satisfaction & 2.000 \\ \hline
convenience & Satisfaction & 1.888 \\ \hline
clean & Satisfaction & 1.886 \\ \hline
comfortable & Satisfaction & 1.724 \\ \hline
dirty & Dissatisfaction & -1.275 \\ \hline
policy & Dissatisfaction & -1.463 \\ \hline
prepay & Dissatisfaction & -1.517 \\ \hline
pricey & Dissatisfaction & -1.614 \\ \hline
sticky & Dissatisfaction & -2.000 \\ \hline
\end{tabular}
\end{table}

\subsection{Keyword frequencies}\label{freqresults}

We observed the words with the highest frequencies for keywords in satisfied and dissatisfied statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh}; and for English speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.

\begin{table}[bp] \centering
\caption{High weight Chinese keywords in satisfaction sentences.}
\label{tab:pos_keys_zh}
\begin{tabular}{|c|l|c|c|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
    & big 
        & 15470 & 0.624 \\ \hline
\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
    & clean 
        & 12166 & 0.638 \\ \hline
\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
    & breakfast 
        & 10575 & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
    & recommendation 
        & 8752 & 0.495 \\ \hline
\begin{CJK}{UTF8}{gbsn} 环境 \end{CJK} 
    & \begin{tabular}[c]{@{}l@{}}
    environment, \\ surroundings 
    \end{tabular} 
        & 8694 & 0.248 \\ \hline
\end{tabular}
\end{table}

\begin{table}[bp] \centering
\caption{High negative weight Chinese keywords in dissatisfaction sentences.}
\label{tab:neg_keys_zh}
\begin{tabular}{|c|l|c|c|} \hline
\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
    & price & 7636 & -1.505 \\ \hline
\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
    & geography & 2238 & -0.812 \\ \hline
\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
    & Chinese language & 1410 & -0.714 \\ \hline
\end{tabular}
\end{table}

\begin{table}[bp]
\centering
\caption{High weight English keywords in satisfaction sentences.}
\label{tab:pos_keys_en}
\begin{threeparttable}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
staff & 138677 & 0.537 \\ \hline
clean & 105971 & 1.886 \\ \hline
location & 103151 & 0.842 \\ \hline
comfortable & 62793 & 1.724 \\ \hline
subway & 38354 & 1.951 \\ \hline
airport & 36328 & 0.839 \\ \hline
shopping & 34355 & 1.308 \\ \hline
onsen \tnote{*} & 31084 & 0.094 \\ \hline
\end{tabular}
\begin{tablenotes}
\item[*]Onsen are Japanese hot springs
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[bp]
\centering
\caption{High negative weight English keywords in dissatisfaction sentences.}
\label{tab:neg_keys_en}
\begin{tabular}{|l|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
pricey & 3809 & -1.614 \\ \hline
carpet & 3683 & -0.507 \\ \hline
dirty & 2943 & -1.275 \\ \hline
stain & 2787 & -1.886 \\ \hline
cigarette & 2468 & -0.435 \\ \hline
\end{tabular}
\end{table}

In order to further analyze the data we obtained, aside from emotional classification, we also investigated the difference in emotional response from customers of hotels in different price brackets in the case of Chinese reviews. We separated hotel prices in 6 categories, and in Table \ref{tab:keys_prices} we show the words that have an interesting change in their ranking order when ordered by frequency in each price bracket. We include the price bracket definitions in \ref{appendix:price_ranges} in Table \ref{tab:price_ranges}.

\begin{table}[bp] \centering
\caption{Words that change in importance between price brackets in positive sentences.}
\label{tab:keys_prices}
\begin{tabular}{|>{\centering\arraybackslash}m{2.5em}|m{6em}|m{16em}|} \hline
\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{Translation}} & \multicolumn{1}{c|}{\textbf{Observation}} \\ \hline
\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK}
    & \begin{tabular}[c]{@{}l@{}}traffic,\\ transportation \end{tabular} 
        & Higher ranking for hotels with lower prices, while not as high in luxury hotels. \\ \hline
\begin{CJK}{UTF8}{gbsn} 环境 \end{CJK} 
    & \begin{tabular}[c]{@{}l@{}}environment,\\ surroundings \end{tabular} 
        & Higher ranking for luxury hotels and in the lowest priced hotels, but not as high in the middle price brackets. \\ \hline
\begin{CJK}{UTF8}{gbsn} 日式 \end{CJK} 
    & japanese-style 
        & Only high ranking in luxury hotels. \\ \hline
\begin{CJK}{UTF8}{gbsn} 人员 \end{CJK} 
    & \begin{tabular}[c]{@{}l@{}}staff,\\ personnel \end{tabular} 
        & Rises in ranking as the hotel price rises. \\ \hline
\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
    & recommend 
        & Included in all hotels, but higher ranking in lower priced hotels. \\ \hline
\end{tabular}
\end{table}

\section{Discussion}\label{discussion}

\subsection{Needs of the Chinese tourist market in Japan}\label{discussionneeds}

Analyzing the results from the extracted keywords is the key to understanding Chinese and English speaking customers of Japanese hotels since they can be interpreted as rankings of their explicit needs and demands. Analyzing satisfaction keywords, we found that the most relevant subjects Chinese customers perceive positively are cleanliness and size, very possibly of the room they had stayed in. There is also the possibility that reviewers were praising, in general, the cleanliness of Japan’s environment, un-littered streets, potable water and their culture of respecting spaces. Our results are compatible with \cite{ryan2001} in their study of Chinese tourist behavior in New Zealand , where Chinese travelers were found to prefer traveling and exploring unfamiliar places that have a reputation for being clean and unpolluted environments, focusing on scenic beauty, history and culture. They also found complaints about the lack of Chinese language availability in the services they consumed. \cite{LIU2019337} describe that the behavior studied in Australia reflected that Chinese tourists were more likely to appreciate touristic places for the scenery, architecture, landmarks, and popular spots, rather than appreciate cultural experiences or activities. Similar to the findings in Liu et al., our results indicate that closeness of the hotel to scenic places is highly tied to satisfaction. However, their research is on online reviews of touristic places, instead of hotels. With this difference, our results showed that breakfast inclusion and the size and cleanliness of rooms were also tied to satisfaction, aside from scenery. According to our data, other positive factors that come into play when Chinese tourists choose a hotel to stay is the location in relation to public transport availability; and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping. \cite{gao2017chinese} argue that Chinese people are heavily influenced by religion and a culture that regards harmony and oneness with nature and humans, which in turn influences their tourism behavior. However, they also argue that there are generational differences and that the older generations that lived through the changes that changed the environment and caused pollution care more about the environment, and as such appreciate natural and scenic touristic spots more than younger generations.

One key component we found in Chinese customer satisfaction is the inclusion of breakfast within the hotel. This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive. While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking. In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words. This specific keyword is previously unmentioned in studies regarding the eating behavior of Chinese tourists. While these studies on eating behavior are very scarce, both a study on the food preferences of Chinese tourists in Australia \cite[][]{chang2010} and an article on Chinese food culture \cite[][]{ma2015} state that even in foreign countries, Chinese people have a habit to eat Chinese food, probably because of a need for familiarity. However, the analysis of our data points to the fact that more than Chinese food as a specific concept, hotel reviews are written with general words that represent food. We would like to further study specific Chinese tourists food preferences, such as the contents of said breakfast and other meals in future work to observe the level of necessity of these particular needs.

Now, when analyzing dissatisfied responses, the most frequently criticized aspect of Japanese hotels was the price. This was true across all of the price brackets, from the cheapest hotels to the most luxurious ones. In their study of Chinese tourists in Vietnam, \cite{truong2009} also found both the tendency to be concerned with value for money. It is possible that concerns over value for money are a general cultural trait in the Chinese population. Applying this previous finding to our data, negativity about the pricing of hotels across all price brackets can mean they believe the price is too high for the service that they receive, regardless of their satisfaction or dissatisfaction with the service. Our results suggest that Chinese customers are expecting lower prices for whatever services they receive.

Another important negative factor can be the availability or lack thereof of Chinese translations. Chinese customers can feel lost when they don't understand directions or instructions, either written or spoken; however, according to our data, most customers can be thought to have complained about written translations.

Additionally, as shown in Table \ref{tab:keys_prices}, there is a positive reaction to “Japanese-style”, which we infer in this context can mean rooms or possibly ceremonies, in luxury rate hotels. Another interesting point is that the expectation for hotel staff increases as the price of the hotel rises. Furthermore, while “recommendation” of a hotel can be seen across all price brackets, customers searching for low priced hotels are relatively more inclined to recommend that hotel to others, based on a comparison of frequency ranking of each word for each price bracket.

\subsection{Comparison with English speaking tourists in Japan}

The results with the English speaking population are similar to the results with the Chinese speaking population, but there are some noteworthy differences that can be explored. For example, while Chinese customers seem to focus positively on the cleanliness of the room first and foremost, English speaking customers seem to consider the behavior of the staff before it. However, when we consider the negative associations, the price is the first concern for both kinds of customers, but there's a high concern for cleanliness in a negative connotation, such as complaints about stains, dirty rooms or carpets. A thing to note is that there is a high number of complaints about cigarette smell, in comparison to the Chinese customers in which it isn't a keyword within our extraction methods. Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.

In previous research, it has been found that Chinese tourists are harsher in their negative touristic attraction reviews than other nationalities \cite[][]{LIU2019337}. Taking this into account, and the large difference in frequency between complaints about price and other elements, Chinese customers can be said to be dissatisfied with price in a disproportionate way. English speaking tourists' dissatisfaction factors, on the other hand, have less of a gap in frequency, and as such can be said to be more concerned about cleanliness related factors than price.

On the positive reviews side, there is a high number of mentions for nearby transportation methods, such as the subway, or access from the airport. This is also different when compared to Chinese customers, who don't mention transportation services as frequently for viewing a hotel in a positive way. Another difference that is noteworthy is that Chinese customers appreciate included breakfast in hotels, but for the English speaking customers it seems to not be a priority.

\section{Conclusions and future work}\label{conclusions}

In this study, with the purpose to understand emotional responses of Chinese customers of Japanese hotels and understand their needs, we extracted keywords from their reviews from the Chinese portal site \textit{Ctrip} using entropy calculations from a manually classified sample of our data; then we used these keywords in machine learning experiments. Using the keywords to train a linear kernel Support Vector Classifier, we obtained the highest performance \((F=0.95\pm0.01\) and \(Accuracy = 0.92\pm0.03)\) using both our positive and negative keywords for a binary emotional classifier.

Using the weight vectors of our classifiers, as well as frequency of the words in our dataset, we found that Chinese customers have a preference for big and clean rooms, big thermal baths or bathhouses, expect good value for money regardless of price, that there is a lack of Chinese text translation and that they prefer hotels where breakfast is included. We also found that the friendliness of the staff increases in priority as the price and luxury of the hotel increases and that transportation is more important for customers looking for cheaper options compared to the more luxurious ones.

For comparison, we also repeated the experiments on reviews written by English speaker tourists staying at Japanese hotels from \textit{TripAdvisor}. Observing the results we identified that English speaking customers hold a bigger contempt and negative reactions for dirty or stained rooms, but that the main concern is also the pricing of the hotels. We also found that they prefer friendly staff and transportation available from the airport or subway.

Our results show the needs of a large and increasing segment of the customers. This would have otherwise presented difficulties with traditional methods because of language and culture barriers. The hotel industry can make use of these results to better the response from Chinese customers by focusing on improving topics they find important, such as cleanliness, the inclusion of breakfast, availability of Chinese translations in text format and so on. By doing this, satisfied users will write new reviews and thus influence future customers positively.

In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or for work. Another point for the future of this study is to use word clusters with similar meanings instead of single words. As mentioned before, we would also study the food preferences of Chinese tourists, as well as the impact of the recommendation in different price brackets. Additionally, it would be interesting to study further into more specific emotions than the satisfaction and dissatisfaction classifications we performed in our study.

\section*{Acknowledgements}

During our research, apart from the group of Chinese students that collaborated with the training data and emotion tagging process, we received the commentary and discussion necessary to understand certain
cultural aspects that could influence the interpretation of the data, from empirical and anecdotal Chinese sources, as well as collaboration in understanding the meaning behind the words we extracted by our dear colleagues, whom we would like to show gratitude to, Mr. Zhou Liangyuan, Ms. Eerdengqiqige, and Mr. Hugo Alberto Mendoza España.

\medskip

Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).

\medskip

Declarations of interest: none

\clearpage
\section*{References}

\bibliography{mybibfile}

\clearpage

\appendixpage
\appendix

\section{Price bracket analysis details}\label{appendix:price_ranges}

In the Keyword Frequency Analysis in section \ref{freqresults} and Table \ref{tab:keys_prices}, we examined the frequency of certain keywords across different price brackets. We show these ranges in Table \ref{tab:price_ranges}. These price brackets were selected by observing different kinds of hotels and their level of luxury, along with their price. Hostels and capsule hotels depending on their location are often in the first two price brackets. Business hotels can range from the third to fourth, while more luxurious hotels are included in the fifth and sixth ranges. The price data was mined as the average price per night in a hotel using the data available in \textit{Ctrip}, and not for each review as it might vary by the number of nights and the kind of room chosen.

\begin{table}[hbp] \centering
\caption{Price per night ranges used for analysis.}\label{tab:price_ranges}
\begin{tabular}{|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Price bracket Number}} & \multicolumn{1}{c|}{\textbf{Price bracket in japanese yen}} \\ \hline
Price Bracket 1 & 0 yen to 5000 yen \\ \hline
Price Bracket 2 & 5000 yen to 10,000 yen \\ \hline
Price Bracket 3 & 10,000 yen to 15,000 yen \\ \hline
Price Bracket 4 & 15,000 yen to 20,000 yen \\ \hline
Price Bracket 5 & 20,000 yen to 100,000 yen \\ \hline
Price Bracket 6 & 100,000 yen to 500,000 yen \\ \hline
\end{tabular}
\end{table}

\end{document}

### 2020-09-27 2_revisions/V0_Before submission/V0_2.5_After first revision by Ola-but better/tmp-emotion_V0_2.5.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V1_Submit version/itt-emotion-manuscript_V1.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-
-% For the ORCID icon
-\usepackage{scalerel}
-\usepackage{tikz}
-\usetikzlibrary{svg.path}
-
-\definecolor{orcidlogocol}{HTML}{A6CE39}
-\tikzset{
-  orcidlogo/.pic={
-    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-  }
-}
-
-\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-\begin{tikzpicture}[yscale=-1,transform shape]
-\pic{orcidlogo};
-\end{tikzpicture}
-}{|}}}}
+\documentclass[review]{elsarticle}
 
@@
 \usepackage{graphicx}
-
-% To use chinese characters
+\usepackage{subcaption}
 \usepackage{CJKutf8}
-
-% To add an appendix page
 \usepackage[page, title]{appendix}
-
-% Stick footnotes to bottom of the page
+% \usepackage{tablefootnote}
+\usepackage{threeparttable}
+\usepackage{etoolbox}
+\appto\TPTnoteSettings{\footnotesize}
 \usepackage[bottom]{footmisc}
-
-% To insert commas into large numbers automatically
 \usepackage{siunitx}
-
-% To add hypothesis theorem
 \usepackage{ntheorem}
@@
 
-% To add the envelope symbol in Corresponding Author using % \Letter
-\usepackage{marvosym}
-
-% to add superscripts to mark the institute of authors
-% patch \maketitle:
-\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-% For table formatting
 \usepackage{multirow}
@@
 
+%to have numbered 4th level sections 1.1.1.1
+\setcounter{tocdepth}{4}
+\setcounter{secnumdepth}{4}
+
+% to remove period in 4th level sections 1.1.1.1
+\makeatletter
+\def\els@aparagraph[#1]#2{\elsparagraph[#1]{#2}}
+\def\els@bparagraph#1{\elsparagraph*{#1}}
+\makeatother
+% to enter a newline after 4th level sections
+\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\smallskip}
+
 \modulolinenumbers[5]
 
-\journalname{Information Technology \& Tourism}
-
-\bibliographystyle{spbasic}
+\journal{Tourism Management}
+
+%% APA style
+\bibliographystyle{model5-names}\biboptions{authoryear}
 
@@
 
-\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}
-
-\titlerunning{Analyzing differences in satisfaction and dissatisfaction between Chinese and ...}
-
-\author{REDACTED
+\begin{frontmatter}
+
+\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with text-mining}
+
+%% or include affiliations in footnotes:
+\author[gidai]{Elisa Claire Alemán Carreón
+\corref{mycorrespondingauthor}}
+\ead{elisa.claire.aleman.carreon@gmail.com}
+% \orcid{0000-0002-6437-0866}
+
+\author[gidai]{Hugo Alberto Mendoza Espa\~na}
+\ead{s173330@stn.nagaokaut.ac.jp}
+
+\author[gidai]{Hirofumi Nonaka}
+\ead{nonaka@kjs.nagaokaut.ac.jp}
+
+\author[nagasaki]{Toru Hiraoka}
+\ead{hiraoka@sun.ac.jp}
+
+\address[gidai]{Nagaoka University of Technology, Nagaoka, Japan}
+\address[nagasaki]{University of Nagasaki, Nagasaki, Japan}
+
+\cortext[mycorrespondingauthor]{
+Corresponding author%: \\
+% Elisa Claire Alemán Carreón \\
+% Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
+% Cell Phone: 080-9869-4756 \\
 }
 
-\authorrunning{REDACTED}
-
-\institute{REDACTED
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
 \begin{abstract}
@@
 Up until recently, most studies in tourist behavior have been biased for the Western world.
-With the increase of Chinese outbound tourists to other countries, academic interest for this group has risen.
-Increasing variation amongst clients means that managing hotels in a way that caters to their different tastes becomes more important.
-Despite this, cross-cultural studies of differences between Asian and Western cultures are scarce and predate the current boom in the Chinese economy.
+With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen.
+However, cross-cultural studies of their differences with other cultures are scarce and predate the current boom in the Chinese economy.
 This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels.
-Taking advantage of Web 2.0, we can apply Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples of online reviews without interfering with the decision process of customers.
-This means that we can measure how important are certain attributes of the hotel to customers, and whether those are managerial or environmental for the hotel.
-In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which is used for top-weighted ranked lists with different elements and lengths.
-We found that Chinese customers prefer big and clean spaces, and that Western customers are satisfied with friendly staff members.
-We also found that Chinese tourists are unsatisfied with lack of a Chinese friendly environment, and that Western customers are unsatisfied with dirty rooms, or the smell of cigarette.
-
-% \medskip
-% \noindent\it{Highlights}
-% \begin{itemize}
-%     \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
-%     \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
-%     \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
-%     \item Both customer groups have concerns about the pricing of hotels (value for money).
-%     \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
-% \end{itemize}
-
-\keywords{Sentiment Analysis\and Hotels and Lodging\and Machine Learning\and Chinese\and English\and Preferences}
+Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel.
+With the spread of the use of Web 2.0 to write online reviews of hotels, a large amount of text data is available for research purposes.
+With text mining, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers.
+This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel.
+In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which can be used for top-weighted ranked lists with different elements and lengths.
+We found that Chinese customers prefer big and clean spaces and that Western customers are satisfied with friendly staff members.
+We also found that Chinese tourists are unsatisfied with the hotel being Chinese friendly with treatment and language and that Western customers are unsatisfied with rooms that they consider dirty, or that smell of cigarette.
+
+\medskip
+\noindent\it{Highlights}
+\begin{itemize}
+    \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
+    \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
+    \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
+    \item Both customer groups have concerns about the pricing of hotels (value for money).
+    \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
+\end{itemize}
 
@@
 
+\begin{keyword}
+Sentiment Analysis\sep Hotels and Lodging\sep Machine Learning\sep Chinese\sep English\sep Preferences
+\end{keyword}
+
+\end{frontmatter}
+
 \linenumbers
@@
 
-In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
+Recently, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
+From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China.
 Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
 Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.
-With these and other multicultural tourists populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Hotel management therefore needs to cater to these different needs and expectations to increase their customers' satisfaction, maintain a good reputation, and, therefore, generate positive word-of-mouth.
-
-However, recent studies on social sciences, which includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations.
+
+However, up until recently studies on social sciences, and that includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
+Those that do include Asian populations in their analysis, most commonly Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations.
 This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
+It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as "long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
 It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
@@
 Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
+Data mining and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
 This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
@@
 We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure.
-Furthermore, we will measure if both customer groups have differences in priorities for the factors that are common to both groups.
-In addition, we also measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes (internal to the hotel), as well as environmental attributes (external to the hotel).
-
-Furthermore, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
+Furthermore, we aim to measure if both customer groups have differences in priorities for the factors that are common to both groups.
+Furthermore, we aim to measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.
+
+Aside from this, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
 In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose; this means that cultural and language differences often cannot be observed in a single study.
@@
 \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} state that satisfaction and dissatisfaction are therefore influenced by each customer's background.
+It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} states that satisfaction and dissatisfaction are therefore influenced by each customer's background.
 This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures.
@@
 \label{hyp:1}
-Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
+Chinese and Western tourists have different satisfaction and dissatisfaction factors.
 \end{hyp}
@@
 However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that solely correlate to satisfaction, as well as exploring factors which are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
+There are fewer examples of this approach, but studies have also done this in the past \cite[e.g.][]{zhou2014}.
 While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
@@
 Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e.
-hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}, without focusing on factors that are uncontrollable by the hotel staff, such as surroundings, location, language immersion of the country as a whole, or of touristic destinations, as well as integration of the hotel with tours available nearby, among other factors that can play a part in the customers choice behavior and satisfaction.
+hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}, while the satisfaction might also be influenced by factors that are uncontrollable by the hotel staff, such as surroundings, location, language immersion of the country as a whole, or of touristic destinations, as well as integration of the hotel with tours available nearby, among other factors that can play a part in the customers choice behavior and satisfaction.
 This leads to our third hypothesis:
@@
 This results in several studies focusing on only the behavior of this subset of tourists.
-To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
-A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; as well as \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
+To this day, cross-cultural studies and analyses for Asian and Western tourists have been scarce.
+A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; and \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
 
 One thing to note with the above cross-culture analyses is that they were performed before the year 2000.
-The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists, and, as such, in their satisfactions and dissatisfactions when traveling.
+The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists and as such, in their satisfactions and dissatisfactions when traveling.
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e.
@@
 \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
+For another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
 In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
@@
 According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
-And as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.
+And according to \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.
 
@@
 This means that the factors will be selected through statistical methods alone.
-This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves.
+This can open opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves.
 In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
@@
 As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation, and only then it can be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge.
+With the tools available to us in the are of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge.
 This process is called Knowledge Discovery in Databases.
@@
 With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed.
-Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer.
-Since then, text mining techniques have improved over the years.
+Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer, and improved on with the years.
 This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
@@
 More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted decades ago \cite[][]{stone1966general}.
+This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted for decades before \cite[][]{stone1966general}.
 With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm.
@@
 We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}}, as well as the travel site \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}} and determined the most commonly used words that would contribute the most to positive and negative opinions in a review using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-After classifying the sentences in the extracted reviews as emotionally positive or negative with an optimized SVM, we also observed the weight values of each keyword in the machine, and the frequency of the terms in all of the reviews to extract the most utilized words in either kind of reviews.
+These positive and negative keywords allow us to perform a Support Vector Machine based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
+After classifying the sentences in the extracted reviews as emotionally positive or negative with an optimized SVM, we also observed their weight values in the machine, and the frequency of the terms in all of the reviews to extract the most utilized words in either kind of reviews.
 We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}.
@@
 
-In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5938} review pages of hotels in Japan were collected.
+In the data collection stage for Chinese reviews in \textit{Ctrip} a total of \num[group-separator={,}]{5938} review pages of hotels in Japan were collected.
 From these pages, we extracted a total of \num[group-separator={,}]{44177} reviews, which were comprised of \num[group-separator={,}]{572218} separate sentences.
+
+% In our corpus, there were \num[group-separator={,}]{23443} different words used, from which \num[group-separator={,}]{2802} were noise characters.
 
@@
 
-To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
+Because Chinese text doesn't have spaces, to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
 In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
@@
 The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier.
-The selected SVM's keywords would then clearly represent the user preferences leading to positive and negative emotions.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}, and SVM performance results are displayed in section \ref{apx:entropy_results}.
-
-Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus.
+A group of keywords is determined by a calculation and comparison of Shannon's entropy \cite[][]{shannon1948} between two classes, and then the keywords are used in a Support Vector Classifier \cite[][]{cortes1995}, optimizing the entropy comparison values to select the best performing classifier.
+The selected classifier's feature keywords would then clearly represent the user preferences leading to positive and negative emotions.
+
+Shannon’s entropy, in the field of Information Theory, is defined to be the expected value of the information content in a signal.
+It is shown in formulas \ref{eq:H} and \ref{eq:lim_H}.
+Using this value we can observe the probability distribution of each word inside the corpus.
 A word that is included in many documents will have a high entropy value for that set of documents.
 Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-After classification, our data contained \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.
+We show this concept in Figure \ref{fig:entropygraphs}.
+
+\begin{equation}\label{eq:H}
+H = - \sum_{i=1}^M [P \log_2 P]
+\end{equation}
+
+\begin{equation}\label{eq:lim_H}
+\lim_{P\to0+} P \log_2 P = 0
+\end{equation}
+
+\begin{figure}[bp]
+    \centering
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{entropyzero.png}
+        \caption{Entropy close to zero.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\linewidth]{entropyhigh.png}
+        \caption{High entropy}
+    \end{subfigure}
+\caption{Probabilities of a word j being contained in a document i.}
+\label{fig:entropygraphs}
+\end{figure}
+
+To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, which were split into 159 sentences.
+We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class.
+In the case of English reviews, we sampled 665 reviews and with the collaboration of English-speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences.
+Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels.
+This is shown in formula \ref{eq:entropy_pos}.
+Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts.
+This is shown in formula \ref{eq:entropy_neg}.
+Examples of positive and negative sentences in English and Chinese are shown in the Appendix, in Table \ref{tab:training_examples}.
+
+\begin{equation}\label{eq:entropy_pos}
+H_{P} > \alpha H_{N} % \rightarrow satisfaction \: keyword
+\end{equation}
+
+\begin{equation}\label{eq:entropy_neg}
+H_{N} > \alpha' H_{P} % \rightarrow dissatisfaction \: keyword
+\end{equation}
+
+The mutually independent coefficients \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
+The result was 40 lists for each language, 20 for each emotional class.
+We trained a different Support Vector Classifier with each of the lists, and we chose the best performing lists for each emotional class and then combined the successful lists to train our best performing classifier.
+This resulted in a best performing positive emotion classifier (positive/non-positive) for each language.
+
+For the performance tests, we used a 5-fold cross-validation \cite[][]{kohavi1995} process in the Chinese reviews, and a 10-fold cross-validation process in the English reviews case, in which we calculated their F-measure \cite[][]{powers2011} means and standard deviations.
+The number of \(k\)-folds was decided from the sample size.
+Table \ref{tab:svm_f1_zh} shows the lists that had the best performance results in the case of Chinese text and Table \ref{tab:svm_f1_en} shows the best performance results in English texts in the Appendix.
+
+We then used these best performing classifiers in the rest of the respective data to label positive emotion sentences in a binary manner.
+The sentences not belonging to the positive emotion class were considered to belong in the negative emotion class.
+This resulted in \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.
 
@@
 During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly.
-These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those close to the separating hyperplane.
+These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those contained in the support vectors, close to the separating hyperplane.
 Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process.
@@
 However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity.
-\cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match.
+\cite{webber2010similarity} proposed a Rank-biased Overlap measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match.
 Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method.
@@
 % WITHOUT PERCENTAGE
-\subsection{Frequent keywords and their SVC weight values}\label{svmresults}
-
-To understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the Support Vector Classifier (SVC).
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value.
+\subsection{Frequent keywords and their SVM weight values}\label{svmresults}
+
+In order to understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers.
+Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVM weight value.
 The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign.
-We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).
+We ranked the keywords by frequency, and use their SVM weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).
 
@@
 \begin{table}[hbp] \centering
-\caption{Top 10 frequent positive Chinese keywords in satisfaction sentences.}
+\caption{Top 10 frequently used positive Chinese keywords in satisfaction sentences.}
 \label{tab:pos_keys_zh}
@@
 \begin{table}[hbp] \centering
-\caption{Frequent negative Chinese keywords in dissatisfaction sentences.}
+\caption{Frequently used negative Chinese keywords in dissatisfaction sentences.}
 \label{tab:neg_keys_zh}
@@
 Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is ``pricey" while in the Chinese keywords it is translated as ``price", and as such, it was changed to ``pricey" to match the English keywords.
-This was purely to overlap the most words possible, so it could have been very well modified the other way around with the same effect.
-The results of these calculations are shown in Table \ref{tab:rbo}.
-In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5.
+For example, in the English keyword lists, the word is 'pricey' while in the Chinese keywords it is translated as 'price', and as such, it was changed to 'pricey' to match the English keywords.
+The results of this are shown in Table \ref{tab:rbo}.
+In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points bigger than 7, and then it is cut at the cutoff point of 5.
 Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.
@@
 \centering
-\caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
+\caption{RBO results between Chinese and English ranked keyword lists, \(p=0.9\).}
 \label{tab:rbo}
@@
 
+\subsection{Chinese tourists' satisfaction and dissatisfaction keywords}
+
+Analyzing satisfaction keywords of Chinese hotel reviews from Table \ref{tab:pos_keys_zh}, we found that the most relevant subjects Chinese customers perceive positively are cleanliness and size, very possibly of the room they had stayed in.
+There is also the possibility that reviewers were praising, in general, the cleanliness of Japan’s environment, streets without litter, potable water and their culture of respecting spaces.
+Our results also indicate that the closeness of the hotel to scenic places is highly preferred by Chinese customers.
+Lower in the list of priorities, other positive factors that come into play when Chinese tourists choose a hotel to stay are the location in relation to public transport availability (such as the subway); and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.
+
+One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel.
+This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive.
+While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking.
+In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.
+
+Regarding dissatisfaction keywords in Table \ref{tab:neg_keys_zh}, we found that the most frequently criticized aspect of Japanese hotels was the price.
+Another important negative factor can be the availability or lack thereof of Chinese translations.
+Chinese customers can feel lost when they don't understand directions or instructions, either written or spoken; however, according to our data, most customers can be thought to have complained about written translations.
+Another dissatisfaction factor is the word 'old', which can be referring to the age of the building, or the general design and look of the place being old-fashioned.
+
+We can assert that Chinese customers value the room quality over transportation availability, that they are interested in included breakfast with the hotel stay, that they are concerned with value for money and the availability of Chinese language translations to have an easier time in the accommodation.
+
+\subsection{English-speaking tourists' satisfaction and dissatisfaction keywords}
+
+The most important satisfaction keyword in English reviews (see Table \ref{tab:pos_keys_en}) is 'staff', while lower in the list we can also observe 'helpful' and 'friendly', possibly referring to the staff as well, and since Japan is famous for its customer service culture, this is not unexpected.
+Next on the list, we can observe they value cleanliness, but a few more items in the list are regarding the location of the hotel, and possibly the availability of nearby transportation, such as the subway or train.
+We can also observe that the word 'free' is present there, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
+
+The negative keywords of dissatisfied customer reviews (see Table \ref{tab:neg_keys_en}) reveal an interesting picture.
+While the most used keyword is also related to the price of the hotels, most of the keywords are related to the hygiene of the hotel, namely dirty carpets, stains, cigarette smell in the room or curtains, and so on.
+We can also observe that the word 'renovation' is written lower in the list, as well as the word 'paper'.
+After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily.
+Regarding the word 'renovation', some cities in Japan (e.g.
+Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
+Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
+Another keyword there is 'slow', which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
+
+We can assert that English-speaking tourists value staff friendliness and location convenience concerning transport, but are concerned about any kind of decline in room quality both visually and regarding the smell and air quality, being quick to judge any sort of remains of cigarette smell.
+
 \subsection{Comparison of Chinese and English-speaking tourists' preferences}
 
-The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)).
+% USE Results from Rank-biased Overlap (full list) experiment results_p_0.9_cutoff_10.txt
+
+The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists at different cutoff points, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values.
 This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:1}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.
+This confirms our hypothesis \ref{hyp:1}, that the satisfaction and dissatisfaction factors are different for Chinese and English-speaking tourists.
 
@@
 
-The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that ``clean", ``recommend", ``subway" and ``price" are common factors to both customer groups.
-Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank.
-Furthermore, when arranging both lists by eliminating all uncommon elements, the lists become identical with an RBO of 1.0 for both satisfaction and dissatisfaction lists.
-This means hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), where the similar aspects in both customer groups were hypothesized to be different in their priority.
+The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common satisfaction and dissatisfaction factors to both customer groups accordingly.
+Furthermore, their place in the ranked list is the same for 'clean', 'subway' and 'price', making only 1 out of 4 factors different in priority.
+This means hypothesis \ref{hyp:2} is rejected, where even the similar aspects in both customer groups were hypothesized to be different in their priority.
 
@@
 As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature.
+For the satisfaction factors of Chinese-speaking tourists, 30\% of the keywords are managerial factors, while 60\% of them are environmental factors ('recommendation' is not counted as either).
+On the other hand, for the satisfaction factors of English-speaking tourists, 60\% of them are managerial, while 30\% of them are environmental.
+Now, for the dissatisfaction factors of Chinese customers, 71.4\% of them are managerial while the remaining 28.6\% of them are environmental.
+On the other hand, a 100\% of the dissatisfaction factors for English-speaking customers are managerial in nature.
 We can see these results in Table \ref{tab:hyp3}.
@@
 % \usepackage{graphicx}
-\begin{table}[hbp]
-\caption{Managerial and Environmental nature of the most frequent keywords}
+\begin{table}[]
+\caption{Managerial and Environmental nature of the most frequently used keywords}
 \label{tab:hyp3}
@@
 
-The results indicate that our main hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
-Below we explore what those differences were, what is the possible cause for them, and what they imply for the industry, as well as discussing similarities between the two groups.
-We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stems from both internal (managerial) and external (environmental) attributes of the hotel.
-
 \subsection{Chinese tourists - A big, clean space, and Chinese friendly}\label{disc:zh}
@@
 
-From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most important satisfaction factor for Chinese customers.
+From these two first ranking keywords, we can assert that 'Room Quality' is the most important satisfaction factor for Chinese customers.
 This means that Chinese tourists have an expectation of spaciousness and cleanliness when coming to Japan, be it by reputation, previous experiences, or cultural backgrounds.
@@
 We can compare this result with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-This other few factors found in previous literature could be linked to the keyword ``environment" as well.
-
-One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel.
-This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive.
-While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking.
-In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.
+This other few factors found in previous literature could be linked to the keyword 'environment' as well.
 
@@
 From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services.
-The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the 4th and 6th place.
+The word 'staff' is the most frequently used word for satisfied customers, while 'helpful' and 'friendly' follow it lower in the list at the 4th and 6th place.
 Japan is famous for their customer service all over the world.
-Staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say ``Please, allow me to guide you", and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
+Staff members are trained to speak in \textit{sonkeigo}, or 'respectful language', one of the most formal of the Japanese formality syntaxes.
+They are also trained to bow with different depths depending on the situation, where a light bow could be used to say 'Please, allow me to guide you', and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
 This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively.
@@
 We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.
-On another note, we can also observe that the word ``free" is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
-
-However, we can see from the rest of the keywords that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
+
+However, we can see from the rest of the keywords in combination that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
 Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards.
@@
 In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.
-Aside from cleanliness, we can also observe the word ``renovation" is written lower in the list, as well as the word ``paper".
-After observation of the samples, it is often used with the expression ``paper-thin walls", which could mean the customers can hear their neighbors easily.
-Regarding the word ``renovation", some cities in Japan (e.g.
-Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
-Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
 
@@
 
-For both customer groups, the main reason for dissatisfaction is price, which can be interpreted as a concern about value for money.
+For both customer groups, the main reason for dissatisfaction is price, which can be interpreted as a concern for value for money.
 A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
@@
 
-The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-While it wasn't the first priority for either of them, we can assert that the location of the hotel is a secondary but still important point in their satisfaction of a hotel.
+The location of the hotel, closeness to subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
+While it wasn't the priority for either of them, we can assert that the location of the hotel is a secondary but still important point in their satisfaction of a hotel.
 However, since this is an external factor to the management of the hotel, it is not often considered in literature.
@@
 Japan is a country with a particular public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for an outside observer.
+The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing map for an outside observer.
 Buses are also available, although less used than the rail systems in the big cities.
@@
 Japanese convenience stores, on the other hand, are also famous worldwide for their convenience.
-From drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs and so on, Japanese convenience stores are a haven for the traveler in need.
+From drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and so on, Japanese convenience stores are a haven for the traveler in need.
 If some trouble occurred, or a traveler forgot to pack a certain item, it is almost sure that they can find it here.
 
-Therefore, considering both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to choose carefully their location from the moment that they are constructed.
+Therefore, considering both transport systems and nearby shops, Japanese hotels have to choose carefully their location from the moment that they are constructed.
 While not a top priority, this is a universal factor for both customer groups and it can be an instant way to generate positive reviews.
@@
 While smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya), it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, there are many places where ``smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others.
+However, there are many places where 'smoking rooms' are available to keep the smoke to an enclosed area and avoid bothering others.
 Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
@@
 
-From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 60\% of keywords used by Chinese tourists are of an environmental nature (namely ``environment", ``periphery", ``close", ``transportation", ``nearby", and ``subway"), while the remaining 30\% is managerial in nature (and an undefined 10\%).
-However, these managerial words are all concentrated at the top of the list (``big", ``clean", ``breakfast").
-In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean", ``helpful", and ``free" to name a few.
+From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, Chinese tourists have a 60\% of keywords of an environmental nature (namely 'environment','periphery','close','transportation','nearby', and 'subway'), while the remaining 30\% is managerial in nature.
+However, those words are all concentrated at the top of the list ('big','clean','breakfast').
+In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as 'staff', 'clean', 'helpful', and 'free' to name a few.
 English-speaking customers also have managerial attributes at the very top of their list.
-This means that if one considers the satisfaction of both Chinese and Western tourists, a hotel has the ability to improve in ways that will attract more customers in the future.
+This means that in order to satisfy both Chinese and Western tourists, a hotel has the ability to improve in ways that will attract more customers in the future.
 If it was the other way around and the satisfaction was to be related more with environmental attributes, hotels would have to compete solely on their location.
@@
 This paper is not without its limitations.
-We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
+We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or not.
 Following that, we performed observations of sentences with those words, in an attempt to understand the context that these words were being used in.
@@
 Another limitation is that a big portion of the Asian tourists coming to Japan are Taiwanese and Korean, of which we couldn't do an analysis because of team members not knowing those languages.
-Aside from that, because of the anonymous nature of the data, further typology analysis couldn't be made (for example, Chinese men and women of different ages, or their Westerner counterparts).
+Aside from that, because of the anonymous nature of the data, further typology analysis couldn't be made (for example, Chinese men and women of different ages, or the same for Westerners).
 
@@
 
-In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via an SVC.
+In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via a Support Vector Classifier.
 We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof).
 We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points.
-These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
-
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups (``clean", ``recommend", ``subway" and ``price"), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0.
-This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
+These are low values, so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
+
+We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), only one of the words ('recommend') had a different place in the ranking of the lists for either group.
+This means our hypothesis \ref{hyp:2} is rejected, and that the common ground within both customer groups is also similar in ranking.
 
@@
 In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
-Another point of interest for the future of this study is to use word clusters with similar meanings instead of single words.
-
-\begin{acknowledgements}
-
-REDACTED
-
-\end{acknowledgements}
+Another point for the future of this study is to use word clusters with similar meanings instead of single words.
+
+\section*{Acknowledgments}
+
+During our research, apart from the group of Chinese students that collaborated with the training data and emotion tagging process, we received the commentary and discussion necessary to understand certain
+cultural aspects that could influence the interpretation of the data, from empirical and anecdotal Chinese sources, as well as collaboration in understanding the meaning behind the words we extracted by our dear colleagues, whom we would like to show gratitude to, Mr.
+Zhou Liangyuan, Ms.
+Fan Min and Ms.
+Eerdengqiqige.
+
+\medskip
+
+Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+\medskip
+
+Declarations of interest: none
+
+\clearpage
 
@@
 
-\section{Sentiment analysis training data examples}\label{apx:sentences_ex}
+\section{Sentiment analysis training data examples}
 
@@
 \textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
-\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good.
+\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: "The service of the hotel is very good.
 \\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it.
+ &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: "There is a back door to the subway station very close to it.
 \\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
+ & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
+ &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
 \multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
  &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
+ & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled 'non-smoking' \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
  &  & A bit pricey though \\ \hline
@@
 
-\section{Entropy keyword extraction experiment results}\label{apx:entropy_results}
+\section{Entropy keyword extraction experiment results}
 
@@
 Then we chose the best performing classification machine based on those keywords as shown in the Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-We also performed experiments to choose the best value of the parameter C used in the SVC.
+We also performed experiments to choose the best value of the parameter C used in SVC.
 C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
@@
 
-\section{Keywords with high SVM weights regardless of frequency}\label{apx:keywords_weights}
+\section{Keywords with high SVM weights regardless of frequency}
 
@@
 \begin{table}[hbp] \centering
-\caption{Chinese keywords with high SVM weights regardless of frequency.}
+\caption{Chinese keywords with high SVM weight values regardless of frequency.}
 \label{tab:key_weights_zh}
@@
 \centering
-\caption{English keywords with high SVM weights regardless of frequency.}
+\caption{English keywords with high SVM weight values regardless of frequency.}
 \label{tab:key_weights_en}
@@
 
-\section{Managerial and Environmental keywords}\label{apx:man_env}
-
-As explained on \ref{disc:hyp3}, we identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
+\section{Managerial and Environmental keywords}
+
+In section \ref{disc:hyp3}, we discussed how satisfaction of the customer can come both from managerial attributes of the hotel, as well as environmental attributes.
+We identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
 The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.

### 2020-09-27 2_revisions/V0_Before submission/V0_2_First draft - After first revision by Ola/tmp-emotion_V0_1.tex
First data commit: V2-1, before second review

--- 2020-09-27 2_revisions/V0_Before submission/V0_2.5_After first revision by Ola-but better/tmp-emotion_V0_2.5.tex
@@
 
-\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with text-mining}
+\title{Analyzing preferences differences between Chinese and English speakers in Japan hotel staying: A text mining method}
 
@@
 \corref{mycorrespondingauthor}}
-\ead{elisa.claire.aleman.carreon@gmail.com}
+\ead{s153400@stn.nagaokaut.ac.jp}
 % \orcid{0000-0002-6437-0866}
+
+\author[gidai]{Hirofumi Nonaka}
+\ead{nonaka@kjs.nagaokaut.ac.jp}
 
@@
 \ead{s173330@stn.nagaokaut.ac.jp}
-
-\author[gidai]{Hirofumi Nonaka}
-\ead{nonaka@kjs.nagaokaut.ac.jp}
 
@@
 \begin{abstract}
-
-Up until recently, most studies in tourist behavior have been biased for the Western world.
-With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen.
-However, cross-cultural studies of their differences with other cultures are scarce and predate the current boom in the Chinese economy.
-This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels.
-Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel.
-With the spread of the use of Web 2.0 to write online reviews of hotels, a large amount of text data is available for research purposes.
-With text mining, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers.
-This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel.
-In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which can be used for top-weighted ranked lists with different elements and lengths.
-We found that Chinese customers prefer big and clean spaces and that Western customers are satisfied with friendly staff members.
-We also found that Chinese tourists are unsatisfied with the hotel being Chinese friendly with treatment and language and that Western customers are unsatisfied with rooms that they consider dirty, or that smell of cigarette.
+Abstract
 
@@
 \begin{itemize}
-    \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
-    \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
-    \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
-    \item Both customer groups have concerns about the pricing of hotels (value for money).
-    \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
+    \item Chinese customers tend to prefer included breakfasts, and rooms that are big and clean.
+    \item Across all hotel prices, unsatisfied Chinese customers focus on the pricing of the hotel.
+    \item English speaking customers are satisfied with the staff, cleanliness, and transportation availability.
+    \item English speaking customers dislike pricey hotels and have a high dislike for dirty rooms and cigarette smell.
 \end{itemize}
@@
 From this total, the tourist population was mostly Asian (86.14\%), with approximately a fourth of the total (25.63\%) coming from China.
-Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
+Western countries, counting English speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
 Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.
@@
 However, up until recently studies on social sciences, and that includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Those that do include Asian populations in their analysis, most commonly Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations.
-This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as "long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
-It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
+Those that do include Asian populations in their analysis, most commonly Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview based studies with small samples, which while valid can have its limitations.
 
@@
 Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
-This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
+Data mining and big data methodologies can increase the number of samples from the hundred or so samples manageable by researchers to the hundreds of thousands that are automatically analyzed by machines.
+This can not only help confirm existing theories, but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
 
-In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Chinese and Western English-speaking tourists populations.
-With this data, we can both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past.
+In this study we take advantage of the availability of enormous amounts of data online for Chinese and western English speaking tourist populations' online reviews for Japanese hotels to both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been missed in the past.
 For this purpose, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel, and perform a statistical extraction of the topics that the customers of each population are most concerned about.
@@
 
-The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques.
-We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure.
-Furthermore, we aim to measure if both customer groups have differences in priorities for the factors that are common to both groups.
-Furthermore, we aim to measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.
+The objective of this study is to determine the difference in preferences between Chinese speaking customers and English speaking customers of Japanese Hotels using text-mining techniques.
+In the past, survey based studies have provided a theoretical background for specific customer groups, and cultural and language differences often cannot be observed in a single study.
+We propose to use large scale data from online hotel reviews in Chinese and English to study these differences in a statistical manner.
 
-Aside from this, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose; this means that cultural and language differences often cannot be observed in a single study.
-
-The difference in preferences that our study uncovers can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence them to write more satisfied online reviews that will in turn increase sales and attract new customers.
+These difference in preferences can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence newer customers to write more satisfied online reviews that will in turn increase sales and attract new customers.
 
@@
 This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the services that a hotel can provide for them, the experiences they want to have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay.
-These contrasting expectations, in turn, will determine the contrasting factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
+These different backgrounds will lead to different expectations of the services that a hotel can provide for them, the experiences they should have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay.
+These differing expectations in turn, will determine the differing factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
 Therefore we propose our first and second hypothesis:
@@
 \label{hyp:2}
-The common satisfaction and dissatisfaction factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
+Chinese and Western tourists have different priorities when it comes to similar satisfaction and dissatisfaction factors.
 \end{hyp}
@@
 There are fewer examples of this approach, but studies have also done this in the past \cite[e.g.][]{zhou2014}.
-While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
+While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via sentiment classification techniques.
 
@@
 Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}.
-This results in several studies focusing on only the behavior of this subset of tourists.
+This results in a number of studies focusing on only the behavior of this subset of tourists.
 To this day, cross-cultural studies and analyses for Asian and Western tourists have been scarce.
-A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; and \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
-
-One thing to note with the above cross-culture analyses is that they were performed before the year 2000.
-The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists and as such, in their satisfactions and dissatisfactions when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e.
-airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
+A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to peruse the Karaoke facilities of hotels, and both groups tend to have high expectations about facilities; \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
+One thing to note with the above cross-culture analyses is that they were performed before around the year 2000.
+The current Chinese economy boom should make an increase in influx, but the question that could be made is if that boom created a difference in the expectations of tourists and as such, of their satisfactions and dissatisfactions when traveling.
 
 % Universal behavior
-Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries aren't representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
+Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries isn't representative, have gone further and studied people from many countries in their samples, and performing a more universal and holistic (not cross-culture) analysis.
 \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
+\cite{choi2001} found that staff service quality, room quality and value for money were the top satisfaction determinants.
 For another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries, but a deeper cross-cultural analysis of the satisfaction factors wasn't performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
+In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from a number of different countries; although the factors were analyzed in general without much cross-cultural analysis, although their general satisfaction score was noticed to be different.
+\cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments and special food services.
 
@@
 \cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.
+\cite{shanka2004} found that English speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.
 
@@
 Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
+In general Chinese tourist populations have been found to have specific attributes by different researchers.
+According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness and scenery in contrast to experiences and activities.
+With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan, and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness and staff.
 Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
 According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
-And according to \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.
+And according to \cite{gao2017chinese} who analyzed Chinese tourists and their connection to nature while traveling in different generations, Chinese tourists prefer nature overall, but the younger generations seems to do so less than their older counterparts.
 
 % Studies are not universal.
-Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire).
-This means that the factors will be selected through statistical methods alone.
+Although the studies focusing on only Chinese tourists or only Western tourists have a narrow view, their theoretical contributions are valuable.
+We can see that depending on the study and the design of questionnaires, the as well as the destinations, the results can vary greatly.
+Not only that but while there seems to be both some overlap in most studies, some factors are completely ignored in one study while not in the other.
+However, with data mining, the definition of each subject or factor is left for the review writers to decide en masse, and be selected through statistical methods alone.
 This can open opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves.
-In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
+In addition, this study could help us compare the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
 
@@
 In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago, but they are now common for market and managerial studies, independent university students and any scientist that can connect to the Internet.
+What was commonly only seen in very specialized large laboratories with super computers a couple of decades ago is now common data size for market and managerial studies, independent university students and any scientist that can connect to the Internet.
 Such quantities of data are available to study now more than ever, but it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation, and only then it can be established as knowledge.
+As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining and evaluation, and only then it can be established as knowledge.
 With the tools available to us in the are of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge.
@@
 With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed.
-Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer, and improved on with the years.
+Text mining then, has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer, and improved on with the years.
 This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
@@
 More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted for decades before \cite[][]{stone1966general}.
+This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted since decades before \cite[][]{stone1966general}.
 With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm.
@@
 Our data could show satisfaction and dissatisfaction factors that are universal and it could also find strictly cultural preferences, but we expect that both of these options will present themselves.
-We can also assert that, if the previous literature is correct in their findings, we could arrive at very similar results, albeit using a database several orders of magnitude larger.
+We can also assert that, if the previous literature is correct in their findings, we could arrive to very similar results, albeit using a database several orders of magnitude larger.
 We can also expect that, because of the lack of questionnaire design and freedom of users to record their pleasures and grievances, it is possible that we will discover patterns that were previously unnoticed by researchers.
@@
 
-Because Chinese text doesn't have spaces, to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
+Because Chinese text doesn't have spaces, in order to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
 In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
@@
 We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class.
-In the case of English reviews, we sampled 665 reviews and with the collaboration of English-speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences.
+In the case of English reviews, we sampled 665 reviews and with the collaboration of English speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences.
 Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels.
@@
 However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity.
-\cite{webber2010similarity} proposed a Rank-biased Overlap measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match.
+\cite{webber2010similarity} proposed a Rank-biased Overlap measurement, which takes all of these factors into consideration.
 Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method.
@@
 
-In order to understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers.
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVM weight value.
+In order to understand the preferences of Chinese speaking tourists and English speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers.
+In order to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy based keyword in our complete data set and their SVM weight value.
 The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign.
@@
 
-We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English-speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.
+We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.
 
@@
 This could mean they were useful for classification (the emotional reaction is more extreme) but aren't as important a preference for users (there aren't many cases in that the keyword was applicable).
-In the appendix, Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context.
+In the appendix, Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes, and their translations in the relevant context.
 In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.
@@
 In order to calculate the similarity between the ranked lists shown in Tables \ref{tab:pos_keys_zh} and \ref{tab:pos_keys_en}, and the lists in Tables \ref{tab:neg_keys_zh} and \ref{tab:neg_keys_en}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points.
-Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is 'pricey' while in the Chinese keywords it is translated as 'price', and as such, it was changed to 'pricey' to match the English keywords.
+In addition, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
+For example, in the English keyword lists, the word is 'pricey' while in the Chinese keywords it is translated as 'price', and as such it was changed to 'pricey' to match the English keywords.
 The results of this are shown in Table \ref{tab:rbo}.
@@
 % \usepackage{multirow}
-\begin{table}[hbp]
+\begin{table}[]
 \centering
@@
 \multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
-\multirow{2}{*}{None}   & Satisfaction      & 0.265 \\ \cline{2-3} 
+\multirow{2}{*}{None} & Satisfaction & 0.222 \\ \cline{2-3} 
  & Dissatisfaction & 0.299 \\ \hline
-\multirow{2}{*}{Top 20} & Satisfaction      & 0.265 \\ \cline{2-3} 
+\multirow{2}{*}{Top 20} & Satisfaction & 0.221 \\ \cline{2-3} 
  & Dissatisfaction & 0.293 \\ \hline
-\multirow{2}{*}{Top 10} & Satisfaction      & 0.266 \\ \cline{2-3} 
+\multirow{2}{*}{Top 10} & Satisfaction & 0.209 \\ \cline{2-3} 
  & Dissatisfaction & 0.285 \\ \hline
@@
 There is also the possibility that reviewers were praising, in general, the cleanliness of Japan’s environment, streets without litter, potable water and their culture of respecting spaces.
-Our results also indicate that the closeness of the hotel to scenic places is highly preferred by Chinese customers.
-Lower in the list of priorities, other positive factors that come into play when Chinese tourists choose a hotel to stay are the location in relation to public transport availability (such as the subway); and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.
+Our results also indicate that closeness of the hotel to scenic places is highly preferred by Chinese customers.
+Lower in the list of priorities, other positive factors that come into play when Chinese tourists choose a hotel to stay is the location in relation to public transport availability (such as the subway); and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.
 
@@
 
-\subsection{English-speaking tourists' satisfaction and dissatisfaction keywords}
+\subsection{English speaking tourists' satisfaction and dissatisfaction keywords}
 
-The most important satisfaction keyword in English reviews (see Table \ref{tab:pos_keys_en}) is 'staff', while lower in the list we can also observe 'helpful' and 'friendly', possibly referring to the staff as well, and since Japan is famous for its customer service culture, this is not unexpected.
-Next on the list, we can observe they value cleanliness, but a few more items in the list are regarding the location of the hotel, and possibly the availability of nearby transportation, such as the subway or train.
+The most important satisfaction keyword in English reviews (see Table \ref{tab:pos_keys_en}) is 'staff', while lower in the list we can also observe 'helpful' and 'friendly', possibly referring to the staff as well, and since Japan is famous for it's customer service culture, this is not unexpected.
+Next on the list we can observe they value cleanliness, but a few more items in the list are regarding location of the hotel, and possibly the availability of nearby transportation, such as the subway or train.
 We can also observe that the word 'free' is present there, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
@@
 The negative keywords of dissatisfied customer reviews (see Table \ref{tab:neg_keys_en}) reveal an interesting picture.
-While the most used keyword is also related to the price of the hotels, most of the keywords are related to the hygiene of the hotel, namely dirty carpets, stains, cigarette smell in the room or curtains, and so on.
-We can also observe that the word 'renovation' is written lower in the list, as well as the word 'paper'.
-After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily.
-Regarding the word 'renovation', some cities in Japan (e.g.
+While the most used keyword is also related to the price of the hotels, most of the keywords relate to the hygiene of the hotel, namely dirty carpets, stains, cigarette smell in the room or curtains, and so on.
+We can also observe that the word 'renovation' is written lower in the list.
+Some cities in Japan (e.g.
 Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
@@
 
-We can assert that English-speaking tourists value staff friendliness and location convenience concerning transport, but are concerned about any kind of decline in room quality both visually and regarding the smell and air quality, being quick to judge any sort of remains of cigarette smell.
+We can assert that English speaking tourists value staff friendliness and location convenience in relation to transport, but are concerned about any kind of decline in room quality both visually and regarding the smell and air quality, being quick to judge any sort of remains of cigarette smell.
 
-\subsection{Comparison of Chinese and English-speaking tourists' preferences}
+\subsection{Comparison of Chinese and English speaking tourists' preferences}
 
@@
 
-The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists at different cutoff points, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values.
+The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.20 to 0.22 in satisfaction lists at different cutoff points, and from 0.28 to 0.32 in the dissatisfaction lists.
 This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:1}, that the satisfaction and dissatisfaction factors are different for Chinese and English-speaking tourists.
 
-From observation, however, we can assert that both Chinese and English-speaking tourists in Japan have different priorities, but consider the location of the hotel and the availability of transport nearby, such as subway or trains, as a secondary but still important point in their satisfaction of a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, while the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-English-speaking tourists on the other hand value staff friendliness over room quality when considering their satisfaction.
-
-The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common satisfaction and dissatisfaction factors to both customer groups accordingly.
-Furthermore, their place in the ranked list is the same for 'clean', 'subway' and 'price', making only 1 out of 4 factors different in priority.
-This means hypothesis \ref{hyp:2} is rejected, where even the similar aspects in both customer groups were hypothesized to be different in their priority.
+From observation however, we can assert that both Chinese and English speaking tourists in Japan have different priorities, but consider the location of the hotel and the availability of transport nearby, such as subway or trains, as a secondary but still important point in their satisfaction of a hotel.
+The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, while the English speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
+English speaking tourists on the other hand value staff friendliness over room quality when considering their satisfaction.
 
 We also can observe some keywords that aren't considered by their counterparts.
-For example, Chinese tourists are very satisfied with breakfast inclusion, while English-speaking customers are satisfied with free amenities.
-On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.
-
-As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature.
-For the satisfaction factors of Chinese-speaking tourists, 30\% of the keywords are managerial factors, while 60\% of them are environmental factors ('recommendation' is not counted as either).
-On the other hand, for the satisfaction factors of English-speaking tourists, 60\% of them are managerial, while 30\% of them are environmental.
-Now, for the dissatisfaction factors of Chinese customers, 71.4\% of them are managerial while the remaining 28.6\% of them are environmental.
-On the other hand, a 100\% of the dissatisfaction factors for English-speaking customers are managerial in nature.
-We can see these results in Table \ref{tab:hyp3}.
-The interpretation of these keywords is shown in the Appendix in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% \usepackage{graphicx}
-\begin{table}[]
-\caption{Managerial and Environmental nature of the most frequently used keywords}
-\label{tab:hyp3}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|c|r|r|r|}
-\hline
-\textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
-\multirow{2}{*}{Satisfaction} & Chinese speakers & 30\% & 60\% & 10\% \\ \cline{2-5} 
- & English speakers & 60\% & 30\% & 10\% \\ \hline
-\multirow{2}{*}{Dissatisfaction} & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
- & English speakers & 100\% & 0\% & 0\% \\ \hline
-\end{tabular}%
-}
-\end{table}
-
-For our purposes, hypothesis \ref{hyp:3} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel.
-This is confirmed for all but one list.
-The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial in nature.
-However, this is only regarding the top 10 items in the list, and lower in the list there are some environmental factors.
+For example, Chinese tourists are very satisfied with breakfast inclusion, while English speaking customers are satisfied with free amenities.
+On the other hand, English speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.
 
@@
 
-\subsection{Chinese tourists - A big, clean space, and Chinese friendly}\label{disc:zh}
+\subsection{}
 
-We found that Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
-From further inspection, we also find that while this is mostly relating to the rooms, there are many references to the public bathing facilities in the hotel.
-In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with special qualities.
-On the other hand, there are natural hot springs, called \textit{onsen}, which can be either bathing in the natural source of the water, or using the hot-spring water in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-This can be a cultural shock for many tourists, but still, this is an important attraction for many.
+% \subsection{Needs of the Chinese tourist market in Japan}\label{discussionneeds}
 
-From these two first ranking keywords, we can assert that 'Room Quality' is the most important satisfaction factor for Chinese customers.
-This means that Chinese tourists have an expectation of spaciousness and cleanliness when coming to Japan, be it by reputation, previous experiences, or cultural backgrounds.
-Whichever is the case, it appears that Chinese tourists are satisfied, which means their expectations regarding the rooms are being met.
-We can compare this result with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-This other few factors found in previous literature could be linked to the keyword 'environment' as well.
+% Analyzing the results from the extracted keywords is the key to understanding Chinese and English speaking customers of Japanese hotels since they can be interpreted as rankings of their explicit needs and demands.
 
-Moreover, Chinese tourists have expectations about the treatment towards the Chinese visitors that aren't being met.
-Be it Chinese language pamphlets, Chinese texts on instructions for the hotel room and it's appliances and features (T.V.
-channels, Wi-Fi setup, etc), or just the treatment towards Chinese people, it seems that their expectations are not being met.
-This is natural, since traveling in a strange land without knowledge of the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulties was one of the main reasons Chinese customers would give for not visiting again.
+% Our results are compatible with \cite{ryan2001} in their study of Chinese tourist behavior in New Zealand , where Chinese travelers were found to prefer traveling and exploring unfamiliar places that have a reputation for being clean and unpolluted environments, focusing on scenic beauty, history and culture.
+They also found complaints about the lack of Chinese language availability in the services they consumed.
+\cite{LIU2019337} describe that the behavior studied in Australia reflected that Chinese tourists were more likely to appreciate touristic places for the scenery, architecture, landmarks, and popular spots, rather than appreciate cultural experiences or activities.
+Similar to the findings in Liu et al., our results indicate that closeness of the hotel to scenic places is highly tied to satisfaction.
+However, their research is on online reviews of touristic places, instead of hotels.
+With this difference, our results showed that breakfast inclusion and the size and cleanliness of rooms were also tied to satisfaction, aside from scenery.
+According to our data, other positive factors that come into play when Chinese tourists choose a hotel to stay is the location in relation to public transport availability; and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.
+\cite{gao2017chinese} argue that Chinese people are heavily influenced by religion and a culture that regards harmony and oneness with nature and humans, which in turn influences their tourism behavior.
+However, they also argue that there are generational differences and that the older generations that lived through the changes that changed the environment and caused pollution care more about the environment, and as such appreciate natural and scenic touristic spots more than younger generations.
 
-\subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
+% This specific keyword is previously unmentioned in studies regarding the eating behavior of Chinese tourists.
+While these studies on eating behavior are very scarce, both a study on the food preferences of Chinese tourists in Australia \cite[][]{chang2010} and an article on Chinese food culture \cite[][]{ma2015} state that even in foreign countries, Chinese people have a habit to eat Chinese food, probably because of a need for familiarity.
+However, the analysis of our data points to the fact that more than Chinese food as a specific concept, hotel reviews are written with general words that represent food.
+We would like to further study specific Chinese tourists food preferences, such as the contents of said breakfast and other meals in future work to observe the level of necessity of these particular needs.
 
-From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services.
-The word 'staff' is the most frequently used word for satisfied customers, while 'helpful' and 'friendly' follow it lower in the list at the 4th and 6th place.
-Japan is famous for their customer service all over the world.
-Staff members are trained to speak in \textit{sonkeigo}, or 'respectful language', one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say 'Please, allow me to guide you', and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
-This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively.
-After all, Japanese staff treats all customers in this respectful manner, but for some customers, this could very well be the best they have been treated until that moment.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.
+% In their study of Chinese tourists in Vietnam, \cite{truong2009} also found both the tendency to be concerned with value for money.
+It is possible that concerns over value for money are a general cultural trait in the Chinese population.
+Applying this previous finding to our data, negativity about the pricing of hotels across all price brackets can mean they believe the price is too high for the service that they receive, regardless of their satisfaction or dissatisfaction with the service.
+Our results suggest that Chinese customers are expecting lower prices for whatever services they receive.
 
-However, we can see from the rest of the keywords in combination that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains.
-\cite{kozak2002} also found that hygiene and cleanliness were important satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.
+% Another important negative factor can be the availability or lack thereof of Chinese translations.
+Chinese customers can feel lost when they don't understand directions or instructions, either written or spoken; however, according to our data, most customers can be thought to have complained about written translations.
 
-\subsection{Price, the common enemy}\label{disc:price}
+% \subsection{Comparison with English speaking tourists in Japan}
 
-For both customer groups, the main reason for dissatisfaction is price, which can be interpreted as a concern for value for money.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, which could have an impact in this placement in the ranking.
+% Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.
 
-\subsection{Location, location, location}\label{disc:location}
+% In previous research, it has been found that Chinese tourists are harsher in their negative touristic attraction reviews than other nationalities \cite[][]{LIU2019337}.
+Taking this into account, and the large difference in frequency between complaints about price and other elements, Chinese customers can be said to be dissatisfied with price in a disproportionate way.
+English speaking tourists' dissatisfaction factors, on the other hand, have less of a gap in frequency, and as such can be said to be more concerned about cleanliness related factors than price.
 
-The location of the hotel, closeness to subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-While it wasn't the priority for either of them, we can assert that the location of the hotel is a secondary but still important point in their satisfaction of a hotel.
-However, since this is an external factor to the management of the hotel, it is not often considered in literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was nearby to at least two other subjects: subway or train, and convenience stores.
+% \section{Conclusions and future work}\label{conclusions}
 
-Japan is a country with a particular public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing map for an outside observer.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are particularly affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price.
-This means that for tourists, subway availability and a good map or plan to travel the city are of utmost necessity.
+% In this study, with the purpose to understand emotional responses of Chinese customers of Japanese hotels and understand their needs, we extracted keywords from their reviews from the Chinese portal site \textit{Ctrip} using entropy calculations from a manually classified sample of our data; then we used these keywords in machine learning experiments.
+Using the keywords to train a linear kernel Support Vector Classifier, we obtained the highest performance \((F=0.95\pm0.01\) using both our positive and negative keywords for a binary emotional classifier.
 
-Japanese convenience stores, on the other hand, are also famous worldwide for their convenience.
-From drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and so on, Japanese convenience stores are a haven for the traveler in need.
-If some trouble occurred, or a traveler forgot to pack a certain item, it is almost sure that they can find it here.
+% Using the weight vectors of our classifiers, as well as frequency of the words in our dataset, we found that Chinese customers have a preference for big and clean rooms, big thermal baths or bathhouses, expect good value for money regardless of price, that there is a lack of Chinese text translation and that they prefer hotels where breakfast is included.
+We also found that the friendliness of the staff increases in priority as the price and luxury of the hotel increases and that transportation is more important for customers looking for cheaper options compared to the more luxurious ones.
 
-Therefore, considering both transport systems and nearby shops, Japanese hotels have to choose carefully their location from the moment that they are constructed.
-While not a top priority, this is a universal factor for both customer groups and it can be an instant way to generate positive reviews.
+% For comparison, we also repeated the experiments on reviews written by English speaker tourists staying at Japanese hotels from \textit{TripAdvisor}.
+Observing the results we identified that English speaking customers hold a bigger contempt and negative reactions for dirty or stained rooms, but that the main concern is also the pricing of the hotels.
+We also found that they prefer friendly staff and transportation available from the airport or subway.
 
-\subsection{Tobacco, what's that smell?}\label{disc:tobacco}
+% Our results show the needs of a large and increasing segment of the customers.
+This would have otherwise presented difficulties with traditional methods because of language and culture barriers.
+The hotel industry can make use of these results to better the response from Chinese customers by focusing on improving topics they find important, such as cleanliness, the inclusion of breakfast, availability of Chinese translations in text format and so on.
+By doing this, satisfied users will write new reviews and thus influence future customers positively.
 
-A main concern for Western tourists was the smell of tobacco in their room.
-Upon manual inspection of a sample of reviews with this keyword, we found that it was often the case that the room was advertised as non-smoking, and yet the smell permeated the room and curtains.
-Another common complaint was that there wasn't any non-smoking facilities available at all, to begin with.
-This can completely ruin some customers' stay, and give a bad impression for review writers, which can lower the number of future customers.
+% In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or for work.
+Another point for the future of this study is to use word clusters with similar meanings instead of single words.
+As mentioned before, we would also study the food preferences of Chinese tourists, as well as the impact of the recommendation in different price brackets.
+Additionally, it would be interesting to study further into more specific emotions than the satisfaction and dissatisfaction classifications we performed in our study.
 
-However, in comparison, Chinese customers seem to not be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.
-
-Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years.
-While smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya), it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, there are many places where 'smoking rooms' are available to keep the smoke to an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it doesn't bother some customers, the lack of smell would not bother any existing customers.
-
-\subsection{Managerial vs. Environmental satisfaction}\label{disc:hyp3}
-
-As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
-For example, staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}.
-However, external or environmental attributes, such as location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, weather, and so on, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the amount of importance that those environmental or managerial attributes can have.
-
-From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, Chinese tourists have a 60\% of keywords of an environmental nature (namely 'environment','periphery','close','transportation','nearby', and 'subway'), while the remaining 30\% is managerial in nature.
-However, those words are all concentrated at the top of the list ('big','clean','breakfast').
-In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as 'staff', 'clean', 'helpful', and 'free' to name a few.
-English-speaking customers also have managerial attributes at the very top of their list.
-This means that in order to satisfy both Chinese and Western tourists, a hotel has the ability to improve in ways that will attract more customers in the future.
-If it was the other way around and the satisfaction was to be related more with environmental attributes, hotels would have to compete solely on their location.
-Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
-Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly.
-However, if hotels want to attract more and more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.
-
-\section{Limitations}\label{limitations}
-
-This paper is not without its limitations.
-We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or not.
-Following that, we performed observations of sentences with those words, in an attempt to understand the context that these words were being used in.
-However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database.
-Another limitation is that a big portion of the Asian tourists coming to Japan are Taiwanese and Korean, of which we couldn't do an analysis because of team members not knowing those languages.
-Aside from that, because of the anonymous nature of the data, further typology analysis couldn't be made (for example, Chinese men and women of different ages, or the same for Westerners).
-
-\section{Conclusion and Future Work}\label{conclusion}
-
-In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via a Support Vector Classifier.
-We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof).
-We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points.
-These are low values, so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
-
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), only one of the words ('recommend') had a different place in the ranking of the lists for either group.
-This means our hypothesis \ref{hyp:2} is rejected, and that the common ground within both customer groups is also similar in ranking.
-
-Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel (that it can be changed via managerial decisions without relocating) or environmental attributes of the hotel (things like location, closeness to shops or public transport).
-We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:3}.
-We also found that most of the Western customer satisfaction (60\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel, while environmental attributes only make for a smaller portion of the factors (30\% of the top 10 satisfaction keywords).
-In the case of Chinese customer satisfaction, the top of the list was managerial in nature (30\% of the top 10 words) and a bigger portion, although lower in ranking, was environmental in nature (60\%).
-For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial in nature, while the other 28.6\% were environmental in nature.
-
-Our results and discussion can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists, and we can observe their stark differences, as well as their common attributes.
-In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
-Another point for the future of this study is to use word clusters with similar meanings instead of single words.
-
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 
-As explained in section \ref{sentimentanalysis}, we performed experiments with different entropy values to extract keywords from the vocabulary.
+As explained on section \ref{sentimentanalysis}, we performed experiments with different entropy values to extract keywords from the vocabulary.
 Then we chose the best performing classification machine based on those keywords as shown in the Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
@@
 This could mean they were useful for classification but aren't as important a preference for users.
-Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context.
+Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes, and their translations in the relevant context.
 In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.
@@
 
-\section{Managerial and Environmental keywords}
-
-In section \ref{disc:hyp3}, we discussed how satisfaction of the customer can come both from managerial attributes of the hotel, as well as environmental attributes.
-We identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
-The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[hbp]
-\centering
-\caption{Hotel attribute types for the top 10 satisfaction keywords}
-\label{tab:man_env_pos}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|l|l|l|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & clean &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & breakfast &  & location & environmental \\ \cline{1-2} \cline{4-5} 
-unidentified & recommendation &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & environment &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & periphery &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & close &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
-environmental & transportation &  & train & environmental \\ \cline{1-2} \cline{4-5} 
-environmental & nearby &  & free & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & subway &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[hbp]
-\centering
-\caption{Hotel attribute types for the top 10 dissatisfaction keywords}
-\label{tab:man_env_neg}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{lll|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & dirty & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & stain & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
- &  &  & curtain & managerial \\ \cline{4-5} 
- &  &  & paper & managerial \\ \cline{4-5} 
- &  &  & renovation & managerial \\ \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
 \end{document}

### 2020-09-27 2_revisions/V0_Before submission/V0_3_1_Second draft/tmp-emotion_V0_3.tex
First data commit: V2-1, before second review

--- 2020-09-27 2_revisions/V0_Before submission/V0_2.5_After first revision by Ola-but better/tmp-emotion_V0_2.5.tex
@@
 
-\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with text-mining}
+\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}
 
@@
 With the increase of Chinese outbound tourists to countries across the globe, academic interest for this group has risen.
-However, cross-cultural studies of their differences with other cultures are scarce and predate the current boom in the Chinese economy.
+Increasing variation amongst clients means that managing hotels in a way that caters to their different tastes becomes more and more important.
+Despite this, cross-cultural studies of differences between Asian and Western cultures are scarce and predate the current boom in the Chinese economy.
 This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels.
 Additionally, most studies choose certain factors to be analyzed in their questionnaire, and this often is limited to managerial attributes of the hotel.
-With the spread of the use of Web 2.0 to write online reviews of hotels, a large amount of text data is available for research purposes.
-With text mining, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers.
+With the spread of Web 2.0 and online hotels reviews, a large amount of text data is available for research purposes.
+With our method, we can use Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples without interfering with the decision process of customers.
 This means that we can measure just how important are certain attributes of the hotel to customers, and whether those are managerial or environmental, that is, internal or external to the hotel.
@@
 Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.
+With these and other multicultural tourists populations, the tourist market is more and more diverse.
+Diversity in customers cultural backgrounds means that their expectations when staying at a hotel will also be varied.
+Hotel management therefore needs to cater to these different needs and expectations to increase their customers' satisfaction and maintain a good reputation generating positive word-of-mouth.
 
@@
 Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
+Data mining, machine learning and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
 This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
@@
 We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure.
-Furthermore, we aim to measure if both customer groups have differences in priorities for the factors that are common to both groups.
-Furthermore, we aim to measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.
+Furthermore, we will measure if both customer groups have differences in priorities for the factors that are common to both groups.
+In addition, we also measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes internal to the hotel, as well as environmental attributes external to the hotel.
 
@@
 \label{hyp:1}
-Chinese and Western tourists have different satisfaction and dissatisfaction factors.
+Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
 \end{hyp}
@@
 
-% In our corpus, there were \num[group-separator={,}]{23443} different words used, from which \num[group-separator={,}]{2802} were noise characters.
-
 In the TripAdvisor data collection, we collected data from \num[group-separator={,}]{21154} different hotels.
@@
 
-Because Chinese text doesn't have spaces, to parse Chinese words on their own we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
+In order to parse Chinese words and separate them we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
 In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
@@
 The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}.
-A group of keywords is determined by a calculation and comparison of Shannon's entropy \cite[][]{shannon1948} between two classes, and then the keywords are used in a Support Vector Classifier \cite[][]{cortes1995}, optimizing the entropy comparison values to select the best performing classifier.
-The selected classifier's feature keywords would then clearly represent the user preferences leading to positive and negative emotions.
-
-Shannon’s entropy, in the field of Information Theory, is defined to be the expected value of the information content in a signal.
-It is shown in formulas \ref{eq:H} and \ref{eq:lim_H}.
-Using this value we can observe the probability distribution of each word inside the corpus.
+Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier.
+The selected SVM's keywords would then clearly represent the user preferences leading to positive and negative emotions.
+Examples of tagged sentences are shown in Table \ref{tab:training_examples}, and SVM performance results are shown in section \ref{apx:entropy_results}.
+
+Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus.
 A word that is included in many documents will have a high entropy value for that set of documents.
 Opposite to this, a word appearing in only one document will have an entropy value of zero.
-We show this concept in Figure \ref{fig:entropygraphs}.
-
-\begin{equation}\label{eq:H}
-H = - \sum_{i=1}^M [P \log_2 P]
-\end{equation}
-
-\begin{equation}\label{eq:lim_H}
-\lim_{P\to0+} P \log_2 P = 0
-\end{equation}
-
-\begin{figure}[bp]
-    \centering
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{entropyzero.png}
-        \caption{Entropy close to zero.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\linewidth]{entropyhigh.png}
-        \caption{High entropy}
-    \end{subfigure}
-\caption{Probabilities of a word j being contained in a document i.}
-\label{fig:entropygraphs}
-\end{figure}
-
-To apply this logic, we retrieved 50 reviews as a sample of our corpus and with the collaboration of a group of 5 Chinese students, which were split into 159 sentences.
-We then tagged each sentence as the classes positive or negative depending on the emotion that the text conveyed, then calculated the entropy values for each word in relation to the set of sentences from each class.
-In the case of English reviews, we sampled 665 reviews and with the collaboration of English-speaking students manually tagged them by sentence, resulting in \num[group-separator={,}]{2357} tagged sentences.
-Words with higher entropy relating to the satisfaction set than to the dissatisfaction set by a factor of \(\alpha\) were determined to be keywords tied with satisfaction in Chinese reviews of hotels.
-This is shown in formula \ref{eq:entropy_pos}.
-Likewise, words with higher entropy for the dissatisfaction set than the satisfaction set by a factor of \(\alpha'\) were determined to be keywords tied to dissatisfaction in our texts.
-This is shown in formula \ref{eq:entropy_neg}.
-Examples of positive and negative sentences in English and Chinese are shown in the Appendix, in Table \ref{tab:training_examples}.
-
-\begin{equation}\label{eq:entropy_pos}
-H_{P} > \alpha H_{N} % \rightarrow satisfaction \: keyword
-\end{equation}
-
-\begin{equation}\label{eq:entropy_neg}
-H_{N} > \alpha' H_{P} % \rightarrow dissatisfaction \: keyword
-\end{equation}
-
-The mutually independent coefficients \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-The result was 40 lists for each language, 20 for each emotional class.
-We trained a different Support Vector Classifier with each of the lists, and we chose the best performing lists for each emotional class and then combined the successful lists to train our best performing classifier.
-This resulted in a best performing positive emotion classifier (positive/non-positive) for each language.
-
-For the performance tests, we used a 5-fold cross-validation \cite[][]{kohavi1995} process in the Chinese reviews, and a 10-fold cross-validation process in the English reviews case, in which we calculated their F-measure \cite[][]{powers2011} means and standard deviations.
-The number of \(k\)-folds was decided from the sample size.
-Table \ref{tab:svm_f1_zh} shows the lists that had the best performance results in the case of Chinese text and Table \ref{tab:svm_f1_en} shows the best performance results in English texts in the Appendix.
-
-We then used these best performing classifiers in the rest of the respective data to label positive emotion sentences in a binary manner.
-The sentences not belonging to the positive emotion class were considered to belong in the negative emotion class.
-This resulted in \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.
+
+We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative.
+The entropy comparison factor was tested from 1.25 to 6 in intervals of 0.25.
+After classification, our data contained \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.
 
@@
 During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly.
-These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those contained in the support vectors, close to the separating hyperplane.
+These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those close to the separating hyperplane.
 Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process.
@@
 The results of this are shown in Table \ref{tab:rbo}.
-In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points bigger than 7, and then it is cut at the cutoff point of 5.
+In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5.
 Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.
@@
 
-\subsection{Chinese tourists' satisfaction and dissatisfaction keywords}
-
-Analyzing satisfaction keywords of Chinese hotel reviews from Table \ref{tab:pos_keys_zh}, we found that the most relevant subjects Chinese customers perceive positively are cleanliness and size, very possibly of the room they had stayed in.
-There is also the possibility that reviewers were praising, in general, the cleanliness of Japan’s environment, streets without litter, potable water and their culture of respecting spaces.
-Our results also indicate that the closeness of the hotel to scenic places is highly preferred by Chinese customers.
-Lower in the list of priorities, other positive factors that come into play when Chinese tourists choose a hotel to stay are the location in relation to public transport availability (such as the subway); and as mentioned before, environments, such as gardens or parks nearby; and services nearby, like places to go shopping.
-
-One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel.
-This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive.
-While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking.
-In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.
-
-Regarding dissatisfaction keywords in Table \ref{tab:neg_keys_zh}, we found that the most frequently criticized aspect of Japanese hotels was the price.
-Another important negative factor can be the availability or lack thereof of Chinese translations.
-Chinese customers can feel lost when they don't understand directions or instructions, either written or spoken; however, according to our data, most customers can be thought to have complained about written translations.
-Another dissatisfaction factor is the word 'old', which can be referring to the age of the building, or the general design and look of the place being old-fashioned.
-
-We can assert that Chinese customers value the room quality over transportation availability, that they are interested in included breakfast with the hotel stay, that they are concerned with value for money and the availability of Chinese language translations to have an easier time in the accommodation.
-
-\subsection{English-speaking tourists' satisfaction and dissatisfaction keywords}
-
-The most important satisfaction keyword in English reviews (see Table \ref{tab:pos_keys_en}) is 'staff', while lower in the list we can also observe 'helpful' and 'friendly', possibly referring to the staff as well, and since Japan is famous for its customer service culture, this is not unexpected.
-Next on the list, we can observe they value cleanliness, but a few more items in the list are regarding the location of the hotel, and possibly the availability of nearby transportation, such as the subway or train.
-We can also observe that the word 'free' is present there, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
-
-The negative keywords of dissatisfied customer reviews (see Table \ref{tab:neg_keys_en}) reveal an interesting picture.
-While the most used keyword is also related to the price of the hotels, most of the keywords are related to the hygiene of the hotel, namely dirty carpets, stains, cigarette smell in the room or curtains, and so on.
-We can also observe that the word 'renovation' is written lower in the list, as well as the word 'paper'.
-After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily.
-Regarding the word 'renovation', some cities in Japan (e.g.
-Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
-Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is 'slow', which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
-
-We can assert that English-speaking tourists value staff friendliness and location convenience concerning transport, but are concerned about any kind of decline in room quality both visually and regarding the smell and air quality, being quick to judge any sort of remains of cigarette smell.
-
 \subsection{Comparison of Chinese and English-speaking tourists' preferences}
 
-% USE Results from Rank-biased Overlap (full list) experiment results_p_0.9_cutoff_10.txt
-
-The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists at different cutoff points, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values.
+The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)).
 This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:1}, that the satisfaction and dissatisfaction factors are different for Chinese and English-speaking tourists.
+This confirms our hypothesis \ref{hyp:1}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.
 
@@
 
-The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common satisfaction and dissatisfaction factors to both customer groups accordingly.
-Furthermore, their place in the ranked list is the same for 'clean', 'subway' and 'price', making only 1 out of 4 factors different in priority.
-This means hypothesis \ref{hyp:2} is rejected, where even the similar aspects in both customer groups were hypothesized to be different in their priority.
+The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that 'clean', 'recommend', 'subway' and 'price' are common factors to both customer groups.
+Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank.
+Furthermore, when arranging both lists by eliminating all uncommon elements, the lists become identical with an RBO of 1.0 for both satisfaction and dissatisfaction lists.
+This means hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), where the similar aspects in both customer groups were hypothesized to be different in their priority.
 
@@
 As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature.
-For the satisfaction factors of Chinese-speaking tourists, 30\% of the keywords are managerial factors, while 60\% of them are environmental factors ('recommendation' is not counted as either).
-On the other hand, for the satisfaction factors of English-speaking tourists, 60\% of them are managerial, while 30\% of them are environmental.
-Now, for the dissatisfaction factors of Chinese customers, 71.4\% of them are managerial while the remaining 28.6\% of them are environmental.
-On the other hand, a 100\% of the dissatisfaction factors for English-speaking customers are managerial in nature.
 We can see these results in Table \ref{tab:hyp3}.
@@
 
+One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel.
+This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive.
+While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking.
+In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.
+
 Moreover, Chinese tourists have expectations about the treatment towards the Chinese visitors that aren't being met.
@@
 We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.
+On another note, we can also observe that the word 'free' is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
 
@@
 In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.
+Aside from cleanliness, we can also observe the word 'renovation' is written lower in the list, as well as the word 'paper'.
+After observation of the samples, it is often used with the expression 'paper-thin walls', which could mean the customers can hear their neighbors easily.
+Regarding the word 'renovation', some cities in Japan (e.g.
+Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
+Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
+Another keyword there is 'slow', which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
 
@@
 We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points.
-These are low values, so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
-
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), only one of the words ('recommend') had a different place in the ranking of the lists for either group.
-This means our hypothesis \ref{hyp:2} is rejected, and that the common ground within both customer groups is also similar in ranking.
+These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
+
+We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ('clean', 'recommend', 'subway' and 'price'), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0.
+This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
 
@@
 
-During our research, apart from the group of Chinese students that collaborated with the training data and emotion tagging process, we received the commentary and discussion necessary to understand certain
-cultural aspects that could influence the interpretation of the data, from empirical and anecdotal Chinese sources, as well as collaboration in understanding the meaning behind the words we extracted by our dear colleagues, whom we would like to show gratitude to, Mr.
+During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr.
 Zhou Liangyuan, Ms.
@@
 Eerdengqiqige.
+We would also like to show gratitude to Ms.
+Jajus Aleksandra, from whom we also received notes on the editing and commentary on the content of our manuscript.
 
@@
 
-% \section*{References}
+\section*{References}
 
@@
 
-\section{Sentiment analysis training data examples}
+\section{Sentiment analysis training data examples}\label{apx:sentences_ex}
 
@@
 
-\section{Entropy keyword extraction experiment results}
+\section{Entropy keyword extraction experiment results}\label{apx:entropy_results}
 
@@
 
-\section{Keywords with high SVM weights regardless of frequency}
+\section{Keywords with high SVM weights regardless of frequency}\label{apx:keywords_weights}
 
@@
 
-\section{Managerial and Environmental keywords}
-
-In section \ref{disc:hyp3}, we discussed how satisfaction of the customer can come both from managerial attributes of the hotel, as well as environmental attributes.
-We identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
+\section{Managerial and Environmental keywords}\label{apx:man_env}
+
+As explained on \ref{disc:hyp3}, we identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
 The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.

### 2020-09-27 2_revisions/V0_Before submission/V0_4_Third draft/itt-emotion_V0_3.tex
First data commit: V2-1, before second review

--- 2020-09-27 2_revisions/V0_Before submission/V0_3_1_Second draft/tmp-emotion_V0_3.tex
@@
-\documentclass[review]{elsarticle}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
+%
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+
+\usepackage{scalerel}
+\usepackage{tikz}
+\usetikzlibrary{svg.path}
+
+\definecolor{orcidlogocol}{HTML}{A6CE39}
+\tikzset{
+  orcidlogo/.pic={
+    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
+    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
+                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
+                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
+  }
+}
+
+\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
+\begin{tikzpicture}[yscale=-1,transform shape]
+\pic{orcidlogo};
+\end{tikzpicture}
+}{|}}}}
 
@@
 
-%to have numbered 4th level sections 1.1.1.1
-\setcounter{tocdepth}{4}
-\setcounter{secnumdepth}{4}
-
-% to remove period in 4th level sections 1.1.1.1
-\makeatletter
-\def\els@aparagraph[#1]#2{\elsparagraph[#1]{#2}}
-\def\els@bparagraph#1{\elsparagraph*{#1}}
-\makeatother
-% to enter a newline after 4th level sections
-\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\smallskip}
-
 \modulolinenumbers[5]
 
-\journal{Tourism Management}
-
+\usepackage{xcolor}
+\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
+
+\journalname{Information Technology \& Tourism}
+
+\bibliographystyle{spbasic}
 %% APA style
-\bibliographystyle{model5-names}\biboptions{authoryear}
+% \bibliographystyle{model5-names}\biboptions{authoryear}
 
@@
 
-\begin{frontmatter}
-
 \title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}
 
-%% or include affiliations in footnotes:
-\author[gidai]{Elisa Claire Alemán Carreón
-\corref{mycorrespondingauthor}}
-\ead{elisa.claire.aleman.carreon@gmail.com}
-% \orcid{0000-0002-6437-0866}
-
-\author[gidai]{Hugo Alberto Mendoza Espa\~na}
-\ead{s173330@stn.nagaokaut.ac.jp}
-
-\author[gidai]{Hirofumi Nonaka}
-\ead{nonaka@kjs.nagaokaut.ac.jp}
-
-\author[nagasaki]{Toru Hiraoka}
-\ead{hiraoka@sun.ac.jp}
-
-\address[gidai]{Nagaoka University of Technology, Nagaoka, Japan}
-\address[nagasaki]{University of Nagasaki, Nagasaki, Japan}
-
-\cortext[mycorrespondingauthor]{
-Corresponding author%: \\
-% Elisa Claire Alemán Carreón \\
-% Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
-% Cell Phone: 080-9869-4756 \\
+\titlerunning{Differences between Chinese and English-speaking customers of Japanese hotels}
+
+\author{Elisa Claire Alem\'an Carre\'on \orcidicon{0000-0002-6437-0866} \and
+        Hugo Alberto Mendoza Espa\~na                                   \and
+        Hirofumi Nonaka                                                 \and
+        Toru Hiraoka
 }
+
+\authorrunning{E. Alemán Carreón et al.}
+
+\institute{Elisa Claire Alem\'an Carre\'on \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            ORCID: 0000-0002-6437-0866 \\
+            \email{elisa.claire.aleman.carreon@gmail.com}           %  \\
+            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+        \and
+            Hugo Alberto Mendoza Espa\~na \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            \email{s173330@stn.nagaokaut.ac.jp}
+        \and
+            Hirofumi Nonaka \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            \email{nonaka@kjs.nagaokaut.ac.jp}
+        \and
+            Toru Hiraoka \at
+            University of Nagasaki, Nagasaki, Japan \\
+            \email{hiraoka@sun.ac.jp}
+}
+
+% Corresponding author%: \\
+% % Elisa Claire Alemán Carreón \\
+% % Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
+% % Cell Phone: 080-9869-4756 \\
+% % ORCID: 0000-0002-6437-0866
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
 
@@
 
-\medskip
-\noindent\it{Highlights}
-\begin{itemize}
-    \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
-    \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
-    \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
-    \item Both customer groups have concerns about the pricing of hotels (value for money).
-    \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
-\end{itemize}
+% \medskip
+% \noindent\it{Highlights}
+% \begin{itemize}
+%     \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
+%     \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
+%     \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
+%     \item Both customer groups have concerns about the pricing of hotels (value for money).
+%     \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
+% \end{itemize}
+
+\keywords{Sentiment Analysis\and Hotels and Lodging\and Machine Learning\and Chinese\and English\and Preferences}
 
 \end{abstract}
-
-\begin{keyword}
-Sentiment Analysis\sep Hotels and Lodging\sep Machine Learning\sep Chinese\sep English\sep Preferences
-\end{keyword}
-
-\end{frontmatter}
 
@@
 
-\section*{Acknowledgments}
+\begin{acknowledgements}
 
 During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr.
-Zhou Liangyuan, Ms.
-Fan Min and Ms.
+Liangyuan Zhou, Ms.
+Min Fan and Ms.
 Eerdengqiqige.
 We would also like to show gratitude to Ms.
-Jajus Aleksandra, from whom we also received notes on the editing and commentary on the content of our manuscript.
+Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
 
@@
 
+\end{acknowledgements}
+
 \clearpage
 
-\section*{References}
+% \section*{References}
 

### 2020-09-27 2_revisions/V0_Before submission/V0_4_Third draft/itt-emotion_V0_4.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V1_Submit version/itt-emotion-manuscript_V1.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
+%
 \RequirePackage{fix-cm}
@@
 
-% For the ORCID icon
 \usepackage{scalerel}
@@
 
+\usepackage{xcolor}
+\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
+
 \journalname{Information Technology \& Tourism}
@@
 \bibliographystyle{spbasic}
+%% APA style
+% \bibliographystyle{model5-names}\biboptions{authoryear}
 
@@
 
-\titlerunning{Analyzing differences in satisfaction and dissatisfaction between Chinese and ...}
-
-\author{REDACTED
+\titlerunning{Differences between Chinese and English-speaking customers of Japanese hotels}
+
+\author{Elisa Claire Alem\'an Carre\'on \orcidicon{0000-0002-6437-0866} \and
+        Hugo Alberto Mendoza Espa\~na                                   \and
+        Hirofumi Nonaka                                                 \and
+        Toru Hiraoka
 }
 
-\authorrunning{REDACTED}
-
-\institute{REDACTED
+\authorrunning{E. Alemán Carreón et al.}
+
+\institute{Elisa Claire Alem\'an Carre\'on \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            ORCID: 0000-0002-6437-0866 \\
+            Corresponding Author* \\
+            \email{elisa.claire.aleman.carreon@gmail.com}           %  \\
+            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+        \and
+            Hugo Alberto Mendoza Espa\~na \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            \email{mendoza.espana@gmail.com}
+        \and
+            Hirofumi Nonaka \at
+            Nagaoka University of Technology, Nagaoka, Japan \\
+            \email{nonaka@kjs.nagaokaut.ac.jp}
+        \and
+            Toru Hiraoka \at
+            University of Nagasaki, Nagasaki, Japan \\
+            \email{hiraoka@sun.ac.jp}
 }
+
+% Corresponding author%: \\
+% % Elisa Claire Alemán Carreón \\
+% % Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
+% % Cell Phone: 080-9869-4756 \\
+% % ORCID: 0000-0002-6437-0866
 
@@
 We found that Chinese customers prefer big and clean spaces, and that Western customers are satisfied with friendly staff members.
-We also found that Chinese tourists are unsatisfied with lack of a Chinese friendly environment, and that Western customers are unsatisfied with dirty rooms, or the smell of cigarette.
+We also found that Chinese tourists are unsatisfied with low levels of Chinese friendliness and language, and that Western customers are unsatisfied with dirty rooms, or the smell of cigarette.
 
@@
 This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
+It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as "long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
 It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
@@
 To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
-A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; as well as \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
+A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; and \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
 
@@
 Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer.
-Since then, text mining techniques have improved over the years.
+Since then, text mining techniques have improved on with the years.
 This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
@@
 % WITHOUT PERCENTAGE
-\subsection{Frequent keywords and their SVC weight values}\label{svmresults}
-
-To understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the Support Vector Classifier (SVC).
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value.
+\subsection{Frequent keywords and their SVM weight values}\label{svmresults}
+
+To understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the SVM classifiers.
+Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVM weight value.
 The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign.
-We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).
+We ranked the keywords by frequency, and use their SVM weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).
 
@@
 Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is ``pricey" while in the Chinese keywords it is translated as ``price", and as such, it was changed to ``pricey" to match the English keywords.
+For example, in the English keyword lists, the word is "pricey" while in the Chinese keywords it is translated as "price", and as such, it was changed to "pricey" to match the English keywords.
 This was purely to overlap the most words possible, so it could have been very well modified the other way around with the same effect.
@@
 
-The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that ``clean", ``recommend", ``subway" and ``price" are common factors to both customer groups.
+The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that "clean", "recommend", "subway" and "price" are common factors to both customer groups.
 Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank.
@@
 \begin{table}[hbp]
-\caption{Managerial and Environmental nature of the most frequent keywords}
+\caption{Managerial and Environmental nature of the most frequently used keywords}
 \label{tab:hyp3}
@@
 
-From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most important satisfaction factor for Chinese customers.
+From these two first ranking keywords ("big" and "clean"), we can assert that room quality is the most important satisfaction factor for Chinese customers.
 This means that Chinese tourists have an expectation of spaciousness and cleanliness when coming to Japan, be it by reputation, previous experiences, or cultural backgrounds.
@@
 We can compare this result with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-This other few factors found in previous literature could be linked to the keyword ``environment" as well.
+This other few factors found in previous literature could be linked to the keyword "environment" as well.
 
@@
 From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services.
-The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the 4th and 6th place.
+The word "staff" is the most frequently used word for satisfied customers, while "helpful" and "friendly" follow it lower in the list at the 4th and 6th place.
 Japan is famous for their customer service all over the world.
-Staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say ``Please, allow me to guide you", and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
+Staff members are trained to speak in \textit{sonkeigo}, or "respectful language", one of the most formal of the Japanese formality syntaxes.
+They are also trained to bow with different depths depending on the situation, where a light bow could be used to say "Please, allow me to guide you", and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
 This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively.
@@
 We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.
-On another note, we can also observe that the word ``free" is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
+On another note, we can also observe that the word "free" is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
 
@@
 In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.
-Aside from cleanliness, we can also observe the word ``renovation" is written lower in the list, as well as the word ``paper".
-After observation of the samples, it is often used with the expression ``paper-thin walls", which could mean the customers can hear their neighbors easily.
-Regarding the word ``renovation", some cities in Japan (e.g.
+Aside from cleanliness, we can also observe the word "renovation" is written lower in the list, as well as the word "paper".
+After observation of the samples, it is often used with the expression "paper-thin walls", which could mean the customers can hear their neighbors easily.
+Regarding the word "renovation", some cities in Japan (e.g.
 Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
 Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
+Another keyword there is "slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
 
@@
 While smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya), it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, there are many places where ``smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others.
+However, there are many places where "smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others.
 Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
@@
 
-From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 60\% of keywords used by Chinese tourists are of an environmental nature (namely ``environment", ``periphery", ``close", ``transportation", ``nearby", and ``subway"), while the remaining 30\% is managerial in nature (and an undefined 10\%).
-However, these managerial words are all concentrated at the top of the list (``big", ``clean", ``breakfast").
-In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean", ``helpful", and ``free" to name a few.
+From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 60\% of keywords used by Chinese tourists are of an environmental nature (namely "environment","periphery","close","transportation","nearby", and "subway"), while the remaining 30\% is managerial in nature (and an undefined 10\%).
+However, these managerial words are all concentrated at the top of the list ("big","clean","breakfast").
+In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as "staff", "clean", "helpful", and "free" to name a few.
 English-speaking customers also have managerial attributes at the very top of their list.
@@
 
-In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via an SVC.
+In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via a Support Vector Classifier.
 We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof).
@@
 
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups (``clean", ``recommend", ``subway" and ``price"), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0.
+We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups ("clean", "recommend", "subway" and "price"), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0.
 This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
@@
 
-REDACTED
+During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr.
+Liangyuan Zhou, Ms.
+Min Fan and Ms.
+Eerdengqiqige.
+We would also like to show gratitude to Ms.
+Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+\medskip
+
+Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+\medskip
+
+Conflict of interest: none
 
 \end{acknowledgements}
+
+\clearpage
 

### 2020-09-27 2_revisions/V1_ITT submit version/itt-emotion_V1.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V1_Submit version/itt-emotion-manuscript_V1.tex
@@
 
-\author{REDACTED
+\author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
+        Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
+        Hirofumi Nonaka                                                 \protect\affmark[1] \and
+        Toru Hiraoka                                                    \protect\affmark[2]
 }
 
-\authorrunning{REDACTED}
+\authorrunning{E. Alemán Carreón et al.}
 
-\institute{REDACTED
+\institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
+            \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
+            % Corresponding Author %  \\
+            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+        \and
+            \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{mendoza.espana@gmail.com}
+        \and
+            \hspace*{1em} Hirofumi Nonaka \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
+        \and
+            \hspace*{1em} Toru Hiraoka \at
+            % University of Nagasaki, Nagasaki, Japan \\
+            \hspace*{1em} \email{hiraoka@sun.ac.jp}
+        \and
+            \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
+        \and
+            \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
 }
+
+% Corresponding author%: \\
+% % Elisa Claire Alemán Carreón \\
+% % Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
+% % Cell Phone: 080-9869-4756 \\
+% % ORCID: 0000-0002-6437-0866
 
@@
 
-REDACTED
+During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr.
+Liangyuan Zhou, Ms.
+Min Fan and Ms.
+Eerdengqiqige.
+We would also like to show gratitude to Ms.
+Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+\medskip
+
+Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+\medskip
+
+Conflict of interest: none
 

### 2020-09-27 2_revisions/V2-1_ITT_first revision_Nonaka revision/tobacco1.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V1_Submit version/itt-emotion-manuscript_V1.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-
-% For the ORCID icon
-\usepackage{scalerel}
-\usepackage{tikz}
-\usetikzlibrary{svg.path}
-
-\definecolor{orcidlogocol}{HTML}{A6CE39}
-\tikzset{
-  orcidlogo/.pic={
-    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-  }
-}
-
-\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-\begin{tikzpicture}[yscale=-1,transform shape]
-\pic{orcidlogo};
-\end{tikzpicture}
-}{|}}}}
-
-\usepackage{lineno, hyperref}
-% \usepackage[hyperfootnotes=false]{hyperref}
-\usepackage{array, pbox}
-\usepackage{mathtools}
-\usepackage{caption}
-\usepackage{graphicx}
-
-% To use chinese characters
-\usepackage{CJKutf8}
-
-% To add an appendix page
-\usepackage[page, title]{appendix}
-
-% Stick footnotes to bottom of the page
-\usepackage[bottom]{footmisc}
-
-% To insert commas into large numbers automatically
-\usepackage{siunitx}
-
-% To add hypothesis theorem
-\usepackage{ntheorem}
-\theoremseparator{:}
-\newtheorem{hyp}{Hypothesis}
-
-% To add the envelope symbol in Corresponding Author using % \Letter
-\usepackage{marvosym}
-
-% to add superscripts to mark the institute of authors
-% patch \maketitle:
-\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-% For table formatting
-\usepackage{multirow}
-\usepackage[normalem]{ulem}
-\useunder{\uline}{\ul}{}
-
-\modulolinenumbers[5]
-
-\journalname{Information Technology \& Tourism}
-
-\bibliographystyle{spbasic}
-
-\begin{document}
-
-\title{Analyzing differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels with machine learning}
-
-\titlerunning{Analyzing differences in satisfaction and dissatisfaction between Chinese and ...}
-
-\author{REDACTED
-}
-
-\authorrunning{REDACTED}
-
-\institute{REDACTED
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-
-Up until recently, most studies in tourist behavior have been biased for the Western world.
-With the increase of Chinese outbound tourists to other countries, academic interest for this group has risen.
-Increasing variation amongst clients means that managing hotels in a way that caters to their different tastes becomes more important.
-Despite this, cross-cultural studies of differences between Asian and Western cultures are scarce and predate the current boom in the Chinese economy.
-This economical boom could change their expectations and experiences of Chinese customers, which would, in turn, influence their satisfaction and dissatisfaction with hotels.
-Taking advantage of Web 2.0, we can apply Shannon's entropy to automatically extract the satisfaction and dissatisfaction factors from very large data samples of online reviews without interfering with the decision process of customers.
-This means that we can measure how important are certain attributes of the hotel to customers, and whether those are managerial or environmental for the hotel.
-In our study, we performed a sentiment analysis using an SVM classifier and then measured the similarity value for satisfaction and dissatisfaction keyword frequency ranking lists using the Rank-biased Overlap measure, which is used for top-weighted ranked lists with different elements and lengths.
-We found that Chinese customers prefer big and clean spaces, and that Western customers are satisfied with friendly staff members.
-We also found that Chinese tourists are unsatisfied with lack of a Chinese friendly environment, and that Western customers are unsatisfied with dirty rooms, or the smell of cigarette.
-
-% \medskip
-% \noindent\it{Highlights}
-% \begin{itemize}
-%     \item Chinese customers tend to prefer big and clean spaces but are unsatisfied with Chinese-friendliness.
-%     \item English-speaking customers are satisfied with friendly staff, but dislike rooms that are dirty or smell of cigarette.
-%     \item Both customer groups value the location of the hotel as a secondary factor for satisfaction.
-%     \item Both customer groups have concerns about the pricing of hotels (value for money).
-%     \item Satisfaction and dissatisfaction of customers come from managerial and environmental attributes of the hotel.
-% \end{itemize}
-
-\keywords{Sentiment Analysis\and Hotels and Lodging\and Machine Learning\and Chinese\and English\and Preferences}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries in addition to the whole of Europe make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
-Specifically for Chinese tourists, the effect on international economies as well as the number of researchers interested in this phenomenon has been increasing as well \cite[][]{sun2017}.
-With these and other multicultural tourists populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Hotel management therefore needs to cater to these different needs and expectations to increase their customers' satisfaction, maintain a good reputation, and, therefore, generate positive word-of-mouth.
-
-However, recent studies on social sciences, which includes tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}, and a few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000}, are commonly survey or interview-based studies with small samples, which while valid can have its limitations.
-This creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians; however, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging, compared to their Asian counterparts only spending 25\% of their budget on hotels.
-It is therefore important to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
-
-With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples from the hundred or so samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
-This can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Chinese and Western English-speaking tourists populations.
-With this data, we can both confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past.
-For this purpose, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel, and perform a statistical extraction of the topics that the customers of each population are most concerned about.
-
-\section{Research objective}\label{research_objective}
-
-The objective of this study is to determine the difference in preferences between Chinese-speaking and English-speaking customers of Japanese hotels using text-mining techniques.
-We aim to determine a quantitative measure of similarity (and therefore, difference) between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure.
-Furthermore, we will measure if both customer groups have differences in priorities for the factors that are common to both groups.
-In addition, we also measure how much satisfaction and dissatisfaction of both customer groups are influenced by managerial attributes (internal to the hotel), as well as environmental attributes (external to the hotel).
-
-Furthermore, our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose; this means that cultural and language differences often cannot be observed in a single study.
-
-The difference in preferences that our study uncovers can become the focal point for making improvements in tourism and service industries, increase the satisfaction of customers, and influence them to write more satisfied online reviews that will in turn increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-\subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}
-
-Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer, and as such, \cite{engel1990} state that satisfaction and dissatisfaction are therefore influenced by each customer's background.
-This is why Western and Asian, specifically Chinese, customers can have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the services that a hotel can provide for them, the experiences they want to have while staying at a hotel, and the level of comfort that they will have, from the moment that they choose the hotel throughout their stay.
-These contrasting expectations, in turn, will determine the contrasting factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
-Therefore we propose our first and second hypothesis:
-
-\begin{hyp}
-\label{hyp:1}
-Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
-\end{hyp}
-
-\begin{hyp}
-\label{hyp:2}
-The common satisfaction and dissatisfaction factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
-\end{hyp}
-
-Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-This leads to correlation analyses (either multivariate or single variable ones) where one factor can lead to satisfaction, while it is implied that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that solely correlate to satisfaction, as well as exploring factors which are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-While it is true that this method can decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e.
-hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}, without focusing on factors that are uncontrollable by the hotel staff, such as surroundings, location, language immersion of the country as a whole, or of touristic destinations, as well as integration of the hotel with tours available nearby, among other factors that can play a part in the customers choice behavior and satisfaction.
-This leads to our third hypothesis:
-
-\begin{hyp}
-\label{hyp:3}
-Satisfaction and dissatisfaction stems from both internal (managerial) and external (environmental) attributes of the hotel.
-\end{hyp}
-
-\subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-% Asians vs Western behavior
-In the past, tourist behavior analyzed from western samples and surveys was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}.
-This results in several studies focusing on only the behavior of this subset of tourists.
-To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
-A few examples are \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money; \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities; as well as \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with escape from routine and an increase in knowledge as a common motivator.
-
-One thing to note with the above cross-culture analyses is that they were performed before the year 2000.
-The current Chinese economy boom is making an increase in the influx of tourists, but the question that could be posed is whether that boom created a difference in the expectations of tourists, and, as such, in their satisfactions and dissatisfactions when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e.
-airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-
-% Universal behavior
-Other more recent studies, perhaps recognizing that samples being comprised of people from Western industrialized countries aren't representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries, but a deeper cross-cultural analysis of the satisfaction factors wasn't performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-% Western behavior 
-Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, efficiency of check-in and check-out, restaurant and bar facilities and lobby ambiance.
-
-% Chinese behavior
-Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-With some overlap, \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
-And as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall, but the younger generations seem to do so less than their older counterparts.
-
-% Studies are not universal.
-Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire).
-This means that the factors will be selected through statistical methods alone.
-This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves.
-In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-\subsection{Data mining, knowledge discovery and sentiment analysis}\label{theory_data}
-
-% Explain data mining and discovery of theory inside the data
-In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago, but they are now common for market and managerial studies, independent university students and any scientist that can connect to the Internet.
-Such quantities of data are available to study now more than ever, but it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation, and only then it can be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize, which can be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-% Text mining 
-Now, there are of course many sources of numerical data to be mined, but perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-With the introduction of Web 2.0, a never before seen quantity of valuable information is being posted to the Internet at a staggering speed.
-Text mining then has been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}, using what is called Natural Language Processing to parse language in a way that it can be analyzed by a computer.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-% Sentiment Analysis
-More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This is called sentiment analysis, or opinion mining, and a precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion, or even other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.
-
-% Data exploration
-Because the methodology for finding patterns in the data is automatic and statistical in nature, it is both reliable, in that the algorithm will find a pattern by its nature, and unpredictable, in that because it has no intervention from the researchers in making questionnaires it can have different results from anything that the researchers could expect.
-This is why, much like actual mining, data mining is mostly exploratory in nature.
-One can never be sure that something can be found, but we can make predictions and estimates about where to find knowledge, and what kind of knowledge can be uncovered.
-
-In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal and it could also find strictly cultural preferences, but we expect that both of these options will present themselves.
-We can also assert that, if the previous literature is correct in their findings, we could arrive at very similar results, albeit using a database several orders of magnitude larger.
-We can also expect that, because of the lack of questionnaire design and freedom of users to record their pleasures and grievances, it is possible that we will discover patterns that were previously unnoticed by researchers.
-
-\section{Methodology}\label{method}
-
-We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}}, as well as the travel site \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}} and determined the most commonly used words that would contribute the most to positive and negative opinions in a review using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-After classifying the sentences in the extracted reviews as emotionally positive or negative with an optimized SVM, we also observed the weight values of each keyword in the machine, and the frequency of the terms in all of the reviews to extract the most utilized words in either kind of reviews.
-We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}.
-
-\begin{figure}[bp]
-\centering
-\includegraphics[width=\textwidth]{emotion-method-overview.png}
-\caption{Overview of the methodology.}
-\label{fig:method-overview}
-\end{figure}
-
-\subsection{Data collection}\label{datacollection}
-
-In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5938} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{44177} reviews, which were comprised of \num[group-separator={,}]{572218} separate sentences.
-
-In the TripAdvisor data collection, we collected data from \num[group-separator={,}]{21154} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews in English, which we then separated into \num[group-separator={,}]{2697086} sentences using the \textit{gensim} python library.
-
-\subsection{Text processing}\label{textprocessing}
-
-To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-Because of variations and conjugations of words depending on the context and tense, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-\subsection{Sentiment analysis}\label{sentimentanalysis}
-
-The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier.
-The selected SVM's keywords would then clearly represent the user preferences leading to positive and negative emotions.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}, and SVM performance results are displayed in section \ref{apx:entropy_results}.
-
-Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus.
-A word that is included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-After classification, our data contained \num[group-separator={,}]{506452} positive Chinese sentences, \num[group-separator={,}]{65766} negative Chinese sentences, \num[group-separator={,}]{1288098} positive English sentences and \num[group-separator={,}]{1408988} negative English sentences.
-
-\subsection{SVM weight analysis}\label{svmweightsanalysis}
-
-During the SVM learning algorithm, each point of data that is classified incorrectly causes a change in the weight vector to better classify new data correctly.
-These changes to the weight vector are strong for features that needed to be taken account of to classify with a minimal error, those close to the separating hyperplane.
-Sequentially, the weight vector can be interpreted as a numerical representation of the effect each feature had for each class in the classification process.
-Below we show the formula for the weight vector (\ref{eq:svm_weight}).
-
-\begin{equation}\label{eq:svm_weight}
-w = \sum_{i=1}^N \alpha_i y_i x_i
-\end{equation}
-
-\subsection{Rank-biased Overlap}\label{rbo}
-
-In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\).
-However, since the lists are not necessarily of the same length, or have necessarily the same contents, and are top-weighted (where the first rank is the most important to know, with less and less importance as the ranks continue), it is necessary to use another measure of similarity.
-\cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement, which takes all of these factors into consideration when calculating a value from 0 to 1, where 0 means completely different lists and 1 means the two lists are an exact match.
-Because our Chinese keywords (their translations, at least) don't match our English keywords one to one, it is necessary to use this method.
-Webber's RBO produces 3 measurements: a minimum RBO, a residual RBO (from which one can know the maximum RBO), and an extrapolated RBO (where the list is assumed to continue in the same pattern of similarity towards infinity).
-The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}), Where \(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists (or it could be thought as \(1-p\) being the probability to stop looking at the next item in the list), and \(X\) being the overlap between the lists.
-The complete process is described at length by \cite{webber2010similarity}.
-
-\begin{equation}\label{eq:rbo_ext}
-RBO_{EXT}(S,T,p,k) = \frac{X_k}{k} \cdot p^k + \frac{1-p}{p} \sum_{d=1}^k{\frac{X_d}{d} \cdot p^d}
-\end{equation}
-
-\section{Data Analysis}\label{dataanalysis}
-
-% WITHOUT PERCENTAGE
-\subsection{Frequent keywords and their SVC weight values}\label{svmresults}
-
-To understand the preferences of Chinese-speaking tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use in relation to the number of total reviews, and their weight in the Support Vector Classifier (SVC).
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value.
-The frequency of the keywords in the database shows the level of priority it has for customers, and the weight value allows us to observe the sentiment it relates to by its positive or negative sign.
-We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment (positive weight means positive sentiment, and negative weight signifies negative sentiment).
-
-We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study and quantitatively rank the needs of Chinese customers, as shown in the Tables \ref{tab:pos_keys_zh} and \ref{tab:neg_keys_zh} (however, the latter does not have more than 7 keywords available); and for English-speaking customers, as shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.
-
-There were many more keywords than shown in most cases, however, and some showed to be high in weight but low in frequency.
-This could mean they were useful for classification (the emotional reaction is more extreme) but aren't as important a preference for users (there aren't many cases in that the keyword was applicable).
-In the appendix, Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context.
-In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.
-
-% Chinese_frequencies_svm_weight_positive_translations_matched.csv
-
-\begin{table}[hbp] \centering
-\caption{Top 10 frequent positive Chinese keywords in satisfaction sentences.}
-\label{tab:pos_keys_zh}
-\begin{tabular}{|c|l|c|c|c|} \hline
-\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
-% 1
-\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
-    & big 
-        & 15470 & 0.624 \\ \hline
-% 2
-\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
-    & clean 
-        & 12166 & 0.638 \\ \hline
-% 3
-\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
-    & breakfast 
-        & 10575 & 0.495 \\ \hline
-% 4
-\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
-    & recommendation 
-        & 8752 & 0.495 \\ \hline
-% 5
-\begin{CJK}{UTF8}{gbsn} 环境 \end{CJK} 
-    & \begin{tabular}[c]{@{}l@{}}
-    environment
-    \end{tabular} 
-        & 8694 & 0.248 \\ \hline
-% 6
-\begin{CJK}{UTF8}{gbsn} 周边 \end{CJK} 
-    & periphery 
-        & 8456 & 0.495 \\ \hline
-% 7
-\begin{CJK}{UTF8}{gbsn} 近 \end{CJK} 
-    & close
-        & 8372 & 0.028 \\ \hline
-% 8
-\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK} 
-    & transportation
-        & 8264 & 0.586 \\ \hline
-% 9
-\begin{CJK}{UTF8}{gbsn} 附近 \end{CJK} 
-    & nearby
-        & 6619 & 0.495 \\ \hline
-% 10
-\begin{CJK}{UTF8}{gbsn} 地铁 \end{CJK} 
-    & subway
-        & 5386 & 0.180 \\ \hline
-\end{tabular}
-\end{table}
-
-% Chinese_frequencies_svm_weight_negative_translations_matched.csv
-
-\begin{table}[hbp] \centering
-\caption{Frequent negative Chinese keywords in dissatisfaction sentences.}
-\label{tab:neg_keys_zh}
-\begin{tabular}{|c|l|c|c|} \hline
-\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
-% 1
-\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
-    & price 
-        & 7636 & -1.505 \\ \hline
-% 2
-\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
-    & geography 
-        & 2238 & -0.812 \\ \hline
-% 3
-\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
-    & Chinese language 
-        & 1410 & -0.714 \\ \hline
-% 4
-\begin{CJK}{UTF8}{gbsn} 陈旧 \end{CJK} 
-    & old-fashioned 
-        & 698 & -0.000 \\ \hline
-% 5
-\begin{CJK}{UTF8}{gbsn} 距离 \end{CJK} 
-    & distance 
-        & 349 & 0 \\ \hline
-% 6
-\begin{CJK}{UTF8}{gbsn} 老 \end{CJK} 
-    & old 
-        & 311 & 0 \\ \hline
-% 7
-\begin{CJK}{UTF8}{gbsn} 华人 \end{CJK} 
-    & Chinese person 
-        & 16 & -0.238 \\ \hline
-\end{tabular}
-\end{table}
-
-% Hugo_1_SVM_Combined_p1.5_n4.25_c2_Frequency_counts_posinega_subject-only.csv
-
-\begin{table}[hbp]
-\centering
-\caption{Top 10 positive English keywords in satisfaction sentences.}
-\label{tab:pos_keys_en}
-\begin{tabular}{|l|c|c|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
-% 1
-staff & 138677 & 0.537 \\ \hline
-% 2
-clean & 105971 & 1.886 \\ \hline
-% 3
-location & 103151 & 0.842 \\ \hline
-% 4
-helpful & 63558 & 1.999 \\ \hline
-% 5
-comfortable & 62793 & 1.724 \\ \hline
-% 6
-friendly & 57307 & 1.199 \\ \hline
-% 7
-recommend & 51433 & 1.158 \\ \hline
-% 8
-train & 45148 & -0.000 \\ \hline
-% 9
-free & 42084 & 0.734 \\ \hline
-% 10
-subway & 38354 & 1.951 \\ \hline
-\end{tabular}
-\end{table}
-
-% Hugo_1_SVM_Combined_p1.5_n4.25_c2_Frequency_counts_posinega_subject-only.csv
-
-\begin{table}[hbp]
-\centering
-\caption{High negative weight English keywords in dissatisfaction sentences.}
-\label{tab:neg_keys_en}
-\begin{tabular}{|l|c|c|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \hline
-% 1
-pricey & 3809 & -1.614 \\ \hline
-% 2
-carpet & 3683 & -0.507 \\ \hline
-% 3
-slow & 3177 & -1.281 \\ \hline
-% 4
-dirty & 2943 & -1.275 \\ \hline
-% 5
-uncomfortable & 2942 & -2.423 \\ \hline
-% 6
-stain & 2787 & -1.886 \\ \hline
-% 7
-cigarette & 2468 & -0.435 \\ \hline
-% 8
-curtain & 2032 & -0.224 \\ \hline
-% 9
-paper & 2029 & -0.503 \\ \hline
-% 10
-renovation & 1898 & -0.548 \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection{Rank-biased Overlap}\label{rboresults}
-
-In order to calculate the similarity between the ranked lists shown in Tables \ref{tab:pos_keys_zh} and \ref{tab:pos_keys_en}, and the lists in Tables \ref{tab:neg_keys_zh} and \ref{tab:neg_keys_en}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points.
-Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is ``pricey" while in the Chinese keywords it is translated as ``price", and as such, it was changed to ``pricey" to match the English keywords.
-This was purely to overlap the most words possible, so it could have been very well modified the other way around with the same effect.
-The results of these calculations are shown in Table \ref{tab:rbo}.
-In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5.
-Since the RBO measure can work regardless of the length of each list, this is not a problem in its calculation.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[hbp]
-\centering
-\caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
-\label{tab:rbo}
-\begin{tabular}{|l|c|r|}
-\hline
-\multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
-\multirow{2}{*}{None}   & Satisfaction      & 0.265 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.299 \\ \hline
-\multirow{2}{*}{Top 20} & Satisfaction      & 0.265 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.293 \\ \hline
-\multirow{2}{*}{Top 10} & Satisfaction      & 0.266 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.285 \\ \hline
-\multirow{2}{*}{Top 5}  & Satisfaction      & 0.221 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.321 \\ \hline
-\end{tabular}
-\end{table}
-
-\section{Results}\label{results}
-
-\subsection{Comparison of Chinese and English-speaking tourists' preferences}
-
-The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.221 to 0.265 in satisfaction lists, and from 0.285 to 0.321 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)).
-This means that, while there is some similarity, the preferences are fundamentally different if we consider them as top-weighted, that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:1}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.
-
-From observation, however, we can assert that both Chinese and English-speaking tourists in Japan have different priorities, but consider the location of the hotel and the availability of transport nearby, such as subway or trains, as a secondary but still important point in their satisfaction of a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, while the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-English-speaking tourists on the other hand value staff friendliness over room quality when considering their satisfaction.
-
-The lists for Chinese and English-speaking tourists are quite different, but if we compare the lists, we find that ``clean", ``recommend", ``subway" and ``price" are common factors to both customer groups.
-Their place in the ranked list is the exact same for most of them, and only 1 out of 4 factors is different in rank.
-Furthermore, when arranging both lists by eliminating all uncommon elements, the lists become identical with an RBO of 1.0 for both satisfaction and dissatisfaction lists.
-This means hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), where the similar aspects in both customer groups were hypothesized to be different in their priority.
-
-We also can observe some keywords that aren't considered by their counterparts.
-For example, Chinese tourists are very satisfied with breakfast inclusion, while English-speaking customers are satisfied with free amenities.
-On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.
-
-As to the top 10 satisfaction and dissatisfaction keywords themselves we can observe whether they are attributes internal to the hotel, that is, managerial in nature, or external to it, environmental in nature.
-We can see these results in Table \ref{tab:hyp3}.
-The interpretation of these keywords is shown in the Appendix in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% \usepackage{graphicx}
-\begin{table}[hbp]
-\caption{Managerial and Environmental nature of the most frequent keywords}
-\label{tab:hyp3}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|c|r|r|r|}
-\hline
-\textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
-\multirow{2}{*}{Satisfaction} & Chinese speakers & 30\% & 60\% & 10\% \\ \cline{2-5} 
- & English speakers & 60\% & 30\% & 10\% \\ \hline
-\multirow{2}{*}{Dissatisfaction} & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
- & English speakers & 100\% & 0\% & 0\% \\ \hline
-\end{tabular}%
-}
-\end{table}
-
-For our purposes, hypothesis \ref{hyp:3} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel.
-This is confirmed for all but one list.
-The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial in nature.
-However, this is only regarding the top 10 items in the list, and lower in the list there are some environmental factors.
-
-\section{Discussion}\label{discussion}
-
-The results indicate that our main hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
-Below we explore what those differences were, what is the possible cause for them, and what they imply for the industry, as well as discussing similarities between the two groups.
-We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stems from both internal (managerial) and external (environmental) attributes of the hotel.
-
-\subsection{Chinese tourists - A big, clean space, and Chinese friendly}\label{disc:zh}
-
-We found that Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
-From further inspection, we also find that while this is mostly relating to the rooms, there are many references to the public bathing facilities in the hotel.
-In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with special qualities.
-On the other hand, there are natural hot springs, called \textit{onsen}, which can be either bathing in the natural source of the water, or using the hot-spring water in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-This can be a cultural shock for many tourists, but still, this is an important attraction for many.
-
-From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most important satisfaction factor for Chinese customers.
-This means that Chinese tourists have an expectation of spaciousness and cleanliness when coming to Japan, be it by reputation, previous experiences, or cultural backgrounds.
-Whichever is the case, it appears that Chinese tourists are satisfied, which means their expectations regarding the rooms are being met.
-We can compare this result with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-This other few factors found in previous literature could be linked to the keyword ``environment" as well.
-
-One key component we found in Chinese customer preferences is the inclusion of breakfast within the hotel.
-This can be inferred from the high frequency with which this keyword was included in the sentences emotionally classified as positive.
-While other food-related words were extracted, most of them were general in nature, like “food” or “eating”, and in a lower ranking.
-In contrast, the word “breakfast”, which is referring to a specific time and very possibly its inclusion in the hotel commodities, was very frequently used in positive texts compared to other food-related words.
-
-Moreover, Chinese tourists have expectations about the treatment towards the Chinese visitors that aren't being met.
-Be it Chinese language pamphlets, Chinese texts on instructions for the hotel room and it's appliances and features (T.V.
-channels, Wi-Fi setup, etc), or just the treatment towards Chinese people, it seems that their expectations are not being met.
-This is natural, since traveling in a strange land without knowledge of the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulties was one of the main reasons Chinese customers would give for not visiting again.
-
-\subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-From the satisfaction factors of English-speaking tourists, we can see that at least 3 words relate to staff friendliness and services.
-The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the 4th and 6th place.
-Japan is famous for their customer service all over the world.
-Staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say ``Please, allow me to guide you", and a deep bow to apologize for any inconvenience the customer could have, with a very respectful apology as well.
-This is all very different from Westerner experiences and while it could be a culture shock to some, it is mostly seen positively.
-After all, Japanese staff treats all customers in this respectful manner, but for some customers, this could very well be the best they have been treated until that moment.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is an important determinant in the satisfaction of Western tourists.
-On another note, we can also observe that the word ``free" is present in the satisfaction keywords, which after observing a few examples in the database, we concluded that it relates to the free amenities in a hotel room, such as cosmetics, soaps, coffee, tea, and so on.
-
-However, we can see from the rest of the keywords that most of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Where Chinese customers were completely satisfied, English-speaking customers have found many places unacceptable to their standards.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains.
-\cite{kozak2002} also found that hygiene and cleanliness were important satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that it is mostly linked to dissatisfaction and that westerners could be said to have high standards of hygiene when compared to their Chinese counterparts.
-Aside from cleanliness, we can also observe the word ``renovation" is written lower in the list, as well as the word ``paper".
-After observation of the samples, it is often used with the expression ``paper-thin walls", which could mean the customers can hear their neighbors easily.
-Regarding the word ``renovation", some cities in Japan (e.g.
-Osaka) are currently going under a large number of renovations, which are also extending to the hotel facilities.
-Customers staying in places in renovation or near a renovation construction can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
-
-\subsection{Price, the common enemy}\label{disc:price}
-
-For both customer groups, the main reason for dissatisfaction is price, which can be interpreted as a concern about value for money.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, which could have an impact in this placement in the ranking.
-
-\subsection{Location, location, location}\label{disc:location}
-
-The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-While it wasn't the first priority for either of them, we can assert that the location of the hotel is a secondary but still important point in their satisfaction of a hotel.
-However, since this is an external factor to the management of the hotel, it is not often considered in literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was nearby to at least two other subjects: subway or train, and convenience stores.
-
-Japan is a country with a particular public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for an outside observer.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are particularly affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price.
-This means that for tourists, subway availability and a good map or plan to travel the city are of utmost necessity.
-
-Japanese convenience stores, on the other hand, are also famous worldwide for their convenience.
-From drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs and so on, Japanese convenience stores are a haven for the traveler in need.
-If some trouble occurred, or a traveler forgot to pack a certain item, it is almost sure that they can find it here.
-
-Therefore, considering both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to choose carefully their location from the moment that they are constructed.
-While not a top priority, this is a universal factor for both customer groups and it can be an instant way to generate positive reviews.
-
 \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
@@
 After all, even if it doesn't bother some customers, the lack of smell would not bother any existing customers.
-
-\subsection{Managerial vs. Environmental satisfaction}\label{disc:hyp3}
-
-As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
-For example, staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}.
-However, external or environmental attributes, such as location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, weather, and so on, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the amount of importance that those environmental or managerial attributes can have.
-
-From Table \ref{tab:hyp3} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 60\% of keywords used by Chinese tourists are of an environmental nature (namely ``environment", ``periphery", ``close", ``transportation", ``nearby", and ``subway"), while the remaining 30\% is managerial in nature (and an undefined 10\%).
-However, these managerial words are all concentrated at the top of the list (``big", ``clean", ``breakfast").
-In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean", ``helpful", and ``free" to name a few.
-English-speaking customers also have managerial attributes at the very top of their list.
-This means that if one considers the satisfaction of both Chinese and Western tourists, a hotel has the ability to improve in ways that will attract more customers in the future.
-If it was the other way around and the satisfaction was to be related more with environmental attributes, hotels would have to compete solely on their location.
-Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
-Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly.
-However, if hotels want to attract more and more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.
-
-\section{Limitations}\label{limitations}
-
-This paper is not without its limitations.
-We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we performed observations of sentences with those words, in an attempt to understand the context that these words were being used in.
-However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database.
-Another limitation is that a big portion of the Asian tourists coming to Japan are Taiwanese and Korean, of which we couldn't do an analysis because of team members not knowing those languages.
-Aside from that, because of the anonymous nature of the data, further typology analysis couldn't be made (for example, Chinese men and women of different ages, or their Westerner counterparts).
-
-\section{Conclusion and Future Work}\label{conclusion}
-
-In this study, with the purpose to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations; then we used these keywords for sentiment classification via an SVC.
-We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences in Chinese and English reviews to find their similarity (or lack thereof).
-We obtained values ranging from 0.221 to 0.265 in satisfaction lists and from 0.285 to 0.321 in dissatisfaction lists at different cutoff points.
-These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the preferences of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:1}.
-
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers, and found that from the four words that were common amongst both groups (``clean", ``recommend", ``subway" and ``price"), their ranking when isolated from the uncommon elements in both lists was identical, resulting in an RBO of 1.0.
-This means our hypothesis \ref{hyp:2} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
-
-Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel (that it can be changed via managerial decisions without relocating) or environmental attributes of the hotel (things like location, closeness to shops or public transport).
-We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:3}.
-We also found that most of the Western customer satisfaction (60\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel, while environmental attributes only make for a smaller portion of the factors (30\% of the top 10 satisfaction keywords).
-In the case of Chinese customer satisfaction, the top of the list was managerial in nature (30\% of the top 10 words) and a bigger portion, although lower in ranking, was environmental in nature (60\%).
-For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial in nature, while the other 28.6\% were environmental in nature.
-
-Our results and discussion can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists, and we can observe their stark differences, as well as their common attributes.
-In future work we plan to investigate further into this topic, extending our data set and researching for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
-Another point of interest for the future of this study is to use word clusters with similar meanings instead of single words.
-
-\begin{acknowledgements}
-
-REDACTED
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
-\clearpage
-
-\appendixpage
-\appendix
-
-\section{Sentiment analysis training data examples}\label{apx:sentences_ex}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[hbp]
-\centering
-\caption{Examples of positive and negative sentences used for training SVM}
-\label{tab:training_examples}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|c|l|}
-\hline
-\textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
-\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good.
-\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
-\multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
- &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
- &  & A bit pricey though \\ \hline
-\end{tabular}%
-}
-\end{table}
-
-\section{Entropy keyword extraction experiment results}\label{apx:entropy_results}
-
-As explained in section \ref{sentimentanalysis}, we performed experiments with different entropy values to extract keywords from the vocabulary.
-Then we chose the best performing classification machine based on those keywords as shown in the Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-We also performed experiments to choose the best value of the parameter C used in the SVC.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives, but depending on the data it can increase false negatives.
-Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[hbp]
-\centering
-\caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-\label{tab:svm_f1_zh}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
-\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[hbp] \centering
-\caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-\label{tab:svm_f1_en}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
-\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
-\end{tabular}
-\end{table}
-
-\section{Keywords with high SVM weights regardless of frequency}\label{apx:keywords_weights}
-
-There were many more keywords than shown in Tables \ref{tab:pos_keys_en} and \ref{tab:neg_keys_en}.
-Some showed to be high in weight but low in frequency.
-This could mean they were useful for classification but aren't as important a preference for users.
-Table \ref{tab:key_weights_zh} shows some keywords that have a relatively high weight value for both positive and negative extremes and their translations in the relevant context.
-In Table \ref{tab:key_weights_en} we show keywords for the English classifier with high weight values as well.
-
-\begin{table}[hbp] \centering
-\caption{Chinese keywords with high SVM weights regardless of frequency.}
-\label{tab:key_weights_zh}
-\begin{tabular}{|>{\centering\arraybackslash}m{3em}|m{10em}|>{\centering\arraybackslash}m{7em}|>{\centering\arraybackslash}m{5em}|} \hline
-\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Entropy List} & \textbf{SVC Weight} \\ \hline
-\begin{CJK}{UTF8}{gbsn} 地方 \end{CJK} 
-    & region, local 
-        & Positive 
-        & 1.343 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK} 
-    & clean 
-        & Positive 
-        & 0.638 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 大 \end{CJK} 
-    & big, wide 
-        & Positive 
-        & 0.624 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK} 
-    & traffic, transportation 
-        & Positive 
-        & 0.586 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 热情 \end{CJK} 
-    & cordial, kindness 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 周边 \end{CJK} 
-    & periphery 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 景色 \end{CJK} 
-    & scenery 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK} 
-    & recommendation 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 日本 \end{CJK} 
-    & Japan 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK} 
-    & breakfast 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 附近 \end{CJK} 
-    & nearby 
-        & Positive 
-        & 0.495 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} 
-    & Chinese text 
-        & Negative 
-        & -0.714 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} 
-    & geography 
-        & Negative 
-        & -0.812 \\ \hline
-\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} 
-    & price 
-        & Negative 
-        & -1.505 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[hbp]
-\centering
-\caption{English keywords with high SVM weights regardless of frequency.}
-\label{tab:key_weights_en}
-\begin{tabular}{|l|c|c|}
-\hline
-\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Entropy\\ List\end{tabular}}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} \\ \hline
-bathhouse & Positive & 2.000 \\ \hline
-museum & Positive & 2.000 \\ \hline
-meeting & Positive & 1.997 \\ \hline
-subway & Positive & 1.951 \\ \hline
-cozy & Positive & 2.000 \\ \hline
-convenience & Positive & 1.888 \\ \hline
-clean & Positive & 1.886 \\ \hline
-comfortable & Positive & 1.724 \\ \hline
-dirty & Negative & -1.275 \\ \hline
-policy & Negative & -1.463 \\ \hline
-prepay & Negative & -1.517 \\ \hline
-pricey & Negative & -1.614 \\ \hline
-sticky & Negative & -2.000 \\ \hline
-\end{tabular}
-\end{table}
-
-\section{Managerial and Environmental keywords}\label{apx:man_env}
-
-As explained on \ref{disc:hyp3}, we identified the nature of each keyword in the top 10 lists of both satisfaction and dissatisfaction for Chinese and English-speaking tourists and summarized them in Table \ref{tab:hyp3}.
-The detailed identification of each keyword is shown in Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg} below.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[hbp]
-\centering
-\caption{Hotel attribute types for the top 10 satisfaction keywords}
-\label{tab:man_env_pos}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|l|l|l|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & clean &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & breakfast &  & location & environmental \\ \cline{1-2} \cline{4-5} 
-unidentified & recommendation &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & environment &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & periphery &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & close &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
-environmental & transportation &  & train & environmental \\ \cline{1-2} \cline{4-5} 
-environmental & nearby &  & free & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & subway &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[hbp]
-\centering
-\caption{Hotel attribute types for the top 10 dissatisfaction keywords}
-\label{tab:man_env_neg}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{lll|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & dirty & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & stain & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
- &  &  & curtain & managerial \\ \cline{4-5} 
- &  &  & paper & managerial \\ \cline{4-5} 
- &  &  & renovation & managerial \\ \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
-\end{document}

### 2020-09-27 2_revisions/V2-1_ITT_first revision_Nonaka revision/tobaco2.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V2-1_First revision/itt-emotion-manuscript_V2-1.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-
-% For the ORCID icon
-\usepackage{scalerel}
-\usepackage{tikz}
-\usetikzlibrary{svg.path}
-
-\definecolor{orcidlogocol}{HTML}{A6CE39}
-\tikzset{
-  orcidlogo/.pic={
-    \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-    \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                 svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                 svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-  }
-}
-
-\newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-\begin{tikzpicture}[yscale=-1,transform shape]
-\pic{orcidlogo};
-\end{tikzpicture}
-}{|}}}}
-
-\usepackage{lineno, hyperref}
-% \usepackage[hyperfootnotes=false]{hyperref}
-\usepackage{array, pbox}
-\usepackage{mathtools}
-\usepackage{caption}
-\usepackage{graphicx}
-
-% To use chinese characters
-\usepackage{CJKutf8}
-
-% To add an appendix page
-\usepackage[page, title]{appendix}
-
-% Stick footnotes to bottom of the page
-\usepackage[bottom]{footmisc}
-
-% To insert commas into large numbers automatically
-\usepackage{siunitx}
-
-% To add hypothesis theorem
-\usepackage{ntheorem}
-\theoremseparator{:}
-\newtheorem{hyp}{Hypothesis}
-
-% To add subhypothesis theorems
-\makeatletter
-\newcounter{subhyp} 
-\let\savedc@hyp\c@hyp
-\newenvironment{subhyp}
- {%
-  \setcounter{subhyp}{0}%
-  \stepcounter{hyp}%
-  \edef\saved@hyp{\thehyp}% Save the current value of hyp
-  \let\c@hyp\c@subhyp     % Now hyp is subhyp
-  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
- }
- {}
-\newcommand{\normhyp}{%
-  \let\c@hyp\savedc@hyp % revert to the old one
-  \renewcommand\thehyp{\arabic{hyp}}%
-} 
-\makeatother
-
-% To add the envelope symbol in Corresponding Author using % \Letter
-\usepackage{marvosym}
-
-% to add superscripts to mark the institute of authors
-% patch \maketitle:
-\newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-\newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-% For table formatting
-\usepackage{multirow}
-\usepackage[normalem]{ulem}
-\useunder{\uline}{\ul}{}
-
-% For landscape tables
-\usepackage{lscape}
-
-\modulolinenumbers[5]
-
-\journalname{Information Technology \& Tourism}
-
-\bibliographystyle{spbasic}
-
-\begin{document}
-
-\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}
-
-\titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}
-
-\author{REDACTED
-}
-
-\authorrunning{REDACTED}
-
-\institute{REDACTED
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-
-The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
-Recent years show a steady increase in international tourists coming to Japan.
-Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world.
-Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors.
-Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then measured the similarity value for the frequency in ranked keyword lists using the Rank-biased Overlap measure.
-It is used for top-weighted ranked lists with different elements and lengths.
-We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-\keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite{al2015characteristics}.
-Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.
-
-In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and the whole of Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-From that, the number of researchers interested in this phenomenon has been increasing as well.
-\cite[][]{sun2017}.
-With these and other multicultural tourist populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Hotel management, therefore, needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
-
-With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
-This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}} and Western English-speaking tourists populations posting in \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}}.
-With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past.
-In order to do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
-We then perform a statistical extraction of the topics that concerns the customers of each population the most.
-
-\section{Research objective}\label{research_objective}
-
-This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine a quantitative measure of similarity between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure, both in general and only considering their common factors.
-More importantly, we also intend to measure how managerial and environmental attributes influence much satisfaction and dissatisfaction of both customer groups.
-We define managerial attributes as those internal and modifiable to the hotel.
-In contrast, environmental attributes are external and unmodifiable, short of moving the hotel building in its entirety.
-
-Our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-The short scope of those studies means that cultural and language differences often cannot be observed in a single study.
-
-Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between cultures.
-These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-\subsection{Japanese hospitality: \textit{Omotenashi}}\label{theory_omotenashi}
-
-The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite{ikeda2013omotenashi, al2015characteristics}.
-There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition.
-In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite{Kuboyama2020}.
-
-It stands to reason that this high level of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in Japan, every business has this high level of hospitality, in differing levels of success.
-A simple convenience shop around the corner could be more hospitable if hotel management falls behind.
-Businesses have to strive to be the most hospitable, and hotels are not allowed to lag in this competition.
-Because of this, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
-Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.
-
-Therefore we pose two hypotheses for our study:
-
-\begin{subhyp}
-\begin{hyp}
-\label{hyp:omotenashi_zh}
-Chinese tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
-\end{hyp}
-
-\begin{hyp}
-\label{hyp:omotenashi_en}
-Western tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
-\end{hyp}
-
-However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different reaction.
-While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above hypothesis:
-
-\begin{hyp}
-\label{hyp:omotenashi_both}
-Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service.
-\end{hyp}
-\end{subhyp}
-
-\subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}
-
-Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Western and Chinese customers can then have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-These different expectations, in turn, will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
-
-Therefore we propose:
-
-\begin{subhyp}
-\begin{hyp}
-\label{hyp:diff_all}
-Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
-\end{hyp}
-
-Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-So we must measure their differences or similarities at their common ground as well.
-For this, we prepare the following hypothesis:
-
-\begin{hyp}
-\label{hyp:diff_com}
-The common factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
-\end{hyp}
-\end{subhyp}
-
-Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The use of the Likert scale leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, little focus is put on factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
-
-This leads to the next hypothesis:
-
-\begin{hyp}
-\label{hyp:man_env}
-Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
-\end{hyp}
-
-The resulting proportions of managerial attributes to environmental attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-\subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-% Asians vs. Western behavior
-In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}.
-This increase resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
-One example is \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money.
-Another is  \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
-Another example is \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
-
-One thing to note with the above cross-culture analyses is that they were performed before the year 2000.
-The current Chinese economy boom is making an increase in the influx of tourists.
-However, that boom could have created a difference in the expectations of tourists.
-In turn, that boom could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-
-More recent studies have surfaced as well.
-A cross-country study \cite{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, it appears that U.S.A.
-customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-These last three articles focus on U.S.A.
-culture, while our study focuses on Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite{FRANCESCO201924} has the context of tourists from 3 countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
-and Chinese tourists eating in 3 countries in Europe, and the third analyzing reviews of restaurants in Bejing.
-Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall?
-Our study measures this at a large scale across different hotels in Japan.
-
-% Universal behavior
-Other studies, perhaps recognizing that samples being comprised of people from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors wasn't performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-% Western behavior 
-Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-% Chinese behavior
-Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-% Studies are not universal.
-Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires, as well as the destinations; the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, the definition of each factor is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives an advantage to our study compared to others with smaller samples.
-Besides, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-% Reviewer comparison table
-Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite{bauer1993changing}, tourist motivation \cite{kim2000}, and closer to our study, satisfaction levels \cite{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924, JIA2020104071, HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its leading rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered as excellent.
-The number of samples in other text-mining studies is also smaller to ours in comparison.
-Apart from that, every study has a different text mining method.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-% \usepackage{lscape}
-\begin{landscape}
-\begin{table}[p]
-\centering
-\caption{Comparison between cross-culture or cross-country previous studies and our study}
-\label{tab:lit-rev}
-\resizebox{\linewidth}{!}{%
-\begin{tabular}{l|l|l|l|l|l|l|l|}
-\cline{2-8}
- & \textbf{Bauer et.al (1993)} & \textbf{\begin{tabular}[c]{@{}l@{}}Choi and\\ Chu (2000)\end{tabular}} & \textbf{Kim and Lee (2000)} & \textbf{Huang (2017)} & \textbf{\begin{tabular}[c]{@{}l@{}}Francesco and\\ Roberta (2019)\end{tabular}} & \textbf{Jia (2020)} & \textbf{Our study} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Comparison subjects}} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} & \begin{tabular}[c]{@{}l@{}}Anglo-Americans\\ vs \\ Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ English-speakers\end{tabular} & \begin{tabular}[c]{@{}l@{}}USA\\ vs\\ China\\ vs\\ Italy\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ US tourists\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Study topic}} & Changes in demand & Satisfaction Levels & Tourist Motivation & \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} & \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} & \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and \\ Dissatisfaction\end{tabular}} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Geographical focus}} & Asia Pacific region & Hong Kong & Global & Beijing & Multi-national & Multi-national & \textbf{Japan} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Industry}} & Hotels & Hotels & Tourism & \begin{tabular}[c]{@{}l@{}}Restaurant \\ (Beijing Roast Duck)\end{tabular} & Hotels & Restaurants & Hotels \\ \hline
-\multicolumn{1}{|l|}{\textbf{Study subjects}} & Hotel managers & Hotel customers & \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Sample method}} & surveys & surveys & survey & text mining & text mining & text mining & text mining \\ \hline
-\multicolumn{1}{|l|}{\textbf{Number of samples}} & 185 surveys & 540 surveys & \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}9000 reviews \\ (3000 per country)\end{tabular} & \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}91,172 reviews\\ (49,561 Chinese)\\ (41,611 English)\end{tabular}} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Study method}} & statistics & VARIMAX & MANOVA & \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} & Text Link Analysis & \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}SVM and \\ Rank-biased overlap\end{tabular}} \\ \hline
-\multicolumn{1}{|l|}{\textbf{Subject nationality}} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Fiji, \\ Hong Kong, \\ Indonesia, \\ Malaysia, \\ Singapore, \\ Taiwan, Guam, \\ Tahiti, Thailand\\ \\ Westerners: \\ Australia, \\ New Zealand\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Taiwan, \\ Japan,\\ South Korea, \\ South-East Asia\\ \\ Westerners: \\ North America,\\ Europe, Australia, \\ New Zealand\end{tabular} & USA, Japan & \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., USA, Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} & USA, China, Italy & USA, China & \begin{tabular}[c]{@{}l@{}}Chinese-speakers: \\ China\\ \\ English speakers:\\ (U.K., USA, \\ Australia,  \\ New Zealand, \\ Canada,  Ireland)\end{tabular} \\ \hline
-\end{tabular}%
-}
-\end{table}
-\end{landscape}
-
-\subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-% Explain the discovery of theory inside the data
-In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist that can connect to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-% Text mining 
-Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-% Sentiment Analysis
-More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.
-
-% Machine Learning
-The algorithm used for sentiment analysis in our study is called a Support Vector Machine.
-It is a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its conclusions on its own.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on the prediction of new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction, and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus our study is a data mining experiment based on machine learning.
-
-% Data exploration
-Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that because it has no intervention from the researchers in making questionnaires, it can have different results from anything that the researchers could expect.
-These qualities determine why, much like actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about where to find knowledge, and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
-
-In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect that, because of the lack of questionnaire design and users' freedom to record their pleasures and grievances, we may discover patterns that researchers previously noticed.
-
-\section{Methodology}\label{method}
-
-We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that would contribute the most to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized SVM.
-We then observed the weight values of each keyword in the machine.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review.
-We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}.
-Finally, we used this ranking in frequency to perform a Rank-biased overlap test and make observations for the hypothesis testing.
-
-\begin{figure}[bp]
-\centering
-\includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
-\caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-\label{fig:method-overview}
-\end{figure}
-
-\subsection{Data collection}\label{datacollection}
-
-In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580} and that the overlapping date range for reviews was from July 2014 to July 2017.
-We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.
-
-We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-\subsection{Text processing}\label{textprocessing}
-
-To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-\subsection{Sentiment analysis}\label{sentimentanalysis}
-
-The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
-Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[hbp]
-\centering
-\caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-\label{tab:svm_f1_zh}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
-\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[h] \centering
-\caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-\label{tab:svm_f1_en}
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
-\begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
-\end{tabular}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[hbp]
-\centering
-\caption{Examples of positive and negative sentences used for training SVM}
-\label{tab:training_examples}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|c|l|}
-\hline
-\textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
-\multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good.
-\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
- &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
-\multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
- &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
- & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
- &  & A bit pricey though \\ \hline
-\end{tabular}%
-}
-\end{table}
-
-Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus.
-A word that is included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-An SVM is trained to classify data based on previously labeled data, generalizing features of the data by defining a separating (p-1)-dimensional hyperplane in a p-dimensional space in which each dimension is a feature of the data.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes the error of classification.
-
-In our study, we used the linear kernel of the SVM classification process, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a point of data, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the angle of the hyperplane.
-The bias coefficient \(b\) determines its position, as explained in section \ref{svmweightsanalysis}.
-
-\begin{equation}\label{eq:svm1}
-f(x) = w^\top x + b
-\end{equation}
-
-We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-After classification, our data contained \num[group-separator={,}]{91239} positive Chinese sentences, \num[group-separator={,}]{13837} negative Chinese sentences, \num[group-separator={,}]{167224} positive English sentences and \num[group-separator={,}]{184798} negative English sentences.
-
-\subsection{SVM weight analysis}\label{svmweightsanalysis}
-
-During the SVM learning algorithm, each data point that is classified incorrectly causes a change in the weight vector to classify new data correctly.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class in the classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-\begin{equation}\label{eq:svm_weight}
-w = \sum_{i=1}^N \alpha_i y_i x_i
-\end{equation}
-
-\subsection{Rank-biased Overlap}\label{rbo}
-
-In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\).
-However, the lists are not necessarily of the same length or necessarily have the same contents.
-They are also top-weighted (where the first rank is the most important to know, and are less and less important as the ranks continue).
-Therefore, we propose that it is necessary to use another measure of similarity.
-\cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement.
-It takes all of these factors into consideration when calculating a value from 0 to 1, where zero means completely different lists, and one means the two lists are an exact match.
-Because our Chinese keywords (their translations, at least) do not match our English keywords one to one, it is necessary to use this method.
-Webber's RBO produces three measurements: a minimum RBO, a residual RBO, and an extrapolated RBO.
-The residual RBO allows us to know the maximum RBO.
-In contrast, the extrapolated RBO is calculated by assuming the list would continue in the same pattern of similarity towards infinity.
-The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}).
-\(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists, and \(X\) is the overlap between the lists.
-The evaluation depth \(p\) can also be understood as \(1-p\) being the probability to stop looking at the next item in the list.
-The complete process is described at length by \cite{webber2010similarity}.
-
-\begin{equation}\label{eq:rbo_ext}
-RBO_{EXT}(S,T,p,k) = \frac{X_k}{k} \cdot p^k + \frac{1-p}{p} \sum_{d=1}^k{\frac{X_d}{d} \cdot p^d}
-\end{equation}
-
-\section{Data Analysis}\label{dataanalysis}
-
-\subsection{Frequent keywords and their SVC weight values}\label{svmresults}
-
-To understand the satisfaction and dissatisfaction factors of Chinese tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use, and their weight in the Support Vector Classifier (SVC).
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-The weight value allows us to observe the sentiment it relates to by its positive or negative sign.
-We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment.
-A positive weight means positive sentiment, and a negative weight signifies negative sentiment).
-
-We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
-This is shown in the Tables \ref{tab:pos_keys} for positive keywords and \ref{tab:neg_keys} for negative ones (however, the negative Chinese keyword list does not have more than seven keywords available).
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[h]
-\centering
-\caption{Top 10 positive keywords in positive sentences}
-\label{tab:pos_keys}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|l|c|c|l|l|c|c|}
-\cline{1-4} \cline{6-8}
-\multicolumn{4}{|c|}{\textbf{Positive Chinese Keywords}}                                             &                                & \multicolumn{3}{c|}{\textbf{Positive English Keywords}}                       \\ \cline{1-4} \cline{6-8}
-\textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 大 \end{CJK}             & big                                       & 10155              & 0.623               &                                & staff                              & 13583              & 0.537               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 干净 \end{CJK}            & clean                                     & 6918               & 0.638               &                                & location                           & 10127              & 0.842               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 交通 \end{CJK}            & transportation                            & 6765               & 0.586               &                                & clean                              & 7636               & 1.886               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 日本 \end{CJK}            & Japan                                     & 5889               & 0.495               &                                & helpful                            & 5271               & 1.999               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK}            & breakfast                                 & 5726               & 0.495               &                                & friendly                           & 5060               & 1.199               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 近 \end{CJK}             & close                                     & 5348               & 0.028               &                                & comfortable                        & 4948               & 1.724               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 地铁 \end{CJK}            & subway                                    & 4491               & 0.18                &                                & shopping                           & 4884               & 1.308               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 购物 \end{CJK}            & shopping                                  & 4206               & 0                   &                                & train                              & 4778               & 0                   \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 下次 \end{CJK}            & next time                                 & 3596               & 0.247               &                                & subway                             & 4405               & 1.951               \\ \cline{1-4} \cline{6-8}
-\begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK}            & recommend                                 & 3574               & 0.495               &                                & recommend                          & 3812               & 1.158               \\ \cline{1-4} \cline{6-8}
-\end{tabular}%
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[h]
-\centering
-\caption{Top 10 negative keywords in negative sentences}
-\label{tab:neg_keys}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{clccl|l|c|c|}
-\cline{1-4} \cline{6-8}
-\multicolumn{4}{|c|}{\textbf{Negative Chinese Keywords}}                                                                                                             & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{3}{c|}{\textbf{Negative English Keywords}}                       \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{Translation}} & \multicolumn{1}{c|}{\textbf{Frequency}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} }            & \multicolumn{1}{l|}{price}                & \multicolumn{1}{c|}{1908}               & \multicolumn{1}{c|}{-2}                  &                                & dated                              & 426                & 0                   \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} }            & \multicolumn{1}{l|}{Chinese language}     & \multicolumn{1}{c|}{744}                & \multicolumn{1}{c|}{-0.714}              &                                & working                            & 350                & -0.557              \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} }            & \multicolumn{1}{l|}{geography}            & \multicolumn{1}{c|}{710}                & \multicolumn{1}{c|}{-0.812}              &                                & pricey                             & 327                & -1.614              \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 距离 \end{CJK} }            & \multicolumn{1}{l|}{distance}             & \multicolumn{1}{c|}{440}                & \multicolumn{1}{c|}{0}                   &                                & slow                               & 306                & -1.281              \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 陈旧 \end{CJK} }            & \multicolumn{1}{l|}{old-fashioned}        & \multicolumn{1}{c|}{338}                & \multicolumn{1}{c|}{0}                   &                                & carpet                             & 224                & -0.507              \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 老   \end{CJK} }             & \multicolumn{1}{l|}{old}                  & \multicolumn{1}{c|}{323}                & \multicolumn{1}{c|}{0}                   &                                & cigarette                          & 220                & -0.435              \\ \cline{1-4} \cline{6-8}
-\multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 华人 \end{CJK} }            & \multicolumn{1}{l|}{Chinese person}       & \multicolumn{1}{c|}{16}                 & \multicolumn{1}{c|}{-0.5}                &                                & uncomfortable                      & 207                & -2.423              \\ \cline{1-4} \cline{6-8}
-                                                                         &                                           &                                         &                                          &                                & paper                              & 185                & -0.503              \\ \cline{6-8}
-                                                                         &                                           &                                         &                                          &                                & smallest                           & 168                & -1.035              \\ \cline{6-8}
-                                                                         &                                           &                                         &                                          &                                & dirty                              & 163                & -1.275              \\ \cline{6-8}
-\end{tabular}%
-}
-\end{table}
-
-\subsection{Rank-biased Overlap}\label{rboresults}
-
-In order to calculate the similarity between the ranked lists shown in Table \ref{tab:pos_keys}, and the lists in Table \ref{tab:neg_keys}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points.
-Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is ``pricey," while in the Chinese keywords it is translated as ``price," so we changed it to ``pricey" to match the English keywords.
-We did this change purely to overlap the most words possible, and so it could have been modified the other way around with the same effect.
-The results of these calculations are shown in Table \ref{tab:rbo}.
-In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5.
-The RBO measure can work regardless of the length of each list, so there was not a problem in its calculation.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[h]
-\centering
-\caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
-\label{tab:rbo}
-\begin{tabular}{|l|c|r|}
-\hline
-\multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
-\multirow{2}{*}{None}   & Satisfaction      & 0.217 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.137 \\ \hline
-\multirow{2}{*}{Top 20} & Satisfaction      & 0.216 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.132 \\ \hline
-\multirow{2}{*}{Top 10} & Satisfaction      & 0.257 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.128 \\ \hline
-\multirow{2}{*}{Top 5}  & Satisfaction      & 0.176 \\ \cline{2-3} 
-                        & Dissatisfaction   & 0.176 \\ \hline
-\end{tabular}
-\end{table}
-
-\section{Results}\label{results}
-
-\subsection{Experiment results and testing the hypotheses}
-
-From the observation of the top-ranking subjects for Chinese tourists, we can assert that keywords relating to service and staff friendliness are not on the top 10 satisfaction factors.
-Besides, there are complaints about a Chinese friendly environment.
-This makes our hypothesis \ref{hyp:omotenashi_zh} rejected.
-On the other hand, the word ``staff'' tops the list of satisfaction factors in English-written reviews, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-This confirms our hypothesis \ref{hyp:omotenashi_en}.
-Since we found that these two populations are different in their satisfaction with Japanese hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.
-
-The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.176 to 0.257 in satisfaction lists, and from 0.128 to 0.176 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)).
-This means that, while there is some similarity, the satisfaction and dissatisfaction factors are fundamentally different if we consider them as top-weighted; that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:diff_all}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.
-
-Both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness.
-In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-English-speaking tourists, on the other hand, value staff friendliness over room quality when considering their satisfaction.
-
-The lists for Chinese and English-speaking tourists are quite different.
-However, if we compare the lists, we find that ``clean", ``recommend," ``subway," ``shopping,"  and ``price" are shared factors to both customer groups.
-Their place in the ranked list is the same for most of them, and only ``shopping" and ``subway" are exchanged in priority.
-Furthermore, when arranging both lists by eliminating all unique elements, the lists become almost identical with an RBO of 0.906 for the top 20 and top 10 satisfaction keywords and 1.0 for the dissatisfaction lists.
-The lists become dissimilar when there is no cutoff point.
-However, it's still an RBO of 0.575 for the satisfaction list and 1.0 for the dissatisfaction list.
-This means hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), where we hypothesized shared aspects in both customer groups to be different in their priority.
-
-We also can observe some keywords that are not considered by their counterparts.
-For example, mainland Chinese tourists are very satisfied with breakfast inclusion.
-At the same time, English-speaking customers are satisfied with the staff and service.
-On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.
-
-We can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are managerial attributes internal to the hotel, that is, or environmental attributes external to it.
-We manually labeled the top keywords of each language into either managerial or environmental by considering how the word would be used when writing a review.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial.
-If the word is describing factors that are unchangeable by the staff or management, we consider them environmental.
-The interpretation of these keywords is shown in the Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-% \usepackage[normalem]{ulem}
-% \useunder{\uline}{\ul}{}
-\begin{table}[h]
-\centering
-\caption{Hotel attribute types for the top 10 satisfaction keywords}
-\label{tab:man_env_pos}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|l|l|l|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & clean &  & location & environmental \\ \cline{1-2} \cline{4-5} 
-environmental & transportation &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
-unidentified & Japan &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
-managerial & breakfast &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & close &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
-environmental & subway &  & shopping & environmental \\ \cline{1-2} \cline{4-5} 
-environmental & shopping &  & train & environmental \\ \cline{1-2} \cline{4-5} 
-unidentified & next time &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
-unidentified & recommend &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{graphicx}
-\begin{table}[h]
-\centering
-\caption{Hotel attribute types for the top 10 dissatisfaction keywords}
-\label{tab:man_env_neg}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{lll|r|r|}
-\cline{1-2} \cline{4-5}
-\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & dated & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & working & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
-\multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
- &  &  & paper & managerial \\ \cline{4-5} 
- &  &  & smallest & managerial \\ \cline{4-5} 
- &  &  & dirty & managerial \\ \cline{4-5} 
-\end{tabular}%
-}
-\end{table}
-
-For our purposes, hypothesis \ref{hyp:man_env} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel.
-This is confirmed for all but one list.
-The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial.
-However, this is only regarding the top 10 items on the list.
-Lower on the list, we can observe some environmental factors.
-We can see the summarized results in Table \ref{tab:hyp_man_env}.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-% \usepackage{graphicx}
-\begin{table}[h]
-\caption{Managerial and Environmental nature of the 10 most frequent keywords}
-\label{tab:hyp_man_env}
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{|c|c|r|r|r|}
-\hline
-\textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
-\multirow{2}{*}{Satisfaction} 
-    & Chinese speakers & 30\% & 40\% & 30\% \\ \cline{2-5} 
-    & English speakers & 50\% & 40\% & 10\% \\ \hline
-\multirow{2}{*}{Dissatisfaction} 
-    & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
-    & English speakers & 100\% & 0\% & 0\% \\ \hline
-\end{tabular}%
-}
-\end{table}
-
-\subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
-From inspecting random samples, we also find that this is mostly relating to the rooms.
-There are also many references to the public bathing facilities in the hotel.
-In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called \textit{onsen}.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most critical satisfaction factor for Chinese customers.
-However, the word ``big" is widespread in the language and could be used in different contexts to point out positive and negative aspects.
-Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word ``big" in Chinese.
-A team of Chinese speaking lab members then pointed out the usage of the word.
-Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities.
-
-One key component we found in Chinese customer satisfaction factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like “food” or “eating,” and in a lower ranking.
-In contrast, the word “breakfast” refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-A recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast.
-
-\subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-From the satisfaction factors of English-speaking tourists, we can see that at least three words relate to staff friendliness and services.
-The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the fourth and fifth place.
-Japanese high standards in hospitality very likely influenced this result.
-
-Aside from cleanliness, we can also observe the word ``working" is written higher on the list, as well as the word ``paper." We observed the samples, and it is often used with the expression ``paper-thin walls", which could mean the customers can easily hear their neighbors.
-Regarding the word ``working,'' we also took a sample of the texts to see its context.
-It seems to be related mostly to construction work near or at the facilities.
-Some cities in Japan (e.g., Osaka) are currently undergoing a large number of renovations, which are also extending to the hotel facilities.
-Customers staying in places in renovation or near a construction site can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
-
-An interesting detail of the keyword ranking is that the word ``comfortable" is high on the list of satisfaction factors and ``uncomfortable" high on the dissatisfaction factors.
-It seems that in general, western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
 \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
@@
 After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all kinds of customers.
-
-\subsection{Location, location, location}\label{disc:location}
-
-The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-While it was not the priority for either of them, we can assert that the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is an external factor to the management of the hotel, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price.
-This means that for tourists, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity.
-
-Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, and so on.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-The results indicate that our hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
-Furthermore, they indicate that, in the context of Japanese hospitality, only Western customers show satisfaction from staff and service amongst their top detected factors.
-Below we explore the possible interactions with \textit{Omotenashi}, what the differences between Chinese and Western tourists were, what is the possible cause for them, and what they imply for the industry.
-We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
-
-\subsection{Western and Chinese tourists in the \textit{Omotenashi} environment}\label{disc:omotenashi}
-
-To this day, scholars continue to correct our historical bias towards the west.
-In this time, studies have determined that different cultural backgrounds lead to different expectations, which in turn influence the satisfaction of tourists.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{Omotenashi}, excels, and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-Our results indicate that Western tourists are the most satisfied with friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses and can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in the satisfaction of Western tourists.
-
-However, we can see from the rest of the western keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench, and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-However, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-We could theorize that despite being presented with high standard hospitality, it is ignored.
-It could be that their culture does not hold the expectation initially.
-That is, when an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly, while perhaps the hospitality grade in Japan is not fulfilling a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-
-However, another possibility presents itself when we observe the Chinese tourists' dissatisfaction factors.
-Chinese tourists may have expectations about the treatment towards the Chinese visitors that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite{heinrich2012making, coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied, since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological place.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in \textit{Omotenashi} does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-\subsection{Managerial vs. Environmental satisfaction}\label{disc:man_env}
-
-As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
-Examples of managerial attributes include staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}.
-However, external or environmental attributes, such as the location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the importance of those environmental or managerial attributes.
-
-From Table \ref{tab:hyp_man_env} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 40\% of keywords used by Chinese tourists are of an environmental nature (namely ``transportation", ``close", ``subway", and ``shopping"), while a lower 30\% is managerial in nature (and an undefined 30\%).
-However, two of these managerial words are all concentrated at the top of the list (``big", ``clean").
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others' cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-The dissatisfaction list for Western tourists could indicate that they perceive the rooms or bathtubs as small compared to Chinese tourists that praise them.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``environment" as well.
-
-In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean," ``helpful," and ``friendly," to name a few.
-English-speaking customers also have managerial attributes at the very top of their list, except for the environmental nature of the location of the hotel.
-If one considers both Chinese and Western tourists' satisfaction, a hotel can improve in ways that will attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with environmental attributes overall, hotels would have to compete solely on their location.
-
-For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, which could impact this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1  meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
-Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly.
-However, if hotels want to attract more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.
-
-Now, a point of interest in this study is the difference in how managerial and environmental factors concern Chinese and Western tourists.
-We can see that for Chinese customers, while the top positive keyword is managerial, the size of a room is hardly modifiable once the hotel's construction is complete.
-The second keyword follows as a managerial factor as well.
-Except, this time, hotel management can readily improve the cleanliness of their hotel.
-The rest of the positive keywords, however, are either undefined or environmental.
-Once the location and construction of the hotel are set, not much can be done to satisfy a Chinese tourist further.
-On the other hand, one can turn the dissatisfaction factors into satisfaction by focusing on those for improvement.
-As mentioned before, Chinese language availability is another managerial attribute that can be improved with investment in staff and training.
-
-Western tourists, on the other hand, are all around both satisfied and dissatisfied with mostly managerial factors, with a 50\% of the top 10 satisfaction factors and a 100\% of the top 10 dissatisfaction factors coming from managerial attributes.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts, and as such, present a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite{choi2000}.
-With bigger returns on managerial improvements, it seems like investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on environmental attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of managerial or environmental attributes.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite{gao2017chinese}.
-However, one could argue that there is a Chinese cultural attribute that emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-
-\subsection{Implications for hotel managers}\label{disc:implications}
-
-Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-Chinese tourists are not experiencing the best that \textit{Omotenashi} has to offer.
-Either they do not get much satisfaction from hospitality or feel that basic language and communication needs are not being met.
-On the other hand, Western tourists are elated with Japanese hospitality.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high standards in comfort, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free.
-
-Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after plans to make new subway lines are made.
-
-It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase.
-
-\section{Limitations and Future Work}\label{limitations}
-
-This paper is not without its limitations.
-We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context that these words were being used in by taking samples and observing them manually.
-However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database.
-Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, because of the nature of the data collected, further typology analysis could not be made (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
-Another point of interest in the future of this study is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels.
-We extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences to find the differences between Chinese and Western tourists.
-
-In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction.
-As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected.
-Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}.
-One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-
-We obtained values ranging from 0.176 to 0.257 in satisfaction lists and from 0.128 to 0.176 in dissatisfaction lists at different cutoff points.
-These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}.
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers.
-We found that from the four words that were common amongst both groups (``clean", ``recommend," ``subway," and ``price").
-When these shared terms were isolated, both lists were almost identical at the cutoff point of 20 words.
-This resulted in an RBO ranging from 0.906 to 1.0.
-This means our hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
-
-Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel.
-Managerial attributes are those that they can be changed via managerial decisions without relocating.
-On the other hand, environmental attributes are things like location, closeness to shops, or public transport.
-We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:man_env}.
-We also found that most of the Western customer satisfaction (50\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel.
-
-In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords).
-In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%).
-For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental.
-We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies.
-One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.
-With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
-
-\begin{acknowledgements}
-
-REDACTED
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
-\end{document}

### 2020-09-27 2_revisions/V3_ITT_second revision/itt-emotion_V2-1.tex
First data commit: V2-1, before second review

--- 2020-09-27 0_manuscript/V2-1_First revision/itt-emotion-manuscript_V2-1.tex
@@
 
-\author{REDACTED
+\author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
+        Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
+        Hirofumi Nonaka                                                 \protect\affmark[1] \and
+        Toru Hiraoka                                                    \protect\affmark[2]
 }
 
-\authorrunning{REDACTED}
-
-\institute{REDACTED
+\authorrunning{E. Alemán Carreón et al.}
+
+\institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
+            \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
+            % Corresponding Author %  \\
+            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+        \and
+            \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{mendoza.espana@gmail.com}
+        \and
+            \hspace*{1em} Hirofumi Nonaka \at
+            % Nagaoka University of Technology, Nagaoka, Japan \\
+            \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
+        \and
+            \hspace*{1em} Toru Hiraoka \at
+            % University of Nagasaki, Nagasaki, Japan \\
+            \hspace*{1em} \email{hiraoka@sun.ac.jp}
+        \and
+            \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
+        \and
+            \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
 }
@@
 
-REDACTED
+During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the interpretation of the data.
+We would like to show gratitude to Mr.
+Liangyuan Zhou, Ms.
+Min Fan, and Ms.
+Eerdengqiqige for this.
+
+We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+\medskip
+
+Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+\medskip
+
+Conflict of interest: none
 

### 2020-09-27 2_revisions/clean_latex_secondary_files.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+find . -name '*.blg' -type f -delete
+find . -name '*.bbl' -type f -delete
+find . -name '*.aux' -type f -delete
+find . -name '*.log' -type f -delete
+find . -name '*.thm' -type f -delete
+find . -name '*.out' -type f -delete
+find . -name '*.spl' -type f -delete
+find . -name '*.gz' -type f -delete

### 2020-09-27 1_manuscript/itt-emotion.tex
Removed footnotes, fork for latexdiff, indent party

--- 2020-09-27 2_revisions/V3_ITT_second revision/itt-emotion_V2-1.tex
@@
   \usepackage{lineno, hyperref}
-% \usepackage[hyperfootnotes=false]{hyperref}
   \usepackage{array, pbox}
@@
   \usepackage[page, title]{appendix}
-
-% Stick footnotes to bottom of the page
-\usepackage[bottom]{footmisc}
 
@@
 
-In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip}\footnote{\label{ctrip}Ctrip: \href {www.ctrip.com/}{\path{www.ctrip.com/}}} and Western English-speaking tourists populations posting in \textit{TripAdvisor}\footnote{\label{tripadvisor}TripAdvisor: \href {www.tripadvisor.com/}{\path{www.tripadvisor.com/}}}.
+  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
 With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past.

### 2020-09-27 1_manuscript/latexcompile.sh

@@ -1,0 +1,50 @@
+#!/bin/bash
+# First install this file
+# https://github.com/nhoffman/argparse-bash
+source $(dirname $0)/argparse.bash || exit 1
+argparse "$@" <<EOF || exit 1
+parser.add_argument('infile')
+parser.add_argument('-v', '--view', action='store_true',
+                    default=False, help='Open the PDF at end of compile. [default %(default)s]')
+parser.add_argument('-c', '--clean', action='store_true',
+                    default=False, help='Clean latex secondary files [default %(default)s]')
+parser.add_argument('-p', '--nobib', action='store_true',
+                    default=False, help='Pdflatex alone as if bibtex already ran previously [default %(default)s]')
+parser.add_argument('-d', '--onlyclean', action='store_true',
+                    default=False, help='Only clean after previous compiles [default %(default)s]')
+EOF
+DOCNAME="${INFILE%.*}"
+if [[ $ONLYCLEAN ]];
+then
+    echo "Removing secondary files, no compile made"
+    rm *.blg *.bbl *.aux *.log *.thm *.out
+else
+    if [[ $NOBIB ]];
+    then
+        pdflatex $DOCNAME.tex
+        if [ $? -ne 0 ]; then
+            echo "Compilation error. Check log."
+            exit 1
+        fi
+        echo "Skipping Bibtex from compile."
+    else
+        echo "Removing secondary files, starting from scratch"
+        rm *.blg *.bbl *.aux *.log *.thm *.out
+        pdflatex $DOCNAME.tex
+        if [ $? -ne 0 ]; then
+            echo "Compilation error. Check log."
+            exit 1
+        fi
+        bibtex $DOCNAME
+        pdflatex $DOCNAME.tex
+        pdflatex $DOCNAME.tex
+    fi
+    if [[ $CLEAN ]]; then
+    echo "Removing secondary files"
+    rm *.blg *.bbl *.aux *.log *.thm *.out
+    fi
+fi
+if [[ $VIEW ]]; then
+    open $DOCNAME.pdf
+fi
+exit 0

### 2020-09-27 1_manuscript/itt-emotion.tex
Restored from sep 24 2020 morning

@@
   \usepackage{caption}
+  \usepackage{subcaption}
   \usepackage{graphicx}
@@
 
-  % To add hypothesis theorem
+  % To add research questions
   \usepackage{ntheorem}
   \theoremseparator{:}
-  \newtheorem{hyp}{Hypothesis}
-
-  % To add subhypothesis theorems
+  \newtheorem{rsq}{Research Question}
+
+  % To add subrsq theorems
   \makeatletter
-  \newcounter{subhyp} 
-  \let\savedc@hyp\c@hyp
-  \newenvironment{subhyp}
+  \newcounter{subrsq} 
+  \let\savedc@rsq\c@rsq
+  \newenvironment{subrsq}
    {%
-    \setcounter{subhyp}{0}%
-    \stepcounter{hyp}%
-    \edef\saved@hyp{\thehyp}% Save the current value of hyp
-    \let\c@hyp\c@subhyp     % Now hyp is subhyp
-    \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
+    \setcounter{subrsq}{0}%
+    \stepcounter{rsq}%
+    \edef\saved@rsq{\thersq}% Save the current value of rsq
+    \let\c@rsq\c@subrsq     % Now rsq is subrsq
+    \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
    }
    {}
-  \newcommand{\normhyp}{%
-    \let\c@hyp\savedc@hyp % revert to the old one
-    \renewcommand\thehyp{\arabic{hyp}}%
+  \newcommand{\normrsq}{%
+    \let\c@rsq\savedc@rsq % revert to the old one
+    \renewcommand\thersq{\arabic{rsq}}%
   } 
@@
 
-\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}
+\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures}
 
@@
 
-  The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
+  % The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
 Recent years show a steady increase in international tourists coming to Japan.
@@
 Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then measured the similarity value for the frequency in ranked keyword lists using the Rank-biased Overlap measure.
-It is used for top-weighted ranked lists with different elements and lengths.
 We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior.
@@
   This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine a quantitative measure of similarity between the satisfaction and dissatisfaction factors of both customer groups using a Rank-biased Overlap measure, both in general and only considering their common factors.
-More importantly, we also intend to measure how managerial and environmental attributes influence much satisfaction and dissatisfaction of both customer groups.
-We define managerial attributes as those internal and modifiable to the hotel.
-In contrast, environmental attributes are external and unmodifiable, short of moving the hotel building in its entirety.
+We aim to contrast the satisfaction and dissatisfaction factors of both customer groups using natural language processing to study commonly used word pairings.
+More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups.
+We define hard attributes as those that are difficult to change by a hotel management without investing in infrastructure or real estate.
+In contrast, soft attributes are easily modifiable by improvements in management.
 
@@
     The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite{ikeda2013omotenashi, al2015characteristics}.
+However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
 There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
 Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite{aishima2015origin}.
+However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
@@
 Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite{Kuboyama2020}.
+In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
 
@@
 
-    Therefore we pose two hypotheses for our study:
-
-    \begin{subhyp}
-    \begin{hyp}
-    \label{hyp:omotenashi_zh}
-    Chinese tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
-    \end{hyp}
-
-    \begin{hyp}
-    \label{hyp:omotenashi_en}
-    Western tourists are most satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service.
-    \end{hyp}
+    Therefore we pose a research question for our study:
+
+    \begin{subrsq}
+    \begin{rsq}
+    \label{rsq:omotenashi}
+    To what degree are Chinese and Western tourists satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service?
+    \end{rsq}
 
@@
 While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above hypothesis:
-
-    \begin{hyp}
-    \label{hyp:omotenashi_both}
-    Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service.
-    \end{hyp}
-    \end{subhyp}
+This point leads us to a derivative of the above research question:
+
+    \begin{rsq}
+    \label{rsq:omotenashi_both}
+    Do Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service?
+    \end{rsq}
+    \end{subrsq}
 
@@
 
-    Therefore we propose:
-
-    \begin{subhyp}
-    \begin{hyp}
-    \label{hyp:diff_all}
-    Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction.
-    \end{hyp}
-
     Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
@@
 So we must measure their differences or similarities at their common ground as well.
-For this, we prepare the following hypothesis:
-
-    \begin{hyp}
-    \label{hyp:diff_com}
-    The common factors identified for both Chinese and Western tourists will be placed at a different priority for each group.
-    \end{hyp}
-    \end{subhyp}
 
@@
 
-    Previous research has also focused on factors that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, little focus is put on factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
+    Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
+However, little focus is put on hard factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
 Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
 
-    This leads to the next hypothesis:
-
-    \begin{hyp}
-    \label{hyp:man_env}
-    Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
-    \end{hyp}
-
-    The resulting proportions of managerial attributes to environmental attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.
+    This leads to another research question:
+
+    \begin{rsq}
+    \label{rsq:hard_soft}
+    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel.
+    \end{rsq}
+
+    The resulting proportions of hard attributes to soft attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.
 
@@
 Another difference with our study is that of the context of the study.
-The first study \cite{FRANCESCO201924} has the context of tourists from 3 countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
-and Chinese tourists eating in 3 countries in Europe, and the third analyzing reviews of restaurants in Bejing.
+The first study \cite{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
+and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing.
 Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
@@
     \begin{landscape}
-    \begin{table}[p]
+    \begin{table}[htp]
     \centering
-    \caption{Comparison between cross-culture or cross-country previous studies and our study}
+    \caption{Comparison between cross-culture or cross-country previous studies and our study.}
     \label{tab:lit-rev}
@@
     \cline{2-8}
-     & \textbf{Bauer et.al (1993)} & \textbf{\begin{tabular}[c]{@{}l@{}}Choi and\\ Chu (2000)\end{tabular}} & \textbf{Kim and Lee (2000)} & \textbf{Huang (2017)} & \textbf{\begin{tabular}[c]{@{}l@{}}Francesco and\\ Roberta (2019)\end{tabular}} & \textbf{Jia (2020)} & \textbf{Our study} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Comparison subjects}} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} & \begin{tabular}[c]{@{}l@{}}Anglo-Americans\\ vs \\ Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ English-speakers\end{tabular} & \begin{tabular}[c]{@{}l@{}}USA\\ vs\\ China\\ vs\\ Italy\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese\\ vs\\ US tourists\end{tabular} & \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Study topic}} & Changes in demand & Satisfaction Levels & Tourist Motivation & \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} & \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} & \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and \\ Dissatisfaction\end{tabular}} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Geographical focus}} & Asia Pacific region & Hong Kong & Global & Beijing & Multi-national & Multi-national & \textbf{Japan} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Industry}} & Hotels & Hotels & Tourism & \begin{tabular}[c]{@{}l@{}}Restaurant \\ (Beijing Roast Duck)\end{tabular} & Hotels & Restaurants & Hotels \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Study subjects}} & Hotel managers & Hotel customers & \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Sample method}} & surveys & surveys & survey & text mining & text mining & text mining & text mining \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Number of samples}} & 185 surveys & 540 surveys & \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} & \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} & \begin{tabular}[c]{@{}l@{}}9000 reviews \\ (3000 per country)\end{tabular} & \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}91,172 reviews\\ (49,561 Chinese)\\ (41,611 English)\end{tabular}} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Study method}} & statistics & VARIMAX & MANOVA & \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} & Text Link Analysis & \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}SVM and \\ Rank-biased overlap\end{tabular}} \\ \hline
-    \multicolumn{1}{|l|}{\textbf{Subject nationality}} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Fiji, \\ Hong Kong, \\ Indonesia, \\ Malaysia, \\ Singapore, \\ Taiwan, Guam, \\ Tahiti, Thailand\\ \\ Westerners: \\ Australia, \\ New Zealand\end{tabular} & \begin{tabular}[c]{@{}l@{}}Asians: \\ China, \\ Taiwan, \\ Japan,\\ South Korea, \\ South-East Asia\\ \\ Westerners: \\ North America,\\ Europe, Australia, \\ New Zealand\end{tabular} & USA, Japan & \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., USA, Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} & USA, China, Italy & USA, China & \begin{tabular}[c]{@{}l@{}}Chinese-speakers: \\ China\\ \\ English speakers:\\ (U.K., USA, \\ Australia,  \\ New Zealand, \\ Canada,  Ireland)\end{tabular} \\ \hline
+    \textbf{} &
+      \textbf{Bauer et.al (1993)} &
+      \textbf{Choi and Chu (2000)} &
+      \textbf{Kim and Lee (2000)} &
+      \textbf{Huang (2017)} &
+      \textbf{Francesco and Roberta (2019)} &
+      \textbf{Jia (2020)} &
+      \textbf{Our study} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
+      \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Study topic}} &
+      Changes in demand &
+      Satisfaction Levels &
+      Tourist Motivation &
+      \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
+      \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
+      Asia Pacific region &
+      Hong Kong &
+      Global &
+      Beijing &
+      Multi-national &
+      Multi-national &
+      \textbf{Japan} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Industry}} &
+      Hotels &
+      Hotels &
+      Tourism &
+      Restaurant (Beijing Roast Duck) &
+      Hotels &
+      Restaurants &
+      Hotels \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Study subjects}} &
+      Hotel managers &
+      Hotel customers &
+      \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Sample method}} &
+      surveys &
+      surveys &
+      survey &
+      text mining &
+      text mining &
+      text mining &
+      text mining \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Number of samples}} &
+      185 surveys &
+      540 surveys &
+      \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
+      9000 reviews (3000 per country) &
+      \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
+      \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Study method}} &
+      statistics &
+      VARIMAX &
+      MANOVA &
+      \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
+      Text Link Analysis &
+      \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
+      \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
+    \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
+      \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
+      \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
+      USA, Japan &
+      \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
+      USA, China, Italy &
+      USA, China &
+      \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
     \end{tabular}%
@@
 These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized SVM.
-We then observed the weight values of each keyword in the machine.
+We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
+We then applied a dependency parsing to the reviews, as well as a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
+We split the dataset in price ranges to observe the satisfaction factors and their differences between different lower class hotels and higher class hotels.
 We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review.
-We show an overview of this methodology in Figure \ref{fig:method-overview} \cite[][]{Aleman2018ICAROB}.
-Finally, we used this ranking in frequency to perform a Rank-biased overlap test and make observations for the hypothesis testing.
+We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
+Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel, meaning whether a hotel management can easily change those attributes, or if they are difficult to change without investing in infrastructure or real estate.
 
@@
   \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
+  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
   \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
@@
 We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580} and that the overlapping date range for reviews was from July 2014 to July 2017.
-We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.
-
+In addition, we selected only the hotels that had a pricing information available.
+We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
+The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel.
+Regardless of the reason, the highest priced room can be an indicator of the class of hotel indirectly, which can give us an insight into the kind of service that is offered.
+After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
+The overlapping date range for reviews was from July 2014 to July 2017.
+Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
 We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
 
+    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
+Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
+We therefore made observations on the distribution of pricing in the hotels of our database and binned the data by price ranges, decided by consideration of objective of stay.
+We show these distributions in Figure \ref{fig:price_dist}.
+The structure of the data after division by price is shown in Table \ref{tab:exp_notes}, which also includes the results of emotional classification after application of our SVC, as explained in \ref{sentimentanalysis}.
+
+    \begin{figure}[h]
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
+            \caption{50 equal lenght bins}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
+            \caption{manually set 9 price ranges}
+        \end{subfigure}
+    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
+    \label{fig:price_dist}
+    \end{figure}
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    % \usepackage{graphicx}
+    \begin{table}[ht]
+      \centering
+      \caption{Collected data and structure after price range categorizing.}
+      \label{tab:exp_notes}
+      \resizebox{\textwidth}{!}{%
+      \begin{tabular}{|l|l|r|r|}
+        \hline
+        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
+        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
+                                                   & Reviews            & 48,070  & 41,137  \\
+                                                   & Sentences          & 101,963 & 348,039 \\
+                                                   & Positive sentences & 88,543  & 165,308 \\
+                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
+        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
+                                                   & Reviews            & 0       & 0       \\ \hline
+        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
+                                                   & Reviews            & 0       & 0       \\ \hline
+        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
+                                                   & Reviews            & 452     & 459     \\
+                                                   & Sentences          & 1,108   & 3,988   \\
+                                                   & Positive sentences & 924     & 1,875   \\
+                                                   & Negative sentences & 184     & 2,113   \\ \hline
+        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
+                                                   & Reviews            & 2,176   & 2,865   \\
+                                                   & Sentences          & 4,240   & 24,107  \\
+                                                   & Positive sentences & 3,566   & 11,619  \\
+                                                   & Negative sentences & 674     & 12,488  \\ \hline
+        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
+                                                   & Reviews            & 7,043   & 4,384   \\
+                                                   & Sentences          & 14,726  & 37,342  \\
+                                                   & Positive sentences & 12,775  & 17,449  \\
+                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
+        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
+                                                   & Reviews            & 11,845  & 13,772  \\
+                                                   & Sentences          & 24,413  & 115,830 \\
+                                                   & Positive sentences & 21,068  & 55,381  \\
+                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
+        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
+                                                   & Reviews            & 8,283   & 7,001   \\
+                                                   & Sentences          & 17,939  & 58,409  \\
+                                                   & Positive sentences & 15,642  & 28,493  \\
+                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
+        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
+                                                   & Reviews            & 16,670  & 9,646   \\
+                                                   & Sentences          & 36,255  & 81,940  \\
+                                                   & Positive sentences & 31,638  & 38,217  \\
+                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
+        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
+                                                   & Reviews            & 1,601   & 3,010   \\
+                                                   & Sentences          & 3,282   & 26,423  \\
+                                                   & Positive sentences & 2,930   & 12,274  \\
+                                                   & Negative sentences & 352     & 14,149  \\ \hline
+        \end{tabular}%
+      }
+    \end{table}
   \subsection{Text processing}\label{textprocessing}
 
-    To parse Chinese words and separate them, we used the Stanford Word Segmenter \cite[][]{chang2008} program developed by the Stanford NLP Group\footnote{\label{stanfordnlp}The Natural Language Processing Group at Stanford University}.
+    Chinese text, unlike English, does not have spaces between each word to separate them.
+In addition, we also needed to analyze the grammatical relationship between words, be it English or Chinese, in order to understand connections between adjectives and the noun they refer to.
+For all these processes we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
+In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
 In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
@@
 For this purpose, we used the \textit{gensim} library with the English texts.
+
+    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections.
+We show an example of these dependencies in Figure \ref{fig:depparse}.
+In this study we use the Stanford NLP Dependency Parser, as described in \cite{chen-EMNLP:2014}.
+A list of dependencies used by this parser is detailed in \cite{marneffe_manning_2016_depparse_manual}.
+In our study, this step was necessary to extract adjective modifiers and their subject.
+We did that by parsing the entire database, and extracting instances of a few determined dependency codes.
+One of these dependency codes is `amod', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g.
+A big apple).
+The other dependency code we used was `nsubj', or nominal subject, which is the syntactic subject of a class.
+We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g.
+The apple is big).
+This dependency does not necessarily only include a combination of adjectives and nouns, but it can also be connected with copular verbs, nouns, or other adjectives.
+For this reason we saw necessary to also perform a Part of Speech (POS) tagging of these clauses.
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{depparse.png}
+    \caption{Example of dependency parsing.}
+    \label{fig:depparse}
+    \end{figure}
+
+    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
+An example is shown in Figure \ref{fig:postag}.
+A Part of Speech is a category of lexical items that serve similar grammatical purposes; for example, nouns, adjectives, verbs, conjunctions, and so on.
+In our study, we used the Stanford NLP POS tagger software, described in \cite{toutanova2000enriching, toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
+
+    \begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{postag.png}
+    \caption{Example of POS tagging with the Penn Treebank tags.}
+    \label{fig:postag}
+    \end{figure}
+
+    In this study we were interested in identifying combinations of adjectives, some verbs and nouns.
+We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
+For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
+What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
+We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
+We also show a detailed description of the tags we needed to filter, which we selected heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    \begin{table}[ht]
+      \centering
+      \caption{Target Parts of Speech for extraction and pairing.}
+      \label{tab:target_postag}
+      \begin{tabular}{|c|c|l|l|}
+        \hline
+        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
+        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
+                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
+                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
+                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
+        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
+                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
+                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
+                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
+                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
+                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
+                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
+                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
+                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
+      \end{tabular}
+    \end{table}
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    \begin{table}[ht]
+      \centering
+      \caption{Filtered out Parts of Speech to aid pairing.}
+      \label{tab:filter_postag}
+      \begin{tabular}{|c|l|l|l|}
+        \hline
+        \textbf{Language} &
+          \multicolumn{1}{c|}{\textbf{POS Tag}} &
+          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
+          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
+        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
+                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
+                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
+                                                & PU    & Punctuation        & .!?                                        \\ \hline
+        \multirow{5}{*}{Chinese filtered tags} &
+          DEV &
+          Particle &
+          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
+                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
+         &
+          M &
+          Measure word &
+          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
+         &
+          SP &
+          Sentence-final particle &
+          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
+                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
+        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
+                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
+                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
+      \end{tabular}
+    \end{table}
+
+    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers are referring to in their reviews, and with what frequency they use those pairings positively or negatively.
 
@@
     % \usepackage{graphicx}
-    \begin{table}[hbp]
+    \begin{table}[ht]
       \centering
@@
       \label{tab:svm_f1_zh}
+      % \resizebox{\textwidth}{!}{%
       \begin{tabular}{|l|l|l|l|l|}
         \hline
-    \textbf{Keyword List} & \textbf{\begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular}} & \textbf{C} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-    \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=2.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction \end{tabular} & 2.5 & 0.91 & 0.01 \\ \hline
-    \begin{tabular}[c]{@{}l@{}}Negative keywords \\ (\(\alpha'=3.75\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction \end{tabular} & 0.5 & 0.67 & 0.11 \\ \hline
-    \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=2.75, \(\alpha'\)=3.75)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{0.5} & \textbf{0.95} & \textbf{0.01} \\ \hline
+        \textbf{Keyword List} &
+          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
+          \textbf{C} &
+          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
+          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
+                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
+                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
+        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
+                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
         \end{tabular}
+        %
+        % }
     \end{table}
 
-    \begin{table}[h] \centering
+    % Please add the following required packages to your document preamble:
+    % \usepackage{graphicx}
+    \begin{table}[ht]
+      \centering
       \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
       \label{tab:svm_f1_en}
+      % \resizebox{\textwidth}{!}{%
       \begin{tabular}{|l|l|l|l|l|}
         \hline
-    Keyword List & \begin{tabular}[c]{@{}l@{}}Classifier \\ emotion\end{tabular} & C & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\mu\)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\(F_1\) \\ \(\sigma\)\end{tabular} \\ \hline
-    \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular} & 1.75 & 0.82 & 0.02 \\ \hline
-    \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular} & \begin{tabular}[c]{@{}l@{}}Dissatisfaction\end{tabular} & 3 & 0.80 & 0.03 \\ \hline
-    \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha\)=1.5, \(\alpha'\)=4.25)\end{tabular} & \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction\end{tabular}} & \textbf{2} & \textbf{0.83} & \textbf{0.02} \\ \hline
+        \textbf{Keyword List} &
+          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
+          \textbf{C} &
+          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
+          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
+                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
+                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
+        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
+                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
         \end{tabular}
+        %
+        % }
     \end{table}
@@
     % \useunder{\uline}{\ul}{}
-    \begin{table}[hbp]
+    \begin{table}[ht]
       \centering
-    \caption{Examples of positive and negative sentences used for training SVM}
+      \caption{Examples of positive and negative sentences used for training SVM.}
       \label{tab:training_examples}
@@
         \hline
-    \textbf{Language} & \textbf{Emotion} & \textbf{Sentences} \\ \hline
-    \multirow{4}{*}{Chinese} & \multirow{2}{*}{Positive} & \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn} 酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害 \end{CJK}\\ (translated as: ``The service of the hotel is very good.
-\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-     &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好 \end{CJK} \\ (translated as: ``There is a back door to the subway station very close to it.
+        \multicolumn{1}{|l|}{\textbf{Language}} &
+          \multicolumn{1}{l|}{\textbf{Emotion}} &
+          \textbf{Sentences} \\ \hline
+        \multirow{4}{*}{Chinese} &
+          \multirow{2}{*}{Positive} &
+          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
+         &
+           &
+          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
 \\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-     & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远 \end{CJK} \\ (translated as: ``The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-     &  & \begin{tabular}[c]{@{}l@{}} \begin{CJK}{UTF8}{gbsn} 唯一 不 足 是 价格 太高 \end{CJK} \\ (translated as: ``The only negative is that the price is too high.")\end{tabular} \\ \hline
-    \multirow{4}{*}{English} & \multirow{2}{*}{Positive} & It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-     &  & \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-     & \multirow{2}{*}{Negative} & \begin{tabular}[c]{@{}l@{}}The only downside: our room was labeled ``non-smoking" \\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-     &  & A bit pricey though \\ \hline
+         &
+          \multirow{2}{*}{Negative} &
+          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
+         &
+           &
+          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
+        \multirow{4}{*}{English} &
+          \multirow{2}{*}{Positive} &
+          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
+         &
+           &
+          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
+         &
+          \multirow{2}{*}{Negative} &
+          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
+         &
+           &
+          A bit pricey though \\ \hline
         \end{tabular}%
@@
 The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the angle of the hyperplane.
-The bias coefficient \(b\) determines its position, as explained in section \ref{svmweightsanalysis}.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-After classification, our data contained \num[group-separator={,}]{91239} positive Chinese sentences, \num[group-separator={,}]{13837} negative Chinese sentences, \num[group-separator={,}]{167224} positive English sentences and \num[group-separator={,}]{184798} negative English sentences.
-
-  \subsection{SVM weight analysis}\label{svmweightsanalysis}
+The bias coefficient \(b\) determines its position.
 
@@
 
+    \begin{equation}\label{eq:svm1}
+    f(x) = w^\top x + b
+    \end{equation}
+
     \begin{equation}\label{eq:svm_weight}
@@
 
-    \subsection{Rank-biased Overlap}\label{rbo}
-
-    In order to compare the similarity between two ranked lists, most cases would call to action a statistical measure such as Kendall's \(\tau\).
-However, the lists are not necessarily of the same length or necessarily have the same contents.
-They are also top-weighted (where the first rank is the most important to know, and are less and less important as the ranks continue).
-Therefore, we propose that it is necessary to use another measure of similarity.
-\cite{webber2010similarity} proposed a Rank-biased Overlap (RBO) measurement.
-It takes all of these factors into consideration when calculating a value from 0 to 1, where zero means completely different lists, and one means the two lists are an exact match.
-Because our Chinese keywords (their translations, at least) do not match our English keywords one to one, it is necessary to use this method.
-Webber's RBO produces three measurements: a minimum RBO, a residual RBO, and an extrapolated RBO.
-    The residual RBO allows us to know the maximum RBO.
-In contrast, the extrapolated RBO is calculated by assuming the list would continue in the same pattern of similarity towards infinity.
-The formula for the extrapolated RBO is shown in (\ref{eq:rbo_ext}).
-\(S\) and \(T\) are listings, \(d\) is their depth, \(k\) is their evaluation depth, \(p\) is a parameter that controls the top-weightedness of the lists, and \(X\) is the overlap between the lists.
-The evaluation depth \(p\) can also be understood as \(1-p\) being the probability to stop looking at the next item in the list.
-The complete process is described at length by \cite{webber2010similarity}.
-
-    \begin{equation}\label{eq:rbo_ext}
-    RBO_{EXT}(S,T,p,k) = \frac{X_k}{k} \cdot p^k + \frac{1-p}{p} \sum_{d=1}^k{\frac{X_d}{d} \cdot p^d}
-    \end{equation}
+    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
+The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
+We applied this SVC to classify the rest of our data collected.
+Subsequently, the positive and negative sentences counts shown in Table \ref{tab:exp_notes} are the result of applying our SVC for classification.
 
@@
 
-  \subsection{Frequent keywords and their SVC weight values}\label{svmresults}
-
-    To understand the satisfaction and dissatisfaction factors of Chinese tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use, and their weight in the Support Vector Classifier (SVC).
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and their SVC weight value.
+  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
+
+    To understand the satisfaction and dissatisfaction factors of Chinese tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use.
+Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and in each price range subsequently.
 The frequency of the keywords in the database shows the level of priority it has for customers.
-The weight value allows us to observe the sentiment it relates to by its positive or negative sign.
-We ranked the keywords by frequency, and use their SVC weight for analyzing the related sentiment.
-A positive weight means positive sentiment, and a negative weight signifies negative sentiment).
 
@@
 The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
-This is shown in the Tables \ref{tab:pos_keys} for positive keywords and \ref{tab:neg_keys} for negative ones (however, the negative Chinese keyword list does not have more than seven keywords available).
-
+We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
+For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}
+
+  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
+
+    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
     % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
     % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[h]
+    % \usepackage{lscape}
+    \begin{landscape}
+    \begin{table}[p]
       \centering
-    \caption{Top 10 positive keywords in positive sentences}
-    \label{tab:pos_keys}
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{|c|l|c|c|l|l|c|c|}
-    \cline{1-4} \cline{6-8}
-    \multicolumn{4}{|c|}{\textbf{Positive Chinese Keywords}}                                             &                                & \multicolumn{3}{c|}{\textbf{Positive English Keywords}}                       \\ \cline{1-4} \cline{6-8}
-    \textbf{Word} & \multicolumn{1}{c|}{\textbf{Translation}} & \textbf{Frequency} & \textbf{SVC Weight} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 大 \end{CJK}             & big                                       & 10155              & 0.623               &                                & staff                              & 13583              & 0.537               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 干净 \end{CJK}            & clean                                     & 6918               & 0.638               &                                & location                           & 10127              & 0.842               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 交通 \end{CJK}            & transportation                            & 6765               & 0.586               &                                & clean                              & 7636               & 1.886               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 日本 \end{CJK}            & Japan                                     & 5889               & 0.495               &                                & helpful                            & 5271               & 1.999               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 早餐 \end{CJK}            & breakfast                                 & 5726               & 0.495               &                                & friendly                           & 5060               & 1.199               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 近 \end{CJK}             & close                                     & 5348               & 0.028               &                                & comfortable                        & 4948               & 1.724               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 地铁 \end{CJK}            & subway                                    & 4491               & 0.18                &                                & shopping                           & 4884               & 1.308               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 购物 \end{CJK}            & shopping                                  & 4206               & 0                   &                                & train                              & 4778               & 0                   \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 下次 \end{CJK}            & next time                                 & 3596               & 0.247               &                                & subway                             & 4405               & 1.951               \\ \cline{1-4} \cline{6-8}
-    \begin{CJK}{UTF8}{gbsn} 推荐 \end{CJK}            & recommend                                 & 3574               & 0.495               &                                & recommend                          & 3812               & 1.158               \\ \cline{1-4} \cline{6-8}
+      \caption{Top 4 words related to the mainly used adjectives in positive texts.}
+      \label{tab:adj_zh_pos}
+      \resizebox{\linewidth}{!}{%
+      \begin{tabular}{|c|l|l|l|l|l|}
+        \hline
+        \multicolumn{1}{|l|}{\textbf{Price range}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} \\ \hline
+        \multirow{5}{*}{\textbf{0: All Prices}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
+          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
+          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
+          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
+          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
+          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 \\ \hline
+        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
+          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
+          \begin{CJK}{UTF8}{gbsn}不错 附近\end{CJK} (not bad nearby) : 0 &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
+          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
+          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
+          \begin{CJK}{UTF8}{gbsn}便利 附 近\end{CJK} (convenient nearby) : 0 &
+           \\ \hline
+        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
+          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
+          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
+          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
+          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
+          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
+           \\ \hline
+        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
+          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
+          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
+          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
+          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
+          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 \\ \hline
+        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
+          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
+          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
+          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
+          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 \\ \hline
+        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
+          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
+          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
+          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
+          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
+          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
+          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 \\ \hline
+        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
+          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
+          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
+          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
+          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
+          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
+          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 \\ \hline
+        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
+          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
+          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
+          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
+          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
+          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
+          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
+          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
+          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
+          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
+          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
+          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
+          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
+          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
+          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
+          \begin{CJK}{UTF8}{gbsn}干净 一如既往\end{CJK} (clean as always) : 0 &
+          \begin{CJK}{UTF8}{gbsn}不错 附近\end{CJK} (not bad nearby) : 0 &
+          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 \\ \hline
         \end{tabular}%
@@
       \end{table}
-
+    \end{landscape}
+
+    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
     % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
     % \usepackage{graphicx}
-    \begin{table}[h]
+    % \usepackage{lscape}
+    \begin{landscape}
+    \begin{table}[p]
       \centering
-    \caption{Top 10 negative keywords in negative sentences}
-    \label{tab:neg_keys}
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{clccl|l|c|c|}
-    \cline{1-4} \cline{6-8}
-    \multicolumn{4}{|c|}{\textbf{Negative Chinese Keywords}}                                                                                                             & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{3}{c|}{\textbf{Negative English Keywords}}                       \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\textbf{Word}} & \multicolumn{1}{c|}{\textbf{Translation}} & \multicolumn{1}{c|}{\textbf{Frequency}} & \multicolumn{1}{c|}{\textbf{SVC Weight}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{Word}} & \textbf{Frequency} & \textbf{SVC Weight} \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 价格 \end{CJK} }            & \multicolumn{1}{l|}{price}                & \multicolumn{1}{c|}{1908}               & \multicolumn{1}{c|}{-2}                  &                                & dated                              & 426                & 0                   \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 中文 \end{CJK} }            & \multicolumn{1}{l|}{Chinese language}     & \multicolumn{1}{c|}{744}                & \multicolumn{1}{c|}{-0.714}              &                                & working                            & 350                & -0.557              \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 地理 \end{CJK} }            & \multicolumn{1}{l|}{geography}            & \multicolumn{1}{c|}{710}                & \multicolumn{1}{c|}{-0.812}              &                                & pricey                             & 327                & -1.614              \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 距离 \end{CJK} }            & \multicolumn{1}{l|}{distance}             & \multicolumn{1}{c|}{440}                & \multicolumn{1}{c|}{0}                   &                                & slow                               & 306                & -1.281              \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 陈旧 \end{CJK} }            & \multicolumn{1}{l|}{old-fashioned}        & \multicolumn{1}{c|}{338}                & \multicolumn{1}{c|}{0}                   &                                & carpet                             & 224                & -0.507              \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 老   \end{CJK} }             & \multicolumn{1}{l|}{old}                  & \multicolumn{1}{c|}{323}                & \multicolumn{1}{c|}{0}                   &                                & cigarette                          & 220                & -0.435              \\ \cline{1-4} \cline{6-8}
-    \multicolumn{1}{|c|}{\begin{CJK}{UTF8}{gbsn} 华人 \end{CJK} }            & \multicolumn{1}{l|}{Chinese person}       & \multicolumn{1}{c|}{16}                 & \multicolumn{1}{c|}{-0.5}                &                                & uncomfortable                      & 207                & -2.423              \\ \cline{1-4} \cline{6-8}
-                                                                             &                                           &                                         &                                          &                                & paper                              & 185                & -0.503              \\ \cline{6-8}
-                                                                             &                                           &                                         &                                          &                                & smallest                           & 168                & -1.035              \\ \cline{6-8}
-                                                                             &                                           &                                         &                                          &                                & dirty                              & 163                & -1.275              \\ \cline{6-8}
+      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
+      \label{tab:adj_zh_neg}
+      \resizebox{\linewidth}{!}{%
+      \begin{tabular}{|c|l|l|l|}
+        \hline
+        \multicolumn{1}{|l|}{\textbf{Price range}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
+        \multirow{5}{*}{\textbf{0: All Prices}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
+          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
+          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
+        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
+           &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
+           &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
+           &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
+           &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
+           &
+           \\ \hline
+        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
+          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
+           &
+           \\ \hline
+        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
+          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
+           &
+           \\ \hline
+        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
+          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
+          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
+        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
+          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
+           &
+          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
+        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
+          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
+          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
+           &
+          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
+        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
+          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
+          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
+          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
+          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
+          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
+           &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
+           &
+           \\
+         &
+          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
+           &
+           \\ \hline
         \end{tabular}%
@@
     \end{table}
-
-  \subsection{Rank-biased Overlap}\label{rboresults}
-
-    In order to calculate the similarity between the ranked lists shown in Table \ref{tab:pos_keys}, and the lists in Table \ref{tab:neg_keys}, we calculated the extrapolated Rank-biased Overlap between the English keyword lists and the English translation of the Chinese keyword lists at different cutoff points.
-Additionally, we prepared and modified the lists so that words that are similar but would not overlap otherwise would overlap in this analysis.
-For example, in the English keyword lists, the word is ``pricey," while in the Chinese keywords it is translated as ``price," so we changed it to ``pricey" to match the English keywords.
-We did this change purely to overlap the most words possible, and so it could have been modified the other way around with the same effect.
-The results of these calculations are shown in Table \ref{tab:rbo}.
-In the case of Chinese dissatisfaction keywords, which is only comprised of 7 keywords, the list remains complete in all cutoff points except 5.
-The RBO measure can work regardless of the length of each list, so there was not a problem in its calculation.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[h]
-    \centering
-    \caption{RBO results between Chinese and English keyword lists, \(p=0.9\).}
-    \label{tab:rbo}
-    \begin{tabular}{|l|c|r|}
-    \hline
-    \multicolumn{1}{|c|}{\textbf{List cutoff}} & \textbf{Emotion} & \(RBO_{EXT}\) \\ \hline
-    \multirow{2}{*}{None}   & Satisfaction      & 0.217 \\ \cline{2-3} 
-                            & Dissatisfaction   & 0.137 \\ \hline
-    \multirow{2}{*}{Top 20} & Satisfaction      & 0.216 \\ \cline{2-3} 
-                            & Dissatisfaction   & 0.132 \\ \hline
-    \multirow{2}{*}{Top 10} & Satisfaction      & 0.257 \\ \cline{2-3} 
-                            & Dissatisfaction   & 0.128 \\ \hline
-    \multirow{2}{*}{Top 5}  & Satisfaction      & 0.176 \\ \cline{2-3} 
-                            & Dissatisfaction   & 0.176 \\ \hline
-    \end{tabular}
-    \end{table}
+    \end{landscape}
 
@@
 
-  \subsection{Experiment results and testing the hypotheses}
+  \subsection{Experiment results and answering research questions}
 
@@
 Besides, there are complaints about a Chinese friendly environment.
-This makes our hypothesis \ref{hyp:omotenashi_zh} rejected.
-On the other hand, the word ``staff'' tops the list of satisfaction factors in English-written reviews, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
+This brings insight onto our research question \ref{rsq:omotenashi_zh}.
+
+    % On the other hand, the word ``staff'' tops the list of satisfaction factors in English-written reviews, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
 This confirms our hypothesis \ref{hyp:omotenashi_en}.
@@
 
-    The extrapolated Rank-biased Overlap (shown in Table \ref{tab:rbo}) ranged from 0.176 to 0.257 in satisfaction lists, and from 0.128 to 0.176 in the dissatisfaction lists, which are low similarity values (\(RBO_{EXT} < 0.5\)).
-This means that, while there is some similarity, the satisfaction and dissatisfaction factors are fundamentally different if we consider them as top-weighted; that is, the first elements are the most important in the lists, and therefore in their similarity measurement as well.
-This confirms our hypothesis \ref{hyp:diff_all}, that the priorities for satisfaction and dissatisfaction are different for Chinese and English-speaking tourists.
-
-    Both Chinese and English-speaking tourists in Japan have different priorities.
+    % Both Chinese and English-speaking tourists in Japan have different priorities.
 However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel.
@@
 
-    The lists for Chinese and English-speaking tourists are quite different.
-However, if we compare the lists, we find that ``clean", ``recommend," ``subway," ``shopping,"  and ``price" are shared factors to both customer groups.
-Their place in the ranked list is the same for most of them, and only ``shopping" and ``subway" are exchanged in priority.
-Furthermore, when arranging both lists by eliminating all unique elements, the lists become almost identical with an RBO of 0.906 for the top 20 and top 10 satisfaction keywords and 1.0 for the dissatisfaction lists.
-The lists become dissimilar when there is no cutoff point.
-However, it's still an RBO of 0.575 for the satisfaction list and 1.0 for the dissatisfaction list.
-This means hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), where we hypothesized shared aspects in both customer groups to be different in their priority.
-
-    We also can observe some keywords that are not considered by their counterparts.
+    % We also can observe some keywords that are not considered by their counterparts.
 For example, mainland Chinese tourists are very satisfied with breakfast inclusion.
@@
 
-    We can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are managerial attributes internal to the hotel, that is, or environmental attributes external to it.
-We manually labeled the top keywords of each language into either managerial or environmental by considering how the word would be used when writing a review.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial.
-If the word is describing factors that are unchangeable by the staff or management, we consider them environmental.
-The interpretation of these keywords is shown in the Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}.
+    We can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft attributes that the hotel management can easily change, or hard attributes that the hotel management cannot change without changing infrastructure or location.
+This is to answer our research question \ref{rsq:hard_soft}
+
+    We manually labeled the top keywords of each language into either hard or soft by considering how the word would be used when writing a review.
+If the word is describing factors that are unchangeable by the staff or management, we consider them hard.
+If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
+For adjectives, we looked at the top 4 adjective and noun pairings and counted the majority of uses in each context.
+If there is a draw or it is not clear, we declare it undefined.
+The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
 
     % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[h]
+    % \usepackage{multirow}
+    \begin{table}[]
       \centering
-    \caption{Hotel attribute types for the top 10 satisfaction keywords}
-    \label{tab:man_env_pos}
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{|l|l|l|r|r|}
-    \cline{1-2} \cline{4-5}
-    \multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese satisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English satisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-    managerial & big &  & staff & managerial \\ \cline{1-2} \cline{4-5} 
-    managerial & clean &  & location & environmental \\ \cline{1-2} \cline{4-5} 
-    environmental & transportation &  & clean & managerial \\ \cline{1-2} \cline{4-5} 
-    unidentified & Japan &  & helpful & managerial \\ \cline{1-2} \cline{4-5} 
-    managerial & breakfast &  & friendly & managerial \\ \cline{1-2} \cline{4-5} 
-    environmental & close &  & comfortable & managerial \\ \cline{1-2} \cline{4-5} 
-    environmental & subway &  & shopping & environmental \\ \cline{1-2} \cline{4-5} 
-    environmental & shopping &  & train & environmental \\ \cline{1-2} \cline{4-5} 
-    unidentified & next time &  & subway & environmental \\ \cline{1-2} \cline{4-5} 
-    unidentified & recommend &  & recommend & unidentified \\ \cline{1-2} \cline{4-5} 
-    \end{tabular}%
-    }
+      \caption{Determination of hard and soft attributes for Chinese keywords.}
+      \label{tab:zh_hard_soft_keywords}
+      \begin{tabular}{|c|l|l|}
+        \hline
+        \textbf{Keyword emotion category}            & \multicolumn{1}{c|}{\textbf{Keyword}}                & \textbf{Attribute category} \\ \hline
+        \multirow{13}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & undefined                   \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & soft                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & soft                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & undefined                   \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & hard                        \\ \hline
+        \multirow{7}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)           & soft                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)         & undefined                   \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)         & soft                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography)       & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)        & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)        & hard                        \\ \cline{2-3} 
+                                                     & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)              & hard                        \\ \hline
+      \end{tabular}
     \end{table}
 
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[h]
-    \centering
-    \caption{Hotel attribute types for the top 10 dissatisfaction keywords}
-    \label{tab:man_env_neg}
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{lll|r|r|}
-    \cline{1-2} \cline{4-5}
-    \multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Chinese dissatisfaction\\ keywords (translation)\end{tabular}}} & \multicolumn{1}{c|}{\textbf{}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}English dissatisfaction\\ keywords\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Hotel Attribute\\ Type\end{tabular}}} \\ \cline{1-2} \cline{4-5}
-    \multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{price} &  & dated & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese language} &  & working & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{geography} &  & pricey & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{environmental} & \multicolumn{1}{l|}{distance} &  & slow & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old-fashioned} &  & carpet & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{old} &  & cigarette & managerial \\ \cline{1-2} \cline{4-5} 
-    \multicolumn{1}{|l|}{managerial} & \multicolumn{1}{l|}{Chinese person} &  & uncomfortable & managerial \\ \cline{1-2} \cline{4-5} 
-     &  &  & paper & managerial \\ \cline{4-5} 
-     &  &  & smallest & managerial \\ \cline{4-5} 
-     &  &  & dirty & managerial \\ \cline{4-5} 
-    \end{tabular}%
-    }
-    \end{table}
-
-    For our purposes, hypothesis \ref{hyp:man_env} states that the satisfaction and dissatisfaction factors would stem from both managerial and environmental attributes to the hotel.
-This is confirmed for all but one list.
+    % This is confirmed for all but one list.
 The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial.
@@
 Lower on the list, we can observe some environmental factors.
-We can see the summarized results in Table \ref{tab:hyp_man_env}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[h]
-    \caption{Managerial and Environmental nature of the 10 most frequent keywords}
-    \label{tab:hyp_man_env}
-    \resizebox{\textwidth}{!}{%
-    \begin{tabular}{|c|c|r|r|r|}
-    \hline
-    \textbf{Emotion} & \textbf{Customer group} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Managerial\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Environmental\\ Factors\end{tabular}}} & \multicolumn{1}{c|}{\textbf{Unidentified}} \\ \hline
-    \multirow{2}{*}{Satisfaction} 
-        & Chinese speakers & 30\% & 40\% & 30\% \\ \cline{2-5} 
-        & English speakers & 50\% & 40\% & 10\% \\ \hline
-    \multirow{2}{*}{Dissatisfaction} 
-        & Chinese speakers & 71.4\% & 28.6\% & 0\% \\ \cline{2-5} 
-        & English speakers & 100\% & 0\% & 0\% \\ \hline
-    \end{tabular}%
-    }
-    \end{table}
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
+
+    We can see the summarized results for the positive and negative Chinese keywords in Figure \ref{fig:zh_hard_soft}. For the English keywords, see Figure \ref{fig:en_hard_soft}.
+
+    \begin{figure}[h]
+        \centering
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
+            \caption{Positive keywords}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+            \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
+            \caption{Negative keywords}
+        \end{subfigure}
+    \caption{Percentages of hard and soft attributes of the top Chinese keywords for all price ranges}
+    \label{fig:zh_hard_soft}
+    \end{figure}
+
+% \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
+
+% We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
 From inspecting random samples, we also find that this is mostly relating to the rooms.
@@
 
-    From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most critical satisfaction factor for Chinese customers.
+% From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most critical satisfaction factor for Chinese customers.
 However, the word ``big" is widespread in the language and could be used in different contexts to point out positive and negative aspects.
@@
 
-    One key component we found in Chinese customer satisfaction factors is the inclusion of breakfast within the hotel.
+% One key component we found in Chinese customer satisfaction factors is the inclusion of breakfast within the hotel.
 While other food-related words were extracted, most of them were general, like “food” or “eating,” and in a lower ranking.
@@
 
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate to staff friendliness and services.
+% \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
+
+% From the satisfaction factors of English-speaking tourists, we can see that at least three words relate to staff friendliness and services.
 The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the fourth and fifth place.
@@
 
-    Aside from cleanliness, we can also observe the word ``working" is written higher on the list, as well as the word ``paper." We observed the samples, and it is often used with the expression ``paper-thin walls", which could mean the customers can easily hear their neighbors.
+% Aside from cleanliness, we can also observe the word ``working" is written higher on the list, as well as the word ``paper." We observed the samples, and it is often used with the expression ``paper-thin walls", which could mean the customers can easily hear their neighbors.
 Regarding the word ``working,'' we also took a sample of the texts to see its context.
@@
 
-    An interesting detail of the keyword ranking is that the word ``comfortable" is high on the list of satisfaction factors and ``uncomfortable" high on the dissatisfaction factors.
+% An interesting detail of the keyword ranking is that the word ``comfortable" is high on the list of satisfaction factors and ``uncomfortable" high on the dissatisfaction factors.
 It seems that in general, western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
 
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room.
+% \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
+
+% A concern for Western tourists was the smell of tobacco in their room.
 Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
@@
 
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
+% However, in comparison, Chinese customers seem not to be bothered by this at all.
 We consulted studies involving the use of tobacco in different countries.
@@
 
-    Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years.
+% Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years.
 Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
@@
 
-  \subsection{Location, location, location}\label{disc:location}
-
-    The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
+% \subsection{Location, location, location}\label{disc:location}
+
+% The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
 While it was not the priority for either of them, we can assert that the hotel's location is a secondary but still important point in the hotel's satisfaction.
@@
 
-    Japan is a country with a peculiar public transport system.
+% Japan is a country with a peculiar public transport system.
 The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
@@
 
-    Japanese convenience stores, on the other hand, are also famous worldwide.
+% Japanese convenience stores, on the other hand, are also famous worldwide.
 Japanese convenience stores are a haven for the traveler in need.
@@
 
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
+% Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
 While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
 
-\section{Discussion}\label{discussion}
-
-  The results indicate that our hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
+% \section{Discussion}\label{discussion}
+
+  % The results indicate that our hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
 Furthermore, they indicate that, in the context of Japanese hospitality, only Western customers show satisfaction from staff and service amongst their top detected factors.
@@
 
-  \subsection{Western and Chinese tourists in the \textit{Omotenashi} environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
+  % \subsection{Western and Chinese tourists in the \textit{Omotenashi} environment}\label{disc:omotenashi}
+
+    % To this day, scholars continue to correct our historical bias towards the west.
 In this time, studies have determined that different cultural backgrounds lead to different expectations, which in turn influence the satisfaction of tourists.
@@
 
-    Our results indicate that Western tourists are the most satisfied with friendly and helpful staff in Japan.
+    % Our results indicate that Western tourists are the most satisfied with friendly and helpful staff in Japan.
 As explained earlier in this paper, Japan is famous for its customer service all over the world.
@@
 
-    However, we can see from the rest of the western keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
+    % However, we can see from the rest of the western keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
 Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
@@
 
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
+    % According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
 When presented with Japanese hospitality, this expectation is met and overcome.
@@
 
-    On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
+    % On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
 It is necessary to note the difference between these two phenomenons.
@@
 
-    However, another possibility presents itself when we observe the Chinese tourists' dissatisfaction factors.
+    % However, another possibility presents itself when we observe the Chinese tourists' dissatisfaction factors.
 Chinese tourists may have expectations about the treatment towards the Chinese visitors that are not being met, even in this high standard hospitality environment.
@@
 
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
+    % Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
 This study brought us closer to the answer.
@@
 
-    It is unclear from our results which of these could be the case.
+    % It is unclear from our results which of these could be the case.
 One thing is clear for hotel managers, however.
@@
 
-  \subsection{Managerial vs. Environmental satisfaction}\label{disc:man_env}
-
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
+  % \subsection{Managerial vs. Environmental satisfaction}\label{disc:man_env}
+
+    % As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
 Examples of managerial attributes include staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}.
@@
 
-    From Table \ref{tab:hyp_man_env} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 40\% of keywords used by Chinese tourists are of an environmental nature (namely ``transportation", ``close", ``subway", and ``shopping"), while a lower 30\% is managerial in nature (and an undefined 30\%).
+    % From Table \ref{tab:hyp_man_env} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 40\% of keywords used by Chinese tourists are of an environmental nature (namely ``transportation", ``close", ``subway", and ``shopping"), while a lower 30\% is managerial in nature (and an undefined 30\%).
 However, two of these managerial words are all concentrated at the top of the list (``big", ``clean").
@@
 
-    In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean," ``helpful," and ``friendly," to name a few.
+    % In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean," ``helpful," and ``friendly," to name a few.
 English-speaking customers also have managerial attributes at the very top of their list, except for the environmental nature of the location of the hotel.
@@
 
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
+    % For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
 A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
@@
 
-    Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
+    % Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
 Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly.
@@
 
-    Now, a point of interest in this study is the difference in how managerial and environmental factors concern Chinese and Western tourists.
+    % Now, a point of interest in this study is the difference in how managerial and environmental factors concern Chinese and Western tourists.
 We can see that for Chinese customers, while the top positive keyword is managerial, the size of a room is hardly modifiable once the hotel's construction is complete.
@@
 
-    Western tourists, on the other hand, are all around both satisfied and dissatisfied with mostly managerial factors, with a 50\% of the top 10 satisfaction factors and a 100\% of the top 10 dissatisfaction factors coming from managerial attributes.
+    % Western tourists, on the other hand, are all around both satisfied and dissatisfied with mostly managerial factors, with a 50\% of the top 10 satisfaction factors and a 100\% of the top 10 dissatisfaction factors coming from managerial attributes.
 The room for improvement for Western tourists is more extensive than their Chinese counterparts, and as such, present a bigger investment opportunity.
@@
 
-    The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
+    % The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
 Attracting a large number of Chinese customers can be a viable strategy for hotels.
@@
 
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
+    % The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
 This premise also plays a role in the differentiation between the preference of managerial or environmental attributes.
@@
 
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
+  % \subsection{Implications for hotel managers}\label{disc:implications}
+
+    % Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
 Chinese tourists are not experiencing the best that \textit{Omotenashi} has to offer.
@@
 
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
+    % To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
 It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
@@
 
-    Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
+    % Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
 As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
@@
 
-    It is left to the managers to consider their business model for the next strategy.
+    % It is left to the managers to consider their business model for the next strategy.
 One option could be attracting more Chinese customers in number with their observed low budgeting.
@@
 
-  \section{Limitations and Future Work}\label{limitations}
-
-    This paper is not without its limitations.
+% \section{Limitations and Future Work}\label{limitations}
+
+  % This paper is not without its limitations.
 We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context that these words were being used in by taking samples and observing them manually.
-However, because of the large number of sentences in our data being analyzed, we could not perform a complete analysis of the context of these sentences across the database.
-Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
+Following that, we attempted to understand the context that these words were being used in by using a dependency parser and observing the related nouns.
+However, the study is limited in that it only analyzes the words directly related to each keyword, and doesn't follow the upstream or downstream path down further connections.
+This means that if the words are used in combination with other keywords we did not trace the effects of multiple contradicting statements.
+For example, in the sentence "The room is good but the food is lacking", we would extract "good food" and "lacking food", but do not consider the fact that both occurred in the same sentence.
+
+  % In this study, we analyzed the differences in customers expectations at different levels of \textit{Omotenashi} by dividing our data into price ranges.
+However, in the same price range, say the high expenses ones, we can find both a western style five stars resort as well as a high end Japanese style \textit{Ryokan}.
+Services offered in these hotels are very high quality, although very different in nature.
+However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service, although still there is a divide between western and Japanese style hotels.
+
+  % Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
 We could not analyze these populations because our team members do not know those languages.
@@
 
-    In future work, we plan to investigate further into this topic.
+  % In future work, we plan to investigate further into this topic.
 We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
@@
 
-  \section{Conclusion}\label{conclusion}
-
-    In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels.
+% \section{Conclusion}\label{conclusion}
+
+  % In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels.
 We extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
 We used these keywords for sentiment classification via an SVC.
-We then measured the Rank-biased Overlap of the top 10 most frequently used keywords in satisfied and dissatisfied sentences to find the differences between Chinese and Western tourists.
-
-    In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}.
+
+  % In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}.
 However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction.
@@
 
-    We obtained values ranging from 0.176 to 0.257 in satisfaction lists and from 0.128 to 0.176 in dissatisfaction lists at different cutoff points.
-These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}.
-We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers.
-We found that from the four words that were common amongst both groups (``clean", ``recommend," ``subway," and ``price").
-When these shared terms were isolated, both lists were almost identical at the cutoff point of 20 words.
-This resulted in an RBO ranging from 0.906 to 1.0.
-This means our hypothesis \ref{hyp:diff_com} is rejected (\(RBO_{EXT} > 0.5\)), and that the common ground within both customer groups is also similar in ranking.
-
-    Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel.
+  % Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel.
 Managerial attributes are those that they can be changed via managerial decisions without relocating.
@@
 
-    In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords).
+  % In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords).
 In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%).

### 2020-09-27 3_review-responses/V2_review_responses/Reviewer #5 Response.txt
Manually compared to recovery file pdf from 2020 sep 27 10:00am

Reviewer #5 Response

Reviewer #5:

------------
Section 3.3 contains a lot of misleading and confusing information:

1.   "In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures (Nielsen et al. 2017; Jones 2010; Gunaratne 2009; Hogan and Emler 1978)". This is a very strong sentence; can the authors show evident that these studies have say such a strong conclusion?
------------

------------
2.   "both academic researchers and businesses have decided to study Chinese tourist behavior (Sun et al. 2017)." Chinese tourists' study did not start from 2017.
------------

------------
3.  "cross-cultural studies and analyses for Asian and Western tourists are scarce." And "One thing to note with the above cross-culture analyses is that they were performed before the year 2000." If the authors use Google scholar to search, I believe they could find hundred thousand of researches, this topic is not special or scarce at all. If the authors want to refer to Chinese and non-Chinese study, please do not generalize it as cross-cultural study. 
------------

------------
4.  "However, that boom could have created a difference in the expectations of tourists. In turn, that boom could have influenced their satisfaction factors when traveling." I cannot understand these two sentences. How can a boom or tourists create a different expectation of tourists? And how a boom can influence satisfaction?!
------------

------------
The authors responded that hotel class were not recorded during data collection so the data cannot be categorized according to the hotel ranking. In that case, I can accept the research design of this study is appropriate. If the research design has such big defect, the result can no longer explain the difference between Chinese and non-Chinese. The authors mentioned the hotel room rate ranged from 2000 to 188000 yen. So how can you expect a customer paying 2000 yen will have same expectation with a customer paying 188000 yen? The definition of Omotenashi refers to high level customized service. For a capsule hotel which costed 2000 yen, what's kind of Omotenashi service can they provide?
I can see the authors had spend a lot of time to revise the paper and re-write the manuscript, however, if the research design is not correct, the result generated is meaningless. Therefore I will not comment the research findings and conclusion.
------------

------------
Editorial: 
Many in-text citations (e.g. Page 4 & 9) are not in standard format, please put them inside a bracket or change the sentence to mention the author name.
Line 236, please spell out the number "3" to three.
------------

We changed the spelling of lone numbers in the text. We also checked the in-text citations throughout the paper.

### 2020-09-27 1_manuscript/itt-emotion.tex
Manually compared to recovery file pdf from 2020 sep 27 10:00am

@@
 
-    This leads to another research question:
-
+    This leads to another couple of research questions:
+
+    \begin{subrsq}
     \begin{rsq}
@@
     \end{rsq}
+    \begin{rsq}
+    \label{rsq:hard_soft_diff}
+    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
+    \end{rsq}
+
+    \end{subrsq}
 
@@
 However, we are using a database of several orders of magnitude larger.
-We can also expect that, because of the lack of questionnaire design and users' freedom to record their pleasures and grievances, we may discover patterns that researchers previously noticed.
+We can also expect that, because of the lack of questionnaire design and users' freedom to record their pleasures and grievances, we may discover patterns that researchers previously hadn't noticed.
 
@@
 The structure of the data after division by price is shown in Table \ref{tab:exp_notes}, which also includes the results of emotional classification after application of our SVC, as explained in \ref{sentimentanalysis}.
+The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low class hotels or even hostels on the lower end, and cheap business hotels on the higher end.
+Further on there are business hotels in the next range (10,000 to 15,000 yen), and after that the stays could be at Japanese style \textit{ryokan} when traveling in groups, high class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
+Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
+Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
+Because of this, other tables will omit these two price ranges.
 
@@
 In this study we use the Stanford NLP Dependency Parser, as described in \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed in \cite{marneffe_manning_2016_depparse_manual}.
+A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
+In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
 In our study, this step was necessary to extract adjective modifiers and their subject.
 We did that by parsing the entire database, and extracting instances of a few determined dependency codes.
-One of these dependency codes is `amod', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g.
+One of these dependency codes is ``amod'', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g.
 A big apple).
-The other dependency code we used was `nsubj', or nominal subject, which is the syntactic subject of a class.
+The other dependency code we used was ``nsubj'', or nominal subject, which is the syntactic subject of a class.
 We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g.
@@
     \centering
-    \includegraphics[width=\textwidth]{depparse.png}
+    \includegraphics[width=0.6\textwidth]{depparse.png}
     \caption{Example of dependency parsing.}
@@
 A Part of Speech is a category of lexical items that serve similar grammatical purposes; for example, nouns, adjectives, verbs, conjunctions, and so on.
-In our study, we used the Stanford NLP POS tagger software, described in \cite{toutanova2000enriching, toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
+In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{postag.png}
+    \includegraphics[width=0.6\textwidth]{postag.png}
     \caption{Example of POS tagging with the Penn Treebank tags.}
@@
       \label{tab:target_postag}
+      \resizebox{\textwidth}{!}{%
       \begin{tabular}{|c|c|l|l|}
@@
                                              & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-      \end{tabular}
+        \end{tabular}%
+        }
     \end{table}
@@
       \label{tab:filter_postag}
+      \resizebox{\textwidth}{!}{%
       \begin{tabular}{|c|l|l|l|}
@@
                                                 & WP    & Wh-pronoun         & What, who                                  \\ \hline
-      \end{tabular}
+        \end{tabular}%
+        }
     \end{table}
@@
 
-  \subsection{Sentiment analysis}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described in \cite{Aleman2018ICAROB}.
+  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
+
+    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
 Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite{powers2011}.
@@
 We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}
+For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
+
+    We can observe that the most used keywords for most price ranges in the same language are similar to each other, with a few changes in priority for the keywords involved.
+For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
+Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels, and it climbs in importance following the increase in price of the hotel.
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    % \usepackage{graphicx}
+    % \usepackage[normalem]{ulem}
+    % \useunder{\uline}{\ul}{}
+    \begin{table}[]
+    \centering
+    \caption{English and Chinese comparison of the top 10 positive keywords per price range.}
+    \label{tab:freq_res_pos}
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{|c|lr|lr|}
+    \hline
+    \textbf{Price range} &
+      \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
+      \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
+      \multicolumn{1}{c|}{\textbf{English keyword}} &
+      \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
+    \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 3258  & friendly    & 5606  \\ \hline
+    \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
+    \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
+    \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
+    \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
+    \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 541   & friendly    & 1001  \\ \hline
+    \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
+    \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 157   & location    & 799   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
+    \end{tabular}%
+    }
+    \end{table}
+
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    % \usepackage{graphicx}
+    \begin{table}[]
+      \centering
+      \caption{English and Chinese comparison of the top 10 negative keywords per price range.}
+      \label{tab:freq_res_neg}
+      \resizebox{\textwidth}{!}{%
+      \begin{tabular}{|c|lr|lr|}
+        \hline
+        \textbf{Price range} &
+          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
+          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
+          \multicolumn{1}{c|}{\textbf{English keyword}} &
+          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
+        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
+                                                             &                                                &      & annoying       & 220 \\  
+                                                             &                                                &      & sense          & 220 \\ \hline
+        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
+                                                             &                                                &      & funny smell    & 3   \\  
+                                                             &                                                &      & poor           & 3   \\  
+                                                             &                                                &      & renovation     & 3   \\  
+                                                             &                                                &      & carpet         & 2   \\ \hline
+        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
+                                                             &                                                &      & minor          & 21  \\  
+                                                             &                                                &      & paper          & 19  \\  
+                                                             &                                                &      & unable         & 19  \\ \hline
+        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
+                                                             &                                                &      & paper          & 25  \\  
+                                                             &                                                &      & pricey         & 24  \\ \hline
+        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
+                                                             &                                                &      & cigarette      & 79  \\  
+                                                             &                                                &      & annoying       & 70  \\ \hline
+        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
+                                                             &                                                &      & cigarette      & 46  \\  
+                                                             &                                                &      & unable         & 43  \\ \hline
+        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
+                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
+                                                             &                                                &      & sense          & 63  \\  
+                                                             &                                                &      & outdated       & 58  \\ \hline
+        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
+                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
+                                                             &                                                &      & mixed          & 15  \\  
+                                                             &                                                &      & disappointment & 14  \\  
+                                                             &                                                &      & paper          & 14  \\ \hline
+        \end{tabular}%
+        }
+    \end{table}
 
   \subsection{Frequently used adjectives and their pairs}\label{adjresults}
+
+    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
+In order to understand those, we performed the dependency parsing and part of speech tagging explained in section \ref{textprocessing}.
+While there were many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
+We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
+Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
 
@@
     \begin{landscape}
-    \begin{table}[p]
+    \begin{table}[]
       \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive texts.}
+      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
       \label{tab:adj_zh_pos}
       \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
+      \begin{tabular}{|c|l|l|l|l|l|l|}
         \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
+        \textbf{Price range} &
           \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
@@
           \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} \\ \hline
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
+          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
         \multirow{5}{*}{\textbf{0: All Prices}} &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           \\
+           &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           \\
+           &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
+           &
            \\
@@
           \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-          \begin{CJK}{UTF8}{gbsn}不错 附近\end{CJK} (not bad nearby) : 0 &
+           &
+           &
            \\
@@
           \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-          \begin{CJK}{UTF8}{gbsn}便利 附 近\end{CJK} (convenient nearby) : 0 &
+           &
+           &
            \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
+          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
+          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
+           &
+          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
+          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
+          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
+          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
           \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
@@
           \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 \\
+          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
+          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 \\
+          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
+          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 \\
+          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
+          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 \\
+          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
+          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
          &
@@
           \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-          \begin{CJK}{UTF8}{gbsn}干净 一如既往\end{CJK} (clean as always) : 0 &
-          \begin{CJK}{UTF8}{gbsn}不错 附近\end{CJK} (not bad nearby) : 0 &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 \\ \hline
+           &
+           &
+          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
+          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
         \end{tabular}%
@@
       \label{tab:adj_zh_neg}
-      \resizebox{\linewidth}{!}{%
+      \resizebox{0.7\linewidth}{!}{%
       \begin{tabular}{|c|l|l|l|}
@@
 
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    From the observation of the top-ranking subjects for Chinese tourists, we can assert that keywords relating to service and staff friendliness are not on the top 10 satisfaction factors.
-Besides, there are complaints about a Chinese friendly environment.
-This brings insight onto our research question \ref{rsq:omotenashi_zh}.
-
-    % On the other hand, the word ``staff'' tops the list of satisfaction factors in English-written reviews, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-This confirms our hypothesis \ref{hyp:omotenashi_en}.
-Since we found that these two populations are different in their satisfaction with Japanese hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.
-
-    % Both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness.
-In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-English-speaking tourists, on the other hand, value staff friendliness over room quality when considering their satisfaction.
-
-    % We also can observe some keywords that are not considered by their counterparts.
-For example, mainland Chinese tourists are very satisfied with breakfast inclusion.
-At the same time, English-speaking customers are satisfied with the staff and service.
-On the other hand, English-speaking customers mentioned tobacco smell in many reviews, while it wasn't statistically identified as a problem at all for their Chinese counterparts.
-
-    We can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft attributes that the hotel management can easily change, or hard attributes that the hotel management cannot change without changing infrastructure or location.
-This is to answer our research question \ref{rsq:hard_soft}
+    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    % \usepackage{graphicx}
+    % \usepackage[normalem]{ulem}
+    % \useunder{\uline}{\ul}{}
+    % \usepackage{lscape}
+    \begin{landscape}
+    \begin{table}[p]
+      \centering
+      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
+      \label{tab:adj_en_pos}
+      \resizebox{\linewidth}{!}{%
+      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
+        \hline
+        \textbf{Price range} &
+          \multicolumn{1}{c|}{\textbf{good}} &
+          \multicolumn{1}{c|}{\textbf{clean}} &
+          \multicolumn{1}{c|}{\textbf{comfortable}} &
+          \multicolumn{1}{c|}{\textbf{helpful}} &
+          \multicolumn{1}{c|}{\textbf{free}} &
+          \multicolumn{1}{c|}{\textbf{large}} &
+          \multicolumn{1}{c|}{\textbf{firendly}} &
+          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
+        \multirow{5}{*}{\textbf{0: All Prices}} &
+          good : 19148 &
+          clean : 9064 &
+          comfortable : 5625 &
+          helpful : 5846 &
+          free : 4318 &
+          large : 4104 &
+          friendly : 5606 &
+          great : 16127 \\
+         &
+          good location : 1985 &
+          clean room : 3596 &
+          comfortable bed : 1919 &
+          helpful staff : 2927 &
+          free wifi : 773 &
+          large room : 1256 &
+          friendly staff : 3819 &
+          great location : 2313 \\
+         &
+          good service : 1042 &
+          clean hotel : 969 &
+          comfortable room : 1098 &
+          helpful concierge : 304 &
+          free shuttle : 286 &
+          large hotel : 268 &
+          friendly service : 169 &
+          great view : 1099 \\
+         &
+          good breakfast : 942 &
+          clean bathroom : 282 &
+          comfortable stay : 272 &
+          helpful desk : 110 &
+          free drink : 234 &
+          large bathroom : 202 &
+          friendly hotel : 73 &
+          great service : 841 \\
+         &
+          good hotel : 874 &
+          clean everything : 200 &
+          comfortable hotel : 238 &
+          helpful service : 74 &
+          free bus : 225 &
+          larger room : 192 &
+          friendly person : 63 &
+          great hotel : 802 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
+          good : 206 &
+          clean : 174 &
+          comfortable : 79 &
+          helpful : 70 &
+          free : 35 &
+          large : 31 &
+          friendly : 64 &
+          great : 143 \\
+         &
+          good location : 30 &
+          clean room : 55 &
+          comfortable bed : 21 &
+          helpful staff : 36 &
+          free wifi : 10 &
+          large room : 7 &
+          friendly staff : 53 &
+          great location : 21 \\
+         &
+          good value : 19 &
+          clean bathroom : 14 &
+          comfortable room : 9 &
+           &
+          free tea : 4 &
+          large area : 2 &
+          friendly everyone : 2 &
+          great view : 14 \\
+         &
+          good english : 10 &
+          clean place : 12 &
+          comfortable futon : 8 &
+           &
+          free raman : 2 &
+          large size : 2 &
+          friendly service : 2 &
+          great place : 13 \\
+         &
+          good place : 7 &
+          clean hotel : 6 &
+          comfortable stay : 3 &
+           &
+          free toothbrush : 2 &
+           &
+           &
+          great experience : 5 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
+          good : 1399 &
+          clean : 656 &
+          comfortable : 391 &
+          helpful : 393 &
+          free : 271 &
+          large : 250 &
+          friendly : 400 &
+          great : 961 \\
+         &
+          good location : 159 &
+          clean room : 247 &
+          comfortable bed : 123 &
+          helpful staff : 206 &
+          free wifi : 53 &
+          large room : 84 &
+          friendly staff : 292 &
+          great location : 158 \\
+         &
+          good breakfast : 87 &
+          clean hotel : 74 &
+          comfortable room : 90 &
+          helpful concierge : 20 &
+          free breakfast : 15 &
+          large bathroom : 20 &
+          friendly service : 15 &
+          great service : 51 \\
+         &
+          good hotel : 71 &
+          clean bathroom : 20 &
+          comfortable hotel : 26 &
+          helpful desk : 10 &
+          free service : 12 &
+          larger room : 12 &
+          friendly hotel : 7 &
+          great hotel : 43 \\
+         &
+          good service : 67 &
+          clean everything : 14 &
+          comfortable stay : 20 &
+          helpful service : 4 &
+          free drink : 11 &
+          large hotel : 10 &
+          friendly person : 6 &
+          great place : 35 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
+          good : 2242 &
+          clean : 1204 &
+          comfortable : 621 &
+          helpful : 552 &
+          free : 581 &
+          large : 349 &
+          friendly : 615 &
+          great : 1414 \\
+         &
+          good location : 242 &
+          clean room : 440 &
+          comfortable bed : 219 &
+          helpful staff : 301 &
+          free wifi : 109 &
+          large room : 85 &
+          friendly staff : 444 &
+          great location : 199 \\
+         &
+          good hotel : 116 &
+          clean hotel : 133 &
+          comfortable room : 99 &
+          helpful desk : 11 &
+          free shuttle : 35 &
+          large suitcase : 18 &
+          friendly hotel : 12 &
+          great view : 81 \\
+         &
+          good breakfast : 113 &
+          clean bathroom : 38 &
+          comfortable stay : 30 &
+          helpful concierge : 9 &
+          free bus : 30 &
+          larger room : 18 &
+          friendly service : 8 &
+          great hotel : 68 \\
+         &
+          good service : 108 &
+          clean everything : 26 &
+          comfortable hotel : 20 &
+          helpful reception : 5 &
+          free breakfast : 27 &
+          large hotel : 17 &
+          friendly most : 7 &
+          great place : 61 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
+          good : 6550 &
+          clean : 3364 &
+          comfortable : 1941 &
+          helpful : 1970 &
+          free : 1186 &
+          large : 1257 &
+          friendly : 1915 &
+          great : 5074 \\
+         &
+          good location : 703 &
+          clean room : 1379 &
+          comfortable bed : 658 &
+          helpful staff : 1019 &
+          free wifi : 269 &
+          large room : 329 &
+          friendly staff : 1311 &
+          great location : 881 \\
+         &
+          good service : 331 &
+          clean hotel : 379 &
+          comfortable room : 359 &
+          helpful concierge : 79 &
+          free breakfast : 68 &
+          large hotel : 87 &
+          friendly service : 51 &
+          great service : 249 \\
+         &
+          good english : 304 &
+          clean bathroom : 95 &
+          comfortable stay : 100 &
+          helpful desk : 42 &
+          free coffee : 57 &
+          larger room : 81 &
+          friendly person : 21 &
+          great hotel : 232 \\
+         &
+          good breakfast : 303 &
+          clean everything : 77 &
+          comfortable hotel : 82 &
+          helpful receptionist : 17 &
+          free drink : 38 &
+          large bed : 43 &
+          friendly hotel : 19 &
+          great view : 220 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
+          good : 3407 &
+          clean : 1750 &
+          comfortable : 1000 &
+          helpful : 1147 &
+          free : 933 &
+          large : 580 &
+          friendly : 1001 &
+          great : 2620 \\
+         &
+          good location : 380 &
+          clean room : 725 &
+          comfortable bed : 345 &
+          helpful staff : 607 &
+          free drink : 145 &
+          large room : 174 &
+          friendly staff : 715 &
+          great location : 393 \\
+         &
+          good breakfast : 191 &
+          clean hotel : 197 &
+          comfortable room : 193 &
+          helpful concierge : 53 &
+          free wifi : 129 &
+          larger room : 32 &
+          friendly service : 24 &
+          great view : 162 \\
+         &
+          good service : 182 &
+          clean bathroom : 61 &
+          comfortable hotel : 49 &
+          helpful service : 20 &
+          free coffee : 45 &
+          large hotel : 30 &
+          friendly hotel : 13 &
+          great hotel : 134 \\
+         &
+          good english : 155 &
+          clean everything : 36 &
+          comfortable stay : 47 &
+          helpful desk : 17 &
+          free bus : 38 &
+          large bed : 28 &
+          friendly person : 13 &
+          great service : 114 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
+          good : 4350 &
+          clean : 1655 &
+          comfortable : 1246 &
+          helpful : 1313 &
+          free : 1072 &
+          large : 1233 &
+          friendly : 1238 &
+          great : 4425 \\
+         &
+          good location : 406 &
+          clean room : 648 &
+          comfortable bed : 425 &
+          helpful staff : 589 &
+          free shuttle : 181 &
+          large room : 442 &
+          friendly staff : 810 &
+          great location : 506 \\
+         &
+          good service : 296 &
+          clean hotel : 156 &
+          comfortable room : 266 &
+          helpful concierge : 108 &
+          free wifi : 172 &
+          large hotel : 109 &
+          friendly service : 51 &
+          great view : 436 \\
+         &
+          good hotel : 196 &
+          clean bathroom : 48 &
+          comfortable stay : 56 &
+          helpful service : 28 &
+          free bus : 127 &
+          large bathroom : 58 &
+          friendly hotel : 20 &
+          great service : 267 \\
+         &
+          good breakfast : 191 &
+          cleanliness : 40 &
+          comfortable hotel : 51 &
+          helpful desk : 26 &
+          free service : 65 &
+          larger room : 38 &
+          friendly person : 12 &
+          great hotel : 241 \\ \hline
+        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
+          good : 994 &
+          clean : 261 &
+          comfortable : 347 &
+          helpful : 401 &
+          free : 240 &
+          large : 404 &
+          friendly : 370 &
+          great : 1488 \\
+         &
+          good location : 65 &
+          clean room : 102 &
+          comfortable bed : 128 &
+          helpful staff : 169 &
+          free wifi : 31 &
+          large room : 135 &
+          friendly staff : 194 &
+          great location : 155 \\
+         &
+          good service : 56 &
+          clean hotel : 24 &
+          comfortable room : 82 &
+          helpful concierge : 35 &
+          free breakfast : 19 &
+          large bathroom : 38 &
+          friendly service : 18 &
+          great view : 155 \\
+         &
+          good breakfast : 53 &
+          cleanliness : 8 &
+          comfortable stay : 16 &
+          helpful everyone : 7 &
+          free drink : 16 &
+          large hotel : 15 &
+          friendly everyone : 7 &
+          great service : 101 \\
+         &
+          good hotel : 40 &
+          clean place : 7 &
+          comfortable hotel : 10 &
+          helpful team : 5 &
+          free bus : 14 &
+          large bed : 12 &
+          friendly person : 4 &
+          great hotel : 80 \\ \hline
+        \end{tabular}%
+        }
+    \end{table}
+    \end{landscape}
+
+    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
+    % Please add the following required packages to your document preamble:
+    % \usepackage{multirow}
+    % \usepackage{graphicx}
+    % \usepackage{lscape}
+    \begin{landscape}
+    \begin{table}[]
+      \centering
+      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
+      \label{tab:adj_en_neg}
+      \resizebox{0.8\linewidth}{!}{%
+      \begin{tabular}{|c|l|l|l|l|l|}
+        \hline
+        \textbf{Price range} &
+          \multicolumn{1}{c|}{\textbf{poor}} &
+          \multicolumn{1}{c|}{\textbf{dated}} &
+          \multicolumn{1}{c|}{\textbf{worst}} &
+          \multicolumn{1}{c|}{\textbf{dirty}} &
+          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
+        \multirow{5}{*}{\textbf{0: All Prices}} &
+          poor : 460 &
+          dated : 431 &
+          worst : 327 &
+          dirty : 188 &
+          uncomfortable : 253 \\
+         &
+          poor service : 55 &
+          outdated : 128 &
+          worst hotel : 43 &
+          dirty carpet : 34 &
+          uncomfortable bed : 63 \\
+         &
+          poor breakfast : 41 &
+          outdated room : 20 &
+          worst experience : 18 &
+          dirty room : 23 &
+          uncomfortable pillow : 20 \\
+         &
+          poor quality : 27 &
+          outdated hotel : 10 &
+          worst part : 15 &
+          not dirty : 7 &
+          uncomfortable mattress : 8 \\
+         &
+          poor english : 24 &
+          outdated bathroom : 7 &
+          worst service : 10 &
+          dirty bathroom : 6 &
+          uncomfortable night : 8 \\ \hline
+        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
+          poor : 3 &
+           &
+          worst : 6 &
+          dirty : 3 &
+          uncomfortable : 2 \\
+         &
+           &
+           &
+          worst room : 2 &
+           &
+           \\
+         &
+           &
+           &
+           &
+           &
+           \\
+         &
+           &
+           &
+           &
+           &
+           \\
+         &
+           &
+           &
+           &
+           &
+           \\ \hline
+        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
+          poor : 29 &
+          dated : 40 &
+          worst : 24 &
+          dirty : 11 &
+          uncomfortable : 23 \\
+         &
+          poor breakfast : 3 &
+          outdated : 11 &
+          worst hotel : 4 &
+          dirty floor : 2 &
+          uncomfortable bed : 4 \\
+         &
+          poor service : 3 &
+          outdated decor : 2 &
+          worst experience : 2 &
+           &
+          not uncomfortable : 2 \\
+         &
+          poor conditioning : 2 &
+          outdated room : 2 &
+           &
+           &
+          uncomfortable night : 2 \\
+         &
+          poor view : 2 &
+           &
+           &
+           &
+          uncomfortable pillow : 2 \\ \hline
+        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
+          poor : 57 &
+          dated : 41 &
+          worst : 36 &
+          dirty : 14 &
+          uncomfortable : 26 \\
+         &
+          poor service : 10 &
+          outdated : 8 &
+          worst hotel : 8 &
+          dirty room : 2 &
+          uncomfortable bed : 7 \\
+         &
+          poor breakfast : 6 &
+           &
+          worst experience : 3 &
+           &
+          uncomfortable pillow : 2 \\
+         &
+          poor hotel : 5 &
+           &
+          worst part : 2 &
+           &
+           \\
+         &
+          poor experience : 3 &
+           &
+          worst service : 2 &
+           &
+           \\ \hline
+        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
+          poor : 136 &
+          dated : 131 &
+          worst : 86 &
+          dirty : 67 &
+          uncomfortable : 103 \\
+         &
+          poor breakfast : 15 &
+          outdated : 31 &
+          worst hotel : 11 &
+          dirty room : 10 &
+          uncomfortable bed : 24 \\
+         &
+          poor service : 14 &
+          outdated room : 6 &
+          worst part : 7 &
+          dirty carpet : 8 &
+          uncomfortable pillow : 11 \\
+         &
+          poor english : 9 &
+          outdated hotel : 2 &
+          worst breakfast : 5 &
+          dirty bathroom : 3 &
+          uncomfortable night : 4 \\
+         &
+          poor quality : 9 &
+           &
+          worst experience : 5 &
+          dirty chair : 2 &
+          uncomfortable experience : 3 \\ \hline
+        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
+          poor : 92 &
+          dated : 65 &
+          worst : 64 &
+          dirty : 51 &
+          uncomfortable : 55 \\
+         &
+          poor service : 8 &
+          outdated : 17 &
+          worst hotel : 10 &
+          dirty carpet : 11 &
+          uncomfortable bed : 20 \\
+         &
+          poor breakfast : 7 &
+          outdated hotel : 4 &
+          worst room : 3 &
+          dirty room : 7 &
+          uncomfortable mattress : 6 \\
+         &
+          poor english : 7 &
+          outdated bathroom : 2 &
+          worst service : 3 &
+          dirty clothe : 2 &
+          uncomfortable pillow : 5 \\
+         &
+          poor connection : 5 &
+          outdated decor : 2 &
+          worst part : 2 &
+          dirty luggage : 2 &
+          uncomfortable room : 5 \\ \hline
+        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
+          poor : 124 &
+          dated : 150 &
+          worst : 98 &
+          dirty : 36 &
+          uncomfortable : 33 \\
+         &
+          poor service : 16 &
+          outdated : 58 &
+          worst hotel : 9 &
+          dirty carpet : 12 &
+          uncomfortable bed : 7 \\
+         &
+          poor breakfast : 9 &
+          outdated room : 9 &
+          worst experience : 5 &
+          dirty room : 3 &
+           \\
+         &
+          poor quality : 9 &
+          outdated furniture : 6 &
+          worst part : 3 &
+          dirty cup : 2 &
+           \\
+         &
+          poor english : 6 &
+          outdated hotel : 4 &
+           &
+          dirty rug : 2 &
+           \\ \hline
+        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
+          poor : 19 &
+          dated : 3 &
+          worst : 12 &
+          dirty : 6 &
+          uncomfortable : 8 \\
+         &
+          poor service : 4 &
+          outdated : 2 &
+          worst experience : 2 &
+           &
+          little uncomfortable : 2 \\
+         &
+          poor choice : 2 &
+           &
+           &
+           &
+           \\
+         &
+          poor experience : 2 &
+           &
+           &
+           &
+           \\
+         &
+           &
+           &
+           &
+           &
+           \\ \hline
+      \end{tabular}%
+      }
+    \end{table}
+    \end{landscape}
+
+  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
+
+  In order to further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
+We define these by the feasibility with which a hotel management might make an improvement on this end to satisfy the customer further.
+We define hard attributes as matters that would be impossible for the hotel to change, such as the surroundings and location of the hotel, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk.
+Soft attributes, on the other hand, are attributes of the hotel which are easily changeable if small investments are made.
+For example, an improvement in the services of the hotel or the cleanliness of the rooms is a soft attribute.
+We can thus observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft attributes that the hotel management can easily change, or hard attributes that the hotel management cannot change without changing infrastructure or location.
 
@@
 If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings and counted the majority of uses in each context.
-If there is a draw or it is not clear, we declare it undefined.
+For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset, and counted the percentage of usage in each context.
+If it is not clear from the word or the pairing alone, we declare it undefined.
+Then, we added the counts of these words in each category, where a single word with no pairing is always 100\% in the category it corresponds to, and we add the partial percentages for each category when an adjective includes various contexts.
 The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
+We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
+For the English keywords, see Figure \ref{fig:hard_soft_en}.
 
@@
   % \usepackage{multirow}
+  % \usepackage{graphicx}
   \begin{table}[]
     \centering
-      \caption{Determination of hard and soft attributes for Chinese keywords.}
+    \caption{Determination of hard and soft attributes for Chinese keywords. }
     \label{tab:zh_hard_soft_keywords}
+    \resizebox{\textwidth}{!}{%
     \begin{tabular}{|c|l|l|}
       \hline
-        \textbf{Keyword emotion category}            & \multicolumn{1}{c|}{\textbf{Keyword}}                & \textbf{Attribute category} \\ \hline
-        \multirow{13}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & undefined                   \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & soft                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & soft                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & undefined                   \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & hard                        \\ \hline
-        \multirow{7}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)           & soft                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)         & undefined                   \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)         & soft                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography)       & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)        & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)        & hard                        \\ \cline{2-3} 
-                                                     & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)              & hard                        \\ \hline
-      \end{tabular}
+      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
+      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
+      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
+       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
+      \end{tabular}%
+      }
   \end{table}
-
-    % This is confirmed for all but one list.
-The exception is the English-speaking tourists' top 10 dissatisfaction factors, which are all managerial.
-However, this is only regarding the top 10 items on the list.
-Lower on the list, we can observe some environmental factors.
-
-    We can see the summarized results for the positive and negative Chinese keywords in Figure \ref{fig:zh_hard_soft}. For the English keywords, see Figure \ref{fig:en_hard_soft}.
 
@@
       \end{subfigure}
-    \caption{Percentages of hard and soft attributes of the top Chinese keywords for all price ranges}
-    \label{fig:zh_hard_soft}
+  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
+  \label{fig:hard_soft_zh}
   \end{figure}
 
-% \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-% We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
-From inspecting random samples, we also find that this is mostly relating to the rooms.
-There are also many references to the public bathing facilities in the hotel.
+  % Please add the following required packages to your document preamble:
+  % \usepackage{multirow}
+  % \usepackage{graphicx}
+  % \usepackage[normalem]{ulem}
+  % \useunder{\uline}{\ul}{}
+  \begin{table}[]
+    \centering
+    \caption{Determination of hard and soft attributes for English keywords. }
+    \label{tab:en_hard_soft_keywords}
+    \resizebox{\textwidth}{!}{%
+    \begin{tabular}{|c|l|l|}
+      \hline
+      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
+      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
+       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
+       & staff          & 100\% soft                           \\ \cline{2-3} 
+       & clean          & 100\% soft                           \\ \cline{2-3} 
+       & location       & 100\% hard                           \\ \cline{2-3} 
+       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
+       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
+       & helpful        & 100\% soft                           \\ \cline{2-3} 
+       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
+       & shopping       & 100\% hard                           \\ \cline{2-3} 
+       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
+       & friendly       & 100\% soft                           \\ \cline{2-3} 
+       & train          & 100\% hard                           \\ \cline{2-3} 
+       & large          & 100\% hard                           \\ \cline{2-3} 
+       & free           & 100\% soft                           \\ \cline{2-3} 
+       & subway         & 100\% hard                           \\ \cline{2-3} 
+       & recommend      & 100\% undefined                      \\ \cline{2-3} 
+       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
+      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
+       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
+       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
+       & poor           & 100\% soft                           \\ \cline{2-3} 
+       & walkway        & 100\% hard                           \\ \cline{2-3} 
+       & sense          & 100\% undefined                      \\ \cline{2-3} 
+       & unable         & 100\% soft                           \\ \cline{2-3} 
+       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
+       & minor          & 100\% undefined                      \\ \cline{2-3} 
+       & worse          & 100\% undefined                      \\ \cline{2-3} 
+       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
+       & lighting       & 100\% soft                           \\ \cline{2-3} 
+       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
+       & carpet         & 100\% soft                           \\ \cline{2-3} 
+       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
+       & cigarette      & 100\% soft                           \\ \cline{2-3} 
+       & funny smell    & 100\% soft                           \\ \cline{2-3} 
+       & rude           & 100\% soft                           \\ \cline{2-3} 
+       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
+       & mixed          & 100\% undefined                      \\ \cline{2-3} 
+       & renovation     & 100\% hard                           \\ \cline{2-3} 
+       & paper          & 100\% undefined                      \\ \cline{2-3} 
+       & disappointment & 100\% undefined                      \\ \cline{2-3} 
+       & outdated       & 75\% hard, 25\% undefined            \\ \hline
+      \end{tabular}%
+      }
+  \end{table}
+
+  \begin{figure}[h]
+      \centering
+      \begin{subfigure}[b]{0.45\textwidth}
+          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
+          \caption{Positive keywords}
+      \end{subfigure}
+      \begin{subfigure}[b]{0.45\textwidth}
+          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
+          \caption{Negative keywords}
+      \end{subfigure}
+  \caption{Hard and soft attributes from the top English keywords for all price ranges}
+  \label{fig:hard_soft_en}
+  \end{figure}
+
+\section{Results}\label{results}
+
+  \subsection{Experiment results and answering research questions}
+
+    Our research questions were about two things.
+In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide as the objective of this study to determine how Chinese and Western tourists interact with the service and hospitality in Japan, \textit{omotenashi}, and how are they different in their perceptions in this matter.
+From the observation of the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}, that while service, cleanliness and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
+When we see the rest of the factors lower on the list, we see that across different price ranges, the list is more populated with hard attributes like location and transportation availability.
+From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about lack of a Chinese friendly environment, although most complaints are also about hard attributes such as the age of the building and the distance from other convenient spots.
+The most complained about aspect, however, is the price of the hotel.
+It is surprising to note that all of the price ranges have this negative keyword at the top of the list, suggesting that it is a main concern to Chinese customers with different purposes of travel.
+
+    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
+When we look at the adjectival pairing of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that mostly, they praise either the location, the service, breakfast, or English availability.
+When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service related concepts that the Western tourists are disappointed with when they react negatively.
+With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
+However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel.
+The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, as well as the service of breakfast.
+In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
+It is surprising that the cigarette smell is an issue even in middle to high class hotels above 30,000 yen per night, although above 50,000 yen per night this problem seems to disappear from the list of top 10 concerns.
+Old and dated buildings seem to be a concern for both populations.
+On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction, while Chinese tourists consider location and transportation more often.
+
+    We also can observe some keywords that are not considered by their counterparts.
+For example, English-speaking customers mentioned tobacco smell in many reviews, while it wasn’t statistically identified as a problem at all for their Chinese counterparts.
+On the other hand, while it appears in both English and Chinese lists, references to ``shopping'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
+Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10
+    positive keywords list for English-speakers.
+
+    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions.
+Here we define hard attributes as those that are impossible or impractical to change for the hotel management, for example matters like the surroundings, view or location convenience.
+On the other hand, soft attributes are those that the hotel could easily and practically change without much limitations except for small financial investments, for example, improvement on the services of the hotel via training or hiring specialized staff.
+In our study, we find that that mostly Chinese tourists are positively reacting more to hard attributes of the hotel, and in negative sentences, there is a slightly hard leaning (53\%) concern with hard attributes, albeit it is more uniform in this instance.
+English-speaking tourists on the other hand, are both positively and negatively more responsive to soft attributes, and in the case of negative keywords, tourists are overwhelmingly more concerned with soft attributes of the hotel dissatisfying them somehow.
+
+    One factor that both populations have in common is, when perceiving the hotel negatively, ``old'' or ``outdated'', or ``obsolete'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
+This is, however, a hard attribute, and is unlikely to change for most hotels.
+
+  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
+
+    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
+From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
+Other mentions are also big markets nearby, or a big bed.
+We can observe that across different price ranges, the usage of the word ``big'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels.
+Inspecting closer by taking random samples of the pairs of ``big space'' or ``large area'', we can see that there are also many references to the public bathing facilities in the hotel.
 In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
@@
 
-% From these two first ranking keywords (``big" and ``clean"), we can assert that room quality is the most critical satisfaction factor for Chinese customers.
-However, the word ``big" is widespread in the language and could be used in different contexts to point out positive and negative aspects.
-Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word ``big" in Chinese.
-A team of Chinese speaking lab members then pointed out the usage of the word.
-Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities.
-
-% One key component we found in Chinese customer satisfaction factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like “food” or “eating,” and in a lower ranking.
-In contrast, the word “breakfast” refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-A recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast.
-
-% \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-% From the satisfaction factors of English-speaking tourists, we can see that at least three words relate to staff friendliness and services.
-The word ``staff" is the most frequently used word for satisfied customers, while ``helpful" and ``friendly" follow it lower in the list at the fourth and fifth place.
+    However, size of the room or the bed is a hard attribute, and without considering rebuilding the hotel, is quite difficult to improve on.
+Cleanliness, on the other hand, is mostly relating to soft attributes when we observe its adjectival pairings.
+We can observe pairs such as ``clean room'' at the top rank of all price ranges, and then variably ``clean hotel'', ``clean overall'', ``clean environment'', and ``clean facilities'', among other examples.
+In negative reviews, there is a mention of criticizing the ``general hygiene'' of the hotel, although it’s an uncommon pair.
+We can therefore assert that cleanliness is an important soft attribute for Chinese customers, and that they are mostly pleased, with their expectations being met.
+
+    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
+While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' and in a lower ranking.
+In contrast, the word ``breakfast'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
+The word ``breakfast'' is also observed across all price ranges, although at different priorities in each of them.
+However we assert that it is an important factor.
+Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``not bad'' is paired with ``breakfast'' in four of the seven price ranges that had reviews available as part of the top 4 pairings, and only slightly lower on other categories, although it is not shown on the table.
+Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast as a strategy to increase good reviews.
+
+  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
+
+    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'',``helpful'' and ``friendliness'' in the general database.
+The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
+Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
+The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
+Similar to Chinese customers, Western customers also seem to be enjoying the included breakfasts when it comes to their satisfaction keyword pairings, although the word doesn’t appear directly in the top 10 list as in their Chinese counterparts.
+The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
+When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service related concepts that the Western tourists are disappointed with when they react negatively.
+The word ``great'', which is also high in most price ranges, and the top keyword in the highest priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location : 2313'', ``great view : 1099'' and ``great service : 841'', if we include the counts from all the price ranges together.
 Japanese high standards in hospitality very likely influenced this result.
 
-% Aside from cleanliness, we can also observe the word ``working" is written higher on the list, as well as the word ``paper." We observed the samples, and it is often used with the expression ``paper-thin walls", which could mean the customers can easily hear their neighbors.
-Regarding the word ``working,'' we also took a sample of the texts to see its context.
-It seems to be related mostly to construction work near or at the facilities.
-Some cities in Japan (e.g., Osaka) are currently undergoing a large number of renovations, which are also extending to the hotel facilities.
-Customers staying in places in renovation or near a construction site can be expected to wake up to construction noises, have their view obstructed by metal bars, and other unpleasant experiences.
-Another keyword there is ``slow", which upon inspection of example reviews, we concluded that it reflects the speed of the Internet connection in the hotel rooms.
-
-% An interesting detail of the keyword ranking is that the word ``comfortable" is high on the list of satisfaction factors and ``uncomfortable" high on the dissatisfaction factors.
+    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
+Since it is an adjective, we have explored the word pairings as well.
+Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also just referring to the hotel in general.
+It seems as well that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
+Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
+
+    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the list of satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
+The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
     It seems that in general, western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-% \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-% A concern for Western tourists was the smell of tobacco in their room.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all.
-The smell of smoke can completely ruin some customers' stay and give a bad impression to review writers, which can lower the number of future customers.
-
-% However, in comparison, Chinese customers seem not to be bothered by this at all.
+The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
+
+    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mention ``free'' as one of the top 10 positive keywords, which is paired mostly with ``wifi''.
+This price range is mostly for business hotels, which can be where users would be expecting this feature the most.ern tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
+
+  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
+
+    A concern for Western tourists was the smell of tobacco in their room.
+This can be considered a soft attribute.
+Not only as a standalone word of ``cigarette'', but also confirming with word pairs in Table \ref{tab:adj_en_neg}, we can find other related word pairs such as ``funny smell''.
+Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non- smoking, yet, the smell permeated the room and curtains.
+Another common complaint was that there were no non-smoking facilities available at all in the first place.
+The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, which can lower the number of future customers.
+
+    However, in comparison, Chinese customers seem not to be bothered by this at all.
 We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of \num[group-separator={,}]{170000} Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco, who2015tobacco}.
-
-% Japan itself has a polarized view on smoking, and despite being one of the world's largest tobacco markets, its use has been decreasing in recent years.
+Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
+
+    Japan itself has a polarized view on smoking, and despite being one of the world’s largest tobacco markets, its use has been decreasing in recent years.
 Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
 However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, there are many places where ``smoking rooms" are available to keep the smoke to an enclosed area and avoid bothering others.
+However, there are many places where ``smoking rooms'' are available to keep the smoke to an enclosed area and avoid bothering others.
 Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
 If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all kinds of customers.
-
-% \subsection{Location, location, location}\label{disc:location}
-
-% The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-While it was not the priority for either of them, we can assert that the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is an external factor to the management of the hotel, it is not often considered in the literature.
+After all, even if it does not bother a few customers, the lack of smell would
+    make it an appropriate space for all kinds of customers.
+
+  \subsection{Location, location, location}\label{disc:location}
+
+    The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
+In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``nice location'', ``near subway station'', ``near subway'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``traffic'', ``shopping'', ``subway'', and ``surroundings'' for Chinese speakers.
+All of these keywords, as well as their location in the priorities of each population across the price ranges, signal that while it was not the priority for either of them, the hotel’s location is a secondary but still important point in the hotel’s satisfaction.
+However, since this is a hard attribute, unchangeable to the management of the hotel, it is not often considered in the literature.
 Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
 
-% Japan is a country with a peculiar public transport system.
+    Japan is a country with a peculiar public transport system.
 The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
@@
 
-% Japanese convenience stores, on the other hand, are also famous worldwide.
+    Japanese convenience stores, on the other hand, are also famous worldwide.
 Japanese convenience stores are a haven for the traveler in need.
@@
 
-% Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
+    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
 While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
@@
 
-% \section{Limitations and Future Work}\label{limitations}
-
-  % This paper is not without its limitations.
+\section{Limitations and Future Work}\label{limitations}
+
+  This paper is not without its limitations.
 We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
 Following that, we attempted to understand the context that these words were being used in by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword, and doesn't follow the upstream or downstream path down further connections.
+However, the study is limited in that it only analyzes the words directly related to each keyword, and doesn’t follow the upstream or downstream path down further connections.
 This means that if the words are used in combination with other keywords we did not trace the effects of multiple contradicting statements.
-For example, in the sentence "The room is good but the food is lacking", we would extract "good food" and "lacking food", but do not consider the fact that both occurred in the same sentence.
-
-  % In this study, we analyzed the differences in customers expectations at different levels of \textit{Omotenashi} by dividing our data into price ranges.
-However, in the same price range, say the high expenses ones, we can find both a western style five stars resort as well as a high end Japanese style \textit{Ryokan}.
+For example, in the sentence ``The room is good but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
+
+  In this study, we analyzed the differences in customers expectations at different levels of \textit{omotenashi} by dividing our data into price ranges.
+However, in the same price range, say the high expenses ones, we can find both a western style five stars resort as well as a high end Japanese style \textit{ryokan}.
 Services offered in these hotels are very high quality, although very different in nature.
@@
 
-  % Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
+  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
 We could not analyze these populations because our team members do not know those languages.
@@
 
-  % In future work, we plan to investigate further into this topic.
+  In future work, we plan to investigate further into this topic.
 We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
@@
 
-% \section{Conclusion}\label{conclusion}
+\section{Conclusion}\label{conclusion}
 

### 2020-09-28 1_manuscript/Chinese_keys_list.tex
Back on track, copied from recovery pdf from 2020 sep 27 20:00

\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)
\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)
\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)
\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)
\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)
\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)
\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)
\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)
\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)
\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)
\begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)
\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)
\begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)
\begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)
\begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station)
\begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)
\begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)
\begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)
\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)
\begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel)
\begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room)
\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)
\begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel)
\begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility)
\begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel)
\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)
\begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed)
\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)
\begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge)
\begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel)
\begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position)
\begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service)
\begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel)
\begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic)
\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)
\begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration)
\begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service)
\begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment)
\begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket)
\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)
\begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station)
\begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room)
\begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast)
\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)
\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)
\begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market)
\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)
\begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room)
\begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club)
\begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level)
\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)
\begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up)
\begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station)
\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)
\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)
\begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain)
\begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service)
\begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu)
\begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new)
\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)
\begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience)
\begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market)
\begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet)
\begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location)
\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)
\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)
\begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)
\begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)
\begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography)
\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)
\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)
\begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)
\begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities)
\begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities)
\begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel)
\begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service)
\begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment)
\begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility)
\begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel)
\begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room)
\begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop)
\begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast)
\begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel)
\begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration)
\begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste)
\begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect)
\begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location)
\begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture)
\begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building)
\begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance)
\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)
\begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration)
\begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room)
\begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling)
\begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room)

### 2020-09-28 1_manuscript/itt-emotion.tex
Back on track, copied from recovery pdf from 2020 sep 27 20:00

@@
 The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite{al2015characteristics}.
+With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
 Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite{engel1990}.
+However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}.
 Thus, it could be theorized that their satisfaction factors should be different.
@@
   This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast the satisfaction and dissatisfaction factors of both customer groups using natural language processing to study commonly used word pairings.
+We aim to contrast the satisfaction and dissatisfaction factors of both customer groups across several price ranges using machine learning to classify the sentiment of texts, and natural language processing to study commonly used word pairings.
 More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups.
@@
 
-  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between cultures.
+  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
 These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction.
@@
 There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{Omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
+Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
 However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
@@
     \label{rsq:omotenashi}
-    To what degree are Chinese and Western tourists satisfied with Japanese \textit{Omotenashi} factors such as staff behavior or service?
+    To what degree are Chinese and Western tourists satisfied with Japanese \textit{omotenashi} factors such as staff behavior or service?
     \end{rsq}
@@
     \label{rsq:omotenashi_both}
-    Do Western and Chinese tourists have a different reaction to Japanese \textit{Omotenashi} factors such as staff behavior or service?
+    Do Western and Chinese tourists have a different reaction to Japanese \textit{omotenashi} factors such as staff behavior or service?
     \end{rsq}
@@
 
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defining customer satisfaction as the realization or overcoming of expectations towards the service.
+    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
 \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
@@
     In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
+
     Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}.
@@
 To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
-One example is \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money.
-Another is  \cite{bauer1993changing}, where Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
-Another example is \cite{kim2000}, where American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
+One example is a study by \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money.
+Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
+Another study, done by \cite{kim2000}, found that American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
 
@@
     More recent studies have surfaced as well.
-A cross-country study \cite{FRANCESCO201924} using posts from U.S.A.
+A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
 citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
@@
 customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
+Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
 tourists using text mining techniques and more massive datasets, although in a restaurant context.
@@
 Another difference with our study is that of the context of the study.
-The first study \cite{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
+The first study \cite[][]{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
 and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing.
@@
 This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite{bauer1993changing}, tourist motivation \cite{kim2000}, and closer to our study, satisfaction levels \cite{choi2000}.
+These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
 However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite{JIA2020104071, HUANG2017117}.
+Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
 One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924, JIA2020104071, HUANG2017117} have a multi-national focus, we instead focus on Japan.
+While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
 The focus on Japan is important because of its leading rank in hospitality across all types of businesses.
@@
 Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.]{kim2017362, alsmadi2018}.
+In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
 
@@
 We show an example of these dependencies in Figure \ref{fig:depparse}.
-In this study we use the Stanford NLP Dependency Parser, as described in \cite{chen-EMNLP:2014}.
+In this study we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
 A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
@@
     The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite{powers2011}.
+Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
 The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
@@
     \centering
-    \caption{English and Chinese comparison of the top 10 positive keywords per price range.}
+    \caption{English and Chinese comparison of the top 10 positive keywords.}
     \label{tab:freq_res_pos}
@@
                                                          & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 3258  & friendly    & 5606  \\ \hline
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
     \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
@@
                                                          & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 541   & friendly    & 1001  \\ \hline
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
     \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
@@
                                                          & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (surroundings)    & 157   & location    & 799   \\  
+                                                         & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
                                                          & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
@@
       \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords per price range.}
+      \caption{English and Chinese comparison of the top 10 negative keywords.}
       \label{tab:freq_res_neg}
@@
     \label{tab:zh_hard_soft_keywords}
-    \resizebox{\textwidth}{!}{%
+    \resizebox{0.7\textwidth}{!}{%
     \begin{tabular}{|c|l|l|}
@@
     \label{tab:en_hard_soft_keywords}
-    \resizebox{\textwidth}{!}{%
+    \resizebox{0.7\textwidth}{!}{%
     \begin{tabular}{|c|l|l|}
@@
 For example, English-speaking customers mentioned tobacco smell in many reviews, while it wasn’t statistically identified as a problem at all for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``shopping'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10
-    positive keywords list for English-speakers.
+On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
+Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
 
@@
 
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``old'' or ``outdated'', or ``obsolete'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
+    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
 This is, however, a hard attribute, and is unlikely to change for most hotels.
@@
 Other mentions are also big markets nearby, or a big bed.
-We can observe that across different price ranges, the usage of the word ``big'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``big space'' or ``large area'', we can see that there are also many references to the public bathing facilities in the hotel.
-In Japan, there is what is called \textit{sent\=o}, which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called \textit{onsen}.
+We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels.
+Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
+We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
+In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
+On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
 They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
@@
 Cleanliness, on the other hand, is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``clean room'' at the top rank of all price ranges, and then variably ``clean hotel'', ``clean overall'', ``clean environment'', and ``clean facilities'', among other examples.
-In negative reviews, there is a mention of criticizing the ``general hygiene'' of the hotel, although it’s an uncommon pair.
+We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
+In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it’s an uncommon pair.
 We can therefore assert that cleanliness is an important soft attribute for Chinese customers, and that they are mostly pleased, with their expectations being met.
@@
 While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' and in a lower ranking.
-In contrast, the word ``breakfast'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``breakfast'' is also observed across all price ranges, although at different priorities in each of them.
+In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
+The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
 However we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``not bad'' is paired with ``breakfast'' in four of the seven price ranges that had reviews available as part of the top 4 pairings, and only slightly lower on other categories, although it is not shown on the table.
+Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges that had reviews available as part of the top 4 pairings, and only slightly lower on other categories, although it is not shown on the table.
 Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast as a strategy to increase good reviews.
@@
 When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service related concepts that the Western tourists are disappointed with when they react negatively.
-The word ``great'', which is also high in most price ranges, and the top keyword in the highest priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location : 2313'', ``great view : 1099'' and ``great service : 841'', if we include the counts from all the price ranges together.
+The word ``great'', which is also high in most price ranges, and the top keyword in the highest priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together.
 Japanese high standards in hospitality very likely influenced this result.
@@
     The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``nice location'', ``near subway station'', ``near subway'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``traffic'', ``shopping'', ``subway'', and ``surroundings'' for Chinese speakers.
+In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
 All of these keywords, as well as their location in the priorities of each population across the price ranges, signal that while it was not the priority for either of them, the hotel’s location is a secondary but still important point in the hotel’s satisfaction.
@@
 
-% \section{Discussion}\label{discussion}
-
-  % The results indicate that our hypothesis - Chinese and Western tourists have different priorities in hotel attributes that lead to their satisfaction and dissatisfaction - is correct.
-Furthermore, they indicate that, in the context of Japanese hospitality, only Western customers show satisfaction from staff and service amongst their top detected factors.
-Below we explore the possible interactions with \textit{Omotenashi}, what the differences between Chinese and Western tourists were, what is the possible cause for them, and what they imply for the industry.
-We also discuss the differences between managerial and environmental elements of the hotel and how they contribute to the satisfaction of customers in light of the results from our third hypothesis - Satisfaction and dissatisfaction stem from both internal (managerial) and external (environmental) attributes of the hotel.
-
-  % \subsection{Western and Chinese tourists in the \textit{Omotenashi} environment}\label{disc:omotenashi}
-
-    % To this day, scholars continue to correct our historical bias towards the west.
+\section{Discussion}\label{discussion}
+
+  Below we explore the possible interactions with \textit{omotenashi}, what the differences between Chinese and Western tourists were, what is the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
+We also discuss the differences between hard and soft attributes of the hotel and how they contribute to the satisfaction of customers.
+
+  \subsection{Western and Chinese tourists in the \textit{omotenashi} environment}\label{disc:omotenashi}
+
+    To this day, scholars continue to correct our historical bias towards the west.
 In this time, studies have determined that different cultural backgrounds lead to different expectations, which in turn influence the satisfaction of tourists.
@@
 However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{Omotenashi}, excels, and is considered the highest standard across the world.
+The spirit of hospitality and service, \textit{omotenashi}, excels, and is considered the highest standard across the world.
 Can such an environment affect different cultures equally?
@@
 
-    % Our results indicate that Western tourists are the most satisfied with friendly and helpful staff in Japan.
+    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
 As explained earlier in this paper, Japan is famous for its customer service all over the world.
@@
 However, for some customers, this could be the best way they have been treated until that moment.
+Now, in higher priced hotels, the adjectives used to praise the service also go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
 We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in the satisfaction of Western tourists.
 
-    % However, we can see from the rest of the western keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
+    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
 Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
+This is particularly true at hotels below 50,000 yen per night.
 The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench, and general dirtiness.
@@
 
-    % According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
+    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
 When presented with Japanese hospitality, this expectation is met and overcome.
-However, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-We could theorize that despite being presented with high standard hospitality, it is ignored.
-It could be that their culture does not hold the expectation initially.
+In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
+However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
+Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
+
+    It could be that Chinese culture does not hold the expectation of high level service initially.
 That is, when an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-
-    % On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
+On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
 It is necessary to note the difference between these two phenomenons.
@@
 For greater satisfaction, the existence of a need being met is necessary.
-
-    % However, another possibility presents itself when we observe the Chinese tourists' dissatisfaction factors.
+However, since the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service, we cannot say that they aren’t satisfied in this matter, but rather that they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
+
+    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
 Chinese tourists may have expectations about the treatment towards the Chinese visitors that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite{heinrich2012making, coulmas2002japan}.
+Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
 While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
@@
 
-    % Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
+    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
 This study brought us closer to the answer.
 On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological place.
+In that case, it appears that the difference stems from a psychological source.
 Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
@@
 
-    % It is unclear from our results which of these could be the case.
+    It is unclear from our results which of these could be the case.
 One thing is clear for hotel managers, however.
-Competing in \textit{Omotenashi} does include language services, especially in the international tourism industry.
+Competing in \textit{omotenashi} does include language services, especially in the international tourism industry.
 Better multilingual support can only improve that already high standard in Japan.
@@
 
-  % \subsection{Managerial vs. Environmental satisfaction}\label{disc:man_env}
-
-    % As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on internal or managerial attributes of the hotel and their influence on customer satisfaction.
-Examples of managerial attributes include staff behavior, facilities, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004, choi2001}.
-However, external or environmental attributes, such as the location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers' online reviews, we can see in their priorities the importance of those environmental or managerial attributes.
-
-    % From Table \ref{tab:hyp_man_env} and appendix Tables \ref{tab:man_env_pos} and \ref{tab:man_env_neg}, we can see that in regards to satisfaction, 40\% of keywords used by Chinese tourists are of an environmental nature (namely ``transportation", ``close", ``subway", and ``shopping"), while a lower 30\% is managerial in nature (and an undefined 30\%).
-However, two of these managerial words are all concentrated at the top of the list (``big", ``clean").
+  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
+
+    As we stated in section 3.2, previous research is focused mostly on soft attributes of the hotel and their influence on customer satisfaction.
+Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
+However, hard attributes, such as the location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
+Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see in their priorities the importance of those hard or soft attributes.
+
+    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general 68\% of the top 10 keywords are hard factors, while only 20\% are soft factors.
+The rates are similar for most price ranges, excepting the highest priced hotels, where a 35\% of the keywords are undefined.
+However, the soft attributes are still similar at 18\%.
+However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
 Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
 That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite{Saulton2017}.
+Some scholars argue that different cultures have different room size perceptions (Saulton et al.
+2017).
 Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others' cultures, so there can be differences between South Korea and China in room size perception.
+We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
 However, an interesting point appears.
 It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-The dissatisfaction list for Western tourists could indicate that they perceive the rooms or bathtubs as small compared to Chinese tourists that praise them.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``environment" as well.
-
-    % In comparison, English speakers are mostly satisfied with managerial attributes of the hotel, with keywords such as ``staff", ``clean," ``helpful," and ``friendly," to name a few.
-English-speaking customers also have managerial attributes at the very top of their list, except for the environmental nature of the location of the hotel.
-If one considers both Chinese and Western tourists' satisfaction, a hotel can improve in ways that will attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with environmental attributes overall, hotels would have to compete solely on their location.
-
-    % For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
+Westerners only start placing a priority on praising room size as the price of the hotel goes up.
+We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery (Ryan and Mo 2001).
+These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well, which is present in hotels priced at more than 20,000 yen per night.
+
+    In comparison, English speakers are mostly satisfied with soft attributes of the hotel, if we observe Figure \ref{fig:hard_soft_en}, where soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
+This price range corresponds to affordable business hotels, for example.
+English-speaking customers also have soft attributes at the very top of their list, except for the hard attribute that is the location of the hotel, which is consistently around the middle of the top 10 lists for all price ranges.
+If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve in ways that will attract more customers in the future.
+If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
+
+    For both customer groups, in general, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
+However, it is interesting to note that while English-speaking customers complain about price with a lower rank in the list in lower priced hotels, while the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
 A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
@@
 Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are expensive, ranging from 5,000 to 12,000 yen per night.
+Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
 For comparison, hotels in the USA with a similar quality can be half the price.
 
-    % Similarly, most of the dissatisfaction is caused by issues that could be solved with improved management.
-Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with smoke smells, or improving the bedding, all of which can be costly.
-However, if hotels want to attract more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best suited to which customer groups.
-
-    % Now, a point of interest in this study is the difference in how managerial and environmental factors concern Chinese and Western tourists.
-We can see that for Chinese customers, while the top positive keyword is managerial, the size of a room is hardly modifiable once the hotel's construction is complete.
-The second keyword follows as a managerial factor as well.
-Except, this time, hotel management can readily improve the cleanliness of their hotel.
-The rest of the positive keywords, however, are either undefined or environmental.
-Once the location and construction of the hotel are set, not much can be done to satisfy a Chinese tourist further.
-On the other hand, one can turn the dissatisfaction factors into satisfaction by focusing on those for improvement.
-As mentioned before, Chinese language availability is another managerial attribute that can be improved with investment in staff and training.
-
-    % Western tourists, on the other hand, are all around both satisfied and dissatisfied with mostly managerial factors, with a 50\% of the top 10 satisfaction factors and a 100\% of the top 10 dissatisfaction factors coming from managerial attributes.
+    For dissatisfaction, including all prices, both Chinese and Western customers have around half of the dissatisfaction being caused by issues that 1040 could be solved with improved management.
+Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding, all of which can be costly.
+However, if hotels want to attract more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best 1045 suited to which customer groups.
+Hotels can use the price range categorization in order to choose the appropriate strategy as well.
+However, for Chinese customers, once the location and construction of the hotel are set, not much else can be done to satisfy them further.
+As mentioned before, Chinese language availability is another soft attribute that can be improved with investment in staff and training.
+
+    Western tourists, on the other hand, are all around dissatisfied with mostly soft attributes, with a lowest of 35\% in the highest price range where undefined factors are the majority, and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
 The room for improvement for Western tourists is more extensive than their Chinese counterparts, and as such, present a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite{choi2000}.
-With bigger returns on managerial improvements, it seems like investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
+As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
+On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
+With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
 Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
 
-    % The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
+    The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
 Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on environmental attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    % The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of managerial or environmental attributes.
+However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
+
+    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
+This premise also plays a role in the differentiation between the preference of hard or soft attributes.
 Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
 Chinese historical backgrounds of Confucianism, Taoism and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite{gao2017chinese}.
-However, one could argue that there is a Chinese cultural attribute that emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite{kim2000}.
+However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
+Nevertheless, one could argue that there is a Chinese cultural attribute that emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
+According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
 A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: disc:implications

@@
 
-    \begin{figure}[h]
+    \begin{figure}[ht]
         \centering
@@
 
-    \begin{figure}[h]
+    \begin{figure}[ht]
     \centering
@@
     % \useunder{\uline}{\ul}{}
-    \begin{table}[]
+    \begin{table}[ht]
     \centering
@@
     % \usepackage{graphicx}
-    \begin{table}[]
+    \begin{table}[ht]
       \centering
@@
     \begin{landscape}
-    \begin{table}[]
+    \begin{table}[p]
       \centering
@@
   % \usepackage{graphicx}
-  \begin{table}[]
+  \begin{table}[ht]
     \centering
@@
 
-  \begin{figure}[h]
+  \begin{figure}[ht]
       \centering
@@
   % \useunder{\uline}{\ul}{}
-  \begin{table}[]
+  \begin{table}[ht]
     \centering
@@
 
-  % \subsection{Implications for hotel managers}\label{disc:implications}
-
-    % Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-Chinese tourists are not experiencing the best that \textit{Omotenashi} has to offer.
-Either they do not get much satisfaction from hospitality or feel that basic language and communication needs are not being met.
-On the other hand, Western tourists are elated with Japanese hospitality.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
+  \subsection{Price range differences}\label{disc:price}
+
+    % some big paragraph about changing the way they speak, and about expectations, nice surprise, etc. 
+    % Introduce the concept of logical expectations vs feelings expectations.
+    % For example expecting it to be clean: ok just as expected / what?! it's not clean?! / cigarette
+    %             expecting them to be nice: Still feel happy after they were nice
+    % Omotenashi comes in play here.
+
+    % paragraph about differences in perceptions from each culture
+    %
+
+    % paragraph about things that stay the same across all prices
+
+    %
+
+  \subsection{Implications for hotel managers}\label{disc:implications}
+
+    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
+Chinese tourists, as a whole, are not showing the most satisfaction towards \textit{omotenashi}, instead focusing on the hard attributes of a hotel.
+Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression.
+On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard set ones.
+The other conclusion is that managerial decisions will mostly benefit Western tourists, excepting that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
 Japan is recently seeing an increase in Chinese students as well as Western students of universities.
@@
 
-    % To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
+    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
 It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
@@
 Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free.
-
-    % Environmental factors, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
+Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
+
+    Hard attributes, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
 As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
@@
 
-    % It is left to the managers to consider their business model for the next strategy.
+    It is left to the managers to consider their business model for the next strategy.
 One option could be attracting more Chinese customers in number with their observed low budgeting.
@@
 For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase.
+On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
 

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: disc:price

@@
 
-  \subsection{Price range differences}\label{disc:price}
-
-    % some big paragraph about changing the way they speak, and about expectations, nice surprise, etc. 
-    % Introduce the concept of logical expectations vs feelings expectations.
-    % For example expecting it to be clean: ok just as expected / what?! it's not clean?! / cigarette
-    %             expecting them to be nice: Still feel happy after they were nice
-    % Omotenashi comes in play here.
-
-    % paragraph about differences in perceptions from each culture
-    %
-
-    % paragraph about things that stay the same across all prices
-
-    %
+  \subsection{Satisfaction across different price ranges}\label{disc:price}
+
+    In previous sections of this paper, we have mentioned the differences reflected in the results across hotel price ranges.
+Nevertheless, it is interesting to discuss this further.
+The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction of the same topics.
+We can know this by observing the adjective + noun pairs, and finding pairs with different adjectives for the same nouns.
+For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower priced hotels.
+In contrast, the adjectives that pair with the same nouns for more highly priced hotels are ``wonderful'' and ``excellent''.
+In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
+We can infer that the level of satisfaction is higher, and that it influences the way that customers write their reviews.
+However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
+Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
+
+    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where it is the meeting or exceeding of expectations that produces satisfaction.
+Therefore, the lack of meeting of expectations would cause dissatisfaction.
+In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
+This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
+As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarette, can lead to disappointment or outrage.
+However, we consistently see customers with high expectations for high class hotels react even more positively when satisfied.
+In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
+We argue that these are two different kinds of interactions with expectations.
+We can observe logical expectations, where customers set a standard in their mind that the service must not fall below or they will be disappointed.
+For example, a customer being disappointed with dirty rooms or cigarette smell.
+In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience, but they don't measure it against any sort of standards.
+For example, having a nice customer service experience, or being treated hospitably by the staff at a high class hotel.
+Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction.
+This is where \textit{omotenashi} comes into play, and enhances the experience of the customers.
+
+    Now, there are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
+For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
+In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
+In fact, it is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and citing \cite{japan2014consumption}, shows that common products besides food and drink are electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit.
+There is an understanding that the objective of shopping in Japan has more to do with the quality of the items rather than their relation to the touristic attractions.
+Our results suggest that Western tourists are engaging more in the touristic attractions in comparison with shopping activities.
+Another interesting difference is that English-speaking tourists start using negative keywords about the price of the hotel only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
+In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
+Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
+
+    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for the customers of each culture.
+For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
+Satisfaction for cleanliness for both cultures stays constantly part of the top 10 keywords, with the exception of the most expensive one, where other keywords take its place in the ranking, although it is still high on the list.
+Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
+Transport and location, as discussed in section \ref{disc:location}, is also important for hotels of all classes and prices.
+While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
+This suggests that culturally the customers have a certain bias to consider some attributes more than others.
 

### 2020-09-28 1_manuscript/itt-emotion.tex
Add: conclusion, upd: moved chinese keyword list

@@
 
-  % In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels.
-We extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-
-  % In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, confirming our hypothesis \ref{hyp:omotenashi_en}.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction.
-As such, our hypothesis \ref{hyp:omotenashi_zh} is rejected.
-Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}.
-One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers.
+  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
+To answer our research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
+We used these keywords for sentiment classification via an SVC, and then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
+We divided this data by sentiment and by hotel price range, considering the most expensive price for a room for one night.
+
+  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness and other attributes relating to services and hospitality of the hotel.
+However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location or the convenience of the hotel.
+We found that both cultures have a different reaction to this environment of hospitality, and both cultures have a different way of reacting to different prices.
+From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
+One theory is that while they are being treated well and they react positively, the environment is not compatible with them because of language or culture barriers and it lessens their experience.
 The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
 We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-
-  % Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to managerial attributes of a hotel or environmental attributes of the hotel.
-Managerial attributes are those that they can be changed via managerial decisions without relocating.
-On the other hand, environmental attributes are things like location, closeness to shops, or public transport.
-We found that both are included in the satisfaction and dissatisfaction of both customer groups, confirming our hypothesis \ref{hyp:man_env}.
-We also found that most of the Western customer satisfaction (50\% of the top 10 words) and dissatisfaction (100\% of the top 10 words) stems from managerial attributes of the hotel.
-
-  % In contrast, environmental attributes only make for a smaller portion of the factors (40\% of the top 10 satisfaction keywords).
-In the case of Chinese customer satisfaction, the top of the list was managerial (30\% of the top 10 words), and a more significant portion, although lower in its ranking, was environmental (40\%).
-For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental.
-We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies.
-One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast.
+On the other hand, Western tourists, even when they hold high expectations in a highly priced hotel, show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
+We consider that Western tourists are more reactive to \textit{omotenashi} than their Chinese counterparts.
+
+  Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to hard and soft attributes of a hotel.
+Soft attributes are those that can be changed via managerial decisions, improvement on services or small investments.
+On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
+We found that for satisfaction, Western tourists favor soft attributes, while Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges.
+For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or the smell of cigarette in rooms.
+In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
+
+  For hotel managers, one possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
+They are less satisfied with soft attributes, but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
 Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.

### 2020-09-28 1_manuscript/itt-emotion.tex
Add:abstract

@@
 
-  % The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
+  The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
 Recent years show a steady increase in international tourists coming to Japan.
@@
 Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Asian and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating.
+Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating.
 Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the hotel's purely managerial attributes or be more concerned with environmental factors that hotel management cannot change?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors.
+Will they be satisfied with the soft attributes a hotel can change or be more concerned with hard attributes that hotel management cannot change?
+We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
 Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
+We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
 We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior.

### 2020-09-28 3_review-responses/V1_review_responses/Reviewer_1_response.tex
moved sh files, improved sh, added previous review comments, indent party, updated .gitignore

\documentclass{letter}

% To insert commas into large numbers automatically
\usepackage{siunitx}

\begin{document}
\pagenumbering{gobble}

\textbf{Reviewer \#1 Response}

Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections. Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values. However, our conclusions and hypothesis testing remained largely unchanged by this. We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript. The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi. In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?

\begin{quotation}
1. Machine learning

While this manuscript contains machine learning in its title, there is no major discussion about it. What is machine learning? How do the authors define it? Is data mining part of machine learning? If so, how so? Why is important or useful to use machine learning particularly for this study? What do the authors want to achieve with machine learning?  
\end{quotation}

Machine learning and data mining often overlap, which is why we had an oversight in defining both of them and explaining their differences. In a journal about Information Technology, we assumed it was general knowledge, but we added it for consistency and for a more widespread reader understanding. In the section previously titled 3.4 "Data mining, knowledge discovery and sentiment analysis", thus renamed 3.4 "Data mining, machine learning, knowledge discovery and sentiment analysis" we introduced two paragraphs defining machine learning, its importance of use for analyzing larger samples, and what we can achieve with it. However the manuscript title changed from another reviewers request.

\begin{quotation}
Also, the manuscript can be improved by justifying and elaborating on the necessity of a large sample. Why is it so important about analysing a large sample? What problem did a "small" sample used in existing literature cause? 
I recommend the authors to prepare a section dedicating to these questions.
\end{quotation}

In regards to the sample size, a paragraph in previously 3.2, now section 3.3 "Chinese and Western tourist behavior" already describes the importance of these bigger samples. We added a bit of text to expand on this importance.

"Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire). This means that the factors will be selected through statistical methods alone. This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. This large variety of opinions in a big sample, added to the automatic findings of statistical text analysis methods, is what gives an advantage to our study in comparison to others with smaller samples. In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature."

\begin{quotation}
2. Theoretical discussion on culture
I also recommend the authors to develop the story on culture with theoretical perspectives. Why would Westerners show different preferences from Chinese? Why do Westerners value soft attributes (or managerial factors) like staff more while Chinese value hard attributes (or environmental factors) like size? Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)? While this study did not measure "culture" per se, I believe the authors can find theoretical explanations.
\end{quotation}

Another reviewer pointed out this, as well as suggesting a new research rationale. Because of it, we added new content to the introduction, changed the abstract and titles, as well as adding a new section in the discussion with theoretical perspectives on the context of Japanese hospitality. It is right that our study did not measure "culture", so we can't be sure of the explanations to certain aspects, although we do explain in the literature review that it has been previously studied how different backgrounds and cultures result in different expectations and as such, different satisfaction factors.

In summary, our expanded discussion is about the differences between Chinese and Western tourists in the context of Japanese hospitality. Western tourists had hospitality and service related satisfaction keywords at the top of their priorities. However, Chinese tourists did not. We theorize this can be from two different causes. One theory is that the Chinese customers have different expectations based on their culture background, and that these expectations lead to different reactions. Specifically, not expecting something and then getting it could be less satisfying than getting an expectation met. Another theory is that despite being in the environment of Omotenashi, their language barriers are enough to disregard hospitality because of their unease or disappointment with the staff and communication availability.

We also expanded on the discussion section by adding more to the previously 7.5, now section 7.2 Managerial vs. Environmental satisfaction, as well as add reasoning to each discussion section as well. In this section we added potential ramifications of the distribution of these factors. While Westerners can be satisfied even more by improving on managerial factors, a big portion of Chinese satisfaction comes from environmental factors. This means that it could be harder for managers to achieve an improvement in their satisfaction. However, we also claim that improving on cleanliness and making hotels tobacco-free could be a solution that benefits both populations. If this is done in addition to improving Chinese language services, both populations can be satisfied further.

We added a section 7.3 Implications for hotel managers, where we discuss different strategies that managers could follow to improve on customer satisfaction for these populations. We propose two possible strategies, which are appropriate or not depending on a hotel business model. A hotel can aim to increase the numbers of Chinese customers by investing on Chinese language services, which are a larger population but spend less percentage of their budget on hotels. On the other hand, a hotel can aim to increase cleanliness and comfort, which are bigger investments, but would satisfy Western customers, who spend almost half their budget on hotels.

As for the comment "Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)?": They are both different. RBO results and our hypothesis testing showed that both satisfactory and dissatisfactory attributes are different for both cultures. Still, I understand that explaining the reasoning behind these results could improve the discussion.

\begin{quotation}
3. Restructing
I found the discussion section (7. Discussion) misrepresents. The section is mainly reporting the findings without in-depth discussion (e.g., discussion on the reason behind such findings). I recommend combining Sections 5 and 6 into one section as an analysis section; and rename 7 Discussion as 6 Results. As suggested in the earlier section, the authors can add a new discussion section with a theoretical discussion.
The current 6.1 section can be revised by presenting one-to-one or item-by-item comparison between Chinese and English-speaking customers. The current format is difficult to follow to see which attributes are similar or different between these two groups.
\end{quotation}

We added most of what was once in the discussion section to the results section, and added more in-depth discussion in section 7 as explained above. The subsections that moved up to the Results section were 6.2 Chinese tourists - A big and clean space, 6.3 Western tourists - A friendly face, and absolutely clean, 6.4 Tobacco, what’s that smell?, and 6.5 Location, location, location. The price section was deleted since it was short enough to be discussed elsewhere.

We revised the tables in what previously was 6.1 to present them side to side for better following the differences in keyword ranking. They are now tables 5 and 6.

\end{document}

### 2020-09-28 3_review-responses/V1_review_responses/Reviewer_3_response.tex
moved sh files, improved sh, added previous review comments, indent party, updated .gitignore

\documentclass{letter}

% To insert commas into large numbers automatically
\usepackage{siunitx}

\begin{document}
\pagenumbering{gobble}

\textbf{Reviewer \#3 Response}

Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections. Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values. However, our conclusions and hypothesis testing remained largely unchanged by this. We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript. The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi. In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?

\begin{quotation}
\#1 - Research rationale
The authors mentioned "Up until recently, most studies in tourist behavior have been biased for the Western world". Yet, to the best of my knowledge, there are fruitful studies examined Chinese consumers' hotel booking behavior

I searched and found that several similar studies have already been published recently like:
*  Francesco, G., \& Roberta, G. (2019). Cross-country analysis of perception and emphasis of hotel attributes. Tourism Management, 74, 24-42.
*  Huang, J. (2017). The dining experience of Beijing Roast Duck: A comparative study of the Chinese and English online consumer reviews. International Journal of Hospitality Management, 66, 117-129.
*  Jia, S. S. (2020). Motivation and satisfaction of Chinese and US tourists in restaurants: A cross-cultural text mining of online reviews. Tourism Management, 78, 104071.

The authors are encouraged to review and indicate the existence of the above articles. To highlight the uniqueness of this work, the authors can highlight how the current study differs from other published works in terms of "research focus", "methodological approach", "study context" or/and "data size"
\end{quotation}

I think the misunderstanding comes from the phrasing of our sentence. "Up until recently" does not mean "Until now". We mean to say that in the last recent years the focus has changed. We changed the phrase to reflect this in a more understandable manner. However, we are glad to add these articles to our manuscript literature review and highlight the differences.

In addition, we found a new rationale for our manuscript that makes it stand against the rest: the study context of Japanese hospitality (omotenashi). The different cultures react differently to this high standard hospitality environment, which is interesting in its own regard. We added a new section 3.1  Japanese hospitality: Omotenashi to explain it and developed hypotheses from that context.

We added a paragraph in the beginning of our introduction, modified the abstract, and added the literature review in this context in previously 3.2, now section 3.3 Chinese and Western tourist behavior. We also changed the title to emphasize this context as well.

Because of the change in rationale, new hypotheses were added as well. The main problem in our refocused paper is: In such a high-standard hospitality environment, will the cultural backgrounds react similarly or differently to them? Will they both be satisfied more with hospitality and service related topics than with other topics, or will they ignore this environment?

We found that Chinese tourists don't react as positively to this hospitality as Westerners did. We have two theories which we discussed in section 7. One is that they don't have the same expectations. Getting what they don't expect leads to less satisfaction than if they were expecting it. Another theory is that the language barrier poses an obstacle to the enjoyment of this hospitality.

\begin{quotation}
\#2 - Research objectives
*  Section 2 shows that the objective of this study is to determine the difference in preferences between Chinese- and English-speaking customers of Japanese hotels using text-mining techniques. Yet, according to my review, this study solely examines what English- and Chinese-speaking customers concern most when they evaluate Japanese hotels

*  I can accept the assertion that the findings can reflect the differences in factors driving satisfaction and dissatisfaction between Chinese- and English-speaking customers. But the findings cannot reflect their preferences
\end{quotation}

In a previous version of our manuscript, we had another reviewer point out that "satisfaction and dissatisfaction factors" was a long way to say preferences, which is why we had it corrected this way. Based on this more recent review, however, we happily reverted it to the previous terminology. This is reflected in the manuscript and title. We also modified the research objective to match the new research rationale that was encouraged in a previous point.

\begin{quotation}
\#3 - Literature review
*  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.

*  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist
\end{quotation}

As to the first point, we believe there is always a necessity in science to re-examine and avoid making assumptions. In addition to this thought, other reviewers have found the hypotheses helpful in the flow of the manuscript, so we decide to keep them as part of the manuscript. As part of the rationale change, we also added new hypotheses.

For the second point, we agree that adding literature was necessary as per a previous point. We also agree that displaying them such a table would give a helpful overview of the current research in this topic for our paper and have included it in the previously 3.2, now section 3.3.

\begin{quotation}
\#4 - Method
*  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period. The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts

*  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc
\end{quotation}

In regards to this point, we apologize and would like to explain. In the original manuscript, the experiments were done while the data was still being collected further. After finishing the manuscript, the original data had changed. Not only this, but we realized our mistake from this and another comment from a different reviewer. Indeed the data should reflect the same kinds of hotels, the same kinds of categories, the same time period and attributes. Since we did not data on the attributes of each hotel, we decided to match both English and Chinese comments to come from exactly the same hotels, matching by name. This reduced the number of comments on each language, but it made the data fairer. We don't have data on what type of hotel or star rating they had since this data wasn't available to us, but we can be sure they are the same 580 hotels for both kinds of reviews.

Because of this change in datasets, we also redid the entire experiment, calculating the frequencies and RBO again accordingly.

The time period resulted to be from July 2014 to July 2017. The price range was from 2000 yen per night, to 188,000 yen a night.

We added this paragraph to the Data collection section:

"However, in order to make the data and comparisons we draw from each of these datasets fair, we filtered both databases to only contain reviews from hotels that were in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580}, and that the common date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general."

\begin{quotation}
\#5 - Discussions and Conclusions
*  Regarding the discussion part, the authors discussed the differences (in sections 7.1 and 7.2) and the similarities (in section 7.3 and 7.4) of Western and Chinese consumers' satisfaction and dissatisfaction factors.  However, the authors discussed the difference in section 7.5 again. Also, the smell of Tobacco was already mentioned in the section 7.2 ("the most common complaint regarding cleanliness was about the carpet, followed by complaints about stains, and cigarette stench in the curtains"). This is a little bit confusing, and I kindly suggest the authors to re-organize the discussion part

*  The manuscript does not include much discussions about its theoretical contributions. Again, how what new knowledge was brought by this study? Any contrasting findings were found?
\end{quotation}

Because of our change in research rationale, we added new content to the introduction, changed the abstract and titles, as well as adding a new section in the discussion with theoretical perspectives on the context of Japanese hospitality. It is right that our study did not measure "culture", so we can't be sure of the explanations to certain aspects, although we do explain in the literature review that it has been previously studied how different backgrounds and cultures result in different expectations and as such, different satisfaction factors.

In summary, our expanded discussion is about the differences between Chinese and Western tourists in the context of Japanese hospitality. Western tourists had hospitality and service related satisfaction keywords at the top of their priorities. However, Chinese tourists did not. We theorize this can be from two different causes. One theory is that the Chinese customers have different expectations based on their culture background, and that these expectations lead to different reactions. Specifically, not expecting something and then getting it could be less satisfying than getting an expectation met. Another theory is that despite being in the environment of Omotenashi, their language barriers are enough to disregard hospitality because of their unease or disappointment with the staff and communication availability.

We also expanded on the discussion section by adding more to the previously 7.5, now section 7.2 Managerial vs. Environmental satisfaction, as well as add reasoning to each discussion section as well. In this section we added potential ramifications of the distribution of these factors. While Westerners can be satisfied even more by improving on managerial factors, a big portion of Chinese satisfaction comes from environmental factors. This means that it could be harder for managers to achieve an improvement in their satisfaction. However, we also claim that improving on cleanliness and making hotels tobacco-free could be a solution that benefits both populations. If this is done in addition to improving Chinese language services, both populations can be satisfied further.

We added a section 7.3 Implications for hotel managers, where we discuss different strategies that managers could follow to improve on customer satisfaction for these populations. We propose two possible strategies, which are appropriate or not depending on a hotel business model. A hotel can aim to increase the numbers of Chinese customers by investing on Chinese language services, which are a larger population but spend less percentage of their budget on hotels. On the other hand, a hotel can aim to increase cleanliness and comfort, which are bigger investments, but would satisfy Western customers, who spend almost half their budget on hotels.

We added most of what was once in the discussion section to the results section, and added more in-depth discussion in section 7 as explained above. The subsections that moved up to the Results section were 6.2 Chinese tourists - A big and clean space, 6.3 Western tourists - A friendly face, and absolutely clean, 6.4 Tobacco, what’s that smell?, and 6.5 Location, location, location. The price section was deleted since it was short enough to be discussed elsewhere.

We also revised the tables in what previously was 6.1 to present them side to side for better following the differences in keyword ranking. They are now tables 5 and 6.

\begin{quotation}
\#6 - Minor
*  The manuscript title should be revised. The phrase "drivers of satisfaction and dissatisfaction" should be added. Also, instead of mentioning "with machine learning" in the manuscript title, the authors may consider highlighting "using Rank-biased Overlap measure"

\end{quotation}

We reconsidered the title from this and another point in this review as follows:

"Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures"

This reflects both points in this comment and focuses on the change in research rationale, while also highlighting the method.

\end{document}

### 2020-09-28 3_review-responses/V1_review_responses/Reviewer_5_response.tex
moved sh files, improved sh, added previous review comments, indent party, updated .gitignore

\documentclass{letter}

% To insert commas into large numbers automatically
\usepackage{siunitx}

\begin{document}
\pagenumbering{gobble}

\textbf{Reviewer \#5 Response}

Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections. Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values. However, our conclusions and hypothesis testing remained largely unchanged by this. We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript. The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi. In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?

\begin{quotation}
This study used Ctrip as the data base. However, majority users of Ctrip is Mainland Chinese, but Chinese-speaking tourists can also be Taiwanese, Malaysian Chinese, Singaporean Chinese and Hong Konger too. Therefore I suggest the authors change the term Chinese-speaking tourists to Mainland Chinese tourists.
\end{quotation}

Thanks for pointing this information out. We pointed this out in the text.

\begin{quotation}
In literature review, the authors listed three hypothesis relating to Chinese and English speaking tourists in 3.1 and then a separate section 3.2 to explain the difference between Chinese and Western tourists. I would suggest the authors combine these two sections so as to give a more comprehensive view on the setting of the three hypothesis.
\end{quotation}

We respectfully disagree with this suggestion since the content of section 3.1 and 3.2 are very different. While 3.1 sets the premise of differences in customer satisfaction and the reasoning behind them existing, 3.2 discusses previous literature on specific behaviors and cultures of each kind of tourist. Since we added a new section 3.1, these two sections are now 3.2 and 3.3 respectively.

\begin{quotation}
In formular (1), what are alpha, x and y?
\end{quotation}

We added a description of the formula to the manuscript, as well as a short description of the SVM algorithm to make it more understandable.

\begin{quotation}
In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted? Are the same hotels extracted from both Ctrip and Tripadvisor? How many hotels are there? I believe different types of hotels would have generated different satisfaction level and perspectives. Please provide more details about these hotels.
\end{quotation}

In regards to this point, we apologize and would like to explain. In the original manuscript, the experiments were done while the data was still being collected further. After finishing the manuscript, the original data had changed. Not only this, but we realized our mistake from this and another comment from a different reviewer. Indeed the data should reflect the same kinds of hotels, the same kinds of categories. Since we did not have these data, we decided to match both English and Chinese comments to come from exactly the same hotels, matching by name. This reduced the number of comments on each language, but it made the data fairer. We don't have data on what type of hotel or star rating they had since this data wasn't available to us, but we can be sure they are the same 580 hotels for both kinds of reviews.

Because of this change in datasets, we also redid the entire experiment, calculating the frequencies and RBO again accordingly.

The time period resulted to be from July 2014 to July 2017. The price range was from 2000 yen per night, to 188,000 yen a night.

We added this paragraph to the Data collection section:

"However, in order to make the data and comparisons we draw from each of these datasets fair, we filtered both databases to only contain reviews from hotels that were in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580}, and that the common date range for reviews was from July 2014 to July 2017. We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.

We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general."

\begin{quotation}
In Table 2, I am quite surprise to see that the last item "Chinese person" can be the top keywords with only 16 occurrences. Can the authors explain why there are so few negative Chinese keywords?
\end{quotation}

Since we repeated the experiment, the frequencies have changed, however this keyword still only has 16 occurrences. The lack of negative keywords comes from a peculiarity of the Chinese reviews from Ctrip. Most of the reviews point out the positive extensively, while only a few sentences are negative. It's a limitation of our paper that the negative keywords depend on the sample taken at the beginning, since we could not label more manually at the time.

\begin{quotation}
Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment". Can the authors explain further how this can be avoided in your data analysis?
\end{quotation}

One thing to note is that using SVM, we labeled sentences as positive or negative, so negative usage of the word when counting the frequencies is negligible. In addition to this, we also had the same question when we saw our results the first time, and took a small sample to observe the usage of the word. However we didn't deem it appropriate in the text at first, but with this comment and thinking it over once again, we have added the next paragraph to the manuscript:

>"From these two first ranking keywords (“big” and “clean”), we can assert
that room quality is the most critical satisfaction factor for Chinese customers. However, the word “big” is widespread in the language and could be used in different contexts to point out positive and negative aspects. Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word “big” in Chinese. A team of Chinese speaking lab members then pointed out the usage of the word. Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities."

\begin{quotation}
For the managerial and environmental keywords, what criteria were used for classifying these keywords? 
\end{quotation}

We explain the difference between managerial and environmental factors in different sections of the manuscript. However, since it might still be unclear, we specified the method for classifying the keywords in the Results section, adding the following text:

> "We manually labeled the top
625 keywords of each language into either managerial or environmental by considering how the word would be used when writing a review. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial. If the word is describing factors that are unchangeable by the staff or management, we consider them environmental. The interpretation of these keywords is shown in the Tables 8 and 9."

We also added the tables that were previously in the appendix clearing this issue into the main text for readability.

\begin{quotation}
Editorial issues
The Appendix is actually part of the manuscript. This manuscript contains too many Tables. First some was mentioned in the manuscript but appeared in Appendix. For example line 306, Table 7 and Section B was mentioned. What is Section B?  Please move all relevant tables to the manuscript but not in Appendix. I would suggest the authors to consider to either combine some of them or not to mention them in the manuscript. 
Besides, the numbering of the tables was not in sequence in the manuscript. Line 360, after Table 3 and 4, it suddenly jumps to Table 10.
\end{quotation}

We moved some tables that we deemed important out of the appendix, but other tables got removed as per this request. We also joined the tables with the top keyword results as per this and another reviewer's request.

\end{document}

### 2020-09-28 latexcompile.sh

@@ -17,7 +17,7 @@ DOCNAME="${INFILE%.*}"
 if [[ $ONLYCLEAN ]];
 then
     echo "Removing secondary files, no compile made"
-    rm *.blg *.bbl *.aux *.log *.thm *.out
+    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
 else
     if [[ $NOBIB ]];
     then
@@ -29,7 +29,7 @@ else
         echo "Skipping Bibtex from compile."
     else
         echo "Removing secondary files, starting from scratch"
-        rm *.blg *.bbl *.aux *.log *.thm *.out
+        rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
         pdflatex $DOCNAME.tex
         if [ $? -ne 0 ]; then
             echo "Compilation error. Check log."
@@ -41,7 +41,7 @@ else
     fi
     if [[ $CLEAN ]]; then
     echo "Removing secondary files"
-    rm *.blg *.bbl *.aux *.log *.thm *.out
+    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
     fi
 fi
 if [[ $VIEW ]]; then

### 2020-09-28 recursive_clean_latex_secondary_files.sh

@@ -1,5 +1,18 @@
 #!/bin/bash
 
+current="$(pwd)"
+if [[ $1 ]];then
+    if [[ -d "$1" ]] ; then
+        cd "$(readlink "$1")"
+    else
+        if [ -f "$1" ]; then
+            cd "$(dirname "$(readlink "$1")")"
+        else
+            echo "Arg must be a directory"
+        fi
+    fi
+fi
+
 find . -name '*.blg' -type f -delete
 find . -name '*.bbl' -type f -delete
 find . -name '*.aux' -type f -delete

### 2020-09-28 3_review-responses/V2_review_responses/Reviewer #1 Response.txt
Added review responses until before corrections from reviewer 5

@@
 Reviewer #1 Response
+
+Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment. I will also include quotes from Reviewer #5 where necessary, using '>>>' before it.
+
+In summary, we added two more layers to our study. We divided the data in price ranges, and we added automatic adjective + noun pairing counts, by using dependency parsing and part of speech tagging.
 
@@
 
-Comment #3 from Reviewer #3
-"#3 - Literature review
+>>>Comment #3 from Reviewer #3
+>>>"#3 - Literature review
     *  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.
@@
 
+After some thought, we do agree that the hypotheses are able to be removed without altering the objective of the paper at all.
+We changed them to "Research Questions" only with the purpose of referencing them throughout the main text, but they don't have to be proven or rejected anymore.
+
 ------------
@@
 
-Comment #4 from Reviewer #3
-"#4 - Method
+>>>Comment #4 from Reviewer #3
+>>>"#4 - Method
     *  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period.
@@
 
-Comment #4 from Reviewer #5
-"In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted?
+>>>Comment #4 from Reviewer #5
+>>>"In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted?
 Are the same hotels extracted from both Ctrip and Tripadvisor?
@@
 
-We added an extra layer to our research to overcome this limitation, although we admit that it's not fully encompassing the category or hotel type. We divided our datasets into price ranges. It is
+We added an extra layer to our research to overcome this limitation, although we admit that it's not fully encompassing the category or hotel type.
+We divided our datasets into price ranges.
+We chose the highest price available in each hotel for a single room and a single night.
+This way, even if most customers aren't staying in that room, we can categorize the hotels by their quality.
+For example, there's probably no capsule hotels with suite rooms that would offer very different experiences.
+This way we think that we can clearly distinguish cheaper hotels and hostels, from business hotels, and from Japanese style ryokan or resorts.
+Then we performed the analysis and updated the discussion that was already written by observing the differences in results across different prices.
+We also added a new subsection of discussion, where we analyze all the differences in one place.
+We also comment in limitations that it is true that some hotels priced similarly will offer different experiences (e.g.
+Western style resorts and Japanese style ryokan).
 
@@
 
-Comment #6 from Reviewer #5
-"Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
+>>>Comment #6 from Reviewer #5
+>>>"Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
 Can the authors explain further how this can be avoided in your data analysis?"
 ------------
+
+We completely agree, and improved the paper by adding more steps to the methodology.
+We used the Stanford CoreNLP pipeline to perform dependency parsing and part of speech tagging to the collected reviews.
+We used the dependency parsing to find which words are connected to each other and how, and we used the part of speech tagging to verify that the connections were of adjectives and nouns.
+Then we incorporated those pairs in the frequency analysis and considered which attributes of the hotel the customers were referring to, and in which context.
+This method is not perfect, and we can only follow one connection per word, but it gives us a deeper insight into the factors that customers consider.
 
@@
 
-Comment #7 from Reviewer #5
-"For the managerial and environmental keywords, what criteria were used for classifying these keywords? "
+>>>Comment #7 from Reviewer #5
+>>>"For the managerial and environmental keywords, what criteria were used for classifying these keywords? "
 ------------
+
+We agree with your comment and decided to reclassify them as hard and soft attributes. Before we explain the new definitions.
+
+Hard attributes are those that are impossible, or highly impractical for the hotel to change.
+For example, aside from an expensive relocation, it is impossible to influence if the transportation system is convenient nearby, or what stores are nearby, once the hotel is constructed.
+We also include the size of the room and the beds in this category, since usually bed size is constricted by the size of the room.
+
+Soft attributes are those that the hotel can feasibly change, with some investment, improvement in services, training of the staff or hiring new staff.
+Perhaps improving the cleanliness of the rooms, or improving language assistance for Chinese tourists.
+
+------------
+
+Thank you for your commentary, we hope this revised version is to your liking.

### 2020-09-28 3_review-responses/V2_review_responses/Reviewer #5 Response.txt
Added review responses until before corrections from reviewer 5

@@
 
-Reviewer #5:
+Thank you for your comments.
+I will enclose them in hyphens and respond below that section for each comment.
+I will also include quotes from the previous revision where necessary, using '>>>' before it.
+
+In summary, we added two more layers to our study. We divided the data in price ranges, and we added automatic adjective + noun pairing counts, by using dependency parsing and part of speech tagging.
 
@@
 
+We understand, and redesigned the study to be able to study those differences.
+And while in Japan the concept of omotenashi permeates into all levels of customer service, the study is all the more interesting when studying the different reactions to differently priced hotels.
+
+For this, we added an extra layer to our research by splitting the data into price ranges, although we admit that it's not fully encompassing the category or hotel type.
+To divide the data, first we observed the distribution of prices with a histogram, and adhered to a number of divisions that was appropriate for our data.
+
+To divide the data, we chose the highest price available in each hotel for a single room and a single night.
+This way, even if most customers aren't staying in that room, we can categorize the hotels by their quality.
+For example, there's probably no capsule hotels with suite rooms that would offer very different experiences.
+This way we think that we can clearly distinguish cheaper hotels and hostels, from business hotels, and from Japanese style ryokan or resorts.
+
+Then we performed the analysis and updated the discussion that was already written by observing the differences in results across different prices.
+We also added a new subsection of discussion, where we analyze all the differences in one place.
+We also comment in limitations that it is true that some hotels priced similarly will offer different experiences (e.g.
+Western style resorts and Japanese style ryokan).
+
+Some of our most interesting findings were added while analyzing price range differences, since we could observe the difference in behavior of Chinese and English-speaking tourists more clearly.
+For example, we found that Chinese people are more interested in shopping in Japan regardless of the level of luxury of the hotel they stay in, while Western tourists would enjoy shopping the most in only one of the categories (20,000 to 30,000 yen per night).
+
+In addition, when redesigning the study, and because Reviewer #1 also pointed out your previous comments as important to consider, we also added a few more improvements.
+
+------------
+>>>Comment #6 from your previous review
+>>>Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
+Can the authors explain further how this can be avoided in your data analysis?
+
+>>> 3. Comment #3 from Reviewer #1
+>>>"Among the four issues, it is the most critical one.
+Adjectives themselves cannot identify their associated attribute.
+I don't think "inspecting random samples" provides sufficient explanation.
+I recommend the authors run systematic analysis to examine the association between adjectives and nouns."
+------------
+
+We reconsidered this and completely agree.
+We decided to improve the paper by adding more steps to the methodology.
+We used the Stanford CoreNLP pipeline to perform dependency parsing and part of speech tagging to the collected reviews.
+We used the dependency parsing to find which words are connected to each other and how, and we used the part of speech tagging to verify that the connections were of adjectives and nouns.
+Then we incorporated those pairs in the frequency analysis and considered which attributes of the hotel the customers were referring to, and in which context.
+This method is not perfect, and we can only follow one connection per word, but it gives us a deeper insight into the factors that customers consider.
+
+------------
+>>>Comment #7 from your previous review
+>>>For the managerial and environmental keywords, what criteria were used for classifying these keywords?
+------------
+
+We received further commentary from Reviewer #1 on this and decided to reclassify these concepts. We define them now as hard and soft attributes.
+
+Hard attributes are those that are impossible, or highly impractical for the hotel to change.
+For example, aside from an expensive relocation, it is impossible to influence if the transportation system is convenient nearby, or what stores are nearby, once the hotel is constructed.
+We also include the size of the room and the beds in this category, since usually bed size is constricted by the size of the room.
+
+Soft attributes are those that the hotel can feasibly change, with some investment, improvement in services, training of the staff or hiring new staff.
+Perhaps improving the cleanliness of the rooms, or improving language assistance for Chinese tourists.
+
 ------------
@@
 
-We changed the spelling of lone numbers in the text. We also checked the in-text citations throughout the paper.
+We changed the spelling of lone numbers in the text. We also checked the in-text citations throughout the paper. Thank you for pointing out these mistakes.
+
+------------
+
+Thank you for your commentary, we hope this revised version is to your liking.

### 2020-09-29 3_review-responses/V2_review_responses/Reviewer #5 Response.txt
Finished reviewers comments and corrections, pre grammarly

@@
 
+We agree that it is a strong conclusion from the cited papers without context, so we have included more information from these papers, as well as a new citation on the origin of the term WEIRD (Western, educated, industrialized, rich, and democratic) populations.
+We expanded the description as follows:
+
+"However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world (Nielsen et al.
+2017).
+The term WEIRD was coined by Henrich et al.
+(2010), who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
+This bias, albeit without the acronym, was discussed earlier in the context of social psychology by Hogan and Emler (1978).
+Gunaratne (2009) pointed this bias out in discussions of globalization, while \cite{nielsen2017} sampled papers on developmental psychology and examined the bias in a statistical manner.
+This western bias is pervasive in social sciences of all kinds, and tourism science is not an exception.
+For example, studies are easily performed in the language of the scientist making surveys for the subjects.
+A great majority of tourist behavior in history analysis was performed with Western subjects, and was thought to be universal behavior until recent years."
+
 ------------
@@
 ------------
+
+We apologize for the ambiguity.
+The citation was not of the start of Chinese tourism studies, but instead it points to a review paper that analyzed this growth in studies by making a survey from 2001 to 2012 of such studies.
+In this paper Sun et al.
+(2020) find that a rapid growth has started since 2007 onwards, and that it's starkly different from the slow growth in previous years.
 
@@
 ------------
+
+We did not intend to generalize, it is a study between Asian and Western studies what we were referring to, so we reworded it in the document.
+While yes, cross-cultural studies in general aren't scarce, the specific case of Asian vs.
+Western, or even Chinese and non-Chinese, were very scarce, even consulting Google Scholar, which was the first place we consulted.
+We reworded the text so that this is more obvious.
 
@@
 ------------
+
+We apologize for the ambiguity, we updated the text to show the connection between the two ideas better:
+
+"The current Chinese economy boom is making an increase in the influx of tourists.
+The resulting increase in marketing and creation of guided tours for Chinese tourists could have created a difference in the perceptions and expectations of tourists.
+In turn, if we follow the definition of satisfaction by Hunt (1975), that change in expectations could have influenced their satisfaction factors when traveling."
 

### 2020-09-29 1_manuscript/itt-emotion.tex
moved sh files, improved sh, added previous review comments, indent party, updated .gitignore
Finished reviewers comments and corrections, pre grammarly

@@
 \documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
+% Fold 1
+  % Fold 2
+    % Fold 3
+      % Fold 4
         %\documentclass[twocolumn]{svjour3}          % twocolumn
@@
 
+% Fold 1
+  % Fold 2
+    % Fold 3
+      % Fold 4
         \titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}
@@
 
-  However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on populations that could be culturally biased for the western world \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-Those that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
+  However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world \cite[][]{nielsen2017}.
+The term WEIRD was coined by \cite{henrich2010weirdest}, who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
+This bias, albeit without the acronym, was discussed earlier in the context of social psychology by \cite{hogan1978biases}.
+\cite{guaratne2009} pointed this bias out in discussions of globalization, while \cite{nielsen2017} sampled papers on developmental psychology and examined the bias in a statistical manner.
+This western bias is pervasive in social sciences of all kinds, and tourism science is not an exception.
+For example, studies are easily performed in the language of the scientist making surveys for the subjects.
+A great majority of tourist behavior in history analysis has been performed with Western subjects, and was thought to be universal behavior until recent years.
+
+  Those studies that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
 The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations.
@@
     \end{rsq}
+
     \begin{rsq}
@@
     % Asians vs. Western behavior
-    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, jones2010WEIRD, guaratne2009, hogan1978biases}.
-
-    Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior \cite[][]{sun2017}.
+    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.
+
+    Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
+This increase was reviewed by \cite{sun2017}, who analyzed the number of studies related to Chinese tourists from 2001 to 2012, and found a steady increase until 2007, since when there is a rapid growth of studies on Chinese tourism.
 This increase resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, cross-cultural studies and analyses for Asian and Western tourists are scarce.
+To this day, studies and analyses specifically comparing Asian and Western tourists are scarce.
 One example is a study by \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money.
@@
 
-    One thing to note with the above cross-culture analyses is that they were performed before the year 2000.
+    One thing to note with the above Asian vs.
+Western analyses is that they were performed before the year 2000.
 The current Chinese economy boom is making an increase in the influx of tourists.
-However, that boom could have created a difference in the expectations of tourists.
-In turn, that boom could have influenced their satisfaction factors when traveling.
+The resulting increase in marketing and creation of guided tours for Chinese tourists could have created a difference in the perceptions and expectations of tourists.
+In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.

### 2020-09-29 1_manuscript/itt-emotion.tex
Grammarly check finished, waiting for Nonaka check

@@
 
-  The Japanese spirit of hospitality and service, \textit{Omotenashi}, is known worldwide for its excellence.
+  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence.
 Recent years show a steady increase in international tourists coming to Japan.
 Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought in a global perspective in recent years, most studies in tourist behavior were biased for the Western world.
+However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world.
 Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the environment of the high standard Japanese hospitality is fascinating.
+Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating.
 Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
@@
 We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality, in contrast with Western tourists, who were delighted by the staff behavior.
+We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists.
+The latter were delighted by the staff behavior.
 We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
@@
 From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and the whole of Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
+Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
 The effect of Chinese tourists on international economies is increasing.
@@
 The term WEIRD was coined by \cite{henrich2010weirdest}, who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
-This bias, albeit without the acronym, was discussed earlier in the context of social psychology by \cite{hogan1978biases}.
-\cite{guaratne2009} pointed this bias out in discussions of globalization, while \cite{nielsen2017} sampled papers on developmental psychology and examined the bias in a statistical manner.
-This western bias is pervasive in social sciences of all kinds, and tourism science is not an exception.
-For example, studies are easily performed in the language of the scientist making surveys for the subjects.
-A great majority of tourist behavior in history analysis has been performed with Western subjects, and was thought to be universal behavior until recent years.
-
-  Those studies that do include Asian populations in their analysis, most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
+This bias, albeit without the acronym, was discussed earlier about social psychology by \cite{hogan1978biases}.
+\cite{guaratne2009} pointed this bias out in discussions of globalization.
+At the same time, \cite{nielsen2017} sampled papers on developmental psychology and statistically examined this bias.
+This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception.
+For example, studies are easily performed in the language of the scientist doing surveys for the subjects.
+A great majority of tourist behavior in history analysis has been performed with Western subjects and was thought to be universal until recent years.
+
+  Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
 The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations.
@@
 In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study both Asian and Western tourist populations, their differences, and contrast the results with existing literature.
+Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.
 
@@
 Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands that are automatically analyzed by machines.
+The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands automatically analyzed by machines.
 This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
@@
   In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior, as well as perform an exploration of the data to discover factors that could have been overlooked in the past.
-In order to do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
+With this data, we can confirm existing theories about their differences in behavior and perform an exploration of the data to discover factors that could have been overlooked in the past.
+To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
 We then perform a statistical extraction of the topics that concerns the customers of each population the most.
@@
   This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast the satisfaction and dissatisfaction factors of both customer groups across several price ranges using machine learning to classify the sentiment of texts, and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence much satisfaction and dissatisfaction of both customer groups.
-We define hard attributes as those that are difficult to change by a hotel management without investing in infrastructure or real estate.
+We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges.
+We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings.
+More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
+We define hard attributes as difficult or impossible elements to change by hotel management without investing in infrastructure or real estate.
 In contrast, soft attributes are easily modifiable by improvements in management.
 
-  Our proposal includes the use of large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
+  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
 In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
@@
   Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for making improvements in the tourism and service industries and increase customer satisfaction.
+These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
 Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
@@
 Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
+However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
 Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training, and high standards are always followed as to not fall behind in the competition.
+Manners, service, and respect towards the customer are taught to workers in their training.
+High standards are always followed as to not fall behind in the competition.
 In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
 They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology as well.
+Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology.
 In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
@@
 A simple convenience shop around the corner could be more hospitable if hotel management falls behind.
-Businesses have to strive to be the most hospitable, and hotels are not allowed to lag in this competition.
-Because of this, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
+Businesses have to strive to be the most hospitable, as hotels cannot lag in this competition.
+Thus, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
 Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.
@@
 As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Western and Chinese customers can then have very different factors of satisfaction and dissatisfaction since they have different backgrounds and cultures.
+Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
 These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
 These expectations will be there from the moment that they choose the hotel throughout their stay.
-These different expectations, in turn, will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
+In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
 
@@
     Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, little focus is put on hard factors that are uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the surroundings of the hotel, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
+However, little focus is put on hard factors uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
+Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
 
@@
 
-    The resulting proportions of hard attributes to soft attributes for each population could serve as a measurement of how much the improvement of management in the hotel can increase future satisfaction in customers.
+    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
 
@@
     Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-This increase was reviewed by \cite{sun2017}, who analyzed the number of studies related to Chinese tourists from 2001 to 2012, and found a steady increase until 2007, since when there is a rapid growth of studies on Chinese tourism.
+\cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
 This increase resulted in several studies focusing on only the behavior of this subset of tourists.
 To this day, studies and analyses specifically comparing Asian and Western tourists are scarce.
-One example is a study by \cite{choi2000}, where it was found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with value for money.
+One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money.
 Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
-Another study, done by \cite{kim2000}, found that American tourists were found to be individualistic and motivated by novelty, while Japanese tourists were found to be collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
+Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
+In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
 
     One thing to note with the above Asian vs.
-Western analyses is that they were performed before the year 2000.
+Western analyses is that they were performed before 2000.
 The current Chinese economy boom is making an increase in the influx of tourists.
-The resulting increase in marketing and creation of guided tours for Chinese tourists could have created a difference in the perceptions and expectations of tourists.
+The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
 In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
@@
 A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, it appears that U.S.A.
-customers perceive cleanliness and quietness most positively and that Chinese customers perceive budget and restaurant above other attributes.
+citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
+According to their results, U.S.A.
+customers perceive cleanliness and quietness most positively.
+In contrast, Chinese customers perceive budget and restaurant above other attributes.
 Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
@@
 Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} has the context of tourists from three countries staying in hotels across the world, the second choosing restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe, and the third analyzing reviews of restaurants in Bejing.
-Our study, on the other hand, focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-The importance of Japan in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors are more important to the customers overall?
+The first study \cite[][]{FRANCESCO201924} was done with the context of tourists from three countries staying in hotels across the world.
+The second one chose restaurant reviews from the U.S.A.
+and Chinese tourists eating in three countries in Europe.
+The third is analyzing restaurants in Bejing.
+
+    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
+Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
+In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
 Our study measures this at a large scale across different hotels in Japan.
@@
     % Universal behavior
-    Other studies, perhaps recognizing that samples being comprised of people from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
+    Other studies, perhaps recognizing that samples from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
 \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
@@
 As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
+In another study \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
 The general satisfaction score was noticed to be different in those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors wasn't performed.
+However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
 As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
@@
     % Studies are not universal.
-    Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires, as well as the destinations; the results can vary greatly.
+    Although the studies focusing only on Chinese tourists or Western tourists have a narrow view, their theoretical contributions are valuable.
+We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
 Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, the definition of each factor is left for hotel customers to decide en masse via their reviews.
+Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
 This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
@@
 It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives an advantage to our study compared to others with smaller samples.
-Besides, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
+This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
+This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
 
@@
 These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it, as well as dissatisfaction, which is overlooked in most studies.
+However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
 Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
@@
 While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its leading rank in hospitality across all types of businesses.
+The focus on Japan is important because of its top rank in hospitality across all types of businesses.
 This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered as excellent.
+Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
 The number of samples in other text-mining studies is also smaller to ours in comparison.
@@
 Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist that can connect to the Internet.
+However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
 Such quantities of data are available to study now more than ever.
@@
 Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its conclusions on its own.
+In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its own conclusions.
 Our study calls for a supervised machine since text analysis can be intricate.
@@
     Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on the prediction of new data based on known properties and patterns of the given data.
+Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
 Data mining, on the other hand, is discovering new information and new properties of the data.
@@
 One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about where to find knowledge, and what kind of knowledge we can uncover.
+However, we can make predictions and estimates about where to find knowledge and what kind of knowledge we can uncover.
 The exploration of large opinion datasets with these methods is essential.
@@
 However, we are using a database of several orders of magnitude larger.
-We can also expect that, because of the lack of questionnaire design and users' freedom to record their pleasures and grievances, we may discover patterns that researchers previously hadn't noticed.
+We can also expect that we may discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
 
@@
   We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that would contribute the most to positive and negative opinions in a review.
+We then determined the most commonly used words that contribute to positive and negative opinions in a review.
 We did this using Shannon's entropy to extract keywords from their vocabulary.
@@
 We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews, as well as a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset in price ranges to observe the satisfaction factors and their differences between different lower class hotels and higher class hotels.
+We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
+We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
 We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review.
 We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel, meaning whether a hotel management can easily change those attributes, or if they are difficult to change without investing in infrastructure or real estate.
+Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
+Soft attributes are those that hotel management can easily change those attributes without investing in infrastructure or real estate.
+Hard attributes are impossible or impractical to change.
 
@@
 We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-In addition, we selected only the hotels that had a pricing information available.
+In addition, we selected only the hotels that had pricing information available.
 We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
 The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel.
-Regardless of the reason, the highest priced room can be an indicator of the class of hotel indirectly, which can give us an insight into the kind of service that is offered.
+Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, which can give us an insight into the kind of service that is offered.
 After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
@@
 Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
+After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
 
@@
 Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-We therefore made observations on the distribution of pricing in the hotels of our database and binned the data by price ranges, decided by consideration of objective of stay.
+Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
 We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}, which also includes the results of emotional classification after application of our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low class hotels or even hostels on the lower end, and cheap business hotels on the higher end.
-Further on there are business hotels in the next range (10,000 to 15,000 yen), and after that the stays could be at Japanese style \textit{ryokan} when traveling in groups, high class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
+The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
+This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
+The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end, and cheap business hotels on the higher end.
+Further on, there are business hotels in the next range (10,000 to 15,000 yen).
+After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
 Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
@@
     Chinese text, unlike English, does not have spaces between each word to separate them.
-In addition, we also needed to analyze the grammatical relationship between words, be it English or Chinese, in order to understand connections between adjectives and the noun they refer to.
-For all these processes we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
+Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
+For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
 In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
@@
 The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns the dictionary form of each word.
+Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
 For this purpose, we used the \textit{gensim} library with the English texts.
@@
 We show an example of these dependencies in Figure \ref{fig:depparse}.
-In this study we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
+In this study, we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
 A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
@@
 In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database, and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for adjectival modifier, where an adjective modifies a noun directly (e.g.
-A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, which is the syntactic subject of a class.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g.
-The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns, but it can also be connected with copular verbs, nouns, or other adjectives.
-For this reason we saw necessary to also perform a Part of Speech (POS) tagging of these clauses.
+We did that by parsing the entire database and extracting instances of a few determined dependency codes.
+One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
+This is used when an adjective modifies a noun directly (e.g., A big apple).
+The other dependency code we used was ``nsubj'', or nominal subject, which is the class's syntactic subject.
+We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
+This dependency does not necessarily only include a combination of adjectives and nouns.
+However, it can also be connected with copular verbs, nouns, or other adjectives.
+We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
 
@@
 An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes; for example, nouns, adjectives, verbs, conjunctions, and so on.
+A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
 In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
@@
 
-    In this study we were interested in identifying combinations of adjectives, some verbs and nouns.
+    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
 We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
@@
 We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter, which we selected heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.
+We also show a detailed description of the tags we needed to filter.
+We selected these tags heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.
 
@@
 
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers are referring to in their reviews, and with what frequency they use those pairings positively or negatively.
+    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
 
@@
 However, depending on the data, it can increase false negatives.
-Inversely, high values of C will likely result in minimal false negatives, but a possibility of false positives.
+Inversely, high C values will likely result in minimal false negatives, but a possibility of false positives.
 SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
@@
 
-    Shannon’s entropy can be used to observe the probability distribution of each word inside the corpus.
+    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
 A word that is included in many documents will have a high entropy value for that set of documents.
@@
 
-    An SVM is trained to classify data based on previously labeled data, generalizing features of the data by defining a separating (p-1)-dimensional hyperplane in a p-dimensional space in which each dimension is a feature of the data.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes the error of classification.
-
-    In our study, we used the linear kernel of the SVM classification process, defined by the formula (\ref{eq:svm1}) below.
+    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
+Each dimension is a feature of the data in this space.
+The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
+
+    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
 Each training sentence is a point of data, a row in the vector \(x\).
@@
 The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the angle of the hyperplane.
+The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
 The bias coefficient \(b\) determines its position.
 
-    During the SVM learning algorithm, each data point that is classified incorrectly causes a change in the weight vector to classify new data correctly.
+    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to classify new data correctly.
 These changes to the weight vector are greater for features close to the separating hyperplane.
 These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class in the classification process.
+Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
 Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
@@
 The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collected.
+We applied this SVC to classify the rest of our data collection.
 Subsequently, the positive and negative sentences counts shown in Table \ref{tab:exp_notes} are the result of applying our SVC for classification.
@@
 
-    To understand the satisfaction and dissatisfaction factors of Chinese tourists and English-speaking tourists when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed the frequencies of each entropy-based keyword in our complete data set and in each price range subsequently.
+    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
+Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
 The frequency of the keywords in the database shows the level of priority it has for customers.
 
-    We observed the top 10 words with the highest frequencies for keywords that were linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
+    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
 The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
@@
 
-    We can observe that the most used keywords for most price ranges in the same language are similar to each other, with a few changes in priority for the keywords involved.
+    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
 For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels, and it climbs in importance following the increase in price of the hotel.
+Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
+After this, it climbs in importance following the increase in the hotel's price.
 
@@
     Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-In order to understand those, we performed the dependency parsing and part of speech tagging explained in section \ref{textprocessing}.
+In order to understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
 While there were many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
@@
 
-  In order to further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define these by the feasibility with which a hotel management might make an improvement on this end to satisfy the customer further.
-We define hard attributes as matters that would be impossible for the hotel to change, such as the surroundings and location of the hotel, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk.
-Soft attributes, on the other hand, are attributes of the hotel which are easily changeable if small investments are made.
-For example, an improvement in the services of the hotel or the cleanliness of the rooms is a soft attribute.
-We can thus observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft attributes that the hotel management can easily change, or hard attributes that the hotel management cannot change without changing infrastructure or location.
-
-  We manually labeled the top keywords of each language into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing factors that are unchangeable by the staff or management, we consider them hard.
+    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
+We define these by the feasibility with which hotel management might improve to satisfy the customer further.
+We define hard attributes as matters that would be impossible for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk.
+On the other hand, soft attributes are attributes of the hotel that are easily changeable if small investments are made.
+For example, the hotel's services or the cleanliness of the rooms are soft attributes.
+Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
+
+    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
+If the word is describing unchangeable factors by the staff or management, we consider them hard.
 If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset, and counted the percentage of usage in each context.
+For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset.
+We counted the percentage of usage in each context.
 If it is not clear from the word or the pairing alone, we declare it undefined.
-Then, we added the counts of these words in each category, where a single word with no pairing is always 100\% in the category it corresponds to, and we add the partial percentages for each category when an adjective includes various contexts.
+Then, we added the counts of these words in each category.
+A single word with no pairing is always 100\% in the category it corresponds to.
+We add the partial percentages for each category when an adjective includes various contexts.
 The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
@@
     Our research questions were about two things.
-In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide as the objective of this study to determine how Chinese and Western tourists interact with the service and hospitality in Japan, \textit{omotenashi}, and how are they different in their perceptions in this matter.
-From the observation of the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}, that while service, cleanliness and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that across different price ranges, the list is more populated with hard attributes like location and transportation availability.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about lack of a Chinese friendly environment, although most complaints are also about hard attributes such as the age of the building and the distance from other convenient spots.
-The most complained about aspect, however, is the price of the hotel.
-It is surprising to note that all of the price ranges have this negative keyword at the top of the list, suggesting that it is a main concern to Chinese customers with different purposes of travel.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges, followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
+In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the service and \textit{omotenashi} hospitality in Japan, and how are they different in their perceptions in this matter.
+We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
+From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
+When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
+From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
+However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
+Nevertheless, the most complained about aspect is the price of the hotel.
+Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
+
+    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
+This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
 When we look at the adjectival pairing of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that mostly, they praise either the location, the service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service related concepts that the Western tourists are disappointed with when they react negatively.
+When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
 With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the location of the hotel and the availability of transport (subways and trains) nearby, as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness, as well as the service of breakfast.
+However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
+The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
+
     In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-It is surprising that the cigarette smell is an issue even in middle to high class hotels above 30,000 yen per night, although above 50,000 yen per night this problem seems to disappear from the list of top 10 concerns.
+Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
+However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
 Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction, while Chinese tourists consider location and transportation more often.
+On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
+In contrast, Chinese tourists consider location and transportation more often.
 
     We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews, while it wasn’t statistically identified as a problem at all for their Chinese counterparts.
+For example, English-speaking customers mentioned tobacco smell in many reviews, while it was not statistically identified as a problem for their Chinese counterparts.
 On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
@@
     In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions.
-Here we define hard attributes as those that are impossible or impractical to change for the hotel management, for example matters like the surroundings, view or location convenience.
-On the other hand, soft attributes are those that the hotel could easily and practically change without much limitations except for small financial investments, for example, improvement on the services of the hotel via training or hiring specialized staff.
-In our study, we find that that mostly Chinese tourists are positively reacting more to hard attributes of the hotel, and in negative sentences, there is a slightly hard leaning (53\%) concern with hard attributes, albeit it is more uniform in this instance.
-English-speaking tourists on the other hand, are both positively and negatively more responsive to soft attributes, and in the case of negative keywords, tourists are overwhelmingly more concerned with soft attributes of the hotel dissatisfying them somehow.
+Here we define hard attributes as impossible or impractical to change for the hotel management, such as the surroundings, view, or location convenience.
+On the other hand, soft attributes are those that the hotel could easily and practically change without many limitations, such as improving the hotel's services via training or hiring specialized staff.
+In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
+There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance.
+English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
+In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
 
@@
 From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby, or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price, but that still they react positively in a significant manner in cheaper hotels.
+Other mentions are also big markets nearby or a big bed.
+We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
+However, we can see that they still react positively in a significant manner in cheaper hotels.
 Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
@@
 
-    However, size of the room or the bed is a hard attribute, and without considering rebuilding the hotel, is quite difficult to improve on.
-Cleanliness, on the other hand, is mostly relating to soft attributes when we observe its adjectival pairings.
+    However, the size of the room or the bed is a hard attribute.
+Without considering rebuilding the hotel, it is not trivial to improve on.
+On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
 We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it’s an uncommon pair.
-We can therefore assert that cleanliness is an important soft attribute for Chinese customers, and that they are mostly pleased, with their expectations being met.
+In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
+Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
 
@@
 The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges that had reviews available as part of the top 4 pairings, and only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast as a strategy to increase good reviews.
+However, we assert that it is an important factor.
+Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
+It is only slightly lower on other categories, although it is not shown on the table.
+Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
 
@@
 
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'',``helpful'' and ``friendliness'' in the general database.
+    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
 The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
@@
 The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Similar to Chinese customers, Western customers also seem to be enjoying the included breakfasts when it comes to their satisfaction keyword pairings, although the word doesn’t appear directly in the top 10 list as in their Chinese counterparts.
+Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings.
+However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
 The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service related concepts that the Western tourists are disappointed with when they react negatively.
-The word ``great'', which is also high in most price ranges, and the top keyword in the highest priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together.
+When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
+The word ``great'', which is also high in most price ranges, and the top keyword in the highest-priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together.
 Japanese high standards in hospitality very likely influenced this result.
@@
 Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also just referring to the hotel in general.
-It seems as well that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
+Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
+It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
 Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
 
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the list of satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
+    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
 The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that in general, western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
+    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
 The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
 
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mention ``free'' as one of the top 10 positive keywords, which is paired mostly with ``wifi''.
-This price range is mostly for business hotels, which can be where users would be expecting this feature the most.ern tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
+    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
+This price range is mostly for business hotels where we infer users would be expecting this feature the most.
+Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
 
@@
 Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, which can lower the number of future customers.
+The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
 
@@
 We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before, taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan itself has a polarized view on smoking, and despite being one of the world’s largest tobacco markets, its use has been decreasing in recent years.
+Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
+This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
+
+    Japan has a polarized view on smoking, and despite being one of the world’s largest tobacco markets, its use has been decreasing in recent years.
 Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
 However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, there are many places where ``smoking rooms'' are available to keep the smoke to an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain kinds of customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
+However, many places have designated smoking rooms are available to keep the smoke to an enclosed area and avoid bothering others.
+Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
 If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would
-    make it an appropriate space for all kinds of customers.
+After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
 
@@
 
-    The location of the hotel, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
+    The hotel's location, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
 In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords, as well as their location in the priorities of each population across the price ranges, signal that while it was not the priority for either of them, the hotel’s location is a secondary but still important point in the hotel’s satisfaction.
-However, since this is a hard attribute, unchangeable to the management of the hotel, it is not often considered in the literature.
+All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
+However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
 Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
@@
 Taxis in Japan are a luxury compared to other countries.
-Where in less developed countries the taxi is the cheap method of transport of choice, in Japan, taxis are made to provide a high-quality experience, with a matching price.
-This means that for tourists, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity.
+In less developed countries, a taxi is the cheap method of transport of choice.
+In Japan, taxis are made to provide a high-quality experience, with a matching price.
+This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
 
@@
 Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, and so on.
+It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
 If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
@@
 
-  Below we explore the possible interactions with \textit{omotenashi}, what the differences between Chinese and Western tourists were, what is the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between hard and soft attributes of the hotel and how they contribute to the satisfaction of customers.
+  Below we explore the possible interactions with \textit{omotenashi}; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry.
+We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.
 
@@
     To this day, scholars continue to correct our historical bias towards the west.
-In this time, studies have determined that different cultural backgrounds lead to different expectations, which in turn influence the satisfaction of tourists.
+In this time, studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
 Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
 However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels, and is considered the highest standard across the world.
+The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
 Can such an environment affect different cultures equally?
@@
 
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
+    Our results indicate that out of the two; Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
 As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses and can even be found in convenience stores.
+Respectful language and bowing are not exclusive to high priced hotels or businesses.
+These can even be found in convenience stores.
 The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
@@
 This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench, and general dirtiness.
+The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
 \cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
@@
 
-    It could be that Chinese culture does not hold the expectation of high level service initially.
-That is, when an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
+    It could be that Chinese culture does not expect high-level service initially.
+When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
 On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
 It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly, while perhaps the hospitality grade in Japan is not fulfilling a high enough need for the Chinese population, resulting in less satisfaction.
+The ``nice surprise'' fulfills a need unexpectedly.
+Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
 For greater satisfaction, the existence of a need being met is necessary.
-However, since the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service, we cannot say that they aren’t satisfied in this matter, but rather that they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
+However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
+Thus, we cannot say that they are not satisfied in this matter, but rather that they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
 
     Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the treatment towards the Chinese visitors that are not being met, even in this high standard hospitality environment.
+Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
 Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
@@
 In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
+Expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
 On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
@@
 
-    As we stated in section 3.2, previous research is focused mostly on soft attributes of the hotel and their influence on customer satisfaction.
+    As we stated in section 3.2, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
 Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes, such as the location of the hotel relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see in their priorities the importance of those hard or soft attributes.
-
-    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general 68\% of the top 10 keywords are hard factors, while only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest priced hotels, where a 35\% of the keywords are undefined.
+However, hard attributes, such as the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
+Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
+
+    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
+In contrast, only 20\% are soft factors.
+The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
 However, the soft attributes are still similar at 18\%.
@@
 
-    In comparison, English speakers are mostly satisfied with soft attributes of the hotel, if we observe Figure \ref{fig:hard_soft_en}, where soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
+    In comparison, English speakers are mostly satisfied with the hotel's soft attributes, if we observe Figure \ref{fig:hard_soft_en}, where soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
 This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the very top of their list, except for the hard attribute that is the location of the hotel, which is consistently around the middle of the top 10 lists for all price ranges.
+English-speaking customers also have soft attributes at the top of their list, except for the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
 If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve in ways that will attract more customers in the future.
@@
 
-    For both customer groups, in general, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in the list in lower priced hotels, while the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}, but our results indicate that in the case of Japanese hotels, this is less of a cultural attribute, and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers, but the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, which could impact this placement in the ranking.
+    In general, for both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
+However, it is interesting to note that while English-speaking customers complain about price with a lower rank in the list in lower-priced hotels.
+In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
+A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
+However, our results indicate that this is less of a cultural attribute in the case of Japanese hotels and has more to do with the pricing of hotels overall.
+The tourists coming to Japan could be both experienced travelers or first-time travelers.
+However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
+In general, Japan is an expensive place to visit, impacting this placement in the ranking.
 Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
@@
 
-    For dissatisfaction, including all prices, both Chinese and Western customers have around half of the dissatisfaction being caused by issues that 1040 could be solved with improved management.
-Of course, this could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding, all of which can be costly.
-However, if hotels want to attract more customers, this paper provides a good guideline for which factors to consider first, and which ones will be best 1045 suited to which customer groups.
+    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
+This is true for all price ranges.
+Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding, all of which can be costly.
+However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
 Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, for Chinese customers, once the location and construction of the hotel are set, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with investment in staff and training.
-
-    Western tourists, on the other hand, are all around dissatisfied with mostly soft attributes, with a lowest of 35\% in the highest price range where undefined factors are the majority, and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts, and as such, present a bigger investment opportunity.
+However, once the location and construction of the hotel are set for Chinese customers, not much else can be done to satisfy them further.
+As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
+
+    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes, with a low of 35\% in the highest price range where undefined factors are the majority, and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
+The room for improvement for Western tourists is more extensive than their Chinese counterparts.
+As such, it presents a bigger investment opportunity.
 As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
@@
 
-    The opposite argument could also be made, however, that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
+    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
 Attracting a large number of Chinese customers can be a viable strategy for hotels.
@@
 Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism and Buddhism permeate the thought processes of Chinese populations.
+Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
 However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-Nevertheless, one could argue that there is a Chinese cultural attribute that emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
+
+    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
 According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
@@
 
-    In previous sections of this paper, we have mentioned the differences reflected in the results across hotel price ranges.
+    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
 Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction of the same topics.
-We can know this by observing the adjective + noun pairs, and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly priced hotels are ``wonderful'' and ``excellent''.
+The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction with the same topics.
+We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
+For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
+In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
 In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is higher, and that it influences the way that customers write their reviews.
+We can infer that the level of satisfaction is higher and that it influences how customers write their reviews.
 However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
@@
     In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where it is the meeting or exceeding of expectations that produces satisfaction.
-Therefore, the lack of meeting of expectations would cause dissatisfaction.
+Therefore, the lack of meeting expectations would cause dissatisfaction.
 In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
 This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarette, can lead to disappointment or outrage.
-However, we consistently see customers with high expectations for high class hotels react even more positively when satisfied.
+As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarettes can lead to disappointment or outrage.
+However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
 In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
 We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations, where customers set a standard in their mind that the service must not fall below or they will be disappointed.
-For example, a customer being disappointed with dirty rooms or cigarette smell.
-In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience, but they don't measure it against any sort of standards.
-For example, having a nice customer service experience, or being treated hospitably by the staff at a high class hotel.
+We can observe logical expectations.
+Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
+
+    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
+However, they do not measure it against any sort of standard.
+For example, having a nice customer service experience or being treated hospitably by the staff at a high-class hotel.
 Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction.
-This is where \textit{omotenashi} comes into play, and enhances the experience of the customers.
-
-    Now, there are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
+This is where \textit{omotenashi} comes into play and enhances the experience of the customers.
+
+    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
 For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
 In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-In fact, it is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
+It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
 \cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and citing \cite{japan2014consumption}, shows that common products besides food and drink are electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit.
-There is an understanding that the objective of shopping in Japan has more to do with the quality of the items rather than their relation to the touristic attractions.
-Our results suggest that Western tourists are engaging more in the touristic attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the price of the hotel only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
+There is an understanding that the fact that tourists choose to shop in Japan has more to do with the quality of the items rather than their relation to the touristic attractions.
+Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
+Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
 In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
@@
 
-    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for the customers of each culture.
+    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for each culture's customers.
 For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness for both cultures stays constantly part of the top 10 keywords, with the exception of the most expensive one, where other keywords take its place in the ranking, although it is still high on the list.
+Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take its place in the ranking.
+However, it is still high on the list.
 Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-Transport and location, as discussed in section \ref{disc:location}, is also important for hotels of all classes and prices.
+Transport and location, as discussed in section \ref{disc:location}, are also important for hotels of all classes and prices.
 While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
@@
     Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-Chinese tourists, as a whole, are not showing the most satisfaction towards \textit{omotenashi}, instead focusing on the hard attributes of a hotel.
+As a whole, Chinese tourists are not showing the most satisfaction towards \textit{omotenashi}.
+Instead, they focus on the hard attributes of a hotel.
 Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, excepting that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
+On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard-set ones.
+The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
 Japan is recently seeing an increase in Chinese students as well as Western students of universities.
@@
 It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high standards in comfort, which can be improved upon managerially for better reviews.
+Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
 Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
 However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types and that a low-cost investment could be to make the facilities tobacco-free.
+Our results suggest that satisfying cleanliness needs can satisfy both customer types.
+A low-cost investment could be to make the facilities tobacco-free.
 Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
 
-    Hard attributes, while not manageable after a hotel has finished its construction, are essential to consider for managers as well.
+    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers as well.
 As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
 Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after plans to make new subway lines are made.
+A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
 
@@
 Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more on cleanliness could improve on Western customers looking for high-quality lodging, even though the price per night would increase.
+For example, investing more on cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
 On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
@@
   This paper is not without its limitations.
-We analyzed keywords of satisfaction and dissatisfaction statistically based on whether they appeared on satisfied reviews or dissatisfied ones.
+We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
 Following that, we attempted to understand the context that these words were being used in by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword, and doesn’t follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  In this study, we analyzed the differences in customers expectations at different levels of \textit{omotenashi} by dividing our data into price ranges.
-However, in the same price range, say the high expenses ones, we can find both a western style five stars resort as well as a high end Japanese style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different in nature.
+However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
+This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
+For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
+
+  This study analyzed the differences in customers' expectations at different levels of \textit{omotenashi} by dividing our data into price ranges.
+However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
+Services offered in these hotels are very high quality, although very different.
 However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service, although still there is a divide between western and Japanese style hotels.
@@
 We could not analyze these populations because our team members do not know those languages.
-Aside from that, because of the nature of the data collected, further typology analysis could not be made (for example, Chinese men and women of different ages or their Westerner counterparts).
+Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
 
   In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels, as well as between customers traveling alone or in groups, for fun or work.
-Another point of interest in the future of this study is to use word clusters with similar meanings instead of single words.
+We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels and between customers traveling alone or in groups, for fun or work.
+Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
 
@@
 To answer our research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC, and then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and by hotel price range, considering the most expensive price for a room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness and other attributes relating to services and hospitality of the hotel.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location or the convenience of the hotel.
-We found that both cultures have a different reaction to this environment of hospitality, and both cultures have a different way of reacting to different prices.
+We used these keywords for sentiment classification via an SVC.
+We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
+We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
+
+  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
+However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
+We found that both cultures have a different reaction to this hospitality environment, and both cultures have a different way of reacting to different prices.
 From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and they react positively, the environment is not compatible with them because of language or culture barriers and it lessens their experience.
+One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
 The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
 We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, Western tourists, even when they hold high expectations in a highly priced hotel, show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
+On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
 We consider that Western tourists are more reactive to \textit{omotenashi} than their Chinese counterparts.
 
-  Lastly, we measured the amount of satisfaction and dissatisfaction factors that were referring to hard and soft attributes of a hotel.
-Soft attributes are those that can be changed via managerial decisions, improvement on services or small investments.
-On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes, while Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or the smell of cigarette in rooms.
+  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
+Soft attributes can be changed via managerial decisions by an improvement in services or small investments.
+On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
+We found that for satisfaction, Western tourists favor soft attributes.
+In contrast, Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges.
+For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
 In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
 
-  For hotel managers, one possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes, but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
+  One possible approach for hotel managers is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
+They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
 Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.
-With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels.
+We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
 While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
+This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
+This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
+We can observe their stark differences and shared attributes.
 
@@
 
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the interpretation of the data.
+  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
 We would like to show gratitude to Mr.

### 2020-09-29 3_review-responses/V2_review_responses/Reviewer #1 Response.txt
After Nonaka check, main manuscript, proceed to make 0_ files

@@
     *  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them. 
-
-    *  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist"
 ------------
@@
 After some thought, we do agree that the hypotheses are able to be removed without altering the objective of the paper at all.
-We changed them to "Research Questions" only with the purpose of referencing them throughout the main text, but they don't have to be proven or rejected anymore.
+However we still view value in using these questions as a statement of the paper's objective and to better structure and showcase our results.
+Because of this, we changed them to "Research Questions".
+Research questions 1a and 1b will relate to the how the customers reach to omotenashi and how they differentiate from each other, while research questions 2a and 2b will relate to hard and soft attributes and how the management decisions can impact future improvement in customer satisfaction.
 

### 2020-09-29 1_manuscript/cur_dir_my_latexdiff.sh
Making authorcontrib and titlepage, Add: sh to run latexdiff and latexcompile easier

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_V2-1.tex itt-emotion.tex --newversion="3" --compile --view --clean

### 2020-09-29 my_latexdiff.sh

@@ -1,0 +1,82 @@
+#!/bin/bash
+# This is my personalized latexdiff arguments to avoid having trouble every time
+# First install this file
+# https://github.com/nhoffman/argparse-bash
+source $(dirname $0)/argparse.bash || exit 1
+argparse "$@" <<EOF || exit 1
+parser.add_argument('oldfile')
+parser.add_argument('newfile')
+parser.add_argument('-n', '--newversion', default="2", type=str,
+                    help='Version number of the new file. [default %(default)s]')
+parser.add_argument('-o', '--oldversion', default="1", type=str,
+                    help='Version number of the new file. [default %(default)s]')
+parser.add_argument('-s', '--setdiffendname', action='store_true',
+                    default=False, help='Use provided --diffendname. [default %(default)s]')
+parser.add_argument('-d', '--diffendname', default="paper", type=str,
+                    help='Name of the project to append at end of the diff file. [default %(default)s]')
+parser.add_argument('-m', '--compile', action='store_true',
+                    default=True, help='Compile with latexcompile.sh [default %(default)s]')
+parser.add_argument('-v', '--view', action='store_true',
+                    default=True, help='Open the PDF at end of compile. [default %(default)s]')
+parser.add_argument('-c', '--clean', action='store_true',
+                    default=True, help='Clean latex secondary files [default %(default)s]')
+EOF
+
+NEWDOCNAME="${NEWFILE%.*}"
+OLDDOCNAME="${OLDFILE%.*}"
+
+if [[ $SETDIFFENDNAME ]]; then
+    echo "Using provided diffendname"
+else
+    DIFFENDNAME="${NEWDOCNAME%_V*}"
+    echo "using $DIFFENDNAME as diffendname, extracted from newdocname%_V*"
+fi
+
+OLD_VEND="${OLDDOCNAME#*_V*}"
+if [[ $OLD_VEND == $OLDDOCNAME ]]; then
+    OLDV=$OLDVERSION
+    echo "Using --oldversion flag instead of filename. Currently set to $OLDV"
+else
+    OLDV=$OLD_VEND
+    echo "Using old version number from filename. Currently set to $OLDV"
+fi
+
[…]

### 2020-09-29 0_coverletter/itt-emotion-coverletter.tex
Added new cover letter

\documentclass{letter}
\makeatletter
  \def\@texttop{}
\makeatother

\signature{Elisa Claire Alemán Carreón}
\address{
\textbf{Corresponding Author:}\\
Elisa Claire Alemán Carreón \\
Nagaoka University of Technology, Nagaoka, Japan \\
P.C. 940-2033, Ribbon Nagaoka B104, \\
1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
E-mail: elisa.claire.aleman.carreon@gmail.com
}

\addtolength{\headheight}{-11em}
\addtolength{\textheight}{10em}
\addtolength{\textwidth}{8em}
\addtolength{\oddsidemargin}{-6em}

\begin{document}

\begin{letter}{
Information Technology \& Tourism Editorial Board \\
Editor-in-Chief:  Zheng Xiang\\
Virginia Tech, USA}

\opening{Dear Zheng Xiang and ITT Editorial Board:}

We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the revised title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.

We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further. This revision required adding new experiments and methodology, namely the introduction of a dependency parser and a part of speech tagger to extract adjective+noun pairs, in order to understand what customers are praising or describing. Finally, thanks to our reviewers, our paper has now another layer of depth by analyzing differences in satisfaction factors across different price ranges for hotels. We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels. We discuss theories on the reason behind this in our revised paper. We also found that Chinese tourists in Japan are interested in shopping at all price ranges of hotels, while Western tourists are more inclined to shop when staying in middle to high-priced hotels.

We believe our new results and discussion are very interesting, and hope we continue to be in your consideration.

\closing{Sincerely,}

\end{letter}

\end{document}

### 2020-09-29 3_review-responses/V2_review_responses/Reviewer_Responses_all.txt
Just pasted all review responses into one txt

--- 2020-09-29 3_review-responses/V2_review_responses/Reviewer #5 Response.txt
@@
+Reviewer #1 Response
+
+Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment. I will also include quotes from Reviewer #5 where necessary, using '>>>' before it.
+
+In summary, we added two more layers to our study. We divided the data in price ranges, and we added automatic adjective + noun pairing counts, by using dependency parsing and part of speech tagging.
+
+------------
+1. Comment #3 from Reviewer #3
+It is not a deal breaker.
+However, I am with Reviewer #3 that the hypotheses of this study bring much value to the body of our knowledge.
+In the sense that this study took an exploratory approach (i.e., data mining), hypothesis testing may not be ideal to achieve the research goal.
+
+>>>Comment #3 from Reviewer #3
+>>>"#3 - Literature review
+    *  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them. 
+------------
+
+After some thought, we do agree that the hypotheses are able to be removed without altering the objective of the paper at all.
+However we still view value in using these questions as a statement of the paper's objective and to better structure and showcase our results.
+Because of this, we changed them to "Research Questions".
+Research questions 1a and 1b will relate to the how the customers reach to omotenashi and how they differentiate from each other, while research questions 2a and 2b will relate to hard and soft attributes and how the management decisions can impact future improvement in customer satisfaction.
+
+------------
+2. Comment #4 from Reviewer #3 & Comment #4 from Reviewer #5
+I don't think there is nothing that the authors can do about it. I recommend the authors acknowledge it as a study limitation.
+
+>>>Comment #4 from Reviewer #3
+>>>"#4 - Method
+    *  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period.
+The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts
+
+    *  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc"
+
+>>>Comment #4 from Reviewer #5
+>>>"In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted?
+Are the same hotels extracted from both Ctrip and Tripadvisor?
+How many hotels are there?
+I believe different types of hotels would have generated different satisfaction level and perspectives.
+Please provide more details about these hotels."
+------------
+
+We added an extra layer to our research to overcome this limitation, although we admit that it's not fully encompassing the category or hotel type.
+We divided our datasets into price ranges.
+We chose the highest price available in each hotel for a single room and a single night.
+This way, even if most customers aren't staying in that room, we can categorize the hotels by their quality.
+For example, there's probably no capsule hotels with suite rooms that would offer very different experiences.
+This way we think that we can clearly distinguish cheaper hotels and hostels, from business hotels, and from Japanese style ryokan or resorts.
+Then we performed the analysis and updated the discussion that was already written by observing the differences in results across different prices.
+We also added a new subsection of discussion, where we analyze all the differences in one place.
+We also comment in limitations that it is true that some hotels priced similarly will offer different experiences (e.g.
+Western style resorts and Japanese style ryokan).
+
+------------
+3. Comment #6 from Reviewer #5
+Among the four issues, it is the most critical one.
+Adjectives themselves cannot identify their associated attribute.
+I don't think "inspecting random samples" provides sufficient explanation.
+I recommend the authors run systematic analysis to examine the association between adjectives and nouns.
+
+>>>Comment #6 from Reviewer #5
+>>>"Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
+Can the authors explain further how this can be avoided in your data analysis?"
+------------
+
+We completely agree, and improved the paper by adding more steps to the methodology.
+We used the Stanford CoreNLP pipeline to perform dependency parsing and part of speech tagging to the collected reviews.
+We used the dependency parsing to find which words are connected to each other and how, and we used the part of speech tagging to verify that the connections were of adjectives and nouns.
+Then we incorporated those pairs in the frequency analysis and considered which attributes of the hotel the customers were referring to, and in which context.
+This method is not perfect, and we can only follow one connection per word, but it gives us a deeper insight into the factors that customers consider.
+
+------------
+4. Comment #7 from Reviewer #5
+I am still confused with internal and external attributes.
+While the "location" of the hotels is an external attribute, "big" rooms, bathtubs, and bath facilities are internal attributes.
+Both the location of the hotel and the size of rooms and facilities cannot be changed once the construction of the hotel is completed.
+The authors may want to recategorise/rename them (e.g., tangibles/intangibles; soft/hard).
+Look forward to it.
+
+>>>Comment #7 from Reviewer #5
+>>>"For the managerial and environmental keywords, what criteria were used for classifying these keywords? "
+------------
+
+We agree with your comment and decided to reclassify them as hard and soft attributes. Before we explain the new definitions.
+
+Hard attributes are those that are impossible, or highly impractical for the hotel to change.
+For example, aside from an expensive relocation, it is impossible to influence if the transportation system is convenient nearby, or what stores are nearby, once the hotel is constructed.
+We also include the size of the room and the beds in this category, since usually bed size is constricted by the size of the room.
+
+Soft attributes are those that the hotel can feasibly change, with some investment, improvement in services, training of the staff or hiring new staff.
+Perhaps improving the cleanliness of the rooms, or improving language assistance for Chinese tourists.
+
+------------
+
+Thank you for your commentary, we hope this revised version is to your liking.
+
+=====================================
+
 Reviewer #5 Response
@@
 
-"However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world (Nielsen et al.
+"However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industri- alized, rich, and democratic) populations that are culturally biased for the western world (Nielsen et al.
 2017).
@@
 (2010), who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
-This bias, albeit without the acronym, was discussed earlier in the context of social psychology by Hogan and Emler (1978).
-Gunaratne (2009) pointed this bias out in discussions of globalization, while \cite{nielsen2017} sampled papers on developmental psychology and examined the bias in a statistical manner.
-This western bias is pervasive in social sciences of all kinds, and tourism science is not an exception.
-For example, studies are easily performed in the language of the scientist making surveys for the subjects.
-A great majority of tourist behavior in history analysis was performed with Western subjects, and was thought to be universal behavior until recent years."
+This bias, albeit without the acronym, was discussed earlier about social psychol- ogy by Hogan and Emler (1978).
+Gunaratne (2009) pointed this bias out in discussions of globalization.
+At the same time, Nielsen et al.
+(2017) sampled papers on developmental psychology and statistically examined this bias.
+This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception.
+For example, studies are easily performed in the language of the scientist doing surveys for the subjects.
+A great majority of tourist be- havior in history analysis has been performed with Western subjects and was thought to be universal until recent years."
 
@@
 In this paper Sun et al.
-(2020) find that a rapid growth has started since 2007 onwards, and that it's starkly different from the slow growth in previous years.
+(2017) find that a rapid growth has started since 2007 onwards, and that it's starkly different from the slow growth in previous years.
+We changed it in the main document as follows:
+
+"Explaining this, Sun et al.
+(2017) analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism."
 
@@
 While yes, cross-cultural studies in general aren't scarce, the specific case of Asian vs.
-Western, or even Chinese and non-Chinese, were very scarce, even consulting Google Scholar, which was the first place we consulted.
+Western, or even Chinese and non-Chinese, were very scarce.
 We reworded the text so that this is more obvious.
+Now, the topic at hand is special, considering its focus in the specific Japanese hospitality environment, which is even more scarcely researched.
+The particular combination that this paper offers is not found in previous research either.
+
+We reworded as follows:
+
+"[...] To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists. [...]
+
+One thing to note with the above Asian vs.
+Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general.
+Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation.
+[...] However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies."
 

### 2020-09-29 2_revisions/V3_ITT_second revision/0_titlepage/itt-emotion-titlepage.tex
SUBMITTED!!!!!!

--- 2020-09-29 1_manuscript/itt-emotion.tex
@@
 
-\begin{abstract}
-
-  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence.
-Recent years show a steady increase in international tourists coming to Japan.
-Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world.
-Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes a hotel can change or be more concerned with hard attributes that hotel management cannot change?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists.
-The latter were delighted by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
-Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.
-
-  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-From that, the number of researchers interested in this phenomenon has been increasing as well.
-\cite[][]{sun2017}.
-With these and other multicultural tourist populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Hotel management, therefore, needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world \cite[][]{nielsen2017}.
-The term WEIRD was coined by \cite{henrich2010weirdest}, who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
-This bias, albeit without the acronym, was discussed earlier about social psychology by \cite{hogan1978biases}.
-\cite{guaratne2009} pointed this bias out in discussions of globalization.
-At the same time, \cite{nielsen2017} sampled papers on developmental psychology and statistically examined this bias.
-This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception.
-For example, studies are easily performed in the language of the scientist doing surveys for the subjects.
-A great majority of tourist behavior in history analysis has been performed with Western subjects and was thought to be universal until recent years.
-
-  Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.
-
-  With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands automatically analyzed by machines.
-This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior and perform an exploration of the data to discover factors that could have been overlooked in the past.
-To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
-We then perform a statistical extraction of the topics that concerns the customers of each population the most.
-
-\section{Research objective}\label{research_objective}
-
-  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as difficult or impossible elements to change by hotel management without investing in infrastructure or real estate.
-In contrast, soft attributes are easily modifiable by improvements in management.
-
-  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-The short scope of those studies means that cultural and language differences often cannot be observed in a single study.
-
-  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-  \subsection{Japanese hospitality: \textit{Omotenashi}}\label{theory_omotenashi}
-
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed as to not fall behind in the competition.
-In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-
-    It stands to reason that this high level of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in Japan, every business has this high level of hospitality, in differing levels of success.
-A simple convenience shop around the corner could be more hospitable if hotel management falls behind.
-Businesses have to strive to be the most hospitable, as hotels cannot lag in this competition.
-Thus, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
-Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.
-
-    Therefore we pose a research question for our study:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:omotenashi}
-    To what degree are Chinese and Western tourists satisfied with Japanese \textit{omotenashi} factors such as staff behavior or service?
-    \end{rsq}
-
-    However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different reaction.
-While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above research question:
-
-    \begin{rsq}
-    \label{rsq:omotenashi_both}
-    Do Western and Chinese tourists have a different reaction to Japanese \textit{omotenashi} factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-So we must measure their differences or similarities at their common ground as well.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The use of the Likert scale leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, little focus is put on hard factors uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel.
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.
-
-    Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-\cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
-This increase resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000.
-The current Chinese economy boom is making an increase in the influx of tourists.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three articles focus on U.S.A.
-culture, while our study focuses on Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done with the context of tourists from three countries staying in hotels across the world.
-The second one chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third is analyzing restaurants in Bejing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies, perhaps recognizing that samples from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese tourists or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller to ours in comparison.
-Apart from that, every study has a different text mining method.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[htp]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a Support Vector Machine.
-It is a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its own conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction, and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that because it has no intervention from the researchers in making questionnaires, it can have different results from anything that the researchers could expect.
-These qualities determine why, much like actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about where to find knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
-
-    In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect that we may discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
-\section{Methodology}\label{method}
-
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are those that hotel management can easily change those attributes without investing in infrastructure or real estate.
-Hard attributes are impossible or impractical to change.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, which can give us an insight into the kind of service that is offered.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end, and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-In this study, we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, which is the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
-Inversely, high C values will likely result in minimal false negatives, but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word that is included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a point of data, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to classify new data correctly.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentences counts shown in Table \ref{tab:exp_notes} are the result of applying our SVC for classification.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-In order to understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While there were many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define these by the feasibility with which hotel management might improve to satisfy the customer further.
-We define hard attributes as matters that would be impossible for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk.
-On the other hand, soft attributes are attributes of the hotel that are easily changeable if small investments are made.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing unchangeable factors by the staff or management, we consider them hard.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset.
-We counted the percentage of usage in each context.
-If it is not clear from the word or the pairing alone, we declare it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the service and \textit{omotenashi} hospitality in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the adjectival pairing of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that mostly, they praise either the location, the service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews, while it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions.
-Here we define hard attributes as impossible or impractical to change for the hotel management, such as the surroundings, view, or location convenience.
-On the other hand, soft attributes are those that the hotel could easily and practically change without many limitations, such as improving the hotel's services via training or hiring specialized staff.
-In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute, and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' and in a lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-The word ``great'', which is also high in most price ranges, and the top keyword in the highest-priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together.
-Japanese high standards in hospitality very likely influenced this result.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room.
-This can be considered a soft attribute.
-Not only as a standalone word of ``cigarette'', but also confirming with word pairs in Table \ref{tab:adj_en_neg}, we can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non- smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on smoking, and despite being one of the world’s largest tobacco markets, its use has been decreasing in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke to an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience, with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-  Below we explore the possible interactions with \textit{omotenashi}; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.
-
-  \subsection{Western and Chinese tourists in the \textit{omotenashi} environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
-In this time, studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two; Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service also go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in the satisfaction of Western tourists.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied in this matter, but rather that they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied, since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in \textit{omotenashi} does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As we stated in section 3.2, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes, such as the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions (Saulton et al.
-2017).
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery (Ryan and Mo 2001).
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well, which is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes, if we observe Figure \ref{fig:hard_soft_en}, where soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list, except for the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve in ways that will attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    In general, for both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in the list in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in the case of Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-This is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding, all of which can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the location and construction of the hotel are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes, with a low of 35\% in the highest price range where undefined factors are the majority, and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is higher and that it influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where it is the meeting or exceeding of expectations that produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarettes can lead to disappointment or outrage.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any sort of standard.
-For example, having a nice customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction.
-This is where \textit{omotenashi} comes into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and citing \cite{japan2014consumption}, shows that common products besides food and drink are electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit.
-There is an understanding that the fact that tourists choose to shop in Japan has more to do with the quality of the items rather than their relation to the touristic attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take its place in the ranking.
-However, it is still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-Transport and location, as discussed in section \ref{disc:location}, are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a certain bias to consider some attributes more than others.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards \textit{omotenashi}.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers as well.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more on cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context that these words were being used in by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of \textit{omotenashi} by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service, although still there is a divide between western and Japanese style hotels.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels and between customers traveling alone or in groups, for fun or work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment, and both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
-We consider that Western tourists are more reactive to \textit{omotenashi} than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via managerial decisions by an improvement in services or small investments.
-On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
-
 \begin{acknowledgements}
@@
 
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
 \end{document}

### 2020-09-29 2_revisions/V3_ITT_second revision/0_manuscript_blind/cur_dir_my_latexdiff.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_blind_V2-1.tex itt-emotion_blind.tex --newversion="3" --compile --view --clean

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #1 Response.txt
restore png to git from lfs, permissions

--- 2020-09-28 3_review-responses/V1_review_responses/Reviewer_1_response.tex
@@
-\documentclass{letter}
-
-% To insert commas into large numbers automatically
-\usepackage{siunitx}
-
-\begin{document}
-\pagenumbering{gobble}
-
-\textbf{Reviewer \#1 Response}
+Reviewer #1 Response
 
@@
 
-\begin{quotation}
+"""
 1. Machine learning
@@
 What do the authors want to achieve with machine learning?
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 Also, the manuscript can be improved by justifying and elaborating on the necessity of a large sample.
@@
 I recommend the authors to prepare a section dedicating to these questions.
-\end{quotation}
+"""
 
@@
 
-"Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
+> "Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
 We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly.
@@
 
-\begin{quotation}
+"""
 2. Theoretical discussion on culture
@@
 While this study did not measure "culture" per se, I believe the authors can find theoretical explanations.
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 3. Restructing
@@
 The current format is difficult to follow to see which attributes are similar or different between these two groups.
-\end{quotation}
+"""
 
@@
 We revised the tables in what previously was 6.1 to present them side to side for better following the differences in keyword ranking. They are now tables 5 and 6.
-
-\end{document}

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #3 Response.txt
restore png to git from lfs, permissions

--- 2020-09-28 3_review-responses/V1_review_responses/Reviewer_3_response.tex
@@
-\documentclass{letter}
-
-% To insert commas into large numbers automatically
-\usepackage{siunitx}
-
-\begin{document}
-\pagenumbering{gobble}
-
-\textbf{Reviewer \#3 Response}
+Reviewer #3 Response
 
@@
 
-\begin{quotation}
-\#1 - Research rationale
+"""
+#1 - Research rationale
 The authors mentioned "Up until recently, most studies in tourist behavior have been biased for the Western world".
@@
 I searched and found that several similar studies have already been published recently like:
-*  Francesco, G., \& Roberta, G. (2019). Cross-country analysis of perception and emphasis of hotel attributes. Tourism Management, 74, 24-42.
-*  Huang, J. (2017). The dining experience of Beijing Roast Duck: A comparative study of the Chinese and English online consumer reviews. International Journal of Hospitality Management, 66, 117-129.
-*  Jia, S. S. (2020). Motivation and satisfaction of Chinese and US tourists in restaurants: A cross-cultural text mining of online reviews. Tourism Management, 78, 104071.
+  Francesco, G., & Roberta, G. (2019). Cross-country analysis of perception and emphasis of hotel attributes. Tourism Management, 74, 24-42.
+  Huang, J. (2017). The dining experience of Beijing Roast Duck: A comparative study of the Chinese and English online consumer reviews. International Journal of Hospitality Management, 66, 117-129.
+  Jia, S. S. (2020). Motivation and satisfaction of Chinese and US tourists in restaurants: A cross-cultural text mining of online reviews. Tourism Management, 78, 104071.
 
@@
 To highlight the uniqueness of this work, the authors can highlight how the current study differs from other published works in terms of "research focus", "methodological approach", "study context" or/and "data size"
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
-\#2 - Research objectives
-*  Section 2 shows that the objective of this study is to determine the difference in preferences between Chinese- and English-speaking customers of Japanese hotels using text-mining techniques.
+"""
+#2 - Research objectives
+  Section 2 shows that the objective of this study is to determine the difference in preferences between Chinese- and English-speaking customers of Japanese hotels using text-mining techniques.
 Yet, according to my review, this study solely examines what English- and Chinese-speaking customers concern most when they evaluate Japanese hotels
 
-*  I can accept the assertion that the findings can reflect the differences in factors driving satisfaction and dissatisfaction between Chinese- and English-speaking customers.
+  I can accept the assertion that the findings can reflect the differences in factors driving satisfaction and dissatisfaction between Chinese- and English-speaking customers.
 But the findings cannot reflect their preferences
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
-\#3 - Literature review
-*  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.
+"""
+#3 - Literature review
+  Since H1, H2 and H3 has already been extensively tested in prior studies, I do not see the worthiness and necessity to re-examine them.
 
-*  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist
-\end{quotation}
+  For Section 3.2, the authors may consider reviewing more cross-country studies and presenting the findings in a tabular format (with the column showing study topic, industry, samples' nationality …) This comparison table shall be helpful for the authors to justify if the research gaps truly exist
+"""
 
@@
 
-\begin{quotation}
-\#4 - Method
-*  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period.
+"""
+#4 - Method
+  To provide a fair comparison, the two sets of texts should review the same hotels within a similar time period.
 The authors should provide this background information in order to demonstrate the fairness of comparing those two sets of texts
 
-*  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc
-\end{quotation}
+  Please report more information about the review samples, including time period, hotel and hotel attributes involved in this study and etc
+"""
 
@@
 
-\begin{quotation}
-\#5 - Discussions and Conclusions
-*  Regarding the discussion part, the authors discussed the differences (in sections 7.1 and 7.2) and the similarities (in section 7.3 and 7.4) of Western and Chinese consumers' satisfaction and dissatisfaction factors.
+"""
+#5 - Discussions and Conclusions
+  Regarding the discussion part, the authors discussed the differences (in sections 7.1 and 7.2) and the similarities (in section 7.3 and 7.4) of Western and Chinese consumers' satisfaction and dissatisfaction factors.
 However, the authors discussed the difference in section 7.5 again.
@@
 
-*  The manuscript does not include much discussions about its theoretical contributions. Again, how what new knowledge was brought by this study? Any contrasting findings were found?
-\end{quotation}
+  The manuscript does not include much discussions about its theoretical contributions. Again, how what new knowledge was brought by this study? Any contrasting findings were found?
+"""
 
@@
 
-\begin{quotation}
-\#6 - Minor
-*  The manuscript title should be revised.
+"""
+#6 - Minor
+  The manuscript title should be revised.
 The phrase "drivers of satisfaction and dissatisfaction" should be added.
@@
 
-\end{quotation}
+"""
 
@@
 This reflects both points in this comment and focuses on the change in research rationale, while also highlighting the method.
-
-\end{document}

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer #5 Response.txt
restore png to git from lfs, permissions

--- 2020-09-28 3_review-responses/V1_review_responses/Reviewer_5_response.tex
@@
-\documentclass{letter}
-
-% To insert commas into large numbers automatically
-\usepackage{siunitx}
-
-\begin{document}
-\pagenumbering{gobble}
-
-\textbf{Reviewer \#5 Response}
+Reviewer #5 Response
 
@@
 
-\begin{quotation}
+"""
 This study used Ctrip as the data base.
@@
 Therefore I suggest the authors change the term Chinese-speaking tourists to Mainland Chinese tourists.
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 In literature review, the authors listed three hypothesis relating to Chinese and English speaking tourists in 3.1 and then a separate section 3.2 to explain the difference between Chinese and Western tourists.
 I would suggest the authors combine these two sections so as to give a more comprehensive view on the setting of the three hypothesis.
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
-In formular (1), what are alpha, x and y?
-\end{quotation}
+"""In formular (1), what are alpha, x and y?"""
 
@@
 
-\begin{quotation}
+"""
 In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted?
@@
 Please provide more details about these hotels.
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 In Table 2, I am quite surprise to see that the last item "Chinese person" can be the top keywords with only 16 occurrences. Can the authors explain why there are so few negative Chinese keywords?
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
 Can the authors explain further how this can be avoided in your data analysis?
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 For the managerial and environmental keywords, what criteria were used for classifying these keywords? 
-\end{quotation}
+"""
 
@@
 
-\begin{quotation}
+"""
 Editorial issues
@@
 Besides, the numbering of the tables was not in sequence in the manuscript. Line 360, after Table 3 and 4, it suddenly jumps to Table 10.
-\end{quotation}
+"""
 
@@
 We also joined the tables with the top keyword results as per this and another reviewer's request.
-
-\end{document}

### 2020-10-07 3_review-responses/V1_review_responses/Reviewer_responses_all.tex
restore png to git from lfs, permissions

--- 2020-09-28 3_review-responses/V1_review_responses/Reviewer_3_response.tex
@@
 
+\textbf{Reviewer \#1 Response}
+
+Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
+Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections.
+Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values.
+However, our conclusions and hypothesis testing remained largely unchanged by this.
+We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript.
+The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi.
+In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?
+
+\begin{quotation}
+1. Machine learning
+
+While this manuscript contains machine learning in its title, there is no major discussion about it.
+What is machine learning?
+How do the authors define it?
+Is data mining part of machine learning?
+If so, how so?
+Why is important or useful to use machine learning particularly for this study?
+What do the authors want to achieve with machine learning?
+\end{quotation}
+
+Machine learning and data mining often overlap, which is why we had an oversight in defining both of them and explaining their differences.
+In a journal about Information Technology, we assumed it was general knowledge, but we added it for consistency and for a more widespread reader understanding.
+In the section previously titled 3.4 "Data mining, knowledge discovery and sentiment analysis", thus renamed 3.4 "Data mining, machine learning, knowledge discovery and sentiment analysis" we introduced two paragraphs defining machine learning, its importance of use for analyzing larger samples, and what we can achieve with it.
+However the manuscript title changed from another reviewers request.
+
+\begin{quotation}
+Also, the manuscript can be improved by justifying and elaborating on the necessity of a large sample.
+Why is it so important about analysing a large sample?
+What problem did a "small" sample used in existing literature cause?
+I recommend the authors to prepare a section dedicating to these questions.
+\end{quotation}
+
+In regards to the sample size, a paragraph in previously 3.2, now section 3.3 "Chinese and Western tourist behavior" already describes the importance of these bigger samples.
+We added a bit of text to expand on this importance.
+
+"Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable.
+We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly.
+Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
+However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire).
+This means that the factors will be selected through statistical methods alone.
+This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves.
+This large variety of opinions in a big sample, added to the automatic findings of statistical text analysis methods, is what gives an advantage to our study in comparison to others with smaller samples.
+In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature."
+
+\begin{quotation}
+2. Theoretical discussion on culture
+I also recommend the authors to develop the story on culture with theoretical perspectives.
+Why would Westerners show different preferences from Chinese?
+Why do Westerners value soft attributes (or managerial factors) like staff more while Chinese value hard attributes (or environmental factors) like size?
+Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)?
+While this study did not measure "culture" per se, I believe the authors can find theoretical explanations.
+\end{quotation}
+
+Another reviewer pointed out this, as well as suggesting a new research rationale.
+Because of it, we added new content to the introduction, changed the abstract and titles, as well as adding a new section in the discussion with theoretical perspectives on the context of Japanese hospitality.
+It is right that our study did not measure "culture", so we can't be sure of the explanations to certain aspects, although we do explain in the literature review that it has been previously studied how different backgrounds and cultures result in different expectations and as such, different satisfaction factors.
+
+In summary, our expanded discussion is about the differences between Chinese and Western tourists in the context of Japanese hospitality.
+Western tourists had hospitality and service related satisfaction keywords at the top of their priorities.
+However, Chinese tourists did not.
+We theorize this can be from two different causes.
+One theory is that the Chinese customers have different expectations based on their culture background, and that these expectations lead to different reactions.
+Specifically, not expecting something and then getting it could be less satisfying than getting an expectation met.
+Another theory is that despite being in the environment of Omotenashi, their language barriers are enough to disregard hospitality because of their unease or disappointment with the staff and communication availability.
+
+We also expanded on the discussion section by adding more to the previously 7.5, now section 7.2 Managerial vs.
+Environmental satisfaction, as well as add reasoning to each discussion section as well.
+In this section we added potential ramifications of the distribution of these factors.
+While Westerners can be satisfied even more by improving on managerial factors, a big portion of Chinese satisfaction comes from environmental factors.
+This means that it could be harder for managers to achieve an improvement in their satisfaction.
+However, we also claim that improving on cleanliness and making hotels tobacco-free could be a solution that benefits both populations.
+If this is done in addition to improving Chinese language services, both populations can be satisfied further.
+
+We added a section 7.3 Implications for hotel managers, where we discuss different strategies that managers could follow to improve on customer satisfaction for these populations.
+We propose two possible strategies, which are appropriate or not depending on a hotel business model.
+A hotel can aim to increase the numbers of Chinese customers by investing on Chinese language services, which are a larger population but spend less percentage of their budget on hotels.
+On the other hand, a hotel can aim to increase cleanliness and comfort, which are bigger investments, but would satisfy Western customers, who spend almost half their budget on hotels.
+
+As for the comment "Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)?": They are both different.
+RBO results and our hypothesis testing showed that both satisfactory and dissatisfactory attributes are different for both cultures.
+Still, I understand that explaining the reasoning behind these results could improve the discussion.
+
+\begin{quotation}
+3. Restructing
+I found the discussion section (7.
+Discussion) misrepresents.
+The section is mainly reporting the findings without in-depth discussion (e.g., discussion on the reason behind such findings).
+I recommend combining Sections 5 and 6 into one section as an analysis section; and rename 7 Discussion as 6 Results.
+As suggested in the earlier section, the authors can add a new discussion section with a theoretical discussion.
+The current 6.1 section can be revised by presenting one-to-one or item-by-item comparison between Chinese and English-speaking customers.
+The current format is difficult to follow to see which attributes are similar or different between these two groups.
+\end{quotation}
+
+We added most of what was once in the discussion section to the results section, and added more in-depth discussion in section 7 as explained above.
+The subsections that moved up to the Results section were 6.2 Chinese tourists - A big and clean space, 6.3 Western tourists - A friendly face, and absolutely clean, 6.4 Tobacco, what’s that smell?, and 6.5 Location, location, location.
+The price section was deleted since it was short enough to be discussed elsewhere.
+
+We revised the tables in what previously was 6.1 to present them side to side for better following the differences in keyword ranking. They are now tables 5 and 6.
+
+\clearpage
 \textbf{Reviewer \#3 Response}
@@
 
+\clearpage
+\textbf{Reviewer \#5 Response}
+
+Thank you for your review observations. I will quote each observation and respond to it while indicating my corrections in the text.
+Aside from these corrections, we also performed a general grammar check and proofread to the new manuscript, including unchanged sections.
+Because of comments by reviewers, we redid the experiment with more balanced data, so the results shown are different in their quantitative values.
+However, our conclusions and hypothesis testing remained largely unchanged by this.
+We also added a new research rationale and focus, which meant new hypotheses were added to the manuscript.
+The new manuscript focuses on how these populations interact with the high-standard spirit of Japanese hospitality and service called Omotenashi.
+In this environment, will the cultural differences be strong enough that their satisfaction stems from different factors?, or will both populations be largely satisfied by service and staff related terms?
+
+\begin{quotation}
+This study used Ctrip as the data base.
+However, majority users of Ctrip is Mainland Chinese, but Chinese-speaking tourists can also be Taiwanese, Malaysian Chinese, Singaporean Chinese and Hong Konger too.
+Therefore I suggest the authors change the term Chinese-speaking tourists to Mainland Chinese tourists.
+\end{quotation}
+
+Thanks for pointing this information out. We pointed this out in the text.
+
+\begin{quotation}
+In literature review, the authors listed three hypothesis relating to Chinese and English speaking tourists in 3.1 and then a separate section 3.2 to explain the difference between Chinese and Western tourists.
+I would suggest the authors combine these two sections so as to give a more comprehensive view on the setting of the three hypothesis.
+\end{quotation}
+
+We respectfully disagree with this suggestion since the content of section 3.1 and 3.2 are very different.
+While 3.1 sets the premise of differences in customer satisfaction and the reasoning behind them existing, 3.2 discusses previous literature on specific behaviors and cultures of each kind of tourist.
+Since we added a new section 3.1, these two sections are now 3.2 and 3.3 respectively.
+
+\begin{quotation}
+In formular (1), what are alpha, x and y?
+\end{quotation}
+
+We added a description of the formula to the manuscript, as well as a short description of the SVM algorithm to make it more understandable.
+
+\begin{quotation}
+In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted?
+Are the same hotels extracted from both Ctrip and Tripadvisor?
+How many hotels are there?
+I believe different types of hotels would have generated different satisfaction level and perspectives.
+Please provide more details about these hotels.
+\end{quotation}
+
+In regards to this point, we apologize and would like to explain.
+In the original manuscript, the experiments were done while the data was still being collected further.
+After finishing the manuscript, the original data had changed.
+Not only this, but we realized our mistake from this and another comment from a different reviewer.
+Indeed the data should reflect the same kinds of hotels, the same kinds of categories.
+Since we did not have these data, we decided to match both English and Chinese comments to come from exactly the same hotels, matching by name.
+This reduced the number of comments on each language, but it made the data fairer.
+We don't have data on what type of hotel or star rating they had since this data wasn't available to us, but we can be sure they are the same 580 hotels for both kinds of reviews.
+
+Because of this change in datasets, we also redid the entire experiment, calculating the frequencies and RBO again accordingly.
+
+The time period resulted to be from July 2014 to July 2017. The price range was from 2000 yen per night, to 188,000 yen a night.
+
+We added this paragraph to the Data collection section:
+
+"However, in order to make the data and comparisons we draw from each of these datasets fair, we filtered both databases to only contain reviews from hotels that were in both datasets, using their English names to do a search match.
+We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
+After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{580}, and that the common date range for reviews was from July 2014 to July 2017.
+We also found that the price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
+Within this range, from \textit{Ctrip} there was \num[group-separator={,}]{49561} reviews comprised of \num[group-separator={,}]{105076} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41611} reviews comprised of \num[group-separator={,}]{352022} sentences.
+
+We found that after filtering the data, the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general."
+
+\begin{quotation}
+In Table 2, I am quite surprise to see that the last item "Chinese person" can be the top keywords with only 16 occurrences. Can the authors explain why there are so few negative Chinese keywords?
+\end{quotation}
+
+Since we repeated the experiment, the frequencies have changed, however this keyword still only has 16 occurrences.
+The lack of negative keywords comes from a peculiarity of the Chinese reviews from Ctrip.
+Most of the reviews point out the positive extensively, while only a few sentences are negative.
+It's a limitation of our paper that the negative keywords depend on the sample taken at the beginning, since we could not label more manually at the time.
+
+\begin{quotation}
+Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment".
+Can the authors explain further how this can be avoided in your data analysis?
+\end{quotation}
+
+One thing to note is that using SVM, we labeled sentences as positive or negative, so negative usage of the word when counting the frequencies is negligible.
+In addition to this, we also had the same question when we saw our results the first time, and took a small sample to observe the usage of the word.
+However we didn't deem it appropriate in the text at first, but with this comment and thinking it over once again, we have added the next paragraph to the manuscript:
+
+>"From these two first ranking keywords (“big” and “clean”), we can assert
+that room quality is the most critical satisfaction factor for Chinese customers.
+However, the word “big” is widespread in the language and could be used in different contexts to point out positive and negative aspects.
+Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word “big” in Chinese.
+A team of Chinese speaking lab members then pointed out the usage of the word.
+Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities."
+
+\begin{quotation}
+For the managerial and environmental keywords, what criteria were used for classifying these keywords? 
+\end{quotation}
+
+We explain the difference between managerial and environmental factors in different sections of the manuscript.
+However, since it might still be unclear, we specified the method for classifying the keywords in the Results section, adding the following text:
+
+> "We manually labeled the top
+625 keywords of each language into either managerial or environmental by considering how the word would be used when writing a review.
+If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial.
+If the word is describing factors that are unchangeable by the staff or management, we consider them environmental.
+The interpretation of these keywords is shown in the Tables 8 and 9."
+
+We also added the tables that were previously in the appendix clearing this issue into the main text for readability.
+
+\begin{quotation}
+Editorial issues
+The Appendix is actually part of the manuscript.
+This manuscript contains too many Tables.
+First some was mentioned in the manuscript but appeared in Appendix.
+For example line 306, Table 7 and Section B was mentioned.
+What is Section B?
+Please move all relevant tables to the manuscript but not in Appendix.
+I would suggest the authors to consider to either combine some of them or not to mention them in the manuscript.
+Besides, the numbering of the tables was not in sequence in the manuscript. Line 360, after Table 3 and 4, it suddenly jumps to Table 10.
+\end{quotation}
+
+We moved some tables that we deemed important out of the appendix, but other tables got removed as per this request.
+We also joined the tables with the top keyword results as per this and another reviewer's request.
+
 \end{document}

### 2020-10-07 3_review-responses/V1_review_responses/olas_review_response.txt
restore png to git from lfs, permissions

From these two rst ranking keywords (\big" and \clean"), we can assert
that room quality is the most important satisfaction factor for Chinese customers.
This means that Chinese tourists have an expectation of spaciousness
18 E. Aleman Carreon et al.
and cleanliness when coming to Japan, be it by reputation, previous experiences,
or cultural backgrounds.
Ola Jajus

so you went and abandoned the search for discussing it further

kinda like ok so this is happening and the reason is whatever now lets move on
Eli ❤

Oh

Ok I still don’t get where

But you have the same impression then
Ola Jajus
My furry fox girlfriend ❤

had a team of Chinese speaking lab-mates point out the
usage of the word

lab members more professional
Eli ❤

Right
Ola Jajus
My furry fox girlfriend ❤

One key component we found in Chinese customer satisfaction factors is
the inclusion of breakfast within the hotel. This can be inferred from the high
555 frequency with which this keyword was included in the sentences emotionally
classied as positive. While other food-related words were extracted, most of
them were general in nature, like \food" or \eating", and in a lower ranking.
In contrast, the word \breakfast", which is referring to a specic time and
very possibly its inclusion in the hotel commodities, was very frequently used
560 in positive texts compared to other food-related words.
Ola Jajus
My furry fox girlfriend ❤

ok so you explained it all nicely

but you just stopped there without giving further tips to the hotel

i mean ofc the tip is provide free breakfast

but maybe refer to idk some hotel strategy?

if u dont know hotel stuff its hard ik
Eli ❤

Hmmm ok i guess it does come across as withholding information even tho I thought it was obvious
Ola Jajus
My furry fox girlfriend ❤

it is
Eli ❤

Hmm well thanks honey
Ola Jajus
My furry fox girlfriend ❤

ik u probably sum it up later on
Eli ❤

I guess you opened my eyes to why they said that
Ola Jajus
My furry fox girlfriend ❤

yeah maybe u have to translate the results to clear strategies

or end every section of discussion with "Strategies to be implemented: ... include breakfast... ...blah...."
Ola Jajus
My furry fox girlfriend ❤

Moreover, mainland Chinese tourists have expectations about the treatment
towards the Chinese visitors that aren't being met. Be it Chinese language
pamphlets, Chinese texts on instructions for the hotel room and it's
appliances and features (T.V. channels, Wi-Fi setup, etc), or just the treat565
ment towards Chinese people, it seems that their expectations are not being
met. This is natural, since traveling in a strange land without knowledge of
the language can be a daunting experience. Ryan and Mo (2001) also found
that communication diculties was one of the main reasons Chinese customers
would give for not visiting again.
Ola Jajus
My furry fox girlfriend ❤

AGAIN

you got so much to elaborate upon here

even from our experience

ok so they got language bareeer problems SO hotels have to make sure they need to provide a more welcoming environment, hire chinese speaking staff, maybe provide chinese news channels on tv

you could touch on the large no of chinese ryugakusei everywhere in japan and how they could be employed in hotels to increase satisfaction lvls

ik its obvious cuz we both in japan and ryugakusei but even for japanese hotel industry its not crystal clear, and for US ppl its not clear at all

This is all very
Analyzing dierences in satisfaction and dissatisfaction between Chinese and ... 19
dierent from Westerner experiences and while it could be a culture shock to
some, it is mostly seen positively.

this one sounds not professional

"This is all very different" part change to sth like "This lies in striking contrast to" or "This significantly differs with", "This is usually outside the scope of"

also i know you know all this stuff from ur experience but you are not referencing this cultural stuff like sento and bowing and idk is that ok for sure?

"After all, Japanese sta treats all customers
in this respectful manner, but for some customers, this could very well be the
best they have been treated until that moment." this sentence is awkward and too informal

"We can also see that Kozak
585 (2002) and Shanka and Taylor (2004) have also found" also also

you overuse "we can see", change it to sth like "the experimental data suggests", "it can be inferred"

"We can also see that Kozak
585 (2002) and Shanka and Taylor (2004) have also found that hospitality and
sta friendliness is an important determinant in the satisfaction of Western
tourists.
However, we can see"
Eli ❤

ok but the english i told you you can miss because im gonna redo the grammar check
Ola Jajus
My furry fox girlfriend ❤

"we can see from the rest of the keywords" looking at the remaining keywords, we can infer

is gramarly gonna fix informal language or very vague repetitions?

your language is just normal in some places and formal in some; is it gonna detect the discrepancy?

"have found many places unacceptable to their standards" is that an expression for sure? maybe just unacceptable
Ola Jajus
My furry fox girlfriend ❤

"In comparison, our research uncovered that it is mostly linked
to dissatisfaction and that westerners could be said to have high standards of
hygiene when compared to their Chinese counterparts" careful here someone might get offended. maybe use higher standards of room cleanliness; specify its ROOM
Ola Jajus
My furry fox girlfriend ❤

"Some cities in Japan (e.g.
605 Osaka) are currently going under a large number of renovations" ahahah experience
😆
1

"Customers staying in places in renovation
or near a construction" add site

oh man so much english mud

you better fix it all

"Another keyword there is \slow", which upon inspection of example reviews,
610 we concluded that it re
ects the speed of the Internet connection in the hotel
rooms." ORDER screwed up
Eli ❤

order?
Ola Jajus
My furry fox girlfriend ❤

"An interesting detail of the keywords of satisfaction and dissatisfaction,
is that the word \comfortable" is high on the list of satisfaction factors and
\uncomfortable" high on the dissatisfaction factors. It seems that in general,
615 western tourists are highly sensitive to comfort levels in the hotels, and whether
it reaches their expectations." ok so for example what
Eli ❤

ah must be from the new experiment
Ola Jajus
My furry fox girlfriend ❤

thats so curt

it sucks

like comfort of what??? should the hotels invest in beds? balcony sets? big baths?

translate your research to applications
Ola Jajus
My furry fox girlfriend <3 replied to you

order?
no sentence order is shit
Eli ❤

YEAH OK

i told you to leave the english alone jeez

i know it sucks

I'm gonna fix it afterwards
Ola Jajus
My furry fox girlfriend ❤

why didnt you fix it before submitting manuscript?
Eli ❤

because.... that was before i bought grammarly and well apparently it helps a lot

beause apparently my english sucks

now i have it and i plan to use it
👍
1
Ola Jajus
My furry fox girlfriend ❤

"In general, Japan is an expensive place
to visit, which could have an impact in this placement in the ranking." maybe give a frame? like compare a price of room in china and japan in usd?
👍
1

"7.4 Location, location, location" are you sure abt this header?
Eli ❤

well... actually no reviewers complained and it's apparently a phrase used a lot in real estate
👍
1

so its not like... out of nowhere
Ola Jajus
My furry fox girlfriend ❤

"availability of nearby shops" maybe change to proximite to shops

"Upon inspection of examples from the data, we found that most customers
635 were satised if the hotel was nearby to at least two other subjects: subway
or train, and convenience stores." what do you mean by other subjects?

like why other
Eli ❤

oh hmmm... idk really, it can go
Ola Jajus
My furry fox girlfriend ❤

"Japan is a country with a particular public transport system. The rush
hour makes for a subway lled to the brim with people in suits making their
commute, and trains and subway stations in Tokyo create a confusing public
640 transport map for an outside observer. Buses are also available, although less
used than the rail systems in the big cities." particular to peculiar, outside observer to visitor
Ola Jajus
My furry fox girlfriend ❤

"Taxis in Japan
are a luxury compared to other countries. Where in less developed countries
645 the taxi is the cheap method of transport of choice, in Japan, taxis are made
to provide a high-quality experience, with a matching price." ok maybe give a price in usd of train from ueno to tokyo station and taxi so that they get an idea? also if u compare taxi price to usa its comparable so maybe you should add that japanese taxis are expensive compared to other southeast asia countries?
Ola Jajus
My furry fox girlfriend ❤

"This means that
for tourists, subway availability and a good map or plan to travel the city are
of utmost necessity" yo come on dont be out of this century, mention travel apps or google maps or sth

"Japanese convenience stores, on the other hand, are also famous worldwide
650 for their convenience" xDDDDDDD

you dont say

can you rephrase it
Eli ❤

i mean

but they are
😆
1

but yeah sure
Ola Jajus
My furry fox girlfriend ❤

"If some trouble occurred, or a traveler forgot to pack
a certain item, it is almost sure that they can nd it here." hmm i think not,
Ola Jajus
My furry fox girlfriend ❤

"Therefore, considering both transport systems and nearby shops are points
of interest for Chinese and Western tourists, Japanese hotels have to choose
carefully their location from the moment that they are constructed. While not
a top priority, this is a universal factor for both customer groups and it can
be an instant way to generate positive reviews." YES thank you this is what we all wanted
Ola Jajus
My furry fox girlfriend ❤

also more like from the moment they purchase/lease land
👍
1

you could also mention they could purchase land and start buuding after the plans to make new metro line/connection hub are made

like to elaborate a lil on the strategies to take

"After all, even if it doesn't bother some customers, the lack of smell would not
bother any existing customers." i know what ur saying but make it clearer
👍
1

hey im not sure if its a problem but u got "undened 30%" maybe you should comment what that could be and how u could analyze it in future work?
Eli ❤

hmm, well for now it wasnt a problem and i dont wanna angry the reviewer
👍
1
Ola Jajus
My furry fox girlfriend ❤

"However, if hotels want
to attract more and more customers" informal

yeah so u only start to touch on applications a tiny bit in the last part of 7 discussion

basically u need more i think

"Another limitation is that a
big portion of the Asian tourists coming to Japan are Taiwanese and Korean," but istnt chinese veeeery similar to taiwanese

"This
means our hypothesis 2 is rejected (RBOEXT > 0:5), and that the common
ground within both customer groups is also similar in ranking." maybe mention again which one it is

its not like ppl reading the paper gonna remember all ur hypothesis and im always annoyed when i gotta look back
Ola Jajus
My furry fox girlfriend ❤

"Our results and discussion can be utilized as a guideline for managerial
770 decisions when considering Chinese and Western tourists, and we can observe
their stark dierences, as well as their common attributes. In future work...." ok but specify the useful managerial decisions thats like the very worth of this paper
Ola Jajus
My furry fox girlfriend ❤

you worte the paper abt the topic you dont care about

but make it useful for someone who does
Eli ❤

thanks honey
Ola Jajus
My furry fox girlfriend ❤

ok done nice work on future work

ima make dinner im so hungry
❤
1
You replied to My furry fox girlfriend <3

"This
means our hypothesis 2 is rejected (RBOEXT > 0:5), and that the common
ground within both customer groups is also similar in ranking." maybe mention again which one it is
i mean it does say a bit in there but i guess i can add more
Ola Jajus
My furry fox girlfriend ❤

i know, they should remember it after reading the paper but still

for ppl who skim to conclusions...
Eli ❤

### 2020-10-07 0_vitae/itt-emotion-vitae.tex
restore png to git from lfs, permissions

\documentclass{letter}
\begin{document}
\thispagestyle{empty}

\textbf{Vitae}

Elisa Claire Alem\'an Carre\'on received the B.S. and M.S. degree and is currently pursuing a Ph.D in Information Science and Control Engineering in the Nagaoka University of Technology, Nagaoka, Japan under the instruction of Hirofumi Nonaka. Her research interests are Text/Data mining for management data and multilingual endeavors.

Hugo Alberto Mendoza Espa\~na received the B.S. and is currently pursuing a M.S. degree in Information and Management Systems Engineering in the Nagaoka University  of Technology, Nagaoka, Japan under the instruction of Hirofumi Nonaka. His research interests are machine learning for data analysis and computer vision.

Hirofumi Nonaka received the B.S., M.S. and Ph.D. degrees in Engineering from Toyohashi University of Technology, Aichi, in 2003, 2005 and 2011, respectively. He was a research fellow at Nagoya University in 2011. He joined the Department of Information Engineering, Oita National College of Technology, Oita, Japan from 2012 to 2015 and was an Associate Professor. He has been an Associate Professor at the Department of Information Management System Engineering, Nagaoka University of Technology since 2015. His recent research interests are Text/Data mining for management data and application of spatial statics.

Toru Hiraoka received B.S. and M.S. degrees in design (1995 and 1997), and a Ph.D. degree in engineering (2005) from Kyushu Institute of Design, Fukuoka, Japan. In 1997 he joined TOA Construction Engineering Co. for research on digital photogrammetry and geographic information systems. In 2009 he conducted research on flood discharge. In 2011 he was an associate professor at the Department of Information Engineering, Oita National College of Technology. Since 2016 he has been a professor at the Department of Information Systems, Faculty of Information Systems, University of Nagasaki. His current research interests are non-photorealistic rendering and disaster prevention.

\end{document}

### 2020-10-07 2_revisions/V2_ITT_first revision/itt-emotion_V2 (1).tex
restore png to git from lfs, permissions

--- 2020-09-27 2_revisions/V3_ITT_second revision/itt-emotion_V2-1.tex
@@
 \includegraphics[width=\textwidth]{emotion-method-overview_V2.png}
-\caption{Overview of the methodology to quantitatively rank satisfaction factors.}
+\caption{Overview of the methodology.}
 \label{fig:method-overview}
@@
 Since both cultures have a different reaction to this environment of hospitality, our hypothesis \ref{hyp:omotenashi_both} is confirmed.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{Omotenashi}.
-One theory is that they are not being treated well enough, and this environment is not compatible with them because of language or culture barriers.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
 
@@
 These are low values (\(RBO_{EXT} < 0.5\)), so we can assert that the satisfaction and dissatisfaction factors of Chinese and English-speaking tourists are different, confirming our hypothesis \ref{hyp:diff_all}.
+
 We then measured the similarity in ranking from the words that were common satisfaction or dissatisfaction factors for both Chinese and English speakers.
@@
 For Chinese customer dissatisfaction, however, 71.4\% of the keywords were managerial, while the other 28.6\% were environmental.
-We discussed how these distributions in managerial or environmental factors having priorities in either population could lead to different management strategies.
-One possible approach is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with managerial factors but have an identifiable method of improving satisfaction by lessening language barriers and providing breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.
-With this strategy, we favor ``long-haul'' Western tourists who spend almost half of their budget on hotels.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-The reason for this being that Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-In this paper, we provide results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
+Our results and discussion can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan, and we can observe their stark differences and shared attributes.
 

### 2020-10-07 2_revisions/V3_ITT_second revision/0_manuscript_blind/itt-emotion_blind.tex
restore png to git from lfs, permissions

--- 2020-09-29 1_manuscript/itt-emotion.tex
@@
 
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
+        \author{REDACTED}
+
+        \authorrunning{REDACTED}
+
+        \institute{REDACTED}
 
@@
     \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel.
+    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
     \end{rsq}
@@
     \end{rsq}
-
     \end{subrsq}
@@
 
+    % We further want to analyze how the differently priced hotels differ in results:
+
+    % \begin{rsq}
+    % \label{rsq:price}
+    % How do Chinese and Western customers' satisfaction and dissatisfaction change across different price ranges?
+    % \end{rsq}
+
   \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
@@
     % Asians vs. Western behavior
-    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.
+    In the past, social science and psychology analyzed from WEIRD (Western, educated, industrialized, rich, and democratic) population samples was wrongly assumed to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.
+This bias is also heavily present in tourist behavior analysis and sampling in previous years.
 
     Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-\cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
-This increase resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce.
+Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
+This increase in research on Chinese tourist behavior resulted in several studies focusing on only the behavior of this subset of tourists.
+To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists.
 One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money.
@@
     One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000.
-The current Chinese economy boom is making an increase in the influx of tourists.
+Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general.
+Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation.
 The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
@@
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
+However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies.
 
@@
 
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  \medskip
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  \medskip
-
-  Conflict of interest: none
+  REDACTED
 

### 2020-10-07 latexcompile.sh
mylatexdiff latexcompile update

@@ -17,7 +17,7 @@ DOCNAME="${INFILE%.*}"
 if [[ $ONLYCLEAN ]];
 then
     echo "Removing secondary files, no compile made"
-    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
+    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out $DOCNAME.spl
 else
     if [[ $NOBIB ]];
     then
@@ -29,7 +29,7 @@ else
         echo "Skipping Bibtex from compile."
     else
         echo "Removing secondary files, starting from scratch"
-        rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
+        rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out $DOCNAME.spl
         pdflatex $DOCNAME.tex
         if [ $? -ne 0 ]; then
             echo "Compilation error. Check log."
@@ -41,7 +41,7 @@ else
     fi
     if [[ $CLEAN ]]; then
     echo "Removing secondary files"
-    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out
+    rm $DOCNAME.blg $DOCNAME.bbl $DOCNAME.aux $DOCNAME.log $DOCNAME.thm $DOCNAME.out $DOCNAME.spl
     fi
 fi
 if [[ $VIEW ]]; then

### 2020-10-07 my_latexdiff.sh

@@ -10,17 +10,31 @@ parser.add_argument('-n', '--newversion', default="2", type=str,
                     help='Version number of the new file. [default %(default)s]')
 parser.add_argument('-o', '--oldversion', default="1", type=str,
                     help='Version number of the new file. [default %(default)s]')
-parser.add_argument('-s', '--setdiffendname', action='store_true',
+parser.add_argument('--setdiffendname', action='store_true',
                     default=False, help='Use provided --diffendname. [default %(default)s]')
-parser.add_argument('-d', '--diffendname', default="paper", type=str,
+parser.add_argument('--diffendname', default="paper", type=str,
                     help='Name of the project to append at end of the diff file. [default %(default)s]')
-parser.add_argument('-m', '--compile', action='store_true',
+parser.add_argument('-m', '--compile', '--make', action='store_true',
                     default=True, help='Compile with latexcompile.sh [default %(default)s]')
 parser.add_argument('-v', '--view', action='store_true',
                     default=True, help='Open the PDF at end of compile. [default %(default)s]')
 parser.add_argument('-c', '--clean', action='store_true',
                     default=True, help='Clean latex secondary files [default %(default)s]')
+parser.add_argument('--graphics-markup', default="new-only", type=str,
+                    help='latexdiff argument pass. Change highlight style for graphics embedded with \includegraphics commands. Check latexdiff -h for more info. [default %(default)s]')
+parser.add_argument('--math-markup', default="coarse", type=str,
+                    help='latexdiff argument pass. Determine granularity of markup in displayed math environments. Check latexdiff -h for more info. [default %(default)s]')
+parser.add_argument('-d','--disable-citation-markup', '--disable-auto-mbox', dest='auto-mbox', action='store_true',
[…]

### 2020-11-20 3_review-responses/V3_review_responses/Reviewer #1 Response.txt
Did most of the reviewers comments except the discussion

Reviewer #1 Response

Thank you for your comments. I will enclose them in hyphens and respond below that section for each comment.

In summary, we agreed with all the comments and revised the manuscript to reflect those changes, as well as added to the reviewed literature in the process.

------------
1. Conceptualisation of satisfaction
How is satisfaction defined in this paper? Is satisfaction different from "perceived value"? Can a customer be satisfied with one aspect while dissatisfied with other aspect? If so, is the customer a satisfied or dissatisfied customer? Satisfaction is a well-researched topic in the hospitality and tourism field and marketing field. Conceptual discussion of satisfaction is necessary.
------------

In our study, we consider the definitions by Hunt (1975) that satisfaction is a realization of a customer's expectation, and posit that customers can have different expectations towards different aspects of a service.

We added more discussion on the conceptual definition of satisfaction for the purposes of our study in section "3.2 Customer satisfaction and dissatisfaction towards individual factors during hotel stay", as well as an actual statement of our definition.

We previously hinged on citing previous definitions and expanding on that, but we agree that it is necessary to state our explicit intentions when discussing satisfaction.

However, we do realize that not knowing the overall satisfaction of each individual customer is a limitation of our study, and thus we added a statement in section "8. Limitations and Future Work.".

------------
2. Conceptualisation of omotenashi (in comparison to hospitality)
What makes Japanese omotenashi different from hospitality in other countries or even in Japan? Do all service organisations in Japan provide omotenashi (high level of hospitality)? What are the factors of omotenashi that differentiate itself form hospitality? Do all hotels provide omotenashi? If omotenashi is used to describe Japanese hospitality and not all hotels provide omotenashi, I recommend the authors to remove omotenashi from research questions (or replace it with another term like hospitality).
------------

In our study, we considered the word Omotenashi to be a cultural aspect in Japan that permeates every business practice. However, we do not intend to measure this influence, or to consider that certain hotels offer more or less omotenashi than others. Rather, our study focuses on the results of that influence: service, staff behavior and hospitality. All of these factors are universal to every kind of hotel, so we removed the word Omotenashi from our research questions.

We'd like to note that when speaking in Japanese, there is no other word for hospitality rather than omotenashi, so in the sense that we wrote this paper in Japan, we didn't realize there could be a theoretical confusion in this aspect. There is no practical difference of omotenashi and hospitality in Japan in the eyes of our study, and the only difference from other countries, is that the culture in Japan has a strong practice of this hospitality in any service business.

------------
3. WEIRD sample
The authors argued that WEIRD sample is biased. I would like to know how the samples for this study are not from WEIRD sample. Similarly, the authors are expected to elaborate on how well their sample represent the population (all Chinese and Western hotel guests). If the authors cannot prove, I recommend the authors to delete the WEIRD sample section or not to have discussion about a biased sample from the manuscript. Instead, the authors may want to elaborate on the role of culture in expectation and evaluation. What makes Chinese customers value hard attributes more than soft ones? I believe the value of this research is in the comparison between Chinese and Western customers, rather than a biased (WEIRD) vs. unbiased sample.
------------

Our samples are not from the WEIRD sample simply because we include non-Western subjects in our sample. However, we agree that arguing for biased or unbiased deters from the main objective of our paper, and adds little value to our argument. Therefore we removed it as asked.

We discuss the role of culture in expectation and evaluation a bit more, as we will state in the following comment.

------------
4. Discussion
I feel the discussion section reads like another version of findings/results. I expect more fundamental/theoretical discussions, which are derived from findings/results. What is known about Chinese and Western cultures? How do these known cultural characteristics affect evaluation of service? Are there something similar and/or different between what we know about the culture and what this study found?
------------

A

=======================
Minor comments:

1. High level of hospitality (line 127)
It is recommended to avoid such adjective-noun phrase as "high level" in this manuscript. How is "high level" of hospitality defined? Unless it is objectively measured, such a phrase is subjective and hurts reliability and validity of the paper.
------------

We rephrased to avoid being subjective in this matter.

------------
2. Not much value added (lines 130 - 136).
I am not sure what message these statements try to deliver.
------------

We removed these and rewrote part of this section to better flow into the research questions.

------------
3. Japanese omotenashi factors (line 139)
Do Japanese omotenashi factors mean hard and soft attributes in Japanese hotels? If so, in what aspects are they (hard and soft attributes in Japanese hotels) different from hard and soft attributes in other countries?
------------

We changed this to "hospitality and service factors". The misconstruction here is that the word Omotenashi in the Japanese language includes both hospitality and service, so it was used as an abbreviation for these. We realized this is confusing for people that don't speak Japanese so we removed instances where this happens across the paper (not only in line 139).

------------
4. Different reaction to Japanese omotenashi factors (line 145)
How is a reaction defined in this study? Isn't it evaluation, which emphasises cognitive and affective aspects, whereas reaction emphasises a behavioral aspect? 
------------

We changed this to evaluation, as pointed out.

------------
5. Hotel lodging (line 147)
It does not sound right. "hotel stay" would be better.
------------

We changed this in the manuscript.

------------
6. Easily changeable if small investments (line 646)
Again, "easily" and "small" are subjective. How is small investment defined? Getting rid of cigarette smell from rooms (assuming it requires the rooms unoccupied for a long period of time) may cost them more than renovating an entire floor.
------------

We changed the definition of soft and hard attributes to be less subjective. Soft attributes are those that the management and staff can directly influence, such as service factors. hard attributes are those that relate to physical aspects of the hotel, such as facilities, location, infrastructure, environment, etc. Technically speaking, the categories stay the same, but the definition lends itself to be objective in this definition.

------------

Thank you for your commentary, we hope this revised version is to your liking.

### 2020-11-20 1_manuscript/itt-emotion.tex
Did most of the reviewers comments except the discussion

@@
 Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes a hotel can change or be more concerned with hard attributes that hotel management cannot change?
+Will they be satisfied with the soft attributes of a hotel like service or be more concerned with hard attributes like location and facilities?
 We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
@@
 
-  However, recent studies on social sciences, and thus, on tourist behavior, have been performed using surveys on WEIRD (Western, educated, industrialized, rich, and democratic) populations that are culturally biased for the western world \cite[][]{nielsen2017}.
-The term WEIRD was coined by \cite{henrich2010weirdest}, who criticizes studies that assume that the subjects chosen from these populations are a representative sample of the rest of the world.
-This bias, albeit without the acronym, was discussed earlier about social psychology by \cite{hogan1978biases}.
-\cite{guaratne2009} pointed this bias out in discussions of globalization.
-At the same time, \cite{nielsen2017} sampled papers on developmental psychology and statistically examined this bias.
-This western bias is pervasive in all kinds of social sciences, and tourism science is not an exception.
-For example, studies are easily performed in the language of the scientist doing surveys for the subjects.
-A great majority of tourist behavior in history analysis has been performed with Western subjects and was thought to be universal until recent years.
-
+  However, a great majority of tourist behavior analysis has been performed with Western subjects and a gap in knowledge and discussion existed until the recent decades.
 Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
@@
 More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as difficult or impossible elements to change by hotel management without investing in infrastructure or real estate.
-In contrast, soft attributes are easily modifiable by improvements in management.
+We define hard attributes as relating to physicial aspects and environmental aspects, such as the facilities of the hotel, the location of the hotel, infrastructure and real estate nearby.
+In contrast, soft attributes are the non-physical attributes of the hotel related to services, staff or management.
 
@@
 
-  \subsection{Japanese hospitality: \textit{Omotenashi}}\label{theory_omotenashi}
+  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
 
@@
 In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-
-    It stands to reason that this high level of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in Japan, every business has this high level of hospitality, in differing levels of success.
-A simple convenience shop around the corner could be more hospitable if hotel management falls behind.
-Businesses have to strive to be the most hospitable, as hotels cannot lag in this competition.
-Thus, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
-Customers can always achieve satisfaction from hospitality elsewhere, so hotels need to be competitive in their hospitality.
+This is permeating into every kind of business with customer interaction in Japan, where a simple convenience shop could express all of these standards of hospitality and service, which aren't exclusive to hotels.
+
+    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
+However, in many cases, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
+In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly, but rather consider it as a cultural factor that influences all businesses in Japan and observe the customers evaluations regarding service and hospitality factors in general, which can be compared to other places and business practice in the world.
+In summary, our study considers the influence of the cultural aspect of \textit{omotenashi}, while only studying the evaluations of service, hospitality and staff behavior factors that are universal to all hotels in any country.
 
@@
     \begin{rsq}
-    \label{rsq:omotenashi}
-    To what degree are Chinese and Western tourists satisfied with Japanese \textit{omotenashi} factors such as staff behavior or service?
+    \label{rsq:hospitality}
+    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
     \end{rsq}
@@
     However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different reaction.
+Different cultures interacting with it could have a different evaluation of it.
 While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
@@
     \begin{rsq}
-    \label{rsq:omotenashi_both}
-    Do Western and Chinese tourists have a different reaction to Japanese \textit{omotenashi} factors such as staff behavior or service?
+    \label{rsq:hospitality_both}
+    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
     \end{rsq}
@@
 
-  \subsection{Customer satisfaction and dissatisfaction during hotel lodging}\label{theory_satisfaction}
+  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
 
@@
 
+    In this study, however, we study not overall customer satisfaction, but the satisfaction and dissatisfaction that stem from individual specific expectations, be they conscious or unconscious.
+For example, if a customer has a conscious  expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
+However if that same customer had a conscious expectation of a comfortable sleep but there were loud noises at night, that is a different aspect that they can be dissatisfied with, regardless of the satisfaction towards the bed.
+Then, the same customer might have packed their own toiletries, thinking that the amenities might not include those, and then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
+While this definition of satisfaction and our current method does not allow us to examine overall customer satisfaction, it will allow us to examine the factors that a hotel can revise individually, and how they are perceived by a population as a whole.
+In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different aspects of a service.
+In our study, therefore, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
+Dissatisfaction, on the other hand, is the emotional response to the lack of a realization, or an under-performance of these conscious or unconscious expectations towards specific aspects of a service.
+
     Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
@@
 
-    Previous research has also focused on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, or facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, little focus is put on hard factors uncontrollable by the hotel staff that can play a part in the customers' choice behavior and satisfaction.
+    Previous research has also focused more on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
+However, hard factors uncontrollable by the hotel staff can play a part in the customers' choice behavior and satisfaction.
 Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
@@
     % Asians vs. Western behavior
-    In the past, tourist behavior analyzed from western samples was wrongly thought to be a representation of universal behavior across all cultures \cite[][]{nielsen2017, henrich2010weirdest, guaratne2009, hogan1978biases}.
-
+    In the past, social science and tourism studies focused greatly on Western tourist behavior in other countries.
 Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-\cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
-This increase resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce.
+Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
+This increase in research on Chinese tourist behavior resulted in several studies focusing on only the behavior of this subset of tourists.
+To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists.
 One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money.
@@
 Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are those that hotel management can easily change those attributes without investing in infrastructure or real estate.
-Hard attributes are impossible or impractical to change.
+Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which are able to be changed by the staff or management.
+Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, the surroundings of the hotel, which are impossible to change directly by the staff alone.
 
@@
     To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define these by the feasibility with which hotel management might improve to satisfy the customer further.
-We define hard attributes as matters that would be impossible for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but of high investment and risk.
-On the other hand, soft attributes are attributes of the hotel that are easily changeable if small investments are made.
+We define hard attributes as matters regarding physical or environmental aspects of the hotel, such as facilities, location, or infrastructure, that would be impractical for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but regarding investment in infrastructure.
+On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
 For example, the hotel's services or the cleanliness of the rooms are soft attributes.
+For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the physical structure of the hotel are also considered soft attributes.
 Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
@@
     We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing unchangeable factors by the staff or management, we consider them hard.
+If the word is describing unchangeable physical factors by the staff or management, we consider them hard.
 If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
@@
     Our research questions were about two things.
-In research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the service and \textit{omotenashi} hospitality in Japan, and how are they different in their perceptions in this matter.
+In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
 We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
@@
     In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions.
-Here we define hard attributes as impossible or impractical to change for the hotel management, such as the surroundings, view, or location convenience.
-On the other hand, soft attributes are those that the hotel could easily and practically change without many limitations, such as improving the hotel's services via training or hiring specialized staff.
+Here we define hard attributes as those relating to physical, structural or environmental aspects of the hotel, which are often impossible or impractical to change directly by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
+On the other hand, soft attributes are those that the hotel staff and management could practically change directly, such as improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
 In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
@@
 When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-The word ``great'', which is also high in most price ranges, and the top keyword in the highest-priced hotels, is also accompanied by mostly soft attributes, in pairings such as ``great location'', ``great view'' and ``great service'', if we include the counts from all the price ranges together.
-Japanese high standards in hospitality very likely influenced this result.
 
@@
 
-  Below we explore the possible interactions with \textit{omotenashi}; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry.
+  Below we explore the possible interactions with Japanese hospitality; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry.
 We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.
 
-  \subsection{Western and Chinese tourists in the \textit{omotenashi} environment}\label{disc:omotenashi}
+  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
 
@@
 One thing is clear for hotel managers, however.
-Competing in \textit{omotenashi} does include language services, especially in the international tourism industry.
+Competing in hospitality and service does include language services, especially in the international tourism industry.
 Better multilingual support can only improve that already high standard in Japan.
@@
 Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction.
-This is where \textit{omotenashi} comes into play and enhances the experience of the customers.
+This is where hospitality and service come into play and enhances the experience of the customers.
 
@@
     Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards \textit{omotenashi}.
+As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
 Instead, they focus on the hard attributes of a hotel.
 Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management can influence to hard-set ones.
+On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management and staff can directly influence to hard-set ones.
 The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
@@
 
-  This study analyzed the differences in customers' expectations at different levels of \textit{omotenashi} by dividing our data into price ranges.
+  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
 However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
@@
 
+  An important aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
+This gives us insight on which factors are possible to focus on by hotel managers in applying this knowledge.
+However, our study was limited in that the overall satisfaction of each individual customer was not measured.
+This could be done by rating the volume of text used to describe satisfaction factors against the volume of text used for dissatisfaction.
+However, this imposes a few difficulties that are out of the scope of this study.
+
   Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
@@
   In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:omotenashi} and \ref{rsq:omotenashi_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
+To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
 We used these keywords for sentiment classification via an SVC.
@@
 On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
-We consider that Western tourists are more reactive to \textit{omotenashi} than their Chinese counterparts.
+We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
 
   Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via managerial decisions by an improvement in services or small investments.
-On the other hand, hard attributes are elements that are impossible or highly impractical to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
+Soft attributes can be changed via management and staff by an improvement in services.
+On the other hand, hard attributes are elements that are physical and impractical to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
 We found that for satisfaction, Western tourists favor soft attributes.

### 2020-11-21 3_review-responses/V3_review_responses/Reviewer #1 Response.txt
Finished reviewing comments

@@
 
-A
+We agree that we hadn't discussed culture and its influence in expectations in as much depths as we could have.
+We added references to Hofstede's and GLOBAL models of cultural dimensions, and discussed how some of these might influence if customers prefer hard or soft attributes in section "7.2 Hard vs.
+soft satisfaction factors".
+
+We mainly found that the individualistic aspect of Western culture had an influence in their expectations towards service, and that the collectivist aspect of Chinese culture lead to a lowered regard for soft attributes.
 

### 2020-11-21 1_manuscript/itt-emotion.tex
Finished reviewing comments

@@
 As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
+Previous studies on the dimensions of culture that influence differences in expectations have also been performed in the past \cite{donthu1998cultural}.
 Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
@@
 This premise also plays a role in the differentiation between the preference of hard or soft attributes.
+
+    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}, where it is stated that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
+These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
+In each of these dimensions, at least one element of service expectations were found to be significantly different for countries grouped under contrasting attributes (e.g.
+individualistic countries vs collectivist countries, high uncertainty avoidance countries vs low uncertainty avoidance countries).
+Although Hofstede's typology, particularly the fifth dimension, which was added with the alternate name \textit{Confucian dynamic}, has received criticism from academics with a Chinese background for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
+Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions .
+The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
+This avoids making the assumption that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
+Gender stereotypes such as these have also been subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
+Our study is in agreement with these critiques, and therefore will avoid considering these for our discussion.
+
+    The background of collectivism in China and individualism in Western countries that have been studied before \cite[][]{gao2017chinese}, the differences in these dimensions of culture could be the underlying cause for differences in expectations.
+Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
+
+    For our purposes in contrasting Western vs.
+Chinese satisfaction stemming from expectations, these dimensions could provide insight into why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied often with soft factors.
 Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
@@
 A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
+According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider compared to collectivist customers, which are aspects of service, a soft attribute of a hotel.
+
+    Among other dimensions in both models, we can consider uncertainty avoidance.
+While high uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
+However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
+While we know that the USA is not representative of the whole of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
+Another factor, power distance, was also shown to be different when measured by Hofstede's method compared to the GLOBAL method, so we decide against making this comparison.
 

### 2020-11-21 1_manuscript/cur_dir_my_latexdiff.sh
Added latexdiff for comments from teacher

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V2-1.tex itt-emotion.tex --newversion="3" --compile --view --clean
+../my_latexdiff.sh itt-emotion_V3.tex itt-emotion.tex --newversion="4" --compile --view --clean

### 2020-11-26 0_coverletter/itt-emotion-coverletter.tex
Added blind manuscript and latexdiff fix, coverletter,references

@@
 
-We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the revised title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.
+We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.
 
 We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further.
-This revision required adding new experiments and methodology, namely the introduction of a dependency parser and a part of speech tagger to extract adjective+noun pairs, in order to understand what customers are praising or describing.
-Finally, thanks to our reviewers, our paper has now another layer of depth by analyzing differences in satisfaction factors across different price ranges for hotels.
-We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels.
+This was a minor revision, with a few additions to the reviewed literature.
+
+As stated before, We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels.
 We discuss theories on the reason behind this in our revised paper.
@@
 
-We believe our new results and discussion are very interesting, and hope we continue to be in your consideration.
+We believe this was an appropriate response to the minor revision, and hope we continue to be in your consideration.
 

### 2020-11-26 0_manuscript_blind/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_blind_V2-1.tex itt-emotion_blind.tex --newversion="3" --compile --view --clean
+../my_latexdiff.sh itt-emotion_blind_V3.tex itt-emotion_blind.tex -d --newversion="4" --compile --view --clean

### 2020-11-26 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V3.tex itt-emotion.tex --newversion="4" --compile --view --clean
+../my_latexdiff.sh itt-emotion_V3.tex itt-emotion.tex --newversion="4" --compile --view --clean 

### 2020-11-26 2_revisions/V4_ITT_minor_revision/0_manuscript_blind/itt-emotion_blind.tex
Added to revisions folder

--- 2020-11-21 1_manuscript/itt-emotion.tex
@@
 Although Hofstede's typology, particularly the fifth dimension, which was added with the alternate name \textit{Confucian dynamic}, has received criticism from academics with a Chinese background for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions .
+Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
 The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.

### 2020-11-26 2_revisions/V4_ITT_minor_revision/1_manuscript/itt-emotion_V3.tex
Added to revisions folder

--- 2020-10-07 2_revisions/V3_ITT_second revision/0_manuscript_blind/itt-emotion_blind.tex
@@
 
-        \author{REDACTED}
-
-        \authorrunning{REDACTED}
-
-        \institute{REDACTED}
+        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
+                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
+                Hirofumi Nonaka                                                 \protect\affmark[1] \and
+                Toru Hiraoka                                                    \protect\affmark[2]
+        }
+
+        \authorrunning{E. Alemán Carreón et al.}
+
+        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
+                    % Nagaoka University of Technology, Nagaoka, Japan \\
+                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
+                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
+                    % Corresponding Author %  \\
+                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+                \and
+                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
+                    % Nagaoka University of Technology, Nagaoka, Japan \\
+                    \hspace*{1em} \email{mendoza.espana@gmail.com}
+                \and
+                    \hspace*{1em} Hirofumi Nonaka \at
+                    % Nagaoka University of Technology, Nagaoka, Japan \\
+                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
+                \and
+                    \hspace*{1em} Toru Hiraoka \at
+                    % University of Nagasaki, Nagasaki, Japan \\
+                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
+                \and
+                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
+                \and
+                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
+        }
 
@@
 
-  REDACTED
+  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
+We would like to show gratitude to Mr.
+Liangyuan Zhou, Ms.
+Min Fan, and Ms.
+Eerdengqiqige for this.
+
+  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+  \medskip
+
+  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+  \medskip
+
+  Conflict of interest: none
 

### 2020-11-26 2_revisions/V4_ITT_minor_revision/0_manuscript_blind/cur_dir_my_latexdiff.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_blind_V3.tex itt-emotion_blind.tex -d --newversion="4" --compile --view --clean

### 2020-11-26 2_revisions/V4_ITT_minor_revision/1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_V3.tex itt-emotion.tex --newversion="4" --compile --view --clean 

### 2020-12-23 0_titlepage/itt-emotion-titlepage.tex
Finished grammar check - send to nonaka

@@
         \usepackage{lineno, hyperref}
-% \usepackage[hyperfootnotes=false]{hyperref}
         \usepackage{array, pbox}
@@
         \usepackage{caption}
+        \usepackage{subcaption}
         \usepackage{graphicx}
@@
 
-% Stick footnotes to bottom of the page
-\usepackage[bottom]{footmisc}
-
         % To insert commas into large numbers automatically
@@
 
-% To add hypothesis theorem
+        % To add research questions
         \usepackage{ntheorem}
         \theoremseparator{:}
-\newtheorem{hyp}{Hypothesis}
+        \newtheorem{rsq}{Research Question}
 
-% To add subhypothesis theorems
+        % To add subrsq theorems
         \makeatletter
-\newcounter{subhyp} 
-\let\savedc@hyp\c@hyp
-\newenvironment{subhyp}
+        \newcounter{subrsq} 
+        \let\savedc@rsq\c@rsq
+        \newenvironment{subrsq}
          {%
-  \setcounter{subhyp}{0}%
-  \stepcounter{hyp}%
-  \edef\saved@hyp{\thehyp}% Save the current value of hyp
-  \let\c@hyp\c@subhyp     % Now hyp is subhyp
-  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
+          \setcounter{subrsq}{0}%
+          \stepcounter{rsq}%
+          \edef\saved@rsq{\thersq}% Save the current value of rsq
+          \let\c@rsq\c@subrsq     % Now rsq is subrsq
+          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
          }
          {}
-\newcommand{\normhyp}{%
-  \let\c@hyp\savedc@hyp % revert to the old one
-  \renewcommand\thehyp{\arabic{hyp}}%
+        \newcommand{\normrsq}{%
+          \let\c@rsq\savedc@rsq % revert to the old one
+          \renewcommand\thersq{\arabic{rsq}}%
         } 
@@
 
-\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures}
+\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
 
-\titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}
+% Fold 1
+  % Fold 2
+    % Fold 3
+      % Fold 4
+        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
 
@@
 
-During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the interpretation of the data.
+  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
 We would like to show gratitude to Mr.

### 2020-12-23 0_manuscript_blind/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_blind_V3.tex itt-emotion_blind.tex -d --newversion="4" --compile --view --clean
+../my_latexdiff.sh itt-emotion_blind_V4.tex itt-emotion_blind.tex -d --newversion="5" --compile --view --clean

### 2020-12-23 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V3.tex itt-emotion.tex --newversion="4" --compile --view --clean 
+../my_latexdiff.sh itt-emotion_V4.tex itt-emotion.tex --newversion="5" --compile --view --clean 

### 2021-02-04 1_manuscript/itt-emotion.tex
Made files to send to correction service 5707 words and 7729 words

--- 2020-11-20 1_manuscript/itt-emotion.tex
@@
 
-\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures}
+\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
 
@@
       % Fold 4
-        \titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}
+        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
 
@@
 Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world.
+However, before the shift that has brought a global perspective in recent years, most tourist behavior studies were biased for the Western world.
 Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
@@
 Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes of a hotel like service or be more concerned with hard attributes like location and facilities?
+Will they be satisfied with the soft attributes like service or be more concerned with hard attributes like location and facilities?
 We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
@@
   Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}.
+The spirit of Japanese hospitality is celebrated worldwide in a single Japanese word: \textit{Omotenashi}.
 With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
@@
 
-  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
+  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009}.
+There was a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
 From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
@@
 Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Hotel management, therefore, needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, a great majority of tourist behavior analysis has been performed with Western subjects and a gap in knowledge and discussion existed until the recent decades.
+Therefore, Hotel management needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
+
+  However, many tourist behavior analyses have been performed with Western subjects.
+As such, a gap in knowledge and discussion existed until recent decades.
 Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations.
+The few that compare Asian to Western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples.
+These, while valid, can have their limitations.
 This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
@@
   In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior and perform an exploration of the data to discover factors that could have been overlooked in the past.
+With this data, we can confirm existing theories about their differences in behavior and explore the data to discover factors that could have been overlooked in the past.
 To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
@@
 More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physicial aspects and environmental aspects, such as the facilities of the hotel, the location of the hotel, infrastructure and real estate nearby.
-In contrast, soft attributes are the non-physical attributes of the hotel related to services, staff or management.
+We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, the hotel's location, infrastructure, and real estate nearby.
+In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
 
@@
 In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-The short scope of those studies means that cultural and language differences often cannot be observed in a single study.
+These studies' short scope often leads to difficulties in observing cultural and language differences in a single study.
 
@@
 In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This is permeating into every kind of business with customer interaction in Japan, where a simple convenience shop could express all of these standards of hospitality and service, which aren't exclusive to hotels.
+This hospitality culture permeates every kind of business with customer interaction in Japan.
+A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
 
     It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in many cases, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.
-In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly, but rather consider it as a cultural factor that influences all businesses in Japan and observe the customers evaluations regarding service and hospitality factors in general, which can be compared to other places and business practice in the world.
-In summary, our study considers the influence of the cultural aspect of \textit{omotenashi}, while only studying the evaluations of service, hospitality and staff behavior factors that are universal to all hotels in any country.
+However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
+In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly.
+Instead, we consider it as a cultural factor that influences all businesses in Japan.
+We then observe the customers' evaluations regarding service and hospitality factors in general, which can be compared to other places and business practices in the world.
+In summary, our study considers the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations of service and hospitality factors that are universal to all hotels in any country.
 
@@
 As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
+Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
 Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
@@
 These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.
+In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
 
@@
 
-    In this study, however, we study not overall customer satisfaction, but the satisfaction and dissatisfaction that stem from individual specific expectations, be they conscious or unconscious.
-For example, if a customer has a conscious  expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
-However if that same customer had a conscious expectation of a comfortable sleep but there were loud noises at night, that is a different aspect that they can be dissatisfied with, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their own toiletries, thinking that the amenities might not include those, and then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-While this definition of satisfaction and our current method does not allow us to examine overall customer satisfaction, it will allow us to examine the factors that a hotel can revise individually, and how they are perceived by a population as a whole.
-In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different aspects of a service.
-In our study, therefore, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-Dissatisfaction, on the other hand, is the emotional response to the lack of a realization, or an under-performance of these conscious or unconscious expectations towards specific aspects of a service.
+    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
+For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
+In that case, they will be satisfied with this matter.
+However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
+In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
+Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
+They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
+This definition of satisfaction does not allow us to examine overall customer satisfaction.
+However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
+In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different service aspects.
+Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
+On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
 
@@
 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The use of the Likert scale leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
+The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
 However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
@@
 
-    Previous research has also focused more on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors uncontrollable by the hotel staff can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.
+    Previous research has also focused more on soft attributes, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
+However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
+Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
 
@@
 
-    % We further want to analyze how the differently priced hotels differ in results:
-
-    % \begin{rsq}
-    % \label{rsq:price}
-    % How do Chinese and Western customers' satisfaction and dissatisfaction change across different price ranges?
-    % \end{rsq}
-
   \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
@@
     % Asians vs. Western behavior
-    In the past, social science and tourism studies focused greatly on Western tourist behavior in other countries.
+    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
 Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism.
-This increase in research on Chinese tourist behavior resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities.
+Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
+This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
+To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies explicitly comparing Chinese and Western tourists.
+One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
+Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
+At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
+Both groups tend to have high expectations for the overall facilities.
 Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.
+In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
 
     One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general.
-Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation.
+Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
+Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
 The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
@@
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies.
+However, our study of online reviews takes the data that the hotel customers uploaded themselves.
+This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
+Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
 
@@
     % Universal behavior
-    Other studies, perhaps recognizing that samples from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
+    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
+\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
 \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
 As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
+In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
 The general satisfaction score was noticed to be different in those countries.
@@
 Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists.
+According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
 Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
@@
 Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller to ours in comparison.
+The number of samples in other text-mining studies is also smaller than ours in comparison.
 Apart from that, every study has a different text mining method.
@@
 Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its own conclusions.
+In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
 Our study calls for a supervised machine since text analysis can be intricate.
@@
 Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction, and using these to label the rest of the data.
+Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
 We are not exploring new patterns in the sentiment data.
@@
 Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that because it has no intervention from the researchers in making questionnaires, it can have different results from anything that the researchers could expect.
+Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could expect.
 These qualities determine why, much like actual mining, data mining is mostly exploratory.
 One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about where to find knowledge and what kind of knowledge we can uncover.
+However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
 The exploration of large opinion datasets with these methods is essential.
@@
 However, we are using a database of several orders of magnitude larger.
-We can also expect that we may discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
+We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
 
@@
 
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}.
+  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
 We then determined the most commonly used words that contribute to positive and negative opinions in a review.
@@
 We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review.
+We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
+We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
 We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
 Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which are able to be changed by the staff or management.
-Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, the surroundings of the hotel, which are impossible to change directly by the staff alone.
+Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management.
+Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.
 
@@
 We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, which can give us an insight into the kind of service that is offered.
+The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
+Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
 After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
@@
 
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
+    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
 Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
@@
 This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end, and cheap business hotels on the higher end.
+The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
 Further on, there are business hotels in the next range (10,000 to 15,000 yen).
@@
 
-    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections.
+    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
 We show an example of these dependencies in Figure \ref{fig:depparse}.
-In this study, we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
+This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
 A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
@@
 This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, which is the class's syntactic subject.
+The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
 We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
@@
 We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.
+We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
 
@@
 However, depending on the data, it can increase false negatives.
-Inversely, high C values will likely result in minimal false negatives, but a possibility of false positives.
+Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
 SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
@@
     Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word that is included in many documents will have a high entropy value for that set of documents.
+A word included in many documents will have a high entropy value for that set of documents.
 Opposite to this, a word appearing in only one document will have an entropy value of zero.
@@
     Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a point of data, a row in the vector \(x\).
+Each training sentence is a data point, a row in the vector \(x\).
 Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
@@
 
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to classify new data correctly.
+    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
 These changes to the weight vector are greater for features close to the separating hyperplane.
@@
 We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentences counts shown in Table \ref{tab:exp_notes} are the result of applying our SVC for classification.
+Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
 
@@
     Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-In order to understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While there were many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
+To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
+While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
 We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
@@
     To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding physical or environmental aspects of the hotel, such as facilities, location, or infrastructure, that would be impractical for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but regarding investment in infrastructure.
+We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
+Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
+Others can be expensive to change, such as matters requiring construction costs, which are possible but regarding infrastructure investment.
 On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
 For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the physical structure of the hotel are also considered soft attributes.
+For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are also considered soft attributes.
 Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
@@
 This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the adjectival pairing of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that mostly, they praise either the location, the service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
+When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
+When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
 With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
@@
     We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews, while it was not statistically identified as a problem for their Chinese counterparts.
+For example, English-speaking customers mentioned tobacco smell in many reviews.
+However, it was not statistically identified as a problem for their Chinese counterparts.
 On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
@@
 
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions.
-Here we define hard attributes as those relating to physical, structural or environmental aspects of the hotel, which are often impossible or impractical to change directly by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, soft attributes are those that the hotel staff and management could practically change directly, such as improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance.
+    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
+Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
+These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
+On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
+Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
+There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
 English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
@@
     One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute, and is unlikely to change for most hotels.
+This is, however, a hard attribute and is unlikely to change for most hotels.
 
@@
 
-    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels.
+    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
 From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
@@
     One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' and in a lower ranking.
+While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
 In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
@@
 The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings.
+Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
 However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
@@
     While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels where we infer users would be expecting this feature the most.
+This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
 Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
@@
 
-    A concern for Western tourists was the smell of tobacco in their room.
-This can be considered a soft attribute.
-Not only as a standalone word of ``cigarette'', but also confirming with word pairs in Table \ref{tab:adj_en_neg}, we can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non- smoking, yet, the smell permeated the room and curtains.
+    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
+Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
+We can find other related word pairs such as ``funny smell''.
+Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
 Another common complaint was that there were no non-smoking facilities available at all in the first place.
@@
 
-    Japan has a polarized view on smoking, and despite being one of the world’s largest tobacco markets, its use has been decreasing in recent years.
+    Japan has a polarized view on the topic of smoking.
+Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
 Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
 However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke to an enclosed area and avoid bothering others.
+However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
 Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
@@
 
-    The hotel's location, closeness to the subway and public transport, and availability of nearby shops were observed to be of importance to both Chinese and English-speaking tourists.
+    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
 In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
@@
 In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience, with a matching price.
+In Japan, taxis are made to provide a high-quality experience with a matching price.
 This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
@@
 
-  Below we explore the possible interactions with Japanese hospitality; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.
+  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
+We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
 
@@
     To this day, scholars continue to correct our historical bias towards the west.
-In this time, studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
+Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
 Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
@@
 
-    Our results indicate that out of the two; Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
+    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
 As explained earlier in this paper, Japan is famous for its customer service all over the world.
@@
 However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service also go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in the satisfaction of Western tourists.
+Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
+We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
 
@@
 However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied in this matter, but rather that they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
+Thus, we cannot say that they are not satisfied with this matter.
+Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
 
@@
 channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied, since traveling in a strange land without knowing the language can be a daunting experience.
+It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
 \cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
@@
 In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
+Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
 On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
@@
 
-    As we stated in section 3.2, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
+    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
 Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes, such as the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
+However, hard attributes are not usually analyzed in satisfaction studies.
+Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
 Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
 
-    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
+    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
 In contrast, only 20\% are soft factors.
@@
 That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions (Saulton et al.
-2017).
+Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
 Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
@@
 Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery (Ryan and Mo 2001).
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well, which is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes, if we observe Figure \ref{fig:hard_soft_en}, where soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
+We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
+These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
+This keyword is present in hotels priced at more than 20,000 yen per night.
+
+    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
+Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
 This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list, except for the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve in ways that will attract more customers in the future.
+English-speaking customers also have soft attributes at the top of their list.
+The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
+If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
 If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
 
-    In general, for both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in the list in lower-priced hotels.
+    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
+However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
 In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
 A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in the case of Japanese hotels and has more to do with the pricing of hotels overall.
+However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
 The tourists coming to Japan could be both experienced travelers or first-time travelers.
@@
     Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-This is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding, all of which can be costly.
+The previous is true for all price ranges.
+Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
+All of these options can be costly.
 However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
 Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the location and construction of the hotel are set for Chinese customers, not much else can be done to satisfy them further.
+However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
 As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
 
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes, with a low of 35\% in the highest price range where undefined factors are the majority, and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
+    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
+They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
 The room for improvement for Western tourists is more extensive than their Chinese counterparts.
@@
 This premise also plays a role in the differentiation between the preference of hard or soft attributes.
+
+    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
+That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
+These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
+In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
+collectivist countries, high uncertainty avoidance countries vs.
+low uncertainty avoidance countries).
+However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
+Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
+Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
+The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
+This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
+Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
+Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
+
+    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
+These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
+Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
+
+    For our purposes in contrasting Western vs.
+Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
 Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
@@
 A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
+According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
+Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
+
+    Among other dimensions in both models, we can consider uncertainty avoidance.
+High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
+On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
+However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
+While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
+Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
 
@@
 Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in language to describe their satisfaction with the same topics.
+The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
 We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
@@
 In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is higher and that it influences how customers write their reviews.
+We can infer that the level of satisfaction is high and influences how customers write their reviews.
 However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
@@
 
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where it is the meeting or exceeding of expectations that produces satisfaction.
+    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
 Therefore, the lack of meeting expectations would cause dissatisfaction.
@@
 This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness or, in the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, the smell of cigarettes can lead to disappointment or outrage.
+As such, any lack of cleanliness can lead to disappointment or outrage.
+In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
 However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
@@
     In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any sort of standard.
-For example, having a nice customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations, and thus a higher satisfaction.
+However, they do not measure it against any standard.
+For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
+Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
 This is where hospitality and service come into play and enhances the experience of the customers.
@@
 It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and citing \cite{japan2014consumption}, shows that common products besides food and drink are electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit.
-There is an understanding that the fact that tourists choose to shop in Japan has more to do with the quality of the items rather than their relation to the touristic attractions.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
+The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
+There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
 Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
@@
 
-    While some aspects of satisfaction and dissatisfaction change depending on the price range the hotel is in, some other factors stay mostly constant for each culture's customers.
+    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
 For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take its place in the ranking.
+Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
 However, it is still high on the list.
 Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-Transport and location, as discussed in section \ref{disc:location}, are also important for hotels of all classes and prices.
+As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
 While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a certain bias to consider some attributes more than others.
+This suggests that culturally the customers have a particular bias to consider some attributes more than others.
 
@@
 Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists, or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes that management and staff can directly influence to hard-set ones.
+Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
+On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
 The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
@@
 
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers as well.
+    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
 As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings since before the hotel is constructed.
+Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
 A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
@@
 Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more on cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
+For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
 On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
@@
 We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context that these words were being used in by using a dependency parser and observing the related nouns.
+Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
 However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
@@
 Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service, although still there is a divide between western and Japanese style hotels.
-
-  An important aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight on which factors are possible to focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each individual customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the volume of text used for dissatisfaction.
+However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
+However, there is still a divide between western and Japanese style hotels.
+
+  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
+This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
+However, our study was limited in that the overall satisfaction of each customer was not measured.
+This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
 However, this imposes a few difficulties that are out of the scope of this study.
@@
   In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and in different kinds of hotels and between customers traveling alone or in groups, for fun or work.
+We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
 Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
@@
 However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment, and both cultures have a different way of reacting to different prices.
+We found that both cultures have a different reaction to this hospitality environment.
+Both cultures have a different way of reacting to different prices.
 From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
@@
 We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by the vocabulary they use for expressing their satisfaction.
+On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
 We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
@@
 Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are elements that are physical and impractical to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots or elements out of the control of the hotel managers.
+On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
 We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in hard attributes of hotels, consistently across price ranges.
+In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
 For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
@@
 
-  One possible approach for hotel managers is to try to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
+  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
 They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect, as well as making the hotels tobacco-free.
+Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
 We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.

### 2021-02-04 Z_manuscript_for_correction_service/itt-emotion.tex
Made files to send to correction service 5707 words and 7729 words

--- 2021-02-04 1_manuscript/itt-emotion.tex
@@
 
+        \usepackage{bibentry}
+
         \modulolinenumbers[5]
@@
 
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
+        \author{REDACTED}
 
@@
 
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
+        \institute{REDACTED}
 
@@
 
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[htp]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
   \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
@@
 
-\section{Methodology}\label{method}
-
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management.
-Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
-Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a data point, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
-
 \section{Data Analysis}\label{dataanalysis}
@@
 After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
 
@@
 Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
 
@@
 For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
 
@@
 
-\begin{acknowledgements}
-
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  \medskip
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  \medskip
-
-  Conflict of interest: none
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
+\nobibliography{bibfile-emotion}
 

### 2021-02-04 Z_manuscript_for_correction_service/itt-emotion_first_half.tex
Made files to send to correction service 5707 words and 7729 words

--- 2021-02-04 Z_manuscript_for_correction_service/itt-emotion.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \usepackage{bibentry}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
 \begin{document}
@@
 \title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{REDACTED}
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{REDACTED}
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
 
@@
 
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
-Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
-Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
-We can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
-Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied with this matter.
-Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in hospitality and service does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-The previous is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
-All of these options can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
-They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-    On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
-Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
-These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
-
-    For our purposes in contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
-Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
-On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is high and influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment or outrage.
-In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any standard.
-For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
-This is where hospitality and service come into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
-There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
-However, it is still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
-However, there is still a divide between western and Japanese style hotels.
-
-  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
-However, this imposes a few difficulties that are out of the scope of this study.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment.
-Both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
-We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
-
-\nobibliography{bibfile-emotion}
-
 \end{document}

### 2021-02-04 Z_manuscript_for_correction_service/itt-emotion_second_half.tex
Made files to send to correction service 5707 words and 7729 words

--- 2021-02-04 Z_manuscript_for_correction_service/itt-emotion.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \usepackage{bibentry}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
 \begin{document}
-
-\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{REDACTED}
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{REDACTED}
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
-
-\begin{abstract}
-
-  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence.
-Recent years show a steady increase in international tourists coming to Japan.
-Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought a global perspective in recent years, most tourist behavior studies were biased for the Western world.
-Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes like service or be more concerned with hard attributes like location and facilities?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists.
-The latter were delighted by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated worldwide in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
-Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.
-
-  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009}.
-There was a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-From that, the number of researchers interested in this phenomenon has been increasing as well.
-\cite[][]{sun2017}.
-With these and other multicultural tourist populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Therefore, Hotel management needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, many tourist behavior analyses have been performed with Western subjects.
-As such, a gap in knowledge and discussion existed until recent decades.
-Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to Western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples.
-These, while valid, can have their limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.
-
-  With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands automatically analyzed by machines.
-This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior and explore the data to discover factors that could have been overlooked in the past.
-To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
-We then perform a statistical extraction of the topics that concerns the customers of each population the most.
-
-\section{Research objective}\label{research_objective}
-
-  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, the hotel's location, infrastructure, and real estate nearby.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-These studies' short scope often leads to difficulties in observing cultural and language differences in a single study.
-
-  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
-
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed as to not fall behind in the competition.
-In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This hospitality culture permeates every kind of business with customer interaction in Japan.
-A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
-
-    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
-In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly.
-Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general, which can be compared to other places and business practices in the world.
-In summary, our study considers the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations of service and hospitality factors that are universal to all hotels in any country.
-
-    Therefore we pose a research question for our study:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hospitality}
-    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-
-    However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different evaluation of it.
-While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above research question:
-
-    \begin{rsq}
-    \label{rsq:hospitality_both}
-    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-So we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
-In that case, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three articles focus on U.S.A.
-culture, while our study focuses on Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done with the context of tourists from three countries staying in hotels across the world.
-The second one chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third is analyzing restaurants in Bejing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese tourists or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a Support Vector Machine.
-It is a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could expect.
-These qualities determine why, much like actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
-
-    In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but regarding infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are also considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing unchangeable physical factors by the staff or management, we consider them hard.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset.
-We counted the percentage of usage in each context.
-If it is not clear from the word or the pairing alone, we declare it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
 
@@
 
-\nobibliography{bibfile-emotion}
-
 \end{document}

### 2021-02-10 1_manuscript/itt-emotion.tex
Added first half correction from service

@@
 
-  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence.
-Recent years show a steady increase in international tourists coming to Japan.
-Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought a global perspective in recent years, most tourist behavior studies were biased for the Western world.
-Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating.
+  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence.
+In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing.
+However, most studies on tourists’ behavior are biased toward the Western world.
+Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
+To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited.
 Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes like service or be more concerned with hard attributes like location and facilities?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists.
-The latter were delighted by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
+Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities?
+We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
+Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
+We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives.
+We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior.
+We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
 
@@
 
-  Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated worldwide in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
-Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}.
+  Japan’s hospitality has been known historically to be of the highest quality.
+\textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide.
+With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}.
+Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
+However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
 Thus, it could be theorized that their satisfaction factors should be different.
 How will different cultures react and perceive hotels and their hospitality in this context?
-Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.
-
-  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009}.
-There was a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
+
+  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}.
+A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
+The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China.
+Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
 The effect of Chinese tourists on international economies is increasing.
-From that, the number of researchers interested in this phenomenon has been increasing as well.
-\cite[][]{sun2017}.
-With these and other multicultural tourist populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Therefore, Hotel management needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, many tourist behavior analyses have been performed with Western subjects.
-As such, a gap in knowledge and discussion existed until recent decades.
-Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to Western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples.
-These, while valid, can have their limitations.
+Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}.
+The tourist market is gradually becoming diverse because of multicultural tourist populations.
+Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied.
+Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
+
+  However, many tourist-behavior analyses have been performed involving Western subjects.
+As such, a gap in knowledge existed until recent decades.
+In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
+Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
+These studies, although valid, can have limitations.
 This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
+It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
+However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels.
 In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.
-
-  With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands automatically analyzed by machines.
-This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior and explore the data to discover factors that could have been overlooked in the past.
-To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
-We then perform a statistical extraction of the topics that concerns the customers of each population the most.
+Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
+
+  Owing to the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
+Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
+Data mining, machine learning, and big data technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
+These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
+
+  In this study, we attempt to evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
+We take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
+Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
+We use machine learning to automatically classify sentences in the online reviews as positive or negative opinions on the hotel.
+We then perform a statistical extraction of the topics that most concern the customers of each population.
 
@@
 
-  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings.
+  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
+We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges.
+We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
 More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, the hotel's location, infrastructure, and real estate nearby.
+We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
 In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
 
-  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-These studies' short scope often leads to difficulties in observing cultural and language differences in a single study.
-
-  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
+  We use large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
+In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
+The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
+
+  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures.
 These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
@@
 
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
+    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
+There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
+However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
-Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
+Presently, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
 Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed as to not fall behind in the competition.
-In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This hospitality culture permeates every kind of business with customer interaction in Japan.
+High standards are always followed to not fall behind in the competition.
+In Japanese businesses, including hotels, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language,'' one of the most formal of the Japanese formality syntaxes.
+They are also trained to bow differently depending on the situation, where a light bow could be used to say ``Please, allow me to guide you.'' Deep bows are used to apologize for any inconvenience the customer could have faced, followed by a very respectful apology.
+Although the word \textit{omotenashi} can be translated directly as ``hospitality,'' it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
+This hospitality culture permeates every type of business with customer interaction in Japan.
 A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
 
-    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
+    It stands to reason that this cultural aspect of hospitality would be a positive factor in influencing customer satisfaction.
 However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
-In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly.
+In this study, we cannot directly determine whether a hotel is practicing the cultural standards of \textit{omotenashi}.
 Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general, which can be compared to other places and business practices in the world.
-In summary, our study considers the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations of service and hospitality factors that are universal to all hotels in any country.
-
-    Therefore we pose a research question for our study:
+We then observe the customers' evaluations regarding service and hospitality factors in general and compare to other places and business practices in the world.
+In summary, we consider the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations on service and hospitality factors that are universal to all hotels in any country.
+
+    Therefore, we pose the following research question:
 
@@
 
-    However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different evaluation of it.
-While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above research question:
+    However, Japanese hospitality is based on the Japanese culture.
+Different cultures interacting with it could provide a different evaluation of it.
+Some might be impressed by it, whereas some might consider other factors more important to their stay in a hotel.
+This point leads us to a derivative of the aforementioned research question:
 
@@
 For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-So we must measure their differences or similarities at their common ground as well.
+Therefore, we must measure their differences or similarities at their common ground as well.
 
@@
 However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different service aspects.
+In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
 Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
@@
 
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
+    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
 However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
@@
 This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies explicitly comparing Chinese and Western tourists.
+To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
 One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
@@
 The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
+In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling.
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
@@
 
-    These last three articles focus on U.S.A.
-culture, while our study focuses on Western culture.
+    These last three studies focus on the U.S.A.
+culture, whereas our study focuses on the Western culture.
 Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done with the context of tourists from three countries staying in hotels across the world.
-The second one chose restaurant reviews from the U.S.A.
+The first study \cite[][]{FRANCESCO201924} was done within the context of tourists from three countries staying in hotels across the world.
+The second study chose restaurant reviews from the U.S.A.
 and Chinese tourists eating in three countries in Europe.
-The third is analyzing restaurants in Bejing.
+The third study analyzed restaurants in Beijing.
 
@@
 As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries.
+In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many countries.
+The general satisfaction score was noticed to be different among those countries.
 However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
@@
     % Studies are not universal.
-    Although the studies focusing only on Chinese tourists or Western tourists have a narrow view, their theoretical contributions are valuable.
+    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
 We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
@@
     % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits.
+    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits.
 A contrast is shown in Table \ref{tab:lit-rev}.
@@
 However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed.
+Since the introduction of Web 2.0, an unprecedented quantity of valuable information is posted to the Internet at a staggering speed.
 Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
@@
     % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a Support Vector Machine.
-It is a form of supervised machine learning used for binary classification.
+    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification.
 This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
@@
 However, we are using sentiment predictions for knowledge discovery in our database.
-Thus our study is a data mining experiment based on machine learning.
+Thus, our study is a data mining experiment based on machine learning.
 
@@
 Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could expect.
-These qualities determine why, much like actual mining, data mining is mostly exploratory.
+Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
+These qualities determine why, similar to actual mining, data mining is mostly exploratory.
 One can never be sure that one will find a specific something.
@@
 The exploration of large opinion datasets with these methods is essential.
-The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
-
-    In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors.
+The reason being that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
+In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
+
+    In this study, we predict that several things might occur.
+Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors.
 However, we expect that both of these options will present themselves.
@@
     We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
+The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
 We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
@@
 Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but regarding infrastructure investment.
+Others can be expensive to change, such as matters requiring construction costs, which are possible but would require significant infrastructure investment.
 On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
 For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are also considered soft attributes.
+For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are considered soft attributes.
 Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
@@
     We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing unchangeable physical factors by the staff or management, we consider them hard.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset.
-We counted the percentage of usage in each context.
-If it is not clear from the word or the pairing alone, we declare it undefined.
+If the word described unchangeable physical factors by the staff or management, we consider them hard.
+If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
+For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the percentage of usage in each context.
+If it was not clear from the word or the pairing alone, we declared it undefined.
 Then, we added the counts of these words in each category.
-A single word with no pairing is always 100\% in the category it corresponds to.
+A single word with no pairing is always deemed 100\% in the category it corresponds to.
 We add the partial percentages for each category when an adjective includes various contexts.

### 2021-02-10 Z_manuscript_for_correction_service/RONON_6_10022021-0744747/itt-emotion_first_half.tex
Added first half correction from service

--- 2021-02-10 1_manuscript/itt-emotion.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
 \begin{document}
@@
 \title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
 
@@
 
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
-Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
-Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
-We can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
-Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied with this matter.
-Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in hospitality and service does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-The previous is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
-All of these options can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
-They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-    On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
-Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
-These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
-
-    For our purposes in contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
-Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
-On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is high and influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment or outrage.
-In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any standard.
-For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
-This is where hospitality and service come into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
-There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
-However, it is still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
-However, there is still a divide between western and Japanese style hotels.
-
-  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
-However, this imposes a few difficulties that are out of the scope of this study.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment.
-Both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
-We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
-
-\begin{acknowledgements}
-
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  \medskip
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  \medskip
-
-  Conflict of interest: none
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
 \end{document}

### 2021-02-10 Z_manuscript_for_correction_service/itt-emotion_first_half_V1.tex
Added first half correction from service

--- 2021-02-04 Z_manuscript_for_correction_service/itt-emotion.tex
@@
 
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
-Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
-Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
-We can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
-Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied with this matter.
-Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in hospitality and service does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-The previous is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
-All of these options can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
-They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-    On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
-Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
-These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
-
-    For our purposes in contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
-Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
-On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is high and influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment or outrage.
-In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any standard.
-For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
-This is where hospitality and service come into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
-There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
-However, it is still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
-However, there is still a divide between western and Japanese style hotels.
-
-  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
-However, this imposes a few difficulties that are out of the scope of this study.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment.
-Both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
-We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
-
 \nobibliography{bibfile-emotion}

### 2021-02-10 Z_manuscript_for_correction_service/itt-emotion_first_half_V2_service.tex
Added first half correction from service

--- 2021-02-10 1_manuscript/itt-emotion.tex
@@
 \title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
 % Fold 1
@@
 
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
-\section{Results}\label{results}
-
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
-Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
-
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
-Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
-We can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
-
-\section{Discussion}\label{discussion}
-
-  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To this day, scholars continue to correct our historical bias towards the west.
-Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied with this matter.
-Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in hospitality and service does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-The previous is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
-All of these options can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
-They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-    On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
-Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
-These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
-
-    For our purposes in contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
-Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
-On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is high and influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment or outrage.
-In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any standard.
-For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
-This is where hospitality and service come into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
-There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
-However, it is still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
-However, there is still a divide between western and Japanese style hotels.
-
-  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
-However, this imposes a few difficulties that are out of the scope of this study.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment.
-Both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
-We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
-Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
-
-\begin{acknowledgements}
-
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  \medskip
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  \medskip
-
-  Conflict of interest: none
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
+\nobibliography{bibfile-emotion}
 

### 2021-02-10 Z_manuscript_for_correction_service/itt-emotion_second_half_V1.tex
Added first half correction from service

--- 2021-02-04 Z_manuscript_for_correction_service/itt-emotion.tex
@@
         \maketitle
-
-\begin{abstract}
-
-  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence.
-Recent years show a steady increase in international tourists coming to Japan.
-Chinese tourists, especially, have been steadily increasing.
-However, before the shift that has brought a global perspective in recent years, most tourist behavior studies were biased for the Western world.
-Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors.
-Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes like service or be more concerned with hard attributes like location and facilities?
-We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set.
-We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists.
-The latter were delighted by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Japan has been known historically for its hospitality being the highest grade.
-The spirit of Japanese hospitality is celebrated worldwide in a single Japanese word: \textit{Omotenashi}.
-With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}.
-Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.
-
-  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009}.
-There was a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}.
-From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China.
-Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-From that, the number of researchers interested in this phenomenon has been increasing as well.
-\cite[][]{sun2017}.
-With these and other multicultural tourist populations, the tourist market is more and more diverse.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied.
-Therefore, Hotel management needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, many tourist behavior analyses have been performed with Western subjects.
-As such, a gap in knowledge and discussion existed until recent decades.
-Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few that compare Asian to Western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples.
-These, while valid, can have their limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners make for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.
-
-  With the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, and their importance for sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequentially, tourism research also began to use information collected online for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data methodologies can increase the number of manageable samples per study.
-The increase can be from the hundred samples manually analyzed by researchers to the hundreds of thousands automatically analyzed by machines.
-This technology can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}.
-With this data, we can confirm existing theories about their differences in behavior and explore the data to discover factors that could have been overlooked in the past.
-To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel.
-We then perform a statistical extraction of the topics that concerns the customers of each population the most.
-
-\section{Research objective}\label{research_objective}
-
-  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, the hotel's location, infrastructure, and real estate nearby.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose.
-These studies' short scope often leads to difficulties in observing cultural and language differences in a single study.
-
-  Our study attempts to uncover the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
-
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history.
-However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''.
-Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed as to not fall behind in the competition.
-In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you".
-Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology.
-In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This hospitality culture permeates every kind of business with customer interaction in Japan.
-A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
-
-    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer.
-However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
-In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly.
-Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general, which can be compared to other places and business practices in the world.
-In summary, our study considers the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations of service and hospitality factors that are universal to all hotels in any country.
-
-    Therefore we pose a research question for our study:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hospitality}
-    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-
-    However, Japanese hospitality comes from Japanese culture.
-Different cultures interacting with it could have a different evaluation of it.
-While some might be impressed by it, some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the above research question:
-
-    \begin{rsq}
-    \label{rsq:hospitality_both}
-    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-So we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
-In that case, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three articles focus on U.S.A.
-culture, while our study focuses on Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done with the context of tourists from three countries staying in hotels across the world.
-The second one chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third is analyzing restaurants in Bejing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries.
-The general satisfaction score was noticed to be different in those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese tourists or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, a never before seen quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a Support Vector Machine.
-It is a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could expect.
-These qualities determine why, much like actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
-
-    In this study, we can predict that several things might occur.
-Our data could show satisfaction and dissatisfaction factors that are universal, and it could also find strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but regarding infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are also considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word is describing unchangeable physical factors by the staff or management, we consider them hard.
-If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top 4 adjective and noun pairings used in the entire dataset.
-We counted the percentage of usage in each context.
-If it is not clear from the word or the pairing alone, we declare it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
 

### 2021-02-10 Z_manuscript_for_correction_service/my_latexdiff_first_half.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_first_half_V1.tex itt-emotion_first_half_V2_service.tex --newversion="V2_service" --compile --view --clean 

### 2021-02-15 1_manuscript/itt-emotion.tex
Added 2nd half corrections after checking, have to checkout to look for V5 since it got deleted

@@
 
-  \subsection{Experiment results and answering research questions}
-
-    Our research questions were about two things.
-In research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we decide that the objective of this study to determine how Chinese and Western tourists interact with the \textit{omotenashi} culture influenced hospitality and service in Japan, and how are they different in their perceptions in this matter.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings in Table \ref{tab:adj_zh_pos}.
-From these observations, we can infer that, while service, cleanliness, and breakfast are praised in most hotels, location is usually placed above it in importance on the pairings.
-When we see the rest of the factors lower on the list, we see that the list is more populated with hard attributes like location and transportation availability across different price ranges.
-From the negative keyword usages in Table \ref{tab:freq_res_neg}, there are complaints about the lack of a Chinese friendly environment.
-However, most complaints are also about hard attributes such as the building's age and the distance from other convenient spots.
-Nevertheless, the most complained about aspect is the price of the hotel.
-Surprisingly, all of the price ranges have this negative keyword at the top of the list, suggesting that it is the main concern to Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    In contrast, the English-speaking customers are easily upset by any lack of cleanliness and smoke smell from cigarettes.
-Surprisingly, the cigarette smell is an issue even in the middle to high-class hotels above 30,000 yen per night.
-However, above 50,000 yen per night, this problem seems to disappear from the list of top 10 concerns.
-Old and dated buildings seem to be a concern for both populations.
-On the positive side, for all price ranges considered, English-speaking tourists value staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists consider location and transportation more often.
-
-    We also can observe some keywords that are not considered by their counterparts.
+  \subsection{Experimental results and answers to research questions}
+
+    Our research questions were related to two issues.
+Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality.
+We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}.
+These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings.
+From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
+The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
+However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.
+
+    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English .
+This word is followed by a few other keywords that are lower in the top 10 list, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability.
+From the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we deduce that  the Western tourists are also disappointed with service-related concepts.
+Therefore, both Chinese and English-speaking tourists in Japan have different priorities.
+However, both populations consider the hotel's location and transportation availability nearby (subways and trains) as secondary yet essential points to their satisfaction.
+The Chinese customers are primarily satisfied with the room quality in terms of the spaciousness and cleanliness as well as the service of breakfast.
+
+    In contrast, the English-speaking customers were easily upset by uncleanliness and smoke smell from cigarettes.
+Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
+For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
+Furthermore, the age of the buildings was a concern for both populations.
+Nevertheless, for all price ranges considered, English-speaking tourists valued staff friendliness over room quality when considering their satisfaction.
+In contrast, Chinese tourists considered location and transportation more often.
+
+    We can also observe some keywords that are not considered by their counterparts.
 For example, English-speaking customers mentioned tobacco smell in many reviews.
 However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.
-
-    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations.
-Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience.
-On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes.
-There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations.
-English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes.
-In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.
-
-    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges.
-This is, however, a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists - A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces.
-From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms.
-Other mentions are also big markets nearby or a big bed.
-We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price.
-However, we can see that they still react positively in a significant manner in cheaper hotels.
-Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel.
-We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''.
-In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''.
-They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities.
-It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes.
-It can be a cultural shock for many tourists, but this is a fundamental attraction for many.
+On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
+Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20,000–30,000 yen per night.
+
+    For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels.
+Here, we define hard attributes as those related to the hotel's physical, structural, or environmental aspects.
+These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, surroundings, view, and location convenience.
+In contrast, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
+Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
+English-speaking tourists, on the other hand, were more responsive to soft attributes, either positively or negatively.
+In the case of negative keywords, they were more concerned about the hotel's soft attributes.
+
+    One factor that both populations had in common is that, when perceiving the hotel negatively, the ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old),'' ``dated,'' ``outdated,'' or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel were surprisingly criticized across most price ranges.
+However, this is a hard attribute and is unlikely to change for most hotels.
+
+  \subsection{Chinese tourists: A big and clean space}\label{disc:zh}
+
+    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels.
+The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms.
+Other mentions included big markets nearby or a big bed.
+Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel.
+However, they still reacted positively in cheaper hotels.
+When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel.
+Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).'' In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
+On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' The word ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})'' can be used bathing in the natural source of the water in rock baths or using the natural hot spring water in artificially made tiled bath facilities.
+It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude.
+It could be a cultural shock for many tourists but a fundamental attraction for many others.
 
     However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve on.
-On the other hand, cleanliness is mostly relating to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges, and then variably ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel)'', ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall)'', ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment)'', and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities)'', among other examples.
-In negative reviews, there is a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it is an uncommon pair.
-Therefore, we can assert that cleanliness is an important soft attribute for Chinese customers and that they are mostly pleased with their expectations being met.
-
-    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them.
-However, we assert that it is an important factor.
-Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings.
-It is only slightly lower on other categories, although it is not shown on the table.
-Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists - A friendly face, and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database.
-The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them.
-Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
-The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the word does not appear directly in the top 10 list as in their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''.
-When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''.
-Since it is an adjective, we have explored the word pairings as well.
-Customers are mostly praising ``clean rooms'' and ``clean bathrooms'', while also referring to the hotel in general.
-It seems that when observing the negative keyword frequencies for English-speakers, we can find words such as ``dirty'', ``carpet'', and from the word pairings ``dirty carpet'', ``dirty room'', and ``dirty bathroom''.
-Along with complaints about off-putting smells, we can conclude that Western tourists have high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' is high on the satisfaction factors and ``uncomfortable'' high on the dissatisfaction factors.
-The words are paired with nouns like ``bed'', or ``room'', ``pillow'' or ``mattress'', generally referring to their sleep conditions in the hotel.
-    It seems that Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges, except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''.
-This price range is mostly for business hotels, where we infer users would be expecting this feature the most.
-Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.
-
-  \subsection{Tobacco, what's that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be considered a soft attribute.
-Tobacco was found not only as a standalone word ``cigarette'', but also as word pairs in Table \ref{tab:adj_en_neg}.
-We can find other related word pairs such as ``funny smell''.
-Upon manual inspection of a sample of reviews with this keyword, we found that the room was often advertised as non-smoking, yet, the smell permeated the room and curtains.
-Another common complaint was that there were no non-smoking facilities available at all in the first place.
-The smell of smoke can completely ruin some customers’ stay and give a bad impression to review writers, lowering the number of future customers.
-
-    However, in comparison, Chinese customers seem not to be bothered by this at all.
-We consulted studies involving the use of tobacco in different countries.
-Previous research states that 49 - 60\% of Chinese men (and 2.0 - 2.8\% of women) currently smoke or have smoked before.
-This was taken from a sample of 170,000 Chinese adults in 2013-2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
+Without considering rebuilding the hotel, it is not trivial to improve this attribute.
+In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
+We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples.
+In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair.
+Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers and they were mostly pleased when their expectations were fulfilled.
+
+    A key component found in Chinese customer satisfaction soft factors was the inclusion of breakfast within the hotel.
+While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking.
+In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
+The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' was also present in all price ranges, albeit at different priorities in each of them.
+For this reason, we regard it as an important factor.
+From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings.
+It is only slightly lower in other categories, although it is not depicted on the table.
+Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase the number of good reviews.
+
+  \subsection{Western tourists: A friendly face and absolutely clean}\label{disc:en}
+
+    From the satisfaction factors of English-speaking tourists, we can see that at least three words were directly related to staff friendliness and services in the general database, ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them.
+In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
+The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
+Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings.
+However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts.
+The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.
+
+    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''; because this is an adjective, we also explored the word pairings.
+Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general.
+When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.
+
+    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors and ``uncomfortable'' was high on the dissatisfaction factors.
+The words were paired with nouns such as ``bed,'' ``room,'' ``pillow,'' and ``mattress,'' when they generally referred to their sleep conditions in the hotel.
+    It seems that Western tourists were particularly sensitive about the hotels’ comfort levels and whether they reached their expectations.
+The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges except the two most expensive ones, where this keyword disappears from the top 10 list.
+
+    Albeit lower in priority, the price range of 15,000 to 20,000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.
+
+  \subsection{Tobacco, what is that smell?}\label{disc:tobacco}
+
+    A concern for Western tourists was the smell of tobacco in their room, which can be regarded as a soft attribute.
+Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
+Another common complaint was that there were no nonsmoking facilities available.
+The smell of smoke can completely ruin some customers’ stay and thus lead to bad reviews, thereby lowering the number of future customers.
+
+    In contrast, Chinese customers seemed to not be bothered by this.
+Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
+This was derived from a sample of 170,000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
 
     Japan has a polarized view on the topic of smoking.
-Despite being one of the world’s largest tobacco markets, its use has decreased in recent years.
+Although it has one of the world’s largest tobacco markets, tobacco use has decreased in recent years.
 Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only urged and not mandatory to have smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms are available to keep the smoke in an enclosed area and avoid bothering others.
-Despite this, businesses, especially those who cater to certain customers, will generally be discouraged from having smoking restrictions if they want to keep their clientele.
-If Japanese hotels want to cater to all kinds of customers, Western and Asian alike, they must provide spaces without tobacco smell.
-After all, even if it does not bother a few customers, the lack of smell would make it an appropriate space for all customers.
+However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas.
+However, many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
+Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele.
+To cater to all kinds of customers, including Western and Asian, Japanese hotels must provide spaces without tobacco smell.
+Even if the smoke does not bother a few customers, the lack of such a smell would make it an appropriate space for all customers.
 
@@
 
-    The hotel's location, closeness to the subway and public transport, and nearby shops' availability were observed to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station)'', ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location'', ``great location'', and ``great view'', as well as single keywords ``location'' and ``shopping'' for English-speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)'', ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'', ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)'', and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signal that while it was not the priority for either of them, the hotel's location is a secondary but still important point in the hotel's satisfaction.
-However, since this is a hard attribute, unchangeable to the hotel's management, it is not often considered in the literature.
-Upon inspection of examples from the data, we found that most customers were satisfied if the hotel was near to at least two other subjects: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transport system.
-The rush hour makes for a subway filled to the brim with people in suits making their commute, and trains and subway stations in Tokyo create a confusing public transport map for a visitor.
-Buses are also available, although less used than the rail systems in the big cities.
-These three are unusually affordable in price.
-Then there are the more expensive transports, such as the bullet train \textit{shinkansen} for traveling across the country, and taxis.
-Taxis in Japan are a luxury compared to other countries.
-In less developed countries, a taxi is the cheap method of transport of choice.
-In Japan, taxis are made to provide a high-quality experience with a matching price.
-This means that for tourists, subway availability and maps or GPS applications and a plan to travel the city are of utmost necessity.
-
-    Japanese convenience stores, on the other hand, are also famous worldwide.
-Japanese convenience stores are a haven for the traveler in need.
-It offers anything, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, international ATMs, among other things.
-If some trouble occurred, or a traveler forgot to pack a particular item, it is almost sure that they can find it.
-
-    Therefore, considering that both transport systems and nearby shops are points of interest for Chinese and Western tourists, Japanese hotels have to carefully choose their location from the moment they are constructed.
-While not a top priority, this is a universal factor for both customer groups, and it can be an instant way to generate positive reviews.
+    The hotel's location, closeness to the subway and public transportation, and availability of nearby shops proved to be of importance to both Chinese and English-speaking tourists.
+In positive word pairings in Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location,'' ``great location,'' and ``great view'' as well as single keywords ``location'' and ``shopping'' for English speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic),'' ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping),'' ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway),'' and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
+All of these keywords and their location in each population's priorities across the price ranges signify that the hotel's location was a secondary but still important point for their satisfaction.
+However, since this is a hard attribute, it is not often considered in the literature.
+By examining examples from the data, we recognized that most customers were satisfied if the hotel was near at least two of the following facilities: subway, train, and convenience stores.
+
+    Japan is a country with a peculiar public transportation system.
+During rush hour, the subway is crowded with commuters, and trains and subway stations create a confusing public transportation map for a visitor in Tokyo.
+Buses are also available, albeit less used than rail systems in metropolitan cities.
+These three means of transportation are usually affordable in price.
+There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis.
+The latter is a luxury in Japan compared to other countries, especially in less developed countries, where this is a low-cost choice.
+In Japan, taxis provide a high-quality experience with a matching price.
+Therefore, subway availability and maps or GPS applications as well as a plan to travel the city are of utmost necessity for tourists.
+
+    Japanese convenience stores are also famous worldwide, because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs.
+If some trouble occurs, or a traveler forgot to pack a particular item, it is mostly certain that they can find it.
+
+    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, the location of a Japanese hotel must be carefully chosen prior to construction.
+Although not a top priority, this is a universal factor for both customer groups and is conducive to generate positive reviews.
 
@@
 
-  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
+  In this section, we explore the possible interactions with Japanese hospitality, the differences between perceptions of Chinese and Western tourists as well as the possible causes, variations in perceptions across different price ranges, and the implications for the industry.
+We also discuss the differences between the hotel's hard and soft attributes and their contributions to customers' satisfaction.
 
@@
 
-    To this day, scholars continue to correct our historical bias towards the west.
-Studies have determined that different cultural backgrounds lead to different expectations, which influences tourists' satisfaction.
-Meaning, tourists of a particular culture will have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment.
-The spirit of hospitality and service, \textit{omotenashi}, excels and is considered the highest standard across the world.
-Can such an environment affect different cultures equally?
-Or is it only attractive to certain cultures?
-Our study brings light to these questions.
-
-    Our results indicate that out of the two, Western tourists are the most satisfied with soft attributes, such as friendly and helpful staff in Japan.
-As explained earlier in this paper, Japan is famous for its customer service all over the world.
-Respectful language and bowing are not exclusive to high priced hotels or businesses.
-These can even be found in convenience stores.
-The level of hospitality in even the cheapest of convenience stores is starkly different from Westerner experiences.
-While it could be a culture shock to some, it is mostly seen positively.
-After all, the Japanese staff respectfully treats all customers.
-However, for some customers, this could be the best way they have been treated until that moment.
-Now, in higher priced hotels, the adjectives used to praise the service go from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff'', ``wonderful experience'', ``excellent service'', and ``excellent staff''.
-We can also see that \cite{kozak2002} and \cite{shanka2004} have also found that hospitality and staff friendliness is a vital determinant in Western tourists' satisfaction.
-
-    However, we can see from the negative English keywords that a big part of the dissatisfaction with Japanese hotels stems from a lack of hygiene and room cleanliness.
-Although Chinese customers only had positive keywords about cleanliness, English-speaking customers have found many places unacceptable to their standards.
-This is particularly true at hotels below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette stench and general dirtiness.
-\cite{kozak2002} also found that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
+    To date, scholars have been correcting our historical bias towards the West.
+Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction.
+In other words, tourists of a particular culture have different leading satisfaction factors across different destinations.
+However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, excels and is considered to be of the highest standard across the world.
+Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.
+
+    Our results indicate that Western tourists are more satisfied with soft attributes, such as friendly and helpful staff in Japan, than Chinese tourists.
+As explained earlier in this paper, Japan is well known for its customer service.
+Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
+The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture.
+Although it could be a cultural shock to some, it is mostly approved.
+The Japanese staff treats all customers respectfully, and this might be unforeseen by some customers.
+In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
+
+    However, the negative English keywords indicate that a large part of the dissatisfaction with Japanese hotels stemmed from a lack of hygiene and room cleanliness.
+Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50,000 yen per night.
+The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette smell and lack of general hygiene.
+\cite{kozak2002} also proved that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
 However, in the previous literature, this was linked merely to satisfaction.
-In comparison, our research uncovered that words relating to cleanliness are mostly linked to dissatisfaction.
-Westerners could be said to have a high standard of room cleanliness when compared to their Chinese counterparts.
-
-    According to previous research, we can see that Western tourists are already inclined to appreciate hospitality for their satisfaction.
+In contrast, our research revealed that words related to cleanliness were mostly linked to dissatisfaction.
+We could assert that Westerners had a high standard of room cleanliness compared to their Chinese counterparts.
+
+    According to previous research, Western tourists are already inclined to appreciate hospitality for their satisfaction.
 When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, we can see from our results that Chinese tourists had less focus on hospitality, staff, or service and were more concerned with room quality.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and for ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'', we can see that they do praise staff, service and breakfast.
-Observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we know that Chinese customers are satisfied more with hard attributes, compared to the Western tourists who seem to be meeting more than their expectations.
-
-    It could be that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction that stems from this is less than if it was expected.
-On the other hand, we have the phenomenon of a ``nice surprise'': When an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two phenomenons.
-The ``nice surprise'' fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a high enough need for the Chinese population, resulting in less satisfaction.
-For greater satisfaction, the existence of a need being met is necessary.
-However, the word ``not bad'' is at the top of the list at most price ranges, and one of the uses is related to service.
-Thus, we cannot say that they are not satisfied with this matter.
-Rather, they hold other factors at a higher priority, considering the keyword frequency is higher for other pairings.
-
-    Another possibility presents itself when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high standard hospitality environment.
-Japan is known worldwide for their hospitality, but they are also known historically to be monolingual and have a relatively large language barrier \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly taking shape, Chinese accommodations can be lagging.
-Chinese language pamphlets, Chinese texts on instructions for the hotel room, and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup), or just the treatment towards Chinese people could be examples.
-It is natural to be dissatisfied since traveling in a strange land without knowing the language can be a daunting experience.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-It seems like this is a problem that is not singular to Japan.
+In contrast, according to our results, Chinese tourists were more concerned about room quality rather than hospitality, staff, or service.
+However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great),'' we can see that they praise staff, service, and breakfast.
+By observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we discover that Chinese customers were more satisfied with hard attributes compared to Western tourists, who seemed to be meeting more than their expectations.
+
+    It could be considered that Chinese culture does not expect high-level service initially.
+When an expectation that is not held is met, the satisfaction derived is less than that if it was expected.
+In contrast, some tourists report a ``nice surprise'': when an unknown need is unexpectedly met, there is more satisfaction.
+It is necessary to note the difference between these two reactions.
+The ``nice surprise'' reaction fulfills a need unexpectedly.
+Perhaps the hospitality grade in Japan does not fulfill a need high enough for the Chinese population, thereby resulting in less satisfaction.
+For greater satisfaction, a need must be met.
+However, the word ``not bad'' is at the top of the list in most price ranges, and one of the uses is related to service.
+Thus, we cannot conclude that they were not satisfied with the service.
+Instead, they held other factors at a higher priority; thus, the keyword frequency was higher for other pairings.
+
+    Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors.
+Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high-standard hospitality environment.
+This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
+While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging.
+Chinese language pamphlets as well as Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
+channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples.
+Dissatisfaction in a foreign country is natural if the language native to that region is not known.
+\cite{ryan2001} also found that communication difficulty was one of the main reasons that Chinese customers would state for not visiting again.
+However, this issue is not exclusive to Japan.
 
     Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study brought us closer to the answer.
-On the one hand, there is a possibility that Chinese customers did have high-grade hospitality and did not get equally satisfied with Westerners.
-In that case, it appears that the difference stems from a psychological source.
-Expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-On the other hand, there is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear from our results which of these could be the case.
-One thing is clear for hotel managers, however.
-Competing in hospitality and service does include language services, especially in the international tourism industry.
-Better multilingual support can only improve that already high standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, this is an endeavor that truly can bring benefits to their investment.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or have a translator application readily available with staff trained in interacting through an electronic translator.
+This study attempted to determine the answer.
+It is possible that Chinese customers had high-grade hospitality and were equally satisfied with Westerners.
+In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
+There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
+
+    The case representing the higher possibility is unclear from our results.
+However, competing in hospitality and service includes language services, especially in the international tourism industry.
+Better multilingual support can only improve the hospitality standard in Japan.
+Considering that most of the tourists in Japan come from other countries in Asia, multilingual support is beneficial.
+Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
 
@@
 
-    As we stated in section \ref{theory_satisfaction}, previous research is focused mostly on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
+    \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
+
+    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction.
+Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.,][]{shanka2004,choi2001}.
 However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
-Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
-In contrast, only 20\% are soft factors.
-The rates are similar for most price ranges, excepting the highest-priced hotels, where 35\% of the keywords are undefined.
-However, the soft attributes are still similar at 18\%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'', ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), plus the adjective pairs relating to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' which are at the top in most price ranges as well.
-Chinese tourists could expect spaciousness and cleanliness when coming to Japan.
-That expectation could be caused by reputation, previous experiences, or cultural backgrounds.
+Examples of hard attributes include the hotel's location relative to public transportation and shops, language immersion of the country, noise pollution, or weather.
+Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
+
+    Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors.
+The rates are similar for most price ranges except the highest-priced hotels, where 35 \% of the keywords are undefined.
+However, the soft attributes are still similar at 18 \%.
+However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
+Chinese tourists may expect spaciousness and cleanliness when coming to Japan.
+The expectation may be due to reputation, previous experiences, or cultural backgrounds.
 Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, so there can be differences between South Korea and China in room size perception.
-However, an interesting point appears.
-It could be that a different room size perception affects the satisfaction of Chinese tourists in contrast with Westerners.
-Westerners only start placing a priority on praising room size as the price of the hotel goes up.
+Although the study subjects are German and South Korean, \cite{Saulton2017} presents the results as differences influenced by Asian and Western cultures.
+We argue that one country is not representative of others’ cultures, and thus, there can be differences between South Korea and China in room size perception.
+However, a different room size perception may affect the satisfaction of Chinese tourists in contrast to Westerners because Westerners prioritize room size as the price of the hotel room rises.
 We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These other few factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword is present in hotels priced at more than 20,000 yen per night.
-
-    In comparison, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48\% in all price ranges, the highest being 65\% in the 15,000 to 20,000 yen per night price range.
-This price range corresponds to affordable business hotels, for example.
+These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
+This keyword was found for hotels priced at more than 20,000 yen per night.
+
+    In contrast, English speakers are mostly satisfied with the hotel's soft attributes.
+Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
 English-speaking customers also have soft attributes at the top of their list.
 The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers both Chinese and Western tourists’ satisfaction, a hotel can improve to attract more customers in the future.
-If it was the other way around, and the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels would have to compete solely on their location.
-
-    For both customer groups, the main reason for dissatisfaction is pricing, which can be interpreted as a concern about value for money.
-However, it is interesting to note that while English-speaking customers complain about price with a lower rank in lower-priced hotels.
-In contrast, the Chinese customers consistently have ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as a top or second-most concern across all price ranges.
-A paper studying Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this is less of a cultural attribute in Japanese hotels and has more to do with the pricing of hotels overall.
-The tourists coming to Japan could be both experienced travelers or first-time travelers.
-However, the fact is that their expectation of the price for hotels was lower than what they found in Japan.
-In general, Japan is an expensive place to visit, impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3,000 to 6,000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5,000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can be half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management.
-The previous is true for all price ranges.
-Of course, the improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding.
-All of these options can be costly.
-However, this paper provides a good guideline for which factors to consider first and which ones will be best suited to each customer group.
-Hotels can use the price range categorization in order to choose the appropriate strategy as well.
-However, once the hotel's location and construction are set for Chinese customers, not much else can be done to satisfy them further.
-As mentioned before, Chinese language availability is another soft attribute that can be improved with staff and training investment.
-
-    On the other hand, Western tourists are all around dissatisfied with mostly soft attributes.
-They show this by having a low of 35\% in the highest price range where undefined factors are the majority and 78\% at most in the price range from 30,000 to 50,000 yen per night in a hotel.
-The room for improvement for Western tourists is more extensive than their Chinese counterparts.
-As such, it presents a bigger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotel lodging.
-    On the other hand, their Asian counterparts only spend 25\% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, it seems like we can recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment that could increase returns many times over.
-
-    However, the opposite argument could also be made that Chinese customers provide a more significant number of customers, even though they tend to spend less on lodging.
+If one considers the satisfaction of both Chinese and Western tourists, a hotel can improve its services to attract more customers in the future.
+Otherwise, if the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels should be built considering the location.
+
+    For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
+However, English-speaking customers complained about price with a lower rank in lower-priced hotels.
+In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
+A study on Chinese tourists found that they had this concern \cite[][]{truong2009}.
+However, our results indicate that this concern is less related to the cultural attribute in Japanese hotels and more related with the pricing of hotels overall.
+Tourists coming to Japan could be either experienced or first-time travelers.
+However, their expectation of the price for hotels was lower than the actual prices in Japan.
+In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking.
+Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night.
+Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night.
+For comparison, hotels in the USA with a similar quality can charge half the price.
+
+    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management; this is true for all price ranges.
+The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, all of these considerations can be costly.
+However, this paper provides a useful guideline about the factors to be prioritized and the factors that would be the most suitable for each customer group.
+Hotels can also use the price range categorization to choose the appropriate strategy.
+However, once the hotel's location and construction are set for Chinese customers, only a few changes can be made to satisfy them further.
+As mentioned previously, Chinese language availability is another soft attribute that can be improved with staff and training investment.
+
+    Western tourists are mainly dissatisfied with soft attributes.
+This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel.
+Improvement scope for Western tourists is more extensive than that for their Chinese counterparts.
+As such, it presents a larger investment opportunity.
+As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, since they spend more than 45 \% of their budget on hotel lodging.
+    Asian tourists spend only 25 \% of their budget on hotels \cite[][]{choi2000}.
+With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
+Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment, which could increase returns by several times.
+
+    However, Chinese customers are more in number, even though they tend to spend less on lodging.
 Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes, leaving language barrier-breaking as one of the few strategies to accomplish this.
+However, as mentioned before, they tend to focus more on hard attributes; thus, breaking the language barrier breaking is one of the few strategies to accomplish this.
 
     The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preference of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-That study states that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}.
+This premise also plays a role in the differentiation between the preferences of hard or soft attributes.
+
+    In \cite{donthu1998cultural}, subjects from 10 different countries were compared with respect to their expectations of service quality and analyzed based on Hofstede's typology of culture \cite[][]{hofstede1984culture}.
+The previous study states that, although culture has no specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
+These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism–-collectivism}, \textit{masculinity–femininity}, and \textit{long-term-–short-term orientation}.
 In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
@@
 low uncertainty avoidance countries).
-However, Hofstede's typology has received criticism from academics, particularly the fifth dimension that Hofstede proposed, which was added afterward with the alternate name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
+However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}.
+Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism as well as considering a difficult dimension to measure \cite[][]{fang2003critique}.
+Other models, such as the GLOBE model, also consider some of Hofstede's dimensions and replace them with others, making a total of nine dimensions \cite[][]{house1999cultural}.
+The \textit{masculinity–-femininity} dimension, for example, is proposed to be instead of two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
 This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Gender stereotypes such as these have also been the subject of critique for Hofstede's model\cite[][]{jeknic2014gender}.
-Our study agrees with these critiques and, therefore, will avoid considering these for our discussion.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied before \cite[][]{gao2017chinese}.
-These backgrounds and the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that these differences in expectations exist \cite[][]{armstrong1997importance}.
-
-    For our purposes in contrasting Western vs.
+Such gender stereotypes have also been the subject of critique on Hofstede's model\cite[][]{jeknic2014gender}.
+We agree with these critiques and thus avoid considering such stereotypes in our discussion.
+
+    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese}.
+These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations.
+Regardless of the cause, however, measures in the past have proven that such differences exist \cite[][]{armstrong1997importance}.
+
+    For our purposes of contrasting Western vs.
 Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-Perhaps the cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
+The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
 Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history gives less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, one could argue that a Chinese cultural attribute emphasizes the environment and the place one is in towards satisfaction, rather than the way one is treated.
-According to previous research, Chinese tourists are collectivist, while Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could result in more of their expectations and priorities be related to how one is treated in social circumstances, rather than the environment one is in.
-According to \cite{donthu1998cultural}, highly individualistic customers have a higher expectation of empathy and assurance from the provider than collectivist customers.
-Empathy and assurance from the provider are aspects of service, a soft attribute of a hotel.
+However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.
+
+    Nevertheless, a Chinese cultural attribute emphasizes that the environment and the location  affect satisfaction, rather than the treatment.
+According to previous research, Chinese tourists are collectivists, whereas Westerners are individualists \cite[][]{kim2000}.
+A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment.
+According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivistic customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
 
     Among other dimensions in both models, we can consider uncertainty avoidance.
-High uncertainty avoidance customers would carefully plan their travel and therefore have higher expectations towards service.
-On the other hand, lower uncertainty avoidance customers would have certain room for risk in their decisions, and therefore face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not so clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, this dimension might not be the one causing the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Another factor, power distance, was also different when measured by Hofstede's method compared to the GLOBAL method, so we decided against making this comparison.
+Customers of high uncertainty avoidance carefully plan their travel and thus have higher expectations towards service.
+In contrast, customers of lower uncertainty avoidance do not take risks in their decisions and thus face less disappointment with different expectations.
+However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology.
+While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard–-soft attribute satisfaction between Chinese and Western cultures.
+Differences in another factor, power distance, were also noted when measuring by Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
 
@@
 
-    In previous sections of this paper, we have mentioned the differences reflected in hotel price ranges.
-Nevertheless, it is interesting to discuss this further.
-The most visible change in satisfaction factors across differently priced hotels is the change in voice to describe their satisfaction with the same topics.
-We can know this by observing the adjective + noun pairs and finding pairs with different adjectives for the same nouns.
+    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
+The most visible change of satisfaction factors across differently priced hotels is the change in voice when describing their satisfaction with the same topics.
+We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
 For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for more highly-priced hotels are ``wonderful'' and ``excellent''.
-In Chinese, the change goes from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)''.
-We can infer that the level of satisfaction is high and influences how customers write their reviews.
-However, when we look at the negative keywords, the change is from ``annoying'' or ``worst'', to ``disappointing''.
-Here we can see how expectations influence satisfaction and dissatisfaction in different ways.
+In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
+Regarding the negative keywords, however, the change ranges from ``annoying'' or ``worst'' to ``disappointing.'' Here, we can determine how expectations influence satisfaction and dissatisfaction in different ways.
 
     In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the lack of meeting expectations would cause dissatisfaction.
-In the cases above, we can infer that a customer that pays more for a higher class of experience has higher expectations.
+Therefore, the failure of meeting expectations would cause dissatisfaction.
+In the aforementioned cases, we can infer that a customer that pays more for a higher-class experience has higher expectations.
 This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment or outrage.
-In the case of English-speaking customers in the 30,000 to 50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels react even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging their reactions.
-We argue that these are two different kinds of interactions with expectations.
-We can observe logical expectations.
-Customers set a standard in their mind that the service must not fall below or be disappointed — for example, a customer being disappointed with dirty rooms or cigarette smell.
-
-    In contrast, we can observe emotional expectations, where customers have a vague idea of having a positive experience.
-However, they do not measure it against any standard.
-For example, having a pleasant customer service experience or being treated hospitably by the staff at a high-class hotel.
-Regardless of their knowledge beforehand of the service to be provided, positive emotions give them a perception of exceeded expectations and high satisfaction.
-This is where hospitality and service come into play and enhances the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their change in satisfaction factors to differently priced hotels.
-For example, we can observe that the Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists only mention it as a top keyword in the 20,000 to 30,000 yen price range.
-It is common knowledge in Japan that Chinese tourists coming to Japan with the express intention of shopping are common.
+As such, any lack of cleanliness can lead to disappointment.
+In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
+However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
+In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
+We argue that these are two different kinds of expectations: logical and emotional.
+In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
+
+    In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
+For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
+Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
+Thus, hospitality and service enhance the experience of the customers.
+
+    There are interesting differences between Chinese and English-speaking tourists in their satisfaction factors to differently priced hotels.
+For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
+In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
+It is widely known in Japan that many Chinese tourists visit Japan for shopping.
 \cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, medicine, among other more traditional \textit{souvenir} items, such as objects representative of the culture or places they visit \cite{japan2014consumption}.
-There is an understanding that tourists choose to shop in Japan has more to do with the quality of the items than their relation to the tourist attractions.
-Our results suggest that Western tourists are engaging more in tourist attractions in comparison with shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only after it concerns hotels of 15,000 yen or more, and it rises in its ranking the more expensive the hotel is.
-In contrast, Chinese customers have this keyword as their top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, while Western customers are more concerned with hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors stay mostly constant for each culture's customers.
+The study shows that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
+Furthermore, tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
+Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities.
+Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15 000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
+In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
+Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
+
+    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors remain constant for each culture's customers.
 For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly stays part of the top 10 keywords, except for the most expensive one, where other keywords take that place in the ranking.
-However, it is still high on the list.
+Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
 Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transport and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within at most a 13\% margin of error per attribute, often being lower.
-This suggests that culturally the customers have a particular bias to consider some attributes more than others.
+As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
+While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
+This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
 
@@
 
-    Our study presents two important conclusions: one about hospitality and cultural differences, and another about managerial decisions towards two different populations.
-As a whole, Chinese tourists are not showing the most satisfaction towards hospitality and service factors.
-Instead, they focus on the hard attributes of a hotel.
-Either they do not get as much satisfaction from hospitality as Western tourists or feel that basic language and communication needs are not being met, so they receive a lesser impression.
-On the other hand, Western tourists are elated with Japanese hospitality, preferring soft attributes to hard-set ones.
-The other conclusion is that managerial decisions will mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion can satisfy more Chinese customers.
-Japan is recently seeing an increase in Chinese students as well as Western students of universities.
+    Our study reached two important conclusions: one about hospitality and cultural differences and another about managerial decisions towards two different populations.
+Overall, Chinese tourists did not attach much importance to hospitality and service factors.
+Instead, they focused on the hard attributes of a hotel.
+In particular, they were not satisfied with hospitality as much as Western tourists were; otherwise, they felt that basic language and communication needs were not met, thereby they were not much satisfied.
+Western tourists were highly satisfied with Japanese hospitality and preferred soft attributes to hard ones.
+The other conclusion is that managerial decisions could mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion could satisfy Chinese customers to a greater extent.
+Recently, Japan has been facing an increase in Chinese students as well as students of Western universities.
 Hiring students as part-time workers could increase the language services of a hotel.
@@
 It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which can be improved upon managerially for better reviews.
+Western tourists were also observed to have high comfort standards, which could be managerially improved for better reviews.
 Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
 However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs can satisfy both customer types.
+Our results suggest that satisfying cleanliness needs could satisfy both customer types.
 A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, so a hotel manager can consider which analysis suits their hotel the most.
-
-    While not manageable after a hotel has finished its construction, hard attributes are essential to consider for managers.
-As previously stated, transport systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers have to consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction after public plans to make new subway lines are made.
-
-    It is left to the managers to consider their business model for the next strategy.
-One option could be attracting more Chinese customers in number with their observed low budgeting.
-Another could be attracting more high budget Western customers is on par with their business model.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even though the price per night would increase.
-On the other hand, hotels might be considered costly by Chinese customers wherever such an investment is made.
+Our results are also divided by price ranges, thereby a hotel manager could consider which analysis suits their hotel the most.
+
+    Albeit not manageable after a hotel is completely constructed, hard attributes should be considered by managers.
+As stated before, transportation systems and nearby shops are points of interest for both Chinese and Western tourists.
+Japanese hotel managers should consider the location and surroundings before the hotel is constructed.
+A suggestion could be to purchase land and start the construction at places where public plans for new subway lines have already been made.
+
+    The managers must consider their business model for implementing the next strategy.
+One option could be attracting more Chinese customers with their observed low budgeting.
+Another could be attracting more big-budget Western customers.
+For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even for an increased price per night.
+On the other hand, hotels might be deemed costly by Chinese customers wherever such an investment is made.
 
@@
 
-  This paper is not without its limitations.
-We analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
+  In this study, we analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
 Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, the study is limited in that it only analyzes the words directly related to each keyword and does not follow the upstream or downstream path down further connections.
-This means that if the words are used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking'', we would extract ``good food'' and ``lacking food'', but do not consider the fact that both occurred in the same sentence.
+However, our study is limited because it analyzed solely the words directly related to each keyword and did not follow the upstream or downstream path down to further connections.
+This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
+For example, in the sentence ``The room is good, but the food is lacking,'' we extracted ``good room'' and ``lacking food'' but did not consider the fact that both occurred in the same sentence.
 
   This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a western-style five-star resort and a high-end Japanese-style \textit{ryokan}.
-Services offered in these hotels are very high quality, although very different.
-However, most of our database is focused on the middle range priced hotels, which is comparably less varied in service.
-However, there is still a divide between western and Japanese style hotels.
-
-  An essential aspect of this study is that we focus on the satisfaction and dissatisfaction towards expectations of individual aspects of the hotels.
-This gives us insight into which factors can focus on by hotel managers in applying this knowledge.
-However, our study was limited in that the overall satisfaction of each customer was not measured.
-This could be done by rating the volume of text used to describe satisfaction factors against the text volume used for dissatisfaction.
-However, this imposes a few difficulties that are out of the scope of this study.
-
-  Another limitation is that a large portion of the Asian tourists coming to Japan is Taiwanese and Korean.
-We could not analyze these populations because our team members do not know those languages.
-Aside from that, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate further into this topic.
-We plan to extend our data to research for different trends for different regions of Japan and different kinds of hotels and between customers traveling alone or in groups, for fun or for work.
-Another point of interest in this study's future is to use word clusters with similar meanings instead of single words.
+However, in the same price range, for example, the highest one, we can find both a Western-style five-star resort and a high-end Japanese style \textit{ryokan}.
+Services offered in these hotels are of high quality, albeit very different.
+However, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
+However, there is still a division between Western and Japanese style hotels, which constitutes another limitation of our study.
+
+  An essential aspect of this study is that we focused on the satisfaction and dissatisfaction towards the expectations of the individual aspects of the hotels.
+This gave us insight into the factors that can be considered by hotel managers.
+However, the overall satisfaction of each customer was not measured.
+This measurement can be performed by rating the volume of text used to describe satisfaction and dissatisfaction factors.
+However, this would impose a few difficulties, which are out of the scope of this study.
+
+  Another limitation is that a large portion of Asian tourists coming to Japan are Taiwanese and Korean.
+We could not analyze these populations because our team members did not know those languages.
+Moreover, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
+
+  In future work, we plan to investigate these topics further.
+We plan to extend our data to research of different trends and regions of Japan, different kinds of hotels, and customers traveling alone or in groups, whether for fun or for work.
+Another point of interest in this study's future work is to use word clusters with similar meanings instead of single words.
 
@@
 We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns, as well as single words.
-We divided this data by sentiment and hotel price range, considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists had the most satisfaction with staff behavior, cleanliness, and other attributes relating to the hotel's services and hospitality.
-However, we found that Chinese customers had other concerns than hospitality when studying their satisfaction, more inclined to praise the room, location, or hotel's convenience.
-We found that both cultures have a different reaction to this hospitality environment.
-Both cultures have a different way of reacting to different prices.
-From this, we discussed two possible theories on why Chinese tourists respond differently to Westerners in this environment of \textit{omotenashi}.
-One theory is that while they are being treated well and react positively, the environment is not compatible with them because of language or culture barriers, which lessens their experience.
-The second possible theory is that they react differently to hospitality since they do not have the same expectations to be satisfied in the same way.
-We theorize that a lack of expectations could result in lessened satisfaction, even if the same service is presented.
-On the other hand, even when they hold high expectations in a highly-priced hotel, Western tourists show that Japanese hospitality exceeds their expectations, judging by their vocabulary for expressing their satisfaction.
-We consider that Western tourists are more reactive to hospitality and service factors than their Chinese counterparts.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, referring to a hotel's hard and soft attributes.
+We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns as well as single words.
+We divided these data by sentiment and hotel price range by considering the most expensive room for one night.
+
+  In the context of Japanese hospitality, we found that Western tourists were most satisfied with staff behavior, cleanliness, and other attributes related to the hotel's services and hospitality.
+However, we found that Chinese customers had concerns other than hospitality when studying their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
+We found that the two cultures had different reactions to the hospitality environment and the prices.
+Thus, we discussed two possible theories on the reasons why Chinese tourists responded differently from Westerners in the environment of \textit{omotenashi}.
+One theory is that, although they were treated well and thus reacted positively, the environment was not compatible with them because of language or culture barriers, which deteriorated their experience.
+The second possible theory is that they reacted to hospitality differently since they did not have the same expectations.
+We theorized that a lack of expectations could result in lessened satisfaction, even if the same service was present.
+On the other hand, even when they held high expectations in a high-priced hotel, Japanese hospitality exceeded Western tourists’ expectations, judging by their vocabulary for expressing their satisfaction.
+We considered that Western tourists were more reactive to hospitality and service factors than their Chinese counterparts.
+
+  Lastly, we measured the satisfaction and dissatisfaction factors, that is, a hotel's hard and soft attributes.
 Soft attributes can be changed via management and staff by an improvement in services.
-On the other hand, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
-We found that for satisfaction, Western tourists favor soft attributes.
-In contrast, Chinese tourists are more interested in the hard attributes of hotels, consistently across price ranges.
-For dissatisfaction, Western tourists are also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction comes evenly from both hard and soft attributes.
-
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate less percentage of their budget to hotels but are more abundant in number.
-They are less satisfied with soft attributes but have an identifiable method of improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach we discussed was focusing on the cleanliness and comfort that Western tourists expect and making the hotels tobacco-free.
-We favor ``long-haul'' Western tourists who spend almost half of their budget on hotels with this strategy.
-While Westerners are less in number than Chinese tourists, it could prove to have more substantial returns.
+In contrast, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
+We found that, for satisfaction, Western tourists favored soft attributes in contrast to Chinese tourists, who were more interested in the hard attributes of hotels across all the price ranges consistently.
+For dissatisfaction, Western tourists were also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
+In contrast, Chinese tourists' dissatisfaction derived from both hard and soft attributes evenly.
+
+  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate lower percentage of their budget to hotels but are more abundant in number.
+They are less satisfied with soft attributes but have an identifiable method for improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
+Another approach was focused on the cleanliness, comfort, and tobacco-free space expected by Western tourists.
+``Long-haul'' Western tourists, who spend almost half of their budget on hotels with this strategy, were favored.
+Although Westerners are less in number than Chinese tourists, it could be proven that they have more substantial returns.
 This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
 This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences and shared attributes.
+We can observe their stark differences as well as shared attributes.
 

### 2021-02-15 Z_manuscript_for_correction_service/RONON_7_11022021-1253449/itt-emotion_second_half.tex
Added 2nd half corrections after checking, have to checkout to look for V5 since it got deleted

--- 2021-02-15 1_manuscript/itt-emotion.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
 \begin{document}
 
-\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
-
-\begin{abstract}
-
-  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence.
-In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing.
-However, most studies on tourists’ behavior are biased toward the Western world.
-Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
-To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities?
-We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide.
-With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}.
-Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-
-  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}.
-A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China.
-Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}.
-The tourist market is gradually becoming diverse because of multicultural tourist populations.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, many tourist-behavior analyses have been performed involving Western subjects.
-As such, a gap in knowledge existed until recent decades.
-In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
-
-  Owing to the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
-These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we attempt to evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
-We take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
-Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
-We use machine learning to automatically classify sentences in the online reviews as positive or negative opinions on the hotel.
-We then perform a statistical extraction of the topics that most concern the customers of each population.
-
-\section{Research objective}\label{research_objective}
-
-  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-  We use large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
-The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
-
-  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
-
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Presently, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed to not fall behind in the competition.
-In Japanese businesses, including hotels, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language,'' one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow differently depending on the situation, where a light bow could be used to say ``Please, allow me to guide you.'' Deep bows are used to apologize for any inconvenience the customer could have faced, followed by a very respectful apology.
-Although the word \textit{omotenashi} can be translated directly as ``hospitality,'' it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This hospitality culture permeates every type of business with customer interaction in Japan.
-A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
-
-    It stands to reason that this cultural aspect of hospitality would be a positive factor in influencing customer satisfaction.
-However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
-In this study, we cannot directly determine whether a hotel is practicing the cultural standards of \textit{omotenashi}.
-Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general and compare to other places and business practices in the world.
-In summary, we consider the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations on service and hospitality factors that are universal to all hotels in any country.
-
-    Therefore, we pose the following research question:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hospitality}
-    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-
-    However, Japanese hospitality is based on the Japanese culture.
-Different cultures interacting with it could provide a different evaluation of it.
-Some might be impressed by it, whereas some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the aforementioned research question:
-
-    \begin{rsq}
-    \label{rsq:hospitality_both}
-    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-Therefore, we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
-In that case, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three studies focus on the U.S.A.
-culture, whereas our study focuses on the Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done within the context of tourists from three countries staying in hotels across the world.
-The second study chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third study analyzed restaurants in Beijing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many countries.
-The general satisfaction score was noticed to be different among those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[htp]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, an unprecedented quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus, our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
-These qualities determine why, similar to actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
-
-    In this study, we predict that several things might occur.
-Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
-\section{Methodology}\label{method}
-
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management.
-Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
-Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a data point, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but would require significant infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word described unchangeable physical factors by the staff or management, we consider them hard.
-If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the percentage of usage in each context.
-If it was not clear from the word or the pairing alone, we declared it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always deemed 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
 \section{Results}\label{results}
@@
     Our research questions were related to two issues.
-Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality.
+Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of the culture.
 We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}.
-These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings.
+These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location was usually rated higher in importance.
 From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
-The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
+The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a friendly Chinese environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
 However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.
@@
 However, both populations consider the hotel's location and transportation availability nearby (subways and trains) as secondary yet essential points to their satisfaction.
-The Chinese customers are primarily satisfied with the room quality in terms of the spaciousness and cleanliness as well as the service of breakfast.
+The Chinese customers are primarily satisfied with the room quality in trms of the spaciousness and cleanliness as well as the service of breakfast.
 
     In contrast, the English-speaking customers were easily upset by uncleanliness and smoke smell from cigarettes.
-Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
-For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
+Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30 000 yen per night.
+For hotels with rooms priced above 50 000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
 Furthermore, the age of the buildings was a concern for both populations.
@@
 However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20,000–30,000 yen per night.
+On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15 000 yen to 200 000 yen per night.
+Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20 000–30 000 yen per night.
 
@@
 In contrast, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
-Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
+Our study discovered that Chinese tourists attached more importance to the hotel's hard attributes, with a tendency of 53 \%, albeit more uniform than the positive evaluations.
 English-speaking tourists, on the other hand, were more responsive to soft attributes, either positively or negatively.
@@
 Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).'' In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' The word ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})'' can be used bathing in the natural source of the water in rock baths or using the natural hot spring water in artificially made tiled bath facilities.
-It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude.
+On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' Therefore, visitors can opt for the former or the latter.
+It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths naked.
 It could be a cultural shock for many tourists but a fundamental attraction for many others.
@@
 
-    Albeit lower in priority, the price range of 15,000 to 20,000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.
+    Albeit lower in priority, the price range of 15 000 to 20 000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.
 
@@
     A concern for Western tourists was the smell of tobacco in their room, which can be regarded as a soft attribute.
-Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
+Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as nonsmoking; however, the smell permeated the room and curtains.
 Another common complaint was that there were no nonsmoking facilities available.
@@
 
-    In contrast, Chinese customers seemed to not be bothered by this.
-Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
-This was derived from a sample of 170,000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
+    In contrast, Chinese customers seemed unbothered in such a case.
+Previous research has stated that 49–-60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
+This was derived from a sample of 170 000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
 
@@
 The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture.
-Although it could be a cultural shock to some, it is mostly approved.
+Although it could be a cultural shock to some of them, it is mostly approved.
 The Japanese staff treats all customers respectfully, and this might be unforeseen by some customers.
@@
     However, the negative English keywords indicate that a large part of the dissatisfaction with Japanese hotels stemmed from a lack of hygiene and room cleanliness.
-Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50,000 yen per night.
+Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50 000 yen per night.
 The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette smell and lack of general hygiene.
@@
 Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high-standard hospitality environment.
-This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
+This could be because Japan is  ia monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
 While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging.
@@
 In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
-There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
+There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural differences between Japan and China.
 
@@
 Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
 
@@
 Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, \cite{Saulton2017} presents the results as differences influenced by Asian and Western cultures.
+Although the subjects in (study) are German and South Korean, the study presents the results as differences influenced by Asian and Western cultures.
 We argue that one country is not representative of others’ cultures, and thus, there can be differences between South Korea and China in room size perception.
@@
 These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword was found for hotels priced at more than 20,000 yen per night.
+This keyword was found for hotels priced at more than 20 000 yen per night.
 
     In contrast, English speakers are mostly satisfied with the hotel's soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
+Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15 000 to 20 000 yen per night, which corresponds to, for example, affordable business hotels.
 English-speaking customers also have soft attributes at the top of their list.
@@
 Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night.
+Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12 000 yen per night.
 For comparison, hotels in the USA with a similar quality can charge half the price.
@@
     Western tourists are mainly dissatisfied with soft attributes.
-This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel.
+This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30 000 to 50 000 yen per night in a hotel.
 Improvement scope for Western tourists is more extensive than that for their Chinese counterparts.
@@
 As such, any lack of cleanliness can lead to disappointment.
-In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
+In the case of English-speaking customers in the 30 000-–50 000 yen per night price range, cigarette smell is particularly disappointing.
 However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
@@
 For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
+In contrast, English-speaking tourists mention it only as a top keyword in the 20 000–-30 000 yen price range.
 It is widely known in Japan that many Chinese tourists visit Japan for shopping.
@@
 This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking,'' we extracted ``good room'' and ``lacking food'' but did not consider the fact that both occurred in the same sentence.
+For example, in the sentence ``The room is good, but the food is lacking,'' we extracted ``good food'' and ``lacking food'' but did not consider the fact that both occurred in the same sentence.
 
@@
 
-\begin{acknowledgements}
-
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  \medskip
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  \medskip
-
-  Conflict of interest: none
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
 \end{document}

### 2021-02-15 Z_manuscript_for_correction_service/itt-emotion_second_half_V2_service.tex
Added 2nd half corrections after checking, have to checkout to look for V5 since it got deleted

--- 2021-02-15 Z_manuscript_for_correction_service/RONON_7_11022021-1253449/itt-emotion_second_half.tex
@@
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
+% Fold 1
+  % Fold 2
+    % Fold 3
+      % Fold 4
+        %\documentclass[twocolumn]{svjour3}          % twocolumn
+        %
+        \smartqed  % flush right qed marks, e.g. at end of proof
+
+        % For the ORCID icon
+        \usepackage{scalerel}
+        \usepackage{tikz}
+        \usetikzlibrary{svg.path}
+
+        \definecolor{orcidlogocol}{HTML}{A6CE39}
+        \tikzset{
+          orcidlogo/.pic={
+            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
+            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
+                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
+                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
+          }
+        }
+
+        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
+        \begin{tikzpicture}[yscale=-1,transform shape]
+        \pic{orcidlogo};
+        \end{tikzpicture}
+        }{|}}}}
+
+        \usepackage{lineno, hyperref}
+        \usepackage{array, pbox}
+        \usepackage{mathtools}
+        \usepackage{caption}
+        \usepackage{subcaption}
+        \usepackage{graphicx}
+
+        % To use chinese characters
+        \usepackage{CJKutf8}
+
+        % To add an appendix page
+        \usepackage[page, title]{appendix}
+
+        % To insert commas into large numbers automatically
+        \usepackage{siunitx}
+
+        % To add research questions
+        \usepackage{ntheorem}
+        \theoremseparator{:}
+        \newtheorem{rsq}{Research Question}
+
+        % To add subrsq theorems
+        \makeatletter
+        \newcounter{subrsq} 
+        \let\savedc@rsq\c@rsq
+        \newenvironment{subrsq}
+         {%
+          \setcounter{subrsq}{0}%
+          \stepcounter{rsq}%
+          \edef\saved@rsq{\thersq}% Save the current value of rsq
+          \let\c@rsq\c@subrsq     % Now rsq is subrsq
+          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
+         }
+         {}
+        \newcommand{\normrsq}{%
+          \let\c@rsq\savedc@rsq % revert to the old one
+          \renewcommand\thersq{\arabic{rsq}}%
+        } 
+        \makeatother
+
+        % To add the envelope symbol in Corresponding Author using % \Letter
+        \usepackage{marvosym}
+
+        % to add superscripts to mark the institute of authors
+        % patch \maketitle:
+        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
+        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
+
+        % For table formatting
+        \usepackage{multirow}
+        \usepackage[normalem]{ulem}
+        \useunder{\uline}{\ul}{}
+
+        % For landscape tables
+        \usepackage{lscape}
+
+        \usepackage{bibentry}
+
+        \modulolinenumbers[5]
+
+        \journalname{Information Technology \& Tourism}
+
+        \bibliographystyle{spbasic}
+
 \begin{document}
+
+\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
+% Fold 1
+  % Fold 2
+    % Fold 3
+      % Fold 4
+        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
+
+        \author{REDACTED}
+
+        \authorrunning{E. Alemán Carreón et al.}
+
+        \institute{REDACTED}
+
+        \date{Received: date / Accepted: date}
+        % The correct dates will be entered by the editor
+
+        \maketitle
 
@@
 
+\nobibliography{bibfile-emotion}
+
 \end{document}

### 2021-02-15 Z_manuscript_for_correction_service/itt-emotion_second_half_V3_service_corrected.tex
Added 2nd half corrections after checking, have to checkout to look for V5 since it got deleted

--- 2021-02-15 1_manuscript/itt-emotion.tex
@@
         \maketitle
-
-\begin{abstract}
-
-  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence.
-In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing.
-However, most studies on tourists’ behavior are biased toward the Western world.
-Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
-To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities?
-We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide.
-With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}.
-Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-
-  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}.
-A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China.
-Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}.
-The tourist market is gradually becoming diverse because of multicultural tourist populations.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  However, many tourist-behavior analyses have been performed involving Western subjects.
-As such, a gap in knowledge existed until recent decades.
-In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
-
-  Owing to the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
-These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we attempt to evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
-We take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
-Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
-We use machine learning to automatically classify sentences in the online reviews as positive or negative opinions on the hotel.
-We then perform a statistical extraction of the topics that most concern the customers of each population.
-
-\section{Research objective}\label{research_objective}
-
-  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges.
-We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-  We use large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
-The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
-
-  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
-  \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
-
-    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
-The practice of high standards in hospitality has survived throughout the years.
-Presently, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones.
-Manners, service, and respect towards the customer are taught to workers in their training.
-High standards are always followed to not fall behind in the competition.
-In Japanese businesses, including hotels, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language,'' one of the most formal of the Japanese formality syntaxes.
-They are also trained to bow differently depending on the situation, where a light bow could be used to say ``Please, allow me to guide you.'' Deep bows are used to apologize for any inconvenience the customer could have faced, followed by a very respectful apology.
-Although the word \textit{omotenashi} can be translated directly as ``hospitality,'' it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}.
-This hospitality culture permeates every type of business with customer interaction in Japan.
-A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.
-
-    It stands to reason that this cultural aspect of hospitality would be a positive factor in influencing customer satisfaction.
-However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
-In this study, we cannot directly determine whether a hotel is practicing the cultural standards of \textit{omotenashi}.
-Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general and compare to other places and business practices in the world.
-In summary, we consider the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations on service and hospitality factors that are universal to all hotels in any country.
-
-    Therefore, we pose the following research question:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hospitality}
-    To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-
-    However, Japanese hospitality is based on the Japanese culture.
-Different cultures interacting with it could provide a different evaluation of it.
-Some might be impressed by it, whereas some might consider other factors more important to their stay in a hotel.
-This point leads us to a derivative of the aforementioned research question:
-
-    \begin{rsq}
-    \label{rsq:hospitality_both}
-    Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-Therefore, we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
-In that case, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three studies focus on the U.S.A.
-culture, whereas our study focuses on the Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done within the context of tourists from three countries staying in hotels across the world.
-The second study chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third study analyzed restaurants in Beijing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many countries.
-The general satisfaction score was noticed to be different among those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[htp]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, an unprecedented quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus, our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
-These qualities determine why, similar to actual mining, data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason being that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
-
-    In this study, we predict that several things might occur.
-Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
-\section{Methodology}\label{method}
-
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management.
-Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
-
-    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
-Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a data point, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but would require significant infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word described unchangeable physical factors by the staff or management, we consider them hard.
-If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the percentage of usage in each context.
-If it was not clear from the word or the pairing alone, we declared it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always deemed 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
 

### 2021-02-15 Z_manuscript_for_correction_service/my_latexdiff_second_half.sh

@@ -1,0 +1,3 @@
+# ../my_latexdiff.sh itt-emotion_second_half_V1.tex itt-emotion_second_half_V2_service.tex --newversion="V2_service" --compile --view --clean 
+
+../my_latexdiff.sh itt-emotion_second_half_V1.tex itt-emotion_second_half_V3_service_corrected.tex --newversion="V3_service_corrected" --compile --view --clean 

### 2021-02-15 2_revisions/V5_ITT_minor_revision/0_manuscript_blind/itt-emotion_blind.tex
Added V5 in revisions and latexdiff of newer version

--- 2020-11-20 1_manuscript/itt-emotion.tex
@@
       % Fold 4
-        \titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}
-
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
+        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
+
+        \author{REDACTED}
+
+        \authorrunning{REDACTED}
+
+        \institute{REDACTED}
 
@@
 Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.][]{shanka2004,choi2001}.
-However, hard attributes, such as the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather, are not usually analyzed in satisfaction studies.
+However, hard attributes are not usually analyzed in satisfaction studies.
+Examples of hard attributes include the hotel's location relative to public transport and shops, language immersion of the country, noise pollution, or weather.
 Because our study left the satisfaction factors to be decided statistically via customers’ online reviews, we can see the importance of those hard or soft attributes in their priorities.
 
-    From Figure \ref{fig:hard_soft_zh}, we can see that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
+    Figure \ref{fig:hard_soft_zh} shows that in regards to Chinese customer satisfaction, in general, 68\% of the top 10 keywords are hard factors.
 In contrast, only 20\% are soft factors.

### 2021-02-15 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V4.tex itt-emotion.tex --newversion="5" --compile --view --clean 
+../my_latexdiff.sh itt-emotion_V5.tex itt-emotion.tex --newversion="6" --compile --view --clean 

### 2021-02-15 2_revisions/V5_ITT_minor_revision/1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_V4.tex itt-emotion.tex --newversion="5" --compile --view --clean 

### 2021-02-24 1_manuscript/itt-emotion_V6-1.tex
Renamed a few files

--- 2021-02-15 1_manuscript/itt-emotion.tex
@@
 
-  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence.
-In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing.
-However, most studies on tourists’ behavior are biased toward the Western world.
   Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
-To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities?
-We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
+We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if these cultures value service over other factors.
+We compared soft attributes, such as service, with hard attributes, such as location and facilities.
+We examined the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
 Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
@@
   Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide.
-With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}.
+\textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}.
 Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
@@
 Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
+Different cultures could perceive hotels and their hospitality through a different lens.
 
@@
 Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}.
+The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
 The tourist market is gradually becoming diverse because of multicultural tourist populations.
@@
 In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
+The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
 These studies, although valid, can have limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
+This gap in research creates a need for large scale cross-cultural studies for the increasing Asian and Western tourist populations.
 It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
@@
 
-  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges.
+  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels, across several price ranges, using text-mining techniques.
 We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
@@
 
-  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
 \section{Theoretical background and hypothesis development}\label{theory_hypothesis}
@@
     The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
+There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century, while other scholars found that it originates in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
@@
 Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures.
+Western and Chinese customers then have very different backgrounds and cultures.
 These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-These expectations will be there from the moment that they choose the hotel throughout their stay.
 In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
@@
     However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit.
-In that case, they will be satisfied with this matter.
+For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
 However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
@@
 
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
+    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
 However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
@@
     In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
+Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}.
 This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
 To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
+One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
+Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
 Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
+Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.
 
     One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
+Western analyses is that they were performed before 2000 and that they are not Chinese specific.
+Meanwhile, the current Chinese economic boom is increasing the influx of tourists of this nation.
 The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling.
+In turn, if we follow the definition of satisfaction in \cite{hunt1975}, the change in expectations could have influenced their satisfaction factors when traveling.
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
@@
 Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
+In this environment, customers could either hold their satisfaction to this hospitality regardless of their culture, or value other factors more depending on their cultural differences.
 Our study measures this at a large scale across different hotels in Japan.
@@
 This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
+This study analyzes the satisfaction and dissatisfaction factors cross-culturally and compares them with the existing literature.
 
@@
 The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures?
 Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
@@
 A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion.
+With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, or a critical one.
 This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
@@
     % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
+    The algorithm used for sentiment analysis in our study is called a Support Vector Machine (SVM), a form of supervised machine learning used for binary classification.
 Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
+Learning machines can be supervised, as in our study, where the algorithm has manually labeled training data to detect patterns in it and use them to  establish a method for classifying other unlabeled data automatically.
+Machine learning can also be unsupervised, where there is no pre-labeled data.
 In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
@@
 
-    In this study, we predict that several things might occur.
-Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
 \section{Methodology}\label{method}
@@
 We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
+These positive and negative keywords allow us to perform an emotional classification of the reviews in large quantities, saving time and resources for the researchers.
 We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
@@
 Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management.
-Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.
 
@@
 
-    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
+    An SVC is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
 Each dimension is a feature of the data in this space.
@@
 
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
+    Our study used the SVC classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
 Each training sentence is a data point, a row in the vector \(x\).
@@
 
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
+    During the SVC learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
 These changes to the weight vector are greater for features close to the separating hyperplane.
@@
     Our research questions were related to two issues.
-Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality.
+Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture.
 We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}.
-These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings.
-From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
+These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location was more important when observing the pairings.
+Including the factors lower on the list, we observed that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
 The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
@@
 
-    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English .
-This word is followed by a few other keywords that are lower in the top 10 list, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability.
+    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English.
+This word is followed by a few other keywords, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability.
 From the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we deduce that the Western tourists are also disappointed with service-related concepts.
@@
 
-  \subsection{Tobacco, what is that smell?}\label{disc:tobacco}
+  \subsection{Tobacco, an unpleasant smell in the room}\label{disc:tobacco}
 

### 2021-02-25 1_manuscript/itt-emotion_V5_no_commands.tex
Made V6-2, -1800 words

--- 2021-02-15 2_revisions/V5_ITT_minor_revision/0_manuscript_blind/itt-emotion_blind.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
-\begin{document}
-
-\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{REDACTED}
-
-        \authorrunning{REDACTED}
-
-        \institute{REDACTED}
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
-
 \begin{abstract}
@@
 
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hospitality}
     To what degree are Chinese and Western tourists satisfied with Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
 
@@
 
-    \begin{rsq}
-    \label{rsq:hospitality_both}
     Do Western and Chinese tourists have a different evaluation of Japanese hospitality factors such as staff behavior or service?
-    \end{rsq}
-    \end{subrsq}
 
@@
 
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
     To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
+
     How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
 
@@
 
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
   \subsection{Data collection}\label{datacollection}
@@
 
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
   \subsection{Text processing}\label{textprocessing}
@@
 
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
     A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
@@
 In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
 
@@
 We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
 
@@
 
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        % }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
     Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
@@
 
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
     We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
@@
 
-  REDACTED
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
-\end{document}
+  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
+We would like to show gratitude to Mr.
+Liangyuan Zhou, Ms.
+Min Fan, and Ms.
+Eerdengqiqige for this.
+
+  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
+
+  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
+
+  Conflict of interest: none

### 2021-02-25 1_manuscript/itt-emotion_V6-1.tex
Made V6-2, -1800 words

@@
 Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15 000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
+Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
 In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.

### 2021-02-25 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,8 @@
-../my_latexdiff.sh itt-emotion_V5.tex itt-emotion.tex --newversion="6" --compile --view --clean 
+# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion.tex --newversion="6" --compile --view --clean 
+
+# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-1.tex --compile --view --clean
+# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-1.tex --compile --view --clean
+
+../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-2.tex --compile --clean
+../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-2.tex --compile --clean
+../my_latexdiff.sh itt-emotion_V6-1.tex itt-emotion_V6-2.tex --compile --clean

### 2021-02-26 1_manuscript/itt-emotion_V6-3.tex
V6-3 -1950 words, before teacher checks

--- 2021-02-25 1_manuscript/itt-emotion_V6-1.tex
@@
         \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
+                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
                     \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
                 \and
                     \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
                     \hspace*{1em} \email{mendoza.espana@gmail.com}
@@
                     \hspace*{1em} Hirofumi Nonaka \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
                     \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
@@
                     \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
                     \hspace*{1em} \email{hiraoka@sun.ac.jp}
@@
 
-  Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
-We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if these cultures value service over other factors.
+  Previous research in satisfaction has shown that different cultural backgrounds give rise to different expectations and thus different satisfaction factors.
+We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if services are valued over other factors in different price ranges.
 We compared soft attributes, such as service, with hard attributes, such as location and facilities.
-We examined the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior.
+  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors and then used them to classify a more extensive data set with an SVM.
+We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
+  We found that Chinese tourists are less concerned with hospitality and more with room quality, whereas, Western tourists are delighted more by the staff behavior.
 We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
@@
 Thus, it could be theorized that their satisfaction factors should be different.
-Different cultures could perceive hotels and their hospitality through a different lens.
 
@@
 A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China.
+The tourist population was 86.14\% Asian, and 25.63\% was from China.
 Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
@@
 
-  However, many tourist-behavior analyses have been performed involving Western subjects.
+  However, many tourist-behavior analyses have been performed only involving Western subjects.
 As such, a gap in knowledge existed until recent decades.
@@
 The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations.
-This gap in research creates a need for large scale cross-cultural studies for the increasing Asian and Western tourist populations.
+These studies, although valid, can have limitations, namely, the scale and sampling.
+In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
+The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
+This creates a need for large scale cross-cultural studies for the increasing Asian and Western tourist populations.
 It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
@@
 Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining, machine learning, and big data technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
+Data mining and machine learning technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
 These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
 
-  In this study, we attempt to evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
-We take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
+  In this study, we evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
+We take advantage of the wide availability of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
 Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
@@
 
-  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels, across several price ranges, using text-mining techniques.
+  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels, across several price ranges.
 We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
@@
 
-  We use large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
-The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
-
 \section{Theoretical background and hypothesis development}\label{theory_hypothesis}
@@
     The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century, while other scholars found that it originates in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
+There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century, while others found that it originates in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
@@
     \begin{landscape}
-    \begin{table}[htp]
+    \begin{table}[p]
       \centering
@@
 
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
+  We extracted a large number of text reviews from the site \textit{Ctrip}, with mostly mainland Chinese users, and the travel site \textit{TripAdvisor}.
+We then determined the most commonly used words that relate to positive and negative opinions in a review.
 We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform an emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
+These positive and negative keywords allow us to train an optimized Support Vector Classifier (SVC) to perform a binary emotional classification of the reviews in large quantities, saving time and resources for the researchers.
+We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and the nouns they refer to.
+We split the dataset into price ranges to observe the differences in keyword usage between lower-class and higher-class hotels.
 We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
@@
 
-    In the data collection stage for Chinese reviews in \textit{Ctrip}, a total of \num[group-separator={,}]{5774} review pages of hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
+    In the \textit{Ctrip} data collection, reviews from a total of \num[group-separator={,}]{5774} hotels in Japan were collected.
+From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese.
 Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
@@
 
-    However, we needed to make the data and comparisons we draw from each of these datasets fair.
-For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
+    However, to make the data comparisons fair, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
+We also filtered them to be in the same date range.
 In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
-Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
-After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}.
+We extracted the lowest and highest price possible for one night as well.
+The difference in pricing can be from better room settings, such as double or twin rooms or suites, depending on the hotel.
+Regardless of the reason, we chose the highest-priced room since it can be an indirect indicator of the hotel's class.
+After filtering, the datasets contained \num[group-separator={,}]{557} hotels in common.
 The overlapping date range for reviews was from July 2014 to July 2017.
 Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.
-
-    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve.
+
+    The price for a night in these hotels ranges from cheap capsule hotels at 2000 yen per night to high-end hotels 188,000 yen a night at the far ends of the bell curve.
 Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
@@
 
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
+    We needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
 For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
 In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
+In the case of English texts, however, only using spaces is not enough to correctly collect concepts.
 The English language is full of variations and conjugations of words depending on the context and tense.
 Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
+For this purpose, we used the \textit{gensim} library for the English texts.
 
@@
 In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the entire database and extracting instances of a few determined dependency codes.
+We did that by parsing the database and extracting instances of a few determined dependency codes.
 One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
@@
     The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVM.
+Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVC \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
+The selected SVC keywords would then clearly represent the user driving factors leading to positive and negative emotions.
+We also performed experiments to choose the best value of the parameter C used in the SVC.
 C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives.
-However, depending on the data, it can increase false negatives.
+Low values of C give some freedom of error, which minimizes false positives but can also increase false negatives.
 Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
+SVC performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
 Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
@@
       \label{tab:svm_f1_zh}
-      % \resizebox{\textwidth}{!}{%
+      \resizebox{0.65\textwidth}{!}{%
       \begin{tabular}{|l|l|l|l|l|}
@@
         %
-        % }
+        }
     \end{table}
@@
       \label{tab:svm_f1_en}
-      % \resizebox{\textwidth}{!}{%
+      \resizebox{0.65\textwidth}{!}{%
       \begin{tabular}{|l|l|l|l|l|}
@@
 
-    Our study used the SVC classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
+    Our study used a linear kernel for the SVC, defined by the formula (\ref{eq:svm1}) below.
 Each training sentence is a data point, a row in the vector \(x\).
@@
 
-    During the SVC learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
+    During the SVC learning algorithm, each data point classified incorrectly alters the weight vector to correctly classify new data.
 These changes to the weight vector are greater for features close to the separating hyperplane.
@@
 
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
+    We observed the top 10 satisfaction and dissatisfaction keywords with the highest frequencies emotionally positive and negative statements to study.
 The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
@@
 Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}.
-These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location was more important when observing the pairings.
-Including the factors lower on the list, we observed that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
-The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
+
+    Observing the top-ranking positive keywords in Chinese reviews, as shown in in Tables \ref{tab:freq_res_pos} and Table \ref{tab:adj_zh_pos}, it was revealed that, while service, cleanliness, and breakfast were praised in most hotels, location was more important when observing the pairings, and hard attributes were abundant lower on the lists.
+The negative keywords in Table \ref{tab:freq_res_neg} indicate that a lack of a Chinese-friendly environment was perceived, although there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
 However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.
 
-    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English.
-This word is followed by a few other keywords, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability.
-From the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we deduce that the Western tourists are also disappointed with service-related concepts.
-Therefore, both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transportation availability nearby (subways and trains) as secondary yet essential points to their satisfaction.
-The Chinese customers are primarily satisfied with the room quality in terms of the spaciousness and cleanliness as well as the service of breakfast.
-
-    In contrast, the English-speaking customers were easily upset by uncleanliness and smoke smell from cigarettes.
-Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
-For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
-Furthermore, the age of the buildings was a concern for both populations.
-Nevertheless, for all price ranges considered, English-speaking tourists valued staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists considered location and transportation more often.
+    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
+This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
+When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
+When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
 
@@
 
+    With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
+However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
+The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
+
     For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels.
-Here, we define hard attributes as those related to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, surroundings, view, and location convenience.
-In contrast, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
 Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
@@
 
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve this attribute.
+    However, the size of the room or the bed is a hard attribute, of which a change is not trivial.
 In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
@@
 In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' was also present in all price ranges, albeit at different priorities in each of them.
+This keyword was also present in all price ranges, albeit at different priorities in each of them.
 For this reason, we regard it as an important factor.
@@
 
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words were directly related to staff friendliness and services in the general database, ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them.
+    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them.
 In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
@@
 
-    A concern for Western tourists was the smell of tobacco in their room, which can be regarded as a soft attribute.
+    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes.
+Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
+For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
 Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
@@
 However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
+Many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
 Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele.
@@
 There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis.
-The latter is a luxury in Japan compared to other countries, especially in less developed countries, where this is a low-cost choice.
+The latter is a luxury in Japan compared to other countries.
 In Japan, taxis provide a high-quality experience with a matching price.
-Therefore, subway availability and maps or GPS applications as well as a plan to travel the city are of utmost necessity for tourists.
+Therefore, for people under a budget, subway availability and maps or GPS applications as well as a plan to travel the city are of utmost necessity for tourists, using taxis only as a last resort.
 
@@
 
-    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, the location of a Japanese hotel must be carefully chosen prior to construction.
-Although not a top priority, this is a universal factor for both customer groups and is conducive to generate positive reviews.
+    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, and perhaps offering guide maps and information about these as an appeal point could result in greater satisfaction.
 
 \section{Discussion}\label{discussion}
-
-  In this section, we explore the possible interactions with Japanese hospitality, the differences between perceptions of Chinese and Western tourists as well as the possible causes, variations in perceptions across different price ranges, and the implications for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and their contributions to customers' satisfaction.
 
@@
 In other words, tourists of a particular culture have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, excels and is considered to be of the highest standard across the world.
+However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world.
 Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.
 
-    Our results indicate that Western tourists are more satisfied with soft attributes, such as friendly and helpful staff in Japan, than Chinese tourists.
+    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists.
 As explained earlier in this paper, Japan is well known for its customer service.
 Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
-The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture.
-Although it could be a cultural shock to some, it is mostly approved.
-The Japanese staff treats all customers respectfully, and this might be unforeseen by some customers.
+The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture, and this might be unforeseen by some customers.
 In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
@@
 
-    The case representing the higher possibility is unclear from our results.
+    It is unclear which of these two is most likely from our results.
 However, competing in hospitality and service includes language services, especially in the international tourism industry.
@@
 However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transportation and shops, language immersion of the country, noise pollution, or weather.
+It is important to consider both kinds of attributes.
+If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future.
+Otherwise, if the satisfaction was related more with hard attributes overall, hotels should be built considering the location while minimizing other costs.
 Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
@@
 The expectation may be due to reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, \cite{Saulton2017} presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, and thus, there can be differences between South Korea and China in room size perception.
-However, a different room size perception may affect the satisfaction of Chinese tourists in contrast to Westerners because Westerners prioritize room size as the price of the hotel room rises.
 We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
@@
 Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers the satisfaction of both Chinese and Western tourists, a hotel can improve its services to attract more customers in the future.
-Otherwise, if the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels should be built considering the location.
+The exception to this is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
 
     For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
-However, English-speaking customers complained about price with a lower rank in lower-priced hotels.
+However, English-speaking customers complained about price less in lower-priced hotels.
 In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
@@
 
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management; this is true for all price ranges.
-The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, all of these considerations can be costly.
-However, this paper provides a useful guideline about the factors to be prioritized and the factors that would be the most suitable for each customer group.
-Hotels can also use the price range categorization to choose the appropriate strategy.
-However, once the hotel's location and construction are set for Chinese customers, only a few changes can be made to satisfy them further.
-As mentioned previously, Chinese language availability is another soft attribute that can be improved with staff and training investment.
+    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could improved; this is true for all price ranges.
+The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, these considerations can be costly.
+However, once the hotel's location and construction are set, only a few changes can be made to satisfy Chinese customers further.
+As mentioned previously, Chinese language availability is a soft attribute that can be improved with staff and training investment.
 
@@
 A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment.
-According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivistic customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
+According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
 
@@
     In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change of satisfaction factors across differently priced hotels is the change in voice when describing their satisfaction with the same topics.
+The most visible change across differently priced hotels is the change in voice when describing satisfaction.
 We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
@@
 In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``worst'' to ``disappointing.'' Here, we can determine how expectations influence satisfaction and dissatisfaction in different ways.
+Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
 
     In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the failure of meeting expectations would cause dissatisfaction.
-In the aforementioned cases, we can infer that a customer that pays more for a higher-class experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment.
+Conversely, the failure of meeting expectations causes dissatisfaction.
+We can assume that a customer that pays more for a higher-class experience has higher expectations.
+For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
 In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
@@
 In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
+
     We argue that these are two different kinds of expectations: logical and emotional.
 In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
-
 In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
@@
 
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction factors to differently priced hotels.
+    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
 For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
@@
 It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
-Furthermore, tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
+Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
 Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities.
@@
 
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors remain constant for each culture's customers.
+    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
 For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
@@
 Our results suggest that satisfying cleanliness needs could satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
+We suggest to invest in making the facilities tobacco-free.
 Our results are also divided by price ranges, thereby a hotel manager could consider which analysis suits their hotel the most.
-
-    Albeit not manageable after a hotel is completely constructed, hard attributes should be considered by managers.
-As stated before, transportation systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers should consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction at places where public plans for new subway lines have already been made.
+Hard attributes are difficult to change, however, improvements in service can be made to accompany these attributes.
+For example, transportation guides for foreigners that might not know the area could increase satisfaction.
 
@@
 
-  In this study, we analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, our study is limited because it analyzed solely the words directly related to each keyword and did not follow the upstream or downstream path down to further connections.
+  In this study, we analyzed keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
+Following that, we attempted to understand the context of these words by using a dependency parser and observing the related nouns.
+However, a limitation is that it analyzed solely the words directly related to each keyword and did not search further connections.
 This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
@@
 Services offered in these hotels are of high quality, albeit very different.
-However, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
-However, there is still a division between Western and Japanese style hotels, which constitutes another limitation of our study.
+Nevertheless, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
 
@@
 This gave us insight into the factors that can be considered by hotel managers.
-However, the overall satisfaction of each customer was not measured.
-This measurement can be performed by rating the volume of text used to describe satisfaction and dissatisfaction factors.
-However, this would impose a few difficulties, which are out of the scope of this study.
-
-  Another limitation is that a large portion of Asian tourists coming to Japan are Taiwanese and Korean.
-We could not analyze these populations because our team members did not know those languages.
-Moreover, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
+However, the overall satisfaction of each customer was not measured, since it would require methods that are out of the scope of this paper.
+Another limitation is that further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
 
@@
 
-  In this study, our objective was to analyze the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-To answer our research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, we extracted keywords from their online reviews uploaded to the portal sites \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
+  In this study, we analyzed the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
+We extracted keywords from their online reviews on \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
 We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract commonly found pairs of adjectives and nouns as well as single words.
-We divided these data by sentiment and hotel price range by considering the most expensive room for one night.
-
-  In the context of Japanese hospitality, we found that Western tourists were most satisfied with staff behavior, cleanliness, and other attributes related to the hotel's services and hospitality.
-However, we found that Chinese customers had concerns other than hospitality when studying their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
+We then used dependency parsing and part of speech tagging to extract common pairs of adjectives and nouns as well as single words.
+We divided these data by sentiment and hotel price range (most expensive room/night).
+
+  We found that Western tourists were most satisfied with staff behavior, cleanliness, and other soft attributes.
+However, Chinese customers had other concerns for their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
 We found that the two cultures had different reactions to the hospitality environment and the prices.
-Thus, we discussed two possible theories on the reasons why Chinese tourists responded differently from Westerners in the environment of \textit{omotenashi}.
-One theory is that, although they were treated well and thus reacted positively, the environment was not compatible with them because of language or culture barriers, which deteriorated their experience.
+Thus, we discussed two possible theories on why Chinese tourists responded differently from Westerners in the environment of \textit{omotenashi}.
+One theory is that, although they were treated well, their experience was deteriorated by language or culture barriers.
 The second possible theory is that they reacted to hospitality differently since they did not have the same expectations.
-We theorized that a lack of expectations could result in lessened satisfaction, even if the same service was present.
+We theorized that a lack of expectations could result in lessened satisfaction than that to the same service if expected.
 On the other hand, even when they held high expectations in a high-priced hotel, Japanese hospitality exceeded Western tourists’ expectations, judging by their vocabulary for expressing their satisfaction.
-We considered that Western tourists were more reactive to hospitality and service factors than their Chinese counterparts.
+We considered that Western tourists were more reactive to hospitality and service factors Chinese tourists.
 
   Lastly, we measured the satisfaction and dissatisfaction factors, that is, a hotel's hard and soft attributes.
-Soft attributes can be changed via management and staff by an improvement in services.
-In contrast, hard attributes are physical and impractical elements to change, such as the size of a room that has already been constructed, the location of a hotel, closeness to convenient spots, or elements out of the control of the hotel managers.
+Hard attributes are physical and environmental elements, and as such, are impractical elements to change.
+In contrast, soft attributes can be changed via management and staff by an improvement in services or amenities.
 We found that, for satisfaction, Western tourists favored soft attributes in contrast to Chinese tourists, who were more interested in the hard attributes of hotels across all the price ranges consistently.
@@
 
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate lower percentage of their budget to hotels but are more abundant in number.
+  One approach for hotel managers is to work to satisfy Chinese tourists more, who dedicate lower percentage of their budget to hotels but are more numerous.
 They are less satisfied with soft attributes but have an identifiable method for improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
@@
 This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-This paper provides results and discussion that can be utilized as a guideline for managerial decisions when considering Chinese and Western tourists in Japan.
-We can observe their stark differences as well as shared attributes.
 
@@
 
-  \medskip
-
   Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
 
-  \medskip
-
   Conflict of interest: none

### 2021-02-26 1_manuscript/itt-emotion_V6-4.tex
V6-4 -2165 words, changed layout of discussion

--- 2021-02-26 1_manuscript/itt-emotion_V6-3.tex
@@
 
-  Previous research in satisfaction has shown that different cultural backgrounds give rise to different expectations and thus different satisfaction factors.
-We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if services are valued over other factors in different price ranges.
-We compared soft attributes, such as service, with hard attributes, such as location and facilities.
+  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for analyzing expectations and satisfaction factors in Chinese and Western cultures, our cross-cultural study contributes to both the theoretical understanding of  satisfaction and suggests practical applications and strategies for hotel managers.
+  We compared soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
   We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors and then used them to classify a more extensive data set with an SVM.
 We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
-  We found that Chinese tourists are less concerned with hospitality and more with room quality, whereas, Western tourists are delighted more by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
+  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior.
+We also found that the lack of a Chinese-friendly environment for Chinese customers, and the smell of cigarettes for Western ones can be disappointing factors of their stay.
 
@@
 Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
+However, studies focusing on only the behavior of this subset of tourists are the majority.
 To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
@@
 Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel.
-However, they still reacted positively in cheaper hotels.
 When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel.
-Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).'' In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' The word ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})'' can be used bathing in the natural source of the water in rock baths or using the natural hot spring water in artificially made tiled bath facilities.
+Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).''
+
+    In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
+On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' However, they are interchangeable if natural hot spring water is used in artificially made tiled bath facilities.
 It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude.
@@
 
-    However, the size of the room or the bed is a hard attribute, of which a change is not trivial.
+    Chinese customers are satisfied with the size of the room or the bed, however it is not trivial to change this.
 In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
@@
 
-    A key component found in Chinese customer satisfaction soft factors was the inclusion of breakfast within the hotel.
+    A key soft satisfaction factor was the inclusion of breakfast within the hotel.
 While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-This keyword was also present in all price ranges, albeit at different priorities in each of them.
+In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' referring to the hotel commodities, was frequently used in positive texts compared to other food-related words across all price ranges, albeit at different priorities in each of them.
 For this reason, we regard it as an important factor.
@@
 
-    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them.
-In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
+    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the highest ranked of these three, ranking second for satisfied customers across most price ranges and only third in one of them.
 The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
@@
 
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean''; because this is an adjective, we also explored the word pairings.
+    Another soft attribute that is high on the list for most of the price ranges is the word ``clean'', so we examined its word pairings.
 Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general.
@@
 For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
-Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
+Tobacco was referenced singularly as ``cigarette'', but also in word pairs in Table \ref{tab:adj_en_neg} as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
 Another common complaint was that there were no nonsmoking facilities available.
@@
 However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world.
-Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.
+Our study explores whether such an environment can affect different cultures equally or whether it is attractive only to certain cultures.
 
@@
 Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
-The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture, and this might be unforeseen by some customers.
+The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture, and perhaps unexpected.
 In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
@@
     Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high-standard hospitality environment.
+Chinese tourists may have expectations about their treatment that are not being met, even in this high-standard hospitality environment.
 This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
@@
 Chinese language pamphlets as well as Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples.
-Dissatisfaction in a foreign country is natural if the language native to that region is not known.
+channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples of these accommodations.
 \cite{ryan2001} also found that communication difficulty was one of the main reasons that Chinese customers would state for not visiting again.
@@
 
-    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.,][]{shanka2004,choi2001}.
+    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction \cite[e.g.,][]{shanka2004,choi2001}.
+Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel.
 However, hard attributes are not usually analyzed in satisfaction studies.
@@
     Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors.
-The rates are similar for most price ranges except the highest-priced hotels, where 35 \% of the keywords are undefined.
-However, the soft attributes are still similar at 18 \%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
+The rates are similar for most price ranges except the highest-priced hotels.
+However, two of these soft attributes are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
 Chinese tourists may expect spaciousness and cleanliness when coming to Japan.
@@
 A study on Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this concern is less related to the cultural attribute in Japanese hotels and more related with the pricing of hotels overall.
-Tourists coming to Japan could be either experienced or first-time travelers.
-However, their expectation of the price for hotels was lower than the actual prices in Japan.
+However, our results indicate that this has more to do with the pricing of hotels in Japan overall, than with Chinese culture.
 In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking.
@@
 As such, it presents a larger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, since they spend more than 45 \% of their budget on hotel lodging.
-    Asian tourists spend only 25 \% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment, which could increase returns by several times.
-
-    However, Chinese customers are more in number, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes; thus, breaking the language barrier breaking is one of the few strategies to accomplish this.
+
+  \subsection{Satisfaction across different price ranges}\label{disc:price}
+
+    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
+The most visible change across differently priced hotels is the change in voice when describing satisfaction.
+We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
+For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
+In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
+Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
+
+    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
+Conversely, the failure of meeting expectations causes dissatisfaction.
+We can assume that a customer that pays more for a higher-class experience has higher expectations.
+For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
+In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
+However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
+In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
+
+    We argue that these are two different kinds of expectations: logical and emotional.
+In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
+In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
+For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
+Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
+Thus, hospitality and service enhance the experience of the customers.
+
+    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
+For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
+In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
+It is widely known in Japan that many Chinese tourists visit Japan for shopping.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among \textit{souvenir} items representative of the culture or places that they visit \cite{japan2014consumption}.
+Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
+Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities compared to Chinese tourists.
+
+    Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
+In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
+Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
+
+    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
+For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
+Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
+Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
+As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
+While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
+This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
+
+  \subsection{Cross-culture analysis of expectations and satisfaction}\label{disc:culture}
 
@@
 low uncertainty avoidance countries).
+
     However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}.
@@
 
-    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese}.
+    For our purposes of contrasting Western vs.
+Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
+
+    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese, kim2000}.
 These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations.
@@
 
-    For our purposes of contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
     The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
@@
 However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, a Chinese cultural attribute emphasizes that the environment and the location  affect satisfaction, rather than the treatment.
-According to previous research, Chinese tourists are collectivists, whereas Westerners are individualists \cite[][]{kim2000}.
+Nevertheless, one could argue a Chinese cultural attribute emphasizes that the environment and the location affect satisfaction, rather than the treatment they receive.
+
     A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment.
@@
 While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard–-soft attribute satisfaction between Chinese and Western cultures.
-Differences in another factor, power distance, were also noted when measuring by Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change across differently priced hotels is the change in voice when describing satisfaction.
-We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Conversely, the failure of meeting expectations causes dissatisfaction.
-We can assume that a customer that pays more for a higher-class experience has higher expectations.
-For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
-In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
-
-    We argue that these are two different kinds of expectations: logical and emotional.
-In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
-In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
-For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
-Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
-Thus, hospitality and service enhance the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
-For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
-It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
-Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
-Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
-In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
-
-    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
-This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
+Differences in another factor, power distance, were also noted when using  Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
 
@@
 Western tourists were highly satisfied with Japanese hospitality and preferred soft attributes to hard ones.
-The other conclusion is that managerial decisions could mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion could satisfy Chinese customers to a greater extent.
+
+    The other conclusion is that managerial decisions could mostly benefit Western tourists, except for language improvements and breakfast inclusion could satisfy both groups.
+As mentioned earlier in this paper, Westerners are ``long-haul'' customers, spending more of their budget on lodging than Asian tourists \cite[][]{choi2000}.
+With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
+In addition, breaking the language barrier breaking is one of the few strategies to satisfy both groups.
 Recently, Japan has been facing an increase in Chinese students as well as students of Western universities.

### 2021-02-26 1_manuscript/cur_dir_my_latexdiff.sh

@@ -3,6 +3,9 @@
 # ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-1.tex --compile --view --clean
 # ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-1.tex --compile --view --clean
 
-../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-2.tex --compile --clean
-../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-2.tex --compile --clean
-../my_latexdiff.sh itt-emotion_V6-1.tex itt-emotion_V6-2.tex --compile --clean
+# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-2.tex --compile --clean
+# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-2.tex --compile --clean
+# ../my_latexdiff.sh itt-emotion_V6-1.tex itt-emotion_V6-2.tex --compile --clean
+
+# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-4.tex --compile --clean
+# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-4.tex --compile --clean

### 2021-02-26 1_manuscript/Z_mid-editing_versions/itt-emotion_V6-2.tex
folder cleanup of mid-editing versions

--- 2021-02-26 1_manuscript/itt-emotion_V6-3.tex
@@
 
-  We extracted a large number of text reviews from the site \textit{Ctrip}, with mostly mainland Chinese users, and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that relate to positive and negative opinions in a review.
+  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
+We then determined the most commonly used words that contribute to positive and negative opinions in a review.
 We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to train an optimized Support Vector Classifier (SVC) to perform a binary emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and the nouns they refer to.
-We split the dataset into price ranges to observe the differences in keyword usage between lower-class and higher-class hotels.
+These positive and negative keywords allow us to perform an emotional classification of the reviews in large quantities, saving time and resources for the researchers.
+We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
+We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
+We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
 We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
@@
     In the \textit{Ctrip} data collection, reviews from a total of \num[group-separator={,}]{5774} hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese.
+From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese from mainland China.
 Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
@@
     However, to make the data comparisons fair, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range.
+We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges.
 In addition, we selected only the hotels that had pricing information available.
 We extracted the lowest and highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites, depending on the hotel.
-Regardless of the reason, we chose the highest-priced room since it can be an indirect indicator of the hotel's class.
+The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel.
+Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered.
 After filtering, the datasets contained \num[group-separator={,}]{557} hotels in common.
@@
 
-    The price for a night in these hotels ranges from cheap capsule hotels at 2000 yen per night to high-end hotels 188,000 yen a night at the far ends of the bell curve.
+    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels 188,000 yen a night as the far ends of the bell curve.
 Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
@@
 
-    We needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
+    Chinese text does not have delimiters between each word, so there is a need to separate them.
+Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
 For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
@@
 In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the database and extracting instances of a few determined dependency codes.
+We did that by parsing the entire database and extracting instances of a few determined dependency codes.
 One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
@@
 
-    We observed the top 10 satisfaction and dissatisfaction keywords with the highest frequencies emotionally positive and negative statements to study.
+    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
 The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
@@
 However, hard attributes are not usually analyzed in satisfaction studies.
-It is important to consider both kinds of attributes.
-If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future.
-Otherwise, if the satisfaction was related more with hard attributes overall, hotels should be built considering the location while minimizing other costs.
 Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
@@
 The expectation may be due to reputation, previous experiences, or cultural backgrounds.
+
     We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
@@
 Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
-The exception to this is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
+English-speaking customers also have soft attributes at the top of their list.
+The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
+If one considers the satisfaction of both Chinese and Western tourists, a hotel can improve its services to attract more customers in the future.
+Otherwise, if the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels should be built considering the location.
 
     For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
-However, English-speaking customers complained about price less in lower-priced hotels.
+However, English-speaking customers complained about price with a lower rank in lower-priced hotels.
 In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
@@
 The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, these considerations can be costly.
+This paper provides a useful guideline about the factors to be prioritized and the factors that would be the most suitable for each customer group.
+Hotels can also use the price range categorization to choose the appropriate strategy.
 However, once the hotel's location and construction are set, only a few changes can be made to satisfy Chinese customers further.
@@
 A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment.
-According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
+According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivistic customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
 
@@
     In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change across differently priced hotels is the change in voice when describing satisfaction.
+The most visible change of satisfaction factors across differently priced hotels is the change in voice when describing their satisfaction.
 We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
@@
 In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
+Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.'' Here, we can determine how expectations influence satisfaction and dissatisfaction in different ways.
 
@@
 Conversely, the failure of meeting expectations causes dissatisfaction.
-We can assume that a customer that pays more for a higher-class experience has higher expectations.
-For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
+In the aforementioned cases, we can infer that a customer that pays more for a higher-class experience has higher expectations.
+This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
+As such, any lack of cleanliness can lead to disappointment.
 In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
@@
 In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
-
 We argue that these are two different kinds of expectations: logical and emotional.
 In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
+
     In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
@@
 
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
+    There are interesting differences between Chinese and English-speaking tourists in their satisfaction factors to differently priced hotels.
 For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
@@
 It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan, and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
+The study shows that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
 Furthermore, Chinese tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
@@
 
-    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
+    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors remain constant for each culture's customers.
 For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
@@
   In this study, we analyzed keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context of these words by using a dependency parser and observing the related nouns.
+Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
 However, a limitation is that it analyzed solely the words directly related to each keyword and did not search further connections.
@@
   We found that Western tourists were most satisfied with staff behavior, cleanliness, and other soft attributes.
-However, Chinese customers had other concerns for their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
+However, we found that Chinese customers had concerns other than hospitality when studying their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
 We found that the two cultures had different reactions to the hospitality environment and the prices.

### 2021-02-27 1_manuscript/itt-emotion_V6-5.tex
V6-5 -2191 words = 13,239 words

--- 2021-02-26 1_manuscript/itt-emotion_V6-4.tex
@@
 
-  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}.
+  Inbound international tourism has been increasingly affecting Japanese economy \cite[][]{jones2009}.
 A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-The tourist population was 86.14\% Asian, and 25.63\% was from China.
-Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
+Chinese tourists accounted for 25.63\% of the tourist population.
+Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language.
 The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
-The tourist market is gradually becoming diverse because of multicultural tourist populations.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied.
+Furthermore, the tourist market is gradually becoming diverse because of multicultural tourist populations.
+This diversity means that the expectations when staying at a hotel will be varied.
 Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

### 2021-02-27 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,11 +1,1 @@
-# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion.tex --newversion="6" --compile --view --clean 
-
-# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-1.tex --compile --view --clean
-# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-1.tex --compile --view --clean
-
-# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-2.tex --compile --clean
-# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-2.tex --compile --clean
-# ../my_latexdiff.sh itt-emotion_V6-1.tex itt-emotion_V6-2.tex --compile --clean
-
-# ../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-4.tex --compile --clean
-# ../my_latexdiff.sh itt-emotion_V6-0.tex itt-emotion_V6-4.tex --compile --clean
+../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-5.tex --compile --clean

### 2021-02-27 1_manuscript/itt-emotion.tex
my_latexdiff update, V6-6 = V5 -2204 words = 13226 words, hand in version

@@
 
-  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence.
-In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing.
-However, most studies on tourists’ behavior are biased toward the Western world.
-Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors.
-To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited.
-Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart?
-Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities?
-We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges.
-Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives.
-We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior.
-We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.
+  We analyzed expectations and satisfaction factors in Chinese and Western cultures, comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
+  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors, and then used them to classify a more extensive data set with an SVM.
+We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
+  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior.
+We also found that the lack of a Chinese-friendly environment for Chinese customers and the smell of cigarettes for Western ones can be disappointing factors of their stay.
+  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.
 
@@
 
+  Inbound international tourism has been increasingly affecting Japanese economy \cite[][]{jones2009}.
+A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
+
   Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide.
-With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}.
-Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
+\textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}.
+Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
 However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
 Thus, it could be theorized that their satisfaction factors should be different.
-How will different cultures react and perceive hotels and their hospitality in this context?
-
-  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}.
-A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China.
-Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language.
-The effect of Chinese tourists on international economies is increasing.
-Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}.
-The tourist market is gradually becoming diverse because of multicultural tourist populations.
-Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied.
+The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations.
+This diversity means that the expectations when staying at a hotel will be varied.
 Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
 
-  However, many tourist-behavior analyses have been performed involving Western subjects.
-As such, a gap in knowledge existed until recent decades.
+  Our study focuses on Western and Chinese tourists, considering their numbers.
+Chinese tourists accounted for 25.63\% of the tourist population.
+On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}.
+The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
+Despite this, many tourist-behavior analyses have been performed only involving Western subjects.
+As such, a knowledge gap existed until recent decades.
+
   In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations.
-This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations.
+The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
+These studies, although valid, can have limitations, namely, the scale and sampling.
+In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose.
+These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study.
+This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations.
 It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
@@
 Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
+For this, we used a data-driven approach to our analysis.
 
@@
 
-  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques.
-We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges.
+  This study aims to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels across several price ranges.
 We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
 More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
+We define hard attributes as attributes relating to physical and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
 In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
 
-  We use large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner.
-In the past, survey-based studies have provided a theoretical background for a few, specific tourist populations of a single culture or traveling with a single purpose.
-The limited scope of these studies often leads to difficulties in observing cultural and language differences in a single study.
-
-  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures.
-These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction.
-Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.
-
 \section{Theoretical background and hypothesis development}\label{theory_hypothesis}
@@
     The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}.
-There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century.
-However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}.
+There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century, while others found that it originates in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}.
 The practice of high standards in hospitality has survived throughout the years.
@@
 
-    It stands to reason that this cultural aspect of hospitality would be a positive factor in influencing customer satisfaction.
+    It stands to reason that this cultural aspect of hospitality would positively influence customer satisfaction.
 However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.
@@
 Instead, we consider it as a cultural factor that influences all businesses in Japan.
-We then observe the customers' evaluations regarding service and hospitality factors in general and compare to other places and business practices in the world.
+We then observe the customers' evaluations regarding service and hospitality factors and compare them to other places and business practices in the world.
 In summary, we consider the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations on service and hospitality factors that are universal to all hotels in any country.
@@
 
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}.
+    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}.
 However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
@@
     In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior.
-Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies.
-This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists.
+Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}.
+However, studies focusing on only the behavior of this subset of tourists are the majority.
 To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities.
-At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
+One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
+Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
 Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty.
-In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.
+Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.
 
     One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general.
-Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation.
+Western analyses is that they were performed before 2000 and not Chinese-specific.
+Meanwhile, the current Chinese economic boom is increasing the influx of tourists of this nation.
 The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling.
+In turn, if we follow the definition of satisfaction in \cite{hunt1975}, the change in expectations could have influenced their satisfaction factors when traveling.
 Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
@@
 Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers?
+In this environment, customers could either hold their satisfaction to this hospitality regardless of their culture or value other factors more depending on their cultural differences.
 Our study measures this at a large scale across different hotels in Japan.
@@
     Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly.
+We can see that depending on the study and the design of questionnaires and the destinations; the results can vary greatly.
 Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
 Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire.
+This means that the factors will be selected through statistical methods alone instead of being defined by the questionnaire.
 Our method allows us to find factors that we would not have contemplated.
@@
 This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.
+This study analyzes the satisfaction and dissatisfaction factors cross-culturally and compares them with the existing literature.
 
     % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits.
+    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may further highlight our study and its merits.
 A contrast is shown in Table \ref{tab:lit-rev}.
@@
     % Machine Learning
-    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification.
-This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically.
+    Our study used an algorithm for sentiment analysis called a Support Vector Machine (SVM), a supervised machine learning used for binary classification.
 Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template.
-Machine learning can also be unsupervised, where without any pre-labeled data.
+Learning machines can be supervised, as in our study, where the algorithm has manually labeled training data to detect patterns in it and use them to establish a method for classifying other unlabeled data automatically.
+Machine learning can also be unsupervised, where there is no pre-labeled data.
 In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
@@
 Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
-These qualities determine why, similar to actual mining, data mining is mostly exploratory.
+These qualities determine why, similar to actual mining; data mining is mostly exploratory.
 One can never be sure that one will find a specific something.
@@
 The exploration of large opinion datasets with these methods is essential.
-The reason being that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
+The reason is that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
 In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
 
-    In this study, we predict that several things might occur.
-Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors.
-However, we expect that both of these options will present themselves.
-We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings.
-However, we are using a database of several orders of magnitude larger.
-We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.
-
 \section{Methodology}\label{method}
 
-  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that contribute to positive and negative opinions in a review.
+  We extracted a large number of text reviews from the site \textit{Ctrip}, with mostly mainland Chinese users, and the travel site \textit{TripAdvisor}.
+We then determined the most commonly used words that relate to positive and negative opinions in a review.
 We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC).
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews.
-We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels.
+These positive and negative keywords allow us to train an optimized Support Vector Classifier (SVC) to perform a binary emotional classification of the reviews in large quantities, saving time and resources for the researchers.
+We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and the nouns they refer to.
+We split the dataset into price ranges to observe the differences in keyword usage between lower-class and higher-class hotels.
 We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
@@
 
-    Chinese text, unlike English, does not have spaces between each word to separate them.
-Besides, we also needed to analyze the grammatical relationship between words, be it English or Chinese, to understand connections between adjectives and nouns.
+    We needed to analyze the grammatical relationship between words, be it English or Chinese, to understand the connections between adjectives and nouns.
 For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
 In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In the case of texts in English, however, only using spaces is not enough to correctly collect concepts.
+In English texts, however, only using spaces is not enough to correctly collect concepts.
 The English language is full of variations and conjugations of words depending on the context and tense.
 Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library with the English texts.
+For this purpose, we used the \textit{gensim} library for the English texts.
 
@@
 
-    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below.
+    Our study used a linear kernel for the SVC, defined by the formula (\ref{eq:svm1}) below.
 Each training sentence is a data point, a row in the vector \(x\).
@@
 
-    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data.
+    During the SVC learning algorithm, each data point classified incorrectly alters the weight vector to correctly classify new data.
 These changes to the weight vector are greater for features close to the separating hyperplane.
@@
 
-    To understand Chinese tourists and English-speaking tourists' satisfaction and dissatisfaction factors when lodging in Japan, we study both the frequency of the words they use.
-Following that, to know the relevance of a keyword as a preference for each group, we observed each entropy-based keyword's frequencies in our complete data set and in each price range.
-The frequency of the keywords in the database shows the level of priority it has for customers.
-
-    We observed the top 10 words with the highest frequencies for keywords linked by entropy to satisfaction and dissatisfaction in emotionally positive and negative statements to study.
+    We observed the top 10 satisfaction and dissatisfaction keywords with the highest frequencies of emotionally positive and negative statements to study.
 The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
@@
     Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}.
+To understand those, we performed the dependency parsing and part of speech tagging explained in section \ref{textprocessing}.
 While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
@@
 For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are considered soft attributes.
+For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not the hotel's physical structure are considered soft attributes.
 Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
@@
 If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the percentage of usage in each context.
+For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the usage percentage in each context.
 If it was not clear from the word or the pairing alone, we declared it undefined.
@@
     Our research questions were related to two issues.
-Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality.
-We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}.
-These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings.
-From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges.
-The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
-However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.
-
-    The word ``staff'' is the second or third in all the price ranges in the lists of satisfaction factors in reviews written in English .
-This word is followed by a few other keywords that are lower in the top 10 list, such as ``helpful'' or ``friendly.'' From the pairings of the top-ranking keyword ``good'' in Table \ref{tab:adj_en_pos}, we realize that customers mainly praise the location, service, breakfast, or English availability.
-From the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we deduce that  the Western tourists are also disappointed with service-related concepts.
-Therefore, both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transportation availability nearby (subways and trains) as secondary yet essential points to their satisfaction.
-The Chinese customers are primarily satisfied with the room quality in terms of the spaciousness and cleanliness as well as the service of breakfast.
-
-    In contrast, the English-speaking customers were easily upset by uncleanliness and smoke smell from cigarettes.
-Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
-For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
-Furthermore, the age of the buildings was a concern for both populations.
-Nevertheless, for all price ranges considered, English-speaking tourists valued staff friendliness over room quality when considering their satisfaction.
-In contrast, Chinese tourists considered location and transportation more often.
+Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture.
+
+    Observing the top-ranking positive keywords in Chinese reviews, as shown in Tables \ref{tab:freq_res_pos} and Table \ref{tab:adj_zh_pos}, it was revealed that, while service, cleanliness, and breakfast were praised in most hotels, the location was more important when observing the pairings.
+Hard attributes were abundant lower on the lists.
+The negative keywords in Table \ref{tab:freq_res_neg} indicate that a lack of a Chinese-friendly environment was perceived, although there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
+However, most complaints were about the hotel's price, which included all of the price ranges; therefore, the price was the primary concern for Chinese customers with different travel purposes.
+
+    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
+This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
+When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
+When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
 
@@
 
+    With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
+However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
+The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
+
     For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels.
-Here, we define hard attributes as those related to the hotel's physical, structural, or environmental aspects.
-These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, surroundings, view, and location convenience.
-In contrast, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness.
 Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
-English-speaking tourists, on the other hand, were more responsive to soft attributes, either positively or negatively.
+On the other hand, English-speaking tourists were more responsive to soft attributes, either positively or negatively.
 In the case of negative keywords, they were more concerned about the hotel's soft attributes.
@@
 
-    However, the size of the room or the bed is a hard attribute.
-Without considering rebuilding the hotel, it is not trivial to improve this attribute.
+    Chinese customers are satisfied with the size of the room or bed; however, it is not trivial to change this.
 In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
@@
 In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair.
-Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers and they were mostly pleased when their expectations were fulfilled.
-
-    A key component found in Chinese customer satisfaction soft factors was the inclusion of breakfast within the hotel.
+Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers, and they were mostly pleased when their expectations were fulfilled.
+
+    A key soft satisfaction factor was the inclusion of breakfast within the hotel.
 While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' which possibly referred to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words.
-The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' was also present in all price ranges, albeit at different priorities in each of them.
+In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' referring to the hotel commodities, was frequently used in positive texts compared to other food-related words across all price ranges, albeit at different priorities in each of them.
 For this reason, we regard it as an important factor.
 From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings.
-It is only slightly lower in other categories, although it is not depicted on the table.
-Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase the number of good reviews.
+It is only slightly lower in other categories, although it is not depicted in the table.
+Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase good reviews.
 
@@
 
-    From the satisfaction factors of English-speaking tourists, we can see that at least three words were directly related to staff friendliness and services in the general database, ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges and only third in one of them.
-In addition, the words ``helpful'' and ``friendly'' follow it lower in the list in most price ranges.
+    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the highest-ranked of these three, ranking second for satisfied customers across most price ranges and only third in one of them.
 The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
@@
 
-    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors and ``uncomfortable'' was high on the dissatisfaction factors.
+    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors, and ``uncomfortable'' was high on the dissatisfaction factors.
 The words were paired with nouns such as ``bed,'' ``room,'' ``pillow,'' and ``mattress,'' when they generally referred to their sleep conditions in the hotel.
@@
 
-  \subsection{Tobacco, what is that smell?}\label{disc:tobacco}
-
-    A concern for Western tourists was the smell of tobacco in their room, which can be regarded as a soft attribute.
-Tobacco was found not only as a standalone word with ``cigarette'' but also in word pairs in Table \ref{tab:adj_en_neg}, such as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
+  \subsection{Tobacco, an unpleasant smell in the room}\label{disc:tobacco}
+
+    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes.
+Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
+For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
+Tobacco was referenced singularly as ``cigarette'', but also in word pairs in Table \ref{tab:adj_en_neg} as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
 Another common complaint was that there were no nonsmoking facilities available.
-The smell of smoke can completely ruin some customers’ stay and thus lead to bad reviews, thereby lowering the number of future customers.
-
-    In contrast, Chinese customers seemed to not be bothered by this.
+The smell of smoke can completely ruin some customers’ stay, leading to bad reviews, thereby lowering the number of future customers.
+
+    In contrast, Chinese customers seemed not to be bothered by this.
 Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
@@
 However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas.
-However, many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
+Many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
+
     Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele.
 To cater to all kinds of customers, including Western and Asian, Japanese hotels must provide spaces without tobacco smell.
-Even if the smoke does not bother a few customers, the lack of such a smell would make it an appropriate space for all customers.
+Even if the smoke does not bother a few customers, the lack of such a smell will make it an appropriate space for all customers.
 
@@
 There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis.
-The latter is a luxury in Japan compared to other countries, especially in less developed countries, where this is a low-cost choice.
+The latter is a luxury in Japan compared to other countries.
 In Japan, taxis provide a high-quality experience with a matching price.
-Therefore, subway availability and maps or GPS applications as well as a plan to travel the city are of utmost necessity for tourists.
-
-    Japanese convenience stores are also famous worldwide, because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs.
-If some trouble occurs, or a traveler forgot to pack a particular item, it is mostly certain that they can find it.
-
-    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, the location of a Japanese hotel must be carefully chosen prior to construction.
-Although not a top priority, this is a universal factor for both customer groups and is conducive to generate positive reviews.
+Therefore, for people under a budget, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity for tourists, using taxis only as a last resort.
+
+    Japanese convenience stores are also famous worldwide because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs.
+If some trouble occurs, or a traveler forgot to pack a particular item, it is most certain that they can find it.
+
+    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, and perhaps offering guide maps and information about these as an appeal point could result in greater satisfaction.
 
 \section{Discussion}\label{discussion}
-
-  In this section, we explore the possible interactions with Japanese hospitality, the differences between perceptions of Chinese and Western tourists as well as the possible causes, variations in perceptions across different price ranges, and the implications for the industry.
-We also discuss the differences between the hotel's hard and soft attributes and their contributions to customers' satisfaction.
 
@@
 In other words, tourists of a particular culture have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, excels and is considered to be of the highest standard across the world.
-Our study explores whether such an environment can affect different cultures equally Or whether it is attractive only to certain cultures.
-
-    Our results indicate that Western tourists are more satisfied with soft attributes, such as friendly and helpful staff in Japan, than Chinese tourists.
+However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world.
+Our study explores whether such an environment can affect different cultures equally or whether it is attractive only to certain cultures.
+
+    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists.
 As explained earlier in this paper, Japan is well known for its customer service.
 Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
-The level of hospitality, even in the cheapest convenience store, is starkly different from Western culture.
-Although it could be a cultural shock to some, it is mostly approved.
-The Japanese staff treats all customers respectfully, and this might be unforeseen by some customers.
+Even in the cheapest convenience store, the level of hospitality is starkly different from Western culture and perhaps unexpected.
 In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
@@
     Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about the Chinese visitors' treatment that are not being met, even in this high-standard hospitality environment.
+Chinese tourists may have expectations about their treatment that are not being met, even in this high-standard hospitality environment.
 This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
 While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging.
-Chinese language pamphlets as well as Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup, etc.), or the treatment towards Chinese people could be examples.
-Dissatisfaction in a foreign country is natural if the language native to that region is not known.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons that Chinese customers would state for not visiting again.
+Chinese language pamphlets and Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
+channels, Wi-Fi setup, etc.), or the treatment towards Chinese people, could be examples of these accommodations.
+\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
 However, this issue is not exclusive to Japan.
@@
 It is possible that Chinese customers had high-grade hospitality and were equally satisfied with Westerners.
-In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction, and a lack of expectation results in lesser satisfaction.
+In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
 There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
 
-    The case representing the higher possibility is unclear from our results.
+    It is unclear which of these two is most likely from our results.
 However, competing in hospitality and service includes language services, especially in the international tourism industry.
@@
 Considering that most of the tourists in Japan come from other countries in Asia, multilingual support is beneficial.
-Proposals for this endeavor include hiring Chinese speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
+Proposals for this endeavor include hiring Chinese-speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
 
@@
 
-    \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel \cite[e.g.,][]{shanka2004,choi2001}.
+    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction \cite[e.g.,][]{shanka2004,choi2001}.
+Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel.
 However, hard attributes are not usually analyzed in satisfaction studies.
-Examples of hard attributes include the hotel's location relative to public transportation and shops, language immersion of the country, noise pollution, or weather.
+It is important to consider both kinds of attributes.
+If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future.
+Otherwise, if the satisfaction was related more to hard attributes overall, hotels should be built considering the location while minimizing other costs.
 Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
@@
     Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors.
-The rates are similar for most price ranges except the highest-priced hotels, where 35 \% of the keywords are undefined.
-However, the soft attributes are still similar at 18 \%.
-However, two of these managerial words are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
+The rates are similar for most price ranges except the highest-priced hotels.
+However, two of these soft attributes are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
 Chinese tourists may expect spaciousness and cleanliness when coming to Japan.
 The expectation may be due to reputation, previous experiences, or cultural backgrounds.
-Some scholars argue that different cultures have different room size perceptions \cite[][]{Saulton2017}.
-Although the study subjects are German and South Korean, \cite{Saulton2017} presents the results as differences influenced by Asian and Western cultures.
-We argue that one country is not representative of others’ cultures, and thus, there can be differences between South Korea and China in room size perception.
-However, a different room size perception may affect the satisfaction of Chinese tourists in contrast to Westerners because Westerners prioritize room size as the price of the hotel room rises.
 We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
@@
 
-    In contrast, English speakers are mostly satisfied with the hotel's soft attributes.
+    In contrast, English speakers are mostly satisfied with the hotels' soft attributes.
 Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
-English-speaking customers also have soft attributes at the top of their list.
-The exception is the hard attribute that is the hotel's location, which is consistently around the middle of the top 10 lists for all price ranges.
-If one considers the satisfaction of both Chinese and Western tourists, a hotel can improve its services to attract more customers in the future.
-Otherwise, if the satisfaction was related more with hard attributes overall for 1020 both cultures, hotels should be built considering the location.
+The exception to this is the hard attribute that is the hotels' location, which is consistently around the middle of the top 10 lists for all price ranges.
 
     For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
-However, English-speaking customers complained about price with a lower rank in lower-priced hotels.
+However, English-speaking customers complained less about the price in lower-priced hotels.
 In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
 A study on Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this concern is less related to the cultural attribute in Japanese hotels and more related with the pricing of hotels overall.
-Tourists coming to Japan could be either experienced or first-time travelers.
-However, their expectation of the price for hotels was lower than the actual prices in Japan.
+However, our results indicate that this has more to do with the pricing of hotels in Japan than with Chinese culture.
 In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking.
@@
 
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be solved with improved management; this is true for all price ranges.
-The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, all of these considerations can be costly.
-However, this paper provides a useful guideline about the factors to be prioritized and the factors that would be the most suitable for each customer group.
-Hotels can also use the price range categorization to choose the appropriate strategy.
-However, once the hotel's location and construction are set for Chinese customers, only a few changes can be made to satisfy them further.
-As mentioned previously, Chinese language availability is another soft attribute that can be improved with staff and training investment.
+    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be improved; this is true for all price ranges.
+The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, these considerations can be costly.
+However, once the hotel's location and construction are set, only a few changes can be made to satisfy Chinese customers further.
+As mentioned previously, Chinese language availability is a soft attribute that can be improved with staff and training investment.
 
@@
 As such, it presents a larger investment opportunity.
-As mentioned earlier in this paper, Westerners are known as ``long-haul'' customers, since they spend more than 45 \% of their budget on hotel lodging.
-    Asian tourists spend only 25 \% of their budget on hotels \cite[][]{choi2000}.
-With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-Making more hotel facilities tobacco-free and deodorizing the rooms can be a low-cost investment, which could increase returns by several times.
-
-    However, Chinese customers are more in number, even though they tend to spend less on lodging.
-Attracting a large number of Chinese customers can be a viable strategy for hotels.
-However, as mentioned before, they tend to focus more on hard attributes; thus, breaking the language barrier breaking is one of the few strategies to accomplish this.
+
+  \subsection{Satisfaction across different price ranges}\label{disc:price}
+
+    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
+The most visible change across differently priced hotels is the change in voice when describing satisfaction.
+We noticed this by observing the adjective-noun pairs and finding pairs with different adjectives for the same nouns.
+For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
+In contrast, the adjectives that pair with the same nouns for higher-priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
+Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
+
+    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
+Conversely, the failure of meeting expectations causes dissatisfaction.
+We can assume that a customer that pays more for a higher-class experience has higher expectations.
+For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
+In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
+However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
+In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
+
+    We argue that these are two different kinds of expectations: logical and emotional.
+In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
+In contrast, in the second case, customers have a vague idea of having a positive experience but do not measure it against any standard.
+For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
+Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
+Thus, hospitality and service enhance the experience of the customers.
+
+    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
+For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
+In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
+It is widely known in Japan that many Chinese tourists visit Japan for shopping.
+\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among \textit{souvenir} items representative of the culture or places that they visit \cite{japan2014consumption}.
+Furthermore, Chinese tourists’ choice to shop in Japan is more related to the quality of the items rather than their relation to the tourist attractions.
+Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities compared to Chinese tourists.
+
+    Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
+In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
+Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
+
+    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
+For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
+Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
+Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
+As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
+While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
+This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
+
+  \subsection{Cross-culture analysis of expectations and satisfaction}\label{disc:culture}
 
@@
 However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-
-    Nevertheless, a Chinese cultural attribute emphasizes that the environment and the location  affect satisfaction, rather than the treatment.
-According to previous research, Chinese tourists are collectivists, whereas Westerners are individualists \cite[][]{kim2000}.
-A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances, rather than the environment.
-According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivistic customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
+Nevertheless, one could argue a Chinese cultural attribute emphasizes that the environment and the location affect satisfaction rather than the treatment they receive.
+
+    A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances rather than the environment.
+According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
 
@@
 However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard–-soft attribute satisfaction between Chinese and Western cultures.
-Differences in another factor, power distance, were also noted when measuring by Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change of satisfaction factors across differently priced hotels is the change in voice when describing their satisfaction with the same topics.
-We noticed this by observing the adjective–-noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for higher- priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``worst'' to ``disappointing.'' Here, we can determine how expectations influence satisfaction and dissatisfaction in different ways.
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Therefore, the failure of meeting expectations would cause dissatisfaction.
-In the aforementioned cases, we can infer that a customer that pays more for a higher-class experience has higher expectations.
-This is true in dissatisfaction, where their expectation is higher in a more expensive hotel.
-As such, any lack of cleanliness can lead to disappointment.
-In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
-We argue that these are two different kinds of expectations: logical and emotional.
-In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
-
-    In the second case, in contrast, customers have a vague idea of having a positive experience but do not measure it against any standard.
-For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
-Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
-Thus, hospitality and service enhance the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction factors to differently priced hotels.
-For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
-It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan.
-The study shows that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among other more traditional \textit{souvenir} items, such as objects that are representative of the culture or places that they visit \cite{japan2014consumption}.
-Furthermore, tourists’ choice to shop in Japan is more related with the quality of the items rather than their relation to the tourist attractions.
-Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities.
-Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15 000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
-In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
-
-    While some aspects of satisfaction and dissatisfaction change depending on the hotel's price range, some other factors remain constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
-This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
+While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
+Differences in another factor, power distance, were also noted when using  Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
 
@@
 Instead, they focused on the hard attributes of a hotel.
-In particular, they were not satisfied with hospitality as much as Western tourists were; otherwise, they felt that basic language and communication needs were not met, thereby they were not much satisfied.
+In particular, they were not satisfied with hospitality as much as Western tourists were; otherwise, they felt that basic language and communication needs were not met; thereby, they were not much satisfied.
 Western tourists were highly satisfied with Japanese hospitality and preferred soft attributes to hard ones.
-The other conclusion is that managerial decisions could mostly benefit Western tourists, except that Chinese language improvements and breakfast inclusion could satisfy Chinese customers to a greater extent.
+
+    The other conclusion is that managerial decisions could mostly benefit Western tourists, except for language improvements and breakfast inclusion could satisfy both groups.
+As mentioned earlier in this paper, Westerners are ``long-haul'' customers, spending more of their budget on lodging than Asian tourists \cite[][]{choi2000}.
+With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
+In addition, breaking the language barrier is one of the few strategies to satisfy both groups.
 Recently, Japan has been facing an increase in Chinese students as well as students of Western universities.
@@
 Our results suggest that satisfying cleanliness needs could satisfy both customer types.
-A low-cost investment could be to make the facilities tobacco-free.
-Our results are also divided by price ranges, thereby a hotel manager could consider which analysis suits their hotel the most.
-
-    Albeit not manageable after a hotel is completely constructed, hard attributes should be considered by managers.
-As stated before, transportation systems and nearby shops are points of interest for both Chinese and Western tourists.
-Japanese hotel managers should consider the location and surroundings before the hotel is constructed.
-A suggestion could be to purchase land and start the construction at places where public plans for new subway lines have already been made.
+We suggest investing in making the facilities tobacco-free.
+Our results are also divided by price ranges; thereby, a hotel manager could consider which analysis suits their hotel the most.
+Hard attributes are difficult to change; however, improvements in service can be made to accompany these attributes.
+For example, transportation guides for foreigners that might not know the area could increase satisfaction.
 
@@
 
-  In this study, we analyzed satisfaction and dissatisfaction keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand the context in which these words were used by using a dependency parser and observing the related nouns.
-However, our study is limited because it analyzed solely the words directly related to each keyword and did not follow the upstream or downstream path down to further connections.
+  In this study, we analyzed keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
+Following that, we attempted to understand these words' context by using a dependency parser and observing the related nouns.
+However, a limitation is that it analyzed solely the words directly related to each keyword and did not search for further connections.
 This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
@@
 Services offered in these hotels are of high quality, albeit very different.
-However, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
-However, there is still a division between Western and Japanese style hotels, which constitutes another limitation of our study.
-
-  An essential aspect of this study is that we focused on the satisfaction and dissatisfaction towards the expectations of the individual aspects of the hotels.
-This gave us insight into the factors that can be considered by hotel managers.
-However, the overall satisfaction of each customer was not measured.
-This measurement can be performed by rating the volume of text used to describe satisfaction and dissatisfaction factors.
-However, this would impose a few difficulties, which are out of the scope of this study.
-
-  Another limitation is that a large portion of Asian tourists coming to Japan are Taiwanese and Korean.
-We could not analyze these populations because our team members did not know those languages.
-Moreover, further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
+Nevertheless, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
+
+  An essential aspect of this study is that we focused on the satisfaction and dissatisfaction towards the expectations of individual aspects of the hotels.
+This gave us insight into the factors that hotel managers can consider.
+However, each customer's overall satisfaction was not measured since it would require methods that are out of the scope of this paper.
+Another limitation is that further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
 
   In future work, we plan to investigate these topics further.
-We plan to extend our data to research of different trends and regions of Japan, different kinds of hotels, and customers traveling alone or in groups, whether for fun or for work.
+We plan to extend our data to research different trends and regions of Japan, different kinds of hotels, and customers traveling alone or in groups, whether for fun or for work.
 Another point of interest in this study's future work is to use word clusters with similar meanings instead of single words.
@@
 
-  One possible approach for hotel managers is to improve the satisfaction levels of Chinese tourists, who dedicate lower percentage of their budget to hotels but are more abundant in number.
+  One approach for hotel managers is to work to satisfy Chinese tourists more, who dedicate a lower percentage of their budget to hotels but are more numerous.
 They are less satisfied with soft attributes but have an identifiable method for improving satisfaction by lessening language barriers and providing a satisfactory breakfast.

### 2021-02-27 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-5.tex --compile --clean
+../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-6.tex --compile --clean --view

### 2021-02-27 0_manuscript_blind/itt-emotion_blind_V6-6.tex
Getting everything ready for sending off

--- 2021-02-27 1_manuscript/itt-emotion.tex
@@
 
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
+        \author{REDACTED}
+
+        \authorrunning{REDACTED}
+
+        \institute{REDACTED}
 
@@
 
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  Conflict of interest: none
+  REDACTED
 

### 2021-03-31 2_revisions/V6_ITT_major_revision/0_coverletter/itt-emotion-coverletter.tex
Add new stuff V6 to revisions history

--- 2020-11-26 0_coverletter/itt-emotion-coverletter.tex
@@
 
-We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.
+We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach" for further review by Information Technology \& Tourism.
 
-We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further.
-This was a minor revision, with a few additions to the reviewed literature.
+We appreciate the consideration by your journal.
+In this revision, we were asked to make the text more concise and to review the English grammar.
+We performed a full check to the manuscript to remove sections of text that weren't necessary, made the text more concise and organized a few paragraphs differently, as well as making a few paragraphs belong to a new section in our discussion to avoid going off topic.
+We also improved on the abstract to make it more concise and appealing.
 
-As stated before, We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels.
-We discuss theories on the reason behind this in our revised paper.
-We also found that Chinese tourists in Japan are interested in shopping at all price ranges of hotels, while Western tourists are more inclined to shop when staying in middle to high-priced hotels.
-
-We believe this was an appropriate response to the minor revision, and hope we continue to be in your consideration.
+We believe this was an appropriate response to the major revision, and hope we continue to be in your consideration.
 

### 2021-03-31 2_revisions/V6_ITT_major_revision/1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,0 +1,1 @@
+../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-6.tex --compile --clean --view

### 2021-03-31 1_manuscript/cur_dir_my_latexdiff.sh
First edit draft to check by sensei

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V5.tex itt-emotion_V6-6.tex --compile --clean --view
+../my_latexdiff.sh itt-emotion_V6-6.tex itt-emotion.tex --newversion="7-0" --compile --clean --view

### 2021-04-12 1_manuscript/cur_dir_my_latexdiff.sh
7-1 after nonaka check, check again

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V6-6.tex itt-emotion.tex --newversion="7-0" --compile --clean --view
+../my_latexdiff.sh itt-emotion_V6-6.tex itt-emotion.tex --newversion="7-1" --compile --clean --view

### 2021-04-13 0_manuscript_blind/itt-emotion_blind_V7-2.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

--- 2021-02-27 0_manuscript_blind/itt-emotion_blind_V6-6.tex
@@
 
-  We analyzed expectations and satisfaction factors in Chinese and Western cultures, comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
-  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors, and then used them to classify a more extensive data set with an SVM.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
-  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior.
-We also found that the lack of a Chinese-friendly environment for Chinese customers and the smell of cigarettes for Western ones can be disappointing factors of their stay.
+  Since culture influences expectations, perceptions, and satisfaction, a cross-culture study is necessary to understand the differences between Japan's biggest tourist populations, Chinese and Western tourists.
+  However, with ever-increasing customer populations, this is hard to accomplish without extensive customer base studies.
+There is a need for an automated method for identifying these expectations at a large scale.
+For this, we used a data-driven approach to our analysis.
+  Our study analyzed their satisfaction factors comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
+  We collected hotel reviews and extracted keywords to classify the sentiment of sentences with an SVC.
+We then used dependency parsing and part-of-speech tagging to extract nouns tied to positive adjectives.
+  We found that Chinese tourists consider room quality more than hospitality, whereas Westerners are delighted more by staff behavior.
+Furthermore, the lack of a Chinese-friendly environment for Chinese customers and cigarette smell for Western ones can be disappointing factors of their stay.
   As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.
@@
 Thus, it could be theorized that their satisfaction factors should be different.
+
   The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations.
 This diversity means that the expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  Our study focuses on Western and Chinese tourists, considering their numbers.
-Chinese tourists accounted for 25.63\% of the tourist population.
+Cultural backgrounds have a decisive role in aspects of satisfaction and in the perceptions of quality \cite[][]{mattila1999role,winsted1997service}, or behavioral intentions \cite[][]{liu2001relationships}, such as the difference in Westerners and Asians in their willingness to pay more \cite[][]{LEVY2010319}.
+Since a difference in cultural background can also heavily influence the expectations of customers, as well as their perceptions of quality, the difference between these two can be smaller or larger depending on the culture in reaction to the same service.
+
+  For a growing industry with increasing cultural diversity, it is essential to identify the cross-culture expectations of customers in order to provide the appropriate services, cater to these expectations to ensure and increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
+
+  In 2017, Chinese tourists accounted for 25.63\% of the tourist population.
 On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}.
-The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
+The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon, \cite[][]{sun2017}.
 Despite this, many tourist-behavior analyses have been performed only involving Western subjects.
+Yet, it is known that Western and Asian customers are heavily differentiated\cite[][]{LEVY2010319}.
 As such, a knowledge gap existed until recent decades.
+Considering the numbers of inbound tourists in Japan and our team's language capabilities, our study focuses on Western and Chinese tourists.
 
@@
 Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
-For this, we used a data-driven approach to our analysis.
+
+  However, with ever-increasing customer populations, this is hard to accomplish without extensive studies of the customer base.
+There is a need for an automated method for identifying these expectations at a large scale.
+Our study intends to answer the need for such a methodology utilizing machine learning and natural language processing of large amounts of data.
+For this, we used a data-driven approach to our analysis, taking advantage of hotel review data.
+With this methodology, we explore the expectations and needs for the two most differing cultures currently interacting with the hospitality industry in Japan.
 
@@
 
+  With the knowledge that cultural background influences expectations in customers, which is the basis for satisfaction, it becomes important to know the difference in factors influencing satisfaction and dissatisfaction between the most differing and numerous tourist populations in a given area.
+
   This study aims to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels across several price ranges.
@@
 \section{Theoretical background and hypothesis development}\label{theory_hypothesis}
+
+  \subsection{Cultural influence in expectation and satisfaction}\label{theory_expectations}
+
+    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
+\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
+It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
+As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
+It can also be said that satisfaction stems from the perceptions of quality in comparison to these expectations.
+
+    These differences in customers' backgrounds can be summed up in cultural differences as well.
+In the past, satisfaction and perceived service quality have been found to be influenced by cultural differences \cite[e.g.][]{mattila1999role, winsted1997service}.
+Service quality perceptions have been studied via measurements such as SERVQUAL \cite[e.g.][]{armstrong1997importance}.
+
+    Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past as well \cite[e.g.][]{MATTILA201910, LEVY2010319, donthu1998cultural}, such as comparing individualism vs.
+collectivism, high context vs.
+low context, uncertainty avoidance, among other factors.
+While culture as a concept is difficult to quantify, some researchers have tried to use these and more dimensions to measure cultural differences, such as the six dimensions described by \cite{hofstede1984culture}, or the nine dimensions of the GLOBE model \cite[][]{house1999cultural}.
+
+    These cultural dimensions are more differentiated in Western and Asian cultures \cite[][]{LEVY2010319}.
+Our study being located in Japan, it stands to reason that the differences in expectations between Western tourists and Asian tourists should be understood in order to provide a good service.
+However, even though geographically close, Japanese and Chinese cultures are both very different when it comes to customer service.
+This is why our study focuses on the difference between Chinese and Western customers in Japan.
+The contrasting cultural backgrounds between Chinese and Western customers will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
+In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
+
+    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
+Therefore, it could be that some factors do not appear in the other reviews at all.
+For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
+Therefore, we must measure their differences or similarities at their common ground as well.
+
+    \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
+
+    We reviewed the importance of expectations in the development of satisfaction and dissatisfaction and the influence that cultural backgrounds have in shaping these expectations.
+This is true for overall satisfaction for the service as a whole, as well as individual elements that contribute to satisfaction.
+
+    In this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
+For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
+However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
+In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
+Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
+They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
+This definition of satisfaction does not allow us to examine overall customer satisfaction.
+However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
+In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
+Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
+On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
+
+    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
+1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
+The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
+However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
+There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
+This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
+However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
 
@@
 
-    However, Japanese hospitality is based on the Japanese culture.
+    However, Japanese hospitality is based on Japanese culture.
 Different cultures interacting with it could provide a different evaluation of it.
@@
 
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers then have very different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-Therefore, we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
+  \subsection{Customer expectations beyond service and hospitality}\label{theory_soft_hard}
+
+    Staff behavior, hospitality and service, and therefore \textit{Omotenashi}, are all soft attributes of a hotel.
+That is, they are non-physical attributes of the hotel, and as such, they are practical to change through changes in management.
+While it is important to know this, it is not known if the cultural differences between Chinese and Western tourists also influence other expectations and satisfaction factors, such as the hard factors of a hotel.
+
+    Hard factors are attributes uncontrollable by the hotel staff, which can play a part in the customers' choice behavior and satisfaction.
 Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
 
-    This leads to another couple of research questions:
+    Besides the facilities, many other aspects of the experience, expectation, and perception of the stay in a hotel can contribute to the overall satisfaction, as well as individual satisfactions and dissatisfactions.
+However, previous research focuses more on these soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}.
+Because of this gap in knowledge, we decided to analyze the differences in cultures regarding both soft and hard attributes of a hotel.
+
+    This leads to two of our research questions:
 
@@
     \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
+    To what degree do satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
     \end{rsq}

### 2021-04-13 0_titlepage/itt-emotion-titlepage.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

@@
         \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
                     \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                    % Corresponding Author %  \\
-                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
+                    \hspace*{1em} ORCID: 0000-0002-6437-0866
                 \and
                     \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    % Nagaoka University of Technology, Nagaoka, Japan \\
                     \hspace*{1em} \email{mendoza.espana@gmail.com}
@@
                     \hspace*{1em} Toru Hiraoka \at
-                    % University of Nagasaki, Nagasaki, Japan \\
                     \hspace*{1em} \email{hiraoka@sun.ac.jp}
                 \and 
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
+                    \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
+                \at 
+                    \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
         }

### 2021-04-13 1_manuscript/Z_latexdiff-helpers/V6-6--V7-2-diff_omotenashi_3.3.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

--- 2021-02-27 0_manuscript_blind/itt-emotion_blind_V6-6.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
-\begin{document}
-
-\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{REDACTED}
-
-        \authorrunning{REDACTED}
-
-        \institute{REDACTED}
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
-
-\begin{abstract}
-
-  We analyzed expectations and satisfaction factors in Chinese and Western cultures, comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
-  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors, and then used them to classify a more extensive data set with an SVM.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
-  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior.
-We also found that the lack of a Chinese-friendly environment for Chinese customers and the smell of cigarettes for Western ones can be disappointing factors of their stay.
-  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Inbound international tourism has been increasingly affecting Japanese economy \cite[][]{jones2009}.
-A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-
-  Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}.
-Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations.
-This diversity means that the expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  Our study focuses on Western and Chinese tourists, considering their numbers.
-Chinese tourists accounted for 25.63\% of the tourist population.
-On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}.
-The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
-Despite this, many tourist-behavior analyses have been performed only involving Western subjects.
-As such, a knowledge gap existed until recent decades.
-
-  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations, namely, the scale and sampling.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose.
-These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study.
-This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
-For this, we used a data-driven approach to our analysis.
-
-  Owing to the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining and machine learning technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
-These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
-We take advantage of the wide availability of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
-Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
-We use machine learning to automatically classify sentences in the online reviews as positive or negative opinions on the hotel.
-We then perform a statistical extraction of the topics that most concern the customers of each population.
-
-\section{Research objective}\label{research_objective}
-
-  This study aims to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels across several price ranges.
-We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as attributes relating to physical and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
 \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
@@
 
-    However, Japanese hospitality is based on the Japanese culture.
+    However, Japanese hospitality is based on \DIFdelbegin \DIFdel{the }\DIFdelend Japanese culture.
 Different cultures interacting with it could provide a different evaluation of it.
@@
     \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers then have very different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-Therefore, we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}.
-However, studies focusing on only the behavior of this subset of tourists are the majority.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and not Chinese-specific.
-Meanwhile, the current Chinese economic boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, the change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three studies focus on the U.S.A.
-culture, whereas our study focuses on the Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done within the context of tourists from three countries staying in hotels across the world.
-The second study chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third study analyzed restaurants in Beijing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, customers could either hold their satisfaction to this hospitality regardless of their culture or value other factors more depending on their cultural differences.
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many countries.
-The general satisfaction score was noticed to be different among those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations; the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study analyzes the satisfaction and dissatisfaction factors cross-culturally and compares them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, an unprecedented quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, or a critical one.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    Our study used an algorithm for sentiment analysis called a Support Vector Machine (SVM), a supervised machine learning used for binary classification.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled training data to detect patterns in it and use them to establish a method for classifying other unlabeled data automatically.
-Machine learning can also be unsupervised, where there is no pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus, our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
-These qualities determine why, similar to actual mining; data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason is that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
-
-\section{Methodology}\label{method}
-
-  We extracted a large number of text reviews from the site \textit{Ctrip}, with mostly mainland Chinese users, and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that relate to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to train an optimized Support Vector Classifier (SVC) to perform a binary emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and the nouns they refer to.
-We split the dataset into price ranges to observe the differences in keyword usage between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the \textit{Ctrip} data collection, reviews from a total of \num[group-separator={,}]{5774} hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, to make the data comparisons fair, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest and highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites, depending on the hotel.
-Regardless of the reason, we chose the highest-priced room since it can be an indirect indicator of the hotel's class.
-After filtering, the datasets contained \num[group-separator={,}]{557} hotels in common.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-
-    The price for a night in these hotels ranges from cheap capsule hotels at 2000 yen per night to high-end hotels 188,000 yen a night at the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    We needed to analyze the grammatical relationship between words, be it English or Chinese, to understand the connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In English texts, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library for the English texts.
-
-    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVC \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVC keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVC.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives but can also increase false negatives.
-Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVC performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      \resizebox{0.65\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      \resizebox{0.65\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVC is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used a linear kernel for the SVC, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a data point, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVC learning algorithm, each data point classified incorrectly alters the weight vector to correctly classify new data.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    We observed the top 10 satisfaction and dissatisfaction keywords with the highest frequencies of emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but would require significant infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not the hotel's physical structure are considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word described unchangeable physical factors by the staff or management, we consider them hard.
-If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the usage percentage in each context.
-If it was not clear from the word or the pairing alone, we declared it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always deemed 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
-\section{Results}\label{results}
-
-  \subsection{Experimental results and answers to research questions}
-
-    Our research questions were related to two issues.
-Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture.
-
-    Observing the top-ranking positive keywords in Chinese reviews, as shown in Tables \ref{tab:freq_res_pos} and Table \ref{tab:adj_zh_pos}, it was revealed that, while service, cleanliness, and breakfast were praised in most hotels, the location was more important when observing the pairings.
-Hard attributes were abundant lower on the lists.
-The negative keywords in Table \ref{tab:freq_res_neg} indicate that a lack of a Chinese-friendly environment was perceived, although there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
-However, most complaints were about the hotel's price, which included all of the price ranges; therefore, the price was the primary concern for Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-
-    We can also observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20,000–30,000 yen per night.
-
-    With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels.
-Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
-On the other hand, English-speaking tourists were more responsive to soft attributes, either positively or negatively.
-In the case of negative keywords, they were more concerned about the hotel's soft attributes.
-
-    One factor that both populations had in common is that, when perceiving the hotel negatively, the ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old),'' ``dated,'' ``outdated,'' or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel were surprisingly criticized across most price ranges.
-However, this is a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists: A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels.
-The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms.
-Other mentions included big markets nearby or a big bed.
-Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel.
-When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel.
-Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).''
-
-    In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' However, they are interchangeable if natural hot spring water is used in artificially made tiled bath facilities.
-It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude.
-It could be a cultural shock for many tourists but a fundamental attraction for many others.
-
-    Chinese customers are satisfied with the size of the room or bed; however, it is not trivial to change this.
-In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples.
-In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair.
-Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers, and they were mostly pleased when their expectations were fulfilled.
-
-    A key soft satisfaction factor was the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' referring to the hotel commodities, was frequently used in positive texts compared to other food-related words across all price ranges, albeit at different priorities in each of them.
-For this reason, we regard it as an important factor.
-From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings.
-It is only slightly lower in other categories, although it is not depicted in the table.
-Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists: A friendly face and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the highest-ranked of these three, ranking second for satisfied customers across most price ranges and only third in one of them.
-The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean'', so we examined its word pairings.
-Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general.
-When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors, and ``uncomfortable'' was high on the dissatisfaction factors.
-The words were paired with nouns such as ``bed,'' ``room,'' ``pillow,'' and ``mattress,'' when they generally referred to their sleep conditions in the hotel.
-    It seems that Western tourists were particularly sensitive about the hotels’ comfort levels and whether they reached their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    Albeit lower in priority, the price range of 15,000 to 20,000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.
-
-  \subsection{Tobacco, an unpleasant smell in the room}\label{disc:tobacco}
-
-    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes.
-Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
-For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
-Tobacco was referenced singularly as ``cigarette'', but also in word pairs in Table \ref{tab:adj_en_neg} as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
-Another common complaint was that there were no nonsmoking facilities available.
-The smell of smoke can completely ruin some customers’ stay, leading to bad reviews, thereby lowering the number of future customers.
-
-    In contrast, Chinese customers seemed not to be bothered by this.
-Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
-This was derived from a sample of 170,000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Although it has one of the world’s largest tobacco markets, tobacco use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas.
-Many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
-
-    Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele.
-To cater to all kinds of customers, including Western and Asian, Japanese hotels must provide spaces without tobacco smell.
-Even if the smoke does not bother a few customers, the lack of such a smell will make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transportation, and availability of nearby shops proved to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings in Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location,'' ``great location,'' and ``great view'' as well as single keywords ``location'' and ``shopping'' for English speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic),'' ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping),'' ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway),'' and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signify that the hotel's location was a secondary but still important point for their satisfaction.
-However, since this is a hard attribute, it is not often considered in the literature.
-By examining examples from the data, we recognized that most customers were satisfied if the hotel was near at least two of the following facilities: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transportation system.
-During rush hour, the subway is crowded with commuters, and trains and subway stations create a confusing public transportation map for a visitor in Tokyo.
-Buses are also available, albeit less used than rail systems in metropolitan cities.
-These three means of transportation are usually affordable in price.
-There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis.
-The latter is a luxury in Japan compared to other countries.
-In Japan, taxis provide a high-quality experience with a matching price.
-Therefore, for people under a budget, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity for tourists, using taxis only as a last resort.
-
-    Japanese convenience stores are also famous worldwide because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs.
-If some trouble occurs, or a traveler forgot to pack a particular item, it is most certain that they can find it.
-
-    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, and perhaps offering guide maps and information about these as an appeal point could result in greater satisfaction.
-
-\section{Discussion}\label{discussion}
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To date, scholars have been correcting our historical bias towards the West.
-Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction.
-In other words, tourists of a particular culture have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world.
-Our study explores whether such an environment can affect different cultures equally or whether it is attractive only to certain cultures.
-
-    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists.
-As explained earlier in this paper, Japan is well known for its customer service.
-Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
-Even in the cheapest convenience store, the level of hospitality is starkly different from Western culture and perhaps unexpected.
-In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
-
-    However, the negative English keywords indicate that a large part of the dissatisfaction with Japanese hotels stemmed from a lack of hygiene and room cleanliness.
-Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette smell and lack of general hygiene.
-\cite{kozak2002} also proved that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In contrast, our research revealed that words related to cleanliness were mostly linked to dissatisfaction.
-We could assert that Westerners had a high standard of room cleanliness compared to their Chinese counterparts.
-
-    According to previous research, Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, according to our results, Chinese tourists were more concerned about room quality rather than hospitality, staff, or service.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great),'' we can see that they praise staff, service, and breakfast.
-By observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we discover that Chinese customers were more satisfied with hard attributes compared to Western tourists, who seemed to be meeting more than their expectations.
-
-    It could be considered that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction derived is less than that if it was expected.
-In contrast, some tourists report a ``nice surprise'': when an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two reactions.
-The ``nice surprise'' reaction fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a need high enough for the Chinese population, thereby resulting in less satisfaction.
-For greater satisfaction, a need must be met.
-However, the word ``not bad'' is at the top of the list in most price ranges, and one of the uses is related to service.
-Thus, we cannot conclude that they were not satisfied with the service.
-Instead, they held other factors at a higher priority; thus, the keyword frequency was higher for other pairings.
-
-    Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about their treatment that are not being met, even in this high-standard hospitality environment.
-This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging.
-Chinese language pamphlets and Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup, etc.), or the treatment towards Chinese people, could be examples of these accommodations.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-However, this issue is not exclusive to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study attempted to determine the answer.
-It is possible that Chinese customers had high-grade hospitality and were equally satisfied with Westerners.
-In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear which of these two is most likely from our results.
-However, competing in hospitality and service includes language services, especially in the international tourism industry.
-Better multilingual support can only improve the hospitality standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, multilingual support is beneficial.
-Proposals for this endeavor include hiring Chinese-speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction \cite[e.g.,][]{shanka2004,choi2001}.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel.
-However, hard attributes are not usually analyzed in satisfaction studies.
-It is important to consider both kinds of attributes.
-If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future.
-Otherwise, if the satisfaction was related more to hard attributes overall, hotels should be built considering the location while minimizing other costs.
-Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors.
-The rates are similar for most price ranges except the highest-priced hotels.
-However, two of these soft attributes are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
-Chinese tourists may expect spaciousness and cleanliness when coming to Japan.
-The expectation may be due to reputation, previous experiences, or cultural backgrounds.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword was found for hotels priced at more than 20,000 yen per night.
-
-    In contrast, English speakers are mostly satisfied with the hotels' soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
-The exception to this is the hard attribute that is the hotels' location, which is consistently around the middle of the top 10 lists for all price ranges.
-
-    For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
-However, English-speaking customers complained less about the price in lower-priced hotels.
-In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
-A study on Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this has more to do with the pricing of hotels in Japan than with Chinese culture.
-In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can charge half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be improved; this is true for all price ranges.
-The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, these considerations can be costly.
-However, once the hotel's location and construction are set, only a few changes can be made to satisfy Chinese customers further.
-As mentioned previously, Chinese language availability is a soft attribute that can be improved with staff and training investment.
-
-    Western tourists are mainly dissatisfied with soft attributes.
-This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel.
-Improvement scope for Western tourists is more extensive than that for their Chinese counterparts.
-As such, it presents a larger investment opportunity.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change across differently priced hotels is the change in voice when describing satisfaction.
-We noticed this by observing the adjective-noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for higher-priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Conversely, the failure of meeting expectations causes dissatisfaction.
-We can assume that a customer that pays more for a higher-class experience has higher expectations.
-For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
-In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
-
-    We argue that these are two different kinds of expectations: logical and emotional.
-In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
-In contrast, in the second case, customers have a vague idea of having a positive experience but do not measure it against any standard.
-For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
-Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
-Thus, hospitality and service enhance the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
-For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
-It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among \textit{souvenir} items representative of the culture or places that they visit \cite{japan2014consumption}.
-Furthermore, Chinese tourists’ choice to shop in Japan is more related to the quality of the items rather than their relation to the tourist attractions.
-Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities compared to Chinese tourists.
-
-    Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
-In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
-
-    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
-This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Cross-culture analysis of expectations and satisfaction}\label{disc:culture}
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preferences of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared with respect to their expectations of service quality and analyzed based on Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-The previous study states that, although culture has no specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism–-collectivism}, \textit{masculinity–femininity}, and \textit{long-term-–short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-
-    However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism as well as considering a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also consider some of Hofstede's dimensions and replace them with others, making a total of nine dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity–-femininity} dimension, for example, is proposed to be instead of two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Such gender stereotypes have also been the subject of critique on Hofstede's model\cite[][]{jeknic2014gender}.
-We agree with these critiques and thus avoid considering such stereotypes in our discussion.
-
-    For our purposes of contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese, kim2000}.
-These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that such differences exist \cite[][]{armstrong1997importance}.
-
-    The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-Nevertheless, one could argue a Chinese cultural attribute emphasizes that the environment and the location affect satisfaction rather than the treatment they receive.
-
-    A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances rather than the environment.
-According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-Customers of high uncertainty avoidance carefully plan their travel and thus have higher expectations towards service.
-In contrast, customers of lower uncertainty avoidance do not take risks in their decisions and thus face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Differences in another factor, power distance, were also noted when using  Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study reached two important conclusions: one about hospitality and cultural differences and another about managerial decisions towards two different populations.
-Overall, Chinese tourists did not attach much importance to hospitality and service factors.
-Instead, they focused on the hard attributes of a hotel.
-In particular, they were not satisfied with hospitality as much as Western tourists were; otherwise, they felt that basic language and communication needs were not met; thereby, they were not much satisfied.
-Western tourists were highly satisfied with Japanese hospitality and preferred soft attributes to hard ones.
-
-    The other conclusion is that managerial decisions could mostly benefit Western tourists, except for language improvements and breakfast inclusion could satisfy both groups.
-As mentioned earlier in this paper, Westerners are ``long-haul'' customers, spending more of their budget on lodging than Asian tourists \cite[][]{choi2000}.
-With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-In addition, breaking the language barrier is one of the few strategies to satisfy both groups.
-Recently, Japan has been facing an increase in Chinese students as well as students of Western universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which could be managerially improved for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs could satisfy both customer types.
-We suggest investing in making the facilities tobacco-free.
-Our results are also divided by price ranges; thereby, a hotel manager could consider which analysis suits their hotel the most.
-Hard attributes are difficult to change; however, improvements in service can be made to accompany these attributes.
-For example, transportation guides for foreigners that might not know the area could increase satisfaction.
-
-    The managers must consider their business model for implementing the next strategy.
-One option could be attracting more Chinese customers with their observed low budgeting.
-Another could be attracting more big-budget Western customers.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even for an increased price per night.
-On the other hand, hotels might be deemed costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  In this study, we analyzed keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand these words' context by using a dependency parser and observing the related nouns.
-However, a limitation is that it analyzed solely the words directly related to each keyword and did not search for further connections.
-This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking,'' we extracted ``good room'' and ``lacking food'' but did not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a Western-style five-star resort and a high-end Japanese style \textit{ryokan}.
-Services offered in these hotels are of high quality, albeit very different.
-Nevertheless, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
-
-  An essential aspect of this study is that we focused on the satisfaction and dissatisfaction towards the expectations of individual aspects of the hotels.
-This gave us insight into the factors that hotel managers can consider.
-However, each customer's overall satisfaction was not measured since it would require methods that are out of the scope of this paper.
-Another limitation is that further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate these topics further.
-We plan to extend our data to research different trends and regions of Japan, different kinds of hotels, and customers traveling alone or in groups, whether for fun or for work.
-Another point of interest in this study's future work is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, we analyzed the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-We extracted keywords from their online reviews on \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract common pairs of adjectives and nouns as well as single words.
-We divided these data by sentiment and hotel price range (most expensive room/night).
-
-  We found that Western tourists were most satisfied with staff behavior, cleanliness, and other soft attributes.
-However, Chinese customers had other concerns for their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
-We found that the two cultures had different reactions to the hospitality environment and the prices.
-Thus, we discussed two possible theories on why Chinese tourists responded differently from Westerners in the environment of \textit{omotenashi}.
-One theory is that, although they were treated well, their experience was deteriorated by language or culture barriers.
-The second possible theory is that they reacted to hospitality differently since they did not have the same expectations.
-We theorized that a lack of expectations could result in lessened satisfaction than that to the same service if expected.
-On the other hand, even when they held high expectations in a high-priced hotel, Japanese hospitality exceeded Western tourists’ expectations, judging by their vocabulary for expressing their satisfaction.
-We considered that Western tourists were more reactive to hospitality and service factors Chinese tourists.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, that is, a hotel's hard and soft attributes.
-Hard attributes are physical and environmental elements, and as such, are impractical elements to change.
-In contrast, soft attributes can be changed via management and staff by an improvement in services or amenities.
-We found that, for satisfaction, Western tourists favored soft attributes in contrast to Chinese tourists, who were more interested in the hard attributes of hotels across all the price ranges consistently.
-For dissatisfaction, Western tourists were also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction derived from both hard and soft attributes evenly.
-
-  One approach for hotel managers is to work to satisfy Chinese tourists more, who dedicate a lower percentage of their budget to hotels but are more numerous.
-They are less satisfied with soft attributes but have an identifiable method for improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach was focused on the cleanliness, comfort, and tobacco-free space expected by Western tourists.
-``Long-haul'' Western tourists, who spend almost half of their budget on hotels with this strategy, were favored.
-Although Westerners are less in number than Chinese tourists, it could be proven that they have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-
-\begin{acknowledgements}
-
-  REDACTED
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
-\end{document}

### 2021-04-13 1_manuscript/Z_latexdiff-helpers/omotenashi_3.3_V6-6.tex
V7-2 after showing to Nonaka again, preparing all files, cover letter still to be written yet

--- 2021-02-27 1_manuscript/itt-emotion.tex
@@
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended,natbib]{svjour3}       % onecolumn (second format)
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        %\documentclass[twocolumn]{svjour3}          % twocolumn
-        %
-        \smartqed  % flush right qed marks, e.g. at end of proof
-
-        % For the ORCID icon
-        \usepackage{scalerel}
-        \usepackage{tikz}
-        \usetikzlibrary{svg.path}
-
-        \definecolor{orcidlogocol}{HTML}{A6CE39}
-        \tikzset{
-          orcidlogo/.pic={
-            \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
-            \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
-                         svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
-                         svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
-          }
-        }
-
-        \newcommand\orcidicon[1]{\href{https://orcid.org/#1}{\mbox{\scalerel*{
-        \begin{tikzpicture}[yscale=-1,transform shape]
-        \pic{orcidlogo};
-        \end{tikzpicture}
-        }{|}}}}
-
-        \usepackage{lineno, hyperref}
-        \usepackage{array, pbox}
-        \usepackage{mathtools}
-        \usepackage{caption}
-        \usepackage{subcaption}
-        \usepackage{graphicx}
-
-        % To use chinese characters
-        \usepackage{CJKutf8}
-
-        % To add an appendix page
-        \usepackage[page, title]{appendix}
-
-        % To insert commas into large numbers automatically
-        \usepackage{siunitx}
-
-        % To add research questions
-        \usepackage{ntheorem}
-        \theoremseparator{:}
-        \newtheorem{rsq}{Research Question}
-
-        % To add subrsq theorems
-        \makeatletter
-        \newcounter{subrsq} 
-        \let\savedc@rsq\c@rsq
-        \newenvironment{subrsq}
-         {%
-          \setcounter{subrsq}{0}%
-          \stepcounter{rsq}%
-          \edef\saved@rsq{\thersq}% Save the current value of rsq
-          \let\c@rsq\c@subrsq     % Now rsq is subrsq
-          \renewcommand{\thersq}{\saved@rsq\alph{rsq}}%
-         }
-         {}
-        \newcommand{\normrsq}{%
-          \let\c@rsq\savedc@rsq % revert to the old one
-          \renewcommand\thersq{\arabic{rsq}}%
-        } 
-        \makeatother
-
-        % To add the envelope symbol in Corresponding Author using % \Letter
-        \usepackage{marvosym}
-
-        % to add superscripts to mark the institute of authors
-        % patch \maketitle:
-        \newcommand*{\affaddr}[1]{#1} % No op here. Customize it for different styles.
-        \newcommand*{\affmark}[1][*]{\textsuperscript{#1}}
-
-        % For table formatting
-        \usepackage{multirow}
-        \usepackage[normalem]{ulem}
-        \useunder{\uline}{\ul}{}
-
-        % For landscape tables
-        \usepackage{lscape}
-
-        \modulolinenumbers[5]
-
-        \journalname{Information Technology \& Tourism}
-
-        \bibliographystyle{spbasic}
-
-\begin{document}
-
-\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
-
-% Fold 1
-  % Fold 2
-    % Fold 3
-      % Fold 4
-        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}
-
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
-
-        \date{Received: date / Accepted: date}
-        % The correct dates will be entered by the editor
-
-        \maketitle
-
-\begin{abstract}
-
-  We analyzed expectations and satisfaction factors in Chinese and Western cultures, comparing soft attributes, such as service, with hard attributes, such as location and facilities, and studied different price ranges.
-  We collected our data with web crawling, labeled a sample, applied Shannon's entropy to extract these factors, and then used them to classify a more extensive data set with an SVM.
-We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to positive adjectives.
-  We found that Chinese tourists are concerned more with room quality than hospitality, whereas, Western tourists are delighted more by the staff behavior.
-We also found that the lack of a Chinese-friendly environment for Chinese customers and the smell of cigarettes for Western ones can be disappointing factors of their stay.
-  As one of the first studies in the tourism field to use the high-standard Japanese hospitality environment for this analysis, our cross-cultural study contributes to both the theoretical understanding of satisfaction and suggests practical applications and strategies for hotel managers.
-
-  \keywords{Sentiment Analysis\and Hotels and Lodging\and Text Mining\and Chinese\and English\and Satisfaction and Dissatisfaction Factors}
-
-\end{abstract}
-
-\linenumbers
-
-\section{Introduction}\label{intro}
-
-  Inbound international tourism has been increasingly affecting Japanese economy \cite[][]{jones2009}.
-A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}.
-
-  Japan’s hospitality has been known historically to be of the highest quality.
-\textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}.
-Consequently, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor.
-However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}.
-Thus, it could be theorized that their satisfaction factors should be different.
-The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations.
-This diversity means that the expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  Our study focuses on Western and Chinese tourists, considering their numbers.
-Chinese tourists accounted for 25.63\% of the tourist population.
-On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}.
-The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
-Despite this, many tourist-behavior analyses have been performed only involving Western subjects.
-As such, a knowledge gap existed until recent decades.
-
-  In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}.
-The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples.
-These studies, although valid, can have limitations, namely, the scale and sampling.
-In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or traveling with a single purpose.
-These studies' limited scope often leads to difficulties in observing cultural and language differences in a single study.
-This creates a need for large-scale cross-cultural studies for the increasing Asian and Western tourist populations.
-It could be said that Westerners account for a smaller portion of the tourist population compared to Asians.
-However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels.
-In comparison, their Asian counterparts only spend 25\% of their budget on hotels.
-Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.
-For this, we used a data-driven approach to our analysis.
-
-  Owing to the advent of Web 2.0 and customer review websites, researchers realized the benefits of online reviews for research, sales  \cite[][]{ye2009, basuroy2003}, customer consideration \cite[][]{vermeulen2009} and perception of services and products \cite[][]{browning2013}, among other effects of online interactions between customers \cite[e.g.][]{xiang2010, ren2019}.
-Consequently, information collected online is being used in tourism research for data mining analysis, such as opinion mining \cite[e.g.][]{hu2017436}, predicting hotel demand from online traffic \cite[][]{yang2014}, recommender systems \cite[e.g.][]{loh2003}, and more.
-Data mining and machine learning technologies can increase the number of manageable samples in a study from hundreds to hundreds of thousands.
-These technologies can not only help confirm existing theories but also lead to finding new patterns and to knowledge discovery \cite[][]{fayyad1996data}.
-
-  In this study, we evaluate the satisfaction factors of two essential tourist populations that are culturally different from Japan: Chinese and Western tourists.
-We take advantage of the wide availability of online reviews of Japanese hotels by both Mainland Chinese tourists posting on \textit{Ctrip} and Western, English-speaking tourists posting on \textit{TripAdvisor}.
-Based on these data, we can confirm existing theories regarding the differences in tourists’ behavior and discover factors that could have been overlooked in the past.
-We use machine learning to automatically classify sentences in the online reviews as positive or negative opinions on the hotel.
-We then perform a statistical extraction of the topics that most concern the customers of each population.
-
-\section{Research objective}\label{research_objective}
-
-  This study aims to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels across several price ranges.
-We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings.
-More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction.
-We define hard attributes as attributes relating to physical and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate.
-In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.
-
-\section{Theoretical background and hypothesis development}\label{theory_hypothesis}
-
 \subsection{Japanese hospitality and service: \textit{Omotenashi}}\label{theory_omotenashi}
@@
     \end{subrsq}
-
-  \subsection{Customer satisfaction and dissatisfaction towards individual factors during hotel stay}\label{theory_satisfaction}
-
-    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service.
-\cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry.
-It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer.
-As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction.
-Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}.
-Western and Chinese customers then have very different backgrounds and cultures.
-These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have.
-In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.
-
-    Because of their different origins, expectations, and cultures, it stands to reason Chinese and Western tourists could have completely different factors to one another.
-Therefore, it could be that some factors do not appear in the other reviews at all.
-For example, between different cultures, it can be that a single word can express some concept that would take more words in the other language.
-Therefore, we must measure their differences or similarities at their common ground as well.
-
-    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious.
-For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter.
-However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night.
-In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed.
-Then, the same customer might have packed their toiletries, thinking that the amenities might not include those.
-They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation.
-This definition of satisfaction does not allow us to examine overall customer satisfaction.
-However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole.
-In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects.
-Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service.
-On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.
-
-    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g.
-1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}.
-The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction.
-However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction.
-There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}.
-This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction.
-However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.
-
-    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing on facilities \cite[e.g.][]{shanka2004, choi2001}.
-However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction.
-Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.
-
-    This leads to another couple of research questions:
-
-    \begin{subrsq}
-    \begin{rsq}
-    \label{rsq:hard_soft}
-    To what degree does satisfaction and dissatisfaction stem from hard and soft attributes of the hotel?
-    \end{rsq}
-
-    \begin{rsq}
-    \label{rsq:hard_soft_diff}
-    How differently do Chinese and Western customers perceive hard and soft attributes of the hotel?
-    \end{rsq}
-    \end{subrsq}
-
-    The resulting proportions of hard attributes to soft attributes for each population could measure how much the improvement of management in the hotel can increase future satisfaction in customers.
-
-  \subsection{Chinese and Western tourist behavior}\label{theory_zh_en}
-
-    % Asians vs. Western behavior
-    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries.
-Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}.
-However, studies focusing on only the behavior of this subset of tourists are the majority.
-To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists.
-One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money.
-Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels.
-Both groups tend to have high expectations for the overall facilities.
-Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.
-
-    One thing to note with the above Asian vs.
-Western analyses is that they were performed before 2000 and not Chinese-specific.
-Meanwhile, the current Chinese economic boom is increasing the influx of tourists of this nation.
-The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations.
-In turn, if we follow the definition of satisfaction in \cite{hunt1975}, the change in expectations could have influenced their satisfaction factors when traveling.
-Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports.
-However, our study of online reviews takes the data that the hotel customers uploaded themselves.
-This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies.
-Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.
-
-    More recent studies have surfaced as well.
-A cross-country study \cite[][]{FRANCESCO201924} using posts from U.S.A.
-citizens, Italians, and Chinese tourists, determined using a text link analysis that customers from different countries indeed have a different perception and emphasis of a few predefined hotel attributes.
-According to their results, U.S.A.
-customers perceive cleanliness and quietness most positively.
-In contrast, Chinese customers perceive budget and restaurant above other attributes.
-Another couple of studies \cite[][]{JIA2020104071, HUANG2017117} analyze differences between Chinese and U.S.
-tourists using text mining techniques and more massive datasets, although in a restaurant context.
-
-    These last three studies focus on the U.S.A.
-culture, whereas our study focuses on the Western culture.
-Another difference with our study is that of the context of the study.
-The first study \cite[][]{FRANCESCO201924} was done within the context of tourists from three countries staying in hotels across the world.
-The second study chose restaurant reviews from the U.S.A.
-and Chinese tourists eating in three countries in Europe.
-The third study analyzed restaurants in Beijing.
-
-    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically.
-Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents.
-In this environment, customers could either hold their satisfaction to this hospitality regardless of their culture or value other factors more depending on their cultural differences.
-Our study measures this at a large scale across different hotels in Japan.
-
-    % Universal behavior
-    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis.
-\cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample.
-\cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants.
-As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan.
-In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many countries.
-The general satisfaction score was noticed to be different among those countries.
-However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed.
-As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.
-
-    % Western behavior 
-    Regarding Western tourist behavior, a few examples can tell us what to expect when analyzing our data.
-\cite{kozak2002} found that British and German tourists' satisfaction determinants while visiting Spain and Turkey were hygiene and cleanliness, hospitality, the availability of facilities and activities, and accommodation services.
-\cite{shanka2004} found that English-speaking tourists in Perth, Australia were most satisfied with staff friendliness, the efficiency of check-in and check-out, restaurant and bar facilities, and lobby ambiance.
-
-    % Chinese behavior
-    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}.
-Different researchers have found that Chinese tourist populations have several specific attributes.
-According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities.
-\cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff.
-Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money.
-According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists.
-Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall.
-However, the younger generations seem to do so less than their older counterparts.
-
-    % Studies are not universal.
-    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable.
-We can see that depending on the study and the design of questionnaires and the destinations; the results can vary greatly.
-Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other.
-Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews.
-This means that the factors will be selected through statistical methods alone instead of being defined by the questionnaire.
-Our method allows us to find factors that we would not have contemplated.
-It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves.
-This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples.
-This study analyzes the satisfaction and dissatisfaction factors cross-culturally and compares them with the existing literature.
-
-    % Reviewer comparison table
-    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may further highlight our study and its merits.
-A contrast is shown in Table \ref{tab:lit-rev}.
-This table shows that older studies were conducted with surveys and had a different study topic.
-These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}.
-However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies.
-Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}.
-One important difference is the geographical focus of their studies.
-While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan.
-The focus on Japan is important because of its top rank in hospitality across all types of businesses.
-Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent.
-The number of samples in other text-mining studies is also smaller than ours in comparison.
-Apart from that, every study has a different text mining method.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Comparison between cross-culture or cross-country previous studies and our study.}
-      \label{tab:lit-rev}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{l|l|l|l|l|l|l|l|}
-        \cline{2-8}
-        \textbf{} &
-          \textbf{Bauer et.al (1993)} &
-          \textbf{Choi and Chu (2000)} &
-          \textbf{Kim and Lee (2000)} &
-          \textbf{Huang (2017)} &
-          \textbf{Francesco and Roberta (2019)} &
-          \textbf{Jia (2020)} &
-          \textbf{Our study} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Comparison objects}} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerns\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians\\ vs\\ Westerners\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Anglo-Americans \\ vs \\ Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ English-speakers\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}USA \\ vs \\ China \\ vs \\ Italy\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ US tourists\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Chinese \\ vs \\ Westerners\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study topic}} &
-          Changes in demand &
-          Satisfaction Levels &
-          Tourist Motivation &
-          \begin{tabular}[c]{@{}l@{}}Dining experience \\ of Roast Duck\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Perception and \\ Emphasis\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Motivation and \\ Satisfaction\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Satisfaction and\\ Dissatisfaction\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Geographical focus}} &
-          Asia Pacific region &
-          Hong Kong &
-          Global &
-          Beijing &
-          Multi-national &
-          Multi-national &
-          \textbf{Japan} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Industry}} &
-          Hotels &
-          Hotels &
-          Tourism &
-          Restaurant (Beijing Roast Duck) &
-          Hotels &
-          Restaurants &
-          Hotels \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study subjects}} &
-          Hotel managers &
-          Hotel customers &
-          \begin{tabular}[c]{@{}l@{}}Tourists arriving \\ in airport\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Diners \\ online reviews\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Hotel customers \\ online reviews\end{tabular} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Sample method}} &
-          surveys &
-          surveys &
-          survey &
-          text mining &
-          text mining &
-          text mining &
-          text mining \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Number of samples}} &
-          185 surveys &
-          540 surveys &
-          \begin{tabular}[c]{@{}l@{}}165 Anglo-American\\ 209 Japanese\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}990 Chinese reviews\\ 398 English reviews\end{tabular} &
-          9000 reviews (3000 per country) &
-          \begin{tabular}[c]{@{}l@{}}2448 reviews\\ (1360 Chinese)\\ (1088 English)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}89,207 reviews\\ (48,070 Chinese)\\ (41,137 English)\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Study method}} &
-          statistics &
-          VARIMAX &
-          MANOVA &
-          \begin{tabular}[c]{@{}l@{}}Semantic \\ Network \\ Analysis\end{tabular} &
-          Text Link Analysis &
-          \begin{tabular}[c]{@{}l@{}}Topic modeling \\ (LDA)\end{tabular} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}SVM, \\ Dependency Parsing\\ and POS tagging\end{tabular}} \\ \hline
-        \multicolumn{1}{|l|}{\textbf{Subject nationality}} &
-          \begin{tabular}[c]{@{}l@{}}Asians: \\ China,\\ Fiji,\\ Hong Kong,\\ Indonesia,\\ Malaysia,\\ Singapore,\\ Taiwan,\\ Guam,\\ Tahiti,\\ Thailand \\ \\ Westerners: Australia,\\ New Zealand\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}Asians:\\ China,\\ Taiwan,\\ Japan,\\ South Korea,\\ South-East Asia\\ \\ Westerners:\\ North America,\\ Europe,\\ Australia,\\ New Zealand\end{tabular} &
-          USA, Japan &
-          \begin{tabular}[c]{@{}l@{}}English-speakers: \\ U.K., U.S., Australia,\\ New Zealand, Canada,\\ Ireland\\ \\ Chinese-speakers: China\end{tabular} &
-          USA, China, Italy &
-          USA, China &
-          \begin{tabular}[c]{@{}l@{}}Chinese-speakers:\\ China\\ \\ English-speakers:\\ (U.K., U.S.,\\ Australia,\\ New Zealand,\\ Canada, Ireland)\end{tabular} \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Data mining, machine learning, knowledge discovery and sentiment analysis}\label{theory_data}
-
-    % Explain the discovery of theory inside the data
-    In the current world, data is presented to us in larger and larger quantities.
-Today's data sizes were commonly only seen in very specialized large laboratories with supercomputers a couple of decades ago.
-However, they are now standard for market and managerial studies, independent university students, and any scientist connecting to the Internet.
-Such quantities of data are available to study now more than ever.
-Nevertheless, it would be impossible for researchers to parse all of this data by themselves.
-As \cite{fayyad1996data} summarizes, data by itself is unusable until it goes through a process of selection, preprocessing, transformation, mining, and evaluation.
-Only then can it be established as knowledge.
-With the tools available to us in the era of information science, algorithms can be used to detect patterns that would take researchers too long to recognize.
-These patterns can, later on, be evaluated to generate knowledge.
-This process is called Knowledge Discovery in Databases.
-
-    % Text mining 
-    Now, there are, of course, many sources of numerical data to be explored.
-However, perhaps what is most available and interesting to managerial purposes is the resource of customers' opinions in text form.
-Since the introduction of Web 2.0, an unprecedented quantity of valuable information is posted to the Internet at a staggering speed.
-Text mining has then been proposed more than a decade ago to utilize this data \cite[e.g.][]{rajman1998text,nahm2002text}.
-Using Natural Language Processing, one can parse language in a way that translates to numbers so that a computer can analyze it.
-Since then, text mining techniques have improved over the years.
-This has been used in the field of hospitality as well for many purposes, including satisfaction analysis from reviews \cite[e.g][]{berezina2016, xu2016, xiang2015, hargreaves2015, balbi2018}, social media's influence on travelers \cite[e.g.][]{xiang2010}, review summarization \cite[e.g.][]{hu2017436}, perceived value of reviews \cite[e.g][]{FANG2016498}, and even predicting hotel demand using web traffic data \cite[e.g][]{yang2014}.
-
-    % Sentiment Analysis
-    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies.
-This method is called sentiment analysis or opinion mining.
-A precursor of this method was attempted decades ago \cite[][]{stone1966general}.
-With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, or a critical one.
-This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm.
-Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on.
-In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.
-
-    % Machine Learning
-    Our study used an algorithm for sentiment analysis called a Support Vector Machine (SVM), a supervised machine learning used for binary classification.
-Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task.
-Learning machines can be supervised, as in our study, where the algorithm has manually labeled training data to detect patterns in it and use them to establish a method for classifying other unlabeled data automatically.
-Machine learning can also be unsupervised, where there is no pre-labeled data.
-In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions.
-Our study calls for a supervised machine since text analysis can be intricate.
-Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels.
-Consequently, we teach the machine through previously labeled text samples.
-
-    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand.
-Machine learning methods focus on predicting new data based on known properties and patterns of the given data.
-Data mining, on the other hand, is discovering new information and new properties of the data.
-Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data.
-We are not exploring new patterns in the sentiment data.
-However, we are using sentiment predictions for knowledge discovery in our database.
-Thus, our study is a data mining experiment based on machine learning.
-
-    % Data exploration
-    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable.
-Reliable in that the algorithm will find a pattern by its nature.
-Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could not expect.
-These qualities determine why, similar to actual mining; data mining is mostly exploratory.
-One can never be sure that one will find a specific something.
-However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover.
-The exploration of large opinion datasets with these methods is essential.
-The reason is that we can discover knowledge that could otherwise be missed by observing a localized sample rather than taking a holistic view of every user's opinion.
-In other words, a machine algorithm can find the needles in a haystack that we did not know were there by examining small bundles of hay at a time.
-
-\section{Methodology}\label{method}
-
-  We extracted a large number of text reviews from the site \textit{Ctrip}, with mostly mainland Chinese users, and the travel site \textit{TripAdvisor}.
-We then determined the most commonly used words that relate to positive and negative opinions in a review.
-We did this using Shannon's entropy to extract keywords from their vocabulary.
-These positive and negative keywords allow us to train an optimized Support Vector Classifier (SVC) to perform a binary emotional classification of the reviews in large quantities, saving time and resources for the researchers.
-We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and the nouns they refer to.
-We split the dataset into price ranges to observe the differences in keyword usage between lower-class and higher-class hotels.
-We observed the frequency of the terms in the dataset to extract the most utilized words in either review.
-We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}.
-Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.
-
-  \begin{figure}[bp]
-  \centering
-  \includegraphics[width=\textwidth]{emotion-method-overview_V3.png}
-  \caption{Overview of the methodology to quantitatively rank satisfaction factors.}
-  \label{fig:method-overview}
-  \end{figure}
-
-  \subsection{Data collection}\label{datacollection}
-
-    In the \textit{Ctrip} data collection, reviews from a total of \num[group-separator={,}]{5774} hotels in Japan were collected.
-From these pages, we extracted a total of \num[group-separator={,}]{245919} reviews, from which \num[group-separator={,}]{211932} were detected to be standard Mandarin Chinese.
-Since a single review can have sentences with different sentiments, we separated sentences using punctuation marks.
-The Chinese reviews were comprised of \num[group-separator={,}]{187348} separate sentences.
-
-    In the \textit{TripAdvisor} data collection, we collected data from \num[group-separator={,}]{21380} different hotels.
-In total, we collected \num[group-separator={,}]{295931} reviews, from which \num[group-separator={,}]{295503} were detected to be in English.
-Similarly to the Chinese data, we then separated these English reviews into \num[group-separator={,}]{2694261} sentences using the \textit{gensim} python library.
-For the language detection in both cases we used the \textit{langdetect} python library.
-
-    However, to make the data comparisons fair, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match.
-We also filtered them to be in the same date range.
-In addition, we selected only the hotels that had pricing information available.
-We extracted the lowest and highest price possible for one night as well.
-The difference in pricing can be from better room settings, such as double or twin rooms or suites, depending on the hotel.
-Regardless of the reason, we chose the highest-priced room since it can be an indirect indicator of the hotel's class.
-After filtering, the datasets contained \num[group-separator={,}]{557} hotels in common.
-The overlapping date range for reviews was from July 2014 to July 2017.
-Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences.
-
-    The price for a night in these hotels ranges from cheap capsule hotels at 2000 yen per night to high-end hotels 188,000 yen a night at the far ends of the bell curve.
-Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at.
-Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay.
-We show these distributions in Figure \ref{fig:price_dist}.
-The structure of the data after division by price is shown in Table \ref{tab:exp_notes}.
-This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}.
-The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end.
-Further on, there are business hotels in the next range (10,000 to 15,000 yen).
-After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen).
-Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen).
-Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night.
-Because of this, other tables will omit these two price ranges.
-
-    \begin{figure}[ht]
-        \centering
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_50_even_bins.png}
-            \caption{50 equal lenght bins}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-            \includegraphics[width=\textwidth]{price_range_distribution_bins_ver_2.png}
-            \caption{manually set 9 price ranges}
-        \end{subfigure}
-    \caption{Price for one night distribution, blue: lowest price, orange: highest price.}
-    \label{fig:price_dist}
-    \end{figure}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Collected data and structure after price range categorizing.}
-      \label{tab:exp_notes}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|l|l|r|r|}
-        \hline
-        \multicolumn{1}{|c|}{\textbf{Price range}} & \multicolumn{1}{c|}{\textbf{Data collected}} & \textbf{Ctrip database} & \textbf{Tripadvisor database} \\ \hline
-        \multirow{5}{*}{0: All Prices}               & Hotels             & 557     & 557     \\
-                                                   & Reviews            & 48,070  & 41,137  \\
-                                                   & Sentences          & 101,963 & 348,039 \\
-                                                   & Positive sentences & 88,543  & 165,308 \\
-                                                   & Negative sentences & 13,420  & 182,731 \\ \hline
-        \multirow{2}{*}{1: 0 to 2500 yen}            & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{2}{*}{2: 2500 to 5000 yen}         & Hotels             & 0       & 0       \\
-                                                   & Reviews            & 0       & 0       \\ \hline
-        \multirow{5}{*}{3: 5000 to 10,000 yen}       & Hotels             & 22      & 22      \\
-                                                   & Reviews            & 452     & 459     \\
-                                                   & Sentences          & 1,108   & 3,988   \\
-                                                   & Positive sentences & 924     & 1,875   \\
-                                                   & Negative sentences & 184     & 2,113   \\ \hline
-        \multirow{5}{*}{4: 10,000 to 15,000 yen}     & Hotels             & 112     & 112     \\
-                                                   & Reviews            & 2,176   & 2,865   \\
-                                                   & Sentences          & 4,240   & 24,107  \\
-                                                   & Positive sentences & 3,566   & 11,619  \\
-                                                   & Negative sentences & 674     & 12,488  \\ \hline
-        \multirow{5}{*}{5: 15,000 to 20,000 yen}     & Hotels             & 138     & 138     \\
-                                                   & Reviews            & 7,043   & 4,384   \\
-                                                   & Sentences          & 14,726  & 37,342  \\
-                                                   & Positive sentences & 12,775  & 17,449  \\
-                                                   & Negative sentences & 1,951   & 19,893  \\ \hline
-        \multirow{5}{*}{6: 20,000 to 30,000 yen}     & Hotels             & 129     & 129     \\
-                                                   & Reviews            & 11,845  & 13,772  \\
-                                                   & Sentences          & 24,413  & 115,830 \\
-                                                   & Positive sentences & 21,068  & 55,381  \\
-                                                   & Negative sentences & 3,345   & 60,449  \\ \hline
-        \multirow{5}{*}{7: 30,000 to 50,000 yen}     & Hotels             & 83      & 83      \\
-                                                   & Reviews            & 8,283   & 7,001   \\
-                                                   & Sentences          & 17,939  & 58,409  \\
-                                                   & Positive sentences & 15,642  & 28,493  \\
-                                                   & Negative sentences & 2,297   & 29,916  \\ \hline
-        \multirow{5}{*}{8: 50,000 to 100,000 yen}    & Hotels             & 59      & 59      \\
-                                                   & Reviews            & 16,670  & 9,646   \\
-                                                   & Sentences          & 36,255  & 81,940  \\
-                                                   & Positive sentences & 31,638  & 38,217  \\
-                                                   & Negative sentences & 4,617   & 43,723  \\ \hline
-        \multirow{5}{*}{9: 100,000 to 200,000 yen}   & Hotels             & 14      & 14      \\
-                                                   & Reviews            & 1,601   & 3,010   \\
-                                                   & Sentences          & 3,282   & 26,423  \\
-                                                   & Positive sentences & 2,930   & 12,274  \\
-                                                   & Negative sentences & 352     & 14,149  \\ \hline
-        \end{tabular}%
-      }
-    \end{table}
-  \subsection{Text processing}\label{textprocessing}
-
-    We needed to analyze the grammatical relationship between words, be it English or Chinese, to understand the connections between adjectives and nouns.
-For all these processes, we used the Stanford CoreNLP pipeline developed by the Natural Language Processing Group at Stanford University \cite[][]{manning-EtAl:2014:P14-5}.
-In order to separate Chinese words for analysis, we used the Stanford Word Segmenter \cite[][]{chang2008}.
-In English texts, however, only using spaces is not enough to correctly collect concepts.
-The English language is full of variations and conjugations of words depending on the context and tense.
-Thus, a better segmentation is achieved by using lemmatization, which returns each word's dictionary form.
-For this purpose, we used the \textit{gensim} library for the English texts.
-
-    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections.
-We show an example of these dependencies in Figure \ref{fig:depparse}.
-This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}.
-A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}.
-In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}.
-In our study, this step was necessary to extract adjective modifiers and their subject.
-We did that by parsing the database and extracting instances of a few determined dependency codes.
-One of these dependency codes is ``amod'', which stands for ``adjectival modifier''.
-This is used when an adjective modifies a noun directly (e.g., A big apple).
-The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject.
-We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big).
-This dependency does not necessarily only include a combination of adjectives and nouns.
-However, it can also be connected with copular verbs, nouns, or other adjectives.
-We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{depparse.png}
-    \caption{Example of dependency parsing.}
-    \label{fig:depparse}
-    \end{figure}
-
-    A Part of Speech (POS) tagger is a program that assigns word tokens with tags identifying the part of speech.
-An example is shown in Figure \ref{fig:postag}.
-A Part of Speech is a category of lexical items that serve similar grammatical purposes, for example, nouns, adjectives, verbs, or conjunctions.
-In our study, we used the Stanford NLP POS tagger software, described by \cite{toutanova2000enriching} and \cite{toutanova2003feature}, which uses the Penn Chinese Treebank tags \cite[][]{xia_penntreebank}.
-
-    \begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.6\textwidth]{postag.png}
-    \caption{Example of POS tagging with the Penn Treebank tags.}
-    \label{fig:postag}
-    \end{figure}
-
-    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns.
-We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies.
-For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied.
-What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well.
-We show a detailed description of the chosen tags in Table \ref{tab:target_postag}.
-We also show a detailed description of the tags we needed to filter.
-We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Target Parts of Speech for extraction and pairing.}
-      \label{tab:target_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|l|}
-        \hline
-        \textbf{Language}                    & \textbf{POS Tag} & \multicolumn{1}{c|}{\textbf{Part of Speech}} & \multicolumn{1}{c|}{\textbf{Examples}}     \\ \hline
-        \multirow{4}{*}{Chinese target tags} & NN               & Noun (general)                               & \begin{CJK}{UTF8}{gbsn}酒店\end{CJK} (hotel) \\ \cline{2-4} 
-                                             & VA  & Predicative Adjective (verb)       & \begin{CJK}{UTF8}{gbsn}干净 的\end{CJK} (clean)   \\ \cline{2-4} 
-                                             & JJ  & Noun modifier (adjectives)         & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)     \\ \cline{2-4} 
-                                             & VV  & Verb (general)                     & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend) \\ \hline
-        \multirow{9}{*}{English target tags} & NN  & Noun (general)                     & room                                           \\ \cline{2-4} 
-                                             & NNS & Noun (plural)                      & beds                                           \\ \cline{2-4} 
-                                             & JJ  & Adjective                          & big                                            \\ \cline{2-4} 
-                                             & JJS & Adjective (superlative)            & best                                           \\ \cline{2-4} 
-                                             & JJR & Adjective (comparative)            & larger                                         \\ \cline{2-4} 
-                                             & VB  & Verb (base form)                   & take                                           \\ \cline{2-4} 
-                                             & VBP & Verb (single present)              & take                                           \\ \cline{2-4} 
-                                             & VBN & Verb (past participle)             & taken                                          \\ \cline{2-4} 
-                                             & VBG & Verb (gerund / present participle) & taking                                         \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    \begin{table}[ht]
-      \centering
-      \caption{Filtered out Parts of Speech to aid pairing.}
-      \label{tab:filter_postag}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \textbf{Language} &
-          \multicolumn{1}{c|}{\textbf{POS Tag}} &
-          \multicolumn{1}{c|}{\textbf{Part of Speech}} &
-          \multicolumn{1}{c|}{\textbf{Examples}} \\ \hline
-        \multirow{4}{*}{Commonly filtered tags} & DT    & Determiner         & a, an                                      \\ \cline{2-4} 
-                                                & PN    & Pronoun            & I, you, they                               \\ \cline{2-4} 
-                                                & CD    & Cardinal Number    & 1, 2, 3, 4, 5                              \\ \cline{2-4} 
-                                                & PU    & Punctuation        & .!?                                        \\ \hline
-        \multirow{5}{*}{Chinese filtered tags} &
-          DEV &
-          Particle &
-          \begin{CJK}{UTF8}{gbsn}地\end{CJK} (Japan) (adverbial particle) \\ \cline{2-4} 
-                                                & NR    & Noun (proper noun) & \begin{CJK}{UTF8}{gbsn}日本\end{CJK} (Japan) \\ \cline{2-4} 
-         &
-          M &
-          Measure word &
-          \begin{CJK}{UTF8}{gbsn}个\end{CJK} (general classifier), \begin{CJK}{UTF8}{gbsn}公里\end{CJK} (kilometer) \\ \cline{2-4} 
-         &
-          SP &
-          Sentence-final particle &
-          \begin{CJK}{UTF8}{gbsn}他\end{CJK} (he), \begin{CJK}{UTF8}{gbsn}好\end{CJK} (good) \\ \cline{2-4} 
-                                                & IJ    & Interjection       & \begin{CJK}{UTF8}{gbsn}啊\end{CJK} (ah)     \\ \hline
-        \multirow{3}{*}{English target tags}    & NNP   & Noun (proper noun) & Japan                                      \\ \cline{2-4} 
-                                                & PRP\$ & Possessive Pronoun & My, your, her, his                         \\ \cline{2-4} 
-                                                & WP    & Wh-pronoun         & What, who                                  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Once we had these adjective + noun or verb + noun pairs, we could determine what the customers referred to in their reviews. With what frequency they use those pairings positively or negatively.
-
-  \subsection{Sentiment analysis using a Support Vector Classifier}\label{sentimentanalysis}
-
-    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}.
-Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVC \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}.
-The selected SVC keywords would then clearly represent the user driving factors leading to positive and negative emotions.
-We also performed experiments to choose the best value of the parameter C used in the SVC.
-C is a constant that affects the optimization process when minimizing the error of the separating hyperplane.
-Low values of C give some freedom of error, which minimizes false positives but can also increase false negatives.
-Inversely, high C values will likely result in minimal false negatives but a possibility of false positives.
-SVC performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}.
-Examples of tagged sentences are shown in Table \ref{tab:training_examples}.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 5-fold cross-validation Chinese text classifiers.}
-      \label{tab:svm_f1_zh}
-      \resizebox{0.65\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords\\ (\(\alpha = 2.75\))\end{tabular} 
-                & Satisfaction              & 2.5             & 0.91              & 0.01          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Negative keywords\\ (\(\alpha' = 3.75\))\end{tabular}    
-                & Dissatisfaction           & 0.5             & 0.67              & 0.11          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined}\\ (\(\alpha=2.75\), \(\alpha'=3.75\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{0.5}    & \textbf{0.95}     & \textbf{0.01} \\ \hline
-        \end{tabular}
-        %
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{Best performing SVC 10-fold cross-validation English text classifiers.}
-      \label{tab:svm_f1_en}
-      \resizebox{0.65\textwidth}{!}{%
-      \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \textbf{Keyword List} &
-          \textbf{\begin{tabular}[c]{@{}l@{}}Classifier\\ emotion\end{tabular}} &
-          \textbf{C} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\mu\)\end{tabular} &
-          \begin{tabular}[c]{@{}l@{}}\(F_1\)\\ \(\sigma\)\end{tabular} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Satisfaction keywords \\ (\(\alpha=1.5\))\end{tabular}       
-                & Satisfaction              & 1.75            & 0.82              & 0.02          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Dissatisfaction keywords \\ (\(\alpha'=4.25\))\end{tabular}  
-                & Dissatisfaction           & 3               & 0.80              & 0.03          \\ \hline
-        \begin{tabular}[c]{@{}l@{}}\textbf{Combined} \\ (\(\alpha=1.5\), \(\alpha'=4.25\))\end{tabular} 
-                & \textbf{Satisfaction}     & \textbf{2}      & \textbf{0.83}     & \textbf{0.02} \\ \hline
-        \end{tabular}
-        %
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{Examples of positive and negative sentences used for training SVM.}
-      \label{tab:training_examples}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|c|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Language}} &
-          \multicolumn{1}{l|}{\textbf{Emotion}} &
-          \textbf{Sentences} \\ \hline
-        \multirow{4}{*}{Chinese} &
-          \multirow{2}{*}{Positive} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 的 服务 很 好 和 我 住 过 的 所有 日本 酒店 一样 各 种 隐形 服务 非常 厉害\end{CJK}\\ (translated as: "The service of the hotel is very good.\\ All the services of the Japanese hotels I have stayed in are extremely good.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}有 一 个 后门 到 地铁站 非常 近 周边 也 算 方便 酒店 服务 和 卫生 都 很 好\end{CJK}\\ (translated as: "There is a back door to the subway station very close to it.
-\\ The surrounding area is also convenient hotel service and health are very good")\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}酒店 旁边 很 荒凉 连个 便利 店 都 要 走 很远\end{CJK}\\ (translated as: "The hotel is very bleak, \\ and you have to go very far to go to the nearest convenience store.")\end{tabular} \\ \cline{3-3}
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}\begin{CJK}{UTF8}{gbsn}唯一 不 足 是 价格 太高\end{CJK}\\ (translated as: "The only negative is that the price is too high.")\end{tabular} \\ \hline
-        \multirow{4}{*}{English} &
-          \multirow{2}{*}{Positive} &
-          It was extremely clean, peaceful and the hotel Hosts made us feel super welcome \\ \cline{3-3} 
-         &
-           &
-          \begin{tabular}[c]{@{}l@{}}Location is very good, close to a main road with a subway station, a bakery,\\  a 7 eleven and a nice restaurant that is not too expensive but serves good food\end{tabular} \\ \cline{2-3}
-         &
-          \multirow{2}{*}{Negative} &
-          \begin{tabular}[c]{@{}l@{}}The only downside. Our room was labeled 'non-smoking'\\ but our duvet reeked of smoke.\end{tabular} \\ \cline{3-3} 
-         &
-           &
-          A bit pricey though \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus.
-A word included in many documents will have a high entropy value for that set of documents.
-Opposite to this, a word appearing in only one document will have an entropy value of zero.
-
-    An SVC is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space.
-Each dimension is a feature of the data in this space.
-The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.
-
-    Our study used a linear kernel for the SVC, defined by the formula (\ref{eq:svm1}) below.
-Each training sentence is a data point, a row in the vector \(x\).
-Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence.
-The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector.
-The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle.
-The bias coefficient \(b\) determines its position.
-
-    During the SVC learning algorithm, each data point classified incorrectly alters the weight vector to correctly classify new data.
-These changes to the weight vector are greater for features close to the separating hyperplane.
-These features have stronger changes because they needed to be taken into account to classify with a minimal error.
-Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process.
-Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\).
-Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications.
-This equation shows the last value of \(\alpha\) after the end of the cycle.
-
-    \begin{equation}\label{eq:svm1}
-    f(x) = w^\top x + b
-    \end{equation}
-
-    \begin{equation}\label{eq:svm_weight}
-    w = \sum_{i=1}^N \alpha_i y_i x_i
-    \end{equation}
-
-    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data.
-The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25.
-We applied this SVC to classify the rest of our data collection.
-Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.
-
-\section{Data Analysis}\label{dataanalysis}
-
-  \subsection{Frequent keywords in differently priced hotels}\label{svmresults}
-
-    We observed the top 10 satisfaction and dissatisfaction keywords with the highest frequencies of emotionally positive and negative statements to study.
-The keywords are the quantitative rank of the needs of Chinese and English-speaking customers.
-We show the top 10 positive keywords for each price range comparing English and Chinese in Table \ref{tab:freq_res_pos}.
-For the negative keywords, we show the results in Table \ref{tab:freq_res_neg}.
-
-    We can observe that the most used keywords for most price ranges in the same language are similar, with a few changes in priority for the keywords involved.
-For example, in Chinese, we can see that the customers praise cleanliness first in cheaper hotels, whereas the size of the room or bed is praised more in hotels of higher class.
-Another example is that in negative English reviews, complaints about price appear only after 10,000 yen hotels.
-After this, it climbs in importance following the increase in the hotel's price.
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 positive keywords.}
-      \label{tab:freq_res_pos}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 12892 & good        & 19148 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 9844  & staff       & 16289 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 6665  & great       & 16127 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 6560  & location    & 11838 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 5605  & nice        & 11615 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 5181  & clean       & 9064  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 4321  & helpful     & 5846  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 4101  & excellent   & 5661  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 3281  & comfortable & 5625  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 3258  & friendly    & 5606  \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 139   & good        & 206   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 114   & staff       & 181   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 112   & clean       & 174   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 76    & nice        & 166   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 72    & great       & 143   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 66    & location    & 91    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 55    & comfortable & 79    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 51    & helpful     & 70    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 41    & friendly    & 64    \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 34    & recommend   & 59    \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 601   & good        & 1399  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 455   & staff       & 1165  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 348   & great       & 961   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 323   & nice        & 808   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 270   & location    & 800   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK} (health)          & 201   & clean       & 656   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 196   & excellent   & 412   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 164   & friendly    & 400   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}远\end{CJK} (far)              & 158   & helpful     & 393   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 150   & comfortable & 391   \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 1925  & good        & 2242  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1348  & staff       & 1674  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1277  & great       & 1414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1058  & clean       & 1204  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1016  & nice        & 1175  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 801   & location    & 1109  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 777   & comfortable & 621   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} (subway station) & 639   & friendly    & 615   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 572   & free        & 581   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 516   & helpful     & 552   \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 3110  & good        & 6550  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 2245  & staff       & 5348  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1990  & great       & 5074  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1940  & location    & 4414  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1433  & nice        & 3451  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1073  & clean       & 3364  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 1007  & shopping    & 1992  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 979   & helpful     & 1970  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 837   & comfortable & 1941  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}附近\end{CJK} (nearby)          & 825   & friendly    & 1915  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 2291  & good        & 3407  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 1913  & staff       & 2867  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1159  & great       & 2620  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 1105  & location    & 2186  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 935   & nice        & 2160  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 846   & clean       & 1750  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 638   & helpful     & 1147  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 636   & train       & 1040  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}周边\end{CJK} (surroundings)    & 552   & subway      & 1034  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 541   & friendly    & 1001  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}}  & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 4451  & great       & 4425  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 3670  & good        & 4350  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 2422  & staff       & 3777  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 2012  & nice        & 2991  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 1764  & location    & 2439  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)              & 1634  & clean       & 1655  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 1626  & excellent   & 1555  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway)          & 1604  & helpful     & 1313  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)           & 1577  & comfortable & 1246  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)             & 1354  & friendly    & 1238  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)         & 375   & great       & 1488  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)              & 315   & staff       & 1277  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)            & 189   & good        & 994   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)       & 171   & nice        & 864   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment)    & 157   & location    & 799   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic)         & 127   & excellent   & 631   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}选择\end{CJK} (select)          & 112   & beautiful   & 455   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK} (recommend)       & 109   & large       & 404   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome)          & 101   & helpful     & 401   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)        & 98    & wonderful   & 372   \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    \begin{table}[ht]
-      \centering
-      \caption{English and Chinese comparison of the top 10 negative keywords.}
-      \label{tab:freq_res_neg}
-      \resizebox{\textwidth}{!}{%
-      \begin{tabular}{|c|lr|lr|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{Chinese keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Ctrip}} &
-          \multicolumn{1}{c|}{\textbf{English keyword}} &
-          \multicolumn{1}{c|}{\textbf{Counts in Tripadvisor}} \\ \hline
-        \multirow{10}{*}{\textbf{0: All Prices}}             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 1838 & pricey         & 462 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 1713 & poor           & 460 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 733  & dated          & 431 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 691  & disappointing  & 376 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 434  & worst          & 327 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 319  & minor          & 258 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 297  & uncomfortable  & 253 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 15   & carpet         & 240 \\  
-                                                             &                                                &      & annoying       & 220 \\  
-                                                             &                                                &      & sense          & 220 \\ \hline
-        \multirow{10}{*}{\textbf{3: 5000 to 10,000 yen}}     & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 31   & worst          & 6   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 28   & walkway        & 5   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 11   & unable         & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 10   & worse          & 4   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 9    & annoying       & 3   \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 2    & dirty          & 3   \\  
-                                                             &                                                &      & funny smell    & 3   \\  
-                                                             &                                                &      & poor           & 3   \\  
-                                                             &                                                &      & renovation     & 3   \\  
-                                                             &                                                &      & carpet         & 2   \\ \hline
-        \multirow{10}{*}{\textbf{4: 10,000 to 15,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 98   & dated          & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 91   & poor           & 29  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 43   & disappointing  & 26  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 34   & worst          & 24  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 31   & uncomfortable  & 23  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 30   & cigarette      & 22  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 26   & pricey         & 22  \\  
-                                                             &                                                &      & minor          & 21  \\  
-                                                             &                                                &      & paper          & 19  \\  
-                                                             &                                                &      & unable         & 19  \\ \hline
-        \multirow{10}{*}{\textbf{5: 15,000 to 20,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 296  & poor           & 57  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 218  & dated          & 41  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 125  & disappointing  & 38  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 93   & annoying       & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 84   & worst          & 36  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 43   & cigarette      & 31  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 26   & rude           & 28  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 3    & uncomfortable  & 26  \\  
-                                                             &                                                &      & paper          & 25  \\  
-                                                             &                                                &      & pricey         & 24  \\ \hline
-        \multirow{10}{*}{\textbf{6: 20,000 to 30,000 yen}}   & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 504  & poor           & 136 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 472  & dated          & 131 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 164  & pricey         & 120 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 155  & disappointing  & 112 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 116  & uncomfortable  & 103 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 75   & minor          & 93  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 55   & smallest       & 88  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & worst          & 86  \\  
-                                                             &                                                &      & cigarette      & 79  \\  
-                                                             &                                                &      & annoying       & 70  \\ \hline
-        \multirow{10}{*}{\textbf{7: 30,000 to 50,000 yen}}   & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 326  & poor           & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 311  & pricey         & 92  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 110  & dated          & 65  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 94   & worst          & 64  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 71   & carpet         & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 68   & uncomfortable  & 55  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 45   & dirty          & 51  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 2    & disappointing  & 50  \\  
-                                                             &                                                &      & cigarette      & 46  \\  
-                                                             &                                                &      & unable         & 43  \\ \hline
-        \multirow{10}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-                                                               \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 561  & pricey         & 163 \\ 
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 510  & dated          & 150 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 337  & disappointing  & 129 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 239  & poor           & 124 \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 134  & worst          & 98  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 97   & walkway        & 82  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 90   & carpet         & 71  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}华人\end{CJK} (Chinese)   & 8    & minor          & 63  \\  
-                                                             &                                                &      & sense          & 63  \\  
-                                                             &                                                &      & outdated       & 58  \\ \hline
-        \multirow{10}{*}{\textbf{9: 100,000 to 200,000 yen}} & \begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)     & 54   & pricey         & 40  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)   & 51   & sense          & 34  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}中文\end{CJK} (Chinese)   & 19   & minor          & 33  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}距离\end{CJK} (distance)  & 15   & lighting       & 20  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}地理\end{CJK} (geography) & 12   & disappointing  & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)  & 6    & poor           & 19  \\  
-                                                             & \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)        & 5    & annoying       & 16  \\  
-                                                             &                                                &      & mixed          & 15  \\  
-                                                             &                                                &      & disappointment & 14  \\  
-                                                             &                                                &      & paper          & 14  \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-
-  \subsection{Frequently used adjectives and their pairs}\label{adjresults}
-
-    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before.
-To understand those, we performed the dependency parsing and part of speech tagging explained in section \ref{textprocessing}.
-While many of these connections, we only considered the top 4 used keyword connections per adjective per price range.
-We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}.
-Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.
-
-    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
-      \label{tab:adj_zh_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
-           &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
-          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
-           &
-          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
-          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
-          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
-          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
-          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
-          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
-          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
-          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
-          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
-          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
-          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
-          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
-          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
-          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
-          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
-          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
-          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
-          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
-          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
-          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
-          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
-          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
-          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
-          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
-          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
-          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
-          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
-          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
-          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
-          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
-          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
-          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
-           &
-           &
-          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
-          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
-      \label{tab:adj_zh_neg}
-      \resizebox{0.7\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|}
-        \hline
-        \multicolumn{1}{|l|}{\textbf{Price range}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
-          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 311 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 71 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 45 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 43 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 22 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 19 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 3 &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 15 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 房间\end{CJK} (old room) : 2 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 510 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 90 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 134 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 39 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 53 &
-          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 34 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 32 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 5 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 26 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 30 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 感觉\end{CJK} (Stale feeling) : 2 &
-          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 9 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 25 &
-           &
-          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 7 \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000}} &
-          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 51 &
-          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 6 &
-          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 5 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 7 &
-          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 4 &
-          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 2 \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 2 &
-           &
-           \\
-         &
-          \begin{CJK}{UTF8}{gbsn}一般 房间\end{CJK} (average room) : 2 &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% POSITIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage[normalem]{ulem}
-    % \useunder{\uline}{\ul}{}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in positive English texts.}
-      \label{tab:adj_en_pos}
-      \resizebox{\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{good}} &
-          \multicolumn{1}{c|}{\textbf{clean}} &
-          \multicolumn{1}{c|}{\textbf{comfortable}} &
-          \multicolumn{1}{c|}{\textbf{helpful}} &
-          \multicolumn{1}{c|}{\textbf{free}} &
-          \multicolumn{1}{c|}{\textbf{large}} &
-          \multicolumn{1}{c|}{\textbf{firendly}} &
-          \multicolumn{1}{c|}{\textbf{great}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          good : 19148 &
-          clean : 9064 &
-          comfortable : 5625 &
-          helpful : 5846 &
-          free : 4318 &
-          large : 4104 &
-          friendly : 5606 &
-          great : 16127 \\
-         &
-          good location : 1985 &
-          clean room : 3596 &
-          comfortable bed : 1919 &
-          helpful staff : 2927 &
-          free wifi : 773 &
-          large room : 1256 &
-          friendly staff : 3819 &
-          great location : 2313 \\
-         &
-          good service : 1042 &
-          clean hotel : 969 &
-          comfortable room : 1098 &
-          helpful concierge : 304 &
-          free shuttle : 286 &
-          large hotel : 268 &
-          friendly service : 169 &
-          great view : 1099 \\
-         &
-          good breakfast : 942 &
-          clean bathroom : 282 &
-          comfortable stay : 272 &
-          helpful desk : 110 &
-          free drink : 234 &
-          large bathroom : 202 &
-          friendly hotel : 73 &
-          great service : 841 \\
-         &
-          good hotel : 874 &
-          clean everything : 200 &
-          comfortable hotel : 238 &
-          helpful service : 74 &
-          free bus : 225 &
-          larger room : 192 &
-          friendly person : 63 &
-          great hotel : 802 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\ 10,000 yen\end{tabular}}} &
-          good : 206 &
-          clean : 174 &
-          comfortable : 79 &
-          helpful : 70 &
-          free : 35 &
-          large : 31 &
-          friendly : 64 &
-          great : 143 \\
-         &
-          good location : 30 &
-          clean room : 55 &
-          comfortable bed : 21 &
-          helpful staff : 36 &
-          free wifi : 10 &
-          large room : 7 &
-          friendly staff : 53 &
-          great location : 21 \\
-         &
-          good value : 19 &
-          clean bathroom : 14 &
-          comfortable room : 9 &
-           &
-          free tea : 4 &
-          large area : 2 &
-          friendly everyone : 2 &
-          great view : 14 \\
-         &
-          good english : 10 &
-          clean place : 12 &
-          comfortable futon : 8 &
-           &
-          free raman : 2 &
-          large size : 2 &
-          friendly service : 2 &
-          great place : 13 \\
-         &
-          good place : 7 &
-          clean hotel : 6 &
-          comfortable stay : 3 &
-           &
-          free toothbrush : 2 &
-           &
-           &
-          great experience : 5 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
-          good : 1399 &
-          clean : 656 &
-          comfortable : 391 &
-          helpful : 393 &
-          free : 271 &
-          large : 250 &
-          friendly : 400 &
-          great : 961 \\
-         &
-          good location : 159 &
-          clean room : 247 &
-          comfortable bed : 123 &
-          helpful staff : 206 &
-          free wifi : 53 &
-          large room : 84 &
-          friendly staff : 292 &
-          great location : 158 \\
-         &
-          good breakfast : 87 &
-          clean hotel : 74 &
-          comfortable room : 90 &
-          helpful concierge : 20 &
-          free breakfast : 15 &
-          large bathroom : 20 &
-          friendly service : 15 &
-          great service : 51 \\
-         &
-          good hotel : 71 &
-          clean bathroom : 20 &
-          comfortable hotel : 26 &
-          helpful desk : 10 &
-          free service : 12 &
-          larger room : 12 &
-          friendly hotel : 7 &
-          great hotel : 43 \\
-         &
-          good service : 67 &
-          clean everything : 14 &
-          comfortable stay : 20 &
-          helpful service : 4 &
-          free drink : 11 &
-          large hotel : 10 &
-          friendly person : 6 &
-          great place : 35 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
-          good : 2242 &
-          clean : 1204 &
-          comfortable : 621 &
-          helpful : 552 &
-          free : 581 &
-          large : 349 &
-          friendly : 615 &
-          great : 1414 \\
-         &
-          good location : 242 &
-          clean room : 440 &
-          comfortable bed : 219 &
-          helpful staff : 301 &
-          free wifi : 109 &
-          large room : 85 &
-          friendly staff : 444 &
-          great location : 199 \\
-         &
-          good hotel : 116 &
-          clean hotel : 133 &
-          comfortable room : 99 &
-          helpful desk : 11 &
-          free shuttle : 35 &
-          large suitcase : 18 &
-          friendly hotel : 12 &
-          great view : 81 \\
-         &
-          good breakfast : 113 &
-          clean bathroom : 38 &
-          comfortable stay : 30 &
-          helpful concierge : 9 &
-          free bus : 30 &
-          larger room : 18 &
-          friendly service : 8 &
-          great hotel : 68 \\
-         &
-          good service : 108 &
-          clean everything : 26 &
-          comfortable hotel : 20 &
-          helpful reception : 5 &
-          free breakfast : 27 &
-          large hotel : 17 &
-          friendly most : 7 &
-          great place : 61 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
-          good : 6550 &
-          clean : 3364 &
-          comfortable : 1941 &
-          helpful : 1970 &
-          free : 1186 &
-          large : 1257 &
-          friendly : 1915 &
-          great : 5074 \\
-         &
-          good location : 703 &
-          clean room : 1379 &
-          comfortable bed : 658 &
-          helpful staff : 1019 &
-          free wifi : 269 &
-          large room : 329 &
-          friendly staff : 1311 &
-          great location : 881 \\
-         &
-          good service : 331 &
-          clean hotel : 379 &
-          comfortable room : 359 &
-          helpful concierge : 79 &
-          free breakfast : 68 &
-          large hotel : 87 &
-          friendly service : 51 &
-          great service : 249 \\
-         &
-          good english : 304 &
-          clean bathroom : 95 &
-          comfortable stay : 100 &
-          helpful desk : 42 &
-          free coffee : 57 &
-          larger room : 81 &
-          friendly person : 21 &
-          great hotel : 232 \\
-         &
-          good breakfast : 303 &
-          clean everything : 77 &
-          comfortable hotel : 82 &
-          helpful receptionist : 17 &
-          free drink : 38 &
-          large bed : 43 &
-          friendly hotel : 19 &
-          great view : 220 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
-          good : 3407 &
-          clean : 1750 &
-          comfortable : 1000 &
-          helpful : 1147 &
-          free : 933 &
-          large : 580 &
-          friendly : 1001 &
-          great : 2620 \\
-         &
-          good location : 380 &
-          clean room : 725 &
-          comfortable bed : 345 &
-          helpful staff : 607 &
-          free drink : 145 &
-          large room : 174 &
-          friendly staff : 715 &
-          great location : 393 \\
-         &
-          good breakfast : 191 &
-          clean hotel : 197 &
-          comfortable room : 193 &
-          helpful concierge : 53 &
-          free wifi : 129 &
-          larger room : 32 &
-          friendly service : 24 &
-          great view : 162 \\
-         &
-          good service : 182 &
-          clean bathroom : 61 &
-          comfortable hotel : 49 &
-          helpful service : 20 &
-          free coffee : 45 &
-          large hotel : 30 &
-          friendly hotel : 13 &
-          great hotel : 134 \\
-         &
-          good english : 155 &
-          clean everything : 36 &
-          comfortable stay : 47 &
-          helpful desk : 17 &
-          free bus : 38 &
-          large bed : 28 &
-          friendly person : 13 &
-          great service : 114 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
-          good : 4350 &
-          clean : 1655 &
-          comfortable : 1246 &
-          helpful : 1313 &
-          free : 1072 &
-          large : 1233 &
-          friendly : 1238 &
-          great : 4425 \\
-         &
-          good location : 406 &
-          clean room : 648 &
-          comfortable bed : 425 &
-          helpful staff : 589 &
-          free shuttle : 181 &
-          large room : 442 &
-          friendly staff : 810 &
-          great location : 506 \\
-         &
-          good service : 296 &
-          clean hotel : 156 &
-          comfortable room : 266 &
-          helpful concierge : 108 &
-          free wifi : 172 &
-          large hotel : 109 &
-          friendly service : 51 &
-          great view : 436 \\
-         &
-          good hotel : 196 &
-          clean bathroom : 48 &
-          comfortable stay : 56 &
-          helpful service : 28 &
-          free bus : 127 &
-          large bathroom : 58 &
-          friendly hotel : 20 &
-          great service : 267 \\
-         &
-          good breakfast : 191 &
-          cleanliness : 40 &
-          comfortable hotel : 51 &
-          helpful desk : 26 &
-          free service : 65 &
-          larger room : 38 &
-          friendly person : 12 &
-          great hotel : 241 \\ \hline
-        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
-          good : 994 &
-          clean : 261 &
-          comfortable : 347 &
-          helpful : 401 &
-          free : 240 &
-          large : 404 &
-          friendly : 370 &
-          great : 1488 \\
-         &
-          good location : 65 &
-          clean room : 102 &
-          comfortable bed : 128 &
-          helpful staff : 169 &
-          free wifi : 31 &
-          large room : 135 &
-          friendly staff : 194 &
-          great location : 155 \\
-         &
-          good service : 56 &
-          clean hotel : 24 &
-          comfortable room : 82 &
-          helpful concierge : 35 &
-          free breakfast : 19 &
-          large bathroom : 38 &
-          friendly service : 18 &
-          great view : 155 \\
-         &
-          good breakfast : 53 &
-          cleanliness : 8 &
-          comfortable stay : 16 &
-          helpful everyone : 7 &
-          free drink : 16 &
-          large hotel : 15 &
-          friendly everyone : 7 &
-          great service : 101 \\
-         &
-          good hotel : 40 &
-          clean place : 7 &
-          comfortable hotel : 10 &
-          helpful team : 5 &
-          free bus : 14 &
-          large bed : 12 &
-          friendly person : 4 &
-          great hotel : 80 \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-    %%%%%%%%%%%%% NEGATIVE ENGLISH ADJECTIVE PAIRS
-    % Please add the following required packages to your document preamble:
-    % \usepackage{multirow}
-    % \usepackage{graphicx}
-    % \usepackage{lscape}
-    \begin{landscape}
-    \begin{table}[p]
-      \centering
-      \caption{Top 4 words related to the mainly used adjectives in negative English texts.}
-      \label{tab:adj_en_neg}
-      \resizebox{0.8\linewidth}{!}{%
-      \begin{tabular}{|c|l|l|l|l|l|}
-        \hline
-        \textbf{Price range} &
-          \multicolumn{1}{c|}{\textbf{poor}} &
-          \multicolumn{1}{c|}{\textbf{dated}} &
-          \multicolumn{1}{c|}{\textbf{worst}} &
-          \multicolumn{1}{c|}{\textbf{dirty}} &
-          \multicolumn{1}{c|}{\textbf{uncomfortable}} \\ \hline
-        \multirow{5}{*}{\textbf{0: All Prices}} &
-          poor : 460 &
-          dated : 431 &
-          worst : 327 &
-          dirty : 188 &
-          uncomfortable : 253 \\
-         &
-          poor service : 55 &
-          outdated : 128 &
-          worst hotel : 43 &
-          dirty carpet : 34 &
-          uncomfortable bed : 63 \\
-         &
-          poor breakfast : 41 &
-          outdated room : 20 &
-          worst experience : 18 &
-          dirty room : 23 &
-          uncomfortable pillow : 20 \\
-         &
-          poor quality : 27 &
-          outdated hotel : 10 &
-          worst part : 15 &
-          not dirty : 7 &
-          uncomfortable mattress : 8 \\
-         &
-          poor english : 24 &
-          outdated bathroom : 7 &
-          worst service : 10 &
-          dirty bathroom : 6 &
-          uncomfortable night : 8 \\ \hline
-        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
-          poor : 3 &
-           &
-          worst : 6 &
-          dirty : 3 &
-          uncomfortable : 2 \\
-         &
-           &
-           &
-          worst room : 2 &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
-          poor : 29 &
-          dated : 40 &
-          worst : 24 &
-          dirty : 11 &
-          uncomfortable : 23 \\
-         &
-          poor breakfast : 3 &
-          outdated : 11 &
-          worst hotel : 4 &
-          dirty floor : 2 &
-          uncomfortable bed : 4 \\
-         &
-          poor service : 3 &
-          outdated decor : 2 &
-          worst experience : 2 &
-           &
-          not uncomfortable : 2 \\
-         &
-          poor conditioning : 2 &
-          outdated room : 2 &
-           &
-           &
-          uncomfortable night : 2 \\
-         &
-          poor view : 2 &
-           &
-           &
-           &
-          uncomfortable pillow : 2 \\ \hline
-        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
-          poor : 57 &
-          dated : 41 &
-          worst : 36 &
-          dirty : 14 &
-          uncomfortable : 26 \\
-         &
-          poor service : 10 &
-          outdated : 8 &
-          worst hotel : 8 &
-          dirty room : 2 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 6 &
-           &
-          worst experience : 3 &
-           &
-          uncomfortable pillow : 2 \\
-         &
-          poor hotel : 5 &
-           &
-          worst part : 2 &
-           &
-           \\
-         &
-          poor experience : 3 &
-           &
-          worst service : 2 &
-           &
-           \\ \hline
-        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
-          poor : 136 &
-          dated : 131 &
-          worst : 86 &
-          dirty : 67 &
-          uncomfortable : 103 \\
-         &
-          poor breakfast : 15 &
-          outdated : 31 &
-          worst hotel : 11 &
-          dirty room : 10 &
-          uncomfortable bed : 24 \\
-         &
-          poor service : 14 &
-          outdated room : 6 &
-          worst part : 7 &
-          dirty carpet : 8 &
-          uncomfortable pillow : 11 \\
-         &
-          poor english : 9 &
-          outdated hotel : 2 &
-          worst breakfast : 5 &
-          dirty bathroom : 3 &
-          uncomfortable night : 4 \\
-         &
-          poor quality : 9 &
-           &
-          worst experience : 5 &
-          dirty chair : 2 &
-          uncomfortable experience : 3 \\ \hline
-        \multirow{5}{*}{\textbf{7: 30,000 to 50,000 yen}} &
-          poor : 92 &
-          dated : 65 &
-          worst : 64 &
-          dirty : 51 &
-          uncomfortable : 55 \\
-         &
-          poor service : 8 &
-          outdated : 17 &
-          worst hotel : 10 &
-          dirty carpet : 11 &
-          uncomfortable bed : 20 \\
-         &
-          poor breakfast : 7 &
-          outdated hotel : 4 &
-          worst room : 3 &
-          dirty room : 7 &
-          uncomfortable mattress : 6 \\
-         &
-          poor english : 7 &
-          outdated bathroom : 2 &
-          worst service : 3 &
-          dirty clothe : 2 &
-          uncomfortable pillow : 5 \\
-         &
-          poor connection : 5 &
-          outdated decor : 2 &
-          worst part : 2 &
-          dirty luggage : 2 &
-          uncomfortable room : 5 \\ \hline
-        \multirow{5}{*}{\textbf{8: 50,000 to 100,000 yen}} &
-          poor : 124 &
-          dated : 150 &
-          worst : 98 &
-          dirty : 36 &
-          uncomfortable : 33 \\
-         &
-          poor service : 16 &
-          outdated : 58 &
-          worst hotel : 9 &
-          dirty carpet : 12 &
-          uncomfortable bed : 7 \\
-         &
-          poor breakfast : 9 &
-          outdated room : 9 &
-          worst experience : 5 &
-          dirty room : 3 &
-           \\
-         &
-          poor quality : 9 &
-          outdated furniture : 6 &
-          worst part : 3 &
-          dirty cup : 2 &
-           \\
-         &
-          poor english : 6 &
-          outdated hotel : 4 &
-           &
-          dirty rug : 2 &
-           \\ \hline
-        \multirow{5}{*}{\textbf{9: 100,000 to 200,000 yen}} &
-          poor : 19 &
-          dated : 3 &
-          worst : 12 &
-          dirty : 6 &
-          uncomfortable : 8 \\
-         &
-          poor service : 4 &
-          outdated : 2 &
-          worst experience : 2 &
-           &
-          little uncomfortable : 2 \\
-         &
-          poor choice : 2 &
-           &
-           &
-           &
-           \\
-         &
-          poor experience : 2 &
-           &
-           &
-           &
-           \\
-         &
-           &
-           &
-           &
-           &
-           \\ \hline
-        \end{tabular}%
-        }
-    \end{table}
-    \end{landscape}
-
-  \subsection{Determining hard and soft attribute usage}\label{det_hard_soft}
-
-    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel.
-We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure.
-Some of these aspects would be impractical for the hotel to change, such as its surroundings and location.
-Others can be expensive to change, such as matters requiring construction costs, which are possible but would require significant infrastructure investment.
-On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management.
-For example, the hotel's services or the cleanliness of the rooms are soft attributes.
-For our purposes, amenities, clean or good quality bed sheets or curtains, and other physical attributes that are part of the service and not the hotel's physical structure are considered soft attributes.
-Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.
-
-    We manually labeled each language's top keywords into either hard or soft by considering how the word would be used when writing a review.
-If the word described unchangeable physical factors by the staff or management, we consider them hard.
-If the word implied an issue that could be solved or managed by the hotel staff or management, we consider it soft.
-For adjectives, we looked at the top four adjective and noun pairings used in the entire dataset and counted the usage percentage in each context.
-If it was not clear from the word or the pairing alone, we declared it undefined.
-Then, we added the counts of these words in each category.
-A single word with no pairing is always deemed 100\% in the category it corresponds to.
-We add the partial percentages for each category when an adjective includes various contexts.
-The interpretation of these keywords is shown in the Tables \ref{tab:zh_hard_soft_keywords} and \ref{tab:en_hard_soft_keywords}.
-We can see the summarized results for the hard and soft percentages of positive and negative Chinese keywords in Figure \ref{fig:hard_soft_zh}.
-For the English keywords, see Figure \ref{fig:hard_soft_en}.
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for Chinese keywords. }
-    \label{tab:zh_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{19}{*}{\textbf{Positive Keywords}} & \begin{CJK}{UTF8}{gbsn}不错\end{CJK}    & 50\% hard, 25\% soft, 25\% undefined             \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}大\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}干净\end{CJK}  & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}早餐\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}交通\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}棒\end{CJK}   & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}近\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}购物\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}环境\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}卫生\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}新\end{CJK}   & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}推荐\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}选择\end{CJK}  & 100\% undefined                      \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地铁站\end{CJK} & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}远\end{CJK}   & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}附近\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}周边\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}赞\end{CJK}   & 100\% undefined                      \\ \hline
-      \multirow{8}{*}{\textbf{Negative Keywords}}  & \begin{CJK}{UTF8}{gbsn}价格\end{CJK}    & 100\% soft                                       \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}一般\end{CJK}  & 50\% hard, 50\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}中文\end{CJK}  & 100\% soft                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}距离\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}地理\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK}  & 100\% hard                           \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}老\end{CJK}   & 75\% hard, 25\% soft                 \\ \cline{2-3} 
-       & \begin{CJK}{UTF8}{gbsn}华人\end{CJK}  & 100\% soft                           \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_zh_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top Chinese keywords for all price ranges}
-  \label{fig:hard_soft_zh}
-  \end{figure}
-
-  % Please add the following required packages to your document preamble:
-  % \usepackage{multirow}
-  % \usepackage{graphicx}
-  % \usepackage[normalem]{ulem}
-  % \useunder{\uline}{\ul}{}
-  \begin{table}[ht]
-    \centering
-    \caption{Determination of hard and soft attributes for English keywords. }
-    \label{tab:en_hard_soft_keywords}
-    \resizebox{0.7\textwidth}{!}{%
-    \begin{tabular}{|c|l|l|}
-      \hline
-      \textbf{Keyword Emotion}                     & \multicolumn{1}{c|}{\textbf{Keyword}} & \multicolumn{1}{c|}{\textbf{Attribute Category}} \\ \hline
-      \multirow{18}{*}{\textbf{Positive Keywords}} & good                                  & 25\% hard, 50\% soft, 25\% undefined             \\ \cline{2-3} 
-       & great          & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & staff          & 100\% soft                           \\ \cline{2-3} 
-       & clean          & 100\% soft                           \\ \cline{2-3} 
-       & location       & 100\% hard                           \\ \cline{2-3} 
-       & nice           & 50\% hard, 25\% soft, 25\% undefined \\ \cline{2-3} 
-       & excellent      & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & helpful        & 100\% soft                           \\ \cline{2-3} 
-       & comfortable    & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & shopping       & 100\% hard                           \\ \cline{2-3} 
-       & beautiful      & 25\% hard, 75\% soft                 \\ \cline{2-3} 
-       & friendly       & 100\% soft                           \\ \cline{2-3} 
-       & train          & 100\% hard                           \\ \cline{2-3} 
-       & large          & 100\% hard                           \\ \cline{2-3} 
-       & free           & 100\% soft                           \\ \cline{2-3} 
-       & subway         & 100\% hard                           \\ \cline{2-3} 
-       & recommend      & 100\% undefined                      \\ \cline{2-3} 
-       & wonderful      & 50\% soft, 50\% undefined            \\ \hline
-      \multirow{24}{*}{\textbf{Negative Keywords}} & pricey                                & 100\% soft                                       \\ \cline{2-3} 
-       & worst          & 25\% hard, 50\% soft, 25\% undefined \\ \cline{2-3} 
-       & dated          & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & poor           & 100\% soft                           \\ \cline{2-3} 
-       & walkway        & 100\% hard                           \\ \cline{2-3} 
-       & sense          & 100\% undefined                      \\ \cline{2-3} 
-       & unable         & 100\% soft                           \\ \cline{2-3} 
-       & disappointing  & 50\% soft, 50\% undefined            \\ \cline{2-3} 
-       & minor          & 100\% undefined                      \\ \cline{2-3} 
-       & worse          & 100\% undefined                      \\ \cline{2-3} 
-       & annoying       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & lighting       & 100\% soft                           \\ \cline{2-3} 
-       & uncomfortable  & 100\% soft                           \\ \cline{2-3} 
-       & carpet         & 100\% soft                           \\ \cline{2-3} 
-       & dirty          & 75\% soft, 25\% undefined            \\ \cline{2-3} 
-       & cigarette      & 100\% soft                           \\ \cline{2-3} 
-       & funny smell    & 100\% soft                           \\ \cline{2-3} 
-       & rude           & 100\% soft                           \\ \cline{2-3} 
-       & smallest       & 75\% hard, 25\% undefined            \\ \cline{2-3} 
-       & mixed          & 100\% undefined                      \\ \cline{2-3} 
-       & renovation     & 100\% hard                           \\ \cline{2-3} 
-       & paper          & 100\% undefined                      \\ \cline{2-3} 
-       & disappointment & 100\% undefined                      \\ \cline{2-3} 
-       & outdated       & 75\% hard, 25\% undefined            \\ \hline
-      \end{tabular}%
-      }
-  \end{table}
-
-  \begin{figure}[ht]
-      \centering
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_pos.png}
-          \caption{Positive keywords}
-      \end{subfigure}
-      \begin{subfigure}[b]{0.45\textwidth}
-          \includegraphics[width=\textwidth]{hard_soft_attr_en_neg.png}
-          \caption{Negative keywords}
-      \end{subfigure}
-  \caption{Hard and soft attributes from the top English keywords for all price ranges}
-  \label{fig:hard_soft_en}
-  \end{figure}
-
-\section{Results}\label{results}
-
-  \subsection{Experimental results and answers to research questions}
-
-    Our research questions were related to two issues.
-Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture.
-
-    Observing the top-ranking positive keywords in Chinese reviews, as shown in Tables \ref{tab:freq_res_pos} and Table \ref{tab:adj_zh_pos}, it was revealed that, while service, cleanliness, and breakfast were praised in most hotels, the location was more important when observing the pairings.
-Hard attributes were abundant lower on the lists.
-The negative keywords in Table \ref{tab:freq_res_neg} indicate that a lack of a Chinese-friendly environment was perceived, although there were more complaints about hard attributes such as the building's age and the distance from other convenient spots.
-However, most complaints were about the hotel's price, which included all of the price ranges; therefore, the price was the primary concern for Chinese customers with different travel purposes.
-
-    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges.
-This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''.
-When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability.
-When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with.
-
-    We can also observe some keywords that are not considered by their counterparts.
-For example, English-speaking customers mentioned tobacco smell in many reviews.
-However, it was not statistically identified as a problem for their Chinese counterparts.
-On the other hand, although they appear in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night.
-Meanwhile, the term ``shopping'' appeared solely in the top 10 positive keywords list for English speakers who stayed in rooms priced 20,000–30,000 yen per night.
-
-    With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities.
-However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel.
-The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.
-
-    For research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we considered how customers of both cultural backgrounds evaluated the hard and soft attributes of hotels.
-Our study discovered that Chinese tourists mostly positively react to the hotel's hard attributes, albeit the negative evaluations are more uniform than the positive evaluations, with a tendency of 53 \% towards hard attributes.
-On the other hand, English-speaking tourists were more responsive to soft attributes, either positively or negatively.
-In the case of negative keywords, they were more concerned about the hotel's soft attributes.
-
-    One factor that both populations had in common is that, when perceiving the hotel negatively, the ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old),'' ``dated,'' ``outdated,'' or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel were surprisingly criticized across most price ranges.
-However, this is a hard attribute and is unlikely to change for most hotels.
-
-  \subsection{Chinese tourists: A big and clean space}\label{disc:zh}
-
-    We found that mainland Chinese tourists were mainly satisfied by big and clean spaces in Japanese hotels.
-The adjectival pairings extracted with dependency parsing and POS tagging (Table \ref{tab:adj_zh_pos})  imply big and clean rooms.
-Other mentions included big markets nearby or a big bed.
-Across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increased with the increasing price of the hotel.
-When inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area),'' we notice that there were also many references to the public bathing facilities in the hotel.
-Such references were also implied by a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring).''
-
-    In Japan, there are the so-called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o}),'' which are artificially constructed public bathing facilities, including saunas and baths with unique qualities.
-On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen}).'' However, they are interchangeable if natural hot spring water is used in artificially made tiled bath facilities.
-It is a Japanese custom that all customers first clean themselves in a shower and afterward use the baths nude.
-It could be a cultural shock for many tourists but a fundamental attraction for many others.
-
-    Chinese customers are satisfied with the size of the room or bed; however, it is not trivial to change this.
-In contrast, cleanliness is mostly related to soft attributes when we observe its adjectival pairings.
-We can observe pairs such as ``\begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room)'' at the top rank of all price ranges and thereupon ``\begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel),'' ``\begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall),'' ``\begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment),'' and ``\begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities),'' among other examples.
-In negative reviews, there was a mention of criticizing the ``\begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene)'' of the hotel, although it was an uncommon pair.
-Therefore, we can assert that cleanliness was an important soft attribute for Chinese customers, and they were mostly pleased when their expectations were fulfilled.
-
-    A key soft satisfaction factor was the inclusion of breakfast within the hotel.
-While other food-related words were extracted, most of them were general, such as ``food'' or ``eating,'' and were lower-ranking.
-In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast),'' referring to the hotel commodities, was frequently used in positive texts compared to other food-related words across all price ranges, albeit at different priorities in each of them.
-For this reason, we regard it as an important factor.
-From the word pairs of the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also note that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired with ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top four pairings.
-It is only slightly lower in other categories, although it is not depicted in the table.
-Thus, we consider that a recommended strategy for hotel management is to invest in the inclusion or improvement of hotel breakfast to increase good reviews.
-
-  \subsection{Western tourists: A friendly face and absolutely clean}\label{disc:en}
-
-    From the satisfaction factors of English-speaking tourists, we observed at least three words were related to staff friendliness and services in the general database: ``staff,'' ``helpful,'' and ``friendliness.'' The word ``staff'' is the highest-ranked of these three, ranking second for satisfied customers across most price ranges and only third in one of them.
-The word ``good'' mainly refers to the location, service, breakfast, or English availability in Table \ref{tab:adj_en_pos}.
-Similar to Chinese customers, Western customers also seemed to enjoy the included breakfasts regarding their satisfaction keyword pairings.
-However, the relevant word does not appear in the top 10 list directly, in contrast to their Chinese counterparts.
-The words ``helpful'' and ``friendly'' are mostly paired with ``staff,'' ``concierge,'' ``desk,'' and ``service.'' By considering the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we realized once again that Western tourists were disappointed with service-related concepts and reacted negatively.
-
-    Another soft attribute that is high on the list for most of the price ranges is the word ``clean'', so we examined its word pairings.
-Customers largely praised ``clean rooms'' and ``clean bathrooms'' and also referred to the hotel in general.
-When observing the negative keyword frequencies for English speakers, we can find words such as ``dirty'' and ``carpet'' as well as word pairings such as ``dirty carpet,'' ``dirty room,'' and ``dirty bathroom.'' Along with complaints about off-putting smells, we could conclude that Western tourists had high expectations about cleanliness when traveling in Japan.
-
-    An interesting detail of the keyword ranking is that the word ``comfortable'' was high on the satisfaction factors, and ``uncomfortable'' was high on the dissatisfaction factors.
-The words were paired with nouns such as ``bed,'' ``room,'' ``pillow,'' and ``mattress,'' when they generally referred to their sleep conditions in the hotel.
-    It seems that Western tourists were particularly sensitive about the hotels’ comfort levels and whether they reached their expectations.
-The ranking for the negative keyword ``uncomfortable'' is similar across most price ranges except the two most expensive ones, where this keyword disappears from the top 10 list.
-
-    Albeit lower in priority, the price range of 15,000 to 20,000 yen hotels also includes ``free'' as one of the top 10 positive keywords, mainly paired with ``Wi-Fi.'' This price range corresponds to business hotels, where users would expect this feature the most.
-
-  \subsection{Tobacco, an unpleasant smell in the room}\label{disc:tobacco}
-
-    A concern for Western tourists was uncleanliness and the smell of cigarettes in their room, which can be regarded as soft attributes.
-Cigarette smell was an issue even in the middle- and high-class hotels, of which the rooms were priced at more than 30,000 yen per night.
-For hotels with rooms priced above 50,000 yen per night, however, this problem seemed to disappear from the list of top 10 concerns.
-Tobacco was referenced singularly as ``cigarette'', but also in word pairs in Table \ref{tab:adj_en_neg} as ``funny smell.'' By manually inspecting a sample of reviews with this keyword, we noticed that the room was often advertised as non-smoking; however, the smell permeated the room and curtains.
-Another common complaint was that there were no nonsmoking facilities available.
-The smell of smoke can completely ruin some customers’ stay, leading to bad reviews, thereby lowering the number of future customers.
-
-    In contrast, Chinese customers seemed not to be bothered by this.
-Previous research has stated that 49–60 \% of Chinese men (and 2.0–2.8 \% of women) currently smoke or smoked in the past.
-This was derived from a sample of 170,000 Chinese adults in 2013–2014, which is high compared to many English-speaking countries \cite[][]{zhang2019tobacco,who2015tobacco}.
-
-    Japan has a polarized view on the topic of smoking.
-Although it has one of the world’s largest tobacco markets, tobacco use has decreased in recent years.
-Smoking in public spaces is prohibited in some wards of Tokyo (namely Chiyoda, Shinjuku, and Shibuya).
-However, it is generally only suggested and not mandatory to lift smoking restrictions in restaurants, bars, hotels, and public areas.
-Many places have designated smoking rooms to keep the smoke in an enclosed area and avoid bothering others.
-
-    Nevertheless, businesses, especially those who cater to certain customers, are generally discouraged by smoking restrictions if they want to maintain their clientele.
-To cater to all kinds of customers, including Western and Asian, Japanese hotels must provide spaces without tobacco smell.
-Even if the smoke does not bother a few customers, the lack of such a smell will make it an appropriate space for all customers.
-
-  \subsection{Location, location, location}\label{disc:location}
-
-    The hotel's location, closeness to the subway and public transportation, and availability of nearby shops proved to be of importance to both Chinese and English-speaking tourists.
-In positive word pairings in Tables \ref{tab:adj_zh_pos} and \ref{tab:adj_en_pos}, we can find pairs such as ``\begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station),'' ``\begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway)'' in Chinese texts and ``good location,'' ``great location,'' and ``great view'' as well as single keywords ``location'' and ``shopping'' for English speakers, and ``\begin{CJK}{UTF8}{gbsn}交通\end{CJK} (traffic),'' ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping),'' ``\begin{CJK}{UTF8}{gbsn}地铁\end{CJK} (subway),'' and ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' for Chinese speakers.
-All of these keywords and their location in each population's priorities across the price ranges signify that the hotel's location was a secondary but still important point for their satisfaction.
-However, since this is a hard attribute, it is not often considered in the literature.
-By examining examples from the data, we recognized that most customers were satisfied if the hotel was near at least two of the following facilities: subway, train, and convenience stores.
-
-    Japan is a country with a peculiar public transportation system.
-During rush hour, the subway is crowded with commuters, and trains and subway stations create a confusing public transportation map for a visitor in Tokyo.
-Buses are also available, albeit less used than rail systems in metropolitan cities.
-These three means of transportation are usually affordable in price.
-There are more expensive means, such as the bullet train \textit{shinkansen} for traveling across the country and taxis.
-The latter is a luxury in Japan compared to other countries.
-In Japan, taxis provide a high-quality experience with a matching price.
-Therefore, for people under a budget, subway availability and maps or GPS applications, as well as a plan to travel the city, are of utmost necessity for tourists, using taxis only as a last resort.
-
-    Japanese convenience stores are also famous worldwide because they offer a wide range of services and products, from drinks and snacks to full meals, copy and scanning machines, alcohol, cleaning supplies, personal hygiene items, underwear, towels, and international ATMs.
-If some trouble occurs, or a traveler forgot to pack a particular item, it is most certain that they can find it.
-
-    Therefore, considering that both transportation systems and nearby shops are points of interest for Chinese and Western tourists, and perhaps offering guide maps and information about these as an appeal point could result in greater satisfaction.
-
-\section{Discussion}\label{discussion}
-
-  \subsection{Western and Chinese tourists in the Japanese hospitality environment}\label{disc:omotenashi}
-
-    To date, scholars have been correcting our historical bias towards the West.
-Studies have determined that different cultural backgrounds lead to different expectations, which influence tourists' satisfaction.
-In other words, tourists of a particular culture have different leading satisfaction factors across different destinations.
-However, Japan presents a particular environment; the spirit of hospitality and service, \textit{omotenashi}, which is considered to be of the highest standard across the world.
-Our study explores whether such an environment can affect different cultures equally or whether it is attractive only to certain cultures.
-
-    Our results indicate that Western tourists are more satisfied with soft attributes than Chinese tourists.
-As explained earlier in this paper, Japan is well known for its customer service.
-Respectful language and bowing are not exclusive to high-priced hotels or businesses; these are met in convenience stores as well.
-Even in the cheapest convenience store, the level of hospitality is starkly different from Western culture and perhaps unexpected.
-In higher-priced hotels, the adjectives used to praise the service ranged from normal descriptors like ``good'' to higher levels of praise like ``wonderful staff,'' ``wonderful experience,'' ``excellent service,'' and ``excellent staff.'' Furthermore, \cite{kozak2002} and \cite{shanka2004} have also proven that hospitality and staff friendliness are two determinants of Western tourists' satisfaction.
-
-    However, the negative English keywords indicate that a large part of the dissatisfaction with Japanese hotels stemmed from a lack of hygiene and room cleanliness.
-Although Chinese customers had solely positive keywords about cleanliness, English-speaking customers deemed many places unacceptable to their standards, particularly hotels with rooms priced below 50,000 yen per night.
-The most common complaint regarding cleanliness was about the carpet, followed by complaints about cigarette smell and lack of general hygiene.
-\cite{kozak2002} also proved that hygiene and cleanliness were essential satisfaction determinants for Western tourists.
-However, in the previous literature, this was linked merely to satisfaction.
-In contrast, our research revealed that words related to cleanliness were mostly linked to dissatisfaction.
-We could assert that Westerners had a high standard of room cleanliness compared to their Chinese counterparts.
-
-    According to previous research, Western tourists are already inclined to appreciate hospitality for their satisfaction.
-When presented with Japanese hospitality, this expectation is met and overcome.
-In contrast, according to our results, Chinese tourists were more concerned about room quality rather than hospitality, staff, or service.
-However, when analyzing the word pairs for ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great),'' we can see that they praise staff, service, and breakfast.
-By observing the percentage of hard to soft attributes in Figure \ref{fig:hard_soft_zh}, however, we discover that Chinese customers were more satisfied with hard attributes compared to Western tourists, who seemed to be meeting more than their expectations.
-
-    It could be considered that Chinese culture does not expect high-level service initially.
-When an expectation that is not held is met, the satisfaction derived is less than that if it was expected.
-In contrast, some tourists report a ``nice surprise'': when an unknown need is unexpectedly met, there is more satisfaction.
-It is necessary to note the difference between these two reactions.
-The ``nice surprise'' reaction fulfills a need unexpectedly.
-Perhaps the hospitality grade in Japan does not fulfill a need high enough for the Chinese population, thereby resulting in less satisfaction.
-For greater satisfaction, a need must be met.
-However, the word ``not bad'' is at the top of the list in most price ranges, and one of the uses is related to service.
-Thus, we cannot conclude that they were not satisfied with the service.
-Instead, they held other factors at a higher priority; thus, the keyword frequency was higher for other pairings.
-
-    Another possibility occurs when we observe the Chinese tourists’ dissatisfaction factors.
-Chinese tourists may have expectations about their treatment that are not being met, even in this high-standard hospitality environment.
-This could be because Japan is monolingual and has a relatively large language barrier to tourists \cite[][]{heinrich2012making,coulmas2002japan}.
-While the Japanese effort to accommodate English speakers is slowly developing, efforts for Chinese accommodations can be lagging.
-Chinese language pamphlets and Chinese texts on instructions for the hotel room and its appliances and features (e.g., T.V.
-channels, Wi-Fi setup, etc.), or the treatment towards Chinese people, could be examples of these accommodations.
-\cite{ryan2001} also found that communication difficulty was one of the main reasons Chinese customers would state for not visiting again.
-However, this issue is not exclusive to Japan.
-
-    Our initial question was whether the environment of high-grade hospitality would affect both cultures equally.
-This study attempted to determine the answer.
-It is possible that Chinese customers had high-grade hospitality and were equally satisfied with Westerners.
-In that case, it appears that the difference in perception stems from a psychological source; expectation leads to satisfaction and a lack of expectation results in lesser satisfaction.
-There is also a possibility that Chinese customers are not receiving the highest grade of hospitality because of cultural friction between Japan and China.
-
-    It is unclear which of these two is most likely from our results.
-However, competing in hospitality and service includes language services, especially in the international tourism industry.
-Better multilingual support can only improve the hospitality standard in Japan.
-Considering that most of the tourists in Japan come from other countries in Asia, multilingual support is beneficial.
-Proposals for this endeavor include hiring Chinese-speaking staff, preparing pamphlets in Chinese, or having a translator application readily available with staff trained in interacting through an electronic translator.
-
-  \subsection{Hard vs. soft satisfaction factors}\label{disc:hard_soft}
-
-    As stated in section \ref{theory_satisfaction}, previous research has mostly focused on the hotel's soft attributes and their influence on customer satisfaction \cite[e.g.,][]{shanka2004,choi2001}.
-Examples of soft attributes include staff behavior, commodities, amenities, and appliances that can be improved within the hotel.
-However, hard attributes are not usually analyzed in satisfaction studies.
-It is important to consider both kinds of attributes.
-If the satisfaction was based on soft attributes, a hotel can improve its services to attract more customers in the future.
-Otherwise, if the satisfaction was related more to hard attributes overall, hotels should be built considering the location while minimizing other costs.
-Because the satisfaction factors were decided statistically in our study via customers’ online reviews, we can see the importance of the hard or soft attributes in their priorities.
-
-    Figure \ref{fig:hard_soft_zh} shows that, in regards to Chinese customer satisfaction, in general, 68 \% of the top 10 keywords are hard factors; in contrast, only 20 \% are soft factors.
-The rates are similar for most price ranges except the highest-priced hotels.
-However, two of these soft attributes are all concentrated at the top of the list (``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad),'' ``\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)''), and the adjective pairs related to soft attributes of ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' are also at the top in most price ranges.
-Chinese tourists may expect spaciousness and cleanliness when coming to Japan.
-The expectation may be due to reputation, previous experiences, or cultural backgrounds.
-We can compare these results with previous literature, where traveling Chinese tourists choose their destination based on several factors, including cleanliness, nature, architecture, and scenery \cite[][]{ryan2001}.
-These factors found in previous literature could be linked to the keyword ``\begin{CJK}{UTF8}{gbsn}环境\end{CJK} (environment or surroundings)'' as well.
-This keyword was found for hotels priced at more than 20,000 yen per night.
-
-    In contrast, English speakers are mostly satisfied with the hotels' soft attributes.
-Figure \ref{fig:hard_soft_en} shows that soft attributes are above 48 \% in all price ranges, the highest being 65 \% in the price range of 15,000 to 20,000 yen per night, which corresponds to, for example, affordable business hotels.
-The exception to this is the hard attribute that is the hotels' location, which is consistently around the middle of the top 10 lists for all price ranges.
-
-    For both customer groups, the main reason for dissatisfaction was pricing, which can be interpreted as a concern about value for money.
-However, English-speaking customers complained less about the price in lower-priced hotels.
-In contrast, Chinese customers consistently had ``\begin{CJK}{UTF8}{gbsn}价格\end{CJK} (price)'' as the first or second-most concern across all price ranges.
-A study on Chinese tourists found that they had this concern \cite[][]{truong2009}.
-However, our results indicate that this has more to do with the pricing of hotels in Japan than with Chinese culture.
-In general, Japan is an expensive place to visit, thereby impacting this placement in the ranking.
-Space is scarce in Japan, and capsule hotels with cramped spaces of 2 x 1 meters cost around 3000 to 6000 yen per night.
-Bigger business hotel rooms are relatively expensive, ranging from 5000 to 12,000 yen per night.
-For comparison, hotels in the USA with a similar quality can charge half the price.
-
-    Around half of the dissatisfaction factors for both Chinese and Western customers are caused by issues that could be improved; this is true for all price ranges.
-The improvements could be staff training (perhaps in language), hiring professional cleaning services for rooms with cigarette smoke smells, or improving the bedding; however, these considerations can be costly.
-However, once the hotel's location and construction are set, only a few changes can be made to satisfy Chinese customers further.
-As mentioned previously, Chinese language availability is a soft attribute that can be improved with staff and training investment.
-
-    Western tourists are mainly dissatisfied with soft attributes.
-This is revealed by a low satisfaction level of 35 \% in the highest price range where undefined factors are the majority and a maximum of 78 \% in the price range of 30,000 to 50,000 yen per night in a hotel.
-Improvement scope for Western tourists is more extensive than that for their Chinese counterparts.
-As such, it presents a larger investment opportunity.
-
-  \subsection{Satisfaction across different price ranges}\label{disc:price}
-
-    In previous sections of this paper, we mentioned the differences reflected in hotel price ranges.
-The most visible change across differently priced hotels is the change in voice when describing satisfaction.
-We noticed this by observing the adjective-noun pairs and finding pairs with different adjectives for the same nouns.
-For example, in English, words describing nouns such as ``location'' or ``hotel'' are ``good'' or ``nice'' in lower-priced hotels.
-In contrast, the adjectives that pair with the same nouns for higher-priced hotels are ``wonderful'' and ``excellent.'' In Chinese, the change ranges from ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' to ``\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)'' or ``\begin{CJK}{UTF8}{gbsn}赞\end{CJK} (awesome).'' We can infer that the level of satisfaction is high and influences how customers write their reviews.
-Regarding the negative keywords, however, the change ranges from ``annoying'' or ``disappointing'' to ``worst.''
-
-    In this paper, we follow the definition of satisfaction by \cite{hunt1975}, where meeting or exceeding expectations produces satisfaction.
-Conversely, the failure of meeting expectations causes dissatisfaction.
-We can assume that a customer that pays more for a higher-class experience has higher expectations.
-For example, in a highly-priced hotel, any lack of cleanliness can lead to disappointment.
-In the case of English-speaking customers in the 30,000-–50,000 yen per night price range, cigarette smell is particularly disappointing.
-However, we consistently see customers with high expectations for high-class hotels reacting even more positively when satisfied.
-In the positive case, expectations appear to be exceeded in most cases, judging from their reactions.
-
-    We argue that these are two different kinds of expectations: logical and emotional.
-In the first case, customers are determined that the service must not fall below a specific standard; for example, they can be disappointed with unhygienic rooms or cigarette smell.
-In contrast, in the second case, customers have a vague idea of having a positive experience but do not measure it against any standard.
-For example, they expect a pleasant customer service experience or a hospitable treatment by the staff at a high-class hotel.
-Regardless of their knowledge in advance, positive emotions offer them a perception of exceeded expectations and high satisfaction.
-Thus, hospitality and service enhance the experience of the customers.
-
-    There are interesting differences between Chinese and English-speaking tourists in their satisfaction to differently priced hotels.
-For example, Chinese tourists have ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' as a top keyword in all the price ranges.
-In contrast, English-speaking tourists mention it only as a top keyword in the 20,000–-30,000 yen price range.
-It is widely known in Japan that many Chinese tourists visit Japan for shopping.
-\cite{tsujimoto2017purchasing} analyzed the souvenir purchasing behavior of Chinese tourists in Japan and showed that common products besides food and drink are: electronics, cameras, cosmetics, and medicine, among \textit{souvenir} items representative of the culture or places that they visit \cite{japan2014consumption}.
-Furthermore, Chinese tourists’ choice to shop in Japan is more related to the quality of the items rather than their relation to the tourist attractions.
-Our results suggested that Western tourists were engaging more in tourist attractions rather than shopping activities compared to Chinese tourists.
-
-    Another interesting difference is that English-speaking tourists start using negative keywords about the hotel's price only if it concerns hotels of 15,000 yen or more; thereafter, the more expensive the hotel, the higher the ranking.
-In contrast, for Chinese customers, this keyword is the top keyword across all price ranges.
-Previous research suggests that value for money is a key concern for Chinese and Asian tourists \cite[][]{choi2000,choi2001,truong2009}, whereas Western customers are more concerned about hospitality \cite[][]{kozak2002}.
-
-    While some attributes' value changes depending on the hotel's price range, some other attributes remain constant for each culture's customers.
-For example, appreciation for staff from English-speaking tourists is ranked close to the top satisfaction factor in all the price ranges.
-Satisfaction for cleanliness by both cultures constantly remains part of the top 10 keywords, except for the most expensive one, where other keywords replace keywords related to satisfaction or cleanliness in the ranking; however, they remain still high on the list.
-Chinese tourists have a high ranking for the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' across all price ranges as well.
-As discussed in section \ref{disc:location}, transportation and location are also important for hotels of all classes and prices.
-While the ranking of attributes might differ between price ranges, hard and soft attribute proportions also appear to be constant within a 13 \% margin of error per attribute.
-This suggests that, from a cultural aspect, the customers have a particular bias to consider some attributes more than others.
-
-  \subsection{Cross-culture analysis of expectations and satisfaction}\label{disc:culture}
-
-    The basic premise of this study is that different cultures lead to different expectations and satisfaction factors.
-This premise also plays a role in the differentiation between the preferences of hard or soft attributes.
-
-    In \cite{donthu1998cultural}, subjects from 10 different countries were compared with respect to their expectations of service quality and analyzed based on Hofstede's typology of culture \cite[][]{hofstede1984culture}.
-The previous study states that, although culture has no specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others.
-These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism–-collectivism}, \textit{masculinity–femininity}, and \textit{long-term-–short-term orientation}.
-In each of these dimensions, at least one element of service expectations was found to be significantly different for countries grouped under contrasting attributes (e.g., individualistic countries vs.
-collectivist countries, high uncertainty avoidance countries vs.
-low uncertainty avoidance countries).
-
-    However, Hofstede's typology has received criticism from academics, particularly for the fifth dimension that Hofstede proposed, which was later added with the alternative name \textit{Confucian dynamic}.
-Academics with a Chinese background criticized Hofstede for being misinformed on the philosophical aspects of Confucianism as well as considering a difficult dimension to measure \cite[][]{fang2003critique}.
-Other models, such as the GLOBE model, also consider some of Hofstede's dimensions and replace them with others, making a total of nine dimensions \cite[][]{house1999cultural}.
-The \textit{masculinity–-femininity} dimension, for example, is proposed to be instead of two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}.
-This addition of dimensions avoids assuming that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes.
-Such gender stereotypes have also been the subject of critique on Hofstede's model\cite[][]{jeknic2014gender}.
-We agree with these critiques and thus avoid considering such stereotypes in our discussion.
-
-    For our purposes of contrasting Western vs.
-Chinese satisfaction stemming from expectations, these dimensions could explain why Chinese customers are generally satisfied more often with hard factors while Westerners are satisfied or dissatisfied with soft factors.
-
-    The backgrounds of collectivism in China and individualism in Western countries have been studied previously \cite[][]{gao2017chinese, kim2000}.
-These backgrounds as well as the differences in these cultural dimensions could be the underlying cause for differences in expectations.
-Regardless of the cause, however, measures in the past have proven that such differences exist \cite[][]{armstrong1997importance}.
-
-    The cultural background of Chinese tourists emphasizes their surroundings and their place in nature and the environment.
-Chinese historical backgrounds of Confucianism, Taoism, and Buddhism permeate the thought processes of Chinese populations.
-However, scholars argue that the changes in generations and their economic and recent history attaches less importance to these concepts in their lives \cite[][]{gao2017chinese}.
-Nevertheless, one could argue a Chinese cultural attribute emphasizes that the environment and the location affect satisfaction rather than the treatment they receive.
-
-    A more anthropocentric and individualistic Western culture could correlate more of their expectations and priorities to the treatment in social circumstances rather than the environment.
-According to \cite{donthu1998cultural}, highly individualistic customers, in contrast to collectivist customers, have a higher expectation of empathy and assurance from the provider, which are aspects of service, a soft attribute of a hotel.
-
-    Among other dimensions in both models, we can consider uncertainty avoidance.
-Customers of high uncertainty avoidance carefully plan their travel and thus have higher expectations towards service.
-In contrast, customers of lower uncertainty avoidance do not take risks in their decisions and thus face less disappointment with different expectations.
-However, according to \cite{xiumei2011cultural}, the difference between China and the USA in uncertainty avoidance is not clear when measuring with the Hofstede typology and the GLOBE typology.
-While the USA is not representative of Western society, uncertainty avoidance may not cause the difference in hard-soft attribute satisfaction between Chinese and Western cultures.
-Differences in another factor, power distance, were also noted when using  Hofstede's method compared to the GLOBAL method; therefore, power distance was not considered for comparison.
-
-  \subsection{Implications for hotel managers}\label{disc:implications}
-
-    Our study reached two important conclusions: one about hospitality and cultural differences and another about managerial decisions towards two different populations.
-Overall, Chinese tourists did not attach much importance to hospitality and service factors.
-Instead, they focused on the hard attributes of a hotel.
-In particular, they were not satisfied with hospitality as much as Western tourists were; otherwise, they felt that basic language and communication needs were not met; thereby, they were not much satisfied.
-Western tourists were highly satisfied with Japanese hospitality and preferred soft attributes to hard ones.
-
-    The other conclusion is that managerial decisions could mostly benefit Western tourists, except for language improvements and breakfast inclusion could satisfy both groups.
-As mentioned earlier in this paper, Westerners are ``long-haul'' customers, spending more of their budget on lodging than Asian tourists \cite[][]{choi2000}.
-With bigger returns on managerial improvements, we recommend investing in improving attributes that dissatisfy Western customers, such as cleanliness and removing tobacco smell.
-In addition, breaking the language barrier is one of the few strategies to satisfy both groups.
-Recently, Japan has been facing an increase in Chinese students as well as students of Western universities.
-Hiring students as part-time workers could increase the language services of a hotel.
-
-    To satisfy both customer types, hotel managers need to invest in cleanliness, deodorizing, and making hotel rooms tobacco-free.
-It could also be recommended to invest in breakfast inclusion and multilingual services and staff preparedness to deal with Chinese and English speakers.
-Western tourists were also observed to have high comfort standards, which could be managerially improved for better reviews.
-Perhaps it could be suggested to perform surveys of the bedding that is most comfortable for Western tourists.
-However, not all hotels can invest in all of these factors simultaneously.
-Our results suggest that satisfying cleanliness needs could satisfy both customer types.
-We suggest investing in making the facilities tobacco-free.
-Our results are also divided by price ranges; thereby, a hotel manager could consider which analysis suits their hotel the most.
-Hard attributes are difficult to change; however, improvements in service can be made to accompany these attributes.
-For example, transportation guides for foreigners that might not know the area could increase satisfaction.
-
-    The managers must consider their business model for implementing the next strategy.
-One option could be attracting more Chinese customers with their observed low budgeting.
-Another could be attracting more big-budget Western customers.
-For example, investing more in cleanliness could improve Western customers looking for high-quality lodging satisfaction, even for an increased price per night.
-On the other hand, hotels might be deemed costly by Chinese customers wherever such an investment is made.
-
-\section{Limitations and Future Work}\label{limitations}
-
-  In this study, we analyzed keywords based on whether they appeared on satisfied reviews or dissatisfied ones.
-Following that, we attempted to understand these words' context by using a dependency parser and observing the related nouns.
-However, a limitation is that it analyzed solely the words directly related to each keyword and did not search for further connections.
-This means that if the words were used in combination with other keywords, we did not trace the effects of multiple contradicting statements.
-For example, in the sentence ``The room is good, but the food is lacking,'' we extracted ``good room'' and ``lacking food'' but did not consider the fact that both occurred in the same sentence.
-
-  This study analyzed the differences in customers' expectations at different levels of hospitality and service factors by dividing our data into price ranges.
-However, in the same price range, for example, the highest one, we can find both a Western-style five-star resort and a high-end Japanese style \textit{ryokan}.
-Services offered in these hotels are of high quality, albeit very different.
-Nevertheless, most of our database was focused on the middle range priced hotels, the services of which are comparably less varied.
-
-  An essential aspect of this study is that we focused on the satisfaction and dissatisfaction towards the expectations of individual aspects of the hotels.
-This gave us insight into the factors that hotel managers can consider.
-However, each customer's overall satisfaction was not measured since it would require methods that are out of the scope of this paper.
-Another limitation is that further typology analysis could not be made because of the nature of the data collected (for example, Chinese men and women of different ages or their Westerner counterparts).
-
-  In future work, we plan to investigate these topics further.
-We plan to extend our data to research different trends and regions of Japan, different kinds of hotels, and customers traveling alone or in groups, whether for fun or for work.
-Another point of interest in this study's future work is to use word clusters with similar meanings instead of single words.
-
-\section{Conclusion}\label{conclusion}
-
-  In this study, we analyzed the differences in satisfaction and dissatisfaction between Chinese and English-speaking customers of Japanese hotels, particularly in the context of Japanese hospitality, \textit{omotenashi}.
-We extracted keywords from their online reviews on \textit{Ctrip} and \textit{TripAdvisor} using Shannon's entropy calculations.
-We used these keywords for sentiment classification via an SVC.
-We then used dependency parsing and part of speech tagging to extract common pairs of adjectives and nouns as well as single words.
-We divided these data by sentiment and hotel price range (most expensive room/night).
-
-  We found that Western tourists were most satisfied with staff behavior, cleanliness, and other soft attributes.
-However, Chinese customers had other concerns for their satisfaction; they were more inclined to praise the room, location, and hotel's convenience.
-We found that the two cultures had different reactions to the hospitality environment and the prices.
-Thus, we discussed two possible theories on why Chinese tourists responded differently from Westerners in the environment of \textit{omotenashi}.
-One theory is that, although they were treated well, their experience was deteriorated by language or culture barriers.
-The second possible theory is that they reacted to hospitality differently since they did not have the same expectations.
-We theorized that a lack of expectations could result in lessened satisfaction than that to the same service if expected.
-On the other hand, even when they held high expectations in a high-priced hotel, Japanese hospitality exceeded Western tourists’ expectations, judging by their vocabulary for expressing their satisfaction.
-We considered that Western tourists were more reactive to hospitality and service factors Chinese tourists.
-
-  Lastly, we measured the satisfaction and dissatisfaction factors, that is, a hotel's hard and soft attributes.
-Hard attributes are physical and environmental elements, and as such, are impractical elements to change.
-In contrast, soft attributes can be changed via management and staff by an improvement in services or amenities.
-We found that, for satisfaction, Western tourists favored soft attributes in contrast to Chinese tourists, who were more interested in the hard attributes of hotels across all the price ranges consistently.
-For dissatisfaction, Western tourists were also highly inclined to criticize soft attributes, such as cleanliness or cigarette smell in rooms.
-In contrast, Chinese tourists' dissatisfaction derived from both hard and soft attributes evenly.
-
-  One approach for hotel managers is to work to satisfy Chinese tourists more, who dedicate a lower percentage of their budget to hotels but are more numerous.
-They are less satisfied with soft attributes but have an identifiable method for improving satisfaction by lessening language barriers and providing a satisfactory breakfast.
-Another approach was focused on the cleanliness, comfort, and tobacco-free space expected by Western tourists.
-``Long-haul'' Western tourists, who spend almost half of their budget on hotels with this strategy, were favored.
-Although Westerners are less in number than Chinese tourists, it could be proven that they have more substantial returns.
-This is because Chinese customers also favor cleanliness as a satisfaction factor, and both populations could be pleased.
-
-\begin{acknowledgements}
-
-  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation.
-We would like to show gratitude to Mr.
-Liangyuan Zhou, Ms.
-Min Fan, and Ms.
-Eerdengqiqige for this.
-
-  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.
-
-  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).
-
-  Conflict of interest: none
-
-\end{acknowledgements}
-
-% \section*{References}
-
-\bibliography{bibfile-emotion}
-
-\end{document}

### 2021-04-13 1_manuscript/cur_dir_my_latexdiff.sh

@@ -1,1 +1,1 @@
-../my_latexdiff.sh itt-emotion_V6-6.tex itt-emotion.tex --newversion="7-1" --compile --clean --view
+../my_latexdiff.sh itt-emotion_V6-6.tex itt-emotion.tex --newversion="7-2" --compile --clean --view

### 2021-04-14 0_coverletter/itt-emotion-coverletter.tex
Edited V7-2 a bit in Intro and made cover letter

@@
 
-We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures" for further review by Information Technology \& Tourism.
+We wish to submit a revision for an original research paper JITT-D-19-00095, which is currently under the title "Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach" for further review by Information Technology \& Tourism.
 
-We appreciate the consideration by your journal, the extensive reviews and are grateful for the opportunity to revise this further.
-This was a minor revision, with a few additions to the reviewed literature.
+We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem.
+Therefore, in this revision, we made a few changes to the structure of section "3.
+Theoretical background and hypothesis development", adding more literature we reviewed, and added to the Abstract, Introduction, and Research objective sections as well.
 
-As stated before, We found that while Western customers are satisfied with mostly soft factors as well as Japanese hospitality and service, Chinese customers are more inclined to be satisfied with hard factors (such as location, transport, size of the room), and that while they are satisfied with hospitality, in exception of a lack of Chinese language service, they do prioritize hospitality in their satisfaction while staying at Japanese hotels.
-We discuss theories on the reason behind this in our revised paper.
-We also found that Chinese tourists in Japan are interested in shopping at all price ranges of hotels, while Western tourists are more inclined to shop when staying in middle to high-priced hotels.
+In the abstract, we added a concise background of why we are interested in a cross-culture study using a large data-base.
+In the introduction, we add citations to clarify the influence of culture on expectations, perceptions of quality and satisfaction, and the importance to analyze the difference between Chinese and Western tourists specifically in Japan (l.17-l.27, l.37-l.41).
+We also added on the necessity to do this analysis on a large scale with automatic methodologies (l.60-l.67).
+We also added to the research objective section to clarify the reasoning behind the objective (l.92-l.95).
 
-We believe this was an appropriate response to the minor revision, and hope we continue to be in your consideration.
+In the Theoretical background section, we moved the section "3.1 Japanese hospitality and service: \textit{Omotenashi}" to 3.3, and talked about the theory behind satisfaction, expectations, and their relationship to culture in the new sections 3.1 and 3.2, which add content and citations to what previously was section "3.2 Customer satisfaction and dissatisfaction towards individual factors during hotel stay".
+It was split into two sections to avoid going off topic, since one of them explains the theory of expectations leading to satisfaction, while the other one explains the theory behind our approach to studying the customers' satisfaction.
+Lastly, we added a section "3.4 Customer expectations beyond service and hospitality" to explain the reasoning behind studying hard and soft attributes better.
+
+We believe this was an appropriate response to the major revision, and hope we continue to be in your consideration.
 

### 2021-04-14 1_manuscript/itt-emotion.tex
Edited V7-2 a bit in Intro and made cover letter

@@
         \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com}, 
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
+                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
+                    \hspace*{1em} ORCID: 0000-0002-6437-0866
                 \and
@@
                 \and 
-                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \and
-                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
+                    \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
+                \at 
+                    \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
         }
@@
 Thus, it could be theorized that their satisfaction factors should be different.
+
   The Japanese tourist market is gradually becoming diverse because of multicultural tourist populations.
 This diversity means that the expectations when staying at a hotel will be varied.
-Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
-
-  Our study focuses on Western and Chinese tourists, considering their numbers.
-Chinese tourists accounted for 25.63\% of the tourist population.
+Cultural backgrounds have a decisive role in aspects of satisfaction and in the perceptions of quality \cite[][]{mattila1999role,winsted1997service}, or behavioral intentions \cite[][]{liu2001relationships}, such as the difference in Westerners and Asians in their willingness to pay more \cite[][]{LEVY2010319}.
+A difference in cultural background can also heavily influence customers' expectations, as well as their perceptions of quality, and the difference between these two is what expresses itself as satisfaction.
+This difference in expectations and perceptions of quality can be smaller or larger depending on the culture in reaction to the same service.
+
+  For a growing industry with increasing cultural diversity, it is essential to identify the cross-culture expectations of customers in order to provide the appropriate services, cater to these expectations to ensure and increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.
+
+  In 2017, Chinese tourists accounted for 25.63\% of the tourist population.
 On the other hand, Western countries accounted for 11.4\% of the total, and 7.23\% were countries where English is the official or the de facto national language \cite[][]{jnto2003-2019}.
-The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}.
+The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon, \cite[][]{sun2017}.
 Despite this, many tourist-behavior analyses have been performed only involving Western subjects.
+Yet, it is known that Western and Asian customers are heavily differentiated\cite[][]{LEVY2010319}.
 As such, a knowledge gap existed until recent decades.
+Considering the numbers of inbound tourists in Japan and our team's language capabilities, our study focuses on Western and Chinese tourists.
 

### 2021-04-16 0_coverletter/itt-emotion-coverletter.tex
7-2 cover letter improved. READY FOR SUBMISSION

@@
 \addtolength{\headheight}{-11em}
-\addtolength{\textheight}{10em}
-\addtolength{\textwidth}{8em}
+\addtolength{\textheight}{20em}
+\addtolength{\textwidth}{10em}
 \addtolength{\oddsidemargin}{-6em}
@@
 
-We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem.
+We appreciate the consideration by your journal, and took the comment in your decision to add to the theoretical reasoning behind the research problem to heart.
+In our revision, we explain further our theoretical interest in the differences between Chinese and Western tourists when faced with Japanese hospitality, and other factors in Japanese hotels.
+A cross-cultural examination of the satisfaction for these factors is indeed our main purpose.
+
+In our literature review, we explain how satisfaction is the realization of an expectation, or rather, the perception of that realization.
+The difference between expectation and perception is what amounts to satisfaction.
+However, we find that both expectations and perceptions of quality are heavily influenced by cultural backgrounds.
+So not only is the expectations tourists would have when visiting Japan, but after experiencing the services influenced by the \textit{Omotenashi} culture, their perceptions of these services can be different.
+Adding to that, the numbers of tourists in Japan is increasing, and Chinese and Western tourists are the two largest populations of tourists.
+This is the reasoning behind our interest in this research problem.
+
 Therefore, in this revision, we made a few changes to the structure of section "3.
-Theoretical background and hypothesis development", adding more literature we reviewed, and added to the Abstract, Introduction, and Research objective sections as well.
+Theoretical background and hypothesis development", adding more literature we reviewed to back our interest in this research, and added to the Abstract, Introduction, and Research objective sections as well.
 

### 2021-05-19 2_revisions/V7-2_ITT_accepted/0_manuscript_blind/itt-emotion_blind_V7-2.tex
V7-2 accepted yay

--- 2021-04-14 1_manuscript/itt-emotion.tex
@@
 
-        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
-                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
-                Hirofumi Nonaka                                                 \protect\affmark[1] \and
-                Toru Hiraoka                                                    \protect\affmark[2]
-        }
-
-        \authorrunning{E. Alemán Carreón et al.}
-
-        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
-                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
-                    \hspace*{1em} ORCID: 0000-0002-6437-0866
-                \and
-                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
-                    \hspace*{1em} \email{mendoza.espana@gmail.com}
-                \and
-                    \hspace*{1em} Hirofumi Nonaka \at
-                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
-                \and
-                    \hspace*{1em} Toru Hiraoka \at
-                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
-                \and 
-                    \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
-                \at 
-                    \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
-        }
+        \author{REDACTED}
+
+        \authorrunning{REDACTED}
+
+        \institute{REDACTED}
 
